### 2019-12-02 main.tex
Initial Overleaf Import

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{float}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage{natbib}
\usepackage{caption}
\usepackage{blkarray}
\usepackage{todonotes}

\input{mathdef.tex}

\title{An Integrated Framework for Robust Estimation, Prediction and Control}
\author{Edouard Leurent, Denis Efimov, Odalric-Ambrym Maillard}
\date{November 2019}

\begin{document}

\maketitle

\section{Problem formulation}

\paragraph{Structured dynamics}
We consider a system with continuous state space $\Real^p$ and dynamics in the form:

\begin{equation}
\label{eq:dynamics}
\dot{x}(t)=A(\theta)x(t)+B_u u(t) + B_\omega \omega(t),\;t\geq0,
\end{equation}
\todo[inline]{EL: merge notations of the system with and without command $u$}
where $\theta$ belongs to some compact set $\Theta \subset \Real^d$, $A(\theta)\in\Real^{p\times p}$ and $\omega$ is a bounded disturbance: $\underline{\omega}(t)\leq \omega(t)\leq\overline{\omega}(t)$ for all $t\geq0$.

\paragraph{Robust objective}

We wish to find a sequence of commands $\pi=(u(t))_{t\geq 0}$ that maximises the robust control objective $v^r$:
\todo[inline]{EL: since the interval dynamics will be deterministic, use open-loop policies, ie sequences of actions $\mathbf{u}$ instead of closed-loop policies $\pi$}

\begin{equation}
\label{eq:robust-control}
\max_\pi \underbrace{\min_{\theta \in \Theta} \expectedvalueover{\omega(t)}\left[\sum_{t=0}^\infty \gamma^t r(x(t))\condbar \dot{x}(t) = A(\theta) x(t) + B_u u(t) + B_\omega\omega(t), u_t = \pi(x_t)\right]}_{v^r(\pi)}
\end{equation}

\section{Model Estimation}

\paragraph{Objective}% The model estimation procedure is dedicated to building a confidence region around the unknown true model $A(\theta)$. 
Having observed a history of transitions $\cD = \{(x(t_n), u(t_n), x(t_n+dt))\}_{n\in[N]}$, and given a confidence level $\delta\in[0, 1]$, our goal is to find a confidence region $\cC_\delta$ as tight as possible and such that it holds that:
\begin{align}
\probability{A(\theta)\in \cC_\delta} \geq 1-\delta
\label{eq:polytope}
\end{align}

This involves the trilemma of confidence intervals, where one of three things must be true:
\begin{itemize}
    \item $A(\theta)$ is in $\cC_\delta$
    \item We got data that was very ($\leq\delta$) unlikely under all possible values $A(\theta)$
    \item Our model is wrong
\end{itemize}

\begin{assumption}[Linear Parametrization]
\label{assum:linear_param}
We further assume that the dynamics $A(\theta)$ enjoy the following additional structure:
\begin{equation}
    A(\theta) = \theta^T \phi
\end{equation}
where $\phi\in \Real^{d \times p \times p}$.
\end{assumption}

We stack the $N$ observations and noises of $\dot{x}(t), x(t), B_u u(t)$ and $B_\omega \omega(t)$ in $\cD$ as $\dot{X}_{[N]}, X_{[N]}, U_{[N]}, \eta_{[N]}^T \in\Real^{p\times N}$, we obtain the regression problem:

\[\dot{X}_{[N]} = \theta^T\phi X_{[N]} + U_{[N]} + \eta_{[N]}\]

This can be rewritten in a canonical form as:
\begin{equation}
    \label{eq:regression}
    Y_{[N]} = \Phi_{[N]} \theta + \eta_{[N]},
\end{equation}
with $Y_{[N]} = \dot{X}_{[N]}^T - U_{[N]}^T  \in\Real^{N\times p}, \Phi_{[N]} = (\phi X_{[N]})^T\in \Real^{N\times p\times d}$; and the assumptions on the noise $\eta_{[N]} \in\Real^{N\times p}$ will be described further.

\paragraph{Regularized solution} Since we expect that $\Phi x(t)$ may have zero-coordinates on long time intervals (i.e. some features are not always active), we consider the $l_2$ regularization with parameter $\lambda\in\Real^+_*$:

\begin{equation*}
    \min_{\theta\in\Real^d} \|Y - \Phi \Theta\|_2^2 + \lambda\|\theta\|_2^2
\end{equation*}

The solution can be obtained by differentiation:

\begin{equation*}
    \theta_{N,\lambda} = G_{N, \lambda}^{-1} \Phi^T_{[N]}Y_{[N]} + \lambda I, \quad \text{where } G_{N, \lambda} = X^T_{[N]}X_{[N]} + \lambda I.
\end{equation*}

\paragraph{Confidence ellipsoid}

We consider the noise vector $\eta(t) = B_\omega \omega(t)\in\Real^p$. Since $\omega$ is bounded, $\eta$ is also bounded by $R=\sup_{t\geq 0}\|B_\omega \omega(t)\|_2^2$, and hence $\eta(t)$ is a $R$-subgaussian vector: $\eta(t)\sim \text{SubG}_p(R)$.

This also implies that each component $\eta_i(t)$ for $i\in[p]$ is itself $R$-subgaussian. Consequently, by flattening the two first $N\times p$ dimensions of $Y_{[N]}, \Phi_{[N]}$ and $\eta_{[N]}$ to a single $Np$ dimension in \eqref{eq:regression}, we recover the conditions of scalar linear regression. We can apply the following theorem:

\begin{theorem}[Theorem 2 of \citet{Abbasi2011}] Assuming that $\|\theta\|_2\leq S$, it holds with probability $1-\delta$ that:
\begin{equation*}
    \|\theta - \theta_{N,\lambda}\|_{G_{N,\lambda}} \leq R\sqrt{2\log \frac{\text{det}(G_{N,\lambda})^{1/2}\text{det}(\lambda I)^{-1/2}}{\delta}} + \lambda^{1/2}S
\end{equation*}
\end{theorem}

\paragraph{Confidence polytope}

Given a confidence ellipsoid $C_\delta$, we can enclose it by a polytope $P_\delta$:
\[\cC_\delta \subset \cP_\delta\]
where $\cP_\delta$ can be written as:
\begin{equation}
     \exists A_0,\Delta A_{1:p}: \cP_\delta = \left\{ A_{0}+\sum_{i=1}^{p}\lambda_{i}\Delta A_{i}: \lambda\in[0, 1]^p,  \sum_{i=1}^{p}\lambda_{i}=1\right\}.
\end{equation}

\section{State Prediction}

In this section, we assume that we found a high-confidence polytope that verifies \eqref{eq:polytope} with probability $1-\delta$.

The objective of the prediction procedure, as illustrated in \autoref{fig:interval-hull} is to design an \emph{interval predictor} for the system \eqref{eq:dynamics}, which takes the information on the observed current state ${x}({0})$, the admissible bounds on the perturbation $[\underline{\omega}(t),\overline{\omega}(t)]$, and the model polytope $\cP_\delta$, and verifies the inclusion property:
\begin{equation}
\label{eq:interval_property}
\underline{x}(t)\leq x(t)\leq\overline{x}(t),\quad\forall t\geq0.
\end{equation}

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{img/interval-hull}
    \caption{A few trajectories are sampled from an initial state $x_0$ following a policy $\pi=(u_0,\cdots)$ with various parameters $\theta$ (in black). The union of reachability sets is shown in green, and its interval hull in red.}
    \label{fig:interval-hull}
\end{figure}

In order to use the interval predictor from \citep{leurent2019interval}, we also require $A_0$ to be Metzler. This can be ensured under some conditions:

\begin{lemma}[Similarity transformation \citep{Efimov_a2013}]
\label{lem:metzler} Let $D\in\Xi\subset\Real^{n\times n}$ be a matrix variable satisfying the interval constraints $\Xi=\{D\in\Real^{n\times n}:\,D_{a}-\Delta\le D\le D_{a}+\Delta\}$ for some $D_{a}^{\text{T}}=D_{a}\in\Real^{n\times n}$ and $\Delta\in\Real_{+}^{n\times n}$. If for some constant $\mu\in\Real_{+}$ and a diagonal matrix $\Upsilon\in\Real^{n\times n}$ the Metzler matrix $Y=\mu E_{n\times n}-\Upsilon$ has the same eigenvalues as the matrix $D_{a}$, then there is an orthogonal matrix $S\in\Real^{n\times n}$ such that the matrices $S^{\text{T}}DS$ are Metzler for all $D\in\Xi$ provided that $\mu>n||\Delta||_{max}$.\textup{ }
\end{lemma}

\begin{theorem}[Interval Predictor \citep{leurent2019interval}]
\label{thm:predictor}
Assuming that \eqref{eq:polytope} is satisfied for the system \eqref{eq:dynamics}, then the interval predictor:
\begin{eqnarray}
\dot{\underline{x}}(t) & = & A_{0}\underline{x}(t)-\Delta A_{+}\underline{x}^{-}(t)-\Delta A_{-}\overline{x}^{+}(t)\nonumber \\
 &  & +B^{+}\underline{\omega}(t)-B^{-}\overline{\omega}(t),\nonumber\\
\dot{\overline{x}}(t) & = & A_{0}\overline{x}(t)+\Delta A_{+}\overline{x}^{+}(t)+\Delta A_{-}\underline{x}^{-}(t) \label{eq:interval_predictor} \\
 &  & +B^{+}\overline{\omega}(t)-B^{-}\underline{\omega}(t),\nonumber \\
 &  & \underline{x}(0)=\underline{x}_{0},\;\overline{x}(0)=\overline{x}_{0}\nonumber 
\end{eqnarray}
ensures the inclusion property \eqref{eq:interval_property}. If there exist diagonal matrices $P$, $Q$, $Q_{+}$, $Q_{-}$, $Z_{+}$, $Z_{-}$, $\Psi_{+}$, $\Psi_{-}$, $\Psi$, $\Gamma\in\Real^{2n\times 2n}$ such that the following LMIs are satisfied:
\begin{gather*}
P+\min\{Z_{+},Z_{-}\}>0,\;\Upsilon\preceq0,\;\Gamma>0,\\
Q+\min\{Q_{+},Q_{-}\}+2\min\{\Psi_{+},\Psi_{-}\}>0,
\end{gather*}
where{\footnotesize{}
\begin{gather*}
\Upsilon=\left[\begin{array}{cccc}
\Upsilon_{11} & \Upsilon_{12} & \Upsilon_{13} & P\\
\Upsilon_{12}^{\top} & \Upsilon_{22} & \Upsilon_{23} & Z_{+}\\
\Upsilon_{13}^{\top} & \Upsilon_{23}^{\top} & \Upsilon_{33} & Z_{-}\\
P & Z_{+} & Z_{-} & -\Gamma
\end{array}\right],\\
\Upsilon_{11}=\mathcal{A}^{\top}P+P\mathcal{A}+Q,\;\Upsilon_{12}=\mathcal{A}^{\top}Z_{+}+PR_{+}+\Psi_{+},\\
\Upsilon_{13}=\mathcal{A}^{\top}Z_{-}+PR_{-}+\Psi_{-},\;\Upsilon_{22}=Z_{+}R_{+}+R_{+}^{\top}Z_{+}+Q_{+},\\
\Upsilon_{23}=Z_{+}R_{-}+R_{+}^{\top}Z_{-}+\Psi,\;\Upsilon_{33}=Z_{-}R_{-}+R_{-}^{\top}Z_{-}+Q_{-},\\
\mathcal{A}=\left[\begin{array}{cc}
A_{0} & 0\\
0 & A_{0}
\end{array}\right],\;R_{+}=\left[\begin{array}{cc}
0 & -\Delta A_{-}\\
0 & \Delta A_{+}
\end{array}\right],\;R_{-}=\left[\begin{array}{cc}
\Delta A_{+} & 0\\
-\Delta A_{-} & 0
\end{array}\right],
\end{gather*}
}then the predictor \eqref{eq:interval_predictor} is input-to-state stable with respect to the inputs $\underline{\omega}$, $\overline{\omega}$.
\end{theorem}

\begin{example*}
Consider a scalar system:
\[
\dot{x}(t)=-\theta(t)x(t)+d(t),\;t\geq0,
\]
where $x(t)\in\Real$ with $x(0)\in[\underline{x}_{0},\overline{x}_{0}]=[1.0, 1.1]$, $\theta(t)\in\Pi=[\underline{\theta},\overline{\theta}]=[0.5,1.5]$ and $d(t)\in[\underline{d},\overline{d}]=[-0.1,0.1]$ for all $t\geq0$. The \autoref{fig:predictor_example} shows the state-interval obtained with \eqref{eq:interval_predictor}.

\begin{figure}
\begin{centering}
\includegraphics[width=\linewidth]{img/interval_predictor}
\par\end{centering}
\caption{Several trajectories for different values of $\theta\in\Theta$ are shown in blue. The result of prediction by \eqref{eq:interval_predictor} is in red: the predictor is stable and produces tight bounds.}
\label{fig:predictor_example}
\end{figure}
\end{example*}

\section{Control}

In this section, we still assume that we have a high-confidence polytope $\cP$ that verifies \eqref{eq:polytope} with probability $1-\delta$.

\begin{definition}[Surrogate objective]
We modify the robust objective $v^r$ in \eqref{eq:robust-control} by replacing the true reachability set by its interval prediction $[\underline{x}(t), \overline{x}(t)]$ based on the polytopic approximation $\cP_\delta$ of $A(\Theta)$:

\begin{equation}
\hat{v^r}(\pi) \eqdef \sum_{t=0}^\infty \gamma^t \min_{x\in[\underline{x}(t, \pi), \overline{x}(t, \pi)]}  r(x)
\end{equation}
where $\underline{x}(t, \pi), \overline{x}(t, \pi)$ follow the dynamics defined in \eqref{eq:interval_predictor}.
\end{definition}

\begin{algorithm}[tp]
  \SetAlgoLined\DontPrintSemicolon
  \SetKwFunction{algo}{robust\_control}
  \SetKwFunction{proc}{pessimistic\_reward}
  \SetKwProg{myalg}{Algorithm}{}{}
  \myalg{\algo{$s_0$}}{
  \While{resources available}
  {
  Generate a candidate sequence $\pi$ with a planning algorithm using \proc{} instead of the true rewards.
  }
  \KwRet $\argmax_{\pi\in\Pi} \hat{v^r}(\pi)$ \;}{}
  \setcounter{AlgoLine}{0}
  \SetKwProg{myproc}{Procedure}{}{}
  \myproc{\proc{$s_0$, $\pi$, T}}{
  Integrate \eqref{eq:interval_predictor} over $[0,t]$ with commands $\pi$ to compute $[\underline{x}(t), \overline{x}(t)]$\;
  \KwRet $\min_{x\in[\underline{x}(t), \overline{x}(t)]} r(x)$\;}
\caption{Interval-based Robust Control}
\label{algo:irc}

\end{algorithm}

\begin{property}[Lower bound]
\label{prop:lower-bound}
With high probability, the surrogate objective $\hat{v^r}$ is a lower bound of the true objective $v^r$:

\begin{equation}
\probability{\forall \pi, \hat{v^r}(\pi) \leq v^r(\pi)} \geq 1-\delta
\end{equation}
\end{property}

\begin{proof}
Let $\theta\in\Theta$, by \autoref{thm:confidence_interval} we have that $A(\theta) \in \cP$ with probability $1-\delta$. Whenever it is the case, we have by \autoref{thm:predictor} that the inclusion property \eqref{eq:interval_property} is verified by the interval predictor \eqref{eq:interval_predictor} for all $\omega(t)\in[\underline{\omega}(t), \overline{\omega}(t)]$. This gives the following bound:
\begin{equation*}
 \sum_{t=0}^\infty \gamma^t r(x_t) \geq \sum_{t=0}^\infty \min_{x\in[\underline{x}(t, \pi), \overline{x}(t, \pi)]} \gamma^t r(x) = \hat{v^r}(\pi)
\end{equation*}

And finally, with probability $1-\delta$,
\begin{align*}
v^r(\pi) &= \min_{A(\theta) \in A(\Theta)} \expectedvalueover{\omega(t)}\left[\sum_{t=0}^\infty \gamma^t r(x_t)\right] \\
&\geq \min_{A \in \cP} \expectedvalueover{\omega(t)}\left[\sum_{t=0}^\infty \gamma^t r(x_t)\right] \\
& \geq \min_{A \in \cP} \expectedvalueover{\omega(t)}\left[\hat{v^r}(\pi)\right] = \hat{v^r}(\pi)
\end{align*}
\end{proof}

The robust objective error $v^r - \hat{v^r}$ stems from two terms: the approximation of the reachable set by the polytopic and interval approximations and the loss of time-dependency between the states within a single trajectory. If both these approximations are tight enough, maximizing the lower bound $\hat{v^r}$ will increase the true objective $v^r$, which is the idea behind Algorithm \ref{algo:irc}.

\section{Multi-model Estimation and Control}

\subsection{Model adequacy}
\subsection{Robust control with Discrete Ambiguity}

\begin{assumption}[Multi-model ambiguity]
Assume that the true dynamics $f$ lies within a finite set of candidate models $f^1, \cdots, f^M$.
\begin{equation}
\exists m\in[M]: \dot{x}(t) = f^M(x(t), u(t)), \forall t\geq 0
\end{equation}

We temporarily ignore the parametric uncertainty $\theta\in\Theta$ to only consider known deterministic models.
\end{assumption}

\begin{definition}[Robust sequence upper bounds] We define an upper-bound for the value of sequences of actions:
\begin{equation}
\label{eq:robust_sequence_ucb}
b_i^r(n)  \eqdef
\begin{cases}
\min_{m\in[1, M]} \sum_{t=0}^{d-1} \gamma^t r_t^m  + \frac{\gamma^d}{1-\gamma} &\text{if } i \in \mathcal{L}_n \text{ ;}\\
\max_{a\in\mathcal{A}} b_{ia}^r(n) & \text{if } i \in \mathcal{T}_n \setminus \mathcal{L}_n 
\end{cases}
\end{equation}
where $r_t^m$ is the reward obtained at step $t$ by following $i$ with dynamics $f^m$.
\end{definition}
An illustration of the computation of the robust b-values is presented in Figure \ref{fig:drop}.

\begin{figure}
\centering
\includegraphics[width=0.5\linewidth]{img/robust-control-tree}
\caption{The computation of robust b-values in Algorithm \ref{algo:drop}. The simulation of trajectories for every dynamics model $f^m$ is represented as stacked versions of the expanded tree $\mathcal{T}_n$.}
\label{fig:drop}
\end{figure}

From this definition we introduce Algorithm \ref{algo:drop}, and analyse its sample-efficiency in Theorem \ref{theorem:drop-regret}.

\begin{algorithm}[tp]
\DontPrintSemicolon
Initialize $\mathcal{T}$ to a root and expand it. Set $n=1$.\;
\While{Numerical resource available}{
Compute the robust u-values $u^r_i(n)$ and robust b-values $b^r_i(n)$.\;
Expand $\argmax_{i\in \mathcal{L}_n} b^r_i(n)$.\;
n = n + 1\;
}
\Return $\argmax_{a\in \mathcal{A}} u^r_a(n)$
\caption{Deterministic Robust Optimistic Planning}
\label{algo:drop}
\end{algorithm}

The simple regret of the action $a$ returned by Algorithm \ref{algo:drop} after $n$ rounds is defined as:
\begin{equation}
\mathcal{R}_n = v^r - v_a^r
\end{equation}
We will say that $\mathcal{R}_n=O(\varepsilon)$ for some $\varepsilon>0$ if there exist $\rho>0$ and $n_0>0$ such that $\mathcal{R}_n\leq\rho\varepsilon$ for all $n\geq n_0$.
A node $i\in\mathcal{T}$ is said to be $\epsilon$-optimal, in a robust sense, if and only if $v_i^r \geq v^r - \epsilon$ for some $\epsilon > 0$. The proportion of $\epsilon$-optimal nodes at depth $d$ is then defined as $p_d(\epsilon) = |i \in \mathcal{A}^d$ s.t $i$ is $\epsilon$-optimal$|/K^d$. Further we will assume that for the graph $\mathcal{T}$ the following hypothesis is satisfied:
\begin{assumption}[Proportion of near-optimal nodes]
\label{assumpt:beta}
There exist $\beta\in[0, \frac{\log K}{\log 1/\gamma}]$, $c > 0$ and $d_0 > 0$ such that $p_d(\epsilon)\leq c\epsilon^\beta$ for all $\epsilon > 0$ and $d\geq d_0$.
\end{assumption}

\begin{theorem}[Regret bound]
\label{theorem:drop-regret}
Let $\kappa = K\gamma^\beta \in [1, K]$. Then the simple regret of Algorithm \ref{algo:drop} is:

\begin{equation}
\text{If } \kappa>1,\qquad 
\mathcal{R}_n = O\left(n^{-\frac{\log 1/\gamma}{\log \kappa}}\right)
\end{equation}

\begin{equation}
\text{If }\kappa=1,\qquad
\mathcal{R}_n = O\left(\gamma^{\frac{(1-\gamma)^\beta}{c}n}\right)
\end{equation}
\end{theorem}

\section{The Use-Case of Autonomous Driving}

We consider the problem of safe decision-making for autonomous highway driving. An autonomous vehicle is driving on a highway populated with $N$ other agents, and uses Model Predictive Control to plan a sequence of decisions. To that end, it relies on parametrized dynamical model for each agent to predict the future trajectory of each traffic participant: \[\dot{z}_i=f_i(Z,\theta_i),\;i=\overline{1,N},\] where $f_i$ are described below, $z_i\in\Real^4$ is the state of an agent, $Z = [z_1,\dots,z_N]^\top\in\Real^{4N}$ and $\theta_i\in\Real^5$ is the corresponding vector of unknown parameters. Crucially, this system describes the couplings and interactions between vehicles, so that the autonomous agent can properly anticipate their reactions. 
However, we assume that we do not have access to the true values of the behavioural parameters $\theta=[\theta_1,\dots,\theta_N]^\top$; instead, we merely know that these parameters lie in a set of admissible values $\Pi\subset\Real^{5N}$. In order to act safely in the face of uncertainty, we follow the framework of robust decision-making: the agent must consider all the possible trajectories in the space of $Z$ that each vehicle can follow in order to take its decisions. In this work, we focus on how to compute these trajectory enclosures through interval prediction.

In the following, we describe the system and its associated interval predictor.

\subsection{Kinematics}

The kinematics of any vehicle $i\in\overline{1,V}$ are represented by the Kinematic Bicycle Model:
\begin{align}
	\dot{x}_i &= v_i\cos(\psi_i), \nonumber\\
	\dot{y}_i &= v_i\sin(\psi_i), \nonumber\\
	\dot{v}_i &= a_i, \nonumber\\
	\dot{\psi}_i &= \frac{v_i}{l}tan(\beta_i), \nonumber
\end{align}
where $(x_i, y_i)$ is the vehicle position, $v_i$ is its forward velocity and $\psi_i$ is its heading, $l$ is the vehicle half-length, $a_i$ is the acceleration command and $\beta_i$ is the slip angle at the centre of gravity, used as a steering command.

\subsection{Longitudinal control}
Longitudinal behaviour is modelled by a linear controller using three features inspired from the intelligent driver model (IDM) \cite{Treiber2000}: a desired velocity, a braking term to drive slower than the front vehicle, and a braking term to respect a safe distance to the front vehicle.

Denoting $f_i$ the index of the front vehicle preceding vehicle $i$, the acceleration command can be presented as follows:
\begin{equation*}
	a_i = \begin{bmatrix}
	\theta_{i,1} & \theta_{i,2} & \theta_{i,3}
	\end{bmatrix} \begin{bmatrix}
		v_0 - v_i \\
		-(v_{f_i}-v_i)^- \\
		-(x_{f_i} - x_i - (d_0 + v_iT))^- \\
	\end{bmatrix},
	\label{eq:theta_a}
\end{equation*}
where $v_0, d_0$ and $T$ respectively denote the speed limit, jam distance and time gap given by traffic rules.

\subsection{Lateral control}

The lane $L_i$ with the lateral position $y_{L_i}$ and heading $\psi_{L_i}$ is tracked by a cascade controller of lateral position and heading $\beta_i$, which is selected in a way the closed-loop dynamics take the form:

\begin{align}
	\label{eq:heading-command}
    \dot{\psi}_i &= \theta_{i,5}\left(\psi_{L_i}+\sin^{-1}\left(\frac{\tilde{v}_{i,y}}{v_i}\right)-\psi_i\right),\\
    \tilde{v}_{i,y} &= \theta_{i,4} (y_{L_i}-y_i). \nonumber
\end{align}
We assume that the drivers choose their steering command $\beta_i$ such that \eqref{eq:heading-command} is always achieved: $\beta_i = \tan^{-1}(\frac{l}{v_i}\dot{\psi}_i)$.

\subsection{LPV formulation}

The system presented so far is non-linear and must be cast into the LPV form. We approximate the non-linearities induced by the trigonometric operators through equilibrium linearisation around $y_i=y_{L_i}$ and $\psi_i=\psi_{L_i}$.

This yields the following longitudinal dynamics:
\begin{align*}
\dot{x}_i &= v_i,\\
\dot v_i &= \theta_{i,1} (v_0 - v_i) + \theta_{i,2} (v_{f_i} - v_i) + \theta_{i,3}(x_{f_i} - x_i - d_0 - v_i T),
\end{align*}
where $\theta_{i,2}$ and $\theta_{i,3}$ are set to $0$ whenever the corresponding features are not active.

It can be rewritten in the form $$\dot{Z} = A(\theta)(Z-Z_c) + d.$$ For example, in the case of two vehicles only:
\begin{equation*}
    Z = \begin{bmatrix}
x_i \\
x_{f_i} \\
v_i \\
v_{f_i} \\
\end{bmatrix}
,\quad
Z_c = \begin{bmatrix}
-d_0-v_0 T \\
0 \\
v_0\\
v_0 \\
\end{bmatrix}
,\quad
d = \begin{bmatrix}
v_0 \\
v_0 \\
0\\
0\\
\end{bmatrix}
\end{equation*}

\begin{equation*}
A(\theta)
=
\begin{blockarray}{ccccc}
 & i & f_i & i & f_i \\
\begin{block}{c[cccc]}
i & 0 & 0 & 1 & 0 \\
f_i & 0 & 0 & 0 & 1 \\
i & -\theta_{i,3} & \theta_{i,3} & -\theta_{i,1}-\theta_{i,2}-\theta_{i,3} & \theta_{i,2} \\
f_i & 0 & 0 & 0 & -\theta_{f_i,1} \\
\end{block}
\end{blockarray}
\end{equation*}

The lateral dynamics are in a similar form:
\begin{equation*}
\begin{bmatrix}
\dot{y}_i \\
\dot{\psi}_i \\
\end{bmatrix}
=
\begin{bmatrix}
0 & v_i \\
-\frac{\theta_{i,4} \theta_{i,5}}{v_i} & -\theta_{i,5}
\end{bmatrix}
\begin{bmatrix}
y_i - y_{L_i} \\
\psi_i - \psi_{L_i}
\end{bmatrix}
+
\begin{bmatrix}
v_i\psi_{L_i} \\
0
\end{bmatrix}
\end{equation*}
Here, the dependency in $v_i$ is seen as an uncertain parametric dependency, \emph{i.e.} $\theta_{i,6}=v_i$, with constant bounds assumed for $v_i$ using an overset of the longitudinal interval predictor.

\subsection{Change of coordinates}
In both cases, the obtained polytope centre $A_0$ is non-Metzler.
We use lemma \ref{lem:metzler} to compute a similarity transformation of coordinates. Precisely, we ensure that the polytope is chosen so that its centre $A_0$ is diagonalisable having real eigenvalues, and perform an eigendecomposition to compute its change of basis matrix $S$. The transformed system $Z'=S^{-1}(Z-Z_c)$ verifies \eqref{eq:polytope} with $A_0$ Metlzer as required to apply the interval predictor of Theorem~\ref{thm:predictor}. Finally, the obtained predictor is transformed back to the original coordinates $Z$ by using the interval arithmetic of Lemma~\ref{lem:interval}.

\bibliographystyle{plainnat}
\bibliography{references}

\end{document}

### 2019-12-02 main.tex
Update notations

@@
 \paragraph{Structured dynamics}
-We consider a system with continuous state space $\Real^p$ and dynamics in the form:
+We consider a system with dynamics in the form:
 
@@
 \end{equation}
+with a state $x\in\Real^p$, control $u\in\Real^m$, parameter $\theta$ that belongs to some compact set $\Theta \subset \Real^d$, $A(\theta)\in\Real^{p\times p}$ and where $\omega\in\Real^q$ is a bounded disturbance: $\underline{\omega}(t)\leq \omega(t)\leq\overline{\omega}(t)$ for all $t\geq0$.
 \todo[inline]{EL: merge notations of the system with and without command $u$}
-where $\theta$ belongs to some compact set $\Theta \subset \Real^d$, $A(\theta)\in\Real^{p\times p}$ and $\omega$ is a bounded disturbance: $\underline{\omega}(t)\leq \omega(t)\leq\overline{\omega}(t)$ for all $t\geq0$.
 
-\paragraph{Robust objective}
+\paragraph{Objective}
 
-We wish to find a sequence of commands $\pi=(u(t))_{t\geq 0}$ that maximises the robust control objective $v^r$:
+We wish to find a sequence of commands $\pi=(u_t)_{t\geq 0}$ that maximises a cumulative objective $V^\pi$:
 \todo[inline]{EL: since the interval dynamics will be deterministic, use open-loop policies, ie sequences of actions $\mathbf{u}$ instead of closed-loop policies $\pi$}
 
+\todo[inline]{EL: the prediction is done in continuous time and the control in discrete time. How to handle the change in notations?}
+
 \begin{equation}
-\label{eq:robust-control}
-\max_\pi \underbrace{\min_{\theta \in \Theta} \expectedvalueover{\omega(t)}\left[\sum_{t=0}^\infty \gamma^t r(x(t))\condbar \dot{x}(t) = A(\theta) x(t) + B_u u(t) + B_\omega\omega(t), u_t = \pi(x_t)\right]}_{v^r(\pi)}
+\max_\pi V^\pi
 \end{equation}
+where
+\begin{equation}
+\label{eq:optimal-control}
+V^\pi = \expectedvalueover{\omega(t)}\left[\sum_{t=0}^\infty \gamma^t r(x(t))\condbar \eqref{eq:dynamics}, u_t = \pi(x_t)\right]
+\end{equation}
+and $r$ is a bounded reward function.
 
@@
 This involves the trilemma of confidence intervals, where one of three things must be true:
-\begin{itemize}
+\begin{enumerate}
     \item $A(\theta)$ is in $\cC_\delta$
@@
     \item Our model is wrong
-\end{itemize}
+\end{enumerate}
 
@@
 In this section, we still assume that we have a high-confidence polytope $\cP$ that verifies \eqref{eq:polytope} with probability $1-\delta$.
+
+The \textbf{robust control} objective $v^r$:
+\todo[inline]{EL: since the interval dynamics will be deterministic, use open-loop policies, ie sequences of actions $\mathbf{u}$ instead of closed-loop policies $\pi$}
+
+\begin{equation}
+\label{eq:robust-control}
+\max_\pi \underbrace{\min_{\theta \in \Theta} \expectedvalueover{\omega(t)}\left[\sum_{t=0}^\infty \gamma^t r(x(t))\condbar \dot{x}(t) = A(\theta) x(t) + B_u u(t) + B_\omega\omega(t), u_t = \pi(x_t)\right]}_{v^r(\pi)}
+\end{equation}
 

### 2019-12-05 main.tex
Updates from Overleaf

@@
 \usepackage{todonotes}
+\usepackage{mathtools}
 
@@
 \label{eq:dynamics}
-\dot{x}(t)=A(\theta)x(t)+B_u u(t) + B_\omega \omega(t),\;t\geq0,
+\dot{x}(t)=A(\theta)x(t) + B u(t) + D \omega(t),\;t\geq0,
 \end{equation}
-with a state $x\in\Real^p$, control $u\in\Real^m$, parameter $\theta$ that belongs to some compact set $\Theta \subset \Real^d$, $A(\theta)\in\Real^{p\times p}$ and where $\omega\in\Real^q$ is a bounded disturbance: $\underline{\omega}(t)\leq \omega(t)\leq\overline{\omega}(t)$ for all $t\geq0$.
-\todo[inline]{EL: merge notations of the system with and without command $u$}
+with state $x\in\Real^p$, control $u\in\Real^q$, and disturbance $\omega\in\Real^s$.
+The dynamics $A(\theta)\in\Real^{p\times p}$  is parametrised by $\theta$ that belongs to a compact set $\Theta \subset \Real^d$.
+The control matrix $B\in\Real^{p\times q}$ and disturbance matrix $D\in\Real^{p\times s}$ are known.
+
+We also have access to a measurement of the form
+$
+    \dot{x}(t) + C\eta(t)
+$
+that we will actually denote (since the control $u(t)$ is known) as:
+\begin{equation}
+\label{eq:measurement}
+    y(t) = \dot{x}(t) - Bu(t) + C\eta(t)
+\end{equation}
+where $\eta(t)\in\Real^r$ is a measurement noise and $C\in\Real^{p\times r}$ is known. Assumptions over the disturbance $\omega$ and noise $\eta$ will be detailed further.
 
@@
 \label{eq:optimal-control}
-V^\pi = \expectedvalueover{\omega(t)}\left[\sum_{t=0}^\infty \gamma^t r(x(t))\condbar \eqref{eq:dynamics}, u_t = \pi(x_t)\right]
+V^\pi = \expectedvalueover{\omega(t)}\left[\sum_{t=0}^\infty \gamma^t r(x(t))\condbar u_t = \pi(x_t),\,\eqref{eq:dynamics}\right]
 \end{equation}
-and $r$ is a bounded reward function.
+and $r:\Real^p\rightarrow[0,1]$ is a bounded reward function.
 
@@
 \paragraph{Objective}% The model estimation procedure is dedicated to building a confidence region around the unknown true model $A(\theta)$. 
-Having observed a history of transitions $\cD = \{(x(t_n), u(t_n), x(t_n+dt))\}_{n\in[N]}$, and given a confidence level $\delta\in[0, 1]$, our goal is to find a confidence region $\cC_\delta$ as tight as possible and such that it holds that:
+Having observed at times $(t_n)_{n\in[N]}$ a history of transitions $\cD = \{(x_n = x(t_n), u_n = u(t_n), y_n = y(t_n))\}_{n\in[N]}$, and given a confidence level $\delta\in[0, 1]$, our goal is to find a confidence region $\cC_\delta$ as tight as possible and such that it holds that:
 \begin{align}
@@
 
-\begin{assumption}[Linear Parametrization]
-\label{assum:linear_param}
+% \paragraph{Tensor notations}
+% We adopt the notations of [Tensor Decompositions and Applications]:
+% Given a tensor $A\in\Real^{I_1\times\cdots\times I_l}$ and matrix $M\in\Real^{I_n\times J}$, the $n$-mode product of $A$ by $M$ is a tensor of $\Real^{I_1\times\cdots\times I_l}$  defined by:
+% \begin{equation*}
+%     (A\times_n M)_{i_1,\cdots,i_{n-1},j,i_{n+1},\cdots,i_l} = \sum_{k=1}^{I_n} A_{i_1,\cdots,i_{n-1},k,i_{n+1},\cdots,i_l}B_{k,j}
+% \end{equation*}
+
 We further assume that the dynamics $A(\theta)$ enjoy the following additional structure:
+\begin{assumption}[Linear Parametrisation]
+\label{assumpt:linear_param}
+There exists a known tensor $\phi\in \Real^{d \times p \times p}$ such that for all $\theta\in\Theta$:
 \begin{equation}
-    A(\theta) = \theta^T \phi
+    A(\theta) = \theta^T \phi \eqdef \sum_{i=1}^d \theta_i\phi_i
 \end{equation}
-where $\phi\in \Real^{d \times p \times p}$.
+where $\phi_i\in\Real^{p\times p}$ for all $i\in[d]$.
 \end{assumption}
 
-We stack the $N$ observations and noises of $\dot{x}(t), x(t), B_u u(t)$ and $B_\omega \omega(t)$ in $\cD$ as $\dot{X}_{[N]}, X_{[N]}, U_{[N]}, \eta_{[N]}^T \in\Real^{p\times N}$, we obtain the regression problem:
+\begin{assumption}[Noise Model]
+\label{assumpt:noise}
+At each time $t\geq0$ the measurement noise $\eta(t)$ and disturbance $\omega(t)$  are independent Gaussians with respective means $0_r, 0_s$ and covariances $\Sigma_r, \Sigma_s$:
+\begin{equation*}
+    \eta(t)\sim \cN(0_r,\Sigma_r),\quad\omega(t)\sim \cN(0_s,\Sigma_s)
+\end{equation*}
+We further require that the matrix $\Sigma_p = C\Sigma_r C^T + D\Sigma_s D^T \in \Real^{p\times p}$ is full-rank.
+\end{assumption}
 
-\[\dot{X}_{[N]} = \theta^T\phi X_{[N]} + U_{[N]} + \eta_{[N]}\]
+Note that the full-rank condition in \autoref{assumpt:noise} would be harder to fulfil were it formulated only for the disturbance $D\Sigma_s D^T$, whereas it would be quite reasonable to assume, for instance, that $r=p$, which is sufficient.
 
-This can be rewritten in a canonical form as:
+\begin{proposition}[Maximum Likelihood Estimate]
+\label{prop:mle}
+The maximum likelihood estimate for $\theta$ minimises a weighted mean square error:
+\begin{equation*}
+    \argmax_{\theta\in\Real^d} \probability{\cD\condbar\eqref{eq:dynamics};\Sigma} = \argmin_{\theta\in\Real^d} \sum_{n=1}^N \|y_n -\theta^T\phi x_n\|_{\Sigma_p^{-1}}^2
+\end{equation*}
+\end{proposition}
+\begin{proof}
+For $n\in[N]$, at time $t_n$, we have
+\begin{align*}
+    \probability{y_n, x_n} 
+    &= \probability{y_n|x_n}\probability{x_n}\\
+    &= \probability{y_n = \dot{x}_n - Bu_n +C\eta_n|x_n,u_n}\probability{x_n}\\
+    &= \probability{A(\theta)x_n + B u_n + D \omega_n - Bu_n +C\eta_n = y_n|x_n}\probability{x_n}\\
+    &= \probability{C\eta_n + D \omega_n = y_n- \theta^T \phi x_n |x_n}\probability{x_n}\\
+    &= \cN(y_n - \theta^T \phi x_n; 0_p,\Sigma_p)\probability{x_n}
+\end{align*}
+By independence of the noise at different times, we have:
+\begin{align*}
+    \log\probability{\cD;\Sigma} &= \log\prod_{n=1}^N\probability{y_n, x_n}\\
+    &= \sum_{n=1}^N\log \cN(y_n- \theta^T \phi x_n;0_p,\Sigma_p) + \log\probability{x_n}\\
+    &= \sum_{n=1}^N -\frac{1}{2} \|y_n -\theta^T\phi x_n\|_{\Sigma_p^{-1}}^2 - \log\left((2\pi)^{p/2} \det(\Sigma_p)^{1/2}\right) + \log\probability{x_n}
+\end{align*}
+\end{proof}
+
+We stack the observations $y(t_n), x(t_n)$ in $\cD$, as $Y_{[N]}, X_{[N]}\in\Real^{N\times p}$ and the noises $C\eta(t_n)+D\omega(t_n)$ as $\Omega_{[N]} \in\Real^{N\times p}$ to obtain the regression problem:
+
 \begin{equation}
     \label{eq:regression}
-    Y_{[N]} = \Phi_{[N]} \theta + \eta_{[N]},
+    Y_{[N]} = \Phi_{[N]} \theta + \Omega_{[N]},
 \end{equation}
-with $Y_{[N]} = \dot{X}_{[N]}^T - U_{[N]}^T  \in\Real^{N\times p}, \Phi_{[N]} = (\phi X_{[N]})^T\in \Real^{N\times p\times d}$; and the assumptions on the noise $\eta_{[N]} \in\Real^{N\times p}$ will be described further.
+with $\Phi_{[N]} = X_{[N]}\phi^T\in \Real^{N\times p\times d}$.
 
-\paragraph{Regularized solution} Since we expect that $\Phi x(t)$ may have zero-coordinates on long time intervals (i.e.
-some features are not always active), we consider the $l_2$ regularization with parameter $\lambda\in\Real^+_*$:
+% As detailed in \autoref{prop:mle}, we wish to solve:
+% \begin{equation*}
+%     \min_{\theta\in\Real^d} \|Y_{[N]} -\Phi_{[N]}\theta\|_{\Sigma_p^{-1}}^2
+% \end{equation*}
 
+% where we denote $\|z\|_S^2 = z S z^T$ for $z\in\Real^{N\times p}$ and $S\in\Real^{p\times p}$.
+
+\subsection{Scalar formulation}
+
+\begin{proposition}[Decoupling the noise]
+Without loss of generality, up to a change of basis, we can assume that $\Sigma_d$ is diagonal.
+\end{proposition}
+\begin{proof}
+Since $\Sigma_p$ is a symmetric real matrix, it is diagonalisable: there exists $Q\in\cO(p)$ and a diagonal matrix $R$ such that $\Sigma_p = QRQ^{-1}$.
+Hence, from \eqref{eq:dynamics} and \eqref{eq:measurement}:
+\begin{align*}
+    Q^{-1}y'(t) &= \sum_{i=1}^d \theta_i Q^{-1}\phi_i x(t) + Q^{-1}(C\eta(t) + D\omega(t))
+\end{align*}
+By rewriting $y \leftarrow Q^{-1}y, \phi_i\leftarrow Q^{-1}\phi_i, C\leftarrow Q^{-1}C$, and $D\leftarrow Q^{-1}D$ we recover \eqref{eq:dynamics} and \eqref{eq:measurement} in their original form, while now having $C\Sigma_rC^T + D\Sigma_rD^T = R$.
+\end{proof}
+
+In order to solve the regression problem \eqref{eq:regression} can simply reshape the two first $N\times p$ dimensions into a single $Np$ dimension.
+Since $\Sigma_p$ is diagonal, the noises on each row of $\Omega$ are independent, the problem becomes a standard scalar regression problem with heteroscedastic noise (if $\Sigma_p$ is not proportional to $I_p$), and the Lemma 5 of \citet{kirschner18heteroscedastic} can be applied.
+
+\begin{lemma}[Confidence ellipsoid \citep{kirschner18heteroscedastic}]
+Assuming that $\Sigma_p$ is diagonal and $\|\theta\|_2\leq S$, it holds with probability $1-\delta$ that:
 \begin{equation*}
-    \min_{\theta\in\Real^d} \|Y - \Phi \Theta\|_2^2 + \lambda\|\theta\|_2^2
+    \|\theta - \theta_{Np,\lambda}\|_{G_{Np,\lambda}} \leq \sqrt{2\log \frac{\text{det}(G_{Np,\lambda})^{1/2}\text{det}(\lambda I)^{-1/2}}{\delta}} + \lambda^{1/2}S
 \end{equation*}
+where
+\begin{align*}
+    \Phi_{[Np]}& \in\Real^{Np\times d},\, Y_{[Np]}\in \Real^{Np} \text{ are the flattened versions of $\Phi_{[N]}$, $Y_{[N]}$};\\
+    \tilde{\Phi}_{[Np]} &= \Phi_{[Np]} [\underbrace{\cdots \Sigma_p^{-1} \cdots}_{\text{$N$ times}}]^T, \qquad  \tilde{Y}_{[Np]} = Y_{[Np]} [\underbrace{\cdots \Sigma_p^{-1} \cdots}_{\text{$N$ times}}]^T;\\
+    G_{Np, \lambda} &= \tilde{\Phi}^T_{[Np]}\tilde{\Phi}_{[Np]} + \lambda I_d;\\
+    \theta_{Np,\lambda} &= G_{Np, \lambda}^{-1} \tilde{\Phi}^T_{[Np]}\tilde{Y}_{[Np]}.
+\end{align*}
+\end{lemma}
 
-The solution can be obtained by differentiation:
+\subsection{Vector formulation}
+In the general case, we denote the weighted version of the Frobenius inner product Frobenius norm as $\inp{M}{N}_{F,\Sigma} = \Tr (M^T \Sigma N)$ and $\|M\|_{F,\Sigma}^2 = \inp{M}{M}_{F,\Sigma}$.
 
+\paragraph{Regularized solution} Since we expect that $\phi x(t)$ may have zero-coordinates during possibly long time intervals (i.e.
+some features are not always active), we consider instead the weighted $l_2$ regularised problem with parameter $\lambda\in\Real^+_*$ and weights $\Sigma_d\in\Real^{d\times d}$:
+
+\begin{equation}
+    \label{eq:regression_min}
+    \min_{\theta\in\Real^d} \|(Y_{[N]} -\Phi_{[N]}\theta)^T\|_{F,\Sigma_p^{-1}}^2 + \lambda\|\theta\|_{\Sigma_d}^2
+\end{equation}
+
+%For simplicity, we abuse notations and replace $Y_{[N]}$ and $\Phi_{[N]}$ by their transposed forms $Y_{[N]}^T\in\Real^{p\timesN}$ and $\Phi_{[N]}^T\in\Real^{d\times p\times N}$.
+
+The solution can be obtained as:
+
+\begin{theorem}
+\begin{equation}
+    \label{eq:vector_rls}
+    \theta_{N,\lambda} = G_{N, \lambda}^{-1} \begin{bmatrix}\inp{\Phi_{[N],i}^T}{Y_{[N]}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]}
+\end{equation}
+where $\Phi_{[N],i}\in\Real^{p\times d}$ is the $i^\text{th}$ component of $\Phi_{[N]}$ along the first component, and
 \begin{equation*}
-    \theta_{N,\lambda} = G_{N, \lambda}^{-1} \Phi^T_{[N]}Y_{[N]} + \lambda I, \quad \text{where } G_{N, \lambda} = X^T_{[N]}X_{[N]} + \lambda I.
+    G_{N, \lambda} = \begin{bmatrix}\inp{\Phi_{[N],i}^T}{\Phi_{[N],j}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i,j\in[d]^2} + \lambda \Sigma_d \in \Real^{d\times d}.
 \end{equation*}
+\end{theorem}
+
+\begin{proof}
+In this proof, we drop the $[N]$ subscripts for simplicity.
+Let $i\in[d]$ and denote $Y_{-i} = Y - \sum_{j\in[d], j\neq i} \theta_j\Phi_{j}$.
+
+We differentiate the objective $J(\theta) = \|(Y -\Phi\theta)^T\|_{F,\Sigma_p^{-1}}^2 + \lambda\|\theta\|_{\Sigma_d}^2$ as in  \eqref{eq:regression_min} with respect to $\theta_i$:
+\begin{align*}
+    J(\theta) &= \|(Y - \sum_{j=1}^d\theta_j\Phi_{j})^T\|_{F,\Sigma_p^{-1}}^2 + \lambda\|\theta\|_{\Sigma_d}^2\\
+    &=  \|(Y_{-i} - \theta_i\Phi_{i})^T\|_{F,\Sigma_p^{-1}}^2 + \lambda\|\theta\|_{\Sigma_d}^2\\
+    &= \Tr\left((Y_{-i} - \theta_i\Phi_{i})\Sigma_p^{-1}(Y_{-i} - \theta_i\Phi_{i})^T\right) + \lambda\|\theta\|_{\Sigma_d}^2\\
+    &= \theta_i^2\Tr\left(\Phi_{i}\Sigma_p^{-1}\Phi_{i}^T\right) 
+    -\theta_i\Tr\left(\Phi_{i}\Sigma_p^{-1}Y_{-i}^T\right) 
+    -\theta_i\Tr\left(Y_{-i}\Sigma_p^{-1}\Phi_{i}^T\right)
+    + \Tr\left(Y_{-i}\Sigma_p^{-1}Y_{-i}^T\right)
+    \\
+    &\quad+ \lambda\|\theta\|_{\Sigma_d}^2
+\end{align*}
+
+Hence, 
+\begin{align*}
+    \nabla_{\theta_i} J(\theta) &= 2\theta_i\Tr\left(\Phi_{i}\Sigma_p^{-1}\Phi_{i}^T\right)
+    -2\Tr\left(\Phi_{i}\Sigma_p^{-1}Y_{-i}^T\right) 
+    +2\lambda\theta^T\Sigma_{d,i}\\
+    &= 2\theta_i\Tr\left(\Phi_{i}\Sigma_p^{-1}\Phi_{i}^T\right)
+    +2\sum_{j\neq i}\theta_j\Tr\left(\Phi_{i}\Sigma_p^{-1}\Phi_j^T\right) 
+    -2\Tr\left(\Phi_{i}\Sigma_p^{-1}Y^T\right) 
+    +2\lambda\theta^T\Sigma_{d,i}\\
+    &= 2\theta^T\begin{bmatrix}
+    \Tr\left(\Phi_i \Sigma_p^{-1} \Phi_j^T\right)
+    \end{bmatrix}_{j\in[d]}
+    -2\Tr\left(\Phi_{i}\Sigma_p^{-1}Y^T\right) 
+    +2\lambda\theta^T\Sigma_{d,i}\\
+\end{align*}
+
+Since, $\nabla_{\theta}J(\theta) = 0 \iff \forall i,\, \nabla_{\theta_i}J(\theta) = 0$, we obtain the following optimality condition:
+
+\begin{align*}
+    \forall i,  \theta^T\left(\lambda\Sigma_{d,i} + \begin{bmatrix}
+    \Tr\left(\Phi_i \Sigma_p^{-1} \Phi_j^T\right)
+    \end{bmatrix}_{j\in[d]}\right)
+     = \Tr\left(\Phi_{i}\Sigma_p^{-1}Y^T\right)
+\end{align*}
+By transposing and arranging the $[d]$ equations in matrix form,
+\begin{align*}
+    \left(\lambda\Sigma_{d} + \begin{bmatrix}
+    \inp{\Phi_{i}^T}{\Phi_{j}^T}_{F,\Sigma_p^{-1}}
+    \end{bmatrix}_{i,j\in[d]^2}\right)\theta
+     = \begin{bmatrix}\inp{\Phi_{i}^T}{Y^T}_{F,\Sigma_p^{-1}}\end{bmatrix}_{i\in[d]}
+\end{align*}
+
+\end{proof}
 
@@
 
-We consider the noise vector $\eta(t) = B_\omega \omega(t)\in\Real^p$.
-Since $\omega$ is bounded, $\eta$ is also bounded by $R=\sup_{t\geq 0}\|B_\omega \omega(t)\|_2^2$, and hence $\eta(t)$ is a $R$-subgaussian vector: $\eta(t)\sim \text{SubG}_p(R)$.
+In order to study the concentration of $\theta_{N,\lambda}$, we reinject the expression of $Y$ into \eqref{eq:vector_rls}:
+\begin{align*}
+    \theta_{N,\lambda} &= G_{N, \lambda}^{-1} \begin{bmatrix}\inp{\Phi_{[N],i}^T}{\sum_{i=j}^d\theta_j\Phi_{[N],j}^T  + \Omega_{[N]}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]}\\
+    &= G_{N, \lambda}^{-1}\begin{bmatrix}\inp{\Phi_{[N],i}^T}{\Omega_{[N]}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]} + 
+    G_{N, \lambda}^{-1} \sum_{i=j}^d\theta_j\begin{bmatrix}\inp{\Phi_{[N],i}^T}{\Phi_{[N],j}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]}\\
+    &= G_{N, \lambda}^{-1}\begin{bmatrix}\inp{\Phi_{[N],i}^T}{\Omega_{[N]}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]} + 
+    G_{N, \lambda}^{-1}\left(G_{N, \lambda}-\lambda\Sigma_d\right)\theta\\
+    &= \theta + G_{N, \lambda}^{-1}\begin{bmatrix}\inp{\Phi_{[N],i}^T}{\Omega_{[N]}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]} -
+    G_{N, \lambda}^{-1}\lambda\Sigma_d\theta
+\end{align*}
 
-This also implies that each component $\eta_i(t)$ for $i\in[p]$ is itself $R$-subgaussian.
-Consequently, by flattening the two first $N\times p$ dimensions of $Y_{[N]}, \Phi_{[N]}$ and $\eta_{[N]}$ to a single $Np$ dimension in \eqref{eq:regression}, we recover the conditions of scalar linear regression.
-We can apply the following theorem:
+Hence, for all $x\in\Real^d$,
+\begin{align*}
+    x^T\theta_{N,\lambda}  -x^T\theta &= x^T G_{N, \lambda}^{-1}\begin{bmatrix}\inp{\Phi_{[N],i}^T}{\Omega_{[N]}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]} 
+    - x^T G_{N, \lambda}^{-1}\lambda\Sigma_d\theta\\
+    &= \inp{x}{\begin{bmatrix}\inp{\Phi_{[N],i}^T}{\Omega_{[N]}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]}}_{G_{N, \lambda}^{-1}} - \lambda\inp{x}{\Sigma_d\theta}_{G_{N, \lambda}^{-1}}
+\end{align*}
 
-\begin{theorem}[Theorem 2 of \citet{Abbasi2011}] Assuming that $\|\theta\|_2\leq S$, it holds with probability $1-\delta$ that:
-\begin{equation*}
-    \|\theta - \theta_{N,\lambda}\|_{G_{N,\lambda}} \leq R\sqrt{2\log \frac{\text{det}(G_{N,\lambda})^{1/2}\text{det}(\lambda I)^{-1/2}}{\delta}} + \lambda^{1/2}S
-\end{equation*}
-\end{theorem}
+Using the Cauchy-Schwartz inequality, we get:
+\begin{align*}
+    |x^T\theta_{N,\lambda}  -x^T\theta| &\leq \|x\|_{G_{N, \lambda}^{-1}}\left(\left\|\begin{bmatrix}\inp{\Phi_{[N],i}^T}{\Omega_{[N]}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]}\right\|_{G_{N, \lambda}^{-1}} + \lambda\|\Sigma_d\theta\|_{G_{N, \lambda}^{-1}}\right)
+\end{align*}
+\todo[inline]{The first term is a $\Real^d$ vector whose coefficients are inner product of matrices (a sum along time and $p$ dimensions). How to analyze its concentration?}
 
@@
 \dot{\underline{x}}(t) & = & A_{0}\underline{x}(t)-\Delta A_{+}\underline{x}^{-}(t)-\Delta A_{-}\overline{x}^{+}(t)\nonumber \\
- &  & +B^{+}\underline{\omega}(t)-B^{-}\overline{\omega}(t),\nonumber\\
+ &  & +Bu(t)+D^{+}\underline{\omega}(t)-D^{-}\overline{\omega}(t),\nonumber\\
 \dot{\overline{x}}(t) & = & A_{0}\overline{x}(t)+\Delta A_{+}\overline{x}^{+}(t)+\Delta A_{-}\underline{x}^{-}(t) \label{eq:interval_predictor} \\
- &  & +B^{+}\overline{\omega}(t)-B^{-}\underline{\omega}(t),\nonumber \\
+ &  & +Bu(t)+D^{+}\overline{\omega}(t)-D^{-}\underline{\omega}(t),\nonumber \\
  &  & \underline{x}(0)=\underline{x}_{0},\;\overline{x}(0)=\overline{x}_{0}\nonumber 

### 2019-12-05 main.tex
Update vector form

@@
 \usepackage[linesnumbered,ruled,vlined]{algorithm2e}
-\usepackage{natbib}
 \usepackage{caption}
@@
 \usepackage{mathtools}
+\usepackage[backend=biber,style=authoryear,natbib=true,url=false]{biblatex}
+
+\addbibresource{references.bib}
 
@@
 \subsection{Vector formulation}
-In the general case, we denote the weighted version of the Frobenius inner product Frobenius norm as $\inp{M}{N}_{F,\Sigma} = \Tr (M^T \Sigma N)$ and $\|M\|_{F,\Sigma}^2 = \inp{M}{M}_{F,\Sigma}$.
+In the general case, we denote the weighted version of the Frobenius inner product and Frobenius norm as $\inp{M}{N}_{F,\Sigma} = \Tr (M^T \Sigma N)$ and $\|M\|_{F,\Sigma}^2 = \inp{M}{M}_{F,\Sigma}$.
 
@@
 
-\begin{theorem}
+\begin{theorem}[Regularized solution] The solution to \eqref{eq:regression_min} is:
 \begin{equation}
@@
 \end{equation}
-where $\Phi_{[N],i}\in\Real^{p\times d}$ is the $i^\text{th}$ component of $\Phi_{[N]}$ along the first component, and
+where $\Phi_{[N],i}\in\Real^{p\times d}$ is the $i^\text{th}$ component of $\Phi_{[N]}$ along the first dimension, and
 \begin{equation*}
@@
 \end{align*}
-\todo[inline]{The first term is a $\Real^d$ vector whose coefficients are inner product of matrices (a sum along time and $p$ dimensions). How to analyze its concentration?}
+\todo[inline]{EL: The first term is a $\Real^d$ vector whose coefficients are inner product of matrices (a sum along both the time $N$ and $p$ dimensions).
+How to analyze its concentration?
+For comparison, in \citep{Abbasi2011} $X^T\eta$ was a  $\Real^d$ vector whose coefficients were inner product of vectors $(X_i^T\eta)_i\in[d]$ (a sum over time $N$)}
 
@@
 
-\bibliographystyle{plainnat}
-\bibliography{references}
+\printbibliography
 

### 2019-12-19 main.tex
Updates from Overleaf

@@
 \end{equation*}
+
+By rewriting $\Phi_n = [\cdots \phi_i x_n \cdots]\in\Real^{p\times d}$,
+\begin{equation*}
+    \argmax_{\theta\in\Real^d} \probability{\cD\condbar\eqref{eq:dynamics};\Sigma} = \argmin_{\theta\in\Real^d} \sum_{n=1}^N \|y_n -\Phi_n \theta\|_{\Sigma_p^{-1}}^2
+\end{equation*}
 \end{proposition}
@@
 
-We stack the observations $y(t_n), x(t_n)$ in $\cD$, as $Y_{[N]}, X_{[N]}\in\Real^{N\times p}$ and the noises $C\eta(t_n)+D\omega(t_n)$ as $\Omega_{[N]} \in\Real^{N\times p}$ to obtain the regression problem:
+We stack the observations $y_n, x_n$ in $\cD$, as $Y_{[N]}, X_{[N]}\in\Real^{N\times p}$ and the noises $C\eta(t_n)+D\omega(t_n)$ as $\Omega_{[N]} \in\Real^{N\times p}$ to obtain the regression problem:
 
@@
 Assuming that $\Sigma_p$ is diagonal and $\|\theta\|_2\leq S$, it holds with probability $1-\delta$ that:
-\begin{equation*}
+\begin{equation}
+    \label{eq:confidence-ellipsoid}
     \|\theta - \theta_{Np,\lambda}\|_{G_{Np,\lambda}} \leq \sqrt{2\log \frac{\text{det}(G_{Np,\lambda})^{1/2}\text{det}(\lambda I)^{-1/2}}{\delta}} + \lambda^{1/2}S
-\end{equation*}
+\end{equation}
 where
 \begin{align*}
-    \Phi_{[Np]}& \in\Real^{Np\times d},\, Y_{[Np]}\in \Real^{Np} \text{ are the flattened versions of $\Phi_{[N]}$, $Y_{[N]}$};\\
-    \tilde{\Phi}_{[Np]} &= \Phi_{[Np]} [\underbrace{\cdots \Sigma_p^{-1} \cdots}_{\text{$N$ times}}]^T, \qquad  \tilde{Y}_{[Np]} = Y_{[Np]} [\underbrace{\cdots \Sigma_p^{-1} \cdots}_{\text{$N$ times}}]^T;\\
+    \Phi_{[Np]}& \in\Real^{Np\times d},\, Y_{[Np]}\in \Real^{Np\times 1} \text{ are the reshaped versions of $\Phi_{[N]}$, $Y_{[N]}$};\\
+    \tilde{\Phi}_{[Np]} &= [\underbrace{\cdots \Sigma_p^{-\frac{1}{2}} \cdots}_{\text{$N$ times}}]^T \Phi_{[Np]} , \qquad  \tilde{Y}_{[Np]} = [\underbrace{\cdots \Sigma_p^{-\frac{1}{2}} \cdots}_{\text{$N$ times}}]^TY_{[Np]};\\
     G_{Np, \lambda} &= \tilde{\Phi}^T_{[Np]}\tilde{\Phi}_{[Np]} + \lambda I_d;\\
@@
 
+{\color{gray}
 \subsection{Vector formulation}
-In the general case, we denote the weighted version of the Frobenius inner product and Frobenius norm as $\inp{M}{N}_{F,\Sigma} = \Tr (M^T \Sigma N)$ and $\|M\|_{F,\Sigma}^2 = \inp{M}{M}_{F,\Sigma}$.
+
+% In the general case, we denote the weighted version of the Frobenius inner product and Frobenius norm as $\inp{M}{N}_{F,\Sigma} = \Tr (M^T \Sigma N)$ and $\|M\|_{F,\Sigma}^2 = \inp{M}{M}_{F,\Sigma}$.
 
@@
     \label{eq:regression_min}
-    \min_{\theta\in\Real^d} \|(Y_{[N]} -\Phi_{[N]}\theta)^T\|_{F,\Sigma_p^{-1}}^2 + \lambda\|\theta\|_{\Sigma_d}^2
+    \min_{\theta\in\Real^d} \sum_{n=1}^N \|y_n -\Phi_n\theta\|_{\Sigma_p^{-1}}^2 + \lambda\|\theta\|_{\Sigma_d}^2
 \end{equation}
-
-%For simplicity, we abuse notations and replace $Y_{[N]}$ and $\Phi_{[N]}$ by their transposed forms $Y_{[N]}^T\in\Real^{p\timesN}$ and $\Phi_{[N]}^T\in\Real^{d\times p\times N}$.
 
@@
     \label{eq:vector_rls}
-    \theta_{N,\lambda} = G_{N, \lambda}^{-1} \begin{bmatrix}\inp{\Phi_{[N],i}^T}{Y_{[N]}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]}
+    \theta_{N,\lambda} = G_{N, \lambda}^{-1} \sum_{n=1}^N \Phi_n^T \Sigma_p^{-1} y_n
 \end{equation}
-where $\Phi_{[N],i}\in\Real^{p\times d}$ is the $i^\text{th}$ component of $\Phi_{[N]}$ along the first dimension, and
+where 
 \begin{equation*}
-    G_{N, \lambda} = \begin{bmatrix}\inp{\Phi_{[N],i}^T}{\Phi_{[N],j}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i,j\in[d]^2} + \lambda \Sigma_d \in \Real^{d\times d}.
+    G_{N, \lambda} = \sum_{n=1}^N \Phi_{n}^T\Sigma_p^{-1}\Phi_{n}  + \lambda \Sigma_d \in \Real^{d\times d}.
 \end{equation*}
@@
 \begin{proof}
-In this proof, we drop the $[N]$ subscripts for simplicity.
-Let $i\in[d]$ and denote $Y_{-i} = Y - \sum_{j\in[d], j\neq i} \theta_j\Phi_{j}$.
+We differentiate $J(\theta) = \sum_{n=1}^N \|y_n -\Phi_n\theta\|_{\Sigma_p^{-1}}^2 + \lambda\|\theta\|_{\Sigma_d}^2$ as in  \eqref{eq:regression_min} with respect to $\theta$:
 
-We differentiate the objective $J(\theta) = \|(Y -\Phi\theta)^T\|_{F,\Sigma_p^{-1}}^2 + \lambda\|\theta\|_{\Sigma_d}^2$ as in  \eqref{eq:regression_min} with respect to $\theta_i$:
 \begin{align*}
-    J(\theta) &= \|(Y - \sum_{j=1}^d\theta_j\Phi_{j})^T\|_{F,\Sigma_p^{-1}}^2 + \lambda\|\theta\|_{\Sigma_d}^2\\
-    &=  \|(Y_{-i} - \theta_i\Phi_{i})^T\|_{F,\Sigma_p^{-1}}^2 + \lambda\|\theta\|_{\Sigma_d}^2\\
-    &= \Tr\left((Y_{-i} - \theta_i\Phi_{i})\Sigma_p^{-1}(Y_{-i} - \theta_i\Phi_{i})^T\right) + \lambda\|\theta\|_{\Sigma_d}^2\\
-    &= \theta_i^2\Tr\left(\Phi_{i}\Sigma_p^{-1}\Phi_{i}^T\right) 
-    -\theta_i\Tr\left(\Phi_{i}\Sigma_p^{-1}Y_{-i}^T\right) 
-    -\theta_i\Tr\left(Y_{-i}\Sigma_p^{-1}\Phi_{i}^T\right)
-    + \Tr\left(Y_{-i}\Sigma_p^{-1}Y_{-i}^T\right)
-    \\
-    &\quad+ \lambda\|\theta\|_{\Sigma_d}^2
+    \nabla_{\theta} J(\theta) &= \sum_{n=1}^N\nabla_{\theta} (y_n - \Phi_n\theta)^T\Sigma_p^{-1}(y_n - \Phi_n\theta) + \nabla_{\theta} \lambda\|\theta\|_{\Sigma_d}^2\\
+    &= -2\sum_{n=1}^N y_n^T\Sigma_p^{-1}\Phi_n + 2\sum_{n=1}^N\theta^T(\Phi_n^T\Sigma^{-1}\Phi_n) +  2 \lambda \theta^T \Sigma_d
 \end{align*}
@@
 \begin{align*}
-    \nabla_{\theta_i} J(\theta) &= 2\theta_i\Tr\left(\Phi_{i}\Sigma_p^{-1}\Phi_{i}^T\right)
-    -2\Tr\left(\Phi_{i}\Sigma_p^{-1}Y_{-i}^T\right) 
-    +2\lambda\theta^T\Sigma_{d,i}\\
-    &= 2\theta_i\Tr\left(\Phi_{i}\Sigma_p^{-1}\Phi_{i}^T\right)
-    +2\sum_{j\neq i}\theta_j\Tr\left(\Phi_{i}\Sigma_p^{-1}\Phi_j^T\right) 
-    -2\Tr\left(\Phi_{i}\Sigma_p^{-1}Y^T\right) 
-    +2\lambda\theta^T\Sigma_{d,i}\\
-    &= 2\theta^T\begin{bmatrix}
-    \Tr\left(\Phi_i \Sigma_p^{-1} \Phi_j^T\right)
-    \end{bmatrix}_{j\in[d]}
-    -2\Tr\left(\Phi_{i}\Sigma_p^{-1}Y^T\right) 
-    +2\lambda\theta^T\Sigma_{d,i}\\
+    \nabla_{\theta} J(\theta) = 0 \iff \left(\sum_{n=1}^N\Phi_n^T\Sigma_p^{-1}\Phi_n + \Sigma_d\right)\theta = \sum_{n=1}^N y_n^T\Sigma_p^{-1}\Phi_n
+\end{align*}
+\end{proof}
+
+\paragraph{Confidence ellipsoid}
+
+In order to study the concentration of $\theta_{N,\lambda}$, we substitute the expression of $y_n$ into \eqref{eq:vector_rls}:
+\begin{align*}
+    \theta_{N,\lambda} &= G_{N, \lambda}^{-1} \sum_{n=1}^N \Phi_n^T \Sigma_p^{-1} (\Phi_n\theta +\eta_n)\\
+    &= \theta - G_{N, \lambda}^{-1}\lambda\Sigma_d\theta + G_{N, \lambda}^{-1}\sum_{n=1}^N \Phi_n^T \Sigma_p^{-1}\eta_n
 \end{align*}
 
-Since, $\nabla_{\theta}J(\theta) = 0 \iff \forall i,\, \nabla_{\theta_i}J(\theta) = 0$, we obtain the following optimality condition:
+Hence, for all $x\in\Real^d$,
+\begin{align*}
+    x^T\theta_{N,\lambda}  -x^T\theta &= x^T G_{N, \lambda}^{-1}\sum_{n=1}^N \Phi_n^T \Sigma_p^{-1}\eta_n
+    - \lambda x^T G_{N, \lambda}^{-1}\Sigma_d\theta\\
+    &= \inp{x}{\sum_{n=1}^N \Phi_n^T \Sigma_p^{-1}\eta_n}_{G_{N, \lambda}^{-1}} - \lambda\inp{x}{\Sigma_d\theta}_{G_{N, \lambda}^{-1}}
+\end{align*}
+
+Using the Cauchy-Schwartz inequality, we get:
+\begin{align*}
+    |x^T\theta_{N,\lambda}  -x^T\theta| &\leq \|x\|_{G_{N, \lambda}^{-1}}\left(\left\|\sum_{n=1}^N \Phi_n^T \Sigma_p^{-1}\eta_n\right\|_{G_{N, \lambda}^{-1}} + \lambda\|\Sigma_d\theta\|_{G_{N, \lambda}^{-1}}\right)
+\end{align*}
+
+\begin{lemma}[Theorem 1 of \citep{Abbasi2011}, Matrix version]
+Let $\{F_t\}_{t=0}$ be a filtration.
+Let $\{\eta_t\}_{t=1}^\infty$ be a $\Real^p$-valued stochastic process such that $\eta_t$ is $F_t$-measurable and $\eta_t$ is $\Sigma_p$-SubGaussian:
+\begin{equation*}
+    \forall u\in\Real^p, \expectedvalue \left[ \exp{\left( u^T \eta_t\right)}\condbar F_{t-1}\right] \leq \exp{\left( u^T \Sigma_p u\right)}
+\end{equation*}
+
+Let $\{X_t\}_{t=1}^\infty$ be an $\Real^{p\times d}$-valued stochastic process such that $X_t$ is $F_t$-measurable.
+Assume that $V$ is a $d\times d$ positive definite matrix.
+For any $t\geq 0$, define:
+
+\begin{equation*}
+    \overline{V}_t = V + \sum_{s=1}^t X_s^T \Sigma_p^{-1} X_s \in \Real^{d\times d} \qquad S_t = \sum_{s=1}^t X_s^T\Sigma_p^{-1}\eta_s \in \Real^{d}
+\end{equation*}
+Then, for any $\delta>0$, with probability at least $1-\delta$, for all $t\geq0$
 
 \begin{align*}
-    \forall i,  \theta^T\left(\lambda\Sigma_{d,i} + \begin{bmatrix}
-    \Tr\left(\Phi_i \Sigma_p^{-1} \Phi_j^T\right)
-    \end{bmatrix}_{j\in[d]}\right)
-     = \Tr\left(\Phi_{i}\Sigma_p^{-1}Y^T\right)
+    \|S_t\|_{\overline{V_t}} \leq \cdots
 \end{align*}
-By transposing and arranging the $[d]$ equations in matrix form,
+
+\end{lemma}
+\begin{proof}
+
+Let 
+\begin{equation*}
+    V_t = \sum_{s=1}^t X_s^T \Sigma_p^{-1} X_s \in \Real^{d\times d}
+\end{equation*}
+And for any $z\in\Real^d$,
+\begin{equation*}
+    M_t^z = \exp{\left(\inp{z}{S_t} - \frac{1}{2}\|z\|_{V_t}\right)}
+\end{equation*}
+\begin{equation*}
+    D_t^z = \exp{\left(\inp{X_t z}{\eta_t}_{\Sigma_p^{-1}} - \frac{1}{2}\|X_t z\|_{\Sigma_p^{-1}}\right)}
+\end{equation*}
+Then,
 \begin{align*}
-    \left(\lambda\Sigma_{d} + \begin{bmatrix}
-    \inp{\Phi_{i}^T}{\Phi_{j}^T}_{F,\Sigma_p^{-1}}
-    \end{bmatrix}_{i,j\in[d]^2}\right)\theta
-     = \begin{bmatrix}\inp{\Phi_{i}^T}{Y^T}_{F,\Sigma_p^{-1}}\end{bmatrix}_{i\in[d]}
+    M_t^z = \exp{\left(\sum_{s=1}^t z^T X_s^T \Sigma_p^{-1} \eta_s - \frac{1}{2} (X_s z)^T\Sigma_p^{-1}(X_s z) \right)} = \prod_{s=1}^{t} D_s^z
+\end{align*}
+and using the Sub-Gaussianity of $\eta_t$
+\begin{align*}
+    \expectedvalue\left[D_t^z \condbar F_{t-1}\right] &= \exp{\left(- \frac{1}{2}\|X_t z\|_{\Sigma_p^{-1}}\right)} \expectedvalue\left[\exp{\left(\inp{X_t z}{\eta_t}_{\Sigma_p^{-1}}\right)} \condbar F_{t-1}\right]  \\
+    &\leq \exp{\left(- \frac{1}{2}\|X_t z\|_{\Sigma_p^{-1}}\right)}\exp{\left((z^T X_t^T \Sigma_p^{-1})\Sigma_p(\Sigma_p^{-1} X_t z)\right)}\\
+    &= 1
+\end{align*}
+\begin{align*}
+    \expectedvalue\left[M_t^z \condbar F_{t-1}\right] = \left(\prod_{s=1}^{t-1} D_s^z\right) \expectedvalue\left[D_t^z \condbar F_{t-1}\right] \leq M_{t-1}^z
 \end{align*}
@@
 
-\paragraph{Confidence ellipsoid}
+% \begin{equation}
+%     \label{eq:regression_min}
+%     \min_{\theta\in\Real^d} \|(Y_{[N]} -\Phi_{[N]}\theta)^T\|_{F,\Sigma_p^{-1}}^2 + \lambda\|\theta\|_{\Sigma_d}^2
+% \end{equation}
 
-In order to study the concentration of $\theta_{N,\lambda}$, we reinject the expression of $Y$ into \eqref{eq:vector_rls}:
-\begin{align*}
-    \theta_{N,\lambda} &= G_{N, \lambda}^{-1} \begin{bmatrix}\inp{\Phi_{[N],i}^T}{\sum_{i=j}^d\theta_j\Phi_{[N],j}^T  + \Omega_{[N]}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]}\\
-    &= G_{N, \lambda}^{-1}\begin{bmatrix}\inp{\Phi_{[N],i}^T}{\Omega_{[N]}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]} + 
-    G_{N, \lambda}^{-1} \sum_{i=j}^d\theta_j\begin{bmatrix}\inp{\Phi_{[N],i}^T}{\Phi_{[N],j}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]}\\
-    &= G_{N, \lambda}^{-1}\begin{bmatrix}\inp{\Phi_{[N],i}^T}{\Omega_{[N]}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]} + 
-    G_{N, \lambda}^{-1}\left(G_{N, \lambda}-\lambda\Sigma_d\right)\theta\\
-    &= \theta + G_{N, \lambda}^{-1}\begin{bmatrix}\inp{\Phi_{[N],i}^T}{\Omega_{[N]}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]} -
-    G_{N, \lambda}^{-1}\lambda\Sigma_d\theta
-\end{align*}
+% The solution can be obtained as:
 
-Hence, for all $x\in\Real^d$,
-\begin{align*}
-    x^T\theta_{N,\lambda}  -x^T\theta &= x^T G_{N, \lambda}^{-1}\begin{bmatrix}\inp{\Phi_{[N],i}^T}{\Omega_{[N]}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]} 
-    - x^T G_{N, \lambda}^{-1}\lambda\Sigma_d\theta\\
-    &= \inp{x}{\begin{bmatrix}\inp{\Phi_{[N],i}^T}{\Omega_{[N]}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]}}_{G_{N, \lambda}^{-1}} - \lambda\inp{x}{\Sigma_d\theta}_{G_{N, \lambda}^{-1}}
-\end{align*}
+% \begin{theorem}[Regularized solution] The solution to \eqref{eq:regression_min} is:
+% \begin{equation}
+%     \label{eq:vector_rls}
+%     \theta_{N,\lambda} = G_{N, \lambda}^{-1} \begin{bmatrix}\inp{\Phi_{[N],i}^T}{Y_{[N]}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]}
+% \end{equation}
+% where $\Phi_{[N],i}\in\Real^{N\times p}$ is the $i^\text{th}$ component of $\Phi_{[N]}$ along the last dimension $i\in[d]$, and
+% \begin{equation*}
+%     G_{N, \lambda} = \begin{bmatrix}\inp{\Phi_{[N],i}^T}{\Phi_{[N],j}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i,j\in[d]^2} + \lambda \Sigma_d \in \Real^{d\times d}.
+% \end{equation*}
+% \end{theorem}
 
-Using the Cauchy-Schwartz inequality, we get:
-\begin{align*}
-    |x^T\theta_{N,\lambda}  -x^T\theta| &\leq \|x\|_{G_{N, \lambda}^{-1}}\left(\left\|\begin{bmatrix}\inp{\Phi_{[N],i}^T}{\Omega_{[N]}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]}\right\|_{G_{N, \lambda}^{-1}} + \lambda\|\Sigma_d\theta\|_{G_{N, \lambda}^{-1}}\right)
-\end{align*}
-\todo[inline]{EL: The first term is a $\Real^d$ vector whose coefficients are inner product of matrices (a sum along both the time $N$ and $p$ dimensions).
+% \begin{proof}
+% In this proof, we drop the $[N]$ subscripts for simplicity.
+% Let $i\in[d]$ and denote $Y_{-i} = Y - \sum_{j\in[d], j\neq i} \theta_j\Phi_{j}$.
+
+% We differentiate the objective $J(\theta) = \|(Y -\Phi\theta)^T\|_{F,\Sigma_p^{-1}}^2 + \lambda\|\theta\|_{\Sigma_d}^2$ as in  \eqref{eq:regression_min} with respect to $\theta_i$:
+% \begin{align*}
+%     J(\theta) &= \|(Y - \sum_{j=1}^d\theta_j\Phi_{j})^T\|_{F,\Sigma_p^{-1}}^2 + \lambda\|\theta\|_{\Sigma_d}^2\\
+%     &=  \|(Y_{-i} - \theta_i\Phi_{i})^T\|_{F,\Sigma_p^{-1}}^2 + \lambda\|\theta\|_{\Sigma_d}^2\\
+%     &= \inp{(Y_{-i} - \theta_i\Phi_{i})^T}{(Y_{-i} - \theta_i\Phi_{i})^T}_{F,\Sigma_p^{-1}} + \lambda\|\theta\|_{\Sigma_d}^2\\
+%     &= \theta_i^2\inp{\Phi_{i}^T}{\Phi_{i}^T}_{F,\Sigma_p^{-1}}
+%     -\theta_i\inp{\Phi_{i}^T}{Y_{-i}^T}_{F,\Sigma_p^{-1}}
+%     -\theta_i\inp{Y_{-i}^T}{\Phi_{i}^T}_{F,\Sigma_p^{-1}}
+%     + \inp{Y_{-i}^T}{Y_{-i}^T}_{F,\Sigma_p^{-1}}
+%     \\
+%     &\quad+ \lambda\|\theta\|_{\Sigma_d}^2
+% \end{align*}
+
+% Hence, 
+% \begin{align*}
+%     \nabla_{\theta_i} J(\theta) &= 2\theta_i\inp{\Phi_{i}^T}{\Phi_{i}^T}_{F,\Sigma_p^{-1}}
+%     -2\inp{\Phi_{i}^T}{Y_{-i}^T}_{F,\Sigma_p^{-1}}
+%     +2\lambda\theta^T\Sigma_{d,i}\\
+%     &= 2\theta_i\inp{\Phi_{i}^T}{\Phi_{i}^T}_{F,\Sigma_p^{-1}}
+%     +2\sum_{j\neq i}\theta_j\inp{\Phi_{i}^T}{\Phi_{j}^T}_{F,\Sigma_p^{-1}}
+%     -2\inp{\Phi_{i}^T}{Y^T}_{F,\Sigma_p^{-1}}
+%     +2\lambda\theta^T\Sigma_{d,i}\\
+%     &= 2\theta^T\begin{bmatrix}
+%     \inp{\Phi_{i}^T}{\Phi_{j}^T}_{F,\Sigma_p^{-1}}
+%     \end{bmatrix}_{j\in[d]}
+%     -2\inp{\Phi_{i}^T}{Y^T}_{F,\Sigma_p^{-1}}
+%     +2\lambda\theta^T\Sigma_{d,i}\\
+% \end{align*}
+
+% Since, $\nabla_{\theta}J(\theta) = 0 \iff \forall i,\, \nabla_{\theta_i}J(\theta) = 0$, we obtain the following optimality condition:
+
+% \begin{align*}
+%     \forall i,  \theta^T\left(\lambda\Sigma_{d,i} + \begin{bmatrix}
+%     \inp{\Phi_{i}^T}{\Phi_{j}^T}_{F,\Sigma_p^{-1}}
+%     \end{bmatrix}_{j\in[d]}\right)
+%      = \inp{\Phi_{i}^T}{Y^T}_{F,\Sigma_p^{-1}}
+% \end{align*}
+% By transposing and arranging the $[d]$ equations in matrix form,
+% \begin{align*}
+%     \left(\lambda\Sigma_{d} + \begin{bmatrix}
+%     \inp{\Phi_{i}^T}{\Phi_{j}^T}_{F,\Sigma_p^{-1}}
+%     \end{bmatrix}_{i,j\in[d]^2}\right)\theta
+%      = \begin{bmatrix}\inp{\Phi_{i}^T}{Y^T}_{F,\Sigma_p^{-1}}\end{bmatrix}_{i\in[d]}
+% \end{align*}
+
+% \end{proof}
+
+% \paragraph{Confidence ellipsoid}
+
+% In order to study the concentration of $\theta_{N,\lambda}$, we reinject the expression of $Y$ into \eqref{eq:vector_rls}:
+% \begin{align*}
+%     \theta_{N,\lambda} &= G_{N, \lambda}^{-1} \begin{bmatrix}\inp{\Phi_{[N],i}^T}{\sum_{i=j}^d\theta_j\Phi_{[N],j}^T  + \Omega_{[N]}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]}\\
+%     &= G_{N, \lambda}^{-1}\begin{bmatrix}\inp{\Phi_{[N],i}^T}{\Omega_{[N]}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]} + 
+%     G_{N, \lambda}^{-1} \sum_{i=j}^d\theta_j\begin{bmatrix}\inp{\Phi_{[N],i}^T}{\Phi_{[N],j}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]}\\
+%     &= G_{N, \lambda}^{-1}\begin{bmatrix}\inp{\Phi_{[N],i}^T}{\Omega_{[N]}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]} + 
+%     G_{N, \lambda}^{-1}\left(G_{N, \lambda}-\lambda\Sigma_d\right)\theta\\
+%     &= \theta + G_{N, \lambda}^{-1}\begin{bmatrix}\inp{\Phi_{[N],i}^T}{\Omega_{[N]}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]} -
+%     G_{N, \lambda}^{-1}\lambda\Sigma_d\theta
+% \end{align*}
+
+% Hence, for all $x\in\Real^d$,
+% \begin{align*}
+%     x^T\theta_{N,\lambda}  -x^T\theta &= x^T G_{N, \lambda}^{-1}\begin{bmatrix}\inp{\Phi_{[N],i}^T}{\Omega_{[N]}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]} 
+%     - x^T G_{N, \lambda}^{-1}\lambda\Sigma_d\theta\\
+%     &= \inp{x}{\begin{bmatrix}\inp{\Phi_{[N],i}^T}{\Omega_{[N]}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]}}_{G_{N, \lambda}^{-1}} - \lambda\inp{x}{\Sigma_d\theta}_{G_{N, \lambda}^{-1}}
+% \end{align*}
+
+% Using the Cauchy-Schwartz inequality, we get:
+% \begin{align*}
+%     |x^T\theta_{N,\lambda}  -x^T\theta| &\leq \|x\|_{G_{N, \lambda}^{-1}}\left(\left\|\begin{bmatrix}\inp{\Phi_{[N],i}^T}{\Omega_{[N]}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]}\right\|_{G_{N, \lambda}^{-1}} + \lambda\|\Sigma_d\theta\|_{G_{N, \lambda}^{-1}}\right)
+% \end{align*}
+
+% \todo[inline]{EL: The first term is a $\Real^d$ vector whose coefficients are inner product of matrices (a sum along both the time $N$ and state dimension $p$).
 How to analyze its concentration?
@@
 
+% \begin{lemma}[Theorem 1 of \citep{Abbasi2011}, Matrix version]
+% Let $\{F_t\}_{t=0}$ be a filtration.
+% Let $\{\eta_t\}_{t=1}^\infty$ be a $\Real^p$-valued stochastic process such that $\eta_t$ is $F_t$-measurable and $\eta_t$ is Gaussian with mean $0_p$ and covariance $\Sigma_p$.
+
+% Let $\{X_t\}_{t=1}^\infty$ be an $\Real^{p\times d}$-valued stochastic process such that $X_t$ is $F_t$-measurable.
+Assume that $V$ is a $d\times d$ positive definite matrix.
+For any $t\geq 0$, define:
+
+% \begin{equation*}
+%     V_t = V + \sum_{s=1}^t X_s X_s^t \qquad S_t = \sum_{s=1}^t X_s^T\eta_s
+% \end{equation*}
+% Then, for any $\delta>0$, with probability at least $1-\delta$, for all $t\geq0$
+% \todo[inline]{EL: Which kind of concentration?}
+% \end{lemma}
+% \begin{proof}
+% \todo[inline]{TODO}
+% \end{proof}
+}
 \paragraph{Confidence polytope}
 
-Given a confidence ellipsoid $C_\delta$, we can enclose it by a polytope $P_\delta$:
+\begin{proposition}
+We can enclose the confidence ellipsoid $C_\delta$ obtained in $\eqref{eq:confidence-ellipsoid}$ within a polytope $P_\delta$:
 \[\cC_\delta \subset \cP_\delta\]
@@
 \begin{equation}
-     \exists A_0,\Delta A_{1:p}: \cP_\delta = \left\{ A_{0}+\sum_{i=1}^{p}\lambda_{i}\Delta A_{i}: \lambda\in[0, 1]^p,  \sum_{i=1}^{p}\lambda_{i}=1\right\}.
+     \cP_\delta = \left\{ A_{0}+\sum_{i=1}^{2^d}\lambda_{i}\Delta A_{i}: \lambda\in[0, 1]^{2^d},  \sum_{i=1}^{2^d}\lambda_{i}=1\right\}.
 \end{equation}
+with 
+\begin{align*}
+    &G_{N,\lambda}^{-1} = PDP^{-1}\\
+    &h_k \text{ is the }k^\text{th}\text{ element of }\{-1,1\}^d\text{, for } k\in[2^d]\\
+    &\Delta\theta_k = 2 C_{n,\lambda,\delta}^{1/2} P^{-1}D^{-1/2} h_k \\
+    &A_0 = \theta_{N,\lambda}^T\Phi\\
+    &\Delta A_k = \Delta\theta_k^T\Phi\\
+\end{align*}
+\end{proposition}
 

### 2019-12-20 main.tex
Updates from Overleaf

@@
     &h_k \text{ is the }k^\text{th}\text{ element of }\{-1,1\}^d\text{, for } k\in[2^d]\\
-    &\Delta\theta_k = 2 C_{n,\lambda,\delta}^{1/2} P^{-1}D^{-1/2} h_k \\
+    &\Delta\theta_k = C_{N,\lambda,\delta}^{1/2} P^{-1}D^{-1/2} h_k \\
     &A_0 = \theta_{N,\lambda}^T\Phi\\
@@
 \end{proposition}
+\begin{proof}
+The ellipsoid in \eqref{eq:confidence-ellipsoid} is described by:
+\begin{align*}
+    \theta\in\cC_\delta &\implies
+    (\theta-\theta_{N,\lambda})^T G_{N,\lambda}^{-1}(\theta-\theta_{N,\lambda}) \leq C_{N,\lambda,\delta}\\
+    &\implies (\theta'-\theta'_{N,\lambda})^T D (\theta'-\theta'_{N,\lambda}) \leq C_{N,\lambda,\delta}\\
+    &\implies \sum_{i=1}^d D_{i,i}(\theta'_i-\theta'_{N,\lambda,i})^2\leq C_{N,\lambda,\delta}\\
+    &\implies\forall i, |\theta'_i-\theta'_{N,\lambda,i}|\leq C_{N,\lambda,\delta}^{1/2}D_{i,i}^{-1/2}
+\end{align*}
+This describes a $\Real^d$ box containing $\theta' = P\theta$, whose $k^\text{th}$ vertex is represented by $\theta_{N,\lambda}' + C_{N,\lambda,\delta}^{1/2}D^{-1/2} h_k$.
+We obtain the corresponding box on $\theta$ by transforming each vertex of the box with $P^{-1}$.
+\end{proof}
 

### 2020-01-13 main.tex
Updates from Overleaf

--- 2019-12-05 main.tex
@@
 \documentclass{article}
+\usepackage[cm]{fullpage}
+
 \usepackage[utf8]{inputenc}
@@
 
-\title{An Integrated Framework for Robust Estimation, Prediction and Control}
+\title{Robust Estimation, Prediction and Control with Dynamics Structure}
 \author{Edouard Leurent, Denis Efimov, Odalric-Ambrym Maillard}
@@
 \maketitle
+
+\section{Related Work}
+
+For LQ systems, where parameters A,B are unknown and no structure is available.
+\begin{itemize}
+    \item OFU: \citep{abbasi-yadkori11a}.
+Summary: $\theta=(A~B)$, ellipsoid in Frobenius norm + controllability constraint, choose and stabilize (Ricatti) an optimistic candidate, cumulative regret in $O(\sqrt{T}\log\frac{1}{\delta})$.
+    \item PSRL with TS: \citep{abeille18a}.
+Summary: RLS estimate + normal perturbation in the ellipsoid + rejection sampling over a controllability constraint, with frequent update, cumulative regret in $\tilde{O}(\sqrt{T})$
+    \item Offline estimation and control synthesis: \citep{Dean2017}.
+Summary: Estimation procedure of $N$ episodes of duration $T$ with gaussian excitation, ellipsoid in L2 norm, robust controller with System Level Synthesis, simple regret in $O(\sqrt{\frac{\log(1/\delta)}{N}})$
+    \item \citep{Dean2018}
+\end{itemize}
+
+Differences with our work:
+\begin{itemize}
+    \item We with to act in a reasonable (structure) but cautious (robust) way, and progressively get more and more aggressive as we obtain more data and reduce uncertainty.
+    \item Thus, we do not wish to explore actively the more promising regions as in OFU, nor the more likely region as in TS, nor act randomly as in Coarse-ID.
+    \item We have linear dynamics but our cost is not quadratic (to accurately represent planning task with discrete/branching decisions: e.g. take or give way)
+    \item Our optimisation problem amounts to discrete controller selection, instead of continuous controller synthesis
+
+\end{itemize}
 
@@
 $
-    \dot{x}(t) + C\eta(t)
+    \dot{x}(t) + C\nu(t)
 $
@@
 \label{eq:measurement}
-    y(t) = \dot{x}(t) - Bu(t) + C\eta(t)
+    y(t) = \dot{x}(t) - Bu(t) + C\nu(t)
 \end{equation}
-where $\eta(t)\in\Real^r$ is a measurement noise and $C\in\Real^{p\times r}$ is known. Assumptions over the disturbance $\omega$ and noise $\eta$ will be detailed further.
+where $\nu(t)\in\Real^r$ is a measurement noise and $C\in\Real^{p\times r}$ is known. Assumptions over the disturbance $\omega$ and noise $\nu$ will be detailed further.
 
@@
 
-\paragraph{Objective}% The model estimation procedure is dedicated to building a confidence region around the unknown true model $A(\theta)$. 
+\paragraph{Objective}
 Having observed at times $(t_n)_{n\in[N]}$ a history of transitions $\cD = \{(x_n = x(t_n), u_n = u(t_n), y_n = y(t_n))\}_{n\in[N]}$, and given a confidence level $\delta\in[0, 1]$, our goal is to find a confidence region $\cC_\delta$ as tight as possible and such that it holds that:
@@
 
-This involves the trilemma of confidence intervals, where one of three things must be true:
-\begin{enumerate}
-    \item $A(\theta)$ is in $\cC_\delta$
-    \item We got data that was very ($\leq\delta$) unlikely under all possible values $A(\theta)$
-    \item Our model is wrong
-\end{enumerate}
+% This involves the trilemma of confidence intervals, where one of three things must be true:
+% \begin{enumerate}
+%     \item $A(\theta)$ is in $\cC_\delta$
+%     \item We got data that was very ($\leq\delta$) unlikely under all possible values $A(\theta)$
+%     \item Our model is wrong
+% \end{enumerate}
 
@@
 We further assume that the dynamics $A(\theta)$ enjoy the following additional structure:
-\begin{assumption}[Linear Parametrisation]
+\begin{assumption}[Linear parametrisation]
 \label{assumpt:linear_param}
@@
 \begin{equation}
-    A(\theta) = \theta^T \phi \eqdef \sum_{i=1}^d \theta_i\phi_i
+    A(\theta) = \theta^\transp \phi \eqdef \sum_{i=1}^d \theta_i\phi_i
 \end{equation}
 where $\phi_i\in\Real^{p\times p}$ for all $i\in[d]$.
+
+For all $n\geq 0$, we also denote $\Phi_n = [\phi_1 x_n \cdots \phi_d x_n]\in\Real^{p\times d}$.
 \end{assumption}
 
-\begin{assumption}[Noise Model]
-\label{assumpt:noise}
-At each time $t\geq0$ the measurement noise $\eta(t)$ and disturbance $\omega(t)$  are independent Gaussians with respective means $0_r, 0_s$ and covariances $\Sigma_r, \Sigma_s$:
-\begin{equation*}
-    \eta(t)\sim \cN(0_r,\Sigma_r),\quad\omega(t)\sim \cN(0_s,\Sigma_s)
-\end{equation*}
-We further require that the matrix $\Sigma_p = C\Sigma_r C^T + D\Sigma_s D^T \in \Real^{p\times p}$ is full-rank.
-\end{assumption}
-
-Note that the full-rank condition in \autoref{assumpt:noise} would be harder to fulfil were it formulated only for the disturbance $D\Sigma_s D^T$, whereas it would be quite reasonable to assume, for instance, that $r=p$, which is sufficient.
-
-\begin{proposition}[Maximum Likelihood Estimate]
-\label{prop:mle}
-The maximum likelihood estimate for $\theta$ minimises a weighted mean square error:
-\begin{equation*}
-    \argmax_{\theta\in\Real^d} \probability{\cD\condbar\eqref{eq:dynamics};\Sigma} = \argmin_{\theta\in\Real^d} \sum_{n=1}^N \|y_n -\theta^T\phi x_n\|_{\Sigma_p^{-1}}^2
-\end{equation*}
-\end{proposition}
-\begin{proof}
-For $n\in[N]$, at time $t_n$, we have
-\begin{align*}
-    \probability{y_n, x_n} 
-    &= \probability{y_n|x_n}\probability{x_n}\\
-    &= \probability{y_n = \dot{x}_n - Bu_n +C\eta_n|x_n,u_n}\probability{x_n}\\
-    &= \probability{A(\theta)x_n + B u_n + D \omega_n - Bu_n +C\eta_n = y_n|x_n}\probability{x_n}\\
-    &= \probability{C\eta_n + D \omega_n = y_n- \theta^T \phi x_n |x_n}\probability{x_n}\\
-    &= \cN(y_n - \theta^T \phi x_n; 0_p,\Sigma_p)\probability{x_n}
-\end{align*}
-By independence of the noise at different times, we have:
-\begin{align*}
-    \log\probability{\cD;\Sigma} &= \log\prod_{n=1}^N\probability{y_n, x_n}\\
-    &= \sum_{n=1}^N\log \cN(y_n- \theta^T \phi x_n;0_p,\Sigma_p) + \log\probability{x_n}\\
-    &= \sum_{n=1}^N -\frac{1}{2} \|y_n -\theta^T\phi x_n\|_{\Sigma_p^{-1}}^2 - \log\left((2\pi)^{p/2} \det(\Sigma_p)^{1/2}\right) + \log\probability{x_n}
-\end{align*}
-\end{proof}
-
-We stack the observations $y(t_n), x(t_n)$ in $\cD$, as $Y_{[N]}, X_{[N]}\in\Real^{N\times p}$ and the noises $C\eta(t_n)+D\omega(t_n)$ as $\Omega_{[N]} \in\Real^{N\times p}$ to obtain the regression problem:
+\paragraph{Regularised least square} Since we expect that $\Phi_n$ may have zero-coordinates during possibly long time intervals (i.e.
+some features are not always active), we consider the weighted $L_2$-regularised regression problem with weights  $\Sigma_p\in\Real^{p\times p}$ and $\Sigma_d\in\Real^{d\times d}$ and parameter $\lambda\in\Real^+_*$:
 
 \begin{equation}
-    \label{eq:regression}
-    Y_{[N]} = \Phi_{[N]} \theta + \Omega_{[N]},
+    \label{eq:regression_min}
+    \min_{\theta\in\Real^d} \sum_{n=1}^N \|y_n -\Phi_n\theta\|_{\Sigma_p^{-1}}^2 + \lambda\|\theta\|_{\Sigma_d}^2
 \end{equation}
-with $\Phi_{[N]} = X_{[N]}\phi^T\in \Real^{N\times p\times d}$.
 
-% As detailed in \autoref{prop:mle}, we wish to solve:
-% \begin{equation*}
-%     \min_{\theta\in\Real^d} \|Y_{[N]} -\Phi_{[N]}\theta\|_{\Sigma_p^{-1}}^2
-% \end{equation*}
+The solution can be obtained as:
 
-% where we denote $\|z\|_S^2 = z S z^T$ for $z\in\Real^{N\times p}$ and $S\in\Real^{p\times p}$.
+\begin{theorem}[Regularised solution]
+\label{thm:regularized_solution}
+The solution to \eqref{eq:regression_min} is:
+\begin{equation}
+    \label{eq:vector_rls}
+    \theta_{N,\lambda} = G_{N, \lambda}^{-1} \sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1} y_n
+\end{equation}
+where 
+\begin{equation*}
+    G_{N, \lambda} = \sum_{n=1}^N \Phi_{n}^\transp\Sigma_p^{-1}\Phi_{n}  + \lambda \Sigma_d \in \Real^{d\times d}.
+\end{equation*}
+\end{theorem}
 
-\subsection{Scalar formulation}
-
-\begin{proposition}[Decoupling the noise]
-Without loss of generality, up to a change of basis, we can assume that $\Sigma_d$ is diagonal.
-\end{proposition}
-\begin{proof}
-Since $\Sigma_p$ is a symmetric real matrix, it is diagonalisable: there exists $Q\in\cO(p)$ and a diagonal matrix $R$ such that $\Sigma_p = QRQ^{-1}$.
-Hence, from \eqref{eq:dynamics} and \eqref{eq:measurement}:
+Denote $\eta(t) = C\nu(t) + D\omega(t)$. By substituting the expression of $y_n$ into \eqref{eq:vector_rls}, we obtain:
+\begin{lemma}[Regression error]
+\label{lem:regression-error}
 \begin{align*}
-    Q^{-1}y'(t) &= \sum_{i=1}^d \theta_i Q^{-1}\phi_i x(t) + Q^{-1}(C\eta(t) + D\omega(t))
-\end{align*}
-By rewriting $y \leftarrow Q^{-1}y, \phi_i\leftarrow Q^{-1}\phi_i, C\leftarrow Q^{-1}C$, and $D\leftarrow Q^{-1}D$ we recover \eqref{eq:dynamics} and \eqref{eq:measurement} in their original form, while now having $C\Sigma_rC^T + D\Sigma_rD^T = R$.
-\end{proof}
-
-In order to solve the regression problem \eqref{eq:regression} can simply reshape the two first $N\times p$ dimensions into a single $Np$ dimension.
-Since $\Sigma_p$ is diagonal, the noises on each row of $\Omega$ are independent, the problem becomes a standard scalar regression problem with heteroscedastic noise (if $\Sigma_p$ is not proportional to $I_p$), and the Lemma 5 of \citet{kirschner18heteroscedastic} can be applied.
-
-\begin{lemma}[Confidence ellipsoid \citep{kirschner18heteroscedastic}]
-Assuming that $\Sigma_p$ is diagonal and $\|\theta\|_2\leq S$, it holds with probability $1-\delta$ that:
-\begin{equation*}
-    \|\theta - \theta_{Np,\lambda}\|_{G_{Np,\lambda}} \leq \sqrt{2\log \frac{\text{det}(G_{Np,\lambda})^{1/2}\text{det}(\lambda I)^{-1/2}}{\delta}} + \lambda^{1/2}S
-\end{equation*}
-where
-\begin{align*}
-    \Phi_{[Np]}& \in\Real^{Np\times d},\, Y_{[Np]}\in \Real^{Np} \text{ are the flattened versions of $\Phi_{[N]}$, $Y_{[N]}$};\\
-    \tilde{\Phi}_{[Np]} &= \Phi_{[Np]} [\underbrace{\cdots \Sigma_p^{-1} \cdots}_{\text{$N$ times}}]^T, \qquad  \tilde{Y}_{[Np]} = Y_{[Np]} [\underbrace{\cdots \Sigma_p^{-1} \cdots}_{\text{$N$ times}}]^T;\\
-    G_{Np, \lambda} &= \tilde{\Phi}^T_{[Np]}\tilde{\Phi}_{[Np]} + \lambda I_d;\\
-    \theta_{Np,\lambda} &= G_{Np, \lambda}^{-1} \tilde{\Phi}^T_{[Np]}\tilde{Y}_{[Np]}.
+    \theta_{N,\lambda} - \theta = G_{N, \lambda}^{-1}\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\eta_n - G_{N, \lambda}^{-1}\lambda\Sigma_d\theta 
 \end{align*}
@@
 
-\subsection{Vector formulation}
-In the general case, we denote the weighted version of the Frobenius inner product and Frobenius norm as $\inp{M}{N}_{F,\Sigma} = \Tr (M^T \Sigma N)$ and $\|M\|_{F,\Sigma}^2 = \inp{M}{M}_{F,\Sigma}$.
+Depending on the assumption we take over the noise $\eta_n$ and the true parameter $\theta$, we can bound the regression error $\theta_{N,\lambda} - \theta$ in different ways.
 
-\paragraph{Regularized solution} Since we expect that $\phi x(t)$ may have zero-coordinates during possibly long time intervals (i.e.
-some features are not always active), we consider instead the weighted $l_2$ regularised problem with parameter $\lambda\in\Real^+_*$ and weights $\Sigma_d\in\Real^{d\times d}$:
+\subsection{Sub-Gaussian noise}
 
-\begin{equation}
-    \label{eq:regression_min}
-    \min_{\theta\in\Real^d} \|(Y_{[N]} -\Phi_{[N]}\theta)^T\|_{F,\Sigma_p^{-1}}^2 + \lambda\|\theta\|_{\Sigma_d}^2
-\end{equation}
+We say that a random vector $x\in\Real^k$ is sub-Gaussian with covariance proxy $\Sigma$, and denote $x\sim Sub_G(\Sigma)$, if $\expectedvalue[x] = 0_k$ and:
+\[
+\forall u\in\Real^k, \expectedvalue \left[ \exp{\left( u^\transp x\right)}\right] \leq \exp{\left( \frac{1}{2} u^\transp \Sigma u\right)}
+\]
 
-%For simplicity, we abuse notations and replace $Y_{[N]}$ and $\Phi_{[N]}$ by their transposed forms $Y_{[N]}^T\in\Real^{p\timesN}$ and $\Phi_{[N]}^T\in\Real^{d\times p\times N}$.
+\begin{assumption}[Sub-Gaussian Noise Model]
+\label{assumpt:noise}
+At each time $t\geq0$ the sum $\eta(t)$ of projected measurement noise $\nu(t)$ and disturbance $\omega(t)$ is a Sub-Gaussian noises with covariance proxy $\Sigma_p \in \Real^{p\times p}$:
+\begin{equation*}
+    \eta(t) = C\nu(t) + D\omega(t) \sim Sub_G(\Sigma_p)
+\end{equation*}
 
-The solution can be obtained as:
+For instance, this is the case of $\nu$ and $\omega$ are Gaussian noises with respective covariance matrices $\Sigma_r$ and $\Sigma_s$, with $\Sigma_p \eqdef C\Sigma_r C^\transp + D\Sigma_s D^\transp$.
+\end{assumption}
 
-\begin{theorem}[Regularized solution] The solution to \eqref{eq:regression_min} is:
-\begin{equation}
-    \label{eq:vector_rls}
-    \theta_{N,\lambda} = G_{N, \lambda}^{-1} \begin{bmatrix}\inp{\Phi_{[N],i}^T}{Y_{[N]}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]}
-\end{equation}
-where $\Phi_{[N],i}\in\Real^{p\times d}$ is the $i^\text{th}$ component of $\Phi_{[N]}$ along the first dimension, and
+\begin{lemma}[Theorem 1 of \citep{Abbasi2011}, Matrix version]
+\label{lem:concentration}
+Let $\{F_t\}_{t=0}$ be a filtration.
+Let $\{\eta_t\}_{t=1}^\infty$ be a $\Real^p$-valued stochastic process such that $\eta_t$ is $F_t$-measurable and conditionally $\Sigma_p$-SubGaussian.
+
+Let $\{\Phi_t\}_{t=1}^\infty$ be an $\Real^{p\times d}$-valued stochastic process such that $\Phi_t$ is $F_t$-measurable.
+Assume that $G$ is a $d\times d$ positive definite matrix.
+For any $t\geq 0$, define:
+
 \begin{equation*}
-    G_{N, \lambda} = \begin{bmatrix}\inp{\Phi_{[N],i}^T}{\Phi_{[N],j}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i,j\in[d]^2} + \lambda \Sigma_d \in \Real^{d\times d}.
+    \overline{G}_t = G + \sum_{s=1}^t \Phi_s^\transp \Sigma_p^{-1} \Phi_s \in \Real^{d\times d} \qquad S_t = \sum_{s=1}^t \Phi_s^\transp\Sigma_p^{-1}\eta_s \in \Real^{d}
 \end{equation*}
+Then, for any $\delta>0$, with probability at least $1-\delta$, for all $t\geq0$
+
+\begin{align*}
+    \|S_t\|_{\overline{G_t}} \leq \cdots
+\end{align*}
+\end{lemma}
+
+\begin{theorem}[Confidence ellipsoid]
+\label{thm:confidence_ellipsoid}
+\todo[inline]{TODO}
 \end{theorem}
 
-\begin{proof}
-In this proof, we drop the $[N]$ subscripts for simplicity.
-Let $i\in[d]$ and denote $Y_{-i} = Y - \sum_{j\in[d], j\neq i} \theta_j\Phi_{j}$.
-
-We differentiate the objective $J(\theta) = \|(Y -\Phi\theta)^T\|_{F,\Sigma_p^{-1}}^2 + \lambda\|\theta\|_{\Sigma_d}^2$ as in  \eqref{eq:regression_min} with respect to $\theta_i$:
-\begin{align*}
-    J(\theta) &= \|(Y - \sum_{j=1}^d\theta_j\Phi_{j})^T\|_{F,\Sigma_p^{-1}}^2 + \lambda\|\theta\|_{\Sigma_d}^2\\
-    &=  \|(Y_{-i} - \theta_i\Phi_{i})^T\|_{F,\Sigma_p^{-1}}^2 + \lambda\|\theta\|_{\Sigma_d}^2\\
-    &= \Tr\left((Y_{-i} - \theta_i\Phi_{i})\Sigma_p^{-1}(Y_{-i} - \theta_i\Phi_{i})^T\right) + \lambda\|\theta\|_{\Sigma_d}^2\\
-    &= \theta_i^2\Tr\left(\Phi_{i}\Sigma_p^{-1}\Phi_{i}^T\right) 
-    -\theta_i\Tr\left(\Phi_{i}\Sigma_p^{-1}Y_{-i}^T\right) 
-    -\theta_i\Tr\left(Y_{-i}\Sigma_p^{-1}\Phi_{i}^T\right)
-    + \Tr\left(Y_{-i}\Sigma_p^{-1}Y_{-i}^T\right)
-    \\
-    &\quad+ \lambda\|\theta\|_{\Sigma_d}^2
-\end{align*}
-
-Hence, 
-\begin{align*}
-    \nabla_{\theta_i} J(\theta) &= 2\theta_i\Tr\left(\Phi_{i}\Sigma_p^{-1}\Phi_{i}^T\right)
-    -2\Tr\left(\Phi_{i}\Sigma_p^{-1}Y_{-i}^T\right) 
-    +2\lambda\theta^T\Sigma_{d,i}\\
-    &= 2\theta_i\Tr\left(\Phi_{i}\Sigma_p^{-1}\Phi_{i}^T\right)
-    +2\sum_{j\neq i}\theta_j\Tr\left(\Phi_{i}\Sigma_p^{-1}\Phi_j^T\right) 
-    -2\Tr\left(\Phi_{i}\Sigma_p^{-1}Y^T\right) 
-    +2\lambda\theta^T\Sigma_{d,i}\\
-    &= 2\theta^T\begin{bmatrix}
-    \Tr\left(\Phi_i \Sigma_p^{-1} \Phi_j^T\right)
-    \end{bmatrix}_{j\in[d]}
-    -2\Tr\left(\Phi_{i}\Sigma_p^{-1}Y^T\right) 
-    +2\lambda\theta^T\Sigma_{d,i}\\
-\end{align*}
-
-Since, $\nabla_{\theta}J(\theta) = 0 \iff \forall i,\, \nabla_{\theta_i}J(\theta) = 0$, we obtain the following optimality condition:
-
-\begin{align*}
-    \forall i,  \theta^T\left(\lambda\Sigma_{d,i} + \begin{bmatrix}
-    \Tr\left(\Phi_i \Sigma_p^{-1} \Phi_j^T\right)
-    \end{bmatrix}_{j\in[d]}\right)
-     = \Tr\left(\Phi_{i}\Sigma_p^{-1}Y^T\right)
-\end{align*}
-By transposing and arranging the $[d]$ equations in matrix form,
-\begin{align*}
-    \left(\lambda\Sigma_{d} + \begin{bmatrix}
-    \inp{\Phi_{i}^T}{\Phi_{j}^T}_{F,\Sigma_p^{-1}}
-    \end{bmatrix}_{i,j\in[d]^2}\right)\theta
-     = \begin{bmatrix}\inp{\Phi_{i}^T}{Y^T}_{F,\Sigma_p^{-1}}\end{bmatrix}_{i\in[d]}
-\end{align*}
-
-\end{proof}
-
-\paragraph{Confidence ellipsoid}
-
-In order to study the concentration of $\theta_{N,\lambda}$, we reinject the expression of $Y$ into \eqref{eq:vector_rls}:
-\begin{align*}
-    \theta_{N,\lambda} &= G_{N, \lambda}^{-1} \begin{bmatrix}\inp{\Phi_{[N],i}^T}{\sum_{i=j}^d\theta_j\Phi_{[N],j}^T  + \Omega_{[N]}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]}\\
-    &= G_{N, \lambda}^{-1}\begin{bmatrix}\inp{\Phi_{[N],i}^T}{\Omega_{[N]}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]} + 
-    G_{N, \lambda}^{-1} \sum_{i=j}^d\theta_j\begin{bmatrix}\inp{\Phi_{[N],i}^T}{\Phi_{[N],j}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]}\\
-    &= G_{N, \lambda}^{-1}\begin{bmatrix}\inp{\Phi_{[N],i}^T}{\Omega_{[N]}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]} + 
-    G_{N, \lambda}^{-1}\left(G_{N, \lambda}-\lambda\Sigma_d\right)\theta\\
-    &= \theta + G_{N, \lambda}^{-1}\begin{bmatrix}\inp{\Phi_{[N],i}^T}{\Omega_{[N]}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]} -
-    G_{N, \lambda}^{-1}\lambda\Sigma_d\theta
-\end{align*}
-
-Hence, for all $x\in\Real^d$,
-\begin{align*}
-    x^T\theta_{N,\lambda}  -x^T\theta &= x^T G_{N, \lambda}^{-1}\begin{bmatrix}\inp{\Phi_{[N],i}^T}{\Omega_{[N]}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]} 
-    - x^T G_{N, \lambda}^{-1}\lambda\Sigma_d\theta\\
-    &= \inp{x}{\begin{bmatrix}\inp{\Phi_{[N],i}^T}{\Omega_{[N]}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]}}_{G_{N, \lambda}^{-1}} - \lambda\inp{x}{\Sigma_d\theta}_{G_{N, \lambda}^{-1}}
-\end{align*}
-
-Using the Cauchy-Schwartz inequality, we get:
-\begin{align*}
-    |x^T\theta_{N,\lambda}  -x^T\theta| &\leq \|x\|_{G_{N, \lambda}^{-1}}\left(\left\|\begin{bmatrix}\inp{\Phi_{[N],i}^T}{\Omega_{[N]}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]}\right\|_{G_{N, \lambda}^{-1}} + \lambda\|\Sigma_d\theta\|_{G_{N, \lambda}^{-1}}\right)
-\end{align*}
-\todo[inline]{EL: The first term is a $\Real^d$ vector whose coefficients are inner product of matrices (a sum along both the time $N$ and $p$ dimensions).
-How to analyze its concentration?
-For comparison, in \citep{Abbasi2011} $X^T\eta$ was a  $\Real^d$ vector whose coefficients were inner product of vectors $(X_i^T\eta)_i\in[d]$ (a sum over time $N$)}
-
-\paragraph{Confidence polytope}
-
-Given a confidence ellipsoid $C_\delta$, we can enclose it by a polytope $P_\delta$:
+\begin{lemma}[Confidence polytope]
+\label{lem:confidence_polytope}
+We can enclose the confidence ellipsoid $C_\delta$ obtained in $\eqref{eq:confidence-ellipsoid}$ within a polytope $P_\delta$:
 \[\cC_\delta \subset \cP_\delta\]
@@
 \begin{equation}
-     \exists A_0,\Delta A_{1:p}: \cP_\delta = \left\{ A_{0}+\sum_{i=1}^{p}\lambda_{i}\Delta A_{i}: \lambda\in[0, 1]^p,  \sum_{i=1}^{p}\lambda_{i}=1\right\}.
+     \cP_\delta = \left\{ A_{0}+\sum_{i=1}^{2^d}\lambda_{i}\Delta A_{i}: \lambda\in[0, 1]^{2^d},  \sum_{i=1}^{2^d}\lambda_{i}=1\right\}.
 \end{equation}
+with 
+\begin{align*}
+    &G_{N,\lambda}^{-1} = PDP^{-1}\\
+    &h_k \text{ is the }k^\text{th}\text{ element of }\{-1,1\}^d\text{, for } k\in[2^d]\\
+    &\Delta\theta_k = C_{N,\lambda,\delta}^{1/2} P^{-1}D^{-1/2} h_k \\
+    &A_0 = \theta_{N,\lambda}^\transp\Phi\\
+    &\Delta A_k = \Delta\theta_k^\transp\Phi\\
+\end{align*}
+\end{lemma}
+
+\begin{figure}
+    \centering
+    \includegraphics[trim={3.8cm, 2cm, 5cm, 3.8cm}, clip, width=0.6\textwidth]{img/ellipsoid_to_polytope}
+    \caption{From the confidence ellipsoid $\cC_\delta$ to its enclosing polytope $\cP_\delta$}
+    \label{fig:ellipsoid_to_polytope}
+\end{figure}
+
+\subsection{Bounded noise}
+
+\begin{assumption}[Bounded noise]
+The noise $\eta(t) = C\nu(t) + D\omega(t)$ is bounded.
+\[\|\eta\|_\infty < \infty\]
+\end{assumption}
+
+Then, 
+\[
+\|\theta_{N,\lambda} - \theta\|_1 \leq \|G_{N, \lambda}^{-1}\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\|_1\|\eta\|_\infty + \lambda\|G_{N, \lambda}^{-1}\Sigma_d\theta\|_1
+\]
+
+This $L_1$-ball is a polytope with $2d$ vertices, that we denote $\cP$.
 
@@
 
-\begin{example*}
-Consider a scalar system:
-\[
-\dot{x}(t)=-\theta(t)x(t)+d(t),\;t\geq0,
-\]
-where $x(t)\in\Real$ with $x(0)\in[\underline{x}_{0},\overline{x}_{0}]=[1.0, 1.1]$, $\theta(t)\in\Pi=[\underline{\theta},\overline{\theta}]=[0.5,1.5]$ and $d(t)\in[\underline{d},\overline{d}]=[-0.1,0.1]$ for all $t\geq0$.
+% \begin{example*}
+% Consider a scalar system:
+% \[
+% \dot{x}(t)=-\theta(t)x(t)+d(t),\;t\geq0,
+% \]
+% where $x(t)\in\Real$ with $x(0)\in[\underline{x}_{0},\overline{x}_{0}]=[1.0, 1.1]$, $\theta(t)\in\Pi=[\underline{\theta},\overline{\theta}]=[0.5,1.5]$ and $d(t)\in[\underline{d},\overline{d}]=[-0.1,0.1]$ for all $t\geq0$.
 The \autoref{fig:predictor_example} shows the state-interval obtained with \eqref{eq:interval_predictor}.
 
-\begin{figure}
-\begin{centering}
-\includegraphics[width=\linewidth]{img/interval_predictor}
-\par\end{centering}
-\caption{Several trajectories for different values of $\theta\in\Theta$ are shown in blue.
+% \begin{figure}
+% \begin{centering}
+% \includegraphics[width=\linewidth]{img/interval_predictor}
+% \par\end{centering}
+% \caption{Several trajectories for different values of $\theta\in\Theta$ are shown in blue.
 The result of prediction by \eqref{eq:interval_predictor} is in red: the predictor is stable and produces tight bounds.}
-\label{fig:predictor_example}
-\end{figure}
-\end{example*}
+% \label{fig:predictor_example}
+% \end{figure}
+% \end{example*}
 
@@
 
-In this section, we still assume that we have a high-confidence polytope $\cP$ that verifies \eqref{eq:polytope} with probability $1-\delta$.
-
-The \textbf{robust control} objective $v^r$:
+We consider the robust control objective $v^r$:
 \todo[inline]{EL: since the interval dynamics will be deterministic, use open-loop policies, ie sequences of actions $\mathbf{u}$ instead of closed-loop policies $\pi$}
@@
 \label{eq:robust-control}
-\max_\pi \underbrace{\min_{\theta \in \Theta} \expectedvalueover{\omega(t)}\left[\sum_{t=0}^\infty \gamma^t r(x(t))\condbar \dot{x}(t) = A(\theta) x(t) + B_u u(t) + B_\omega\omega(t), u_t = \pi(x_t)\right]}_{v^r(\pi)}
+\max_\pi \underbrace{\min_{A(\theta) \in \cP} \left[\sum_{t=0}^\infty \gamma^t r(x(t))\condbar u_t = \pi(x_t), \omega(t)\right]}_{v^r(\pi)}
 \end{equation}
@@
 \begin{definition}[Surrogate objective]
-We modify the robust objective $v^r$ in \eqref{eq:robust-control} by replacing the true reachability set by its interval prediction $[\underline{x}(t), \overline{x}(t)]$ based on the polytopic approximation $\cP_\delta$ of $A(\Theta)$:
+We approximate the robust objective $v^r$ in \eqref{eq:robust-control} by replacing the true reachability set by its interval prediction $[\underline{x}(t), \overline{x}(t)]$ based on the polytopic approximation $\cP_\delta$ of $A(\Theta)$:
 
 \begin{equation}
-\hat{v^r}(\pi) \eqdef \sum_{t=0}^\infty \gamma^t \min_{x\in[\underline{x}(t, \pi), \overline{x}(t, \pi)]}  r(x)
+\hat{v}^r(\pi) \eqdef \sum_{t=0}^\infty \gamma^t \min_{x\in[\underline{x}(t, \pi), \overline{x}(t, \pi)]}  r(x)
 \end{equation}
@@
 \label{prop:lower-bound}
-With high probability, the surrogate objective $\hat{v^r}$ is a lower bound of the true objective $v^r$:
+With high probability, the surrogate objective $\hat{v}^r$ is a lower bound of the true objective $v^r$:
 
 \begin{equation}
-\probability{\forall \pi, \hat{v^r}(\pi) \leq v^r(\pi)} \geq 1-\delta
+\hat{v}^r(\pi) \leq v^r(\pi)
 \end{equation}
+
+If we assume that $R$ is $L$-Lipschitz, then we can bound the other side:
+\begin{equation*}
+     \hat{v}^r(\pi) \leq v^r(\pi) \leq \hat{v}^r(\pi) + L\sum_{t=0}^\infty \gamma^t \mu([\underline{x}_N(t),\overline{x}_N(t)])
+\end{equation*}
 \end{property}
@@
 The robust objective error $v^r - \hat{v^r}$ stems from two terms: the approximation of the reachable set by the polytopic and interval approximations and the loss of time-dependency between the states within a single trajectory.
-If both these approximations are tight enough, maximizing the lower bound $\hat{v^r}$ will increase the true objective $v^r$, which is the idea behind Algorithm \ref{algo:irc}.
+If both these approximations are tight enough, maximising the lower bound $\hat{v^r}$ will increase the true objective $v^r$, which is the idea behind Algorithm \ref{algo:irc}.
 
@@
 
+What if our system dynamics \eqref{eq:dynamics} or linear parametrisation assumption \ref{assumpt:linear_param} are wrong?
+
 \subsection{Model adequacy}
+
+We can test the model adequacy, and eventually reject it.
+
+This suggest using multiple models with different sets of features.
+
 \subsection{Robust control with Discrete Ambiguity}
@@
 
+\appendix
+
+\section{Proofs}
+
+\subsection{Proof of \autoref{thm:regularized_solution}}
+
+\begin{proof}
+We differentiate $J(\theta) = \sum_{n=1}^N \|y_n -\Phi_n\theta\|_{\Sigma_p^{-1}}^2 + \lambda\|\theta\|_{\Sigma_d}^2$ as in  \eqref{eq:regression_min} with respect to $\theta$:
+
+\begin{align*}
+    \nabla_{\theta} J(\theta) &= \sum_{n=1}^N\nabla_{\theta} (y_n - \Phi_n\theta)^\transp\Sigma_p^{-1}(y_n - \Phi_n\theta) + \nabla_{\theta} \lambda\|\theta\|_{\Sigma_d}^2\\
+    &= -2\sum_{n=1}^N y_n^\transp\Sigma_p^{-1}\Phi_n + 2\sum_{n=1}^N\theta^\transp(\Phi_n^\transp\Sigma^{-1}\Phi_n) +  2 \lambda \theta^\transp \Sigma_d
+\end{align*}
+
+Hence,
+\begin{align*}
+    \nabla_{\theta} J(\theta) = 0 \iff \left(\sum_{n=1}^N\Phi_n^\transp\Sigma_p^{-1}\Phi_n + \Sigma_d\right)\theta = \sum_{n=1}^N y_n^\transp\Sigma_p^{-1}\Phi_n
+\end{align*}
+\end{proof}
+
+\subsection{Proof of \autoref{lem:regression-error}}
+
+In order to study the concentration of $\theta_{N,\lambda}$, we substitute the expression of $y_n$ into \eqref{eq:vector_rls}:
+\begin{align*}
+    \theta_{N,\lambda} &= G_{N, \lambda}^{-1} \sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1} (\Phi_n\theta +\eta_n)\\
+    &= \theta - G_{N, \lambda}^{-1}\lambda\Sigma_d\theta + G_{N, \lambda}^{-1}\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\eta_n
+\end{align*}
+
+\subsection{Proof of \autoref{lem:concentration}}
+
+\begin{proof}
+
+Let 
+\begin{equation*}
+    V_t = \sum_{s=1}^t X_s^\transp \Sigma_p^{-1} X_s \in \Real^{d\times d}
+\end{equation*}
+And for any $z\in\Real^d$,
+\begin{equation*}
+    M_t^z = \exp{\left(\inp{z}{S_t} - \frac{1}{2}\|z\|_{V_t}\right)}
+\end{equation*}
+\begin{equation*}
+    D_t^z = \exp{\left(\inp{X_t z}{\eta_t}_{\Sigma_p^{-1}} - \frac{1}{2}\|X_t z\|_{\Sigma_p^{-1}}\right)}
+\end{equation*}
+Then,
+\begin{align*}
+    M_t^z = \exp{\left(\sum_{s=1}^t z^\transp X_s^\transp \Sigma_p^{-1} \eta_s - \frac{1}{2} (X_s z)^\transp\Sigma_p^{-1}(X_s z) \right)} = \prod_{s=1}^{t} D_s^z
+\end{align*}
+and using the Sub-Gaussianity of $\eta_t$
+\begin{align*}
+    \expectedvalue\left[D_t^z \condbar F_{t-1}\right] &= \exp{\left(- \frac{1}{2}\|X_t z\|_{\Sigma_p^{-1}}\right)} \expectedvalue\left[\exp{\left(\inp{X_t z}{\eta_t}_{\Sigma_p^{-1}}\right)} \condbar F_{t-1}\right]  \\
+    &\leq \exp{\left(- \frac{1}{2}\|X_t z\|_{\Sigma_p^{-1}}\right)}\exp{\left((z^\transp X_t^\transp \Sigma_p^{-1})\Sigma_p(\Sigma_p^{-1} X_t z)\right)}\\
+    &= 1
+\end{align*}
+\begin{align*}
+    \expectedvalue\left[M_t^z \condbar F_{t-1}\right] = \left(\prod_{s=1}^{t-1} D_s^z\right) \expectedvalue\left[D_t^z \condbar F_{t-1}\right] \leq M_{t-1}^z
+\end{align*}
+
+\end{proof}
+
+\subsection{Proof of \autoref{thm:confidence_ellipsoid}}
+
+Hence, for all $x\in\Real^d$,
+\begin{align*}
+    x^\transp\theta_{N,\lambda}  -x^\transp\theta &= x^\transp G_{N, \lambda}^{-1}\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\eta_n
+    - \lambda x^\transp G_{N, \lambda}^{-1}\Sigma_d\theta\\
+    &= \inp{x}{\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\eta_n}_{G_{N, \lambda}^{-1}} - \lambda\inp{x}{\Sigma_d\theta}_{G_{N, \lambda}^{-1}}
+\end{align*}
+
+Using the Cauchy-Schwartz inequality, we get:
+\begin{align*}
+    |x^\transp\theta_{N,\lambda}  -x^\transp\theta| &\leq \|x\|_{G_{N, \lambda}^{-1}}\left(\left\|\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\eta_n\right\|_{G_{N, \lambda}^{-1}} + \lambda\|\Sigma_d\theta\|_{G_{N, \lambda}^{-1}}\right)
+\end{align*}
+
+\subsection{Proof of \autoref{lem:confidence_polytope}}
+
+\begin{proof}
+The ellipsoid in \eqref{eq:confidence-ellipsoid} is described by:
+\begin{align*}
+    \theta\in\cC_\delta &\implies
+    (\theta-\theta_{N,\lambda})^\transp G_{N,\lambda}^{-1}(\theta-\theta_{N,\lambda}) \leq C_{N,\lambda,\delta}\\
+    &\implies (\theta'-\theta'_{N,\lambda})^\transp D (\theta'-\theta'_{N,\lambda}) \leq C_{N,\lambda,\delta}\\
+    &\implies \sum_{i=1}^d D_{i,i}(\theta'_i-\theta'_{N,\lambda,i})^2\leq C_{N,\lambda,\delta}\\
+    &\implies\forall i, |\theta'_i-\theta'_{N,\lambda,i}|\leq C_{N,\lambda,\delta}^{1/2}D_{i,i}^{-1/2}
+\end{align*}
+This describes a $\Real^d$ box containing $\theta' = P\theta$, whose $k^\text{th}$ vertex is represented by $\theta_{N,\lambda}' + C_{N,\lambda,\delta}^{1/2}D^{-1/2} h_k$.
+We obtain the corresponding box on $\theta$ by transforming each vertex of the box with $P^{-1}$.
+\end{proof}
+
 \end{document}

### 2020-01-13 notes.tex
Updates from Overleaf

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{float}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage{caption}
\usepackage{blkarray}
\usepackage{todonotes}
\usepackage{mathtools}
\usepackage[backend=biber,style=authoryear,natbib=true,url=false]{biblatex}

\addbibresource{references.bib}

\input{mathdef.tex}

\title{Robust Estimation, Prediction and Control with Dynamics Structure}
\author{Edouard Leurent, Denis Efimov, Odalric-Ambrym Maillard}
\date{November 2019}

\begin{document}

\begin{assumption}[Noise Model]
\label{assumpt:noise}
At each time $t\geq0$ the measurement noise $\eta(t)$ and disturbance $\omega(t)$  are independent Gaussians with respective means $0_r, 0_s$ and covariances $\Sigma_r, \Sigma_s$:
\begin{equation*}
    \eta(t)\sim \cN(0_r,\Sigma_r),\quad\omega(t)\sim \cN(0_s,\Sigma_s)
\end{equation*}
We further require that the matrix $\Sigma_p = C\Sigma_r C^T + D\Sigma_s D^T \in \Real^{p\times p}$ is full-rank.
\end{assumption}

\begin{proposition}[Maximum Likelihood Estimate]
\label{prop:mle}
The maximum likelihood estimate for $\theta$ minimises a weighted mean square error:
\begin{equation*}
    \argmax_{\theta\in\Real^d} \probability{\cD\condbar\eqref{eq:dynamics};\Sigma} = \argmin_{\theta\in\Real^d} \sum_{n=1}^N \|y_n -\theta^T\phi x_n\|_{\Sigma_p^{-1}}^2
\end{equation*}

By rewriting $\Phi_n = [\cdots \phi_i x_n \cdots]\in\Real^{p\times d}$,
\begin{equation*}
    \argmax_{\theta\in\Real^d} \probability{\cD\condbar\eqref{eq:dynamics};\Sigma} = \argmin_{\theta\in\Real^d} \sum_{n=1}^N \|y_n -\Phi_n \theta\|_{\Sigma_p^{-1}}^2
\end{equation*}
\end{proposition}

\subsection{Scalar formulation}

We stack the observations $y_n, x_n$ in $\cD$, as $Y_{[N]}, X_{[N]}\in\Real^{N\times p}$ and the noises $C\eta(t_n)+D\omega(t_n)$ as $\Omega_{[N]} \in\Real^{N\times p}$ to obtain the regression problem:

\begin{equation}
    \label{eq:regression}
    Y_{[N]} = \Phi_{[N]} \theta + \Omega_{[N]},
\end{equation}
with $\Phi_{[N]} = X_{[N]}\phi^T\in \Real^{N\times p\times d}$.

\begin{proposition}[Decoupling the noise]
\label{prop:decoupling}
Without loss of generality, up to a change of basis, we can assume that $\Sigma_d$ is diagonal.
\end{proposition}

In order to solve the regression problem \eqref{eq:regression} can simply reshape the two first $N\times p$ dimensions into a single $Np$ dimension. Since $\Sigma_p$ is diagonal, the noises on each row of $\Omega$ are independent, the problem becomes a standard scalar regression problem with heteroscedastic noise (if $\Sigma_p$ is not proportional to $I_p$), and the Lemma 5 of \citet{kirschner18heteroscedastic} can be applied.

\begin{lemma}[Confidence ellipsoid \citep{kirschner18heteroscedastic}]
Assuming that $\Sigma_p$ is diagonal and $\|\theta\|_2\leq S$, it holds with probability $1-\delta$ that:
\begin{equation}
    \label{eq:confidence-ellipsoid}
    \|\theta - \theta_{Np,\lambda}\|_{G_{Np,\lambda}} \leq \sqrt{2\log \frac{\text{det}(G_{Np,\lambda})^{1/2}\text{det}(\lambda I)^{-1/2}}{\delta}} + \lambda^{1/2}S
\end{equation}
where
\begin{align*}
    \Phi_{[Np]}& \in\Real^{Np\times d},\, Y_{[Np]}\in \Real^{Np\times 1} \text{ are the reshaped versions of $\Phi_{[N]}$, $Y_{[N]}$};\\
    \tilde{\Phi}_{[Np]} &= [\underbrace{\cdots \Sigma_p^{-\frac{1}{2}} \cdots}_{\text{$N$ times}}]^T \Phi_{[Np]} , \qquad  \tilde{Y}_{[Np]} = [\underbrace{\cdots \Sigma_p^{-\frac{1}{2}} \cdots}_{\text{$N$ times}}]^TY_{[Np]};\\
    G_{Np, \lambda} &= \tilde{\Phi}^T_{[Np]}\tilde{\Phi}_{[Np]} + \lambda I_d;\\
    \theta_{Np,\lambda} &= G_{Np, \lambda}^{-1} \tilde{\Phi}^T_{[Np]}\tilde{Y}_{[Np]}.
\end{align*}
\end{lemma}

\section{Proofs}

\subsection{Proof of \autoref{prop:mle}}

\begin{proof}
For $n\in[N]$, at time $t_n$, we have
\begin{align*}
    \probability{y_n, x_n} 
    &= \probability{y_n|x_n}\probability{x_n}\\
    &= \probability{y_n = \dot{x}_n - Bu_n +C\eta_n|x_n,u_n}\probability{x_n}\\
    &= \probability{A(\theta)x_n + B u_n + D \omega_n - Bu_n +C\eta_n = y_n|x_n}\probability{x_n}\\
    &= \probability{C\eta_n + D \omega_n = y_n- \theta^T \phi x_n |x_n}\probability{x_n}\\
    &= \cN(y_n - \theta^T \phi x_n; 0_p,\Sigma_p)\probability{x_n}
\end{align*}
By independence of the noise at different times, we have:
\begin{align*}
    \log\probability{\cD;\Sigma} &= \log\prod_{n=1}^N\probability{y_n, x_n}\\
    &= \sum_{n=1}^N\log \cN(y_n- \theta^T \phi x_n;0_p,\Sigma_p) + \log\probability{x_n}\\
    &= \sum_{n=1}^N -\frac{1}{2} \|y_n -\theta^T\phi x_n\|_{\Sigma_p^{-1}}^2 - \log\left((2\pi)^{p/2} \det(\Sigma_p)^{1/2}\right) + \log\probability{x_n}
\end{align*}
\end{proof}

\subsection{Proof of \autoref{prop:decoupling}}

\begin{proof}
Since $\Sigma_p$ is a symmetric real matrix, it is diagonalisable: there exists $Q\in\cO(p)$ and a diagonal matrix $R$ such that $\Sigma_p = QRQ^{-1}$. Hence, from \eqref{eq:dynamics} and \eqref{eq:measurement}:
\begin{align*}
    Q^{-1}y'(t) &= \sum_{i=1}^d \theta_i Q^{-1}\phi_i x(t) + Q^{-1}(C\eta(t) + D\omega(t))
\end{align*}
By rewriting $y \leftarrow Q^{-1}y, \phi_i\leftarrow Q^{-1}\phi_i, C\leftarrow Q^{-1}C$, and $D\leftarrow Q^{-1}D$ we recover \eqref{eq:dynamics} and \eqref{eq:measurement} in their original form, while now having $C\Sigma_rC^T + D\Sigma_rD^T = R$.
\end{proof}

\end{document}

### 2020-01-13 main.tex
Updates from Overleaf

@@
 \begin{itemize}
-    \item We with to act in a reasonable (structure) but cautious (robust) way, and progressively get more and more aggressive as we obtain more data and reduce uncertainty.
+    \item We wish to act straight away in a reasonable (structure) but cautious (robust) way, and progressively get more and more aggressive as we obtain more data and reduce uncertainty.
     \item Thus, we do not wish to explore actively the more promising regions as in OFU, nor the more likely region as in TS, nor act randomly as in Coarse-ID.
-    \item We have linear dynamics but our cost is not quadratic (to accurately represent planning task with discrete/branching decisions: e.g. take or give way)
-    \item Our optimisation problem amounts to discrete controller selection, instead of continuous controller synthesis
+    \item We have linear dynamics but our cost is not quadratic.
+Thus, we can accurately represent planning tasks with discrete/branching decisions involving discontinuities (e.g.
+collision vs non-collision states).
+    \item Our optimisation problem amounts to a sequence of controllers selection, instead of continuous controller synthesis
 
@@
 \end{align*}
+This conversion is illustrated in \autoref{fig:ellipsoid_to_polytope}
 \end{lemma}
@@
     \centering
-    \includegraphics[trim={3.8cm, 2cm, 5cm, 3.8cm}, clip, width=0.6\textwidth]{img/ellipsoid_to_polytope}
+    \includegraphics[trim={3.8cm, 2cm, 5cm, 3.8cm}, clip, width=0.4\textwidth]{img/ellipsoid_to_polytope}
     \caption{From the confidence ellipsoid $\cC_\delta$ to its enclosing polytope $\cP_\delta$}
@@
 Then, 
-\[
-\|\theta_{N,\lambda} - \theta\|_1 \leq \|G_{N, \lambda}^{-1}\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\|_1\|\eta\|_\infty + \lambda\|G_{N, \lambda}^{-1}\Sigma_d\theta\|_1
-\]
+\begin{align*}
+\|\theta_{N,\lambda} - \theta\|_1 &\leq \|G_{N, \lambda}^{-1}\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\|_1\|\eta\|_\infty + \lambda\|G_{N, \lambda}^{-1}\Sigma_d\theta\|_1\\
+&\leq \|G_{N, \lambda}^{-1}\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\|_1\|\eta\|_\infty + \lambda\|G_{N, \lambda}^{-1}\Sigma_d\|_1\|\theta\|_\infty
+\end{align*}
 
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{img/interval-hull}
+    \includegraphics[width=0.3\textwidth]{img/interval-hull}
     \caption{A few trajectories are sampled from an initial state $x_0$ following a policy $\pi=(u_0,\cdots)$ with various parameters $\theta$ (in black).
@@
   \SetKwFunction{algo}{robust\_control}
-  \SetKwFunction{proc}{pessimistic\_reward}
+  \SetKwFunction{proc}{pessimistic\_step}
   \SetKwProg{myalg}{Algorithm}{}{}
@@
   {
-  Generate a candidate sequence $\pi$ with a planning algorithm using \proc{} instead of the true rewards.
+  Select a candidate action sequence $a$ with a planning algorithm.\;
+  Sample a pessimistic transition and reward $\underline{r}_t$ using \proc{$\underline{x}(t)$, $\overline{x}(t)$, a}.
+ \;
+ Update the planning algorithm with the sampled pessimistic transition.
   }
@@
   \SetKwProg{myproc}{Procedure}{}{}
-  \myproc{\proc{$s_0$, $\pi$, T}}{
-  Integrate \eqref{eq:interval_predictor} over $[0,t]$ with commands $\pi$ to compute $[\underline{x}(t), \overline{x}(t)]$\;
-  \KwRet $\min_{x\in[\underline{x}(t), \overline{x}(t)]} r(x)$\;}
+  \myproc{\proc{$\underline{x}(t)$, $\overline{x}(t)$, $a$}}{
+  Integrate \eqref{eq:interval_predictor} over $dt$ with controls $a$ to compute $\underline{x}(t+dt), \overline{x}(t+dt)$\;
+  Compute worst-case reward $\underline{r}_t = \min_{x\in[\underline{x}(t), \overline{x}(t)]} r(x)$\;
+  \KwRet $\underline{x}(t+dt), \overline{x}(t+dt), \underline{r}_t$\;}
 \caption{Interval-based Robust Control}
@@
 \end{property}
-
-\begin{proof}
-Let $\theta\in\Theta$, by \autoref{thm:confidence_interval} we have that $A(\theta) \in \cP$ with probability $1-\delta$.
-Whenever it is the case, we have by \autoref{thm:predictor} that the inclusion property \eqref{eq:interval_property} is verified by the interval predictor \eqref{eq:interval_predictor} for all $\omega(t)\in[\underline{\omega}(t), \overline{\omega}(t)]$.
-This gives the following bound:
-\begin{equation*}
- \sum_{t=0}^\infty \gamma^t r(x_t) \geq \sum_{t=0}^\infty \min_{x\in[\underline{x}(t, \pi), \overline{x}(t, \pi)]} \gamma^t r(x) = \hat{v^r}(\pi)
-\end{equation*}
-
-And finally, with probability $1-\delta$,
-\begin{align*}
-v^r(\pi) &= \min_{A(\theta) \in A(\Theta)} \expectedvalueover{\omega(t)}\left[\sum_{t=0}^\infty \gamma^t r(x_t)\right] \\
-&\geq \min_{A \in \cP} \expectedvalueover{\omega(t)}\left[\sum_{t=0}^\infty \gamma^t r(x_t)\right] \\
-& \geq \min_{A \in \cP} \expectedvalueover{\omega(t)}\left[\hat{v^r}(\pi)\right] = \hat{v^r}(\pi)
-\end{align*}
-\end{proof}
 
@@
 \centering
-\includegraphics[width=0.5\linewidth]{img/robust-control-tree}
+\includegraphics[width=0.3\linewidth]{img/robust-control-tree}
 \caption{The computation of robust b-values in Algorithm \ref{algo:drop}.
@@
 Initialize $\mathcal{T}$ to a root and expand it. Set $n=1$.\;
-\While{Numerical resource available}{
-Compute the robust u-values $u^r_i(n)$ and robust b-values $b^r_i(n)$.\;
-Expand $\argmax_{i\in \mathcal{L}_n} b^r_i(n)$.\;
-n = n + 1\;
+\While{Numerical resource available for episode $n$}{
+Compute the robust b-values $b^r_i(n)$.\;
+Expand the leaf $\argmax_{i\in \mathcal{L}_n} b^r_i(n)$.\;
 }
@@
 
+\subsection{Proof of \autoref{prop:lower-bound}}
+
+\begin{proof}
+We have that $A(\theta) \in \cP$ with probability $1-\delta$.
+Whenever it is the case, we have by \autoref{thm:predictor} that the inclusion property \eqref{eq:interval_property} is verified by the interval predictor \eqref{eq:interval_predictor} for all $\omega(t)\in[\underline{\omega}(t), \overline{\omega}(t)]$.
+This gives the following bound:
+\begin{equation*}
+ \sum_{t=0}^\infty \gamma^t r(x_t) \geq \sum_{t=0}^\infty \min_{x\in[\underline{x}(t, \pi), \overline{x}(t, \pi)]} \gamma^t r(x) = \hat{v^r}(\pi)
+\end{equation*}
+
+And finally, with probability $1-\delta$,
+\begin{align*}
+v^r(\pi) &= \min_{A(\theta) \in A(\Theta)} \expectedvalueover{\omega(t)}\left[\sum_{t=0}^\infty \gamma^t r(x_t)\right] \\
+&\geq \min_{A \in \cP} \expectedvalueover{\omega(t)}\left[\sum_{t=0}^\infty \gamma^t r(x_t)\right] \\
+& \geq \min_{A \in \cP} \expectedvalueover{\omega(t)}\left[\hat{v^r}(\pi)\right] = \hat{v^r}(\pi)
+\end{align*}
+\end{proof}
+
 \end{document}

### 2020-01-13 main.tex
Add ICML template

@@
+%%%%%%%% ICML 2020 EXAMPLE LATEX SUBMISSION FILE %%%%%%%%%%%%%%%%%
+
 \documentclass{article}
-\usepackage[cm]{fullpage}
 
-\usepackage[utf8]{inputenc}
+% Recommended, but optional, packages for figures and better typesetting:
+\usepackage{microtype}
 \usepackage{graphicx}
+\usepackage{subfigure}
+\usepackage{booktabs} % for professional tables
+
+% hyperref makes hyperlinks in the resulting PDF.
+% If your build breaks (sometimes temporarily if a hyperlink spans a page)
+% please comment out the following usepackage line and replace
+% \usepackage{icml2020} with \usepackage[nohyperref]{icml2020} above.
+\usepackage{hyperref}
+
+% Attempt to make hyperref and algorithmic work together better:
+\newcommand{\theHalgorithm}{\arabic{algorithm}}
+
+% Use the following line for the initial blind version submitted for review:
+\usepackage{icml2020}
+
+% If accepted, instead use the following line for the camera-ready submission:
+%\usepackage[accepted]{icml2020}
+
+% The \icmltitle you define below is probably too long as a header.
+% Therefore, a short form for the running title is supplied here:
+%\icmltitlerunning{Submission and Formatting Instructions for ICML 2020}
+
+% Custom packages
 \usepackage{amsthm}
@@
 \usepackage{hyperref}
-\usepackage{booktabs}
-\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
-\usepackage{caption}
 \usepackage{blkarray}
@@
 \usepackage{mathtools}
-\usepackage[backend=biber,style=authoryear,natbib=true,url=false]{biblatex}
-
-\addbibresource{references.bib}
 
@@
 
-\title{Robust Estimation, Prediction and Control with Dynamics Structure}
-\author{Edouard Leurent, Denis Efimov, Odalric-Ambrym Maillard}
-\date{November 2019}
+%\author{Edouard Leurent, Denis Efimov, Odalric-Ambrym Maillard}
 
@@
 
-\maketitle
+	\twocolumn[
+	\icmltitle{Robust Estimation, Prediction and Control with \\ Continuous States and Dynamics Structure}
+
+	% It is OKAY to include author information, even for blind
+	% submissions: the style file will automatically remove it for you
+	% unless you've provided the [accepted] option to the icml2020
+	% package.
+
+	% List of affiliations: The first argument should be a (short)
+	% identifier you will use later to specify author affiliations
+	% Academic affiliations should list Department, University, City, Region, Country
+	% Industry affiliations should list Company, City, Region, Country
+
+	% You can specify symbols, otherwise they are numbered in order.
+	% Ideally, you should not use this facility. Affiliations will be numbered
+	% in order of appearance and this is the preferred way.
+	\icmlsetsymbol{equal}{*}
+
+	\begin{icmlauthorlist}
+		\icmlauthor{Edouard Leurent}{seq,val,ren}
+		\icmlauthor{Denis Efimov}{val}
+		\icmlauthor{Odalric Ambrym-Maillard}{seq}
+	\end{icmlauthorlist}
+
+	\icmlaffiliation{seq}{Inria Lille Nord-Europe, Sequel Project, Lille, France}
+	\icmlaffiliation{val}{Inria Lille Nord-Europe, Valse Project, Lille, France}
+	\icmlaffiliation{ren}{Renault Group, Guyancourt, France}
+
+	\icmlcorrespondingauthor{Edouard Leurent}{edouard.leurent@inria.fr}
+
+	% You may provide any keywords that you
+	% find helpful for describing your paper; these are used to populate
+	% the "keywords" metadata in the PDF but will not be shown in the document
+	\icmlkeywords{Machine Learning, ICML}
+
+	\vskip 0.3in
+	]
+
+	% this must go after the closing bracket ] following \twocolumn[ ...
+
+	% This command actually creates the footnote in the first column
+	% listing the affiliations and the copyright notice.
+	% The command takes one argument, which is text to display at the start of the footnote.
+	% The \icmlEqualContribution command is standard text for equal contribution.
+	% Remove it (just {}) if you do not need this facility.
+
+	\printAffiliationsAndNotice{}  % leave blank if no need to mention equal contribution
+%	\printAffiliationsAndNotice{\icmlEqualContribution} % otherwise use the standard text.
+
+	\begin{abstract}
+		This document provides a basic paper template and submission guidelines.
+		Abstracts must be a single paragraph, ideally between 4--6 sentences long.
+		Gross violations will trigger corrections at the camera-ready phase.
+	\end{abstract}
+
+\section{Introduction}
 
@@
 
-\begin{algorithm}[tp]
-  \SetAlgoLined\DontPrintSemicolon
-  \SetKwFunction{algo}{robust\_control}
-  \SetKwFunction{proc}{pessimistic\_step}
-  \SetKwProg{myalg}{Algorithm}{}{}
-  \myalg{\algo{$s_0$}}{
-  \While{resources available}
-  {
-  Select a candidate action sequence $a$ with a planning algorithm.\;
-  Sample a pessimistic transition and reward $\underline{r}_t$ using \proc{$\underline{x}(t)$, $\overline{x}(t)$, a}.
- \;
- Update the planning algorithm with the sampled pessimistic transition.
-  }
-  \KwRet $\argmax_{\pi\in\Pi} \hat{v^r}(\pi)$ \;}{}
-  \setcounter{AlgoLine}{0}
-  \SetKwProg{myproc}{Procedure}{}{}
-  \myproc{\proc{$\underline{x}(t)$, $\overline{x}(t)$, $a$}}{
-  Integrate \eqref{eq:interval_predictor} over $dt$ with controls $a$ to compute $\underline{x}(t+dt), \overline{x}(t+dt)$\;
-  Compute worst-case reward $\underline{r}_t = \min_{x\in[\underline{x}(t), \overline{x}(t)]} r(x)$\;
-  \KwRet $\underline{x}(t+dt), \overline{x}(t+dt), \underline{r}_t$\;}
-\caption{Interval-based Robust Control}
-\label{algo:irc}
-
-\end{algorithm}
+%\begin{algorithm}[tp]
+%  \SetAlgoLined\DontPrintSemicolon
+%  \SetKwFunction{algo}{robust\_control}
+%  \SetKwFunction{proc}{pessimistic\_step}
+%  \SetKwProg{myalg}{Algorithm}{}{}
+%  \myalg{\algo{$s_0$}}{
+%  \While{resources available}
+%  {
+%  Select a candidate action sequence $a$ with a planning algorithm.\;
+%  Sample a pessimistic transition and reward $\underline{r}_t$ using \proc{$\underline{x}(t)$, $\overline{x}(t)$, a}.
+% \;
+% Update the planning algorithm with the sampled pessimistic transition.
+%  }
+%  \KwRet $\argmax_{\pi\in\Pi} \hat{v^r}(\pi)$ \;}{}
+%  \setcounter{AlgoLine}{0}
+%  \SetKwProg{myproc}{Procedure}{}{}
+%  \myproc{\proc{$\underline{x}(t)$, $\overline{x}(t)$, $a$}}{
+%  Integrate \eqref{eq:interval_predictor} over $dt$ with controls $a$ to compute $\underline{x}(t+dt), \overline{x}(t+dt)$\;
+%  Compute worst-case reward $\underline{r}_t = \min_{x\in[\underline{x}(t), \overline{x}(t)]} r(x)$\;
+%  \KwRet $\underline{x}(t+dt), \overline{x}(t+dt), \underline{r}_t$\;}
+%\caption{Interval-based Robust Control}
+%\label{algo:irc}
+%
+%\end{algorithm}
 
@@
 
-\begin{algorithm}[tp]
-\DontPrintSemicolon
-Initialize $\mathcal{T}$ to a root and expand it. Set $n=1$.\;
-\While{Numerical resource available for episode $n$}{
-Compute the robust b-values $b^r_i(n)$.\;
-Expand the leaf $\argmax_{i\in \mathcal{L}_n} b^r_i(n)$.\;
-}
-\Return $\argmax_{a\in \mathcal{A}} u^r_a(n)$
-\caption{Deterministic Robust Optimistic Planning}
-\label{algo:drop}
-\end{algorithm}
+%\begin{algorithm}[tp]
+%\DontPrintSemicolon
+%Initialize $\mathcal{T}$ to a root and expand it. Set $n=1$.\;
+%\While{Numerical resource available for episode $n$}{
+%Compute the robust b-values $b^r_i(n)$.\;
+%Expand the leaf $\argmax_{i\in \mathcal{L}_n} b^r_i(n)$.\;
+%}
+%\Return $\argmax_{a\in \mathcal{A}} u^r_a(n)$
+%\caption{Deterministic Robust Optimistic Planning}
+%\label{algo:drop}
+%\end{algorithm}
 
@@
 
-\printbibliography
+\bibliography{references}
+\bibliographystyle{icml2020}
 

### 2020-01-14 example_paper.tex
Updates from Overleaf

%%%%%%%% ICML 2020 EXAMPLE LATEX SUBMISSION FILE %%%%%%%%%%%%%%%%%

\documentclass{article}

\usepackage{amsmath}

% Recommended, but optional, packages for figures and better typesetting:
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{booktabs} % for professional tables

% hyperref makes hyperlinks in the resulting PDF.
% If your build breaks (sometimes temporarily if a hyperlink spans a page)
% please comment out the following usepackage line and replace
% \usepackage{icml2020} with \usepackage[nohyperref]{icml2020} above.
\usepackage{hyperref}

% Attempt to make hyperref and algorithmic work together better:
\newcommand{\theHalgorithm}{\arabic{algorithm}}

% Use the following line for the initial blind version submitted for review:
\usepackage{icml2020}

% If accepted, instead use the following line for the camera-ready submission:
%\usepackage[accepted]{icml2020}

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{Submission and Formatting Instructions for ICML 2020}

\begin{document}

\twocolumn[
\icmltitle{Submission and Formatting Instructions for \\
           International Conference on Machine Learning (ICML 2020)}

% It is OKAY to include author information, even for blind
% submissions: the style file will automatically remove it for you
% unless you've provided the [accepted] option to the icml2020
% package.

% List of affiliations: The first argument should be a (short)
% identifier you will use later to specify author affiliations
% Academic affiliations should list Department, University, City, Region, Country
% Industry affiliations should list Company, City, Region, Country

% You can specify symbols, otherwise they are numbered in order.
% Ideally, you should not use this facility. Affiliations will be numbered
% in order of appearance and this is the preferred way.
\icmlsetsymbol{equal}{*}

\begin{icmlauthorlist}
\icmlauthor{Aeiau Zzzz}{equal,to}
\icmlauthor{Bauiu C.~Yyyy}{equal,to,goo}
\icmlauthor{Cieua Vvvvv}{goo}
\icmlauthor{Iaesut Saoeu}{ed}
\icmlauthor{Fiuea Rrrr}{to}
\icmlauthor{Tateu H.~Yasehe}{ed,to,goo}
\icmlauthor{Aaoeu Iasoh}{goo}
\icmlauthor{Buiui Eueu}{ed}
\icmlauthor{Aeuia Zzzz}{ed}
\icmlauthor{Bieea C.~Yyyy}{to,goo}
\icmlauthor{Teoau Xxxx}{ed}
\icmlauthor{Eee Pppp}{ed}
\end{icmlauthorlist}

\icmlaffiliation{to}{Department of Computation, University of Torontoland, Torontoland, Canada}
\icmlaffiliation{goo}{Googol ShallowMind, New London, Michigan, USA}
\icmlaffiliation{ed}{School of Computation, University of Edenborrow, Edenborrow, United Kingdom}

\icmlcorrespondingauthor{Cieua Vvvvv}{c.vvvvv@googol.com}
\icmlcorrespondingauthor{Eee Pppp}{ep@eden.co.uk}

% You may provide any keywords that you
% find helpful for describing your paper; these are used to populate
% the "keywords" metadata in the PDF but will not be shown in the document
\icmlkeywords{Machine Learning, ICML}

\vskip 0.3in
]

% this must go after the closing bracket ] following \twocolumn[ ...

% This command actually creates the footnote in the first column
% listing the affiliations and the copyright notice.
% The command takes one argument, which is text to display at the start of the footnote.
% The \icmlEqualContribution command is standard text for equal contribution.
% Remove it (just {}) if you do not need this facility.

%\printAffiliationsAndNotice{}  % leave blank if no need to mention equal contribution
\printAffiliationsAndNotice{\icmlEqualContribution} % otherwise use the standard text.

\begin{abstract}
This document provides a basic paper template and submission guidelines.
Abstracts must be a single paragraph, ideally between 4--6 sentences long.
Gross violations will trigger corrections at the camera-ready phase.
\end{abstract}

\section{Electronic Submission}
\label{submission}

Submission to ICML 2020 will be entirely electronic, via a web site
(not email). Information about the submission process and \LaTeX\ templates
are available on the conference web site at:
\begin{center}
\textbf{\texttt{http://icml.cc/}}
\end{center}

The guidelines below will be enforced for initial submissions and
camera-ready copies. Here is a brief summary:
\begin{itemize}
\item Submissions must be in PDF\@.
\item Submitted papers can be up to eight pages long, not including references, plus unlimited space for references. Accepted papers can be up to nine pages long, not including references, to allow authors to address reviewer comments. Any paper exceeding this length will automatically be rejected. 
\item \textbf{Do not include author information or acknowledgements} in your
    initial submission.
\item Your paper should be in \textbf{10 point Times font}.
\item Make sure your PDF file only uses Type-1 fonts.
\item Place figure captions \emph{under} the figure (and omit titles from inside
    the graphic file itself). Place table captions \emph{over} the table.
\item References must include page numbers whenever possible and be as complete
    as possible. Place multiple citations in chronological order.
\item Do not alter the style template; in particular, do not compress the paper
    format by reducing the vertical spaces.
\item Keep your abstract brief and self-contained, one paragraph and roughly
    4--6 sentences. Gross violations will require correction at the
    camera-ready phase. The title should have content words capitalized.
\end{itemize}

\subsection{Submitting Papers}

\textbf{Paper Deadline:} The deadline for paper submission that is
advertised on the conference website is strict. If your full,
anonymized, submission does not reach us on time, it will not be
considered for publication.

\textbf{Anonymous Submission:} ICML uses double-blind review: no identifying
author information may appear on the title page or in the paper
itself. Section~\ref{author info} gives further details.

\textbf{Simultaneous Submission:} ICML will not accept any paper which,
at the time of submission, is under review for another conference or
has already been published. This policy also applies to papers that
overlap substantially in technical content with conference papers
under review or previously published. ICML submissions must not be
submitted to other conferences during ICML's review period. Authors
may submit to ICML substantially different versions of journal papers
that are currently under review by the journal, but not yet accepted
at the time of submission. Informal publications, such as technical
reports or papers in workshop proceedings which do not appear in
print, do not fall under these restrictions.

\medskip

Authors must provide their manuscripts in \textbf{PDF} format.
Furthermore, please make sure that files contain only embedded Type-1 fonts
(e.g.,~using the program \texttt{pdffonts} in linux or using
File/DocumentProperties/Fonts in Acrobat). Other fonts (like Type-3)
might come from graphics files imported into the document.

Authors using \textbf{Word} must convert their document to PDF\@. Most
of the latest versions of Word have the facility to do this
automatically. Submissions will not be accepted in Word format or any
format other than PDF\@. Really. We're not joking. Don't send Word.

Those who use \textbf{\LaTeX} should avoid including Type-3 fonts.
Those using \texttt{latex} and \texttt{dvips} may need the following
two commands:

{\footnotesize
\begin{verbatim}
dvips -Ppdf -tletter -G0 -o paper.ps paper.dvi
ps2pdf paper.ps
\end{verbatim}}
It is a zero following the ``-G'', which tells dvips to use
the config.pdf file. Newer \TeX\ distributions don't always need this
option.

Using \texttt{pdflatex} rather than \texttt{latex}, often gives better
results. This program avoids the Type-3 font problem, and supports more
advanced features in the \texttt{microtype} package.

\textbf{Graphics files} should be a reasonable size, and included from
an appropriate format. Use vector formats (.eps/.pdf) for plots,
lossless bitmap formats (.png) for raster graphics with sharp lines, and
jpeg for photo-like images.

The style file uses the \texttt{hyperref} package to make clickable
links in documents. If this causes problems for you, add
\texttt{nohyperref} as one of the options to the \texttt{icml2020}
usepackage statement.

\subsection{Submitting Final Camera-Ready Copy}

The final versions of papers accepted for publication should follow the
same format and naming convention as initial submissions, except that
author information (names and affiliations) should be given. See
Section~\ref{final author} for formatting instructions.

The footnote, ``Preliminary work. Under review by the International
Conference on Machine Learning (ICML). Do not distribute.'' must be
modified to ``\textit{Proceedings of the
$\mathit{37}^{th}$ International Conference on Machine Learning},
Vienna, Austria, 2020.
Copyright 2020 by the author(s).''

For those using the \textbf{\LaTeX} style file, this change (and others) is
handled automatically by simply changing
$\mathtt{\backslash usepackage\{icml2020\}}$ to
$$\mathtt{\backslash usepackage[accepted]\{icml2020\}}$$
Authors using \textbf{Word} must edit the
footnote on the first page of the document themselves.

Camera-ready copies should have the title of the paper as running head
on each page except the first one. The running title consists of a
single line centered above a horizontal rule which is $1$~point thick.
The running head should be centered, bold and in $9$~point type. The
rule should be $10$~points above the main text. For those using the
\textbf{\LaTeX} style file, the original title is automatically set as running
head using the \texttt{fancyhdr} package which is included in the ICML
2020 style file package. In case that the original title exceeds the
size restrictions, a shorter form can be supplied by using

\verb|\icmltitlerunning{...}|

just before $\mathtt{\backslash begin\{document\}}$.
Authors using \textbf{Word} must edit the header of the document themselves.

\section{Format of the Paper}

All submissions must follow the specified format.

\subsection{Dimensions}

The text of the paper should be formatted in two columns, with an
overall width of 6.75~inches, height of 9.0~inches, and 0.25~inches
between the columns. The left margin should be 0.75~inches and the top
margin 1.0~inch (2.54~cm). The right and bottom margins will depend on
whether you print on US letter or A4 paper, but all final versions
must be produced for US letter size.

The paper body should be set in 10~point type with a vertical spacing
of 11~points. Please use Times typeface throughout the text.

\subsection{Title}

The paper title should be set in 14~point bold type and centered
between two horizontal rules that are 1~point thick, with 1.0~inch
between the top rule and the top edge of the page. Capitalize the
first letter of content words and put the rest of the title in lower
case.

\subsection{Author Information for Submission}
\label{author info}

ICML uses double-blind review, so author information must not appear. If
you are using \LaTeX\/ and the \texttt{icml2020.sty} file, use
\verb+\icmlauthor{...}+ to specify authors and \verb+\icmlaffiliation{...}+ to specify affiliations. (Read the TeX code used to produce this document for an example usage.) The author information
will not be printed unless \texttt{accepted} is passed as an argument to the
style file.
Submissions that include the author information will not
be reviewed.

\subsubsection{Self-Citations}

If you are citing published papers for which you are an author, refer
to yourself in the third person. In particular, do not use phrases
that reveal your identity (e.g., ``in previous work \cite{langley00}, we
have shown \ldots'').

Do not anonymize citations in the reference section. The only exception are manuscripts that are
not yet published (e.g., under submission). If you choose to refer to
such unpublished manuscripts \cite{anonymous}, anonymized copies have
to be submitted
as Supplementary Material via CMT\@. However, keep in mind that an ICML
paper should be self contained and should contain sufficient detail
for the reviewers to evaluate the work. In particular, reviewers are
not required to look at the Supplementary Material when writing their
review.

\subsubsection{Camera-Ready Author Information}
\label{final author}

If a paper is accepted, a final camera-ready copy must be prepared.
%
For camera-ready papers, author information should start 0.3~inches below the
bottom rule surrounding the title. The authors' names should appear in 10~point
bold type, in a row, separated by white space, and centered. Author names should
not be broken across lines. Unbolded superscripted numbers, starting 1, should
be used to refer to affiliations.

Affiliations should be numbered in the order of appearance. A single footnote
block of text should be used to list all the affiliations. (Academic
affiliations should list Department, University, City, State/Region, Country.
Similarly for industrial affiliations.)

Each distinct affiliations should be listed once. If an author has multiple
affiliations, multiple superscripts should be placed after the name, separated
by thin spaces. If the authors would like to highlight equal contribution by
multiple first authors, those authors should have an asterisk placed after their
name in superscript, and the term ``\textsuperscript{*}Equal contribution"
should be placed in the footnote block ahead of the list of affiliations. A
list of corresponding authors and their emails (in the format Full Name
\textless{}email@domain.com\textgreater{}) can follow the list of affiliations.
Ideally only one or two names should be listed.

A sample file with author names is included in the ICML2020 style file
package. Turn on the \texttt{[accepted]} option to the stylefile to
see the names rendered. All of the guidelines above are implemented
by the \LaTeX\ style file.

\subsection{Abstract}

The paper abstract should begin in the left column, 0.4~inches below the final
address. The heading `Abstract' should be centered, bold, and in 11~point type.
The abstract body should use 10~point type, with a vertical spacing of
11~points, and should be indented 0.25~inches more than normal on left-hand and
right-hand margins. Insert 0.4~inches of blank space after the body. Keep your
abstract brief and self-contained, limiting it to one paragraph and roughly 4--6
sentences. Gross violations will require correction at the camera-ready phase.

\subsection{Partitioning the Text}

You should organize your paper into sections and paragraphs to help
readers place a structure on the material and understand its
contributions.

\subsubsection{Sections and Subsections}

Section headings should be numbered, flush left, and set in 11~pt bold
type with the content words capitalized. Leave 0.25~inches of space
before the heading and 0.15~inches after the heading.

Similarly, subsection headings should be numbered, flush left, and set
in 10~pt bold type with the content words capitalized. Leave
0.2~inches of space before the heading and 0.13~inches afterward.

Finally, subsubsection headings should be numbered, flush left, and
set in 10~pt small caps with the content words capitalized. Leave
0.18~inches of space before the heading and 0.1~inches after the
heading.

Please use no more than three levels of headings.

\subsubsection{Paragraphs and Footnotes}

Within each section or subsection, you should further partition the
paper into paragraphs. Do not indent the first line of a given
paragraph, but insert a blank line between succeeding ones.

You can use footnotes\footnote{Footnotes
should be complete sentences.} to provide readers with additional
information about a topic without interrupting the flow of the paper.
Indicate footnotes with a number in the text where the point is most
relevant. Place the footnote in 9~point type at the bottom of the
column in which it appears. Precede the first footnote in a column
with a horizontal rule of 0.8~inches.\footnote{Multiple footnotes can
appear in each column, in the same order as they appear in the text,
but spread them across columns and pages if possible.}

\begin{figure}[ht]
\vskip 0.2in
\begin{center}
\centerline{\includegraphics[width=\columnwidth]{icml_numpapers}}
\caption{Historical locations and number of accepted papers for International
Machine Learning Conferences (ICML 1993 -- ICML 2008) and International
Workshops on Machine Learning (ML 1988 -- ML 1992). At the time this figure was
produced, the number of accepted papers for ICML 2008 was unknown and instead
estimated.}
\label{icml-historical}
\end{center}
\vskip -0.2in
\end{figure}

\subsection{Figures}

You may want to include figures in the paper to illustrate
your approach and results. Such artwork should be centered,
legible, and separated from the text. Lines should be dark and at
least 0.5~points thick for purposes of reproduction, and text should
not appear on a gray background.

Label all distinct components of each figure. If the figure takes the
form of a graph, then give a name for each axis and include a legend
that briefly describes each curve. Do not include a title inside the
figure; instead, the caption should serve this function.

Number figures sequentially, placing the figure number and caption
\emph{after} the graphics, with at least 0.1~inches of space before
the caption and 0.1~inches after it, as in
Figure~\ref{icml-historical}. The figure caption should be set in
9~point type and centered unless it runs two or more lines, in which
case it should be flush left. You may float figures to the top or
bottom of a column, and you may set wide figures across both columns
(use the environment \texttt{figure*} in \LaTeX). Always place
two-column figures at the top or bottom of the page.

\subsection{Algorithms}

If you are using \LaTeX, please use the ``algorithm'' and ``algorithmic''
environments to format pseudocode. These require
the corresponding stylefiles, algorithm.sty and
algorithmic.sty, which are supplied with this package.
Algorithm~\ref{alg:example} shows an example.

\begin{algorithm}[tb]
   \caption{Bubble Sort}
   \label{alg:example}
\begin{algorithmic}
   \STATE {\bfseries Input:} data $x_i$, size $m$
   \REPEAT
   \STATE Initialize $noChange = true$.
   \FOR{$i=1$ {\bfseries to} $m-1$}
   \IF{$x_i > x_{i+1}$}
   \STATE Swap $x_i$ and $x_{i+1}$
   \STATE $noChange = false$
   \ENDIF
   \ENDFOR
   \UNTIL{$noChange$ is $true$}
\end{algorithmic}
\end{algorithm}

\subsection{Tables}

You may also want to include tables that summarize material. Like
figures, these should be centered, legible, and numbered consecutively.
However, place the title \emph{above} the table with at least
0.1~inches of space before the title and the same after it, as in
Table~\ref{sample-table}. The table title should be set in 9~point
type and centered unless it runs two or more lines, in which case it
should be flush left.

% Note use of \abovespace and \belowspace to get reasonable spacing
% above and below tabular lines.

\begin{table}[t]
\caption{Classification accuracies for naive Bayes and flexible
Bayes on various data sets.}
\label{sample-table}
\vskip 0.15in
\begin{center}
\begin{small}
\begin{sc}
\begin{tabular}{lcccr}
\toprule
Data set & Naive & Flexible & Better? \\
\midrule
Breast    & 95.9$\pm$ 0.2& 96.7$\pm$ 0.2& $\surd$ \\
Cleveland & 83.3$\pm$ 0.6& 80.0$\pm$ 0.6& $\times$\\
Glass2    & 61.9$\pm$ 1.4& 83.8$\pm$ 0.7& $\surd$ \\
Credit    & 74.8$\pm$ 0.5& 78.3$\pm$ 0.6&         \\
Horse     & 73.3$\pm$ 0.9& 69.7$\pm$ 1.0& $\times$\\
Meta      & 67.1$\pm$ 0.6& 76.5$\pm$ 0.5& $\surd$ \\
Pima      & 75.1$\pm$ 0.6& 73.9$\pm$ 0.5&         \\
Vehicle   & 44.9$\pm$ 0.6& 61.5$\pm$ 0.4& $\surd$ \\
\bottomrule
\end{tabular}
\end{sc}
\end{small}
\end{center}
\vskip -0.1in
\end{table}

Tables contain textual material, whereas figures contain graphical material.
Specify the contents of each row and column in the table's topmost
row. Again, you may float tables to a column's top or bottom, and set
wide tables across both columns. Place two-column tables at the
top or bottom of the page.

\begin{equation}
    2+2=4
    \label{eq:trivial}
\end{equation}

See equation \eqref{eq:trivial}.

\subsection{Citations and References}

Please use APA reference format regardless of your formatter
or word processor. If you rely on the \LaTeX\/ bibliographic
facility, use \texttt{natbib.sty} and \texttt{icml2020.bst}
included in the style-file package to obtain this format.

Citations within the text should include the authors' last names and
year. If the authors' names are included in the sentence, place only
the year in parentheses, for example when referencing Arthur Samuel's
pioneering work \yrcite{Samuel59}. Otherwise place the entire
reference in parentheses with the authors and year separated by a
comma \cite{Samuel59}. List multiple references separated by
semicolons \cite{kearns89,Samuel59,mitchell80}. Use the `et~al.'
construct only for citations with three or more authors or after
listing all authors to a publication in an earlier reference \cite{MachineLearningI}.

Authors should cite their own work in the third person
in the initial version of their paper submitted for blind review.
Please refer to Section~\ref{author info} for detailed instructions on how to
cite your own papers.

Use an unnumbered first-level section heading for the references, and use a
hanging indent style, with the first line of the reference flush against the
left margin and subsequent lines indented by 10 points. The references at the
end of this document give examples for journal articles \cite{Samuel59},
conference publications \cite{langley00}, book chapters \cite{Newell81}, books
\cite{DudaHart2nd}, edited volumes \cite{MachineLearningI}, technical reports
\cite{mitchell80}, and dissertations \cite{kearns89}.

Alphabetize references by the surnames of the first authors, with
single author entries preceding multiple author entries. Order
references for the same authors by year of publication, with the
earliest first. Make sure that each reference includes all relevant
information (e.g., page numbers).

Please put some effort into making references complete, presentable, and
consistent. If using bibtex, please protect capital letters of names and
abbreviations in titles, for example, use \{B\}ayesian or \{L\}ipschitz
in your .bib file.

\section*{Software and Data}

If a paper is accepted, we strongly encourage the publication of software and data with the
camera-ready version of the paper whenever appropriate. This can be
done by including a URL in the camera-ready copy. However, \textbf{do not}
include URLs that reveal your institution or identity in your
submission for review. Instead, provide an anonymous URL or upload
the material as ``Supplementary Material'' into the CMT reviewing
system. Note that reviewers are not required to look at this material
when writing their review.

% Acknowledgements should only appear in the accepted version.
\section*{Acknowledgements}

\textbf{Do not} include acknowledgements in the initial version of
the paper submitted for blind review.

If a paper is accepted, the final camera-ready version can (and
probably should) include acknowledgements. In this case, please
place such acknowledgements in an unnumbered section at the
end of the paper. Typically, this will include thanks to reviewers
who gave useful comments, to colleagues who contributed to the ideas,
and to funding agencies and corporate sponsors that provided financial
support.

% In the unusual situation where you want a paper to appear in the
% references without citing it in the main text, use \nocite
\nocite{langley00}

\bibliography{example_paper}
\bibliographystyle{icml2020}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% DELETE THIS PART. DO NOT PLACE CONTENT AFTER THE REFERENCES!
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix
\section{Do \emph{not} have an appendix here}

\textbf{\emph{Do not put content after the references.}}
%
Put anything that you might normally include after the references in a separate
supplementary file.

We recommend that you build supplementary material in a separate document.
If you must create one PDF and cut it up, please be careful to use a tool that
doesn't alter the margins, and that doesn't aggressively rewrite the PDF file.
pdftk usually works fine.

\textbf{Please do not use Apple's preview to cut off supplementary material.} In
previous years it has altered margins, and created headaches at the camera-ready
stage. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

% This document was modified from the file originally made available by
% Pat Langley and Andrea Danyluk for ICML-2K. This version was created
% by Iain Murray in 2018, and modified by Alexandre Bouchard in
% 2019 and 2020. Previous contributors include Dan Roy, Lise Getoor and Tobias
% Scheffer, which was slightly modified from the 2010 version by
% Thorsten Joachims & Johannes Fuernkranz, slightly modified from the
% 2009 version by Kiri Wagstaff and Sam Roweis's 2008 version, which is
% slightly modified from Prasad Tadepalli's 2007 version which is a
% lightly changed version of the previous year's version by Andrew
% Moore, which was in turn edited from those of Kristian Kersting and
% Codrina Lauth. Alex Smola contributed to the algorithmic style files.

### 2020-01-14 main.tex
Updates from Overleaf

@@
 \documentclass{article}
+
+% Custom packages
+\usepackage{amsthm}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{blkarray}
+\usepackage{todonotes}
+\usepackage{mathtools}
+\input{mathdef.tex}
 
@@
 % Therefore, a short form for the running title is supplied here:
-%\icmltitlerunning{Submission and Formatting Instructions for ICML 2020}
-
-% Custom packages
-\usepackage{amsthm}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{float}
-\usepackage{hyperref}
-\usepackage{blkarray}
-\usepackage{todonotes}
-\usepackage{mathtools}
-
-\input{mathdef.tex}
-
-%\author{Edouard Leurent, Denis Efimov, Odalric-Ambrym Maillard}
+\icmltitlerunning{Robust Estimation, Prediction and Control}
 
@@
 	\begin{abstract}
-		This document provides a basic paper template and submission guidelines.
-		Abstracts must be a single paragraph, ideally between 4--6 sentences long.
-		Gross violations will trigger corrections at the camera-ready phase.
+
 	\end{abstract}
@@
 \section{Introduction}
+
+% Industrial setting: data-driven but good initial performances
+% Prior knowledge: structure
 
@@
 Differences with our work:
-\begin{itemize}
-    \item We wish to act straight away in a reasonable (structure) but cautious (robust) way, and progressively get more and more aggressive as we obtain more data and reduce uncertainty.
-    \item Thus, we do not wish to explore actively the more promising regions as in OFU, nor the more likely region as in TS, nor act randomly as in Coarse-ID.
-    \item We have linear dynamics but our cost is not quadratic.
+
+    We wish to act straight away in a reasonable (structure) but cautious (robust) way, and progressively get more and more aggressive as we obtain more data and reduce uncertainty.
+
+    Thus, we do not wish to explore actively the more promising regions as in OFU, nor the more likely region as in TS, nor act randomly as in Coarse-ID.
+
+    We have linear dynamics but our cost is not quadratic.
 Thus, we can accurately represent planning tasks with discrete/branching decisions involving discontinuities (e.g.
 collision vs non-collision states).
-    \item Our optimisation problem amounts to a sequence of controllers selection, instead of continuous controller synthesis
 
-\end{itemize}
+    Our optimisation problem amounts to a sequence of controllers selection, instead of continuous controller synthesis
 
@@
 
-\paragraph{Objective}
+\paragraph{Notations}
 
-We wish to find a sequence of commands $\pi=(u_t)_{t\geq 0}$ that maximises a cumulative objective $V^\pi$:
-\todo[inline]{EL: since the interval dynamics will be deterministic, use open-loop policies, ie sequences of actions $\mathbf{u}$ instead of closed-loop policies $\pi$}
+The dynamics of the real system are described in continuous time.
+However, all the sensing and control performed on-board happen in discrete time, with time-step $\dd t$.
+For any variable $z$, we use the subscript notation to refer to these discrete times: $z_n = z(n\dd t)$.
 
-\todo[inline]{EL: the prediction is done in continuous time and the control in discrete time. How to handle the change in notations?}
+% \paragraph{Objective}
 
-\begin{equation}
-\max_\pi V^\pi
-\end{equation}
-where
-\begin{equation}
-\label{eq:optimal-control}
-V^\pi = \expectedvalueover{\omega(t)}\left[\sum_{t=0}^\infty \gamma^t r(x(t))\condbar u_t = \pi(x_t),\,\eqref{eq:dynamics}\right]
-\end{equation}
-and $r:\Real^p\rightarrow[0,1]$ is a bounded reward function.
+% We wish to find a sequence of commands $\bu=(u_t)_{t\geq 0}$ that maximises a cumulative objective $V^\bu$:
+
+% \todo[inline]{EL: the prediction is done in continuous time and the control in discrete time. How to handle the change in notations?}
+
+% \begin{equation}
+% \max_\bu V^\bu
+% \end{equation}
+% where
+% \begin{equation}
+% \label{eq:optimal-control}
+% V^\bu = \expectedvalueover{\omega(t)}\left[\sum_{t=0}^\infty \gamma^t r(x(t))\condbar u_t,\,\eqref{eq:dynamics}\right]
+% \end{equation}
+% and $r:\Real^p\rightarrow[0,1]$ is a bounded reward function.
 
@@
 \paragraph{Objective}
-Having observed at times $(t_n)_{n\in[N]}$ a history of transitions $\cD = \{(x_n = x(t_n), u_n = u(t_n), y_n = y(t_n))\}_{n\in[N]}$, and given a confidence level $\delta\in[0, 1]$, our goal is to find a confidence region $\cC_\delta$ as tight as possible and such that it holds that:
+Having observed at times a history of transitions $\cD = \{(x_n, u_n, y_n)\}_{n\in[N]}$, and given a confidence level $\delta\in(0, 1)$, our goal is to find a confidence region $\cC_\delta$ as tight as possible and such that it holds that:
 \begin{align}
@@
 
-We further assume that the dynamics $A(\theta)$ enjoy the following additional structure:
+To that end, we further assume that the dynamics $A(\theta)$ enjoy the following additional structure:
 \begin{assumption}[Linear parametrisation]
 \label{assumpt:linear_param}
-There exists a known tensor $\phi\in \Real^{d \times p \times p}$ such that for all $\theta\in\Theta$:
+There exists a known feature tensor $\phi\in \Real^{d \times p \times p}$ such that for all $\theta\in\Theta$:
 \begin{equation}
-    A(\theta) = \theta^\transp \phi \eqdef \sum_{i=1}^d \theta_i\phi_i
+    A(\theta) = A_0 + %\theta^\transp \phi \eqdef A_0 + 
+    \sum_{i=1}^d \theta_i\phi_i
 \end{equation}
-where $\phi_i\in\Real^{p\times p}$ for all $i\in[d]$.
-
-For all $n\geq 0$, we also denote $\Phi_n = [\phi_1 x_n \cdots \phi_d x_n]\in\Real^{p\times d}$.
+where $\phi_i\in\Real^{p\times p}$ for all $i\in[d]$. For all $n$, we also denote $\Phi_n = [\phi_1 x_n \cdots \phi_d x_n]\in\Real^{p\times d}$.
 \end{assumption}
@@
 \begin{align*}
-    \theta_{N,\lambda} - \theta = G_{N, \lambda}^{-1}\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\eta_n - G_{N, \lambda}^{-1}\lambda\Sigma_d\theta 
+    \theta_{N,\lambda} - \theta = G_{N, \lambda}^{-1}\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\eta_n - \lambda G_{N, \lambda}^{-1}\Sigma_d\theta 
 \end{align*}
@@
 Depending on the assumption we take over the noise $\eta_n$ and the true parameter $\theta$, we can bound the regression error $\theta_{N,\lambda} - \theta$ in different ways.
+
+\subsection{Bounded noise}
+
+\begin{assumption}[Bounded noise]
+\label{assumpt:bounded-noise}
+The noise $\eta(t) = C\nu(t) + D\omega(t)$ is bounded.
+\[\|\eta\|_\infty < \infty\]
+\end{assumption}
+
+Then, 
+\begin{align}
+\|\theta_{N,\lambda} - \theta\|_1 \leq &\|G_{N, \lambda}^{-1}\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\|_1\|\eta\|_\infty \\
+&+ \lambda\|G_{N, \lambda}^{-1}\Sigma_d\|_1\|\theta\|_\infty \nonumber
+\end{align}
+
+This $L_1$-ball is a polytope with $2d$ vertices, denoted $\cP$.
+
+If \autoref{assumpt:bounded-noise} does not hold, another weaker assumption can be made.
 
@@
 \begin{assumption}[Sub-Gaussian Noise Model]
-\label{assumpt:noise}
-At each time $t\geq0$ the sum $\eta(t)$ of projected measurement noise $\nu(t)$ and disturbance $\omega(t)$ is a Sub-Gaussian noises with covariance proxy $\Sigma_p \in \Real^{p\times p}$:
+\label{assumpt:gaussian-noise}
+At each time $t\geq0$ the sum $\eta(t)$ of projected measurement noise $\nu(t)$ and disturbance $\omega(t)$ is a sub-Gaussian noise with covariance proxy $\Sigma_p \in \Real^{p\times p}$:
 \begin{equation*}
-    \eta(t) = C\nu(t) + D\omega(t) \sim Sub_G(\Sigma_p)
+    \eta(t) = C\nu(t) + D\omega(t) \sim Sub_G(\Sigma_p).
 \end{equation*}
-
 For instance, this is the case of $\nu$ and $\omega$ are Gaussian noises with respective covariance matrices $\Sigma_r$ and $\Sigma_s$, with $\Sigma_p \eqdef C\Sigma_r C^\transp + D\Sigma_s D^\transp$.
+Also note that \autoref{assumpt:bounded-noise} implies that $\eta$ is $\|\eta\|_\infty I_p$-sub-Gaussian, and is therefore a stronger assumption.
 \end{assumption}
 
-\begin{lemma}[Theorem 1 of \citep{Abbasi2011}, Matrix version]
-\label{lem:concentration}
+\begin{proposition}[Theorem 1 of \citep{Abbasi2011}, Matrix version]
+\label{prop:concentration}
 Let $\{F_t\}_{t=0}$ be a filtration.
-Let $\{\eta_t\}_{t=1}^\infty$ be a $\Real^p$-valued stochastic process such that $\eta_t$ is $F_t$-measurable and conditionally $\Sigma_p$-SubGaussian.
+Let $\{\eta_t\}_{t=1}^\infty$ be a $\Real^p$-valued stochastic process such that $\eta_t$ is $F_t$-measurable and $\expectedvalue\left[\eta_t\condbar F_{t-1}\right]$ is $\Sigma_p$-sub-Gaussian.
 
@@
 For any $t\geq 0$, define:
-
 \begin{equation*}
-    \overline{G}_t = G + \sum_{s=1}^t \Phi_s^\transp \Sigma_p^{-1} \Phi_s \in \Real^{d\times d} \qquad S_t = \sum_{s=1}^t \Phi_s^\transp\Sigma_p^{-1}\eta_s \in \Real^{d}
+    \overline{G}_t = G + \sum_{s=1}^t \Phi_s^\transp \Sigma_p^{-1} \Phi_s \in \Real^{d\times d} \quad S_t = \sum_{s=1}^t \Phi_s^\transp\Sigma_p^{-1}\eta_s \in \Real^{d}.
 \end{equation*}
-Then, for any $\delta>0$, with probability at least $1-\delta$, for all $t\geq0$
-
+Then, for any $\delta>0$, with probability at least $1-\delta$, for all $t\geq0$,
 \begin{align*}
-    \|S_t\|_{\overline{G_t}} \leq \cdots
+\| S_t \|_{\overline{G}_t^{-1}} \geq \sqrt{2\ln \left(\frac{\det\left(\overline{G}_t\right)^{1/2}}{\delta\det(G)^{1/2}}\right)}.
 \end{align*}
-\end{lemma}
+\end{proposition}
 
@@
 \label{thm:confidence_ellipsoid}
-\todo[inline]{TODO}
+
 \end{theorem}
@@
 
-\subsection{Bounded noise}
-
-\begin{assumption}[Bounded noise]
-The noise $\eta(t) = C\nu(t) + D\omega(t)$ is bounded.
-\[\|\eta\|_\infty < \infty\]
-\end{assumption}
-
-Then, 
-\begin{align*}
-\|\theta_{N,\lambda} - \theta\|_1 &\leq \|G_{N, \lambda}^{-1}\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\|_1\|\eta\|_\infty + \lambda\|G_{N, \lambda}^{-1}\Sigma_d\theta\|_1\\
-&\leq \|G_{N, \lambda}^{-1}\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\|_1\|\eta\|_\infty + \lambda\|G_{N, \lambda}^{-1}\Sigma_d\|_1\|\theta\|_\infty
-\end{align*}
-
-This $L_1$-ball is a polytope with $2d$ vertices, that we denote $\cP$.
-
 \section{State Prediction}
@@
     \includegraphics[width=0.3\textwidth]{img/interval-hull}
-    \caption{A few trajectories are sampled from an initial state $x_0$ following a policy $\pi=(u_0,\cdots)$ with various parameters $\theta$ (in black).
+    \caption{A few trajectories are sampled from an initial state $x_0$ following a policy $\bu=(u_0,\cdots)$ with various parameters $\theta$ (in black).
 The union of reachability sets is shown in green, and its interval hull in red.}
@@
 We consider the robust control objective $v^r$:
-\todo[inline]{EL: since the interval dynamics will be deterministic, use open-loop policies, ie sequences of actions $\mathbf{u}$ instead of closed-loop policies $\pi$}
 
@@
 \label{eq:robust-control}
-\max_\pi \underbrace{\min_{A(\theta) \in \cP} \left[\sum_{t=0}^\infty \gamma^t r(x(t))\condbar u_t = \pi(x_t), \omega(t)\right]}_{v^r(\pi)}
+\max_\bu \underbrace{\min_{A(\theta) \in \cP} \left[\sum_{t=0}^\infty \gamma^t r(x(t))\condbar u_t, \omega(t)\right]}_{v^r(\bu)}
 \end{equation}
@@
 \begin{equation}
-\hat{v}^r(\pi) \eqdef \sum_{t=0}^\infty \gamma^t \min_{x\in[\underline{x}(t, \pi), \overline{x}(t, \pi)]}  r(x)
+\hat{v}^r(\bu) \eqdef \sum_{t=0}^\infty \gamma^t \min_{x\in[\underline{x}(t, \bu), \overline{x}(t, \bu)]}  r(x)
 \end{equation}
-where $\underline{x}(t, \pi), \overline{x}(t, \pi)$ follow the dynamics defined in \eqref{eq:interval_predictor}.
+where $\underline{x}(t, \bu), \overline{x}(t, \bu)$ follow the dynamics defined in \eqref{eq:interval_predictor}.
 \end{definition}
@@
 %  }
-%  \KwRet $\argmax_{\pi\in\Pi} \hat{v^r}(\pi)$ \;}{}
+%  \KwRet $\argmax_{\bu} \hat{v^r}(\bu)$ \;}{}
 %  \setcounter{AlgoLine}{0}
@@
 
-\begin{property}[Lower bound]
+\begin{proposition}[Lower bound]
 \label{prop:lower-bound}
@@
 \begin{equation}
-\hat{v}^r(\pi) \leq v^r(\pi)
+\hat{v}^r(\bu) \leq v^r(\bu)
 \end{equation}
@@
 \begin{equation*}
-     \hat{v}^r(\pi) \leq v^r(\pi) \leq \hat{v}^r(\pi) + L\sum_{t=0}^\infty \gamma^t \mu([\underline{x}_N(t),\overline{x}_N(t)])
+     \hat{v}^r(\bu) \leq v^r(\bu) \leq \hat{v}^r(\bu) + L\sum_{t=0}^\infty \gamma^t \mu([\underline{x}_N(t),\overline{x}_N(t)])
 \end{equation*}
-\end{property}
+\end{proposition}
 
@@
 \centering
-\includegraphics[width=0.3\linewidth]{img/robust-control-tree}
+\includegraphics[width=0.4\linewidth]{img/robust-control-tree}
 \caption{The computation of robust b-values in Algorithm \ref{algo:drop}.
@@
 Crucially, this system describes the couplings and interactions between vehicles, so that the autonomous agent can properly anticipate their reactions.
-However, we assume that we do not have access to the true values of the behavioural parameters $\theta=[\theta_1,\dots,\theta_N]^\top$; instead, we merely know that these parameters lie in a set of admissible values $\Pi\subset\Real^{5N}$.
+However, we assume that we do not have access to the true values of the behavioural parameters $\theta=[\theta_1,\dots,\theta_N]^\top$; instead, we merely know that these parameters lie in a set of admissible values $\Theta\subset\Real^{5N}$.
 In order to act safely in the face of uncertainty, we follow the framework of robust decision-making: the agent must consider all the possible trajectories in the space of $Z$ that each vehicle can follow in order to take its decisions.
@@
 
+\begin{proof}
 In order to study the concentration of $\theta_{N,\lambda}$, we substitute the expression of $y_n$ into \eqref{eq:vector_rls}:
@@
 
-\subsection{Proof of \autoref{lem:concentration}}
+\subsection{Proof of \autoref{prop:concentration}}
 
@@
 \begin{equation*}
-    V_t = \sum_{s=1}^t X_s^\transp \Sigma_p^{-1} X_s \in \Real^{d\times d}
+    G_t = \sum_{s=1}^t \Phi_s^\transp \Sigma_p^{-1} \Phi_s \in \Real^{d\times d}
 \end{equation*}
@@
 \begin{equation*}
-    M_t^z = \exp{\left(\inp{z}{S_t} - \frac{1}{2}\|z\|_{V_t}\right)}
+    M_t^z = \exp{\left(\inp{z}{S_t} - \frac{1}{2}\|z\|_{G_t}\right)}
 \end{equation*}
 \begin{equation*}
-    D_t^z = \exp{\left(\inp{X_t z}{\eta_t}_{\Sigma_p^{-1}} - \frac{1}{2}\|X_t z\|_{\Sigma_p^{-1}}\right)}
+    D_t^z = \exp{\left(\inp{\Phi_t z}{\eta_t}_{\Sigma_p^{-1}} - \frac{1}{2}\|\Phi_t z\|_{\Sigma_p^{-1}}\right)}
 \end{equation*}
@@
 \begin{align*}
-    M_t^z = \exp{\left(\sum_{s=1}^t z^\transp X_s^\transp \Sigma_p^{-1} \eta_s - \frac{1}{2} (X_s z)^\transp\Sigma_p^{-1}(X_s z) \right)} = \prod_{s=1}^{t} D_s^z
+    M_t^z = \exp{\left(\sum_{s=1}^t z^\transp \Phi_s^\transp \Sigma_p^{-1} \eta_s - \frac{1}{2} (\Phi_s z)^\transp\Sigma_p^{-1}(\Phi_s z) \right)} = \prod_{s=1}^{t} D_s^z
 \end{align*}
@@
 \begin{align*}
-    \expectedvalue\left[D_t^z \condbar F_{t-1}\right] &= \exp{\left(- \frac{1}{2}\|X_t z\|_{\Sigma_p^{-1}}\right)} \expectedvalue\left[\exp{\left(\inp{X_t z}{\eta_t}_{\Sigma_p^{-1}}\right)} \condbar F_{t-1}\right]  \\
-    &\leq \exp{\left(- \frac{1}{2}\|X_t z\|_{\Sigma_p^{-1}}\right)}\exp{\left((z^\transp X_t^\transp \Sigma_p^{-1})\Sigma_p(\Sigma_p^{-1} X_t z)\right)}\\
+    \expectedvalue\left[D_t^z \condbar F_{t-1}\right] = {}& \exp{\left(- \frac{1}{2}\|\Phi_t z\|_{\Sigma_p^{-1}}\right)}\\ &\expectedvalue\left[\exp{\left(\inp{\Phi_t z}{\eta_t}_{\Sigma_p^{-1}}\right)} \condbar F_{t-1}\right]  \\
+    \leq {} & \exp{\left(- \frac{1}{2}\|\Phi_t z\|_{\Sigma_p^{-1}}\right)}\\
+    &\exp{\left((z^\transp \Phi_t^\transp \Sigma_p^{-1})\Sigma_p(\Sigma_p^{-1} \Phi_t z)\right)}\\
     &= 1
@@
 \end{align*}
+Showing that $(M_t^z)_{t=1}^\infty$ is indeed a supermartingale and in fact $\expectedvalue[M_t^z]\leq 1$.
+I then follows by Doob's upcrossing lemma for super-martnigales that $M_\infty^z = \lim_{t\to\infty} M_t^z$ is almost surely well-defined, ans so is $M_\tau^z$ for any random stopping time $\tau$.
+
+Next, we consider the stopped martingale $M_{\min(\tau,t)}^z$. Since 
+$(M_t^z)_{t=1}^\infty$ is a non-negative supermartingale and $\tau$ is a random stopping time, we deduce by Doob's decomposition that
+\begin{align*}
+\expectedvalue[M_{\min(\tau,t)}^z] &= \expectedvalue[M_0^z] + \expectedvalue[\sum_{s=0}^{t-1} (M_{s+1}^z-M_s^z) \mathbb{I}\{\tau>s\}]\\
+&\leq 1 + \expectedvalue[\sum_{s=0}^{t-1} \expectedvalue[M_{s+1}^z-M_s^z|F_{s}] \mathbb{I}\{\tau>s\}]\\
+&\leq 1
+\end{align*}
+Finally, an application of Fatou's lemma show that 
+$\expectedvalue[M_\tau^z] = \expectedvalue[\liminf_{t\to\infty} M_{\min(\tau,t)}^z] \leq \liminf_{t\to\infty} \expectedvalue[M_{\min(\tau,t)}^z] \leq 1.$
+\end{proof}
+
+% The following uses the method of mixtures.
+% Let $\Gamma$ be a Gaussian random variable which is independent of all other random variables and whose covariance is $\Sigma^{-1}$. (in our estimator, $\Sigma = \lambda\Sigma_d$).
+
+% Define 
+% \[
+% M_t = \expectedvalue \left[M_t^\Gamma \condbar F_\infty\right]
+% \]
+
+% where $F_\infty$ is the tail $\sigma$-algebra of the filtration. Clearly, we still have $\expectedvalue[M_\tau] = \expectedvalue[\expectedvalue[M_\tau^\Gamma|\Gamma]]\leq 1$.
+
+% Let us calculate $M_t$. Let $f$ denote the density of $\Gamma$ and for a positive definite matrix $P$ let $c(P) = \sqrt{(2\pi)^d/\det(P)} = \int \exp (-\frac{1}{2}x^\transp P x)$
+
+\begin{lemma}[Theorem 14.7 of \citep{pena2008self}]
+If $Z$ is a random vector and $B$ is a symmetric positive definite matrix such that
+\[\forall \gamma\in\Real^d, \ln \expectedvalue \exp \left(\gamma^\transp Z -\frac{1}{2} \gamma^\transp B \gamma \right)\leq 0,\]
+then for any positive definite non-random matrix C, it holds
+\[\expectedvalue\left[ \sqrt{\frac{\det(C)}{\det(B+C)} } \exp\left( \frac{1}{2}\|Z\|^2_{(B+C)^{-1}}\right)\right]\leq 1. \] 
+In particular, by Markov inequality, for all $\delta\in(0,1)$, 
+\[\probability{\|Z\|_{(B+C)^{-1}} \geq \sqrt{2\ln \left(\frac{\det \left((B+C)^{1/2}\right)}{\delta\det(C)^{1/2}}\right)}}\leq \delta.\]
+\end{lemma}
+
+Here, by using $Z = \sum_{s=1}^t\Phi_s\Sigma_p^{-1}\eta_s$, $B=G_t$, $C=G$,
+
+\[
+\probability{\| S_t \|_{(G_t+G)^{-1}} \geq \sqrt{2\ln \left(\frac{\det(G_t+G)^{1/2}}{\delta\det(G)^{1/2}}\right)}} \leq \delta
+\]
 
@@
 \subsection{Proof of \autoref{thm:confidence_ellipsoid}}
+
+\begin{proof}
 
@@
 \end{align*}
+
+In particular, for $x = G_{N,\lambda}(\theta_{N,\lambda} - \theta)$, we get after simplifying with $\| \theta_{N,\lambda}  - \theta\|_{G_{N,\lambda}}$:
+\begin{align*}
+    \| \theta_{N,\lambda}  - \theta\|_{G_{N,\lambda}} &\leq \left\|\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\eta_n\right\|_{G_{N, \lambda}^{-1}} + \lambda\|\Sigma_d\theta\|_{G_{N, \lambda}^{-1}}
+\end{align*}
+
+By applying \autoref{prop:concentration}, we obtain:
+\begin{align*}
+    \| \theta_{N,\lambda}  - \theta\|_{G_{N,\lambda}} &\leq 
+     + \lambda\|\Sigma_d\theta\|_{G_{N, \lambda}^{-1}}
+\end{align*}
+\end{proof}
 
@@
 \begin{equation*}
- \sum_{t=0}^\infty \gamma^t r(x_t) \geq \sum_{t=0}^\infty \min_{x\in[\underline{x}(t, \pi), \overline{x}(t, \pi)]} \gamma^t r(x) = \hat{v^r}(\pi)
+ \sum_{t=0}^\infty \gamma^t r(x_t) \geq \sum_{t=0}^\infty \min_{x\in[\underline{x}(t, \bu), \overline{x}(t, \bu)]} \gamma^t r(x) = \hat{v^r}(\bu)
 \end{equation*}
@@
 \begin{align*}
-v^r(\pi) &= \min_{A(\theta) \in A(\Theta)} \expectedvalueover{\omega(t)}\left[\sum_{t=0}^\infty \gamma^t r(x_t)\right] \\
+v^r(\bu) &= \min_{A(\theta) \in A(\Theta)} \expectedvalueover{\omega(t)}\left[\sum_{t=0}^\infty \gamma^t r(x_t)\right] \\
 &\geq \min_{A \in \cP} \expectedvalueover{\omega(t)}\left[\sum_{t=0}^\infty \gamma^t r(x_t)\right] \\
-& \geq \min_{A \in \cP} \expectedvalueover{\omega(t)}\left[\hat{v^r}(\pi)\right] = \hat{v^r}(\pi)
+& \geq \min_{A \in \cP} \expectedvalueover{\omega(t)}\left[\hat{v^r}(\bu)\right] = \hat{v^r}(\bu)
 \end{align*}

### 2020-01-14 main.tex
Remove regularization matrix \Sigma_d

@@
 \paragraph{Regularised least square} Since we expect that $\Phi_n$ may have zero-coordinates during possibly long time intervals (i.e.
-some features are not always active), we consider the weighted $L_2$-regularised regression problem with weights  $\Sigma_p\in\Real^{p\times p}$ and $\Sigma_d\in\Real^{d\times d}$ and parameter $\lambda\in\Real^+_*$:
+some features are not always active), we consider the weighted $L_2$-regularised regression problem with weights  $\Sigma_p\in\Real^{p\times p}$ and parameter $\lambda\in\Real^+_*$:
 
@@
     \label{eq:regression_min}
-    \min_{\theta\in\Real^d} \sum_{n=1}^N \|y_n -\Phi_n\theta\|_{\Sigma_p^{-1}}^2 + \lambda\|\theta\|_{\Sigma_d}^2
+    \min_{\theta\in\Real^d} \sum_{n=1}^N \|y_n -\Phi_n\theta\|_{\Sigma_p^{-1}}^2 + \lambda\|\theta\|_{}^2
 \end{equation}
@@
 \begin{equation*}
-    G_{N, \lambda} = \sum_{n=1}^N \Phi_{n}^\transp\Sigma_p^{-1}\Phi_{n}  + \lambda \Sigma_d \in \Real^{d\times d}.
+    G_{N, \lambda} = \sum_{n=1}^N \Phi_{n}^\transp\Sigma_p^{-1}\Phi_{n}  + \lambda I_d \in \Real^{d\times d}.
 \end{equation*}
@@
 \begin{align*}
-    \theta_{N,\lambda} - \theta = G_{N, \lambda}^{-1}\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\eta_n - \lambda G_{N, \lambda}^{-1}\Sigma_d\theta 
+    \theta_{N,\lambda} - \theta = G_{N, \lambda}^{-1}\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\eta_n - \lambda G_{N, \lambda}^{-1}\theta 
 \end{align*}
@@
 \|\theta_{N,\lambda} - \theta\|_1 \leq &\|G_{N, \lambda}^{-1}\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\|_1\|\eta\|_\infty \\
-&+ \lambda\|G_{N, \lambda}^{-1}\Sigma_d\|_1\|\theta\|_\infty \nonumber
+&+ \lambda\|G_{N, \lambda}^{-1}\|_1\|\theta\|_\infty \nonumber
 \end{align}
@@
 \begin{proof}
-We differentiate $J(\theta) = \sum_{n=1}^N \|y_n -\Phi_n\theta\|_{\Sigma_p^{-1}}^2 + \lambda\|\theta\|_{\Sigma_d}^2$ as in  \eqref{eq:regression_min} with respect to $\theta$:
+We differentiate $J(\theta) = \sum_{n=1}^N \|y_n -\Phi_n\theta\|_{\Sigma_p^{-1}}^2 + \lambda\|\theta\|_{}^2$ as in  \eqref{eq:regression_min} with respect to $\theta$:
 
 \begin{align*}
-    \nabla_{\theta} J(\theta) &= \sum_{n=1}^N\nabla_{\theta} (y_n - \Phi_n\theta)^\transp\Sigma_p^{-1}(y_n - \Phi_n\theta) + \nabla_{\theta} \lambda\|\theta\|_{\Sigma_d}^2\\
-    &= -2\sum_{n=1}^N y_n^\transp\Sigma_p^{-1}\Phi_n + 2\sum_{n=1}^N\theta^\transp(\Phi_n^\transp\Sigma^{-1}\Phi_n) +  2 \lambda \theta^\transp \Sigma_d
+    \nabla_{\theta} J(\theta) &= \sum_{n=1}^N\nabla_{\theta} (y_n - \Phi_n\theta)^\transp\Sigma_p^{-1}(y_n - \Phi_n\theta) + \nabla_{\theta} \lambda\|\theta\|_{}^2\\
+    &= -2\sum_{n=1}^N y_n^\transp\Sigma_p^{-1}\Phi_n + 2\sum_{n=1}^N\theta^\transp(\Phi_n^\transp\Sigma^{-1}\Phi_n) +  2 \lambda \theta^\transp
 \end{align*}
@@
 \begin{align*}
-    \nabla_{\theta} J(\theta) = 0 \iff \left(\sum_{n=1}^N\Phi_n^\transp\Sigma_p^{-1}\Phi_n + \Sigma_d\right)\theta = \sum_{n=1}^N y_n^\transp\Sigma_p^{-1}\Phi_n
+    \nabla_{\theta} J(\theta) = 0 \iff \left(\sum_{n=1}^N\Phi_n^\transp\Sigma_p^{-1}\Phi_n + I_d\right)\theta = \sum_{n=1}^N y_n^\transp\Sigma_p^{-1}\Phi_n
 \end{align*}
@@
     \theta_{N,\lambda} &= G_{N, \lambda}^{-1} \sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1} (\Phi_n\theta +\eta_n)\\
-    &= \theta - G_{N, \lambda}^{-1}\lambda\Sigma_d\theta + G_{N, \lambda}^{-1}\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\eta_n
+    &= \theta - G_{N, \lambda}^{-1}\lambda\theta + G_{N, \lambda}^{-1}\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\eta_n
 \end{align*}
@@
 % The following uses the method of mixtures.
-% Let $\Gamma$ be a Gaussian random variable which is independent of all other random variables and whose covariance is $\Sigma^{-1}$. (in our estimator, $\Sigma = \lambda\Sigma_d$).
+% Let $\Gamma$ be a Gaussian random variable which is independent of all other random variables and whose covariance is $\Sigma^{-1}$. (in our estimator, $\Sigma = \lambda$).
 
@@
     x^\transp\theta_{N,\lambda}  -x^\transp\theta &= x^\transp G_{N, \lambda}^{-1}\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\eta_n
-    - \lambda x^\transp G_{N, \lambda}^{-1}\Sigma_d\theta\\
-    &= \inp{x}{\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\eta_n}_{G_{N, \lambda}^{-1}} - \lambda\inp{x}{\Sigma_d\theta}_{G_{N, \lambda}^{-1}}
+    - \lambda x^\transp G_{N, \lambda}^{-1}\theta\\
+    &= \inp{x}{\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\eta_n}_{G_{N, \lambda}^{-1}} - \lambda\inp{x}{\theta}_{G_{N, \lambda}^{-1}}
 \end{align*}
@@
 \begin{align*}
-    |x^\transp\theta_{N,\lambda}  -x^\transp\theta| &\leq \|x\|_{G_{N, \lambda}^{-1}}\left(\left\|\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\eta_n\right\|_{G_{N, \lambda}^{-1}} + \lambda\|\Sigma_d\theta\|_{G_{N, \lambda}^{-1}}\right)
+    |x^\transp\theta_{N,\lambda}  -x^\transp\theta| &\leq \|x\|_{G_{N, \lambda}^{-1}}\left(\left\|\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\eta_n\right\|_{G_{N, \lambda}^{-1}} + \lambda\|\theta\|_{G_{N, \lambda}^{-1}}\right)
 \end{align*}
@@
 \begin{align*}
-    \| \theta_{N,\lambda}  - \theta\|_{G_{N,\lambda}} &\leq \left\|\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\eta_n\right\|_{G_{N, \lambda}^{-1}} + \lambda\|\Sigma_d\theta\|_{G_{N, \lambda}^{-1}}
+    \| \theta_{N,\lambda}  - \theta\|_{G_{N,\lambda}} &\leq \left\|\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\eta_n\right\|_{G_{N, \lambda}^{-1}} + \lambda\|\theta\|_{G_{N, \lambda}^{-1}}
 \end{align*}
@@
     \| \theta_{N,\lambda}  - \theta\|_{G_{N,\lambda}} &\leq 
-     + \lambda\|\Sigma_d\theta\|_{G_{N, \lambda}^{-1}}
+     + \lambda\|\theta\|_{G_{N, \lambda}^{-1}}
 \end{align*}

### 2020-01-14 main.tex
Confidence ellipsoid proof complete

@@
 	\twocolumn[
-	\icmltitle{Robust Estimation, Prediction and Control with \\ Continuous States and Dynamics Structure}
+	\icmltitle{Robust Estimation, Prediction and Control with \\ Linear Dynamics and Arbitrary Costs}
 
@@
 
-Denote $\eta(t) = C\nu(t) + D\omega(t)$. By substituting the expression of $y_n$ into \eqref{eq:vector_rls}, we obtain:
-\begin{lemma}[Regression error]
-\label{lem:regression-error}
-\begin{align*}
+Denote $\eta(t) = C\nu(t) + D\omega(t)$. By simply substituting the expression of $y_n$ into \eqref{eq:vector_rls}, we obtain the regression error:
+\begin{align}
     \theta_{N,\lambda} - \theta = G_{N, \lambda}^{-1}\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\eta_n - \lambda G_{N, \lambda}^{-1}\theta 
-\end{align*}
-\end{lemma}
+\end{align}
 
-Depending on the assumption we take over the noise $\eta_n$ and the true parameter $\theta$, we can bound the regression error $\theta_{N,\lambda} - \theta$ in different ways.
+Depending on the assumption we have over the noise $\eta_n$ and the true parameter $\theta$, we can bound this error in different ways.
 
@@
 \begin{align}
+\label{eq:bounded-noise-polytope}
 \|\theta_{N,\lambda} - \theta\|_1 \leq &\|G_{N, \lambda}^{-1}\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\|_1\|\eta\|_\infty \\
@@
 
-If \autoref{assumpt:bounded-noise} does not hold, another weaker assumption can be made.
+There may be cases where \autoref{assumpt:bounded-noise} does not hold, for instance if the noise $\eta$ is Gaussian, which implies $\|\eta\|_\infty=+\infty$ and makes \eqref{eq:bounded-noise-polytope} uninformative.
+Then, another weaker assumption can be made.
 
@@
 
-\begin{assumption}[Sub-Gaussian Noise Model]
+\begin{assumption}[Sub-Gaussian Noise]
 \label{assumpt:gaussian-noise}
-At each time $t\geq0$ the sum $\eta(t)$ of projected measurement noise $\nu(t)$ and disturbance $\omega(t)$ is a sub-Gaussian noise with covariance proxy $\Sigma_p \in \Real^{p\times p}$:
+At each time $t\geq0$ the noise $\eta(t)$ is an independent sub-Gaussian noise with covariance proxy $\Sigma_p \in \Real^{p\times p}$:
 \begin{equation*}
-    \eta(t) = C\nu(t) + D\omega(t) \sim Sub_G(\Sigma_p).
+    \eta(t) \sim Sub_G(\Sigma_p).
 \end{equation*}
-For instance, this is the case of $\nu$ and $\omega$ are Gaussian noises with respective covariance matrices $\Sigma_r$ and $\Sigma_s$, with $\Sigma_p \eqdef C\Sigma_r C^\transp + D\Sigma_s D^\transp$.
+For instance, this is the case when $\nu$ and $\omega$ are Gaussian noises with respective covariance matrices $\Sigma_r$ and $\Sigma_s$, with $\Sigma_p \eqdef C\Sigma_r C^\transp + D\Sigma_s D^\transp$.
 Also note that \autoref{assumpt:bounded-noise} implies that $\eta$ is $\|\eta\|_\infty I_p$-sub-Gaussian, and is therefore a stronger assumption.
@@
 \label{prop:concentration}
-Let $\{F_t\}_{t=0}$ be a filtration.
-Let $\{\eta_t\}_{t=1}^\infty$ be a $\Real^p$-valued stochastic process such that $\eta_t$ is $F_t$-measurable and $\expectedvalue\left[\eta_t\condbar F_{t-1}\right]$ is $\Sigma_p$-sub-Gaussian.
+Let $\{F_n\}_{n=0}$ be a filtration.
+Let $\{\eta_n\}_{n=1}^\infty$ be a $\Real^p$-valued stochastic process such that $\eta_n$ is $F_n$-measurable and $\expectedvalue\left[\eta_n\condbar F_{n-1}\right]$ is $\Sigma_p$-sub-Gaussian.
 
-Let $\{\Phi_t\}_{t=1}^\infty$ be an $\Real^{p\times d}$-valued stochastic process such that $\Phi_t$ is $F_t$-measurable.
+Let $\{\Phi_n\}_{n=1}^\infty$ be an $\Real^{p\times d}$-valued stochastic process such that $\Phi_n$ is $F_n$-measurable.
 Assume that $G$ is a $d\times d$ positive definite matrix.
-For any $t\geq 0$, define:
+For any $n\geq 0$, define:
 \begin{equation*}
-    \overline{G}_t = G + \sum_{s=1}^t \Phi_s^\transp \Sigma_p^{-1} \Phi_s \in \Real^{d\times d} \quad S_t = \sum_{s=1}^t \Phi_s^\transp\Sigma_p^{-1}\eta_s \in \Real^{d}.
+    \overline{G}_n = G + \sum_{s=1}^n \Phi_s^\transp \Sigma_p^{-1} \Phi_s \in \Real^{d\times d} \quad S_n = \sum_{s=1}^n \Phi_s^\transp\Sigma_p^{-1}\eta_s \in \Real^{d}.
 \end{equation*}
-Then, for any $\delta>0$, with probability at least $1-\delta$, for all $t\geq0$,
+Then, for any $\delta>0$, with probability at least $1-\delta$, for all $n\geq0$,
 \begin{align*}
-\| S_t \|_{\overline{G}_t^{-1}} \geq \sqrt{2\ln \left(\frac{\det\left(\overline{G}_t\right)^{1/2}}{\delta\det(G)^{1/2}}\right)}.
+\| S_n \|_{\overline{G}_n^{-1}} \geq \sqrt{2\ln \left(\frac{\det\left(\overline{G}_n\right)^{1/2}}{\delta\det(G)^{1/2}}\right)}.
 \end{align*}
@@
 \begin{theorem}[Confidence ellipsoid]
+Under \autoref{assumpt:gaussian-noise}, it holds with probability at least $1-\delta$ that
+\begin{align}
+    \label{eq:confidence-ellipsoid}
+    \| \theta_{N,\lambda}  - \theta\|_{G_{N,\lambda}} &\leq \sqrt{2\ln \left(\frac{\det(G_{N,\lambda})^{1/2}}{\delta\det(\lambda I_d)^{1/2}}\right)}
+     + \lambda^{1/2}\|\theta\|_2.
+\end{align}
 \label{thm:confidence_ellipsoid}
@@
     &A_0 = \theta_{N,\lambda}^\transp\Phi\\
-    &\Delta A_k = \Delta\theta_k^\transp\Phi\\
+    &\Delta A_k = \Delta\theta_k^\transp\Phi
 \end{align*}
-This conversion is illustrated in \autoref{fig:ellipsoid_to_polytope}
+This conversion is illustrated in \autoref{fig:ellipsoid_to_polytope}.
 \end{lemma}
@@
 
-In order to use the interval predictor from \citep{leurent2019interval}, we also require $A_0$ to be Metzler. This can be ensured under some conditions:
+In order to use the interval predictor from \citep{leurent2019interval}, we need an additional assumption.
 
-\begin{lemma}[Similarity transformation \citep{Efimov_a2013}]
-\label{lem:metzler} Let $D\in\Xi\subset\Real^{n\times n}$ be a matrix variable satisfying the interval constraints $\Xi=\{D\in\Real^{n\times n}:\,D_{a}-\Delta\le D\le D_{a}+\Delta\}$ for some $D_{a}^{\text{T}}=D_{a}\in\Real^{n\times n}$ and $\Delta\in\Real_{+}^{n\times n}$.
+% \begin{lemma}[Similarity Transformation]
+% \label{lem:metzler} Let $D\in\Xi\subset\Real^{n\times n}$ be a matrix variable satisfying the interval constraints $\Xi=\{D\in\Real^{n\times n}:\,D_{a}-\Delta\le D\le D_{a}+\Delta\}$ for some $D_{a}^{\text{T}}=D_{a}\in\Real^{n\times n}$ and $\Delta\in\Real_{+}^{n\times n}$.
 If for some constant $\mu\in\Real_{+}$ and a diagonal matrix $\Upsilon\in\Real^{n\times n}$ the Metzler matrix $Y=\mu E_{n\times n}-\Upsilon$ has the same eigenvalues as the matrix $D_{a}$, then there is an orthogonal matrix $S\in\Real^{n\times n}$ such that the matrices $S^{\text{T}}DS$ are Metzler for all $D\in\Xi$ provided that $\mu>n||\Delta||_{max}$.\textup{ }
-\end{lemma}
+% \end{lemma}
+
+\begin{assumption}
+There exists an orthogonal $S\in\Real^{d\times d}$ such that $S^\transp A_0 S$ is Metzler.
+\end{assumption}
+
+This for instance the case when $A_0$ is diagonalizable. Another way ... the similarity transformation of \citep{Efimov_a2013}.
 
@@
 ensures the inclusion property \eqref{eq:interval_property}.
-If there exist diagonal matrices $P$, $Q$, $Q_{+}$, $Q_{-}$, $Z_{+}$, $Z_{-}$, $\Psi_{+}$, $\Psi_{-}$, $\Psi$, $\Gamma\in\Real^{2n\times 2n}$ such that the following LMIs are satisfied:
-\begin{gather*}
-P+\min\{Z_{+},Z_{-}\}>0,\;\Upsilon\preceq0,\;\Gamma>0,\\
-Q+\min\{Q_{+},Q_{-}\}+2\min\{\Psi_{+},\Psi_{-}\}>0,
-\end{gather*}
-where{\footnotesize{}
-\begin{gather*}
-\Upsilon=\left[\begin{array}{cccc}
-\Upsilon_{11} & \Upsilon_{12} & \Upsilon_{13} & P\\
-\Upsilon_{12}^{\top} & \Upsilon_{22} & \Upsilon_{23} & Z_{+}\\
-\Upsilon_{13}^{\top} & \Upsilon_{23}^{\top} & \Upsilon_{33} & Z_{-}\\
-P & Z_{+} & Z_{-} & -\Gamma
-\end{array}\right],\\
-\Upsilon_{11}=\mathcal{A}^{\top}P+P\mathcal{A}+Q,\;\Upsilon_{12}=\mathcal{A}^{\top}Z_{+}+PR_{+}+\Psi_{+},\\
-\Upsilon_{13}=\mathcal{A}^{\top}Z_{-}+PR_{-}+\Psi_{-},\;\Upsilon_{22}=Z_{+}R_{+}+R_{+}^{\top}Z_{+}+Q_{+},\\
-\Upsilon_{23}=Z_{+}R_{-}+R_{+}^{\top}Z_{-}+\Psi,\;\Upsilon_{33}=Z_{-}R_{-}+R_{-}^{\top}Z_{-}+Q_{-},\\
-\mathcal{A}=\left[\begin{array}{cc}
-A_{0} & 0\\
-0 & A_{0}
-\end{array}\right],\;R_{+}=\left[\begin{array}{cc}
-0 & -\Delta A_{-}\\
-0 & \Delta A_{+}
-\end{array}\right],\;R_{-}=\left[\begin{array}{cc}
-\Delta A_{+} & 0\\
--\Delta A_{-} & 0
-\end{array}\right],
-\end{gather*}
-}then the predictor \eqref{eq:interval_predictor} is input-to-state stable with respect to the inputs $\underline{\omega}$, $\overline{\omega}$.
+
+Moreover, the stability of the predictor can be assessed with a sufficient condition in form of an LMI.
+% if there exist diagonal matrices $P$, $Q$, $Q_{+}$, $Q_{-}$, $Z_{+}$, $Z_{-}$, $\Psi_{+}$, $\Psi_{-}$, $\Psi$, $\Gamma\in\Real^{2n\times 2n}$ such that the following LMIs are satisfied:
+% \begin{gather*}
+% P+\min\{Z_{+},Z_{-}\}>0,\;\Upsilon\preceq0,\;\Gamma>0,\\
+% Q+\min\{Q_{+},Q_{-}\}+2\min\{\Psi_{+},\Psi_{-}\}>0,
+% \end{gather*}
+% where{\footnotesize{}
+% \begin{gather*}
+% \Upsilon=\left[\begin{array}{cccc}
+% \Upsilon_{11} & \Upsilon_{12} & \Upsilon_{13} & P\\
+% \Upsilon_{12}^{\top} & \Upsilon_{22} & \Upsilon_{23} & Z_{+}\\
+% \Upsilon_{13}^{\top} & \Upsilon_{23}^{\top} & \Upsilon_{33} & Z_{-}\\
+% P & Z_{+} & Z_{-} & -\Gamma
+% \end{array}\right],\\
+% \Upsilon_{11}=\mathcal{A}^{\top}P+P\mathcal{A}+Q,\;\Upsilon_{12}=\mathcal{A}^{\top}Z_{+}+PR_{+}+\Psi_{+},\\
+% \Upsilon_{13}=\mathcal{A}^{\top}Z_{-}+PR_{-}+\Psi_{-},\;\Upsilon_{22}=Z_{+}R_{+}+R_{+}^{\top}Z_{+}+Q_{+},\\
+% \Upsilon_{23}=Z_{+}R_{-}+R_{+}^{\top}Z_{-}+\Psi,\;\Upsilon_{33}=Z_{-}R_{-}+R_{-}^{\top}Z_{-}+Q_{-},\\
+% \mathcal{A}=\left[\begin{array}{cc}
+% A_{0} & 0\\
+% 0 & A_{0}
+% \end{array}\right],\;R_{+}=\left[\begin{array}{cc}
+% 0 & -\Delta A_{-}\\
+% 0 & \Delta A_{+}
+% \end{array}\right],\;R_{-}=\left[\begin{array}{cc}
+% \Delta A_{+} & 0\\
+% -\Delta A_{-} & 0
+% \end{array}\right],
+% \end{gather*}
+% }then the predictor \eqref{eq:interval_predictor} is input-to-state stable with respect to the inputs $\underline{\omega}$, $\overline{\omega}$.
 \end{theorem}
@@
 \begin{equation}
-\hat{v}^r(\bu) \eqdef \sum_{t=0}^\infty \gamma^t \min_{x\in[\underline{x}(t, \bu), \overline{x}(t, \bu)]}  r(x)
+\hat{v}^r(\bu) \eqdef \sum_{t=0}^\infty \gamma^t \min_{x\in[\underline{x}(t, \bu), \overline{x}(t, \bu)]}  R(x)
 \end{equation}
@@
 
-If we assume that $R$ is $L$-Lipschitz, then we can bound the other side:
+If we assume that $R$ is $L$-Lipschitz, then we can also bound the other side:
 \begin{equation*}
@@
 
-\section{The Use-Case of Autonomous Driving}
+\section{Experiments}
 
@@
 
-In the following, we describe the system and its associated interval predictor.
+The system
+
+\bibliography{references}
+\bibliographystyle{icml2020}
+
+\clearpage
+\appendix
+
+\section{Proofs}
+
+\subsection{Proof of \autoref{thm:regularized_solution}}
+
+\begin{proof}
+We differentiate $J(\theta) = \sum_{n=1}^N \|y_n -\Phi_n\theta\|_{\Sigma_p^{-1}}^2 + \lambda\|\theta\|_{}^2$ as in  \eqref{eq:regression_min} with respect to $\theta$:
+
+\begin{align*}
+    \nabla_{\theta} J(\theta) &= \sum_{n=1}^N\nabla_{\theta} (y_n - \Phi_n\theta)^\transp\Sigma_p^{-1}(y_n - \Phi_n\theta) + \nabla_{\theta} \lambda\|\theta\|_{}^2\\
+    &= -2\sum_{n=1}^N y_n^\transp\Sigma_p^{-1}\Phi_n + 2\sum_{n=1}^N\theta^\transp(\Phi_n^\transp\Sigma^{-1}\Phi_n) +  2 \lambda \theta^\transp
+\end{align*}
+
+Hence,
+\begin{align*}
+    \nabla_{\theta} J(\theta) = 0 \iff \left(\sum_{n=1}^N\Phi_n^\transp\Sigma_p^{-1}\Phi_n + I_d\right)\theta = \sum_{n=1}^N y_n^\transp\Sigma_p^{-1}\Phi_n
+\end{align*}
+\end{proof}
+
+\subsection{Proof of \autoref{prop:concentration}}
+
+\begin{proof}
+
+Let 
+\begin{equation*}
+    G_t = \sum_{s=1}^t \Phi_s^\transp \Sigma_p^{-1} \Phi_s \in \Real^{d\times d}
+\end{equation*}
+And for any $z\in\Real^d$,
+\begin{equation*}
+    M_t^z = \exp{\left(\inp{z}{S_t} - \frac{1}{2}\|z\|_{G_t}\right)}
+\end{equation*}
+\begin{equation*}
+    D_t^z = \exp{\left(\inp{\Phi_t z}{\eta_t}_{\Sigma_p^{-1}} - \frac{1}{2}\|\Phi_t z\|_{\Sigma_p^{-1}}\right)}
+\end{equation*}
+Then,
+\begin{align*}
+    M_t^z = \exp{\left(\sum_{s=1}^t z^\transp \Phi_s^\transp \Sigma_p^{-1} \eta_s - \frac{1}{2} (\Phi_s z)^\transp\Sigma_p^{-1}(\Phi_s z) \right)} = \prod_{s=1}^{t} D_s^z
+\end{align*}
+and using the Sub-Gaussianity of $\eta_t$
+\begin{align*}
+    \expectedvalue\left[D_t^z \condbar F_{t-1}\right] = {}& \exp{\left(- \frac{1}{2}\|\Phi_t z\|_{\Sigma_p^{-1}}\right)}\\ &\expectedvalue\left[\exp{\left(\inp{\Phi_t z}{\eta_t}_{\Sigma_p^{-1}}\right)} \condbar F_{t-1}\right]  \\
+    \leq {} & \exp{\left(- \frac{1}{2}\|\Phi_t z\|_{\Sigma_p^{-1}}\right)}\\
+    &\exp{\left((z^\transp \Phi_t^\transp \Sigma_p^{-1})\Sigma_p(\Sigma_p^{-1} \Phi_t z)\right)}\\
+    &= 1
+\end{align*}
+\begin{align*}
+    \expectedvalue\left[M_t^z \condbar F_{t-1}\right] = \left(\prod_{s=1}^{t-1} D_s^z\right) \expectedvalue\left[D_t^z \condbar F_{t-1}\right] \leq M_{t-1}^z
+\end{align*}
+Showing that $(M_t^z)_{t=1}^\infty$ is indeed a supermartingale and in fact $\expectedvalue[M_t^z]\leq 1$.
+I then follows by Doob's upcrossing lemma for super-martnigales that $M_\infty^z = \lim_{t\to\infty} M_t^z$ is almost surely well-defined, ans so is $M_\tau^z$ for any random stopping time $\tau$.
+
+Next, we consider the stopped martingale $M_{\min(\tau,t)}^z$. Since 
+$(M_t^z)_{t=1}^\infty$ is a non-negative supermartingale and $\tau$ is a random stopping time, we deduce by Doob's decomposition that
+\begin{align*}
+\expectedvalue[M_{\min(\tau,t)}^z] &= \expectedvalue[M_0^z] + \expectedvalue[\sum_{s=0}^{t-1} (M_{s+1}^z-M_s^z) \mathbb{I}\{\tau>s\}]\\
+&\leq 1 + \expectedvalue[\sum_{s=0}^{t-1} \expectedvalue[M_{s+1}^z-M_s^z|F_{s}] \mathbb{I}\{\tau>s\}]\\
+&\leq 1
+\end{align*}
+Finally, an application of Fatou's lemma show that 
+$\expectedvalue[M_\tau^z] = \expectedvalue[\liminf_{t\to\infty} M_{\min(\tau,t)}^z] \leq \liminf_{t\to\infty} \expectedvalue[M_{\min(\tau,t)}^z] \leq 1.$
+
+% The following uses the method of mixtures.
+% Let $\Gamma$ be a Gaussian random variable which is independent of all other random variables and whose covariance is $\Sigma^{-1}$. (in our estimator, $\Sigma = \lambda$).
+
+% Define 
+% \[
+% M_t = \expectedvalue \left[M_t^\Gamma \condbar F_\infty\right]
+% \]
+
+% where $F_\infty$ is the tail $\sigma$-algebra of the filtration. Clearly, we still have $\expectedvalue[M_\tau] = \expectedvalue[\expectedvalue[M_\tau^\Gamma|\Gamma]]\leq 1$.
+
+% Let us calculate $M_t$. Let $f$ denote the density of $\Gamma$ and for a positive definite matrix $P$ let $c(P) = \sqrt{(2\pi)^d/\det(P)} = \int \exp (-\frac{1}{2}x^\transp P x)$
+
+\begin{lemma}[Theorem 14.7 of \citep{pena2008self}]
+If $Z$ is a random vector and $B$ is a symmetric positive definite matrix such that
+\[\forall \gamma\in\Real^d, \ln \expectedvalue \exp \left(\gamma^\transp Z -\frac{1}{2} \gamma^\transp B \gamma \right)\leq 0,\]
+then for any positive definite non-random matrix C, it holds
+\[\expectedvalue\left[ \sqrt{\frac{\det(C)}{\det(B+C)} } \exp\left( \frac{1}{2}\|Z\|^2_{(B+C)^{-1}}\right)\right]\leq 1. \] 
+In particular, by Markov inequality, for all $\delta\in(0,1)$, 
+\[\probability{\|Z\|_{(B+C)^{-1}} \geq \sqrt{2\ln \left(\frac{\det \left((B+C)^{1/2}\right)}{\delta\det(C)^{1/2}}\right)}}\leq \delta.\]
+\end{lemma}
+
+Here, by using $Z = \sum_{s=1}^t\Phi_s\Sigma_p^{-1}\eta_s$, $B=G_t$, $C=G$,
+
+\[
+\probability{\| S_t \|_{(G_t+G)^{-1}} \geq \sqrt{2\ln \left(\frac{\det(G_t+G)^{1/2}}{\delta\det(G)^{1/2}}\right)}} \leq \delta
+\]
+
+\end{proof}
+
+\subsection{Proof of \autoref{thm:confidence_ellipsoid}}
+
+\begin{proof}
+
+Hence, for all $x\in\Real^d$,
+\begin{align*}
+    x^\transp\theta_{N,\lambda}  -x^\transp\theta &= x^\transp G_{N, \lambda}^{-1}\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\eta_n
+    - \lambda x^\transp G_{N, \lambda}^{-1}\theta\\
+    &= \inp{x}{\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\eta_n}_{G_{N, \lambda}^{-1}} - \lambda\inp{x}{\theta}_{G_{N, \lambda}^{-1}}
+\end{align*}
+
+Using the Cauchy-Schwartz inequality, we get:
+\begin{align*}
+    |x^\transp\theta_{N,\lambda}  -x^\transp\theta| &\leq \|x\|_{G_{N, \lambda}^{-1}}\left(\left\|\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\eta_n\right\|_{G_{N, \lambda}^{-1}} + \lambda\|\theta\|_{G_{N, \lambda}^{-1}}\right)
+\end{align*}
+
+In particular, for $x = G_{N,\lambda}(\theta_{N,\lambda} - \theta)$, we get after simplifying with $\| \theta_{N,\lambda}  - \theta\|_{G_{N,\lambda}}$:
+\begin{align*}
+    \| \theta_{N,\lambda}  - \theta\|_{G_{N,\lambda}} &\leq \left\|\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\eta_n\right\|_{G_{N, \lambda}^{-1}} + \lambda\|\theta\|_{G_{N, \lambda}^{-1}}
+\end{align*}
+
+By applying \autoref{prop:concentration} with $G=\lambda I_d$, we obtain that with probability at least $1-\delta$,
+\begin{align*}
+    \| \theta_{N,\lambda}  - \theta\|_{G_{N,\lambda}} &\leq \sqrt{2\ln \left(\frac{\det(G_{N,\lambda})^{1/2}}{\delta\det(\lambda I_d)^{1/2}}\right)}
+     + \lambda\|\theta\|_{G_{N, \lambda}^{-1}}
+\end{align*}
+And since $\|\theta\|_{G_{N, \lambda}^{-1}}^2 \leq 1/\lambda_{\min}(G_{N,\lambda})\|\theta\|_2^2 \leq 1/\lambda \|\theta\|_2^2$,
+\begin{align*}
+    \| \theta_{N,\lambda}  - \theta\|_{G_{N,\lambda}} &\leq \sqrt{2\ln \left(\frac{\det(G_{N,\lambda})^{1/2}}{\delta\det(\lambda I_d)^{1/2}}\right)}
+     + \lambda^{1/2}\|\theta\|_2
+\end{align*}
+\end{proof}
+
+\subsection{Proof of \autoref{lem:confidence_polytope}}
+
+\begin{proof}
+The ellipsoid in \eqref{eq:confidence-ellipsoid} is described by:
+\begin{align*}
+    \theta\in\cC_\delta &\implies
+    (\theta-\theta_{N,\lambda})^\transp G_{N,\lambda}^{-1}(\theta-\theta_{N,\lambda}) \leq C_{N,\lambda,\delta}\\
+    &\implies (\theta'-\theta'_{N,\lambda})^\transp D (\theta'-\theta'_{N,\lambda}) \leq C_{N,\lambda,\delta}\\
+    &\implies \sum_{i=1}^d D_{i,i}(\theta'_i-\theta'_{N,\lambda,i})^2\leq C_{N,\lambda,\delta}\\
+    &\implies\forall i, |\theta'_i-\theta'_{N,\lambda,i}|\leq C_{N,\lambda,\delta}^{1/2}D_{i,i}^{-1/2}
+\end{align*}
+This describes a $\Real^d$ box containing $\theta' = P\theta$, whose $k^\text{th}$ vertex is represented by $\theta_{N,\lambda}' + C_{N,\lambda,\delta}^{1/2}D^{-1/2} h_k$.
+We obtain the corresponding box on $\theta$ by transforming each vertex of the box with $P^{-1}$.
+\end{proof}
+
+\subsection{Proof of \autoref{prop:lower-bound}}
+
+\begin{proof}
+We have that $A(\theta) \in \cP$ with probability $1-\delta$.
+Whenever it is the case, we have by \autoref{thm:predictor} that the inclusion property \eqref{eq:interval_property} is verified by the interval predictor \eqref{eq:interval_predictor} for all $\omega(t)\in[\underline{\omega}(t), \overline{\omega}(t)]$.
+This gives the following bound:
+\begin{equation*}
+ \sum_{t=0}^\infty \gamma^t r(x_t) \geq \sum_{t=0}^\infty \min_{x\in[\underline{x}(t, \bu), \overline{x}(t, \bu)]} \gamma^t r(x) = \hat{v^r}(\bu)
+\end{equation*}
+
+And finally, with probability $1-\delta$,
+\begin{align*}
+v^r(\bu) &= \min_{A(\theta) \in A(\Theta)} \expectedvalueover{\omega(t)}\left[\sum_{t=0}^\infty \gamma^t r(x_t)\right] \\
+&\geq \min_{A \in \cP} \expectedvalueover{\omega(t)}\left[\sum_{t=0}^\infty \gamma^t r(x_t)\right] \\
+& \geq \min_{A \in \cP} \expectedvalueover{\omega(t)}\left[\hat{v^r}(\bu)\right] = \hat{v^r}(\bu)
+\end{align*}
+\end{proof}
+
+\section{The use case of autonomous driving}
+
+In the following, we describe the structure of the model representing the dynamics of of several vehicles driving and interacting with one another.
 
@@
 
-\bibliography{references}
-\bibliographystyle{icml2020}
-
-\appendix
-
-\section{Proofs}
-
-\subsection{Proof of \autoref{thm:regularized_solution}}
-
-\begin{proof}
-We differentiate $J(\theta) = \sum_{n=1}^N \|y_n -\Phi_n\theta\|_{\Sigma_p^{-1}}^2 + \lambda\|\theta\|_{}^2$ as in  \eqref{eq:regression_min} with respect to $\theta$:
-
-\begin{align*}
-    \nabla_{\theta} J(\theta) &= \sum_{n=1}^N\nabla_{\theta} (y_n - \Phi_n\theta)^\transp\Sigma_p^{-1}(y_n - \Phi_n\theta) + \nabla_{\theta} \lambda\|\theta\|_{}^2\\
-    &= -2\sum_{n=1}^N y_n^\transp\Sigma_p^{-1}\Phi_n + 2\sum_{n=1}^N\theta^\transp(\Phi_n^\transp\Sigma^{-1}\Phi_n) +  2 \lambda \theta^\transp
-\end{align*}
-
-Hence,
-\begin{align*}
-    \nabla_{\theta} J(\theta) = 0 \iff \left(\sum_{n=1}^N\Phi_n^\transp\Sigma_p^{-1}\Phi_n + I_d\right)\theta = \sum_{n=1}^N y_n^\transp\Sigma_p^{-1}\Phi_n
-\end{align*}
-\end{proof}
-
-\subsection{Proof of \autoref{lem:regression-error}}
-
-\begin{proof}
-In order to study the concentration of $\theta_{N,\lambda}$, we substitute the expression of $y_n$ into \eqref{eq:vector_rls}:
-\begin{align*}
-    \theta_{N,\lambda} &= G_{N, \lambda}^{-1} \sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1} (\Phi_n\theta +\eta_n)\\
-    &= \theta - G_{N, \lambda}^{-1}\lambda\theta + G_{N, \lambda}^{-1}\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\eta_n
-\end{align*}
-
-\subsection{Proof of \autoref{prop:concentration}}
-
-\begin{proof}
-
-Let 
-\begin{equation*}
-    G_t = \sum_{s=1}^t \Phi_s^\transp \Sigma_p^{-1} \Phi_s \in \Real^{d\times d}
-\end{equation*}
-And for any $z\in\Real^d$,
-\begin{equation*}
-    M_t^z = \exp{\left(\inp{z}{S_t} - \frac{1}{2}\|z\|_{G_t}\right)}
-\end{equation*}
-\begin{equation*}
-    D_t^z = \exp{\left(\inp{\Phi_t z}{\eta_t}_{\Sigma_p^{-1}} - \frac{1}{2}\|\Phi_t z\|_{\Sigma_p^{-1}}\right)}
-\end{equation*}
-Then,
-\begin{align*}
-    M_t^z = \exp{\left(\sum_{s=1}^t z^\transp \Phi_s^\transp \Sigma_p^{-1} \eta_s - \frac{1}{2} (\Phi_s z)^\transp\Sigma_p^{-1}(\Phi_s z) \right)} = \prod_{s=1}^{t} D_s^z
-\end{align*}
-and using the Sub-Gaussianity of $\eta_t$
-\begin{align*}
-    \expectedvalue\left[D_t^z \condbar F_{t-1}\right] = {}& \exp{\left(- \frac{1}{2}\|\Phi_t z\|_{\Sigma_p^{-1}}\right)}\\ &\expectedvalue\left[\exp{\left(\inp{\Phi_t z}{\eta_t}_{\Sigma_p^{-1}}\right)} \condbar F_{t-1}\right]  \\
-    \leq {} & \exp{\left(- \frac{1}{2}\|\Phi_t z\|_{\Sigma_p^{-1}}\right)}\\
-    &\exp{\left((z^\transp \Phi_t^\transp \Sigma_p^{-1})\Sigma_p(\Sigma_p^{-1} \Phi_t z)\right)}\\
-    &= 1
-\end{align*}
-\begin{align*}
-    \expectedvalue\left[M_t^z \condbar F_{t-1}\right] = \left(\prod_{s=1}^{t-1} D_s^z\right) \expectedvalue\left[D_t^z \condbar F_{t-1}\right] \leq M_{t-1}^z
-\end{align*}
-Showing that $(M_t^z)_{t=1}^\infty$ is indeed a supermartingale and in fact $\expectedvalue[M_t^z]\leq 1$.
-I then follows by Doob's upcrossing lemma for super-martnigales that $M_\infty^z = \lim_{t\to\infty} M_t^z$ is almost surely well-defined, ans so is $M_\tau^z$ for any random stopping time $\tau$.
-
-Next, we consider the stopped martingale $M_{\min(\tau,t)}^z$. Since 
-$(M_t^z)_{t=1}^\infty$ is a non-negative supermartingale and $\tau$ is a random stopping time, we deduce by Doob's decomposition that
-\begin{align*}
-\expectedvalue[M_{\min(\tau,t)}^z] &= \expectedvalue[M_0^z] + \expectedvalue[\sum_{s=0}^{t-1} (M_{s+1}^z-M_s^z) \mathbb{I}\{\tau>s\}]\\
-&\leq 1 + \expectedvalue[\sum_{s=0}^{t-1} \expectedvalue[M_{s+1}^z-M_s^z|F_{s}] \mathbb{I}\{\tau>s\}]\\
-&\leq 1
-\end{align*}
-Finally, an application of Fatou's lemma show that 
-$\expectedvalue[M_\tau^z] = \expectedvalue[\liminf_{t\to\infty} M_{\min(\tau,t)}^z] \leq \liminf_{t\to\infty} \expectedvalue[M_{\min(\tau,t)}^z] \leq 1.$
-\end{proof}
-
-% The following uses the method of mixtures.
-% Let $\Gamma$ be a Gaussian random variable which is independent of all other random variables and whose covariance is $\Sigma^{-1}$. (in our estimator, $\Sigma = \lambda$).
-
-% Define 
-% \[
-% M_t = \expectedvalue \left[M_t^\Gamma \condbar F_\infty\right]
-% \]
-
-% where $F_\infty$ is the tail $\sigma$-algebra of the filtration. Clearly, we still have $\expectedvalue[M_\tau] = \expectedvalue[\expectedvalue[M_\tau^\Gamma|\Gamma]]\leq 1$.
-
-% Let us calculate $M_t$. Let $f$ denote the density of $\Gamma$ and for a positive definite matrix $P$ let $c(P) = \sqrt{(2\pi)^d/\det(P)} = \int \exp (-\frac{1}{2}x^\transp P x)$
-
-\begin{lemma}[Theorem 14.7 of \citep{pena2008self}]
-If $Z$ is a random vector and $B$ is a symmetric positive definite matrix such that
-\[\forall \gamma\in\Real^d, \ln \expectedvalue \exp \left(\gamma^\transp Z -\frac{1}{2} \gamma^\transp B \gamma \right)\leq 0,\]
-then for any positive definite non-random matrix C, it holds
-\[\expectedvalue\left[ \sqrt{\frac{\det(C)}{\det(B+C)} } \exp\left( \frac{1}{2}\|Z\|^2_{(B+C)^{-1}}\right)\right]\leq 1. \] 
-In particular, by Markov inequality, for all $\delta\in(0,1)$, 
-\[\probability{\|Z\|_{(B+C)^{-1}} \geq \sqrt{2\ln \left(\frac{\det \left((B+C)^{1/2}\right)}{\delta\det(C)^{1/2}}\right)}}\leq \delta.\]
-\end{lemma}
-
-Here, by using $Z = \sum_{s=1}^t\Phi_s\Sigma_p^{-1}\eta_s$, $B=G_t$, $C=G$,
-
-\[
-\probability{\| S_t \|_{(G_t+G)^{-1}} \geq \sqrt{2\ln \left(\frac{\det(G_t+G)^{1/2}}{\delta\det(G)^{1/2}}\right)}} \leq \delta
-\]
-
-\end{proof}
-
-\subsection{Proof of \autoref{thm:confidence_ellipsoid}}
-
-\begin{proof}
-
-Hence, for all $x\in\Real^d$,
-\begin{align*}
-    x^\transp\theta_{N,\lambda}  -x^\transp\theta &= x^\transp G_{N, \lambda}^{-1}\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\eta_n
-    - \lambda x^\transp G_{N, \lambda}^{-1}\theta\\
-    &= \inp{x}{\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\eta_n}_{G_{N, \lambda}^{-1}} - \lambda\inp{x}{\theta}_{G_{N, \lambda}^{-1}}
-\end{align*}
-
-Using the Cauchy-Schwartz inequality, we get:
-\begin{align*}
-    |x^\transp\theta_{N,\lambda}  -x^\transp\theta| &\leq \|x\|_{G_{N, \lambda}^{-1}}\left(\left\|\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\eta_n\right\|_{G_{N, \lambda}^{-1}} + \lambda\|\theta\|_{G_{N, \lambda}^{-1}}\right)
-\end{align*}
-
-In particular, for $x = G_{N,\lambda}(\theta_{N,\lambda} - \theta)$, we get after simplifying with $\| \theta_{N,\lambda}  - \theta\|_{G_{N,\lambda}}$:
-\begin{align*}
-    \| \theta_{N,\lambda}  - \theta\|_{G_{N,\lambda}} &\leq \left\|\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\eta_n\right\|_{G_{N, \lambda}^{-1}} + \lambda\|\theta\|_{G_{N, \lambda}^{-1}}
-\end{align*}
-
-By applying \autoref{prop:concentration}, we obtain:
-\begin{align*}
-    \| \theta_{N,\lambda}  - \theta\|_{G_{N,\lambda}} &\leq 
-     + \lambda\|\theta\|_{G_{N, \lambda}^{-1}}
-\end{align*}
-\end{proof}
-
-\subsection{Proof of \autoref{lem:confidence_polytope}}
-
-\begin{proof}
-The ellipsoid in \eqref{eq:confidence-ellipsoid} is described by:
-\begin{align*}
-    \theta\in\cC_\delta &\implies
-    (\theta-\theta_{N,\lambda})^\transp G_{N,\lambda}^{-1}(\theta-\theta_{N,\lambda}) \leq C_{N,\lambda,\delta}\\
-    &\implies (\theta'-\theta'_{N,\lambda})^\transp D (\theta'-\theta'_{N,\lambda}) \leq C_{N,\lambda,\delta}\\
-    &\implies \sum_{i=1}^d D_{i,i}(\theta'_i-\theta'_{N,\lambda,i})^2\leq C_{N,\lambda,\delta}\\
-    &\implies\forall i, |\theta'_i-\theta'_{N,\lambda,i}|\leq C_{N,\lambda,\delta}^{1/2}D_{i,i}^{-1/2}
-\end{align*}
-This describes a $\Real^d$ box containing $\theta' = P\theta$, whose $k^\text{th}$ vertex is represented by $\theta_{N,\lambda}' + C_{N,\lambda,\delta}^{1/2}D^{-1/2} h_k$.
-We obtain the corresponding box on $\theta$ by transforming each vertex of the box with $P^{-1}$.
-\end{proof}
-
-\subsection{Proof of \autoref{prop:lower-bound}}
-
-\begin{proof}
-We have that $A(\theta) \in \cP$ with probability $1-\delta$.
-Whenever it is the case, we have by \autoref{thm:predictor} that the inclusion property \eqref{eq:interval_property} is verified by the interval predictor \eqref{eq:interval_predictor} for all $\omega(t)\in[\underline{\omega}(t), \overline{\omega}(t)]$.
-This gives the following bound:
-\begin{equation*}
- \sum_{t=0}^\infty \gamma^t r(x_t) \geq \sum_{t=0}^\infty \min_{x\in[\underline{x}(t, \bu), \overline{x}(t, \bu)]} \gamma^t r(x) = \hat{v^r}(\bu)
-\end{equation*}
-
-And finally, with probability $1-\delta$,
-\begin{align*}
-v^r(\bu) &= \min_{A(\theta) \in A(\Theta)} \expectedvalueover{\omega(t)}\left[\sum_{t=0}^\infty \gamma^t r(x_t)\right] \\
-&\geq \min_{A \in \cP} \expectedvalueover{\omega(t)}\left[\sum_{t=0}^\infty \gamma^t r(x_t)\right] \\
-& \geq \min_{A \in \cP} \expectedvalueover{\omega(t)}\left[\hat{v^r}(\bu)\right] = \hat{v^r}(\bu)
-\end{align*}
-\end{proof}
-
 \end{document}

### 2020-01-14 main.tex
Sketch of introduction

@@
 
-% Industrial setting: data-driven but good initial performances
-% Prior knowledge: structure
+We would like to control a system in order to maximise an \textit{arbitrary} reward function $R$, e.g.
+non-convex, non-smooth.
+These happen naturally: combinatorial optimization such as scheduling, obstacle avoidance.
+Critical industrial setting: we do not want to commit mistakes. 
+In particular, this rules out shiny Deep RL etc.
+The only way to avoid mistakes from the outset, when the system is first deployed, is to incorporate some kind of prior knowledge.
+In this work, we assume that the system dynamics are partially known: known structure of a parametrized system, with unknown parameters.
+This is realistic in the sense that most industrial applications to date have been relying on physical models and corresponding optimal controllers rather than machine learning.
+Here, instead of providing the whole model, its main parts
+Data driven scheme: as we interact and observe more data of the true system, we can estimate the parameters more accurately.
+This estimated model could be use to derive the corresponding optimal control, but this is unsafe: model bias.
+To address this, we want to perform robust estimation: not just a maximum likelihood model, but a whole high-confidence region where the true system is likely to lie.
+Given this ambiguity set, how should we act?
+Given the critical setting, we do not want to be optimistic, and try to minimise some cumulative regret.
+Quite the contrary, we want to be cautious, safe, prepare for the worst and plan for the best.
+A robust control scheme.
+Minimax problem are hard to solve, especially since $R$ can be arbitrary.
+We cannot use traditional tools from the robust LQ control community (coarse-id control, system-level synthesis).
+Instead, we adopt a hierachical control architecture, controller selection: discrete choice of a driving maneuver, a short-term goal, whose execution is performed by a fixed low-level controller.
+It is true that the passage from continuous optimization to discrete optimization induces a suboptimality.
+However, it can be mitigated by using a more diverse controller basis.
+We are left with a sequential optimization problem with continuous states and discrete actions: tree-based planning algorithms.
+But not a point estimate, a whole confidence region.
+Hence, a two step procedure: robust prediction of the reachability set, which provides a conservative pessimistic reward to the planning algorithm.
 
@@
 
+This does not amount to defining a pessimistic reward-function $\underline{R}$, since the worst case is assessed over the whole trajectory being optimized, and not at the level of a local transition.
+It cannot be precomputed prior to the control optimization procedure, it needs to be done jointly.
+
 %\begin{algorithm}[tp]
@@
 
-If we assume that $R$ is $L$-Lipschitz, then we can also bound the other side:
+If we assume that $R$ is $L$-Lipschitz, then we can also bound the approximation error:
 \begin{equation*}
-     \hat{v}^r(\bu) \leq v^r(\bu) \leq \hat{v}^r(\bu) + L\sum_{t=0}^\infty \gamma^t \mu([\underline{x}_N(t),\overline{x}_N(t)])
+     v^r(\bu) - \hat{v}^r(\bu) \leq L\sum_{t=0}^\infty \gamma^t \mu([\underline{x}_N(t),\overline{x}_N(t)])
 \end{equation*}
@@
 
-The robust objective error $v^r - \hat{v^r}$ stems from two terms: the approximation of the reachable set by the polytopic and interval approximations and the loss of time-dependency between the states within a single trajectory.
-If both these approximations are tight enough, maximising the lower bound $\hat{v^r}$ will increase the true objective $v^r$, which is the idea behind Algorithm \ref{algo:irc}.
+Since all our approximations were conservative, if we manage to find a control sequence such that no \textit{bad event} (e.g.
+a collision) happens with our surrogate objective, then we are guaranteed so they will not happen either when the controls are executed on the true system.
 
@@
 
-We consider the problem of safe decision-making for autonomous highway driving.
+We consider the problem of safe decision-making for an autonomous vehicle.
 An autonomous vehicle is driving on a highway populated with $N$ other agents, and uses Model Predictive Control to plan a sequence of decisions.

### 2020-01-14 main.tex
Update introduction

@@
 
+Our contributions are the following:
+In Section 2, we structured dynamics.
+In order to derive the confidence regions, we rely on the work of \citet{Abbasi2011} that provide confidence ellipsoid for the regularised least-square estimator.
+However, we need to extend their result by one dimension, with matricial features and vectorial noise where the original setting involved vectorial features and scalar noise.
+
 \section{Related Work}
@@
 
-We also have access to a measurement of the form
+We also have access to the observation of $x(t)$ and to noisy a measurement of $\dot{x}(t)$ in the form
 $
     \dot{x}(t) + C\nu(t)
-$
-that we will actually denote (since the control $u(t)$ is known) as:
+$ where $\nu(t)\in\Real^r$ is a measurement noise and $C\in\Real^{p\times r}$ is known.
+For better readability, we will actually denote the measurement as:
 \begin{equation}
 \label{eq:measurement}
-    y(t) = \dot{x}(t) - Bu(t) + C\nu(t)
+    y(t) = \dot{x}(t) - A_0 x(t) - Bu(t) + C\nu(t)
 \end{equation}
-where $\nu(t)\in\Real^r$ is a measurement noise and $C\in\Real^{p\times r}$ is known. Assumptions over the disturbance $\omega$ and noise $\nu$ will be detailed further.
+which is possible since the nominal dynamics $A_0$, thet state $x(t)$ and the control $u(t)$ are known.
+Assumptions over the disturbance $\omega$ and noise $\nu$ will be detailed further, and we denote their total contribution as $\eta(t) = C\nu(t) + D\omega(t)$.
 
@@
 
-Denote $\eta(t) = C\nu(t) + D\omega(t)$. By simply substituting the expression of $y_n$ into \eqref{eq:vector_rls}, we obtain the regression error:
+By simply substituting the expression of $y_n$ into \eqref{eq:vector_rls}, we obtain the regression error:
 \begin{align}
@@
 \label{assumpt:bounded-noise}
-The noise $\eta(t) = C\nu(t) + D\omega(t)$ is bounded.
+The noise $\eta(t)$ is bounded.
 \[\|\eta\|_\infty < \infty\]
@@
 
-Then, 
-\begin{align}
+With Hölder inequality, we obtain a confidence region $\cC$ defined by a $L_1$-ball, i.e. a polytope with $2d$ vertices:
+\begin{equation}
+\begin{split}
 \label{eq:bounded-noise-polytope}
-\|\theta_{N,\lambda} - \theta\|_1 \leq &\|G_{N, \lambda}^{-1}\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\|_1\|\eta\|_\infty \\
-&+ \lambda\|G_{N, \lambda}^{-1}\|_1\|\theta\|_\infty \nonumber
-\end{align}
-
-This $L_1$-ball is a polytope with $2d$ vertices, denoted $\cP$.
+\|\theta_{N,\lambda} - \theta\|_1 \leq {} &\|G_{N, \lambda}^{-1}\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\|_1\|\eta\|_\infty \\
+&+ \lambda\|G_{N, \lambda}^{-1}\|_1\|\theta\|_\infty
+\end{split}
+\end{equation}
 

### 2020-01-15 main.tex
Updates from Overleaf

@@
 $ where $\nu(t)\in\Real^r$ is a measurement noise and $C\in\Real^{p\times r}$ is known.
-For better readability, we will actually denote the measurement as:
-\begin{equation}
-\label{eq:measurement}
-    y(t) = \dot{x}(t) - A_0 x(t) - Bu(t) + C\nu(t)
-\end{equation}
-which is possible since the nominal dynamics $A_0$, thet state $x(t)$ and the control $u(t)$ are known.
 Assumptions over the disturbance $\omega$ and noise $\nu$ will be detailed further, and we denote their total contribution as $\eta(t) = C\nu(t) + D\omega(t)$.
@@
 \paragraph{Objective}
-Having observed at times a history of transitions $\cD = \{(x_n, u_n, y_n)\}_{n\in[N]}$, and given a confidence level $\delta\in(0, 1)$, our goal is to find a confidence region $\cC_\delta$ as tight as possible and such that it holds that:
+Having observed at times a history of transitions $\cD_{[N]} = \{(x_n, u_n, y_n)\}_{n\in[N]}$, and given a confidence level $\delta\in(0, 1)$, our goal is to find a confidence region $\cC_{[N],\delta}$ as tight as possible and such that it holds that:
 \begin{align}
-\probability{A(\theta)\in \cC_\delta} \geq 1-\delta
+\probability{A(\theta)\in \cC_{[N],\delta}} \geq 1-\delta
 \label{eq:polytope}
@@
 \begin{equation}
-    A(\theta) = A_0 + %\theta^\transp \phi \eqdef A_0 + 
+    A(\theta) = A + %\theta^\transp \phi \eqdef A + 
     \sum_{i=1}^d \theta_i\phi_i
@@
 
-\paragraph{Regularised least square} Since we expect that $\Phi_n$ may have zero-coordinates during possibly long time intervals (i.e.
-some features are not always active), we consider the weighted $L_2$-regularised regression problem with weights  $\Sigma_p\in\Real^{p\times p}$ and parameter $\lambda\in\Real^+_*$:
+For readability, we denote the noisy measurement of $\dot{x}$ as:
+\begin{equation}
+\label{eq:measurement}
+    y(t) = \dot{x}(t) + C\nu(t) - A x(t) - Bu(t)
+\end{equation}
+which is possible since the nominal dynamics $A$, the state $x(t)$ and the control $u(t)$ are known.
+Thus, we obtain the system
+\[
+y_n = \Phi_n\theta + \eta_n
+\]
+
+\paragraph{Regularised least square} We consider the weighted $L_2$-regularised regression problem with weights  $\Sigma_p\in\Real^{p\times p}$ and parameter $\lambda\in\Real^+_*$:
 
@@
 
-\begin{theorem}[Regularised solution]
-\label{thm:regularized_solution}
+\begin{proposition}[Regularised solution]
+\label{prop:regularized_solution}
 The solution to \eqref{eq:regression_min} is:
@@
 \end{equation*}
-\end{theorem}
+\end{proposition}
 
@@
 
-With Hölder inequality, we obtain a confidence region $\cC$ defined by a $L_1$-ball, i.e. a polytope with $2d$ vertices:
+By Hölder inequality, we obtain a confidence region $\cC_\delta$ defined by a $L_1$-ball, i.e. a polytope with $2d$ vertices:
 \begin{equation}
@@
     \label{eq:confidence-ellipsoid}
-    \| \theta_{N,\lambda}  - \theta\|_{G_{N,\lambda}} &\leq \sqrt{2\ln \left(\frac{\det(G_{N,\lambda})^{1/2}}{\delta\det(\lambda I_d)^{1/2}}\right)}
+    \| \theta_{N,\lambda}  - \theta\|_{G_{N,\lambda}} \leq \beta_N(\delta),
+\end{align}
+with
+\begin{equation}
+    \beta_N(\delta)\eqdef \sqrt{2\ln \left(\frac{\det(G_{N,\lambda})^{1/2}}{\delta\det(\lambda I_d)^{1/2}}\right)}
      + \lambda^{1/2}\|\theta\|_2.
-\end{align}
+\end{equation}
 \label{thm:confidence_ellipsoid}
-
 \end{theorem}
 
-\begin{lemma}[Confidence polytope]
-\label{lem:confidence_polytope}
-We can enclose the confidence ellipsoid $C_\delta$ obtained in $\eqref{eq:confidence-ellipsoid}$ within a polytope $P_\delta$:
-\[\cC_\delta \subset \cP_\delta\]
-where $\cP_\delta$ can be written as:
-\begin{equation}
-     \cP_\delta = \left\{ A_{0}+\sum_{i=1}^{2^d}\lambda_{i}\Delta A_{i}: \lambda\in[0, 1]^{2^d},  \sum_{i=1}^{2^d}\lambda_{i}=1\right\}.
-\end{equation}
-with 
-\begin{align*}
-    &G_{N,\lambda}^{-1} = PDP^{-1}\\
-    &h_k \text{ is the }k^\text{th}\text{ element of }\{-1,1\}^d\text{, for } k\in[2^d]\\
-    &\Delta\theta_k = C_{N,\lambda,\delta}^{1/2} P^{-1}D^{-1/2} h_k \\
-    &A_0 = \theta_{N,\lambda}^\transp\Phi\\
-    &\Delta A_k = \Delta\theta_k^\transp\Phi
-\end{align*}
-This conversion is illustrated in \autoref{fig:ellipsoid_to_polytope}.
-\end{lemma}
+We can enclose this confidence ellipsoid $\eqref{eq:confidence-ellipsoid}$ into a polytope $C_\delta$.
+For simplicity, we present here a very simple but coarse strategy: bound the ellipsoid by its enclosing sphere, and the sphere by its enclosing hypercube:
+\begin{align}
+    \label{eq:generic-polytope}
+     &\cC_\delta = \left\{ A_{0}+\sum_{i=1}^{2^d}\lambda_{i}\Delta A_{i}: \lambda\in[0, 1]^{2^d},  \sum_{i=1}^{2^d}\lambda_{i}=1\right\},\\
+     &A_0 = A + \theta_{N,\lambda}^\transp\phi, \quad\Delta A_{i} = h_i \sqrt{\frac{\beta_N(\delta)}{\lambda_{\max}(G_{N,\lambda})}}
+\end{align}
 
-\begin{figure}
-    \centering
-    \includegraphics[trim={3.8cm, 2cm, 5cm, 3.8cm}, clip, width=0.4\textwidth]{img/ellipsoid_to_polytope}
-    \caption{From the confidence ellipsoid $\cC_\delta$ to its enclosing polytope $\cP_\delta$}
-    \label{fig:ellipsoid_to_polytope}
-\end{figure}
+Another strategy presented in \autoref{sec:tight-polytope} produces a much tighter polytope, at the price of an increased computational cost required by the diagonalization of $G_{N,\lambda}$.
 
@@
 
-Moreover, the stability of the predictor can be assessed with a sufficient condition in form of an LMI.
+% Moreover, the stability of the predictor can be assessed with a sufficient condition in form of an LMI.
 % if there exist diagonal matrices $P$, $Q$, $Q_{+}$, $Q_{-}$, $Z_{+}$, $Z_{-}$, $\Psi_{+}$, $\Psi_{-}$, $\Psi$, $\Gamma\in\Real^{2n\times 2n}$ such that the following LMIs are satisfied:
@@
 
+We consider interval prediction rather than zonotope prediction for instance, for the sake of simplicity of implementation and computational efficiency.
+Among interval prediction algorithms, this predictor tends to produce tighter and more stable predictions than other candidates, and its stability can be assessed simply in terms of LMI.
+
 % \begin{example*}
@@
 
-We consider the robust control objective $v^r$:
+At time $N$, we denote the vector of future controls as $\bu = (u_{N+1},u_{N+2},\cdots)$ and future perturbations as $\bw = (\omega_N, \omega_{N+1},\cdots)$.
+
+We consider the robust control objective $V^r$:
 
@@
 \label{eq:robust-control}
-\max_\bu \underbrace{\min_{A(\theta) \in \cP} \left[\sum_{t=0}^\infty \gamma^t r(x(t))\condbar u_t, \omega(t)\right]}_{v^r(\bu)}
+\max_\bu \underbrace{\min_{\substack{A(\theta) \in \cP \\ \bw\in[\underline{\omega},\overline{\omega}]^\Natural}} \left[\sum_{t=0}^\infty \gamma^t r(x(t,\bu,\bw))\right]}_{V^r(\bu)}
 \end{equation}
@@
 \begin{definition}[Surrogate objective]
-We approximate the robust objective $v^r$ in \eqref{eq:robust-control} by replacing the true reachability set by its interval prediction $[\underline{x}(t), \overline{x}(t)]$ based on the polytopic approximation $\cP_\delta$ of $A(\Theta)$:
+We approximate the robust objective $V^r$ in \eqref{eq:robust-control} by replacing the true reachability set by its interval prediction $[\underline{x}(t), \overline{x}(t)]$ based on the dynamics confidence region $\cC_\delta$:
 
-\begin{equation}
-\hat{v}^r(\bu) \eqdef \sum_{t=0}^\infty \gamma^t \min_{x\in[\underline{x}(t, \bu), \overline{x}(t, \bu)]}  R(x)
-\end{equation}
+\begin{align}
+\underline{R}(t,\bu) \eqdef \min_{x\in[\underline{x}(t, \bu), \overline{x}(t, \bu)]}  R(x) \\
+\hat{V}^r(\bu) \eqdef \sum_{t=0}^\infty \gamma^t \underline{R}(t,\bu) \label{eq:surrogate_objective}
+\end{align}
 where $\underline{x}(t, \bu), \overline{x}(t, \bu)$ follow the dynamics defined in \eqref{eq:interval_predictor}.
@@
 \label{prop:lower-bound}
-With high probability, the surrogate objective $\hat{v}^r$ is a lower bound of the true objective $v^r$:
+With high probability, the surrogate objective $\hat{V}^r$ is a lower bound of the true objective $V^r$:
 
 \begin{equation}
-\hat{v}^r(\bu) \leq v^r(\bu)
+\hat{V}^r(\bu) \leq V^r(\bu)
 \end{equation}
-
-If we assume that $R$ is $L$-Lipschitz, then we can also bound the approximation error:
-\begin{equation*}
-     v^r(\bu) - \hat{v}^r(\bu) \leq L\sum_{t=0}^\infty \gamma^t \mu([\underline{x}_N(t),\overline{x}_N(t)])
-\end{equation*}
 \end{proposition}
@@
 
-\section{Multi-model Estimation and Control}
+\begin{proposition}
+\label{prop:control-error}
+If we assume that the reward function $R$ is lipschitz, then we can bound the approximation error:
+\begin{equation*}
+     V^r(\bu) - \hat{V}^r(\bu) = \cO\left(\frac{1}{\sqrt{N}}\right)
+\end{equation*}
+\end{proposition}
 
-What if our system dynamics \eqref{eq:dynamics} or linear parametrisation assumption \ref{assumpt:linear_param} are wrong?
+\begin{algorithm}[tb]
+   \caption{Robust Estimation, Prediction and Control}
+   \label{alg:full}
+\begin{algorithmic}
+   \STATE {\bfseries Input:} confidence level $\delta$
+   \FOR{$N = 1,2,3,\dots$} 
+   \STATE Compute the dynamics confidence region $\cC_{[N],\delta}$ with \textsc{Model Estimation} \eqref{eq:generic-polytope} on $\cD_{[N]}$.
+   \FOR{planning steps $[T]$}
+   \STATE Get the tree node $\bu^t$ to expand with \textsc{Pessimistic Planning}  \eqref{eq:surrogate_objective} using $[\underline{x}(t,\bu), \overline{x}(t,\bu)]$.
+   \STATE For each child transition, simulate $[\underline{x}, \overline{x}]$ with \textsc{Interval Prediction} \eqref{eq:interval_predictor} using $\cC_{[N],\delta}$.
+   \ENDFOR
+   \STATE Execute the first recommended control $u_N$, and add the observed transition $(x_N, u_N, \dot{x}_N)$ to $\cD_{[N+1]}$.
+   \ENDFOR
 
-\subsection{Model adequacy}
+\end{algorithmic}
+\end{algorithm}
+
+\section{Multi-model Extension}
+
+The procedure we developed in sections relies on several modelling assumptions which can be quite restrictive, such as the system dynamics \eqref{eq:dynamics} or its linear parametrisation in \autoref{assumpt:linear_param}.
+But what if they are wrong?
+
+\paragraph{Model adequacy}
 
@@
 
-The simple regret of the action $a$ returned by Algorithm \ref{algo:drop} after $n$ rounds is defined as:
-\begin{equation}
-\mathcal{R}_n = v^r - v_a^r
-\end{equation}
-We will say that $\mathcal{R}_n=O(\varepsilon)$ for some $\varepsilon>0$ if there exist $\rho>0$ and $n_0>0$ such that $\mathcal{R}_n\leq\rho\varepsilon$ for all $n\geq n_0$.
-A node $i\in\mathcal{T}$ is said to be $\epsilon$-optimal, in a robust sense, if and only if $v_i^r \geq v^r - \epsilon$ for some $\epsilon > 0$.
+We introduce a measure of the problem difficulty: TODO: Definition of $\kappa\in [1, K]$
+A node $i\in\mathcal{T}$ is said to be $\epsilon$-optimal, in a robust sense, if and only if $V_i^r \geq V^r - \epsilon$ for some $\epsilon > 0$.
 The proportion of $\epsilon$-optimal nodes at depth $d$ is then defined as $p_d(\epsilon) = |i \in \mathcal{A}^d$ s.t $i$ is $\epsilon$-optimal$|/K^d$.
 Further we will assume that for the graph $\mathcal{T}$ the following hypothesis is satisfied:
-\begin{assumption}[Proportion of near-optimal nodes]
-\label{assumpt:beta}
-There exist $\beta\in[0, \frac{\log K}{\log 1/\gamma}]$, $c > 0$ and $d_0 > 0$ such that $p_d(\epsilon)\leq c\epsilon^\beta$ for all $\epsilon > 0$ and $d\geq d_0$.
-\end{assumption}
 
@@
 \label{theorem:drop-regret}
-Let $\kappa = K\gamma^\beta \in [1, K]$. Then the simple regret of Algorithm \ref{algo:drop} is:
+The simple regret of Algorithm \ref{algo:drop} after $T$ iterations is:
 
@@
 \text{If } \kappa>1,\qquad 
-\mathcal{R}_n = O\left(n^{-\frac{\log 1/\gamma}{\log \kappa}}\right)
+v^r - v^r_{a_T} = O\left(T^{-\frac{\log 1/\gamma}{\log \kappa}}\right)
 \end{equation}
@@
 \text{If }\kappa=1,\qquad
-\mathcal{R}_n = O\left(\gamma^{\frac{(1-\gamma)^\beta}{c}n}\right)
+v^r - v^r_{a_T} = O\left(\gamma^{\frac{(1-\gamma)^\beta}{c}T}\right)
 \end{equation}
@@
 
-\subsection{Proof of \autoref{thm:regularized_solution}}
+\subsection{Proof of \autoref{prop:regularized_solution}}
 
@@
 
-\subsection{Proof of \autoref{lem:confidence_polytope}}
-
-\begin{proof}
-The ellipsoid in \eqref{eq:confidence-ellipsoid} is described by:
-\begin{align*}
-    \theta\in\cC_\delta &\implies
-    (\theta-\theta_{N,\lambda})^\transp G_{N,\lambda}^{-1}(\theta-\theta_{N,\lambda}) \leq C_{N,\lambda,\delta}\\
-    &\implies (\theta'-\theta'_{N,\lambda})^\transp D (\theta'-\theta'_{N,\lambda}) \leq C_{N,\lambda,\delta}\\
-    &\implies \sum_{i=1}^d D_{i,i}(\theta'_i-\theta'_{N,\lambda,i})^2\leq C_{N,\lambda,\delta}\\
-    &\implies\forall i, |\theta'_i-\theta'_{N,\lambda,i}|\leq C_{N,\lambda,\delta}^{1/2}D_{i,i}^{-1/2}
-\end{align*}
-This describes a $\Real^d$ box containing $\theta' = P\theta$, whose $k^\text{th}$ vertex is represented by $\theta_{N,\lambda}' + C_{N,\lambda,\delta}^{1/2}D^{-1/2} h_k$.
-We obtain the corresponding box on $\theta$ by transforming each vertex of the box with $P^{-1}$.
-\end{proof}
-
 \subsection{Proof of \autoref{prop:lower-bound}}
@@
 \begin{proof}
-We have that $A(\theta) \in \cP$ with probability $1-\delta$.
+We have that $A(\theta) \in \cC_{[N],\delta}$ with probability $1-\delta$.
 Whenever it is the case, we have by \autoref{thm:predictor} that the inclusion property \eqref{eq:interval_property} is verified by the interval predictor \eqref{eq:interval_predictor} for all $\omega(t)\in[\underline{\omega}(t), \overline{\omega}(t)]$.
@@
 
+\subsection{Tighter conversion form ellipsoid to polytope}
+\label{sec:tight-polytope}
+\begin{lemma}[Confidence polytope]
+\label{lem:tight_polytope}
+We can enclose the confidence ellipsoid obtained in $\eqref{eq:confidence-ellipsoid}$ within a polytope $C_\delta$:
+\begin{equation}
+     \cC_\delta = \left\{ A_{1}+\sum_{i=1}^{2^d}\lambda_{i}\Delta A_{i}: \lambda\in[0, 1]^{2^d},  \sum_{i=1}^{2^d}\lambda_{i}=1\right\}.
+\end{equation}
+with 
+\begin{align*}
+    &h_k \text{ is the }k^\text{th}\text{ element of }\{-1,1\}^d\text{ for } k\in[2^d],\\
+    &G_{N,\lambda}^{-1} = PDP^{-1}, \quad \Delta\theta_k = C_{N,\lambda,\delta}^{1/2} P^{-1}D^{-1/2} h_k, \\
+    &A_0 = A + \theta_{N,\lambda}^\transp\Phi, \quad \Delta A_k = \Delta\theta_k^\transp\Phi.
+\end{align*}
+This conversion is illustrated in \autoref{fig:ellipsoid_to_polytope}.
+\end{lemma}
+
+\begin{proof}
+The ellipsoid in \eqref{eq:confidence-ellipsoid} is described by:
+\begin{align*}
+    \theta\in\cC_\delta &\implies
+    (\theta-\theta_{N,\lambda})^\transp G_{N,\lambda}^{-1}(\theta-\theta_{N,\lambda}) \leq C_{N,\lambda,\delta}\\
+    &\implies (\theta'-\theta'_{N,\lambda})^\transp D (\theta'-\theta'_{N,\lambda}) \leq C_{N,\lambda,\delta}\\
+    &\implies \sum_{i=1}^d D_{i,i}(\theta'_i-\theta'_{N,\lambda,i})^2\leq C_{N,\lambda,\delta}\\
+    &\implies\forall i, |\theta'_i-\theta'_{N,\lambda,i}|\leq C_{N,\lambda,\delta}^{1/2}D_{i,i}^{-1/2}
+\end{align*}
+This describes a $\Real^d$ box containing $\theta' = P\theta$, whose $k^\text{th}$ vertex is represented by $\theta_{N,\lambda}' + C_{N,\lambda,\delta}^{1/2}D^{-1/2} h_k$.
+We obtain the corresponding box on $\theta$ by transforming each vertex of the box with $P^{-1}$.
+\end{proof}
+
+\begin{figure}
+    \centering
+    \includegraphics[trim={3.8cm, 2cm, 5cm, 3.8cm}, clip, width=0.4\textwidth]{img/ellipsoid_to_polytope}
+    \caption{From the confidence ellipsoid $\cC_\delta$ to its enclosing polytope $\cP_\delta$}
+    \label{fig:ellipsoid_to_polytope}
+\end{figure}
+
 \subsection{Change of coordinates}

### 2020-01-15 main.tex
Multi model extension

@@
 
+\label{sec:estimation}
+
 \paragraph{Objective}
@@
 
+\label{sec:prediction}
+
 In this section, we assume that we found a high-confidence polytope that verifies \eqref{eq:polytope} with probability $1-\delta$.
@@
 
+\label{sec:control}
+
 At time $N$, we denote the vector of future controls as $\bu = (u_{N+1},u_{N+2},\cdots)$ and future perturbations as $\bw = (\omega_N, \omega_{N+1},\cdots)$.
@@
 
-The procedure we developed in sections relies on several modelling assumptions which can be quite restrictive, such as the system dynamics \eqref{eq:dynamics} or its linear parametrisation in \autoref{assumpt:linear_param}.
+The procedure we developed in sections \ref{sec:estimation}, \ref{sec:prediction} and \ref{sec:control} relies on several modelling assumptions, such as the system dynamics \eqref{eq:dynamics} or \autoref{assumpt:linear_param}.
 But what if they are wrong?
@@
 
-We can test the model adequacy, and eventually reject it.
+One of the major benefits of using the family of linear models compared to richer classes is that it enables to measure empirically the adequacy of the modelling assumptions to capture the observed signal,  and thus to raise an alert when the adequacy is too low.
 
+We define the model adequacy for an observation $y$ at point $x$ of the modelling assumptions $(A, \phi)$ trained on history $\cD$.
+A value of 1 indicates no mismatch, while a value of 0 indicates a strong mismatch.
+
+This is especially relevant in the context of model selection or aggregation.
 This suggest using multiple models with different sets of features.

### 2020-01-16 main.tex
Updates from Overleaf

--- 2020-01-15 main.tex
@@
 \begin{cases}
-\min_{m\in[1, M]} \sum_{t=0}^{d-1} \gamma^t r_t^m  + \frac{\gamma^d}{1-\gamma} &\text{if } i \in \mathcal{L}_n \text{ ;}\\
-\max_{a\in\mathcal{A}} b_{ia}^r(n) & \text{if } i \in \mathcal{T}_n \setminus \mathcal{L}_n 
+\min_{m\in[1, M]} \sum_{t=0}^{d-1} \gamma^t R_t^m  + \frac{\gamma^d}{1-\gamma} &\text{if } i \in \mathcal{L}_n \text{ ;}\\
+\max_{a\in\mathcal{A}} B_{ia}^r(n) & \text{if } i \in \mathcal{T}_n \setminus \mathcal{L}_n 
 \end{cases}
 \end{equation}
-where $r_t^m$ is the reward obtained at step $t$ by following $i$ with dynamics $f^m$.
+where $R_t^m$ is the reward obtained at step $t$ by following $i$ with dynamics $f^m$.
 \end{definition}
@@
 \includegraphics[width=0.4\linewidth]{img/robust-control-tree}
-\caption{The computation of robust b-values in Algorithm \ref{algo:drop}.
+\caption{The computation of robust B-values in Algorithm \ref{algo:drop}.
 The simulation of trajectories for every dynamics model $f^m$ is represented as stacked versions of the expanded tree $\mathcal{T}_n$.}
@@
 
-We introduce a measure of the problem difficulty: TODO: Definition of $\kappa\in [1, K]$
-A node $i\in\mathcal{T}$ is said to be $\epsilon$-optimal, in a robust sense, if and only if $V_i^r \geq V^r - \epsilon$ for some $\epsilon > 0$.
-The proportion of $\epsilon$-optimal nodes at depth $d$ is then defined as $p_d(\epsilon) = |i \in \mathcal{A}^d$ s.t $i$ is $\epsilon$-optimal$|/K^d$.
-Further we will assume that for the graph $\mathcal{T}$ the following hypothesis is satisfied:
+We express the performance of the planning problem in terms of a measure of the proportion of near-optimal paths:
+\[
+\kappa = \limsup_{h\rightarrow\infty} \left|\left\{a\in A^h: V(a)\geq V - \frac{\gamma^{h+1}}{1-\gamma}\right\}\right|^{1/h}.
+\]
 

### 2020-01-16 main.tex
Abstract

@@
 \begin{abstract}
-
+	We study the adaptive control of a linear system with unknown parameters and arbitrary costs in a critical setting where failures are costly and should be prevented at all time.
+We build on two ideas.
+First, we incorporate prior knowledge of the dynamics in the form of a known structure of uncertainty, that can be tightened as we collect interaction data by building high-confidence regions through least-square regression.
+Second, we act in a cautious way with respect to this uncertainty by formulating a robust objective, that we solve approximately in a prediction-optimisation manner, leveraging tools from interval prediction and tree-based planning.
+Additionally, we relax our modelling assumptions by proposing an extension based on multi-model selection and aggregation.
+The full procedure is designed to produce reasonable and safe behaviour at deployment, get more aggressive with time, and be asymptotically optimal.
+We illustrate it on a practical case of autonomous driving at an intersection.
 \end{abstract}
@@
 
-We would like to control a system in order to maximise an \textit{arbitrary} reward function $R$, e.g.
+We would like to control a system in order to maximise an \textit{arbitrary} bounded reward function $R$, e.g.
 non-convex, non-smooth.
@@
 
-\section{Multi-model Extension}
+\section{Multi-model Aggregation}
 
@@
 
-One of the major benefits of using the family of linear models compared to richer classes is that it enables to measure empirically the adequacy of the modelling assumptions to capture the observed signal,  and thus to raise an alert when the adequacy is too low.
+One of the major benefits of using the family of linear models, compared to richer model classes, is that it enables to measure empirically the adequacy of the modelling assumptions to capture the observed signal, and thus to raise an alert when the adequacy is too low.
 
-We define the model adequacy for an observation $y$ at point $x$ of the modelling assumptions $(A, \phi)$ trained on history $\cD$.
+We define the model adequacy for an observation $y$ at point $x$ of the modelling assumptions $(A, \phi)$ trained on history $\cD$ by:
+\begin{equation*}
+    \alpha(y,x)
+\end{equation*}
 A value of 1 indicates no mismatch, while a value of 0 indicates a strong mismatch.
@@
 
-\begin{definition}[Robust sequence upper bounds] We define an upper-bound for the value of sequences of actions:
+\begin{definition}[Robust sequence upper bounds] We define an upper-bound for the value of a sequences of action $a$:
 \begin{equation}
 \label{eq:robust_sequence_ucb}
-b_i^r(n)  \eqdef
+B_a^r(n)  \eqdef
 \begin{cases}
-\min_{m\in[1, M]} \sum_{t=0}^{d-1} \gamma^t R_t^m  + \frac{\gamma^d}{1-\gamma} &\text{if } i \in \mathcal{L}_n \text{ ;}\\
-\max_{a\in\mathcal{A}} B_{ia}^r(n) & \text{if } i \in \mathcal{T}_n \setminus \mathcal{L}_n 
+\min_{m\in[M]} \sum_{t=0}^{h-1} \gamma^t R_t^m  + \frac{\gamma^h}{1-\gamma} &\text{if } a \text{ is a leaf;}\\
+\max_{b\in\mathcal{A}} B_{ab}^r(n) & \text{else.}
 \end{cases}
 \end{equation}
-where $R_t^m$ is the reward obtained at step $t$ by following $i$ with dynamics $f^m$.
+where $R_t^m$ is the reward obtained at step $t$ by following $a$ with dynamics $f^m$.
 \end{definition}

### 2020-01-16 main.tex
Updates from Overleaf

@@
 
+Robust optimization has been studied in the context of finite Markov Decision Processes (MDP) with uncertain parameters by Iyengar (2005), Nilim and El Ghaoui (2005) and Wiesemann et al.
+(2013).They show that the main results of Dynamic Programming can be extended to their robust counterparts only when the dynamics ambiguity set verifies certain rectangularity properties, which can be seen as an independance assumption:
+
 \section{Problem formulation}
@@
 where $\phi_i\in\Real^{p\times p}$ for all $i\in[d]$. For all $n$, we also denote $\Phi_n = [\phi_1 x_n \cdots \phi_d x_n]\in\Real^{p\times d}$.
+
+We also assume that some bound $S$ over $\|\theta\|_\infty$ is known.
 \end{assumption}
@@
 
-Depending on the assumption we have over the noise $\eta_n$ and the true parameter $\theta$, we can bound this error in different ways.
+Depending on the assumption we have over the noise $\eta_n$, we can bound this error in different ways.
 
@@
 \label{assumpt:bounded-noise}
-The noise $\eta(t)$ is bounded.
-\[\|\eta\|_\infty < \infty\]
+The noise $\eta(t)$ is bounded
+\[
+\|\eta\|_\infty < \infty
+\]
 \end{assumption}
@@
 \|\theta_{N,\lambda} - \theta\|_1 \leq {} &\|G_{N, \lambda}^{-1}\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\|_1\|\eta\|_\infty \\
-&+ \lambda\|G_{N, \lambda}^{-1}\|_1\|\theta\|_\infty
+&+ \lambda\|G_{N, \lambda}^{-1}\|_1 S
 \end{split}
@@
 \begin{theorem}[Confidence ellipsoid]
+\label{thm:confidence_ellipsoid}
 Under \autoref{assumpt:gaussian-noise}, it holds with probability at least $1-\delta$ that
@@
     \beta_N(\delta)\eqdef \sqrt{2\ln \left(\frac{\det(G_{N,\lambda})^{1/2}}{\delta\det(\lambda I_d)^{1/2}}\right)}
-     + \lambda^{1/2}\|\theta\|_2.
+     + (\lambda d)^{1/2}S.
 \end{equation}
-\label{thm:confidence_ellipsoid}
 \end{theorem}
@@
 
+From now on, we consider that we reached time $N$, which is now fixed, and that a confidence region $\cC_{[N],\delta}$ was obtained with data $\cD$ collected so far.
+The following sections tackle the optimisation of the robust control objective:
+\begin{equation}
+\label{eq:robust-control}
+\max_\bu \underbrace{\min_{\substack{A(\theta) \in \cP \\ \bw\in[\underline{\omega},\overline{\omega}]^\Natural}} \left[\sum_{t=0}^\infty \gamma^t r(x(t,\bu,\bw))\right]}_{V^r(\bu)}
+\end{equation}
+where $\bu = (u_{N+1},u_{N+2},\cdots)$ and $\bw = (\omega_N, \omega_{N+1},\cdots)$ are the sequences of future controls and perturbations, respectively.
+
 \section{State Prediction}
@@
 
-In this section, we assume that we found a high-confidence polytope that verifies \eqref{eq:polytope} with probability $1-\delta$.
-
-The objective of the prediction procedure, as illustrated in \autoref{fig:interval-hull} is to design an \emph{interval predictor} for the system \eqref{eq:dynamics}, which takes the information on the observed current state ${x}({0})$, the admissible bounds on the perturbation $[\underline{\omega}(t),\overline{\omega}(t)]$, and the model polytope $\cP_\delta$, and verifies the inclusion property:
+The objective of this section, as illustrated in \autoref{fig:interval-hull} is to  derive a \emph{set predictor} for the system \eqref{eq:dynamics}, which takes the information on the observed current state ${x}({0})$, some admissible bounds on the perturbation $[\underline{\omega}(t),\overline{\omega}(t)]$, and a confidence region $\cC_\delta$ in the form \eqref{eq:generic-polytope} containing $A(\theta)$; and verifies the inclusion property:
 \begin{equation}
@@
 
-In order to use the interval predictor from \citep{leurent2019interval}, we need an additional assumption.
-
-% \begin{lemma}[Similarity Transformation]
-% \label{lem:metzler} Let $D\in\Xi\subset\Real^{n\times n}$ be a matrix variable satisfying the interval constraints $\Xi=\{D\in\Real^{n\times n}:\,D_{a}-\Delta\le D\le D_{a}+\Delta\}$ for some $D_{a}^{\text{T}}=D_{a}\in\Real^{n\times n}$ and $\Delta\in\Real_{+}^{n\times n}$.
-If for some constant $\mu\in\Real_{+}$ and a diagonal matrix $\Upsilon\in\Real^{n\times n}$ the Metzler matrix $Y=\mu E_{n\times n}-\Upsilon$ has the same eigenvalues as the matrix $D_{a}$, then there is an orthogonal matrix $S\in\Real^{n\times n}$ such that the matrices $S^{\text{T}}DS$ are Metzler for all $D\in\Xi$ provided that $\mu>n||\Delta||_{max}$.\textup{ }
-% \end{lemma}
+We consider interval prediction rather than zonotope prediction for instance, for the sake of simplicity of implementation and computational efficiency.
+Among interval prediction algorithms, we consider the algorithm from \citep{leurent2019interval}, which produces tighter and more stable predictions than other baselines, and whose stability can be assessed simply in terms of LMI.
+The price to pay for this improved stability is the requirement of an additional assumption:
 
 \begin{assumption}
-There exists an orthogonal $S\in\Real^{d\times d}$ such that $S^\transp A_0 S$ is Metzler.
+There exists an orthogonal matrix $P\in\Real^{d\times d}$ such that $P^\transp A_0 P$ is Metzler, that is, all non-diagonal coefficients are non-negative.
 \end{assumption}
-
-This for instance the case when $A_0$ is diagonalizable. Another way ... the similarity transformation of \citep{Efimov_a2013}.
+In practice, this assumption is often verified.
+It is for instance the case whenever $A_0$ is diagonalizable.
+The similarity transformation of \citep{Efimov_a2013} provides a method to compute such $P$ whenever there exist $C_1,C_2$ which make $A(\theta)$ and $A_0$ is observable.
+Note that similar requirements involving the controllability of $A_0$ exist the literature of the LQ setting, see e.g.
+\citep{abbasi-yadkori11a,abeille18a}.
+Under this assumption, without loss of generality up to a change of basis $x\rightarrow P^{-1}x$ that we do not write for the sake of readability, we can consider that $A_0$ itself is Metzler.
 
@@
 
-We consider interval prediction rather than zonotope prediction for instance, for the sake of simplicity of implementation and computational efficiency.
-Among interval prediction algorithms, this predictor tends to produce tighter and more stable predictions than other candidates, and its stability can be assessed simply in terms of LMI.
-
 % \begin{example*}
@@
 
-At time $N$, we denote the vector of future controls as $\bu = (u_{N+1},u_{N+2},\cdots)$ and future perturbations as $\bw = (\omega_N, \omega_{N+1},\cdots)$.
-
-We consider the robust control objective $V^r$:
-
-\begin{equation}
-\label{eq:robust-control}
-\max_\bu \underbrace{\min_{\substack{A(\theta) \in \cP \\ \bw\in[\underline{\omega},\overline{\omega}]^\Natural}} \left[\sum_{t=0}^\infty \gamma^t r(x(t,\bu,\bw))\right]}_{V^r(\bu)}
-\end{equation}
-
 \begin{definition}[Surrogate objective]
@@
 This does not amount to defining a pessimistic reward-function $\underline{R}$, since the worst case is assessed over the whole trajectory being optimized, and not at the level of a local transition.
-It cannot be precomputed prior to the control optimization procedure, it needs to be done jointly.
+In particular, it cannot be precomputed prior to the control optimization procedure, it needs to be done jointly.
 
@@
 \label{prop:control-error}
-If we assume that the reward function $R$ is lipschitz, then we can bound the approximation error:
+If we assume that the reward function $R$ is lipschitz, then the approximation error is upper-bounded by:
 \begin{equation*}
@@
 
-The procedure we developed in sections \ref{sec:estimation}, \ref{sec:prediction} and \ref{sec:control} relies on several modelling assumptions, such as the system dynamics \eqref{eq:dynamics} or \autoref{assumpt:linear_param}.
+The procedure we developed in sections \ref{sec:estimation}, \ref{sec:prediction} and \ref{sec:control} relies on restrictive modelling assumptions, such as the linear dynamics \eqref{eq:dynamics} or \autoref{assumpt:linear_param}.
 But what if they are wrong?
@@
 
-One of the major benefits of using the family of linear models, compared to richer model classes, is that it enables to measure empirically the adequacy of the modelling assumptions to capture the observed signal, and thus to raise an alert when the adequacy is too low.
+In the case of bounded noise, model adequacy is simply measured by the violation of
 
-We define the model adequacy for an observation $y$ at point $x$ of the modelling assumptions $(A, \phi)$ trained on history $\cD$ by:
+One of the major benefits of using the family of linear models, compared to richer model classes, is that it enables to measure the adequacy of the modelling assumptions to the observations.
+
+Following \citep{maillard:hal-01349727}, we define the model adequacy for an observation $x(t), u(t), \dot{x}(t)$ of the modelling assumptions $(A, \phi)$ trained on history $\cD_{[N]}$ by:
 \begin{equation*}
-    \alpha(y,x)
+    \alpha(x(t), u(t), \dot{x}(t)) = \sup_\delta \argmin_{\delta\in(0,1)} d\left(\dot{x}(t), \cC_{[N],\delta}(x(t), u(t))\right)
 \end{equation*}
-A value of 1 indicates no mismatch, while a value of 0 indicates a strong mismatch.
+where $d(\dot x,\cC(x,u)) = \inf_{\hat{A}\in\cC} \left\|\hat{A}x + Bu - \dot{x}\right\|^2 + \|\eta\|_\infty^2$.
+An adequacy of $0$ indicates a strong match of the assumptions, while an adequacy of $1$ indicates a strong mismatch. The
 
-This is especially relevant in the context of model selection or aggregation.
+This metric gets useful in the context of model selection and aggregation: 
 This suggest using multiple models with different sets of features.
 
-\subsection{Robust control with Discrete Ambiguity}
+\subsection{Robust aggregation}
+
+We temporarily ignore the parametric uncertainty over $\theta$ to simply consider several known candidate dynamics models.
 
 \begin{assumption}[Multi-model ambiguity]
+\label{assumpt:multi-model-ambiguity}
 Assume that the true dynamics $f$ lies within a finite set of candidate models $f^1, \cdots, f^M$.
@@
 \end{equation}
+\end{assumption}
+We want to adapt our planning algorithm in order to aggregate these concurrent hypotheses in a robust fashion, i.e. maximise a robust objective with discrete ambiguity:
+\[
+V^r = \max_{\bu}\min_{m\in[M]} \sum_{t=1}^\infty \gamma^t R_t^m
+\]
+where $R_t^m$ is the reward obtain by following the sequence $\bu$ up to step $t$ under the dynamics $f^m$.
 
-We temporarily ignore the parametric uncertainty $\theta\in\Theta$ to only consider known deterministic models.
-\end{assumption}
+The traditional robust optimization procedures do not apply: Robust MDP: only with finite states (here continuous), and based on rectangular ambiguity.
+$\cH_\infty$ control also concern linear dynamics (which is not required under \autoref{assumpt:multi-model-ambiguity}) and .
 
@@
 \begin{align*}
-    M_t^z = \exp{\left(\sum_{s=1}^t z^\transp \Phi_s^\transp \Sigma_p^{-1} \eta_s - \frac{1}{2} (\Phi_s z)^\transp\Sigma_p^{-1}(\Phi_s z) \right)} = \prod_{s=1}^{t} D_s^z
+    M_t^z &= \exp{\left(\sum_{s=1}^t z^\transp \Phi_s^\transp \Sigma_p^{-1} \eta_s - \frac{1}{2} (\Phi_s z)^\transp\Sigma_p^{-1}(\Phi_s z) \right)} \\
+    &= \prod_{s=1}^{t} D_s^z
 \end{align*}
@@
 Showing that $(M_t^z)_{t=1}^\infty$ is indeed a supermartingale and in fact $\expectedvalue[M_t^z]\leq 1$.
-I then follows by Doob's upcrossing lemma for super-martnigales that $M_\infty^z = \lim_{t\to\infty} M_t^z$ is almost surely well-defined, ans so is $M_\tau^z$ for any random stopping time $\tau$.
+It then follows by Doob's upcrossing lemma for supermartingale that $M_\infty^z = \lim_{t\to\infty} M_t^z$ is almost surely well-defined, and so is $M_\tau^z$ for any random stopping time $\tau$.
 
@@
 \end{align*}
-And since $\|\theta\|_{G_{N, \lambda}^{-1}}^2 \leq 1/\lambda_{\min}(G_{N,\lambda})\|\theta\|_2^2 \leq 1/\lambda \|\theta\|_2^2$,
+And since $\|\theta\|_{G_{N, \lambda}^{-1}}^2 \leq 1/\lambda_{\min}(G_{N,\lambda})\|\theta\|_2^2 \leq 1/\lambda \|\theta\|_2^2$ and $\|\theta\|_2^2 \leq d\|\theta\|_\infty^2\leq d S^2$,
 \begin{align*}
     \| \theta_{N,\lambda}  - \theta\|_{G_{N,\lambda}} &\leq \sqrt{2\ln \left(\frac{\det(G_{N,\lambda})^{1/2}}{\delta\det(\lambda I_d)^{1/2}}\right)}
-     + \lambda^{1/2}\|\theta\|_2
+     + (\lambda d)^{1/2}S
 \end{align*}

### 2020-01-17 main.tex
Updates from Overleaf

@@
 Our contributions are the following:
-In Section 2, we structured dynamics.
-In order to derive the confidence regions, we rely on the work of \citet{Abbasi2011} that provide confidence ellipsoid for the regularised least-square estimator.
-However, we need to extend their result by one dimension, with matricial features and vectorial noise where the original setting involved vectorial features and scalar noise.
+In Section 2, structured dynamics.
+We extend the work of \citet{Abbasi2011} that provide a confidence ellipsoid for the regularised least-square estimator in the case of scalar noise and vector features to our setting of vector noise and matrix features.
 
@@
 \[
-\|\eta\|_\infty < \infty
+\|\eta\|_\infty < \infty.
 \]
+In particular, we denote the coefficient-wise bounds over perturbations as $\underline{\omega}(t) \leq \omega(t) \leq \overline{\omega}(t)$.
 \end{assumption}
@@
 
-From now on, we consider that we reached time $N$, which is now fixed, and that a confidence region $\cC_{[N],\delta}$ was obtained with data $\cD$ collected so far.
+\paragraph{Robust objective}
+
+From now on, we consider that we have reached step $N$, and that a confidence region $\cC_{[N],\delta}$ was obtained with data $\cD_{[N]}$ collected so far.
 The following sections tackle the optimisation of the robust control objective:
@@
 \label{eq:robust-control}
-\max_\bu \underbrace{\min_{\substack{A(\theta) \in \cP \\ \bw\in[\underline{\omega},\overline{\omega}]^\Natural}} \left[\sum_{t=0}^\infty \gamma^t r(x(t,\bu,\bw))\right]}_{V^r(\bu)}
+\max_\bu \underbrace{\min_{\substack{A(\theta) \in \cC_{[N],\delta} \\ \bw\in[\underline{\bw},\overline{\bw}]^\Natural}} \left[\sum_{n=1}^\infty \gamma^n R(x_n(\bu,\bw))\right]}_{V^r(\bu)}
 \end{equation}
 where $\bu = (u_{N+1},u_{N+2},\cdots)$ and $\bw = (\omega_N, \omega_{N+1},\cdots)$ are the sequences of future controls and perturbations, respectively.
+Here, we considered the bounded noise setting of \autoref{assumpt:bounded-noise}.
+In the sub-Gaussian noise setting of \autoref{assumpt:gaussian-noise}, we can use the same formulation by deriving high-confidence bounds $\underline{\omega}(t) \leq \omega(t) \leq \overline{\omega}(t)$ that each hold with probability $\delta_t$.
+By choosing $\delta_t = \frac{\delta}{t(t+1)}$, we have that the event $\{\forall t, \underline{\omega}(t) \leq \omega(t) \leq \overline{\omega}(t)\}$ holds with probability $1-\delta$.
 
@@
 
+Limitations: set-based method assumes time-varying uncertainty where we have time-invariant uncertainty: $A(\theta)$ is fixed vs $A(\theta)$ can vary in $\cC_\delta$ at each step.
+Consequence: conservative overset.
+
 \section{Control}
@@
 
-Since all our approximations were conservative, if we manage to find a control sequence such that no \textit{bad event} (e.g.
+The consequence of \autoref{prop:lower-bound} is that since all our approximations were conservative, if we manage to find a control sequence such that no \textit{``bad event''} (e.g.
 a collision) happens with our surrogate objective, then we are guaranteed so they will not happen either when the controls are executed on the true system.
@@
 
-In the case of bounded noise, model adequacy is simply measured by the violation of
+One of the major benefits of using the family of linear models, compared to richer model classes, is that they provide strict conditions allowing to quantify the adequacy of the modelling assumptions to the observations.
 
-One of the major benefits of using the family of linear models, compared to richer model classes, is that it enables to measure the adequacy of the modelling assumptions to the observations.
+TODO: from $\cC$ to confidence regions for $y_{n+1}$.
 
-Following \citep{maillard:hal-01349727}, we define the model adequacy for an observation $x(t), u(t), \dot{x}(t)$ of the modelling assumptions $(A, \phi)$ trained on history $\cD_{[N]}$ by:
-\begin{equation*}
-    \alpha(x(t), u(t), \dot{x}(t)) = \sup_\delta \argmin_{\delta\in(0,1)} d\left(\dot{x}(t), \cC_{[N],\delta}(x(t), u(t))\right)
-\end{equation*}
-where $d(\dot x,\cC(x,u)) = \inf_{\hat{A}\in\cC} \left\|\hat{A}x + Bu - \dot{x}\right\|^2 + \|\eta\|_\infty^2$.
-An adequacy of $0$ indicates a strong match of the assumptions, while an adequacy of $1$ indicates a strong mismatch. The
+% Following \citep{maillard:hal-01349727}, we define the model adequacy for an observation $x(t), u(t), \dot{x}(t)$ of the modelling assumptions $(A, \phi)$ trained on history $\cD_{[N]}$ by:
+% \begin{equation*}
+%     \alpha(x(t), u(t), \dot{x}(t)) = \sup_\delta \argmin_{\delta\in(0,1)} d\left(\dot{x}(t), \cC_{[N],\delta}(x(t), u(t))\right)
+% \end{equation*}
+% where $d(\dot x,\cC(x,u)) = \inf_{\hat{A}\in\cC} \left\|\hat{A}x + Bu - \dot{x}\right\|^2 + \|\eta\|_\infty^2$.
+% An adequacy of $0$ indicates a strong match of the assumptions, while an adequacy of $1$ indicates a strong mismatch. The
 

### 2020-01-17 main.tex
Add parts on planning

@@
 The dynamics of the real system are described in continuous time.
-However, all the sensing and control performed on-board happen in discrete time, with time-step $\dd t$.
-For any variable $z$, we use the subscript notation to refer to these discrete times: $z_n = z(n\dd t)$.
+However, all the sensing and control performed on-board happen in discrete time, with time-step $\tau$.
+For any variable $z$, we use the subscript notation to refer to these discrete times: $z_n = z(n\tau)$.
 
@@
 
-From now on, we consider that we have reached step $N$, and that a confidence region $\cC_{[N],\delta}$ was obtained with data $\cD_{[N]}$ collected so far.
+From now on, we consider that we have reached the time step $n=N$, and that a confidence region $\cC_{[N],\delta}$ was obtained with data $\cD_{[N]}$ collected so far.
 The following sections tackle the optimisation of the robust control objective:
@@
 \label{eq:robust-control}
-\max_\bu \underbrace{\min_{\substack{A(\theta) \in \cC_{[N],\delta} \\ \bw\in[\underline{\bw},\overline{\bw}]^\Natural}} \left[\sum_{n=1}^\infty \gamma^n R(x_n(\bu,\bw))\right]}_{V^r(\bu)}
+\max_\bu \underbrace{\min_{\substack{A(\theta) \in \cC_{[N],\delta} \\ \bw\in[\underline{\bw},\overline{\bw}]^\Natural}} \left[\sum_{n=N+1}^\infty \gamma^n R(x_n(\bu,\bw))\right]}_{V^r(\bu)}
 \end{equation}
@@
 \label{eq:interval_property}
-\underline{x}(t)\leq x(t)\leq\overline{x}(t),\quad\forall t\geq0.
+\underline{x}(t)\leq x(t)\leq\overline{x}(t),\quad\forall t\geq N\tau.
 \end{equation}
@@
  &  & +Bu(t)+D^{+}\overline{\omega}(t)-D^{-}\underline{\omega}(t),\nonumber \\
- &  & \underline{x}(0)=\underline{x}_{0},\;\overline{x}(0)=\overline{x}_{0}\nonumber 
+ &  & \underline{x}(N\tau)=\overline{x}(N\tau)={x}(N\tau)\nonumber 
 \end{eqnarray}
@@
 \begin{align}
-\underline{R}(t,\bu) \eqdef \min_{x\in[\underline{x}(t, \bu), \overline{x}(t, \bu)]}  R(x) \\
-\hat{V}^r(\bu) \eqdef \sum_{t=0}^\infty \gamma^t \underline{R}(t,\bu) \label{eq:surrogate_objective}
+\underline{R}_n(\bu) \eqdef \min_{x\in[\underline{x}_n(\bu), \overline{x}_n(\bu)]}  R(x) \label{eq:pessimistic-rewards} \\
+\hat{V}^r(\bu) \eqdef \sum_{n=N+1}^\infty \gamma^n \underline{R}_n(\bu) \label{eq:surrogate_objective}
 \end{align}
-where $\underline{x}(t, \bu), \overline{x}(t, \bu)$ follow the dynamics defined in \eqref{eq:interval_predictor}.
+where $\underline{x}_n(\bu), \overline{x}_n(\bu)$ follow the dynamics defined in \eqref{eq:interval_predictor}.
 \end{definition}
 
-This does not amount to defining a pessimistic reward-function $\underline{R}$, since the worst case is assessed over the whole trajectory being optimized, and not at the level of a local transition.
-In particular, it cannot be precomputed prior to the control optimization procedure, it needs to be done jointly.
-
-%\begin{algorithm}[tp]
-%  \SetAlgoLined\DontPrintSemicolon
-%  \SetKwFunction{algo}{robust\_control}
-%  \SetKwFunction{proc}{pessimistic\_step}
-%  \SetKwProg{myalg}{Algorithm}{}{}
-%  \myalg{\algo{$s_0$}}{
-%  \While{resources available}
-%  {
-%  Select a candidate action sequence $a$ with a planning algorithm.\;
-%  Sample a pessimistic transition and reward $\underline{r}_t$ using \proc{$\underline{x}(t)$, $\overline{x}(t)$, a}.
-% \;
-% Update the planning algorithm with the sampled pessimistic transition.
-%  }
-%  \KwRet $\argmax_{\bu} \hat{v^r}(\bu)$ \;}{}
-%  \setcounter{AlgoLine}{0}
-%  \SetKwProg{myproc}{Procedure}{}{}
-%  \myproc{\proc{$\underline{x}(t)$, $\overline{x}(t)$, $a$}}{
-%  Integrate \eqref{eq:interval_predictor} over $dt$ with controls $a$ to compute $\underline{x}(t+dt), \overline{x}(t+dt)$\;
-%  Compute worst-case reward $\underline{r}_t = \min_{x\in[\underline{x}(t), \overline{x}(t)]} r(x)$\;
-%  \KwRet $\underline{x}(t+dt), \overline{x}(t+dt), \underline{r}_t$\;}
-%\caption{Interval-based Robust Control}
-%\label{algo:irc}
-%
-%\end{algorithm}
+This does not simply amounts to a change of reward function, since the worst case is assessed over the whole past trajectory being optimized, which means that this pessimistic reward $\underline{R}$ does not respect the Markov assumption.
 
@@
 a collision) happens with our surrogate objective, then we are guaranteed so they will not happen either when the controls are executed on the true system.
+
+In order to optimize our surrogate objective $\hat{V}^r$, we turn to sequential planning algorithms.
+We cannot use the Dynamic Programming techniques because the state space is continuous and the pessimistic rewards are non-markovian.
+Instead, we turn to tree-based planning algorithms which optimize a sequence of actions based on the corresponding sequence of rewards without enumerating the states nor requiring the markovity of the rewards.
+In particular, we use the \texttt{OPD} algorithm \citep{Hren2008} tailored for the case where the sequence of rewards is a deterministic function of the sequence of actions, which is appropriate since both the predictor dynamics \eqref{eq:interval_predictor} and the corresponding pessimistic rewards \eqref{eq:pessimistic-rewards} are deterministic.
+
+\texttt{OPD} progressively builds a tree $\cT_k$ by expanding the leaf $a_k\in\cL_k$ with highest B-value:
+\begin{equation}
+\argmax_{a\in\cL_k} B_a(k), \quad B_a(k) = \sum_{n=0}^{h-1} \underline{R}_n(a) + \frac{\gamma^h}{A-\gamma}.
+\end{equation}
 
@@
 \begin{equation}
-\label{eq:robust_sequence_ucb}
-B_a^r(n)  \eqdef
+\label{eq:robust-b-values}
+B_a^r(k)  \eqdef
 \begin{cases}
-\min_{m\in[M]} \sum_{t=0}^{h-1} \gamma^t R_t^m  + \frac{\gamma^h}{1-\gamma} &\text{if } a \text{ is a leaf;}\\
-\max_{b\in\mathcal{A}} B_{ab}^r(n) & \text{else.}
+\min_{m\in[M]} \sum_{n=0}^{h-1} \gamma^n R_n^m  + \frac{\gamma^h}{1-\gamma} &\text{if } a \text{ is a leaf;}\\
+\max_{b\in\mathcal{A}} B_{ab}^r(k) & \text{else.}
 \end{cases}
@@
 \begin{align*}
-    |x^\transp\theta_{N,\lambda}  -x^\transp\theta| &\leq \|x\|_{G_{N, \lambda}^{-1}}\left(\left\|\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\eta_n\right\|_{G_{N, \lambda}^{-1}} + \lambda\|\theta\|_{G_{N, \lambda}^{-1}}\right)
+    |x^\transp\theta_{N,\lambda}  -x^\transp\theta| \leq {} & \|x\|_{G_{N, \lambda}^{-1}}\left(\left\|\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\eta_n\right\|_{G_{N, \lambda}^{-1}}\right.\\ 
+    &+ \left.\lambda\|\theta\|_{G_{N, \lambda}^{-1}}\right)
 \end{align*}
@@
 & \geq \min_{A \in \cP} \expectedvalueover{\omega(t)}\left[\hat{v^r}(\bu)\right] = \hat{v^r}(\bu)
+\end{align*}
+\end{proof}
+
+\subsection{Proof of \autoref{theorem:drop-regret}}
+
+We start by showing the following lemma:
+
+\begin{lemma}[Robust values ordering]
+	In addition to the robust B-value defined in \eqref{eq:robust-b-values}, we also define the robust value of a sequence of actions $a$
+	\begin{equation}
+	V_a^r \eqdef \max_{\bu \in a\mathcal{A^\infty}} \min_{m\in[1, M]} \sum_{n=h(a)+1}^\infty \gamma^n R^m_n
+	\end{equation}
+	and the robust U-values of a sequence of action $a$
+	\begin{equation}
+	U_a^r(T)  \eqdef
+	\begin{cases}
+	\min_{m\in[M]} \sum_{n=0}^{h-1} \gamma^n R_n^m &\text{if } a \text{ is a leaf;}\\
+	\max_{b\in\mathcal{A}} U_{ab}^r(n) & \text{else.}
+	\end{cases}
+	\end{equation}.
+
+	Then, the robust values, U-values and B-values exhibit similar properties as the optimal values, U-values and B-values, that is: for all $0 < t < T$ and $a\in\mathcal{T}_T$,
+	\begin{equation}
+	U^r_a(t) \leq U^r_a(T) \leq V^r_a \leq B^r_a(T) \leq B^r_a(t)
+	\end{equation}
+	\label{lemma:uvb}
+\end{lemma}
+\begin{proof}
+	By definition, when starting with sequence $i$, the value $u_i^m(n)$ represents the minimum admissible reward, while $b_i^m(n)$ corresponds to the best admissible reward achievable with respect to the the possible continuations of $i$.
+Thus, for all $i\in\mathcal{A}^*$, $u_i^m(n)$ and $u_i^r(n)$ are non-decreasing functions of $n$ and $b_i^m(n)$ and $b_i^r(n)$ are a non-increasing functions of $n$, while $v_i^m$ and $v_i^r$ do not depend on $n$.
+
+	Moreover, since the reward function $r$ is assumed to have values in $[0, 1]$, the sum of discounted rewards from a node of depth $d$ is at most $\gamma^d + \gamma^{d+1}+\cdots = \frac{\gamma^d}{1-\gamma}$.
+As a consequence, for all $n \geq 0$ , $i\in\mathcal{L}_n$ of depth $d$, and any sequence of rewards $(r_t)_{t\in\mathbb{N}}$ obtained from following a path in $i\mathcal{A}^\infty$ with any dynamics $m \in [1, M]$:
+
+	\begin{equation*}
+	\sum_{t=0}^{d-1} \gamma^t r_t \leq \sum_{t=0}^{d-1} \gamma^t r_t + \sum_{t=d}^\infty \gamma^t r_t \leq \sum_{t=0}^{d-1} \gamma^t r_t + \frac{\gamma^d}{1-\gamma}
+	\end{equation*}
+	That is equivalent to:
+	\begin{equation*}
+	u^m_i(n) \leq \sum_{t=0}^\infty \gamma^t r_t \leq b^m_i(n) 
+	\end{equation*}
+	Hence,
+	\begin{equation}
+	\label{eq:min_m_values}
+	\min_{m \in [1, M]} u^m_i(n) \leq \min_{m \in [1, M]} \sum_{t=0}^\infty \gamma^t r_t \leq \min_{m \in [1, M]} b^m_i(n)
+	\end{equation}
+	And as the left-hand and right-hand sides of \eqref{eq:min_m_values} are independent of the particular path that was followed in $i\mathcal{A}^\infty$, it also holds for the robust path:
+
+	\begin{equation*}
+	\min_{m \in [1, M]} u^m_i(n) \leq \max_{\pi\in i\mathcal{A}^\infty} \min_{m \in [1, M]} \sum_{t=0}^\infty \gamma^t r_t \leq \min_{m \in [1, M]} b^m_i(n)
+	\end{equation*}
+	that is,
+	\begin{equation}
+	\label{eq:urvrbr}
+	u^r_i(n) \leq v^r_i  \leq b^r_i(n)
+	\end{equation}
+
+	Finally, \eqref{eq:urvrbr} is extended to the rest of $\mathcal{T}_n$ by recursive application of \eqref{eq:max_vr}, \eqref{eq:ur} and \eqref{eq:br}.
+\end{proof}
+
+We now turn to the proof of the theorem.
+
+\begin{proof}
+	\citet{Hren2008} first show in Theorem 2 that the simple regret of their optimistic planner is bounded by $\frac{\gamma^{d_n}}{1 - \gamma}$ where $d_n$ is the depth of $\mathcal{T}_n$.
+This properties relies on the fact that the returned action belongs to the deepest explored branch, which we can show likewise by contradiction using Lemma \ref{lemma:uvb}.
+This yields directly that $a = i_0$ where $i$ is some node of maximal depth $d_n$ expanded at round $t\leq n$, which by Algorithm \ref{algo:drop} verifies $b_a^r(t) = b_i^r(t) = \max_{x\in\mathcal{A}} b_x^r(t)$ and:
+	\begin{align}
+	\label{eq:Rndn}
+	v^r - v_a^r &= v_{a^*}^r - v_a^r \\
+	&\leq b_{a^*}^r(t) - v_a^r \\
+	&\leq b_{a}^r(t) - u_a^r(t) \\
+	&= b_{i}^r(t) - u_i^r(t) \\
+	&= \frac{\gamma^{d_n}}{1-\gamma}.
+	\end{align}
+
+	Secondly, they bound the depth $d_n$ of $\mathcal{T}_n$ with respect to $n$.
+To that end, they show that the expanded nodes always belong to the sub-tree $\mathcal{T}_\infty$ of all the nodes of depth $d$ that are $\frac{\gamma^d}{1-\gamma}$-optimal.
+Indeed, if a node $i$ of depth $d$ is expanded at round $n$, then $b_i^r(n) \geq b_j^r(n)$ for all $j\in \mathcal{L}_n$ by Algorithm \ref{algo:drop}, thus the max-backups of \eqref{eq:br} up to the root yield $b^r_i(n) = b_\emptyset^r(n)$.
+Moreover, by Lemma \ref{lemma:uvb} we have that $b_\emptyset^r(n) \geq v_\emptyset^r = v^r$ and so $v_i^r \geq u_i^r(n) = b_i^r(n) - \frac{\gamma^d}{1-\gamma} \geq v^r - \frac{\gamma^d}{1-\gamma}$, thus $i \in \mathcal{T}_\infty$.
+
+	Then from Assumption \ref{assumpt:beta} and the definition of $\beta$ applied to nodes in $\mathcal{T}_\infty$, there exists $d_0$ and $c$ such that the number $n_d$ of nodes of depth $d \geq d_0$ in $\mathcal{T}_\infty$ is bounded by $c\left(\frac{\gamma^d}{1-\gamma}\right)^\beta K^d$.
+As a consequence,
+	\begin{eqnarray*}
+		n &= \sum_{d=0}^{d_n} n_d = n_0 + \sum_{d=d_0+1}^{d_n} n_d \\
+		&\leq n_0 + \sum_{d=d_0+1}^{d_n} c\left(\frac{\gamma^d}{1-\gamma}\right)^\beta K^d \\
+		&= n_0 + c'\sum_{d={d_0+1}}^{d_n} \kappa^d
+	\end{eqnarray*}
+	where $c'=\frac{c}{(1-\gamma)^\beta}$.
+
+	\begin{itemize}
+		\item If $\kappa > 1$, then $n \leq n_0 + c'\kappa^{d_0+1}\frac{\kappa^{d_n-d_0}-1}{\kappa-1}$ and thus $d_n \geq d_0 + \log_\kappa \frac{(n-n_0)(\kappa - 1)}{c'\kappa^{d_0+1}}$.
+		We conclude from \eqref{eq:Rndn} that $\mathcal{R}_n \leq \frac{\gamma^{d_n}}{1-\gamma} = \frac{1}{1-\gamma} \left( \frac{(n-n_0)(\kappa - 1)}{c'\kappa^{d_0+1}} \right)^\frac{\log \gamma}{\log \kappa} = O\left(n^{-\frac{\log 1/\gamma}{\log \kappa}}\right)$.
+
+		\item If $\kappa = 1$, then $n \leq n_0 + c'(d_n-d_0)$, hence from \eqref{eq:Rndn} we have $\mathcal{R}_n = O\left(\gamma^{nc'}\right)$.
+	\end{itemize}
+\end{proof}
+
+\subsection{Proof of \autoref{prop:lower-bound}}
+
+\begin{proof}
+	For any $\theta \in \Theta$, $t \in [0, H]$ and any trajectory $(s_0, \cdots, s_t)$ sampled from $\pi$ and $T_\theta$,
+
+	\begin{equation*}
+	s_t \in S(t, s_0, \pi) \subset \square S(t, s_0, \pi)
+	\end{equation*}
+
+	Hence, 
+	\begin{equation*}
+	R^{T_\theta}_\pi = \sum_{t=0}^\infty \gamma^t r(s_t, a_t) \geq \sum_{t=0}^H \gamma^t r(s_t, a_t) \geq \sum_{t=0}^H \min_{s\in \square S(t, s_0, \pi)} \gamma^t r(s, \pi(s)) = \hat{v^r}(\pi)
+	\end{equation*}
+
+	And finally,
+	\begin{align*}
+	v^r(\pi) = \min_{\theta\in\Theta} {v_\pi^{T_\theta}} = \min_{\theta\in\Theta} \expectedvalue(R^{T_\theta}_\pi) \geq \hat{v^r}(\pi)
 	\end{align*}

### 2020-01-20 main.tex
Updates from Overleaf

@@
 
+    Optimistic exploration = information seeking and uncertainty reduction.
+Our objective: do not commit mistakes (do not explore uncertain regions).
+If some information is collected allowing to reduce uncertainty, use it to be more optimal, but do not actively seek it.
+
 Robust optimization has been studied in the context of finite Markov Decision Processes (MDP) with uncertain parameters by Iyengar (2005), Nilim and El Ghaoui (2005) and Wiesemann et al.
@@
 However, all the sensing and control performed on-board happen in discrete time, with time-step $\tau$.
-For any variable $z$, we use the subscript notation to refer to these discrete times: $z_n = z(n\tau)$.
+For any variable $z$, we use the subscript notation to refer to these discrete times: $z_n = z(t_n)$ with $t_n = n\tau$.
 
@@
 \begin{equation}
-\label{eq:interval_property}
-\underline{x}(t)\leq x(t)\leq\overline{x}(t),\quad\forall t\geq N\tau.
+\label{eq:inclusion-property}
+\underline{x}(t)\leq x(t)\leq\overline{x}(t),\quad\forall t\geq t_N.
 \end{equation}
@@
  &  & +Bu(t)+D^{+}\underline{\omega}(t)-D^{-}\overline{\omega}(t),\nonumber\\
-\dot{\overline{x}}(t) & = & A_{0}\overline{x}(t)+\Delta A_{+}\overline{x}^{+}(t)+\Delta A_{-}\underline{x}^{-}(t) \label{eq:interval_predictor} \\
+\dot{\overline{x}}(t) & = & A_{0}\overline{x}(t)+\Delta A_{+}\overline{x}^{+}(t)+\Delta A_{-}\underline{x}^{-}(t) \label{eq:interval-predictor} \\
  &  & +Bu(t)+D^{+}\overline{\omega}(t)-D^{-}\underline{\omega}(t),\nonumber \\
- &  & \underline{x}(N\tau)=\overline{x}(N\tau)={x}(N\tau)\nonumber 
+ &  & \underline{x}(t_N)=\overline{x}(t_N)={x}(t_N)\nonumber 
 \end{eqnarray}
-ensures the inclusion property \eqref{eq:interval_property}.
+ensures the inclusion property \eqref{eq:inclusion-property}.
 
@@
 % \end{gather*}
-% }then the predictor \eqref{eq:interval_predictor} is input-to-state stable with respect to the inputs $\underline{\omega}$, $\overline{\omega}$.
+% }then the predictor \eqref{eq:interval-predictor} is input-to-state stable with respect to the inputs $\underline{\omega}$, $\overline{\omega}$.
 \end{theorem}
@@
 % where $x(t)\in\Real$ with $x(0)\in[\underline{x}_{0},\overline{x}_{0}]=[1.0, 1.1]$, $\theta(t)\in\Pi=[\underline{\theta},\overline{\theta}]=[0.5,1.5]$ and $d(t)\in[\underline{d},\overline{d}]=[-0.1,0.1]$ for all $t\geq0$.
-The \autoref{fig:predictor_example} shows the state-interval obtained with \eqref{eq:interval_predictor}.
+The \autoref{fig:predictor_example} shows the state-interval obtained with \eqref{eq:interval-predictor}.
 
@@
 % \begin{centering}
-% \includegraphics[width=\linewidth]{img/interval_predictor}
+% \includegraphics[width=\linewidth]{img/interval-predictor}
 % \par\end{centering}
 % \caption{Several trajectories for different values of $\theta\in\Theta$ are shown in blue.
-The result of prediction by \eqref{eq:interval_predictor} is in red: the predictor is stable and produces tight bounds.}
+The result of prediction by \eqref{eq:interval-predictor} is in red: the predictor is stable and produces tight bounds.}
 % \label{fig:predictor_example}
@@
 \end{align}
-where $\underline{x}_n(\bu), \overline{x}_n(\bu)$ follow the dynamics defined in \eqref{eq:interval_predictor}.
+where $\underline{x}_n(\bu), \overline{x}_n(\bu)$ follow the dynamics defined in \eqref{eq:interval-predictor}.
 \end{definition}
 
-This does not simply amounts to a change of reward function, since the worst case is assessed over the whole past trajectory being optimized, which means that this pessimistic reward $\underline{R}$ does not respect the Markov assumption.
+This does not simply amounts to a change of reward function, since the worst case is assessed over the whole past trajectory being optimized, which means that this pessimistic reward $\underline{R}$ is not \emph{markovian}.
 
@@
 The consequence of \autoref{prop:lower-bound} is that since all our approximations were conservative, if we manage to find a control sequence such that no \textit{``bad event''} (e.g.
-a collision) happens with our surrogate objective, then we are guaranteed so they will not happen either when the controls are executed on the true system.
-
-In order to optimize our surrogate objective $\hat{V}^r$, we turn to sequential planning algorithms.
-We cannot use the Dynamic Programming techniques because the state space is continuous and the pessimistic rewards are non-markovian.
-Instead, we turn to tree-based planning algorithms which optimize a sequence of actions based on the corresponding sequence of rewards without enumerating the states nor requiring the markovity of the rewards.
-In particular, we use the \texttt{OPD} algorithm \citep{Hren2008} tailored for the case where the sequence of rewards is a deterministic function of the sequence of actions, which is appropriate since both the predictor dynamics \eqref{eq:interval_predictor} and the corresponding pessimistic rewards \eqref{eq:pessimistic-rewards} are deterministic.
-
-\texttt{OPD} progressively builds a tree $\cT_k$ by expanding the leaf $a_k\in\cL_k$ with highest B-value:
-\begin{equation}
-\argmax_{a\in\cL_k} B_a(k), \quad B_a(k) = \sum_{n=0}^{h-1} \underline{R}_n(a) + \frac{\gamma^h}{A-\gamma}.
-\end{equation}
-
+a collision) happens according to the surrogate objective $\hat{V}^r$, then we are guaranteed so they will not happen either when the controls are executed on the true system.
+
+\paragraph{Planning}
+In order to optimise $\hat{V}^r$, we turn to sequential planning algorithms.
+We cannot use Dynamic Programming algorithms because the state space is continuous and the pessimistic rewards are non-markovian.
+Instead, we turn to tree-based planning algorithms which optimise a sequence of actions based on the corresponding sequence of rewards.
+These methods no dot require the enumeration of the states nor the markovity of the rewards.
+In particular, we consider the \emph{Optimistic Planning of Deterministic Systems} (\texttt{OPD}) algorithm \citep{Hren2008} tailored for the case where the sequence of rewards is a deterministic function of the sequence of actions.
+Indeed, the stochasticity of the perturbations and measurements is encased in $\hat{V}^r$: both the predictor dynamics \eqref{eq:interval-predictor} and the corresponding pessimistic rewards \eqref{eq:pessimistic-rewards} are deterministic.
+
+At each planning iteration $k\in[K]$, \texttt{OPD} progressively builds a tree $\cT_{k+1}$ by expanding the leaf $a_k$ with highest B-value, where the expansion of a leaf $a$ refers to the simulation of its children transitions $aA = \{ab, b\in A\}$:
+\begin{equation}
+\label{eq:opd}
+a_k = \argmax_{a\in\cL_k} B_a(k), \quad B_a(k) = \sum_{n=0}^{h(a)-1} \underline{R}_n(a) + \frac{\gamma^{h(a)}}{1-\gamma}
+\end{equation}
+where $\cL_k$ is the set of leaves of $\cT_k$, $h(a)$ is the length of the sequence $a$, and $\underline{R}_n(a)$ the pessimistic reward \eqref{eq:pessimistic-rewards} obtained at time $n$ by following the sequence $a$.
+\begin{theorem}[Planning performance, \citep{Hren2008}]
+\label{theorem:opd-regret}
+The simple regret of the \texttt{OPD} algorithm \eqref{eq:opd} after $K$ iterations is:
+\begin{align*}
+\text{if } \kappa>1,\quad& 
+\hat{V}^r(a^*) - \hat{V}^r({a_K}) = \cO\left(K^{-\frac{\log 1/\gamma}{\log \kappa}}\right);\\
+\text{if }\kappa=1,\quad&
+\hat{V}^r(a^*) - \hat{V}^r({a_K}) = \cO\left(\gamma^{\frac{(1-\gamma)^\beta}{c}K}\right)
+\end{align*}
+where $\kappa$ is a problem-dependent measure of the proportion of near-optimal paths:
+\[
+\kappa = \limsup_{h\rightarrow\infty} \left|\left\{a\in A^h: \hat{V}^r(a)\geq \hat{V}^r - \frac{\gamma^{h+1}}{1-\gamma}\right\}\right|^{1/h}.
+\]
+\end{theorem}
+
+Hence, by using enough computational budget $K$ for planning we can get as close as we want to the optimal surrogate value $\hat{V}^r(\bu^*)$, at a polynomial rate.
+However, there exists a gap between $\hat{V}^r$ and the true robust objective $V^r$, which stems from three approximations: (i) the true reachable set was approximated by an enclosing interval in \eqref{eq:inclusion-property}; (ii) the time-invariance of the dynamics uncertainty $A(\theta)\in\cC_{[N],\delta}$ was handled by the interval predictor \eqref{eq:interval-predictor} as if it were a time-varying uncertainty $\forall t, A(\theta(t))\in\cC_{[N],\delta}$ ; and (iii) the lower-bound $\sum\min\leq \min\sum$ used to define the surrogate objective \eqref{eq:surrogate_objective} is not tight.
+
+However, under an additional smoothness assumption on $R$, we can bound this gap:
 \begin{proposition}
 \label{prop:control-error}
-If we assume that the reward function $R$ is lipschitz, then the approximation error is upper-bounded by:
+If the reward function $R$ is lipschitz, then the approximation error is upper-bounded by:
 \begin{equation*}
@@
    \STATE Get the tree node $\bu^t$ to expand with \textsc{Pessimistic Planning}  \eqref{eq:surrogate_objective} using $[\underline{x}(t,\bu), \overline{x}(t,\bu)]$.
-   \STATE For each child transition, simulate $[\underline{x}, \overline{x}]$ with \textsc{Interval Prediction} \eqref{eq:interval_predictor} using $\cC_{[N],\delta}$.
+   \STATE For each child transition, simulate $[\underline{x}, \overline{x}]$ with \textsc{Interval Prediction} \eqref{eq:interval-predictor} using $\cC_{[N],\delta}$.
    \ENDFOR
@@
 
-We temporarily ignore the parametric uncertainty over $\theta$ to simply consider several known candidate dynamics models.
+We temporarily ignore the parametric uncertainty over $\theta$ to simply consider several known candidate dynamics models, which all correspond to different modelling assumptions.
 
@@
 
-We express the performance of the planning problem in terms of a measure of the proportion of near-optimal paths:
-\[
-\kappa = \limsup_{h\rightarrow\infty} \left|\left\{a\in A^h: V(a)\geq V - \frac{\gamma^{h+1}}{1-\gamma}\right\}\right|^{1/h}.
-\]
-
 \begin{theorem}[Regret bound]
@@
 \begin{proof}
-We have that $A(\theta) \in \cC_{[N],\delta}$ with probability $1-\delta$.
-Whenever it is the case, we have by \autoref{thm:predictor} that the inclusion property \eqref{eq:interval_property} is verified by the interval predictor \eqref{eq:interval_predictor} for all $\omega(t)\in[\underline{\omega}(t), \overline{\omega}(t)]$.
-This gives the following bound:
-\begin{equation*}
- \sum_{t=0}^\infty \gamma^t r(x_t) \geq \sum_{t=0}^\infty \min_{x\in[\underline{x}(t, \bu), \overline{x}(t, \bu)]} \gamma^t r(x) = \hat{v^r}(\bu)
-\end{equation*}
-
-And finally, with probability $1-\delta$,
-\begin{align*}
-v^r(\bu) &= \min_{A(\theta) \in A(\Theta)} \expectedvalueover{\omega(t)}\left[\sum_{t=0}^\infty \gamma^t r(x_t)\right] \\
-&\geq \min_{A \in \cP} \expectedvalueover{\omega(t)}\left[\sum_{t=0}^\infty \gamma^t r(x_t)\right] \\
-& \geq \min_{A \in \cP} \expectedvalueover{\omega(t)}\left[\hat{v^r}(\bu)\right] = \hat{v^r}(\bu)
-\end{align*}
+	The predictor designed in \autoref{sec:prediction} verifies the inclusion property \eqref{eq:inclusion-property}.
+Thus, for sequence of controls $\bu$, any dynamics $A(\theta)\in C_{[N],\delta}$, and perturbations $\underline{\bw} \leq \bw \leq \overline{\bw}$, the corresponding state at time $t_n$ is bounded by $\underline{x}_n \leq x_n \leq \overline{x}_n$, which implies that $R(x_n) \geq \min_{x\in[\underline{x}_n(\bu), \overline{x}_n(\bu)]}  R(x) = \underline{R}_n(\bu)$.
+
+	Thus, by taking the min over $C_{[N],\delta}$ and $[\underline{\bw}, \overline{\bw}]$, we also have for any sequence of controls $\bu$:
+	\begin{align*}
+	    V^r(\bu) &= \min_{\substack{A(\theta)\in C_{[N],\delta}\\ \underline{\bw} \leq \bw \leq \overline{\bw}}} \sum_{n=N+1}^\infty \gamma^n R(x_n)\\
+	    &\geq \sum_{n=N+1}^\infty \gamma^n \underline{R}_n(\bu)\\
+	    &= \hat{V}^r(\bu)
+	\end{align*}
+\end{proof}
+
+\subsection{Proof of \autoref{prop:control-error}}
+
+\begin{proof}
+ By the inclusion property \eqref{eq:inclusion-property}, for any sequence of controls $\bu$, dynamics $A(\theta)\in C_{[N],\delta}$ and perturbations $\underline{\bw} \leq \bw \leq \overline{\bw}$, we have that $\underline{x}_n \leq x_n \leq \overline{x}_n$, which implies that $R(x_n) \leq \max_{x\in[\underline{x}_n(\bu), \overline{x}_n(\bu)]}  R(x)$.
+
+ Thus, since we assume that $R$ is $L$-lipschitz,
+ \begin{align}
+     V^r(\bu) - \hat{V}^r(\bu) &\leq \sum_{n=N+1}^\infty \gamma^n \underset{{x\in[\underline{x}_n(\bu), \overline{x}_n(\bu)]}}{(\max - \min)} R(x)\\
+     &\leq \sum_{n=N+1}^\infty \gamma^n L \left\|\underline{x}_n(\bu) - \overline{x}_n(\bu)\right\|
+ \end{align}
+
 \end{proof}
@@
 	\end{itemize}
-\end{proof}
-
-\subsection{Proof of \autoref{prop:lower-bound}}
-
-\begin{proof}
-	For any $\theta \in \Theta$, $t \in [0, H]$ and any trajectory $(s_0, \cdots, s_t)$ sampled from $\pi$ and $T_\theta$,
-
-	\begin{equation*}
-	s_t \in S(t, s_0, \pi) \subset \square S(t, s_0, \pi)
-	\end{equation*}
-
-	Hence, 
-	\begin{equation*}
-	R^{T_\theta}_\pi = \sum_{t=0}^\infty \gamma^t r(s_t, a_t) \geq \sum_{t=0}^H \gamma^t r(s_t, a_t) \geq \sum_{t=0}^H \min_{s\in \square S(t, s_0, \pi)} \gamma^t r(s, \pi(s)) = \hat{v^r}(\pi)
-	\end{equation*}
-
-	And finally,
-	\begin{align*}
-	v^r(\pi) = \min_{\theta\in\Theta} {v_\pi^{T_\theta}} = \min_{\theta\in\Theta} \expectedvalue(R^{T_\theta}_\pi) \geq \hat{v^r}(\pi)
-	\end{align*}
 \end{proof}

### 2020-01-20 main.tex
Update intro and algo

@@
 \begin{abstract}
-	We study the adaptive control of a linear system with unknown parameters and arbitrary costs in a critical setting where failures are costly and should be prevented at all time.
-We build on two ideas.
-First, we incorporate prior knowledge of the dynamics in the form of a known structure of uncertainty, that can be tightened as we collect interaction data by building high-confidence regions through least-square regression.
-Second, we act in a cautious way with respect to this uncertainty by formulating a robust objective, that we solve approximately in a prediction-optimisation manner, leveraging tools from interval prediction and tree-based planning.
+	We develop a framework for the adaptive control of a linear system with unknown parameters and arbitrary costs in a critical setting where failures are costly and should be prevented at all time.
+We build on two ideas: first, we incorporate prior knowledge of the dynamics in the form of a known structure of the uncertainty, which can be tightened as we collect interaction data by building high-confidence regions through least-square regression.
+Second, we act in a cautious way with respect to this uncertainty by formulating a robust objective, that we solve approximately in a prediction-optimisation manner, leveraging tools from interval prediction and sequential planning literatures.
 Additionally, we relax our modelling assumptions by proposing an extension based on multi-model selection and aggregation.
@@
 \section{Introduction}
+
+Despite the dazzling successes of Reinforcement learning in cracking many problems considered unsolvable in the past decade [ref needed], this tool has hardly been applied in real industrial issues.
+This could be attributed to two undesirable properties which limit its practical applications: its dependence on a tremendous amount of interaction data that cannot always be simulated, and its reliance on trial-and-error and random exploration.
+In this paper, we consider the problem of controlling an unknown system in a critical setting where mistakes are costly and must be avoided at all time.
+Crucially, we wish to handle \emph{arbitrary} bounded reward functions $R$, for instance non-convex and non-smooth functions that naturally arise in problems
 
@@
 \begin{algorithm}[tb]
-   \caption{Robust Estimation, Prediction and Control}
+   \caption{Robust Estimation, Prediction and Control (v1)}
    \label{alg:full}
@@
    \STATE Compute the dynamics confidence region $\cC_{[N],\delta}$ with \textsc{Model Estimation} \eqref{eq:generic-polytope} on $\cD_{[N]}$.
-   \FOR{planning steps $[T]$}
-   \STATE Get the tree node $\bu^t$ to expand with \textsc{Pessimistic Planning}  \eqref{eq:surrogate_objective} using $[\underline{x}(t,\bu), \overline{x}(t,\bu)]$.
-   \STATE For each child transition, simulate $[\underline{x}, \overline{x}]$ with \textsc{Interval Prediction} \eqref{eq:interval-predictor} using $\cC_{[N],\delta}$.
+   \FOR{planning steps $k\in[K]$}
+   \STATE Get the tree node $\bu_k$ to expand with \textsc{Pessimistic Planning}  \eqref{eq:opd} using $\underline{R_n}$ over $[\underline{x}_{n}, \overline{x}_{n}]$. \COMMENT{Selection}
+   \STATE For each action, simulate the child transition $[\underline{x}_{n+1}, \overline{x}_{n+1}]$ with \textsc{Interval Prediction} \eqref{eq:interval-predictor} using $\cC_{[N],\delta}$.
+\COMMENT{Expansion}
    \ENDFOR
@@
    \ENDFOR
-
+\end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}[tb]
+	\caption{Robust Estimation, Prediction and Control (v2)}
+	\begin{algorithmic}
+		\STATE {\bfseries Input:} confidence level $\delta$
+		\FOR{$N = 1,2,3,\dots$} 
+		\STATE $\cC_{[N],\delta} \gets$\textsc{Model Estimation}$(\cD_{[N]})$. \eqref{eq:generic-polytope}
+		\FOR{planning steps $k\in[K]$}
+		\STATE $a_k\gets$\textsc{Pessimistic Planning}$(\underline{R_n}([\underline{x}_{n}, \overline{x}_{n}]))$.  \eqref{eq:opd}
+		\FOR{$b\in A$}
+		\STATE $[\underline{x}_{n+1}(a_k b), \overline{x}_{n+1}(a_k b)]\gets$ \textsc{Interval Prediction}($\cC_{[N],\delta}$). \eqref{eq:interval-predictor}
+		\ENDFOR
+		\ENDFOR
+		\STATE Execute the first recommended control $u_N$, and add the observed transition $(x_N, u_N, \dot{x}_N)$ to $\cD_{[N+1]}$.
+		\ENDFOR
 	\end{algorithmic}

### 2020-01-20 main.tex
Rewrite problem formulation

@@
 Despite the dazzling successes of Reinforcement learning in cracking many problems considered unsolvable in the past decade [ref needed], this tool has hardly been applied in real industrial issues.
-This could be attributed to two undesirable properties which limit its practical applications: its dependence on a tremendous amount of interaction data that cannot always be simulated, and its reliance on trial-and-error and random exploration.
-In this paper, we consider the problem of controlling an unknown system in a critical setting where mistakes are costly and must be avoided at all time.
-Crucially, we wish to handle \emph{arbitrary} bounded reward functions $R$, for instance non-convex and non-smooth functions that naturally arise in problems
-
-We would like to control a system in order to maximise an \textit{arbitrary} bounded reward function $R$, e.g.
-non-convex, non-smooth.
-These happen naturally: combinatorial optimization such as scheduling, obstacle avoidance.
-Critical industrial setting: we do not want to commit mistakes. 
-In particular, this rules out shiny Deep RL etc.
-The only way to avoid mistakes from the outset, when the system is first deployed, is to incorporate some kind of prior knowledge.
-In this work, we assume that the system dynamics are partially known: known structure of a parametrized system, with unknown parameters.
-This is realistic in the sense that most industrial applications to date have been relying on physical models and corresponding optimal controllers rather than machine learning.
-Here, instead of providing the whole model, its main parts
-Data driven scheme: as we interact and observe more data of the true system, we can estimate the parameters more accurately.
-This estimated model could be use to derive the corresponding optimal control, but this is unsafe: model bias.
-To address this, we want to perform robust estimation: not just a maximum likelihood model, but a whole high-confidence region where the true system is likely to lie.
-Given this ambiguity set, how should we act?
-Given the critical setting, we do not want to be optimistic, and try to minimise some cumulative regret.
-Quite the contrary, we want to be cautious, safe, prepare for the worst and plan for the best.
-A robust control scheme.
+This could be attributed to two undesirable properties which limit its practical applications: the dependence on a tremendous amount of interaction data that cannot always be simulated, and the reliance on trial-and-error and random exploration.
+In this paper, we consider the problem of controlling an unknown linear system $x(t)$ so as to maximise an \emph{arbitrary} bounded reward function $R$, in a critical setting where mistakes are costly and must be avoided at all time.
+This choice of the rich reward space is crucial to have sufficient flexibility to model non-convex and non-smooth functions that naturally arise in many practical problems such as combinatorial optimisation, obstacle avoidance, etc.
+
+Since experiencing failures is out of question, the only way to prevent them from the outset, when the system is first deployed, is to rely on some sort of prior knowledge.
+In this work, we assume that the system dynamics are partially known, in the form of a parametrized dynamical system with unknown parameters.
+We argue that this assumption is realistic given that most industrial applications to date have been relying on physical models to describe their processes and engineered controllers to operate them, rather than machine learning.
+Our framework relaxes this modelling effort by allowing some structured uncertainty around the nominal model.
+We adopt a data-driven scheme where we wish to estimate the parameters more accurately as we interact with our true system.
+Most model-based reinforcement learning algorithms only rely on the estimated dynamics to derive the corresponding optimal controller, but these methods often suffer from \emph{model bias}: they ignore the error that exists between the learned and true dynamics, which can dramatically degrade the control performances \citep{Schneider1997}.
+
+To address this issue, we turn to the framework of \emph{robust} decision-making: instead of merely considering a point estimate of the dynamics, we build an entire \emph{confidence region} that contains the true dynamics with high probability, and optimise the decisions so as to maximise the worst-case outcome with respect to this uncertainty.
 Minimax problem are hard to solve, especially since $R$ can be arbitrary.
@@
 
-Our contributions are the following:
-In Section 2, structured dynamics.
-We extend the work of \citet{Abbasi2011} that provide a confidence ellipsoid for the regularised least-square estimator in the case of scalar noise and vector features to our setting of vector noise and matrix features.
+\subsection{Problem Statement and Our Contributions}
+
+\paragraph{Notations}
+
+The dynamics of the real system are described in continuous time.
+However, all the sensing and control performed on-board happen in discrete time, with time-step $\dd t$.
+For any variable $z$, we use the subscript notation to refer to these discrete times: $z_n = z(t_n)$ with $t_n = n\dd t$.
+
+\paragraph{Structured dynamics}
+We consider a linear system with state $x\in\Real^p$, acted on by controls $u\in\Real^q$ and perturbations $\omega\in\Real^r$, and following a dynamics in the form:
+
+\begin{equation}
+\label{eq:dynamics}
+\dot{x}(t)=A(\theta)x(t) + B u(t) + D \omega(t),\;t\geq0.
+\end{equation}
+The dynamics $A(\theta)\in\Real^{p\times p}$  depends on some parameter $\theta$ that belongs to a compact set $\Theta \subset \Real^d$.
+The control matrix $B\in\Real^{p\times q}$ and disturbance matrix $D\in\Real^{p\times r}$ are known.
+
+We also have access to the observation of $x(t)$ and to a noisy measurement of $\dot{x}(t)$ in the form $\dot{x}(t) + C\nu(t)$, where $\nu(t)\in\Real^s$ is a measurement noise and $C\in\Real^{p\times s}$ is known.
+Assumptions over the disturbance $\omega$ and noise $\nu$ will be detailed further, and we denote $\eta(t) = C\nu(t) + D\omega(t)$.
+
+\paragraph{Model estimation}
+
+In \autoref{sec:estimation}, having observed history of transitions $\cD_{[N]} = \{(x_n, u_n, y_n)\}_{n\in[N]}$, and given a confidence level $\delta\in(0, 1)$, our goal is to find a confidence region $\cC_{[N],\delta}$ as tight as possible and such that it holds that:
+\begin{align}
+\probability{A(\theta)\in \cC_{[N],\delta}} \geq 1-\delta
+\label{eq:polytope}
+\end{align}
+Our first contribution is to extend the work of \citet{Abbasi2011} that provide a confidence ellipsoid for the regularised least-square estimator in the case of scalar noise and vector features to our setting of vector noise and matrix features.
+
+\paragraph{Robust objective}
+
+At the time step $n=N$, considering the model uncertainty $\cC_{[N],\delta}$ obtained in the model estimation phase, we formulate our robust control objective:
+\begin{equation}
+\label{eq:robust-control}
+\sup_{\bu\in{(\Real^q)}^\Natural} \underbrace{\inf_{\substack{A(\theta) \in \cC_{[N],\delta} \\ \bw\in[\underline{\bw},\overline{\bw}]^\Natural}} \left[\sum_{n=N+1}^\infty \gamma^n R(x_n(\bu,\bw))\right]}_{V^r(\bu)}
+\end{equation}
+where $\bu = (u_{N+1},u_{N+2},\cdots)$ and $\bw = (\omega_N, \omega_{N+1},\cdots)$ are the sequences of future controls and perturbations, respectively.
+
+The rest of the paper will tackle the optimisation of this objective.
+
+\paragraph{State prediction}
+
+Minimax problems such as \eqref{eq:robust-control} are notoriously difficult to solve even in cases such as Linear-Quadratic systems (LQ) where the reward $R$ has a simple form.
+Here with an arbitrary function $R$, we cannot hope to derive a solution in explicit form.
+Our second contribution is to propose to solve \eqref{eq:robust-control} numerically by adopting a \emph{predict-then-optimise} scheme.
+Thus, in \autoref{sec:prediction}, as illustrated in \autoref{fig:interval-hull}, we aim to derive a \emph{set predictor} $X(t)$ for the system \eqref{eq:dynamics}, which takes the information on the observed current state ${x}_N$, a confidence region $\cC_\delta$ containing $A(\theta)$, a planned control sequence $\bu$ and some admissible bounds on the perturbation $[\underline{\omega}(t),\overline{\omega}(t)]$; and verifies the inclusion property:
+\begin{equation}
+ x(t)\in X(t),\quad\forall t\geq t_N.
+\end{equation}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.3\textwidth]{img/interval-hull}
+    \caption{A few trajectories are sampled from an initial state $x_N$ following controls $\bu=(u_0,\cdots)$ with various parameters $A(\theta)\in\cC_{[N],\delta}$ (in black).
+At time $t\geq t_N$, any reachable state $x(t)$ (in green) must belong to the candidate set predictor $X(t)$ (in red).}
+    \label{fig:interval-hull}
+\end{figure}
+
+We leverage known techniques from the uncertain system simulation literature to efficiently compute such a predictor.
+
+\paragraph{Robust planning}
+
+Since $R$ is arbitrary, solving the optimal -- not to mention the robust -- control objective in the original continuous control space $(\Real q)^\Natural$ is intractable.
+In this work, we choose to approximate the solution by turning the continuous optimisation problem \eqref{eq:robust-control} into a discrete one, by optimising over a finite set of \emph{actions} $\cA$.
+Each action $a\in\cA$ corresponds to the selection of a low-level controller $\pi_a$, that we take affine:
+\[u(t) = \pi_a(x(t)) \eqdef -K_a x(t) + u_a\]
+
+The robust objective we consider becomes 
+\begin{equation}
+\label{eq:robust-control-disc}
+\sup_{\ba\in{\cA}^\Natural} \underbrace{\inf_{\substack{A(\theta) \in \cC_{[N],\delta} \\ \bw\in[\underline{\bw},\overline{\bw}]^\Natural}} \left[\sum_{n=N+1}^\infty \gamma^n R(x_n(\ba,\bw))\right]}_{V^r(\ba)}
+\end{equation}
+where $x_n(\ba, \bw)$ is obtained by integrating \eqref{eq:dynamics} with $u_n = \pi_{a_n}(x_n)$.
+
+In \autoref{sec:control}, facing an optimisation problem with continuous states and discrete actions, we turn to the literature of tree-based planning.
+Our third contribution proposes to approximate the true robust objective ${V}^r$ by an easily-evaluable surrogate $\hat{V}^r$ that exploits the set predictor to define a pessimistic reward, used to evaluate sequences of actions in a tree-based planning algorithm.
+We show that
+
+% \paragraph{Objective}
+
+% We wish to find a sequence of commands $\bu=(u_t)_{t\geq 0}$ that maximises a cumulative objective $V^\bu$:
+
+% \todo[inline]{EL: the prediction is done in continuous time and the control in discrete time. How to handle the change in notations?}
+
+% \begin{equation}
+% \max_\bu V^\bu
+% \end{equation}
+% where
+% \begin{equation}
+% \label{eq:optimal-control}
+% V^\bu = \expectedvalueover{\omega(t)}\left[\sum_{t=0}^\infty \gamma^t r(x(t))\condbar u_t,\,\eqref{eq:dynamics}\right]
+% \end{equation}
+% and $r:\Real^p\rightarrow[0,1]$ is a bounded reward function.
 
@@
 
+ Given the critical setting, we do not want to be optimistic, and try to minimise some cumulative regret. Quite the contrary, we want to be cautious, safe, prepare for the worst and plan for the best.
+
 Robust optimization has been studied in the context of finite Markov Decision Processes (MDP) with uncertain parameters by Iyengar (2005), Nilim and El Ghaoui (2005) and Wiesemann et al.
@@
 
-\section{Problem formulation}
-
-\paragraph{Structured dynamics}
-We consider a system with dynamics in the form:
-
-\begin{equation}
-\label{eq:dynamics}
-\dot{x}(t)=A(\theta)x(t) + B u(t) + D \omega(t),\;t\geq0,
-\end{equation}
-with state $x\in\Real^p$, control $u\in\Real^q$, and disturbance $\omega\in\Real^s$.
-The dynamics $A(\theta)\in\Real^{p\times p}$  is parametrised by $\theta$ that belongs to a compact set $\Theta \subset \Real^d$.
-The control matrix $B\in\Real^{p\times q}$ and disturbance matrix $D\in\Real^{p\times s}$ are known.
-
-We also have access to the observation of $x(t)$ and to noisy a measurement of $\dot{x}(t)$ in the form
-$
-    \dot{x}(t) + C\nu(t)
-$ where $\nu(t)\in\Real^r$ is a measurement noise and $C\in\Real^{p\times r}$ is known.
-Assumptions over the disturbance $\omega$ and noise $\nu$ will be detailed further, and we denote their total contribution as $\eta(t) = C\nu(t) + D\omega(t)$.
-
-\paragraph{Notations}
-
-The dynamics of the real system are described in continuous time.
-However, all the sensing and control performed on-board happen in discrete time, with time-step $\tau$.
-For any variable $z$, we use the subscript notation to refer to these discrete times: $z_n = z(t_n)$ with $t_n = n\tau$.
-
-% \paragraph{Objective}
-
-% We wish to find a sequence of commands $\bu=(u_t)_{t\geq 0}$ that maximises a cumulative objective $V^\bu$:
-
-% \todo[inline]{EL: the prediction is done in continuous time and the control in discrete time. How to handle the change in notations?}
-
-% \begin{equation}
-% \max_\bu V^\bu
-% \end{equation}
-% where
-% \begin{equation}
-% \label{eq:optimal-control}
-% V^\bu = \expectedvalueover{\omega(t)}\left[\sum_{t=0}^\infty \gamma^t r(x(t))\condbar u_t,\,\eqref{eq:dynamics}\right]
-% \end{equation}
-% and $r:\Real^p\rightarrow[0,1]$ is a bounded reward function.
-
 \section{Model Estimation}
@@
 
-\paragraph{Objective}
-Having observed at times a history of transitions $\cD_{[N]} = \{(x_n, u_n, y_n)\}_{n\in[N]}$, and given a confidence level $\delta\in(0, 1)$, our goal is to find a confidence region $\cC_{[N],\delta}$ as tight as possible and such that it holds that:
-\begin{align}
-\probability{A(\theta)\in \cC_{[N],\delta}} \geq 1-\delta
-\label{eq:polytope}
-\end{align}
-
-% This involves the trilemma of confidence intervals, where one of three things must be true:
-% \begin{enumerate}
-%     \item $A(\theta)$ is in $\cC_\delta$
-%     \item We got data that was very ($\leq\delta$) unlikely under all possible values $A(\theta)$
-%     \item Our model is wrong
-% \end{enumerate}
-
-% \paragraph{Tensor notations}
-% We adopt the notations of [Tensor Decompositions and Applications]:
-% Given a tensor $A\in\Real^{I_1\times\cdots\times I_l}$ and matrix $M\in\Real^{I_n\times J}$, the $n$-mode product of $A$ by $M$ is a tensor of $\Real^{I_1\times\cdots\times I_l}$  defined by:
-% \begin{equation*}
-%     (A\times_n M)_{i_1,\cdots,i_{n-1},j,i_{n+1},\cdots,i_l} = \sum_{k=1}^{I_n} A_{i_1,\cdots,i_{n-1},k,i_{n+1},\cdots,i_l}B_{k,j}
-% \end{equation*}
-
-To that end, we further assume that the dynamics $A(\theta)$ enjoy the following additional structure:
-\begin{assumption}[Linear parametrisation]
-\label{assumpt:linear_param}
+In the general case, 
+ assume that the dynamics $A(\theta)$ enjoy the following additional structure:
+\begin{assumption}[Structure]
+\label{assumpt:structure}
 There exists a known feature tensor $\phi\in \Real^{d \times p \times p}$ such that for all $\theta\in\Theta$:
@@
 
-\paragraph{Robust objective}
-
-From now on, we consider that we have reached the time step $n=N$, and that a confidence region $\cC_{[N],\delta}$ was obtained with data $\cD_{[N]}$ collected so far.
-The following sections tackle the optimisation of the robust control objective:
-\begin{equation}
-\label{eq:robust-control}
-\max_\bu \underbrace{\min_{\substack{A(\theta) \in \cC_{[N],\delta} \\ \bw\in[\underline{\bw},\overline{\bw}]^\Natural}} \left[\sum_{n=N+1}^\infty \gamma^n R(x_n(\bu,\bw))\right]}_{V^r(\bu)}
-\end{equation}
-where $\bu = (u_{N+1},u_{N+2},\cdots)$ and $\bw = (\omega_N, \omega_{N+1},\cdots)$ are the sequences of future controls and perturbations, respectively.
-Here, we considered the bounded noise setting of \autoref{assumpt:bounded-noise}.
-In the sub-Gaussian noise setting of \autoref{assumpt:gaussian-noise}, we can use the same formulation by deriving high-confidence bounds $\underline{\omega}(t) \leq \omega(t) \leq \overline{\omega}(t)$ that each hold with probability $\delta_t$.
+\paragraph{Remark} The robust objective framing involves on some bounds $\underline{\omega}(t)\leq \omega(t) \leq \overline{\omega}(t)$ over the possible perturbations we want to protect against.
+In the unbounded sub-Gaussian noise setting of \autoref{assumpt:gaussian-noise}, we can use the same formulation by deriving high-confidence bounds that each holds with probability $\delta_t$.
 By choosing $\delta_t = \frac{\delta}{t(t+1)}$, we have that the event $\{\forall t, \underline{\omega}(t) \leq \omega(t) \leq \overline{\omega}(t)\}$ holds with probability $1-\delta$.
@@
 
-The objective of this section, as illustrated in \autoref{fig:interval-hull} is to  derive a \emph{set predictor} for the system \eqref{eq:dynamics}, which takes the information on the observed current state ${x}({0})$, some admissible bounds on the perturbation $[\underline{\omega}(t),\overline{\omega}(t)]$, and a confidence region $\cC_\delta$ in the form \eqref{eq:generic-polytope} containing $A(\theta)$; and verifies the inclusion property:
+Set representation: interval prediction
+
 \begin{equation}
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=0.3\textwidth]{img/interval-hull}
-    \caption{A few trajectories are sampled from an initial state $x_0$ following a policy $\bu=(u_0,\cdots)$ with various parameters $\theta$ (in black).
-The union of reachability sets is shown in green, and its interval hull in red.}
-    \label{fig:interval-hull}
-\end{figure}
-
 We consider interval prediction rather than zonotope prediction for instance, for the sake of simplicity of implementation and computational efficiency.
-Among interval prediction algorithms, we consider the algorithm from \citep{leurent2019interval}, which produces tighter and more stable predictions than other baselines, and whose stability can be assessed simply in terms of LMI.
-The price to pay for this improved stability is the requirement of an additional assumption:
+
+A simple solution is proposed in \citep{efimov:hal-00701643}, where they use matrix interval arithmetics to derive the predictor:
+\begin{proposition}
+Assuming that \eqref{eq:polytope} is satisfied for the system \eqref{eq:dynamics}, then the interval predictor:
+\begin{eqnarray}
+\dot{\underline{x}}(t) & = & \underline{A}^{+}\underline{x}^{+}(t)-\overline{A}^{+}\underline{x}^{-}(t)-\underline{A}^{-}\overline{x}^{+}(t)\nonumber \\
+ &  & +\overline{A}^{-}\overline{x}^{-}(t)+B^{+}\underline{d}(t)-B^{-}\overline{d}(t),\label{eq:IP_direct}\\
+\dot{\overline{x}}(t) & = & \overline{A}^{+}\overline{x}^{+}(t)-\underline{A}^{+}\overline{x}^{-}(t)-\overline{A}^{-}\underline{x}^{+}(t)\nonumber \\
+ &  & +\underline{A}^{-}\underline{x}^{-}(t)+B^{+}\overline{d}(t)-B^{-}\underline{d}(t),\nonumber \\
+ &  & \underline{x}(0)=\underline{x}_{0},\;\overline{x}(0)=\overline{x}_{0},\nonumber 
+\end{eqnarray}
+ensures the inclusion property \eqref{eq:inclusion-property}.
+\end{proposition}
+
+However, \citet{leurent2019interval} showed that this predictor can have very unstable dynamics, even for stable systems, which can cause a rapid build-up of uncertainty and produce over-cautious behaviours.
+They propose an enhanced predictor which produces tighter and more stable predictions, and whose stability can be assessed by solving a linear matrix inequality, at the price of an additional requirement:
 
 \begin{assumption}
+\label{assumpt:metzler}
 There exists an orthogonal matrix $P\in\Real^{d\times d}$ such that $P^\transp A_0 P$ is Metzler, that is, all non-diagonal coefficients are non-negative.
@@
 \citep{abbasi-yadkori11a,abeille18a}.
-Under this assumption, without loss of generality up to a change of basis $x\rightarrow P^{-1}x$ that we do not write for the sake of readability, we can consider that $A_0$ itself is Metzler.
+Under this assumption, without loss of generality up to a change of basis $x\rightarrow P^{-1}x$ that we do not write for the sake of readability, this assumption is equivalent to considering that $A_0$ itself is Metzler.
 
@@
 \label{thm:predictor}
-Assuming that \eqref{eq:polytope} is satisfied for the system \eqref{eq:dynamics}, then the interval predictor:
+Assuming that \eqref{eq:polytope} and \autoref{assumpt:metzler} are satisfied for the system \eqref{eq:dynamics}, then the interval predictor:
 \begin{eqnarray}
@@
 \begin{definition}[Surrogate objective]
-We approximate the robust objective $V^r$ in \eqref{eq:robust-control} by replacing the true reachability set by its interval prediction $[\underline{x}(t), \overline{x}(t)]$ based on the dynamics confidence region $\cC_\delta$:
+We approximate the robust objective $V^r$ in \eqref{eq:robust-control} by considering its interval prediction $[\underline{x}(t), \overline{x}(t)]$ based on the dynamics confidence region $\cC_\delta$:
 
@@
 
-This does not simply amounts to a change of reward function, since the worst case is assessed over the whole past trajectory being optimized, which means that this pessimistic reward $\underline{R}$ is not \emph{markovian}.
+This does not simply amounts to a change of reward function, since the worst case is assessed over the whole past trajectory being optimized, which means that this pessimistic reward $\underline{R_n}$ is not \emph{markovian}.
 
@@
 
+% \begin{algorithm}[tb]
+%   \caption{Robust Estimation, Prediction and Control (v1)}
+%   \label{alg:full}
+% \begin{algorithmic}
+%   \STATE {\bfseries Input:} confidence level $\delta$
+%   \FOR{$N = 1,2,3,\dots$} 
+%   \STATE Compute the dynamics confidence region $\cC_{[N],\delta}$ with \textsc{Model Estimation} \eqref{eq:generic-polytope} on $\cD_{[N]}$.
+%   \FOR{planning steps $k\in[K]$}
+%   \STATE Get the tree node $\bu_k$ to expand with \textsc{Pessimistic Planning}  \eqref{eq:opd} using $\underline{R_n}$ over $[\underline{x}_{n}, \overline{x}_{n}]$. \COMMENT{Selection}
+%   \STATE For each action, simulate the child transition $[\underline{x}_{n+1}, \overline{x}_{n+1}]$ with \textsc{Interval Prediction} \eqref{eq:interval-predictor} using $\cC_{[N],\delta}$.
+\COMMENT{Expansion}
+%   \ENDFOR
+%   \STATE Execute the first recommended control $u_N$, and add the observed transition $(x_N, u_N, \dot{x}_N)$ to $\cD_{[N+1]}$.
+%   \ENDFOR
+% \end{algorithmic}
+% \end{algorithm}
+
 \begin{algorithm}[tb]
-   \caption{Robust Estimation, Prediction and Control (v1)}
+	\caption{Robust Estimation, Prediction and Control}
 	\label{alg:full}
-\begin{algorithmic}
-   \STATE {\bfseries Input:} confidence level $\delta$
-   \FOR{$N = 1,2,3,\dots$} 
-   \STATE Compute the dynamics confidence region $\cC_{[N],\delta}$ with \textsc{Model Estimation} \eqref{eq:generic-polytope} on $\cD_{[N]}$.
-   \FOR{planning steps $k\in[K]$}
-   \STATE Get the tree node $\bu_k$ to expand with \textsc{Pessimistic Planning}  \eqref{eq:opd} using $\underline{R_n}$ over $[\underline{x}_{n}, \overline{x}_{n}]$. \COMMENT{Selection}
-   \STATE For each action, simulate the child transition $[\underline{x}_{n+1}, \overline{x}_{n+1}]$ with \textsc{Interval Prediction} \eqref{eq:interval-predictor} using $\cC_{[N],\delta}$.
-\COMMENT{Expansion}
-   \ENDFOR
-   \STATE Execute the first recommended control $u_N$, and add the observed transition $(x_N, u_N, \dot{x}_N)$ to $\cD_{[N+1]}$.
-   \ENDFOR
-\end{algorithmic}
-\end{algorithm}
-
-\begin{algorithm}[tb]
-	\caption{Robust Estimation, Prediction and Control (v2)}
 	\begin{algorithmic}
@@
 
-The procedure we developed in sections \ref{sec:estimation}, \ref{sec:prediction} and \ref{sec:control} relies on restrictive modelling assumptions, such as the linear dynamics \eqref{eq:dynamics} or \autoref{assumpt:linear_param}.
+The procedure we developed in sections \ref{sec:estimation}, \ref{sec:prediction} and \ref{sec:control} relies on restrictive modelling assumptions, such as the linear dynamics \eqref{eq:dynamics} or \autoref{assumpt:structure}.
 But what if they are wrong?
@@
 An illustration of the computation of the robust b-values is presented in Figure \ref{fig:drop}.
+From this definition we introduce Algorithm \ref{algo:drop}, and analyse its sample-efficiency in Theorem \ref{theorem:drop-regret}.
 
@@
 
-From this definition we introduce Algorithm \ref{algo:drop}, and analyse its sample-efficiency in Theorem \ref{theorem:drop-regret}.
-
-%\begin{algorithm}[tp]
-%\DontPrintSemicolon
-%Initialize $\mathcal{T}$ to a root and expand it. Set $n=1$.\;
-%\While{Numerical resource available for episode $n$}{
-%Compute the robust b-values $b^r_i(n)$.\;
-%Expand the leaf $\argmax_{i\in \mathcal{L}_n} b^r_i(n)$.\;
-%}
-%\Return $\argmax_{a\in \mathcal{A}} u^r_a(n)$
-%\caption{Deterministic Robust Optimistic Planning}
-%\label{algo:drop}
-%\end{algorithm}
-
 \begin{theorem}[Regret bound]
 \label{theorem:drop-regret}
-The simple regret of Algorithm \ref{algo:drop} after $T$ iterations is:
-
-\begin{equation}
-\text{If } \kappa>1,\qquad 
-v^r - v^r_{a_T} = O\left(T^{-\frac{\log 1/\gamma}{\log \kappa}}\right)
-\end{equation}
-
-\begin{equation}
-\text{If }\kappa=1,\qquad
-v^r - v^r_{a_T} = O\left(\gamma^{\frac{(1-\gamma)^\beta}{c}T}\right)
-\end{equation}
+\texttt{ROPD} enjoys the same regret bound as provided for \texttt{OPD} in \autoref{theorem:opd-regret}.
 \end{theorem}
 
+The caveat is that $K$ measures the number of planning iterations, but actually expanding a node requires the simulation of $M$ time more transitions for each action than in the non-robust single-model setting.
+
 \section{Experiments}
 
+\paragraph{Obstacle avoidance with unknown friction}
+We first consider a simple illustrative example: the control of a $2D$-
+\paragraph{Behavioural planning for an autonomous vehicle}
 We consider the problem of safe decision-making for an autonomous vehicle.
-An autonomous vehicle is driving on a highway populated with $N$ other agents, and uses Model Predictive Control to plan a sequence of decisions.
-To that end, it relies on parametrized dynamical model for each agent to predict the future trajectory of each traffic participant: \[\dot{z}_i=f_i(Z,\theta_i),\;i=\overline{1,N},\] where $f_i$ are described below, $z_i\in\Real^4$ is the state of an agent, $Z = [z_1,\dots,z_N]^\top\in\Real^{4N}$ and $\theta_i\in\Real^5$ is the corresponding vector of unknown parameters.
-Crucially, this system describes the couplings and interactions between vehicles, so that the autonomous agent can properly anticipate their reactions.
-However, we assume that we do not have access to the true values of the behavioural parameters $\theta=[\theta_1,\dots,\theta_N]^\top$; instead, we merely know that these parameters lie in a set of admissible values $\Theta\subset\Real^{5N}$.
-In order to act safely in the face of uncertainty, we follow the framework of robust decision-making: the agent must consider all the possible trajectories in the space of $Z$ that each vehicle can follow in order to take its decisions.
-In this work, we focus on how to compute these trajectory enclosures through interval prediction.
+An autonomous vehicle with state $\chi_0\in\Real^4$ is driving on a highway populated with $V$ other vehicles with states $\chi_i\in\Real^4$, resulting in a joint traffic state $x = [\chi_0, \chi_1,\dots,\chi_V]^\top\in\Real^{4V+4}$.
+In order to plan a sequence of high-level decisions, the autonomous agent relies on both a model of its own dynamics $\chi_0 = f_0(\chi_0,u)$, but also a parametrized dynamical model for each observed agent to predict their future trajectory: \[\dot{\chi}_i=f_i(x,\theta_i),\;i\in[V],\] where $f_i$ are described below, $\chi_i\in\Real^4$ is the state of an agent, $\theta_i\in\Real^5$ is the corresponding vector of unknown parameters.
+Crucially, this system $f$ describes the couplings and interactions between vehicles, so that the autonomous agent can properly anticipate their reactions.
+Already, we can appreciate a first advantage of the imposed structure \autoref{assumpt:structure}: the uncertainty space of $\theta$ is $\Real^{5V}$.
+In comparison, the traditional adaptive LQ setting where the whole state matrix $A$ is estimated would have resulted in a much larger parameter space $\theta\in\Real^{16V^2}$.
+% In order to act safely in the face of uncertainty, we follow the framework of robust decision-making: the agent must consider all the possible trajectories in the space of $Z$ that each vehicle can follow in order to take its decisions.
 

### 2020-01-20 main.tex
Little bit of related work

@@
 
-We leverage known techniques from the uncertain system simulation literature to efficiently compute such a predictor.
+We leverage recent results from the uncertain system simulation literature to efficiently compute such a predictor.
 
@@
 
-For LQ systems, where parameters A,B are unknown and no structure is available.
-\begin{itemize}
-    \item OFU: \citep{abbasi-yadkori11a}.
-Summary: $\theta=(A~B)$, ellipsoid in Frobenius norm + controllability constraint, choose and stabilize (Ricatti) an optimistic candidate, cumulative regret in $O(\sqrt{T}\log\frac{1}{\delta})$.
-    \item PSRL with TS: \citep{abeille18a}.
-Summary: RLS estimate + normal perturbation in the ellipsoid + rejection sampling over a controllability constraint, with frequent update, cumulative regret in $\tilde{O}(\sqrt{T})$
-    \item Offline estimation and control synthesis: \citep{Dean2017}.
+\paragraph{LQ systems} There is a rich body of literature dedicated to the study of LQ systems, and we focus on those providing non-asymptotic results when the system parameters $A, B$ are unknown.
+In their seminal work \citet{abbasi-yadkori11a}, consider the problem of cumulative regret minimisation.
+They follow the \emph{Optimism in the Face of Uncertainty} paradigm from the multi-armed bandit literature, that consists in selecting an optimistic system within a high-confidence region while enforcing a controllability constraint, and computing the corresponding optimal control in closed-form by solving a Riccati equation.
+They show that this procedures achieves a $\tilde{\cO}\left(T^{1/2}\right)$ cumulative regret.
+\citet{abeille18a} provide the same result by applying Thomson Sampling rather of optimism to select a dynamical model, and rejection sampling to enforce the controllability constraint.
+While previous methods suffered from limited applicability and computationally intractable subroutines, \citep{Dean2018} provide a polynomial-time algorithm which achieves a suboptimal cumulative regret of $\tilde{\cO}\left(T^{2/3}\right)$.
+
+Offline estimation and control synthesis: \citep{Dean2017}.
 Summary: Estimation procedure of $N$ episodes of duration $T$ with gaussian excitation, ellipsoid in L2 norm, robust controller with System Level Synthesis, simple regret in $O(\sqrt{\frac{\log(1/\delta)}{N}})$
-    \item \citep{Dean2018}
-\end{itemize}
-
-Differences with our work:
 
@@
 
-    Thus, we do not wish to explore actively the more promising regions as in OFU, nor the more likely region as in TS, nor act randomly as in Coarse-ID.
+Thus, we do not wish to explore actively the more promising regions as in OFU, nor the more likely region as in TS, nor act randomly as in Coarse-ID They inject exploration noise.
 
 We have linear dynamics but our cost is not quadratic.
+Quadratic cost: stabilize a system around a reference trajectory known a priori.
 Thus, we can accurately represent planning tasks with discrete/branching decisions involving discontinuities (e.g.
@@
 
-Robust optimization has been studied in the context of finite Markov Decision Processes (MDP) with uncertain parameters by Iyengar (2005), Nilim and El Ghaoui (2005) and Wiesemann et al.
-(2013).They show that the main results of Dynamic Programming can be extended to their robust counterparts only when the dynamics ambiguity set verifies certain rectangularity properties, which can be seen as an independance assumption:
+\paragraph{Robust planning}
+Robust optimization has been studied in the context of finite Markov Decision Processes with uncertain parameters by Iyengar (2005), Nilim and El Ghaoui (2005) and Wiesemann et al.
+(2013).
+They show that the main results of Dynamic Programming can be extended to their robust counterparts only when the dynamics ambiguity set verifies a certain rectangularity property, that amounts to an independence assumption between the uncertainty sets of each transition and is related to time-varying uncertainty.
+They do not consider continuous states, nor handle time-invariant uncertainty.
+We do so by not relying on a dynamic programming evaluation of the robust cost-to-go, but on monte-carlo estimates along a full trajectory.
 
@@
 
-We also assume that some bound $S$ over $\|\theta\|_\infty$ is known.
+We also assume to know an upper-bound $S$ over $\|\theta\|_\infty$.
 \end{assumption}
@@
 
-\begin{proposition}[Theorem 1 of \citep{Abbasi2011}, Matrix version]
-\label{prop:concentration}
-Let $\{F_n\}_{n=0}$ be a filtration.
-Let $\{\eta_n\}_{n=1}^\infty$ be a $\Real^p$-valued stochastic process such that $\eta_n$ is $F_n$-measurable and $\expectedvalue\left[\eta_n\condbar F_{n-1}\right]$ is $\Sigma_p$-sub-Gaussian.
-
-Let $\{\Phi_n\}_{n=1}^\infty$ be an $\Real^{p\times d}$-valued stochastic process such that $\Phi_n$ is $F_n$-measurable.
-Assume that $G$ is a $d\times d$ positive definite matrix.
-For any $n\geq 0$, define:
-\begin{equation*}
-    \overline{G}_n = G + \sum_{s=1}^n \Phi_s^\transp \Sigma_p^{-1} \Phi_s \in \Real^{d\times d} \quad S_n = \sum_{s=1}^n \Phi_s^\transp\Sigma_p^{-1}\eta_s \in \Real^{d}.
-\end{equation*}
-Then, for any $\delta>0$, with probability at least $1-\delta$, for all $n\geq0$,
-\begin{align*}
-\| S_n \|_{\overline{G}_n^{-1}} \geq \sqrt{2\ln \left(\frac{\det\left(\overline{G}_n\right)^{1/2}}{\delta\det(G)^{1/2}}\right)}.
-\end{align*}
-\end{proposition}
-
-\begin{theorem}[Confidence ellipsoid]
+\begin{theorem}[Confidence ellipsoid of \citep{Abbasi2011}, Matrix version]
 \label{thm:confidence_ellipsoid}
@@
 
-Another strategy presented in \autoref{sec:tight-polytope} produces a much tighter polytope, at the price of an increased computational cost required by the diagonalization of $G_{N,\lambda}$.
+Another strategy presented in \autoref{sec:tight-polytope} produces a much tighter polytope, at the price of an increased computational cost required by the diagonalisation of $G_{N,\lambda}$.
 
@@
 
-However, \citet{leurent2019interval} showed that this predictor can have very unstable dynamics, even for stable systems, which can cause a rapid build-up of uncertainty and produce over-cautious behaviours.
+However, \citet{leurent2019interval} showed that this predictor can have unstable dynamics, even for stable systems, which can cause a rapid build-up of uncertainty and produce over-conservative behaviours.
 They propose an enhanced predictor which produces tighter and more stable predictions, and whose stability can be assessed by solving a linear matrix inequality, at the price of an additional requirement:
@@
 In practice, this assumption is often verified.
-It is for instance the case whenever $A_0$ is diagonalizable.
-The similarity transformation of \citep{Efimov_a2013} provides a method to compute such $P$ whenever there exist $C_1,C_2$ which make $A(\theta)$ and $A_0$ is observable.
-Note that similar requirements involving the controllability of $A_0$ exist the literature of the LQ setting, see e.g.
-\citep{abbasi-yadkori11a,abeille18a}.
+It is for instance the case whenever $A_0$ is diagonalisable, and a fortiori when it is stabilisable.
+The similarity transformation of \citep{Efimov_a2013} provides a method to compute such $P$ whenever there exist $C_1,C_2$ which make $A(\theta, C_1)$ and $(A_0, C_2)$ observable.
 Under this assumption, without loss of generality up to a change of basis $x\rightarrow P^{-1}x$ that we do not write for the sake of readability, this assumption is equivalent to considering that $A_0$ itself is Metzler.
@@
 
-\subsection{Proof of \autoref{prop:concentration}}
-
+\subsection{Proof of \autoref{thm:confidence_ellipsoid}}
+
+We start by showing a preliminary proposition:
+
+\begin{proposition}[Theorem 1 of \citep{Abbasi2011}, Matrix version]
+\label{prop:concentration}
+Let $\{F_n\}_{n=0}$ be a filtration.
+Let $\{\eta_n\}_{n=1}^\infty$ be a $\Real^p$-valued stochastic process such that $\eta_n$ is $F_n$-measurable and $\expectedvalue\left[\eta_n\condbar F_{n-1}\right]$ is $\Sigma_p$-sub-Gaussian.
+
+Let $\{\Phi_n\}_{n=1}^\infty$ be an $\Real^{p\times d}$-valued stochastic process such that $\Phi_n$ is $F_n$-measurable.
+Assume that $G$ is a $d\times d$ positive definite matrix.
+For any $n\geq 0$, define:
+\begin{equation*}
+    \overline{G}_n = G + \sum_{s=1}^n \Phi_s^\transp \Sigma_p^{-1} \Phi_s \in \Real^{d\times d} \quad S_n = \sum_{s=1}^n \Phi_s^\transp\Sigma_p^{-1}\eta_s \in \Real^{d}.
+\end{equation*}
+Then, for any $\delta>0$, with probability at least $1-\delta$, for all $n\geq0$,
+\begin{align*}
+\| S_n \|_{\overline{G}_n^{-1}} \geq \sqrt{2\ln \left(\frac{\det\left(\overline{G}_n\right)^{1/2}}{\delta\det(G)^{1/2}}\right)}.
+\end{align*}
+\end{proposition}
 \begin{proof}
-
 Let 
@@
 $\expectedvalue[M_\tau^z] = \expectedvalue[\liminf_{t\to\infty} M_{\min(\tau,t)}^z] \leq \liminf_{t\to\infty} \expectedvalue[M_{\min(\tau,t)}^z] \leq 1.$
-
-% The following uses the method of mixtures.
-% Let $\Gamma$ be a Gaussian random variable which is independent of all other random variables and whose covariance is $\Sigma^{-1}$. (in our estimator, $\Sigma = \lambda$).
-
-% Define 
-% \[
-% M_t = \expectedvalue \left[M_t^\Gamma \condbar F_\infty\right]
-% \]
-
-% where $F_\infty$ is the tail $\sigma$-algebra of the filtration. Clearly, we still have $\expectedvalue[M_\tau] = \expectedvalue[\expectedvalue[M_\tau^\Gamma|\Gamma]]\leq 1$.
-
-% Let us calculate $M_t$. Let $f$ denote the density of $\Gamma$ and for a positive definite matrix $P$ let $c(P) = \sqrt{(2\pi)^d/\det(P)} = \int \exp (-\frac{1}{2}x^\transp P x)$
 
@@
 
-\subsection{Proof of \autoref{thm:confidence_ellipsoid}}
+Having shown this preliminary result, we move on to the proof of \autoref{thm:confidence_ellipsoid}.
 
 \begin{proof}
-
-Hence, for all $x\in\Real^d$,
+For all $x\in\Real^d$, \eqref{eq:vector_rls} gives:
 \begin{align*}

### 2020-01-25 main.tex
Updates from Overleaf

@@
 
-Since $R$ is arbitrary, solving the optimal -- not to mention the robust -- control objective in the original continuous control space $(\Real q)^\Natural$ is intractable.
+Since $R$ is arbitrary, solving the optimal -- not to mention the robust -- control objective in the original continuous control space $(\Real^q)^\Natural$ is intractable.
 In this work, we choose to approximate the solution by turning the continuous optimisation problem \eqref{eq:robust-control} into a discrete one, by optimising over a finite set of \emph{actions} $\cA$.
@@
 They show that the main results of Dynamic Programming can be extended to their robust counterparts only when the dynamics ambiguity set verifies a certain rectangularity property, that amounts to an independence assumption between the uncertainty sets of each transition and is related to time-varying uncertainty.
+L1/KL ball around the empirical transition.
 They do not consider continuous states, nor handle time-invariant uncertainty.
@@
     &h_k \text{ is the }k^\text{th}\text{ element of }\{-1,1\}^d\text{ for } k\in[2^d],\\
-    &G_{N,\lambda}^{-1} = PDP^{-1}, \quad \Delta\theta_k = C_{N,\lambda,\delta}^{1/2} P^{-1}D^{-1/2} h_k, \\
+    &G_{N,\lambda} = PDP^{-1}, \quad \Delta\theta_k = \beta_{N}(\delta)^{1/2} P^{-1}D^{-1/2} h_k, \\
     &A_0 = A + \theta_{N,\lambda}^\transp\Phi, \quad \Delta A_k = \Delta\theta_k^\transp\Phi.
@@
     \theta\in\cC_\delta &\implies
-    (\theta-\theta_{N,\lambda})^\transp G_{N,\lambda}^{-1}(\theta-\theta_{N,\lambda}) \leq C_{N,\lambda,\delta}\\
-    &\implies (\theta'-\theta'_{N,\lambda})^\transp D (\theta'-\theta'_{N,\lambda}) \leq C_{N,\lambda,\delta}\\
-    &\implies \sum_{i=1}^d D_{i,i}(\theta'_i-\theta'_{N,\lambda,i})^2\leq C_{N,\lambda,\delta}\\
-    &\implies\forall i, |\theta'_i-\theta'_{N,\lambda,i}|\leq C_{N,\lambda,\delta}^{1/2}D_{i,i}^{-1/2}
-\end{align*}
-This describes a $\Real^d$ box containing $\theta' = P\theta$, whose $k^\text{th}$ vertex is represented by $\theta_{N,\lambda}' + C_{N,\lambda,\delta}^{1/2}D^{-1/2} h_k$.
+    (\theta-\theta_{N,\lambda})^\transp G_{N,\lambda}(\theta-\theta_{N,\lambda}) \leq \beta_{N}(\delta)\\
+    &\implies (\theta'-\theta'_{N,\lambda})^\transp D (\theta'-\theta'_{N,\lambda}) \leq \beta_{N}(\delta)\\
+    &\implies \sum_{i=1}^d D_{i,i}(\theta'_i-\theta'_{N,\lambda,i})^2\leq \beta_{N}(\delta)\\
+    &\implies\forall i, |\theta'_i-\theta'_{N,\lambda,i}|\leq \beta_{N}(\delta)^{1/2}D_{i,i}^{-1/2}
+\end{align*}
+This describes a $\Real^d$ box containing $\theta' = P\theta$, whose $k^\text{th}$ vertex is represented by $\theta_{N,\lambda}' + \beta_{N}(\delta)^{1/2}D^{-1/2} h_k$.
 We obtain the corresponding box on $\theta$ by transforming each vertex of the box with $P^{-1}$.

### 2020-01-25 main.tex
Minor updates

@@
 \begin{abstract}
-	We develop a framework for the adaptive control of a linear system with unknown parameters and arbitrary costs in a critical setting where failures are costly and should be prevented at all time.
+	We develop a framework for the adaptive control of a linear system with unknown parameters and arbitrary costs, in a critical setting where failures are costly and should be prevented at all time.
 We build on two ideas: first, we incorporate prior knowledge of the dynamics in the form of a known structure of the uncertainty, which can be tightened as we collect interaction data by building high-confidence regions through least-square regression.
 Second, we act in a cautious way with respect to this uncertainty by formulating a robust objective, that we solve approximately in a prediction-optimisation manner, leveraging tools from interval prediction and sequential planning literatures.
-Additionally, we relax our modelling assumptions by proposing an extension based on multi-model selection and aggregation.
-The full procedure is designed to produce reasonable and safe behaviour at deployment, get more aggressive with time, and be asymptotically optimal.
+We eventually relax our modelling assumptions by proposing an extension based on multi-model selection and aggregation.
+The full procedure is designed to produce reasonable and safe behaviour at deployment, get closer to optimality with time, and be asymptotically optimal.
 We illustrate it on a practical case of autonomous driving at an intersection.
@@
 Our second contribution is to propose to solve \eqref{eq:robust-control} numerically by adopting a \emph{predict-then-optimise} scheme.
-Thus, in \autoref{sec:prediction}, as illustrated in \autoref{fig:interval-hull}, we aim to derive a \emph{set predictor} $X(t)$ for the system \eqref{eq:dynamics}, which takes the information on the observed current state ${x}_N$, a confidence region $\cC_\delta$ containing $A(\theta)$, a planned control sequence $\bu$ and some admissible bounds on the perturbation $[\underline{\omega}(t),\overline{\omega}(t)]$; and verifies the inclusion property:
+Thus, in \autoref{sec:prediction}, we aim to derive a \emph{set predictor} $X(t)$ for the system \eqref{eq:dynamics}, which takes the information on the observed current state ${x}_N$, a confidence region $\cC_\delta$ containing $A(\theta)$, a planned control sequence $\bu$ and some admissible bounds on the perturbation $[\underline{\omega}(t),\overline{\omega}(t)]$; and produces predictions that verify the inclusion property:
 \begin{equation}
@@
 
-We leverage recent results from the uncertain system simulation literature to efficiently compute such a predictor.
+This property is illustrated in \autoref{fig:interval-hull}. We leverage recent results from the uncertain system simulation literature to efficiently compute such a predictor.
 
@@
 
-Set representation: interval prediction
+We consider interval prediction rather than zonotope prediction for instance, for the sake of simplicity of implementation and computational efficiency.
+Thus, we represent an interval as $X(t) = [\underline{x}(t), \overline{x}(t)]\in \Real^p\times \Real^p$, and the inclusion property becomes:
 
@@
 
-We consider interval prediction rather than zonotope prediction for instance, for the sake of simplicity of implementation and computational efficiency.
-
-A simple solution is proposed in \citep{efimov:hal-00701643}, where they use matrix interval arithmetics to derive the predictor:
+A simple solution to \eqref{eq:inclusion-property} is proposed in \citep{efimov:hal-00701643}, where they use matrix interval arithmetics to derive the predictor:
 \begin{proposition}
@@
 \label{sec:control}
+We approximate the robust objective $V^r$ in \eqref{eq:robust-control} by considering its interval prediction $[\underline{x}(t), \overline{x}(t)]$ based on the dynamics confidence region $\cC_\delta$.
 
 \begin{definition}[Surrogate objective]
-We approximate the robust objective $V^r$ in \eqref{eq:robust-control} by considering its interval prediction $[\underline{x}(t), \overline{x}(t)]$ based on the dynamics confidence region $\cC_\delta$:
-
 \begin{align}
@@
 Crucially, this system $f$ describes the couplings and interactions between vehicles, so that the autonomous agent can properly anticipate their reactions.
-Already, we can appreciate a first advantage of the imposed structure \autoref{assumpt:structure}: the uncertainty space of $\theta$ is $\Real^{5V}$.
+Already, we can appreciate a first advantage of the structure imposed in \autoref{assumpt:structure}: the uncertainty space of $\theta$ is $\Real^{5V}$.
 In comparison, the traditional adaptive LQ setting where the whole state matrix $A$ is estimated would have resulted in a much larger parameter space $\theta\in\Real^{16V^2}$.

### 2020-02-03 main.tex
Updates from Overleaf

@@
 \usepackage{blkarray}
-\usepackage{todonotes}
 \usepackage{mathtools}
 \input{mathdef.tex}
+\newcommand{\todo}[1]{\textcolor{red}{#1}}
 
@@
 	\twocolumn[
-	\icmltitle{Robust Estimation, Prediction and Control with \\ Linear Dynamics and Arbitrary Costs}
+	\icmltitle{Robust Estimation, Prediction and Control with \\ Linear Dynamics and Generic Costs}
 
@@
 \begin{abstract}
-	We develop a framework for the adaptive control of a linear system with unknown parameters and arbitrary costs, in a critical setting where failures are costly and should be prevented at all time.
-We build on two ideas: first, we incorporate prior knowledge of the dynamics in the form of a known structure of the uncertainty, which can be tightened as we collect interaction data by building high-confidence regions through least-square regression.
-Second, we act in a cautious way with respect to this uncertainty by formulating a robust objective, that we solve approximately in a prediction-optimisation manner, leveraging tools from interval prediction and sequential planning literatures.
-We eventually relax our modelling assumptions by proposing an extension based on multi-model selection and aggregation.
-The full procedure is designed to produce reasonable and safe behaviour at deployment, get closer to optimality with time, and be asymptotically optimal.
-We illustrate it on a practical case of autonomous driving at an intersection.
+We develop a framework for the adaptive model predictive control of a linear system with unknown parameters and arbitrary bounded costs, in a critical setting where failures are costly and should be prevented at all time.
+Our approach builds on two ideas: first, we incorporate prior knowledge of the dynamics in the form of a known structure that shapes uncertainty, which can be tightened as we collect interaction data by building high-confidence regions through least-square regression.
+Second, in order to handle this uncertainty we formulate a robust control objective.
+Leveraging tools from interval prediction literature, we convert the confidence regions on parameters into confidence sets on trajectories induced by the controls.
+These controls are then optimised resorting to tree-based planning methods.
+We eventually relax our modeling assumptions with a multi-model extension based on a data-driven robust model selection mechanism.
+The full procedure is designed to produce reasonable and safe behaviours at deployment while recovering an asymptotic optimality.
+We illustrate it on a practical case of autonomous driving at a crossroads intersection among vehicles with uncertain behaviours.
 \end{abstract}
@@
 \probability{A(\theta)\in \cC_{[N],\delta}} \geq 1-\delta
-\label{eq:polytope}
+\label{eq:confidence}
 \end{align}
@@
 
-By Hölder inequality, we obtain a confidence region $\cC_\delta$ defined by a $L_1$-ball, i.e. a polytope with $2d$ vertices:
+By Hölder inequality, we obtain a confidence region $\cC_{[N],\delta}$ defined by a $L_1$-ball, i.e. a polytope with $2d$ vertices:
 \begin{equation}
@@
 
-There may be cases where \autoref{assumpt:bounded-noise} does not hold, for instance if the noise $\eta$ is Gaussian, which implies $\|\eta\|_\infty=+\infty$ and makes \eqref{eq:bounded-noise-polytope} uninformative.
-Then, another weaker assumption can be made.
+There may be cases where \autoref{assumpt:bounded-noise} does not hold.
+For instance, when the noise $\eta$ is Gaussian, then $\|\eta\|_\infty=+\infty$ which makes \eqref{eq:bounded-noise-polytope} uninformative.
+Then, a weaker assumption can be made.
 
 \subsection{Sub-Gaussian noise}
-
-We say that a random vector $x\in\Real^k$ is sub-Gaussian with covariance proxy $\Sigma$, and denote $x\sim Sub_G(\Sigma)$, if $\expectedvalue[x] = 0_k$ and:
-\[
-\forall u\in\Real^k, \expectedvalue \left[ \exp{\left( u^\transp x\right)}\right] \leq \exp{\left( \frac{1}{2} u^\transp \Sigma u\right)}
-\]
 
@@
 \begin{equation*}
-    \eta(t) \sim Sub_G(\Sigma_p).
+    \forall u\in\Real^k,\, \expectedvalue \left[ \exp{\left( u^\transp \eta(t)\right)}\right] \leq \exp{\left( \frac{1}{2} u^\transp \Sigma_p u\right)}
 \end{equation*}
@@
 
-\begin{theorem}[Confidence ellipsoid of \citep{Abbasi2011}, Matrix version]
+\begin{theorem}[Confidence ellipsoid, matrix version of \citep{Abbasi2011}]
 \label{thm:confidence_ellipsoid}
@@
 
-We can enclose this confidence ellipsoid $\eqref{eq:confidence-ellipsoid}$ into a polytope $C_\delta$.
+We can enclose this confidence ellipsoid $\eqref{eq:confidence-ellipsoid}$ into a polytope $C_{[N],\delta}$.
 For simplicity, we present here a very simple but coarse strategy: bound the ellipsoid by its enclosing sphere, and the sphere by its enclosing hypercube:
 \begin{align}
-    \label{eq:generic-polytope}
-     &\cC_\delta = \left\{ A_{0}+\sum_{i=1}^{2^d}\lambda_{i}\Delta A_{i}: \lambda\in[0, 1]^{2^d},  \sum_{i=1}^{2^d}\lambda_{i}=1\right\},\\
+    \label{eq:polytope}
+     &\cC_{[N],\delta} = \left\{ A_{0}+\sum_{i=1}^{2^d}\lambda_{i}\Delta A_{i}: \lambda\in[0, 1]^{2^d},  \sum_{i=1}^{2^d}\lambda_{i}=1\right\},\\
      &A_0 = A + \theta_{N,\lambda}^\transp\phi, \quad\Delta A_{i} = h_i \sqrt{\frac{\beta_N(\delta)}{\lambda_{\max}(G_{N,\lambda})}}
@@
 \begin{proposition}
-Assuming that \eqref{eq:polytope} is satisfied for the system \eqref{eq:dynamics}, then the interval predictor:
+Assuming that \eqref{eq:confidence} is satisfied for the system \eqref{eq:dynamics}, then the interval predictor:
 \begin{eqnarray}
-\dot{\underline{x}}(t) & = & \underline{A}^{+}\underline{x}^{+}(t)-\overline{A}^{+}\underline{x}^{-}(t)-\underline{A}^{-}\overline{x}^{+}(t)\nonumber \\
- &  & +\overline{A}^{-}\overline{x}^{-}(t)+B^{+}\underline{d}(t)-B^{-}\overline{d}(t),\label{eq:IP_direct}\\
-\dot{\overline{x}}(t) & = & \overline{A}^{+}\overline{x}^{+}(t)-\underline{A}^{+}\overline{x}^{-}(t)-\overline{A}^{-}\underline{x}^{+}(t)\nonumber \\
- &  & +\underline{A}^{-}\underline{x}^{-}(t)+B^{+}\overline{d}(t)-B^{-}\underline{d}(t),\nonumber \\
+\dot{\underline{x}}(t) & = & \underline{A}^{+}\underline{x}^{+}(t)-\overline{A}^{+}\underline{x}^{-}(t)-\underline{A}^{-}\overline{x}^{+}(t) +\overline{A}^{-}\overline{x}^{-}(t)\nonumber \\
+ &  &+Bu(t) + D^{+}\underline{\omega}(t)-D^{-}\overline{\omega}(t),\label{eq:IP_direct}\\
+\dot{\overline{x}}(t) & = & \overline{A}^{+}\overline{x}^{+}(t)-\underline{A}^{+}\overline{x}^{-}(t)-\overline{A}^{-}\underline{x}^{+}(t)+\underline{A}^{-}\underline{x}^{-}(t)\nonumber \\
+ &  &+Bu(t) + D^{+}\overline{\omega}(t)-D^{-}\underline{\omega}(t),\nonumber \\
  &  & \underline{x}(0)=\underline{x}_{0},\;\overline{x}(0)=\overline{x}_{0},\nonumber 
@@
 
-At each planning iteration $k\in[K]$, \texttt{OPD} progressively builds a tree $\cT_{k+1}$ by expanding the leaf $a_k$ with highest B-value, where the expansion of a leaf $a$ refers to the simulation of its children transitions $aA = \{ab, b\in A\}$:
+At each planning iteration $k\in[K]$, \texttt{OPD} progressively builds a tree $\cT_{k+1}$ by forming upper-bounds $B_a(k)$ over the sequence values called B-values, and expanding\footnote{The expansion of a leaf node $a$ refers to the simulation of its children transitions $aA = \{ab, b\in A\}$} the leaf $a_k$ with highest B-value:
 \begin{equation}
@@
 		\FOR{$N = 1,2,3,\dots$} 
-		\STATE $\cC_{[N],\delta} \gets$\textsc{Model Estimation}$(\cD_{[N]})$. \eqref{eq:generic-polytope}
+		\STATE $\cC_{[N],\delta} \gets$\textsc{Model Estimation}$(\cD_{[N]})$. \eqref{eq:polytope}
 		\FOR{planning steps $k\in[K]$}
@@
 
-\section{Multi-model Aggregation}
+\section{Multi-model Selection}
+\label{sec:multi-model}
 
@@
 
-TODO: from $\cC$ to confidence regions for $y_{n+1}$.
-
-% Following \citep{maillard:hal-01349727}, we define the model adequacy for an observation $x(t), u(t), \dot{x}(t)$ of the modelling assumptions $(A, \phi)$ trained on history $\cD_{[N]}$ by:
-% \begin{equation*}
-%     \alpha(x(t), u(t), \dot{x}(t)) = \sup_\delta \argmin_{\delta\in(0,1)} d\left(\dot{x}(t), \cC_{[N],\delta}(x(t), u(t))\right)
-% \end{equation*}
-% where $d(\dot x,\cC(x,u)) = \inf_{\hat{A}\in\cC} \left\|\hat{A}x + Bu - \dot{x}\right\|^2 + \|\eta\|_\infty^2$.
-% An adequacy of $0$ indicates a strong match of the assumptions, while an adequacy of $1$ indicates a strong mismatch. The
-
-This metric gets useful in the context of model selection and aggregation: 
-This suggest using multiple models with different sets of features.
-
-\subsection{Robust aggregation}
+Given $N-1$ observations, the \autoref{sec:estimation} provides a polytopic confidence region \eqref{eq:polytope} that contains $A(\theta)$ with probability at least $1-\delta$.
+Since the dynamics are linear, we can propagate this confidence region to the next observation: $y_{N}$ must belong to the Minkowski sum of a polytope representing model uncertainty $\cP(A_{0} x_N + Bu_N, \Delta A_{1}x_N,\cdots \Delta A_{2^d}x_N)$ and a polytope $\cP(0_p, \underline{\eta}, \overline{\eta})$ bounding the perturbation and measurement noises.
+\citet{delos2015} provide a way to test this membership in polynomial time using linear programming.
+
+Whenever this membership property is not verified, we can confidently reject the $(A,\phi)$-modelling \autoref{assumpt:structure}.
+This enables us to consider a rich set of potential features $\left((A^1, \phi^1), \cdots, (A^M, \phi^M)\right)$ rather than relying on a single assumption.
+
+\paragraph{Robust selection}
 
@@
 \end{assumption}
-We want to adapt our planning algorithm in order to aggregate these concurrent hypotheses in a robust fashion, i.e. maximise a robust objective with discrete ambiguity:
-\[
-V^r = \max_{\bu}\min_{m\in[M]} \sum_{t=1}^\infty \gamma^t R_t^m
-\]
-where $R_t^m$ is the reward obtain by following the sequence $\bu$ up to step $t$ under the dynamics $f^m$.
-
-The traditional robust optimization procedures do not apply: Robust MDP: only with finite states (here continuous), and based on rectangular ambiguity.
-$\cH_\infty$ control also concern linear dynamics (which is not required under \autoref{assumpt:multi-model-ambiguity}) and .
+We want to adapt our planning algorithm in order to balance these concurrent hypotheses in a robust fashion, i.e. maximise a robust objective with discrete ambiguity:
+\begin{equation}
+\label{eq:robust-objective-discrete}
+V^r = \sup{\bu}\min_{m\in[M]} \sum_{t=1}^\infty \gamma^t R_t^m
+\end{equation}
+where $R_t^m$ is the reward obtain by following the control sequence $\bu$ up to step $t$ under the dynamics $f^m$.
+This objective could be optimised in the same way as \ref{sec:control}, by computing a hull over the $M$ possible trajectories, but this would result in a coarse and lossy approximation.
+Instead, we can exploit the finite uncertainty structure of \autoref{assumpt:multi-model-ambiguity} to asymptotically recover the true $V^r$ by modifying the \texttt{OPD} planning algorithm in the following way:
 
@@
 \end{definition}
-An illustration of the computation of the robust b-values is presented in Figure \ref{fig:drop}.
-From this definition we introduce Algorithm \ref{algo:drop}, and analyse its sample-efficiency in Theorem \ref{theorem:drop-regret}.
+An illustration of the computation of the robust b-values is presented in Figure \ref{fig:drop}. We analyse the sample complexity of the corresponding robust planning algorithm.
 
@@
 \includegraphics[width=0.4\linewidth]{img/robust-control-tree}
-\caption{The computation of robust B-values in Algorithm \ref{algo:drop}.
-The simulation of trajectories for every dynamics model $f^m$ is represented as stacked versions of the expanded tree $\mathcal{T}_n$.}
+\caption{The computation of robust B-values in \eqref{eq:robust-b-values}.
+The simulation of trajectories for every dynamics model $f^m$ is represented as stacked versions of the expanded tree $\mathcal{T}_k$.}
 \label{fig:drop}
@@
 
-The caveat is that $K$ measures the number of planning iterations, but actually expanding a node requires the simulation of $M$ time more transitions for each action than in the non-robust single-model setting.
+Note that this theorem bounds the performance gap with respect to the number of node expansions, but each expansion still requires $M$ time more simulations in the multi-model setting than in the single-model setting.
+The solution of the robust objective \eqref{eq:robust-objective-discrete} with discrete ambiguity $f\in\{f^m\}_{m\in[M]}$ can be recovered exactly, asymptotically when the planning budget $H$ goes to infinity.
+This is in contrast to the results obtained \autoref{sec:control} regarding the robust objective \eqref{eq:robust-control} with continuous ambiguity $A(\theta)\in\cC_{[N],\delta}$, for which there is a gap between the asymptotic performance and the true robust value, as discussed in \autoref{prop:control-error}.
 
@@
 
-\paragraph{Obstacle avoidance with unknown friction}
-We first consider a simple illustrative example: the control of a $2D$-
+% \paragraph{Obstacle avoidance with unknown friction}
+% We first consider a simple illustrative example: the control of a $2D$-
+
 \paragraph{Behavioural planning for an autonomous vehicle}
@@
 In order to plan a sequence of high-level decisions, the autonomous agent relies on both a model of its own dynamics $\chi_0 = f_0(\chi_0,u)$, but also a parametrized dynamical model for each observed agent to predict their future trajectory: \[\dot{\chi}_i=f_i(x,\theta_i),\;i\in[V],\] where $f_i$ are described below, $\chi_i\in\Real^4$ is the state of an agent, $\theta_i\in\Real^5$ is the corresponding vector of unknown parameters.
-Crucially, this system $f$ describes the couplings and interactions between vehicles, so that the autonomous agent can properly anticipate their reactions.
 Already, we can appreciate a first advantage of the structure imposed in \autoref{assumpt:structure}: the uncertainty space of $\theta$ is $\Real^{5V}$.
 In comparison, the traditional adaptive LQ setting where the whole state matrix $A$ is estimated would have resulted in a much larger parameter space $\theta\in\Real^{16V^2}$.
-% In order to act safely in the face of uncertainty, we follow the framework of robust decision-making: the agent must consider all the possible trajectories in the space of $Z$ that each vehicle can follow in order to take its decisions.
-
-The system
+%This allows to scale to larger systems: in our experiments, we used a state space of dimension $44$ ($V=10$) where \citep{Dean2018,abeille18a} only reported numerical experiments with states of dimensions 3 and 4, respectively.
+
+This system dynamics $f$ describes the couplings and interactions between vehicles, so that the autonomous agent can properly anticipate their reactions.
+It can only be expressed in the form \eqref{eq:dynamics} given the knowledge of the desired routes of each vehicle, with the features $\phi$ expressing deviations of the vehicles trajectories with respect to the lane centerline being followed.
+Since these are unknown in practice, we adopt the multi-model perspective of \autoref{sec:multi-model} and consider one model per possible route allocation for every observed vehicle before an intersection.
 
@@
 
+This results allows to apply a result from \citep{pena2008self}:
 \begin{lemma}[Theorem 14.7 of \citep{pena2008self}]
@@
 Precisely, we ensure that the polytope is chosen so that its centre $A_0$ is diagonalisable having real eigenvalues, and perform an eigendecomposition to compute its change of basis matrix $S$.
-The transformed system $Z'=S^{-1}(Z-Z_c)$ verifies \eqref{eq:polytope} with $A_0$ Metlzer as required to apply the interval predictor of Theorem~\ref{thm:predictor}.
+The transformed system $Z'=S^{-1}(Z-Z_c)$ verifies \eqref{eq:confidence} with $A_0$ Metlzer as required to apply the interval predictor of Theorem~\ref{thm:predictor}.
 Finally, the obtained predictor is transformed back to the original coordinates $Z$ by using the interval arithmetic of Lemma~\ref{lem:interval}.

### 2020-02-03 main.tex
Update intro

@@
 Our framework relaxes this modelling effort by allowing some structured uncertainty around the nominal model.
-We adopt a data-driven scheme where we wish to estimate the parameters more accurately as we interact with our true system.
+We adopt a data-driven scheme where we wish to estimate the parameters more accurately as we interact with the true system.
 Most model-based reinforcement learning algorithms only rely on the estimated dynamics to derive the corresponding optimal controller, but these methods often suffer from \emph{model bias}: they ignore the error that exists between the learned and true dynamics, which can dramatically degrade the control performances \citep{Schneider1997}.
+In particular, the framework of maximising an objective under constraints naturally pushes systems to operate in the vicinity of constraint saturation, which makes it more prone to failure when the model is imperfect.
 
 To address this issue, we turn to the framework of \emph{robust} decision-making: instead of merely considering a point estimate of the dynamics, we build an entire \emph{confidence region} that contains the true dynamics with high probability, and optimise the decisions so as to maximise the worst-case outcome with respect to this uncertainty.
-Minimax problem are hard to solve, especially since $R$ can be arbitrary.
-We cannot use traditional tools from the robust LQ control community (coarse-id control, system-level synthesis).
-Instead, we adopt a hierachical control architecture, controller selection: discrete choice of a driving maneuver, a short-term goal, whose execution is performed by a fixed low-level controller.
-It is true that the passage from continuous optimization to discrete optimization induces a suboptimality.
-However, it can be mitigated by using a more diverse controller basis.
-We are left with a sequential optimization problem with continuous states and discrete actions: tree-based planning algorithms.
-But not a point estimate, a whole confidence region.
-Hence, a two step procedure: robust prediction of the reachability set, which provides a conservative pessimistic reward to the planning algorithm.
+Minimax problem are hard to solve, especially since the reward function $R$ can be arbitrary.
+In particular, this keeps us from employing traditional tools from the robust synthesis literature, such as $\cH_\infty$ \todo{(ref needed)} control or system-level synthesis \todo{(ref needed)}.
+Since we are optimising a generic reward function, we turn to more general sequential optimisation algorithms.
+The continuous state space prevents us from using dynamic programming techniques, so we consider tree-based planning instead.
+Though some work address continuous actions \todo{ref needed}, we resort to a first approximation and discretise the decision space by adopting a hierarchical control architecture.
+We  formulate the problem high-level decision of selecting a low-level controller among a finite basis \todo{(ref from temporal abstraction)}.
+For instance, this could amount to choosing a short-term goal to follow, or a skill to execute such as a driving maneuver.
+The passage from continuous to discrete optimization induces a suboptimality, but it can be mitigated by diversifying the controller basis.
+These low-level controllers are not learnt, which also constitutes a limitation \todo{realistic in industrial setting?}.
+However, tree-based planning algorithms are designed to optimise a singled known generative model, and not a whole confidence region.
+Hence, we adapt them to the robust framework by following a two step procedure: we first predict of the set of states that can be reached by following a control sequence, under all possible dynamics.
+This reachability set is used to provide a conservative pessimistic reward to the planning algorithm.
 

### 2020-02-03 main.tex
Update

@@
 \usepackage{mathtools}
+\usepackage{multirow}
+\usepackage{siunitx}
 \input{mathdef.tex}
@@
 The passage from continuous to discrete optimization induces a suboptimality, but it can be mitigated by diversifying the controller basis.
-These low-level controllers are not learnt, which also constitutes a limitation \todo{realistic in industrial setting?}.
-However, tree-based planning algorithms are designed to optimise a singled known generative model, and not a whole confidence region.
-Hence, we adapt them to the robust framework by following a two step procedure: we first predict of the set of states that can be reached by following a control sequence, under all possible dynamics.
+These low-level controllers are not learnt, which also constitutes a limitation \todo{(argue it is realistic in industrial setting?)}.
+However, tree-based planning algorithms are only designed for a single known generative model instead of an entire confidence region for the system dynamics.
+Hence, we adapt them to the robust framework by following a two-steps procedure: we first predict a set of states that can be reached under a planned control sequence with respect to all possible dynamics.
 This reachability set is used to provide a conservative pessimistic reward to the planning algorithm.
@@
 
-In \autoref{sec:estimation}, having observed history of transitions $\cD_{[N]} = \{(x_n, u_n, y_n)\}_{n\in[N]}$, and given a confidence level $\delta\in(0, 1)$, our goal is to find a confidence region $\cC_{[N],\delta}$ as tight as possible and such that it holds that:
+In \autoref{sec:estimation}, having observed history of transitions $\cD_{[N]} = \{(x_n, y_n)\}_{n\in[N]}$, and given a confidence level $\delta\in(0, 1)$, our goal is to find a confidence region $\cC_{[N],\delta}$ as tight as possible and such that it holds that:
 \begin{align}
@@
 \end{align}
-Our first contribution is to extend the work of \citet{Abbasi2011} that provide a confidence ellipsoid for the regularised least-square estimator in the case of scalar noise and vector features to our setting of vector noise and matrix features.
+Our first contribution is to extend the work of \citet{Abbasi2011} that provide a confidence ellipsoid for the regularised least-square estimator to our setting of vector observations and matrix features, instead of scalar observations and vector features.
 
@@
 
-At the time step $n=N$, considering the model uncertainty $\cC_{[N],\delta}$ obtained in the model estimation phase, we formulate our robust control objective:
+At the time step $n=N$, considering the confidence region $\cC_{[N],\delta}$ obtained in the model estimation phase, we formulate our robust control objective:
 \begin{equation}
@@
 \end{equation}
-where $\bu = (u_{N+1},u_{N+2},\cdots)$ and $\bw = (\omega_N, \omega_{N+1},\cdots)$ are the sequences of future controls and perturbations, respectively.
-
+where $\bu = (u_{N+1},u_{N+2},\dots)$ and $\bw = (\omega_N, \omega_{N+1},\dots)$ are the sequences of future controls and perturbations, respectively.
 The rest of the paper will tackle the optimisation of this objective.
@@
 Our second contribution is to propose to solve \eqref{eq:robust-control} numerically by adopting a \emph{predict-then-optimise} scheme.
-Thus, in \autoref{sec:prediction}, we aim to derive a \emph{set predictor} $X(t)$ for the system \eqref{eq:dynamics}, which takes the information on the observed current state ${x}_N$, a confidence region $\cC_\delta$ containing $A(\theta)$, a planned control sequence $\bu$ and some admissible bounds on the perturbation $[\underline{\omega}(t),\overline{\omega}(t)]$; and produces predictions that verify the inclusion property:
+Thus, in \autoref{sec:prediction}, we aim to derive a \emph{set predictor} $X(t)$ for the system \eqref{eq:dynamics}, which takes the information on the observed current state ${x}_N$, a confidence region $\cC_\delta$ verifying \eqref{eq:confidence}, a planned control sequence $\bu$ and some admissible bounds on the perturbation $[\underline{\omega}(t),\overline{\omega}(t)]$; and produces predictions of sets $X(t)$ that verify the inclusion property:
 \begin{equation}
@@
     \centering
-    \includegraphics[width=0.3\textwidth]{img/interval-hull}
-    \caption{A few trajectories are sampled from an initial state $x_N$ following controls $\bu=(u_0,\cdots)$ with various parameters $A(\theta)\in\cC_{[N],\delta}$ (in black).
-At time $t\geq t_N$, any reachable state $x(t)$ (in green) must belong to the candidate set predictor $X(t)$ (in red).}
+    \includegraphics[width=\linewidth]{img/epc-friction}
+    \caption{\textbf{Left}: the state prediction procedure. \textbf{Right}: the model estimation procedure.}
     \label{fig:interval-hull}
@@
 
-Since $R$ is arbitrary, solving the optimal -- not to mention the robust -- control objective in the original continuous control space $(\Real^q)^\Natural$ is intractable.
+Since $R$ is generic, potentially non-smooth and non-convex, solving the optimal -- not to mention the robust -- control objective in the original continuous control space $(\Real^q)^\Natural$ is intractable.
 In this work, we choose to approximate the solution by turning the continuous optimisation problem \eqref{eq:robust-control} into a discrete one, by optimising over a finite set of \emph{actions} $\cA$.
@@
 Our third contribution proposes to approximate the true robust objective ${V}^r$ by an easily-evaluable surrogate $\hat{V}^r$ that exploits the set predictor to define a pessimistic reward, used to evaluate sequences of actions in a tree-based planning algorithm.
-We show that
-
-% \paragraph{Objective}
-
-% We wish to find a sequence of commands $\bu=(u_t)_{t\geq 0}$ that maximises a cumulative objective $V^\bu$:
-
-% \todo[inline]{EL: the prediction is done in continuous time and the control in discrete time. How to handle the change in notations?}
-
-% \begin{equation}
-% \max_\bu V^\bu
-% \end{equation}
-% where
-% \begin{equation}
-% \label{eq:optimal-control}
-% V^\bu = \expectedvalueover{\omega(t)}\left[\sum_{t=0}^\infty \gamma^t r(x(t))\condbar u_t,\,\eqref{eq:dynamics}\right]
-% \end{equation}
-% and $r:\Real^p\rightarrow[0,1]$ is a bounded reward function.
-
-\section{Related Work}
+
+The \autoref{alg:full} shows the full integration of the three procedures of estimation, prediction and control.
+
+\paragraph{Model selection} In \autoref{sec:multi-model}, we question our modelling assumption and relax them to a more flexible setting.
+
+\paragraph{Experiments} We illustrate the \autoref{alg:full} in a simple 2D example, before moving to a more realistic simulation of an autonomous driving application.
+
+% \begin{algorithm}[tb]
+%   \caption{Robust Estimation, Prediction and Control (v1)}
+%   \label{alg:full}
+% \begin{algorithmic}
+%   \STATE {\bfseries Input:} confidence level $\delta$
+%   \FOR{$N = 1,2,3,\dots$} 
+%   \STATE Compute the dynamics confidence region $\cC_{[N],\delta}$ with \textsc{Model Estimation} \eqref{eq:generic-polytope} on $\cD_{[N]}$.
+%   \FOR{planning steps $k\in[K]$}
+%   \STATE Get the tree node $\bu_k$ to expand with \textsc{Pessimistic Planning}  \eqref{eq:opd} using $\underline{R_n}$ over $[\underline{x}_{n}, \overline{x}_{n}]$. \COMMENT{Selection}
+%   \STATE For each action, simulate the child transition $[\underline{x}_{n+1}, \overline{x}_{n+1}]$ with \textsc{Interval Prediction} \eqref{eq:interval-predictor} using $\cC_{[N],\delta}$.
+\COMMENT{Expansion}
+%   \ENDFOR
+%   \STATE Execute the first recommended control $u_N$, and add the observed transition $(x_N, u_N, \dot{x}_N)$ to $\cD_{[N+1]}$.
+%   \ENDFOR
+% \end{algorithmic}
+% \end{algorithm}
+
+\begin{algorithm}[tb]
+	\caption{Robust Estimation, Prediction and Control}
+	\label{alg:full}
+	\begin{algorithmic}
+		\STATE {\bfseries Input:} confidence level $\delta$
+		\FOR{$N = 1,2,3,\dots$} 
+		\STATE $\cC_{[N],\delta} \gets$\textsc{Model Estimation}$(\cD_{[N]})$. \eqref{eq:polytope}
+		\FOR{planning steps $k\in[K]$}
+		\FOR{$a\in A$}
+		\STATE $[\underline{x}_{n+1}, \overline{x}_{n+1}]\gets$ \textsc{Interval Prediction}(
+		\STATE $\qquad\qquad\qquad\qquad\cC_{[N],\delta}, a_k$). \eqref{eq:interval-predictor}
+		\ENDFOR
+		\STATE $a_{k+1}$ $\gets$\textsc{Pessimistic Planning}$($
+		\STATE$\qquad\qquad\underline{R_{n+1}}([\underline{x}_{n+1}, \overline{x}_{n+1}]))$.  \eqref{eq:opd}
+		\ENDFOR
+		\STATE Execute the first recommended control $u_N$, and add the observed transition $(x_N, y_N)$ to $\cD_{[N+1]}$.
+		\ENDFOR
+	\end{algorithmic}
+\end{algorithm}
+
+\subsection{Related Work}
 
@@
 \end{equation}
-where $\phi_i\in\Real^{p\times p}$ for all $i\in[d]$. For all $n$, we also denote $\Phi_n = [\phi_1 x_n \cdots \phi_d x_n]\in\Real^{p\times d}$.
+where $\phi_i\in\Real^{p\times p}$ for all $i\in[d]$. For all $n$, we also denote $\Phi_n = [\phi_1 x_n \dots \phi_d x_n]\in\Real^{p\times d}$.
 
@@
 where 
-\begin{equation*}
+\begin{equation}
+\label{eq:g_n_lambda}
     G_{N, \lambda} = \sum_{n=1}^N \Phi_{n}^\transp\Sigma_p^{-1}\Phi_{n}  + \lambda I_d \in \Real^{d\times d}.
-\end{equation*}
+\end{equation}
 \end{proposition}
@@
 \begin{equation}
+	\label{eq:beta_n}
     \beta_N(\delta)\eqdef \sqrt{2\ln \left(\frac{\det(G_{N,\lambda})^{1/2}}{\delta\det(\lambda I_d)^{1/2}}\right)}
@@
 
-A simple solution to \eqref{eq:inclusion-property} is proposed in \citep{efimov:hal-00701643}, where they use matrix interval arithmetics to derive the predictor:
+A simple solution to \eqref{eq:inclusion-property} is proposed in \citep{efimov:hal-00701643}, where, given bounds $\underline{A}\leq A(\theta)\leq\overline{A}$ on $A(\theta)$ from $\cC_{[N],\delta}$ they use matrix interval arithmetics to derive the predictor:
 \begin{proposition}
@@
 \dot{\underline{x}}(t) & = & \underline{A}^{+}\underline{x}^{+}(t)-\overline{A}^{+}\underline{x}^{-}(t)-\underline{A}^{-}\overline{x}^{+}(t) +\overline{A}^{-}\overline{x}^{-}(t)\nonumber \\
- &  &+Bu(t) + D^{+}\underline{\omega}(t)-D^{-}\overline{\omega}(t),\label{eq:IP_direct}\\
+ &  &+Bu(t) + D^{+}\underline{\omega}(t)-D^{-}\overline{\omega}(t),\label{eq:predictor-naive}\\
 \dot{\overline{x}}(t) & = & \overline{A}^{+}\overline{x}^{+}(t)-\underline{A}^{+}\overline{x}^{-}(t)-\overline{A}^{-}\underline{x}^{+}(t)+\underline{A}^{-}\underline{x}^{-}(t)\nonumber \\
  &  &+Bu(t) + D^{+}\overline{\omega}(t)-D^{-}\underline{\omega}(t),\nonumber \\
- &  & \underline{x}(0)=\underline{x}_{0},\;\overline{x}(0)=\overline{x}_{0},\nonumber 
+ &  & \underline{x}(t_N)=\underline{x}_{t_N},\;\overline{x}(t_N)=\overline{x}_{t_N},\nonumber 
 \end{eqnarray}
@@
 
-% \begin{example*}
-% Consider a scalar system:
-% \[
-% \dot{x}(t)=-\theta(t)x(t)+d(t),\;t\geq0,
-% \]
-% where $x(t)\in\Real$ with $x(0)\in[\underline{x}_{0},\overline{x}_{0}]=[1.0, 1.1]$, $\theta(t)\in\Pi=[\underline{\theta},\overline{\theta}]=[0.5,1.5]$ and $d(t)\in[\underline{d},\overline{d}]=[-0.1,0.1]$ for all $t\geq0$.
-The \autoref{fig:predictor_example} shows the state-interval obtained with \eqref{eq:interval-predictor}.
-
-% \begin{figure}
-% \begin{centering}
-% \includegraphics[width=\linewidth]{img/interval-predictor}
-% \par\end{centering}
-% \caption{Several trajectories for different values of $\theta\in\Theta$ are shown in blue.
-The result of prediction by \eqref{eq:interval-predictor} is in red: the predictor is stable and produces tight bounds.}
-% \label{fig:predictor_example}
-% \end{figure}
-% \end{example*}
-
 Limitations: set-based method assumes time-varying uncertainty where we have time-invariant uncertainty: $A(\theta)$ is fixed vs $A(\theta)$ can vary in $\cC_\delta$ at each step.
 Consequence: conservative overset.
+\begin{figure}[tp]
+	\centering
+	\includegraphics[width=\linewidth]{img/interval-predictor}
+	\caption{Comparison of \eqref{eq:predictor-naive} to \eqref{eq:interval-predictor} for a simple system $\dot{x}(t)=-\theta x(t)+d(t)$}
+	\label{fig:predictor_example}
+\end{figure}
 
@@
 However, under an additional smoothness assumption on $R$, we can bound this gap:
-\begin{proposition}
-\label{prop:control-error}
-If the reward function $R$ is lipschitz, then the approximation error is upper-bounded by:
+\begin{theorem}
+\label{thm:control-error}
+If the reward function $R$ is lipschitz, then the approximation error of \autoref{alg:full} is upper-bounded by:
 \begin{equation*}
@@
 \end{equation*}
-\end{proposition}
-
-% \begin{algorithm}[tb]
-%   \caption{Robust Estimation, Prediction and Control (v1)}
-%   \label{alg:full}
-% \begin{algorithmic}
-%   \STATE {\bfseries Input:} confidence level $\delta$
-%   \FOR{$N = 1,2,3,\dots$} 
-%   \STATE Compute the dynamics confidence region $\cC_{[N],\delta}$ with \textsc{Model Estimation} \eqref{eq:generic-polytope} on $\cD_{[N]}$.
-%   \FOR{planning steps $k\in[K]$}
-%   \STATE Get the tree node $\bu_k$ to expand with \textsc{Pessimistic Planning}  \eqref{eq:opd} using $\underline{R_n}$ over $[\underline{x}_{n}, \overline{x}_{n}]$. \COMMENT{Selection}
-%   \STATE For each action, simulate the child transition $[\underline{x}_{n+1}, \overline{x}_{n+1}]$ with \textsc{Interval Prediction} \eqref{eq:interval-predictor} using $\cC_{[N],\delta}$.
-\COMMENT{Expansion}
-%   \ENDFOR
-%   \STATE Execute the first recommended control $u_N$, and add the observed transition $(x_N, u_N, \dot{x}_N)$ to $\cD_{[N+1]}$.
-%   \ENDFOR
-% \end{algorithmic}
-% \end{algorithm}
-
-\begin{algorithm}[tb]
-	\caption{Robust Estimation, Prediction and Control}
-	\label{alg:full}
-	\begin{algorithmic}
-		\STATE {\bfseries Input:} confidence level $\delta$
-		\FOR{$N = 1,2,3,\dots$} 
-		\STATE $\cC_{[N],\delta} \gets$\textsc{Model Estimation}$(\cD_{[N]})$. \eqref{eq:polytope}
-		\FOR{planning steps $k\in[K]$}
-		\STATE $a_k\gets$\textsc{Pessimistic Planning}$(\underline{R_n}([\underline{x}_{n}, \overline{x}_{n}]))$.  \eqref{eq:opd}
-		\FOR{$b\in A$}
-		\STATE $[\underline{x}_{n+1}(a_k b), \overline{x}_{n+1}(a_k b)]\gets$ \textsc{Interval Prediction}($\cC_{[N],\delta}$). \eqref{eq:interval-predictor}
-		\ENDFOR
-		\ENDFOR
-		\STATE Execute the first recommended control $u_N$, and add the observed transition $(x_N, u_N, \dot{x}_N)$ to $\cD_{[N+1]}$.
-		\ENDFOR
-	\end{algorithmic}
-\end{algorithm}
+\end{theorem}
 
@@
 Given $N-1$ observations, the \autoref{sec:estimation} provides a polytopic confidence region \eqref{eq:polytope} that contains $A(\theta)$ with probability at least $1-\delta$.
-Since the dynamics are linear, we can propagate this confidence region to the next observation: $y_{N}$ must belong to the Minkowski sum of a polytope representing model uncertainty $\cP(A_{0} x_N + Bu_N, \Delta A_{1}x_N,\cdots \Delta A_{2^d}x_N)$ and a polytope $\cP(0_p, \underline{\eta}, \overline{\eta})$ bounding the perturbation and measurement noises.
+Since the dynamics are linear, we can propagate this confidence region to the next observation: $y_{N}$ must belong to the Minkowski sum of a polytope representing model uncertainty $\cP(A_{0} x_N + Bu_N, \Delta A_{1}x_N,\dots, \Delta A_{2^d}x_N)$ and a polytope $\cP(0_p, \underline{\eta}, \overline{\eta})$ bounding the perturbation and measurement noises.
 \citet{delos2015} provide a way to test this membership in polynomial time using linear programming.
@@
 Whenever this membership property is not verified, we can confidently reject the $(A,\phi)$-modelling \autoref{assumpt:structure}.
-This enables us to consider a rich set of potential features $\left((A^1, \phi^1), \cdots, (A^M, \phi^M)\right)$ rather than relying on a single assumption.
+This enables us to consider a rich set of potential features $\left((A^1, \phi^1), \dots, (A^M, \phi^M)\right)$ rather than relying on a single assumption.
 
@@
 \label{assumpt:multi-model-ambiguity}
-Assume that the true dynamics $f$ lies within a finite set of candidate models $f^1, \cdots, f^M$.
+Assume that the true dynamics $f$ lies within a finite set of candidate models $f^1, \dots, f^M$.
 \begin{equation}
@@
 \label{eq:robust-objective-discrete}
-V^r = \sup{\bu}\min_{m\in[M]} \sum_{t=1}^\infty \gamma^t R_t^m
+V^r = \sup_{\bu}\min_{m\in[M]} \sum_{t=1}^\infty \gamma^t R_t^m
 \end{equation}
@@
 The solution of the robust objective \eqref{eq:robust-objective-discrete} with discrete ambiguity $f\in\{f^m\}_{m\in[M]}$ can be recovered exactly, asymptotically when the planning budget $H$ goes to infinity.
-This is in contrast to the results obtained \autoref{sec:control} regarding the robust objective \eqref{eq:robust-control} with continuous ambiguity $A(\theta)\in\cC_{[N],\delta}$, for which there is a gap between the asymptotic performance and the true robust value, as discussed in \autoref{prop:control-error}.
+This is in contrast to the results obtained \autoref{sec:control} regarding the robust objective \eqref{eq:robust-control} with continuous ambiguity $A(\theta)\in\cC_{[N],\delta}$, for which there is a gap between the asymptotic performance and the true robust value, as discussed in \autoref{thm:control-error}.
 
@@
 
-% \paragraph{Obstacle avoidance with unknown friction}
-% We first consider a simple illustrative example: the control of a $2D$-
+\paragraph{Obstacle avoidance with unknown friction}
+We first consider a simple illustrative example: the control of a 2D system with position $(x,y)$ and velocity $(v_x, v_y)$ moving by means of a force $(u_x, u_y)$ in an environment with unknown anisotropic friction.
+The dynamics are:
+
+\begin{equation*}
+\begin{bmatrix}
+\dot{x}\\
+\dot{y}\\
+\dot{v_x}\\
+\dot{v_y}\\
+\end{bmatrix} = 
+\begin{bmatrix}
+0 & 0 & 1 & 0 \\
+0 & 0 & 0 & 1 \\
+0 & 0 & -\theta_x & 0 \\
+0 & 0 & 0 & -\theta_y
+\end{bmatrix}
+\begin{bmatrix}
+{x}\\
+{y}\\
+{v_x}\\
+{v_y}\\
+\end{bmatrix}
++
+\begin{bmatrix}
+0\\
+0\\
+{u_x}\\
+{u_y}\\
+\end{bmatrix}
+\end{equation*}
+
+The reward is non-smooth and encodes the task of reaching a goal position $x_g$ while avoiding collisions: $R(x) = \delta(x)/(1 + \|x - x_g\|_2)$  where $\delta(x)$ is $0$ whenever $x$ overlaps with an obstacle position.
+
+\begin{table}[htbp]
+	\caption{Mean and worst-case performance}
+	\label{tab:results}
+	\centering
+	\begin{tabular}{lcccc}
+		\toprule
+		\multicolumn{1}{l}{Task} &
+		\multicolumn{2}{c}{Obstacle}    &
+		\multicolumn{2}{c}{Driving}\\
+		\cmidrule(lr){2-3}
+		\cmidrule(lr){4-5}
+		Perf. &
+		\multicolumn{1}{c}{mean} &
+		\multicolumn{1}{c}{min} &
+		\multicolumn{1}{c}{mean} &
+		\multicolumn{1}{c}{min}\\
+		\midrule
+		Oracle & \num{0} & \num{0} & \num{0} & \num{0} \\
+		Nominal & \num{0} & \num{0} & \num{0} & \num{0} \\
+		\OurAlgorithm & \num{0} & \num{0} & \num{0} & \num{0} \\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+In  \autoref{fig:regret} study the evolution of the agent conservativeness as they collect more data.
+Given a trajectory $x_0, R_0, x_1, R_1, \dots$, we compute the cumulative return $J_n(x_n) = \sum_{k\geq n} \gamma^k R_k$ at each state, and compare it to the optimal value $V(x_n)$, the return the agent would have got if it had acted optimally with respect to the oracle model.
+
+\begin{figure}[tp]
+	\centering
+	\includegraphics[width=0.8\linewidth]{img/regret.pdf}
+	\caption{We compare the performance of the robust agent to the optimal performance $\hat{V}^r(s_n)-V^*(s_n)$, with respect to the number $n$ of interactions.}
+	\label{fig:regret}
+\end{figure}
 
@@
 Since these are unknown in practice, we adopt the multi-model perspective of \autoref{sec:multi-model} and consider one model per possible route allocation for every observed vehicle before an intersection.
+
+\section*{Conclusion}
+
+Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum
 
@@
 
-\subsection{Proof of \autoref{prop:control-error}}
-
+\subsection{Proof of \autoref{thm:control-error}}
+
+We first bound the model estimation error.
+\begin{lemma}
+Under sufficient excitations in the features 
+\begin{align}
+\label{eq:excitation}
+\exists \underline{\phi},\overline{\phi}>0, n_0: \forall n\geq n_0,i,j\in[p],\nonumber\\ \underline{\phi}^2 \leq \sum_k \sum_l \phi_{n,k,i}\Sigma_{p,k,l}^{-1}\phi_{n,l,j} \leq \overline{\phi}^2,
+\end{align}
+then,
+\[\|\theta - \theta_{[N],\lambda}\|_{2} = \cO\left( \sqrt{\frac{\log N}{N}} \right) \]
+\end{lemma}
+\begin{proof}
+By \eqref{eq:g_n_lambda} and \eqref{eq:excitation}, we have $G_{[N],\lambda,i,j} \geq N\underline{\phi}^2 $
+
+Hence, by \eqref{eq:confidence-ellipsoid} we have 
+\begin{align*}
+	\|\theta - \theta_{[N],\lambda}\|_{G_{[N],\lambda}} \geq \sqrt{N}\underline{\phi} \|\theta - \theta_{[N],\lambda}\|_{2} 
+\end{align*}
+and \eqref{eq:beta_n} gives
+
+\begin{align*}
+\beta_N(\delta) &= \sqrt{2\ln \left(\frac{\det(G_{N,\lambda})^{1/2}}{\delta\det(\lambda I_d)^{1/2}}\right)}
++ (\lambda d)^{1/2}S\\
+&\leq \sqrt{d\log (N\overline{\phi}^2) / \lambda^{d/2}} + \cO(1)
+\end{align*}
+
+which yields the desired bound.
+\end{proof}
+
+Then, we propagate this estimation error through the state prediction.
+
+\begin{lemma}
+	\todo{Which result?}
+\end{lemma}
+\begin{proof}
+Let $\delta x = \ox - \ux$. Assuming that eventually after $n\geq n_0$ $A_0$ becomes close enough to $A(\theta)$ to always be Metlzer. Then, \eqref{eq:interval-predictor} gives the dynamics:
+\begin{align*}
+\dot{\delta x} = A_0\delta x + |\Delta A|(\ox^+ + \ux^-) + |D|(\overline{\omega} - \underline{\omega})
+\end{align*}
+where $|M| = M^+ + M^-$.
+
+Moreover, it holds that $-\ux^+ -\ox^- \leq \delta x \leq \ox^+ + \ux^-$, which implies $|\ux^+ + \ox^-| \leq 2 |\delta x|$.
+
+We define $V = \delta x^\transp P \delta x$, and compute its derivative:
+\begin{align*}
+\dot{V} ={}& X^\transp
+\begin{bmatrix}
+A_0^\transp P + P A_0^\transp + Q & P|\Delta A| & P|D|\\
+|\Delta A|^\transp P & -\alpha I_n & 0\\
+D^\transp|P| & 0 & -\rho I_p
+\end{bmatrix}
+X\\
+& - \delta x^\transp Q \delta x + \alpha |\ux^+ + \ox^-|^2 + \rho |\overline{\omega} - \underline{\omega}|^2
+\end{align*}
+with $X=\begin{bmatrix}
+\delta x\\ \ux^+ + \ox^- \\ \overline{\omega} - \underline{\omega}
+\end{bmatrix}$. Hence, 
+\begin{align*}
+\dot{V} \leq {}& X^\transp
+\begin{bmatrix}
+A_0^\transp P + P A_0^\transp + Q + 2\alpha^2 I_p & P|\Delta A| & P|D|\\
+|\Delta A|^\transp P & -\alpha I_n & 0\\
+D^\transp|P| & 0 & -\rho I_p
+\end{bmatrix}
+X\\
+& - \delta x^\transp Q \delta x + \rho |\overline{\omega} - \underline{\omega}|^2
+\end{align*}
+
+\end{proof}
+
+Finally, we propagate the state prediction error bound to the pessimistic rewards and surrogate objective to get our final result.
 \begin{proof}
@@
 
- Thus, since we assume that $R$ is $L$-lipschitz,
+ Thus, assuming $R$ is $L$-lipschitz,
  \begin{align}
      V^r(\bu) - \hat{V}^r(\bu) &\leq \sum_{n=N+1}^\infty \gamma^n \underset{{x\in[\underline{x}_n(\bu), \overline{x}_n(\bu)]}}{(\max - \min)} R(x)\\
-     &\leq \sum_{n=N+1}^\infty \gamma^n L \left\|\underline{x}_n(\bu) - \overline{x}_n(\bu)\right\|
+     &\leq \sum_{n=N+1}^\infty \gamma^n L \left\|\underline{x}_n(\bu) - \overline{x}_n(\bu)\right\|\\
+     &\leq L/(1-\gamma) \cO\left(\sqrt{\log N / N}\right)
  \end{align}
-
 \end{proof}
@@
 	\begin{equation}
+	\label{eq:max_vr}
 	V_a^r \eqdef \max_{\bu \in a\mathcal{A^\infty}} \min_{m\in[1, M]} \sum_{n=h(a)+1}^\infty \gamma^n R^m_n
@@
 	\begin{equation}
+	\label{eq:ur}
 	U_a^r(T)  \eqdef
@@
 \begin{proof}
-	By definition, when starting with sequence $i$, the value $u_i^m(n)$ represents the minimum admissible reward, while $b_i^m(n)$ corresponds to the best admissible reward achievable with respect to the the possible continuations of $i$.
-Thus, for all $i\in\mathcal{A}^*$, $u_i^m(n)$ and $u_i^r(n)$ are non-decreasing functions of $n$ and $b_i^m(n)$ and $b_i^r(n)$ are a non-increasing functions of $n$, while $v_i^m$ and $v_i^r$ do not depend on $n$.
-
-	Moreover, since the reward function $r$ is assumed to have values in $[0, 1]$, the sum of discounted rewards from a node of depth $d$ is at most $\gamma^d + \gamma^{d+1}+\cdots = \frac{\gamma^d}{1-\gamma}$.
-As a consequence, for all $n \geq 0$ , $i\in\mathcal{L}_n$ of depth $d$, and any sequence of rewards $(r_t)_{t\in\mathbb{N}}$ obtained from following a path in $i\mathcal{A}^\infty$ with any dynamics $m \in [1, M]$:
-
-	\begin{equation*}
-	\sum_{t=0}^{d-1} \gamma^t r_t \leq \sum_{t=0}^{d-1} \gamma^t r_t + \sum_{t=d}^\infty \gamma^t r_t \leq \sum_{t=0}^{d-1} \gamma^t r_t + \frac{\gamma^d}{1-\gamma}
+	By definition, when starting with sequence $i$, the value $U_i^m(n)$ represents the minimum admissible reward, while $B_i^m(n)$ corresponds to the best admissible reward achievable with respect to the the possible continuations of $i$.
+Thus, for all $i\in\mathcal{A}^*$, $U_i^m(n)$ and $U_i^r(n)$ are non-decreasing functions of $n$ and $b_i^m(n)$ and $B_i^r(n)$ are a non-increasing functions of $n$, while $V_i^m$ and $V_i^r$ do not depend on $n$.
+
+	Moreover, since the reward function $R$ is assumed to have values in $[0, 1]$, the sum of discounted rewards from a node of depth $d$ is at most $\gamma^d + \gamma^{d+1}+\dots = \frac{\gamma^d}{1-\gamma}$.
+As a consequence, for all $n \geq 0$ , $i\in\mathcal{L}_n$ of depth $d$, and any sequence of rewards $(R_t)_{t\in\mathbb{N}}$ obtained from following a path in $i\mathcal{A}^\infty$ with any dynamics $m \in [1, M]$:
+
+	\begin{equation*}
+	\sum_{t=0}^{d-1} \gamma^t R_t \leq \sum_{t=0}^{d-1} \gamma^t R_t + \sum_{t=d}^\infty \gamma^t R_t \leq \sum_{t=0}^{d-1} \gamma^t R_t + \frac{\gamma^d}{1-\gamma}
 	\end{equation*}
@@
 	\begin{equation*}
-	u^m_i(n) \leq \sum_{t=0}^\infty \gamma^t r_t \leq b^m_i(n) 
+	U^m_i(n) \leq \sum_{t=0}^\infty \gamma^t R_t \leq B^m_i(n) 
 	\end{equation*}
@@
 	\label{eq:min_m_values}
-	\min_{m \in [1, M]} u^m_i(n) \leq \min_{m \in [1, M]} \sum_{t=0}^\infty \gamma^t r_t \leq \min_{m \in [1, M]} b^m_i(n)
+	\min_{m \in [1, M]} U^m_i(n) \leq \min_{m \in [1, M]} \sum_{t=0}^\infty \gamma^t R_t \leq \min_{m \in [1, M]} B^m_i(n)
 	\end{equation}
@@
 	\begin{equation*}
-	\min_{m \in [1, M]} u^m_i(n) \leq \max_{\pi\in i\mathcal{A}^\infty} \min_{m \in [1, M]} \sum_{t=0}^\infty \gamma^t r_t \leq \min_{m \in [1, M]} b^m_i(n)
+	\min_{m \in [1, M]} U^m_i(n) \leq \max_{\pi\in i\mathcal{A}^\infty} \min_{m \in [1, M]} \sum_{t=0}^\infty \gamma^t R_t \leq \min_{m \in [1, M]} B^m_i(n)
 	\end{equation*}
@@
 	\label{eq:urvrbr}
-	u^r_i(n) \leq v^r_i  \leq b^r_i(n)
-	\end{equation}
-
-	Finally, \eqref{eq:urvrbr} is extended to the rest of $\mathcal{T}_n$ by recursive application of \eqref{eq:max_vr}, \eqref{eq:ur} and \eqref{eq:br}.
+	U^r_i(n) \leq V^r_i  \leq B^r_i(n)
+	\end{equation}
+
+	Finally, \eqref{eq:urvrbr} is extended to the rest of $\mathcal{T}_n$ by recursive application of \eqref{eq:max_vr}, \eqref{eq:ur} and \eqref{eq:robust-b-values}.
 \end{proof}
@@
 This properties relies on the fact that the returned action belongs to the deepest explored branch, which we can show likewise by contradiction using Lemma \ref{lemma:uvb}.
-This yields directly that $a = i_0$ where $i$ is some node of maximal depth $d_n$ expanded at round $t\leq n$, which by Algorithm \ref{algo:drop} verifies $b_a^r(t) = b_i^r(t) = \max_{x\in\mathcal{A}} b_x^r(t)$ and:
+This yields directly that $a = i_0$ where $i$ is some node of maximal depth $d_n$ expanded at round $t\leq n$, which by selection rule verifies $B_a^r(t) = B_i^r(t) = \max_{x\in\mathcal{A}} B_x^r(t)$ and:
 	\begin{align}
 	\label{eq:Rndn}
-	v^r - v_a^r &= v_{a^*}^r - v_a^r \\
-	&\leq b_{a^*}^r(t) - v_a^r \\
-	&\leq b_{a}^r(t) - u_a^r(t) \\
-	&= b_{i}^r(t) - u_i^r(t) \\
+	V^r - V_a^r &= V_{a^*}^r - V_a^r \\
+	&\leq B_{a^*}^r(t) - V_a^r \\
+	&\leq B_{a}^r(t) - U_a^r(t) \\
+	&= B_{i}^r(t) - U_i^r(t) \\
 	&= \frac{\gamma^{d_n}}{1-\gamma}.
@@
 To that end, they show that the expanded nodes always belong to the sub-tree $\mathcal{T}_\infty$ of all the nodes of depth $d$ that are $\frac{\gamma^d}{1-\gamma}$-optimal.
-Indeed, if a node $i$ of depth $d$ is expanded at round $n$, then $b_i^r(n) \geq b_j^r(n)$ for all $j\in \mathcal{L}_n$ by Algorithm \ref{algo:drop}, thus the max-backups of \eqref{eq:br} up to the root yield $b^r_i(n) = b_\emptyset^r(n)$.
-Moreover, by Lemma \ref{lemma:uvb} we have that $b_\emptyset^r(n) \geq v_\emptyset^r = v^r$ and so $v_i^r \geq u_i^r(n) = b_i^r(n) - \frac{\gamma^d}{1-\gamma} \geq v^r - \frac{\gamma^d}{1-\gamma}$, thus $i \in \mathcal{T}_\infty$.
-
-	Then from Assumption \ref{assumpt:beta} and the definition of $\beta$ applied to nodes in $\mathcal{T}_\infty$, there exists $d_0$ and $c$ such that the number $n_d$ of nodes of depth $d \geq d_0$ in $\mathcal{T}_\infty$ is bounded by $c\left(\frac{\gamma^d}{1-\gamma}\right)^\beta K^d$.
+Indeed, if a node $i$ of depth $d$ is expanded at round $n$, then $B_i^r(n) \geq B_j^r(n)$ for all $j\in \mathcal{L}_n$ by selection rule, thus the max-backups of \eqref{eq:robust-b-values} up to the root yield $B^r_i(n) = B_\emptyset^r(n)$.
+Moreover, by Lemma \ref{lemma:uvb} we have that $B_\emptyset^r(n) \geq V_\emptyset^r = V^r$ and so $V_i^r \geq U_i^r(n) = B_i^r(n) - \frac{\gamma^d}{1-\gamma} \geq V^r - \frac{\gamma^d}{1-\gamma}$, thus $i \in \mathcal{T}_\infty$.
+
+	Then from the definition of $\kappa$ applied to nodes in $\mathcal{T}_\infty$, there exists $d_0$ and $c$ such that the number $n_d$ of nodes of depth $d \geq d_0$ in $\mathcal{T}_\infty$ is bounded by $c\kappa^d$.
 As a consequence,
@@
 		n &= \sum_{d=0}^{d_n} n_d = n_0 + \sum_{d=d_0+1}^{d_n} n_d \\
-		&\leq n_0 + \sum_{d=d_0+1}^{d_n} c\left(\frac{\gamma^d}{1-\gamma}\right)^\beta K^d \\
-		&= n_0 + c'\sum_{d={d_0+1}}^{d_n} \kappa^d
+		&\leq n_0 + c\sum_{d={d_0+1}}^{d_n} \kappa^d
 	\end{eqnarray*}

### 2020-02-03 main.tex
Update

@@
 In this paper, we consider the problem of controlling an unknown linear system $x(t)$ so as to maximise an \emph{arbitrary} bounded reward function $R$, in a critical setting where mistakes are costly and must be avoided at all time.
-This choice of the rich reward space is crucial to have sufficient flexibility to model non-convex and non-smooth functions that naturally arise in many practical problems such as combinatorial optimisation, obstacle avoidance, etc.
+This choice of rich reward space is crucial to have sufficient flexibility to model non-convex and non-smooth functions that naturally arise in many practical problems such as combinatorial optimisation, obstacle avoidance, etc., while quadratic costs are only suited for the tracking of a reference trajectory known a priori.
 
@@
 To address this issue, we turn to the framework of \emph{robust} decision-making: instead of merely considering a point estimate of the dynamics, we build an entire \emph{confidence region} that contains the true dynamics with high probability, and optimise the decisions so as to maximise the worst-case outcome with respect to this uncertainty.
-Minimax problem are hard to solve, especially since the reward function $R$ can be arbitrary.
-In particular, this keeps us from employing traditional tools from the robust synthesis literature, such as $\cH_\infty$ \todo{(ref needed)} control or system-level synthesis \todo{(ref needed)}.
-Since we are optimising a generic reward function, we turn to more general sequential optimisation algorithms.
+Minimax problem are hard to solve, and all the more in our setting where the reward function $R$ is generic.
+In particular, this excludes a number of tools from the robust synthesis literature, such as $\cH_\infty$ \todo{(ref needed)} control or system-level synthesis \todo{(ref needed)}.
+We turn instead to more general planning algorithms.
 The continuous state space prevents us from using dynamic programming techniques, so we consider tree-based planning instead.
@@
 The passage from continuous to discrete optimization induces a suboptimality, but it can be mitigated by diversifying the controller basis.
-These low-level controllers are not learnt, which also constitutes a limitation \todo{(argue it is realistic in industrial setting?)}.
 However, tree-based planning algorithms are only designed for a single known generative model instead of an entire confidence region for the system dynamics.
@@
 This reachability set is used to provide a conservative pessimistic reward to the planning algorithm.
+The next section aims to clarify and formalize these ideas.
 
@@
 For any variable $z$, we use the subscript notation to refer to these discrete times: $z_n = z(t_n)$ with $t_n = n\dd t$.
+We use bold symbols to denote sequences $\bz = (z_1,z_2,\dots)$.
 
@@
 		\FOR{planning steps $k\in[K]$}
-		\FOR{$a\in A$}
+		\FOR{$b\in A$}
 		\STATE $[\underline{x}_{n+1}, \overline{x}_{n+1}]\gets$ \textsc{Interval Prediction}(
-		\STATE $\qquad\qquad\qquad\qquad\cC_{[N],\delta}, a_k$). \eqref{eq:interval-predictor}
+		\STATE $\qquad\qquad\qquad\qquad\cC_{[N],\delta}, a_kb$). \eqref{eq:interval-predictor}
 		\ENDFOR
@@
 
-\paragraph{LQ systems} There is a rich body of literature dedicated to the study of LQ systems, and we focus on those providing non-asymptotic results when the system parameters $A, B$ are unknown.
+\paragraph{Linear Quadratic systems} There is a rich body of literature dedicated to the study of LQ systems, and we focus on those providing non-asymptotic results when the system parameters $A, B$ are unknown.
 In their seminal work \citet{abbasi-yadkori11a}, consider the problem of cumulative regret minimisation.
@@
 \citet{abeille18a} provide the same result by applying Thomson Sampling rather of optimism to select a dynamical model, and rejection sampling to enforce the controllability constraint.
-While previous methods suffered from limited applicability and computationally intractable subroutines, \citep{Dean2018} provide a polynomial-time algorithm which achieves a suboptimal cumulative regret of $\tilde{\cO}\left(T^{2/3}\right)$.
-
-Offline estimation and control synthesis: \citep{Dean2017}.
-Summary: Estimation procedure of $N$ episodes of duration $T$ with gaussian excitation, ellipsoid in L2 norm, robust controller with System Level Synthesis, simple regret in $O(\sqrt{\frac{\log(1/\delta)}{N}})$
-
-We wish to act straight away in a reasonable (structure) but cautious (robust) way, and progressively get more and more aggressive as we obtain more data and reduce uncertainty.
-
-Thus, we do not wish to explore actively the more promising regions as in OFU, nor the more likely region as in TS, nor act randomly as in Coarse-ID They inject exploration noise.
-
-We have linear dynamics but our cost is not quadratic.
-Quadratic cost: stabilize a system around a reference trajectory known a priori.
-Thus, we can accurately represent planning tasks with discrete/branching decisions involving discontinuities (e.g.
-collision vs non-collision states).
+These methods which aim at regret minimization are actively exploring to quickly reduce uncertainty, through information-seeking behaviours.
+Other work use noise injection for exploration such as \citep{Dean2017} or \citep{Dean2018}, who provide a polynomial-time algorithm with a cumulative regret of $\tilde{\cO}\left(T^{2/3}\right)$.
+In contrast, our main objective is to prevent failures, which forbids to explore uncertain regions.
+% They also suffer from a limited applicability and computationally intractable subroutines.
+%$
+The work of \citet{Dean2017} is closest to our setting: after an offline estimation phase under random exploration, they estimate a simple regret between a robust controller and the oracle optimal performance.
 

### 2020-02-03 main.tex
Update related work, experiments

@@
 \usepackage{multirow}
-\usepackage{siunitx}
 \input{mathdef.tex}
@@
 
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{img/epc-friction}
+	\caption{\textbf{Left}: the state prediction procedure. \textbf{Right}: the model estimation procedure.}
+	\label{fig:estimation-prediction}
+\end{figure}
+
 In \autoref{sec:estimation}, having observed history of transitions $\cD_{[N]} = \{(x_n, y_n)\}_{n\in[N]}$, and given a confidence level $\delta\in(0, 1)$, our goal is to find a confidence region $\cC_{[N],\delta}$ as tight as possible and such that it holds that:
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{img/epc-friction}
-    \caption{\textbf{Left}: the state prediction procedure. \textbf{Right}: the model estimation procedure.}
-    \label{fig:interval-hull}
-\end{figure}
-
-This property is illustrated in \autoref{fig:interval-hull}. We leverage recent results from the uncertain system simulation literature to efficiently compute such a predictor.
+This property is illustrated in \autoref{fig:estimation-prediction}. We leverage recent results from the uncertain system simulation literature to efficiently compute such a predictor.
 
@@
 \citet{abeille18a} provide the same result by applying Thomson Sampling rather of optimism to select a dynamical model, and rejection sampling to enforce the controllability constraint.
-These methods which aim at regret minimization are actively exploring to quickly reduce uncertainty, through information-seeking behaviours.
-Other work use noise injection for exploration such as \citep{Dean2017} or \citep{Dean2018}, who provide a polynomial-time algorithm with a cumulative regret of $\tilde{\cO}\left(T^{2/3}\right)$.
-In contrast, our main objective is to prevent failures, which forbids to explore uncertain regions.
-% They also suffer from a limited applicability and computationally intractable subroutines.
-%$
+These methods aim at regret minimization and explore actively to quickly reduce uncertainty, through information-seeking behaviours.
+Other work use noise injection for exploration such as \citep{Dean2017} or \citep{Dean2018}.
+However, being optimistic and minimising a cumulative regret does not fit a critical setting, where ensuring safety is the first criteria requires instead to consider the pessimistic outcomes.
 The work of \citet{Dean2017} is closest to our setting: after an offline estimation phase under random exploration, they estimate a simple regret between a robust controller and the oracle optimal performance.
-
-Our optimisation problem amounts to a sequence of controllers selection, instead of continuous controller synthesis
-
-Optimistic exploration = information seeking and uncertainty reduction.
-Our objective: do not commit mistakes (do not explore uncertain regions).
-If some information is collected allowing to reduce uncertainty, use it to be more optimal, but do not actively seek it.
-
-Given the critical setting, we do not want to be optimistic, and try to minimise some cumulative regret. Quite the contrary, we want to be cautious, safe, prepare for the worst and plan for the best.
+We also focus on where previous methods often suffer from a limited applicability and computationally intractable subroutines, with the exception of \cite{Dean2018} who provide a polynomial-time algorithm.
 
 \paragraph{Robust planning}
-Robust optimization has been studied in the context of finite Markov Decision Processes with uncertain parameters by Iyengar (2005), Nilim and El Ghaoui (2005) and Wiesemann et al.
-(2013).
-They show that the main results of Dynamic Programming can be extended to their robust counterparts only when the dynamics ambiguity set verifies a certain rectangularity property, that amounts to an independence assumption between the uncertainty sets of each transition and is related to time-varying uncertainty.
-L1/KL ball around the empirical transition.
-They do not consider continuous states, nor handle time-invariant uncertainty.
-We do so by not relying on a dynamic programming evaluation of the robust cost-to-go, but on monte-carlo estimates along a full trajectory.
+Robust optimization has also been studied in the context of finite Markov Decision Processes with uncertain parameters by \citet{Iyengar2005}, \citet{Nilim2005} and \citet{Wiesemann2013}.
+They showed that the main results of Dynamic Programming can be extended to their robust counterparts only when the dynamics ambiguity set verifies a certain rectangularity property, that amounts to an independence assumption between the uncertainty sets of each transition and is related to time-varying uncertainty.
+Since our setting requires dealing with continuous states and time-invariant uncertainty, we rely on monte-carlo value estimates and tree-based planning rather than temporal-difference dynamic programming.
 
@@
 
-In the general case, 
- assume that the dynamics $A(\theta)$ enjoy the following additional structure:
+To derive a confidence region for the dynamical parameters $\theta$, the functional relationship $A(\theta)$ must be specified.
 \begin{assumption}[Structure]
@@
 \end{equation}
-where $\phi_i\in\Real^{p\times p}$ for all $i\in[d]$. For all $n$, we also denote $\Phi_n = [\phi_1 x_n \dots \phi_d x_n]\in\Real^{p\times d}$.
+where $\phi_i\in\Real^{p\times p}$ for all $i\in[d]$. For all $n$, we denote $\Phi_n = [\phi_1 x_n \dots \phi_d x_n]\in\Real^{p\times d}$.
 
@@
 
-Another strategy presented in \autoref{sec:tight-polytope} produces a much tighter polytope, at the price of an increased computational cost required by the diagonalisation of $G_{N,\lambda}$.
-
-\paragraph{Remark} The robust objective framing involves on some bounds $\underline{\omega}(t)\leq \omega(t) \leq \overline{\omega}(t)$ over the possible perturbations we want to protect against.
-In the unbounded sub-Gaussian noise setting of \autoref{assumpt:gaussian-noise}, we can use the same formulation by deriving high-confidence bounds that each holds with probability $\delta_t$.
+Another strategy presented in Appendix \ref{sec:tight-polytope} produces a much tighter polytope, at the price of an increased computational cost required by the diagonalisation of $G_{N,\lambda}$.
+
+\paragraph{Remark} The robust objective \eqref{eq:robust-control} involves bounds $\underline{\omega}(t)\leq \omega(t) \leq \overline{\omega}(t)$ over the possible perturbations we want to protect against.
+In the unbounded sub-Gaussian noise setting of \autoref{assumpt:gaussian-noise}, we can use the same formulation by deriving local high-confidence bounds that each holds with probability $\delta_t$.
 By choosing $\delta_t = \frac{\delta}{t(t+1)}$, we have that the event $\{\forall t, \underline{\omega}(t) \leq \omega(t) \leq \overline{\omega}(t)\}$ holds with probability $1-\delta$.
@@
 
-We consider interval prediction rather than zonotope prediction for instance, for the sake of simplicity of implementation and computational efficiency.
+In order to study the inclusion property \eqref{eq:inclusion-property}, we must start by choosing a set representation $X(t)$.
+We consider interval prediction, rather than zonotope prediction for instance, for the sake of simplicity of implementation and computational efficiency.
 Thus, we represent an interval as $X(t) = [\underline{x}(t), \overline{x}(t)]\in \Real^p\times \Real^p$, and the inclusion property becomes:
@@
 
-However, \citet{leurent2019interval} showed that this predictor can have unstable dynamics, even for stable systems, which can cause a rapid build-up of uncertainty and produce over-conservative behaviours.
+However, \citet{leurent2019interval} showed that this predictor can have unstable dynamics, even for stable systems, which can cause a rapid build-up of uncertainty.
 They propose an enhanced predictor which produces tighter and more stable predictions, and whose stability can be assessed by solving a linear matrix inequality, at the price of an additional requirement:
@@
 \label{assumpt:metzler}
-There exists an orthogonal matrix $P\in\Real^{d\times d}$ such that $P^\transp A_0 P$ is Metzler, that is, all non-diagonal coefficients are non-negative.
+There exists an orthogonal matrix $P\in\Real^{d\times d}$ such that $P^\transp A_0 P$ is Metzler\footnote{A matrix is said to be Metlzer when all its non-diagonal coefficients are non-negative.}.
 \end{assumption}
@@
 The similarity transformation of \citep{Efimov_a2013} provides a method to compute such $P$ whenever there exist $C_1,C_2$ which make $A(\theta, C_1)$ and $(A_0, C_2)$ observable.
-Under this assumption, without loss of generality up to a change of basis $x\rightarrow P^{-1}x$ that we do not write for the sake of readability, this assumption is equivalent to considering that $A_0$ itself is Metzler.
+% Under this assumption, without loss of generality up to a change of basis $x\rightarrow P^{-1}x$ that we do not write for the sake of readability, this assumption is equivalent to considering that $A_0$ itself is Metzler.
 
@@
 ensures the inclusion property \eqref{eq:inclusion-property}.
-
-% Moreover, the stability of the predictor can be assessed with a sufficient condition in form of an LMI.
-% if there exist diagonal matrices $P$, $Q$, $Q_{+}$, $Q_{-}$, $Z_{+}$, $Z_{-}$, $\Psi_{+}$, $\Psi_{-}$, $\Psi$, $\Gamma\in\Real^{2n\times 2n}$ such that the following LMIs are satisfied:
-% \begin{gather*}
-% P+\min\{Z_{+},Z_{-}\}>0,\;\Upsilon\preceq0,\;\Gamma>0,\\
-% Q+\min\{Q_{+},Q_{-}\}+2\min\{\Psi_{+},\Psi_{-}\}>0,
-% \end{gather*}
-% where{\footnotesize{}
-% \begin{gather*}
-% \Upsilon=\left[\begin{array}{cccc}
-% \Upsilon_{11} & \Upsilon_{12} & \Upsilon_{13} & P\\
-% \Upsilon_{12}^{\top} & \Upsilon_{22} & \Upsilon_{23} & Z_{+}\\
-% \Upsilon_{13}^{\top} & \Upsilon_{23}^{\top} & \Upsilon_{33} & Z_{-}\\
-% P & Z_{+} & Z_{-} & -\Gamma
-% \end{array}\right],\\
-% \Upsilon_{11}=\mathcal{A}^{\top}P+P\mathcal{A}+Q,\;\Upsilon_{12}=\mathcal{A}^{\top}Z_{+}+PR_{+}+\Psi_{+},\\
-% \Upsilon_{13}=\mathcal{A}^{\top}Z_{-}+PR_{-}+\Psi_{-},\;\Upsilon_{22}=Z_{+}R_{+}+R_{+}^{\top}Z_{+}+Q_{+},\\
-% \Upsilon_{23}=Z_{+}R_{-}+R_{+}^{\top}Z_{-}+\Psi,\;\Upsilon_{33}=Z_{-}R_{-}+R_{-}^{\top}Z_{-}+Q_{-},\\
-% \mathcal{A}=\left[\begin{array}{cc}
-% A_{0} & 0\\
-% 0 & A_{0}
-% \end{array}\right],\;R_{+}=\left[\begin{array}{cc}
-% 0 & -\Delta A_{-}\\
-% 0 & \Delta A_{+}
-% \end{array}\right],\;R_{-}=\left[\begin{array}{cc}
-% \Delta A_{+} & 0\\
-% -\Delta A_{-} & 0
-% \end{array}\right],
-% \end{gather*}
-% }then the predictor \eqref{eq:interval-predictor} is input-to-state stable with respect to the inputs $\underline{\omega}$, $\overline{\omega}$.
 \end{theorem}
 
-Limitations: set-based method assumes time-varying uncertainty where we have time-invariant uncertainty: $A(\theta)$ is fixed vs $A(\theta)$ can vary in $\cC_\delta$ at each step.
-Consequence: conservative overset.
 \begin{figure}[tp]
@@
 	\includegraphics[width=\linewidth]{img/interval-predictor}
-	\caption{Comparison of \eqref{eq:predictor-naive} to \eqref{eq:interval-predictor} for a simple system $\dot{x}(t)=-\theta x(t)+d(t)$}
+	\caption{Comparison of \eqref{eq:predictor-naive} to \eqref{eq:interval-predictor} for a simple system $\dot{x}(t)=-\theta x(t)+d(t)$, with $\theta\in[1, 2]$.}
 	\label{fig:predictor_example}
 \end{figure}
+
+The \autoref{fig:predictor_example} illustrates the differences of stability of the two predictors with a simple example.
+It suggests to always prefer \eqref{eq:interval-predictor} whenever \autoref{assumpt:metzler} is verified, and only use \eqref{eq:predictor-naive} as a last resort.
+
+% Limitations: set-based method assumes time-varying uncertainty where we have time-invariant uncertainty: $A(\theta)$ is fixed vs $A(\theta)$ can vary in $\cC_\delta$ at each step.
+Consequence: conservative overset.
 
@@
 \label{prop:lower-bound}
-With high probability, the surrogate objective $\hat{V}^r$ is a lower bound of the true objective $V^r$:
-
+With high probability, the surrogate objective  \eqref{eq:surrogate_objective} is a lower bound of the true objective \eqref{eq:robust-control-disc}:
 \begin{equation}
@@
 The consequence of \autoref{prop:lower-bound} is that since all our approximations were conservative, if we manage to find a control sequence such that no \textit{``bad event''} (e.g.
-a collision) happens according to the surrogate objective $\hat{V}^r$, then we are guaranteed so they will not happen either when the controls are executed on the true system.
+a collision) happens according to the surrogate objective $\hat{V}^r$, then we are guaranteed that they will not happen either when the controls are executed on the true system.
 
@@
 \label{theorem:opd-regret}
-The simple regret of the \texttt{OPD} algorithm \eqref{eq:opd} after $K$ iterations is:
+The simple regret of the \texttt{OPD} algorithm \eqref{eq:opd} applied to the surrogate objective \eqref{eq:surrogate_objective} after $K$ iterations is:
 \begin{align*}
@@
 \label{eq:robust-objective-discrete}
-V^r = \sup_{\bu}\min_{m\in[M]} \sum_{t=1}^\infty \gamma^t R_t^m
+V^r = \sup_{a\in\cA^\Natural}\min_{m\in[M]} \sum_{t=1}^\infty \gamma^t R_t^m
 \end{equation}
@@
 \label{theorem:drop-regret}
-\texttt{ROPD} enjoys the same regret bound as provided for \texttt{OPD} in \autoref{theorem:opd-regret}.
+The \texttt{Robust-OPD} \eqref{eq:robust-b-values} enjoys the same regret bound as provided for \texttt{OPD} in \autoref{theorem:opd-regret}, with respect to the robust objective \eqref{eq:robust-objective-discrete}.
 \end{theorem}
@@
 The solution of the robust objective \eqref{eq:robust-objective-discrete} with discrete ambiguity $f\in\{f^m\}_{m\in[M]}$ can be recovered exactly, asymptotically when the planning budget $H$ goes to infinity.
-This is in contrast to the results obtained \autoref{sec:control} regarding the robust objective \eqref{eq:robust-control} with continuous ambiguity $A(\theta)\in\cC_{[N],\delta}$, for which there is a gap between the asymptotic performance and the true robust value, as discussed in \autoref{thm:control-error}.
+This is in contrast to the results obtained in \autoref{sec:control} for the robust objective \eqref{eq:robust-control} with continuous ambiguity $A(\theta)\in\cC_{[N],\delta}$, for which \texttt{OPD} only recovers the surrogate approximation $\hat{V}^r$, as discussed in \autoref{thm:control-error}.
 
@@
 \paragraph{Obstacle avoidance with unknown friction}
-We first consider a simple illustrative example: the control of a 2D system with position $(x,y)$ and velocity $(v_x, v_y)$ moving by means of a force $(u_x, u_y)$ in an environment with unknown anisotropic friction.
+We first consider a simple illustrative example: the control of a 2D system with position $(p_x,p_y)$ and velocity $(v_x, v_y)$ moving by means of a force $(u_x, u_y)$ in an environment with unknown anisotropic friction.
 The dynamics are:
@@
 \begin{bmatrix}
-\dot{x}\\
-\dot{y}\\
+\dot{p_x}\\
+\dot{p_y}\\
 \dot{v_x}\\
@@
 \begin{bmatrix}
-{x}\\
-{y}\\
+{p_x}\\
+{p_y}\\
 {v_x}\\
@@
 
-The reward is non-smooth and encodes the task of reaching a goal position $x_g$ while avoiding collisions: $R(x) = \delta(x)/(1 + \|x - x_g\|_2)$  where $\delta(x)$ is $0$ whenever $x$ overlaps with an obstacle position.
+The reward is non-smooth and encodes the task of reaching a goal position $x_g$ while avoiding collisions: $R(x) = \delta(x)/(1 + \|x - x_g\|_2)$  where $\delta(x)$ is $0$ whenever $x$ collides with an obstacle.
 
@@
 	\centering
-	\begin{tabular}{lcccc}
+	\begin{tabular}{lcccccc}
 		\toprule
 		\multicolumn{1}{l}{Task} &
-		\multicolumn{2}{c}{Obstacle}    &
-		\multicolumn{2}{c}{Driving}\\
-		\cmidrule(lr){2-3}
-		\cmidrule(lr){4-5}
+		\multicolumn{3}{c}{Obstacle}    &
+		\multicolumn{3}{c}{Driving}\\
+		\cmidrule(lr){2-4}
+		\cmidrule(lr){5-7}
 		Perf. &
-		\multicolumn{1}{c}{mean} &
 		\multicolumn{1}{c}{min} &
 		\multicolumn{1}{c}{mean} &
-		\multicolumn{1}{c}{min}\\
+		\multicolumn{1}{c}{failures} &
+		\multicolumn{1}{c}{min} &
+		\multicolumn{1}{c}{mean} & 
+		\multicolumn{1}{c}{failures}\\
 		\midrule
-		Oracle & \num{0} & \num{0} & \num{0} & \num{0} \\
-		Nominal & \num{0} & \num{0} & \num{0} & \num{0} \\
-		\OurAlgorithm & \num{0} & \num{0} & \num{0} & \num{0} \\
+		Oracle & {11.6} & {14.2} & 0\% & {0} & {0} & 0\\
+		{Nominal} & {2.8} & \textbf{13.8} & 4\% & {0} & {0} & 0 \\
+		Robust & \textbf{10.4} & {13.0} & \textbf{0\%} & {0} & {0} & 0 \\
 		\bottomrule
@@
 
-In  \autoref{fig:regret} study the evolution of the agent conservativeness as they collect more data.
-Given a trajectory $x_0, R_0, x_1, R_1, \dots$, we compute the cumulative return $J_n(x_n) = \sum_{k\geq n} \gamma^k R_k$ at each state, and compare it to the optimal value $V(x_n)$, the return the agent would have got if it had acted optimally with respect to the oracle model.
-
 \begin{figure}[tp]
@@
 	\includegraphics[width=0.8\linewidth]{img/regret.pdf}
-	\caption{We compare the performance of the robust agent to the optimal performance $\hat{V}^r(s_n)-V^*(s_n)$, with respect to the number $n$ of interactions.}
+	\caption{The mean regret with its $95\%$ confidence interval for the robust and nominal agents with respect to time.}
 	\label{fig:regret}
 \end{figure}
+
+In  \autoref{fig:regret} study the evolution of the agent conservativeness as they collect more data.
+Given a trajectory $x_0, R_0, x_1, R_1, \dots$, we compute the cumulative return $J_n(x_n) = \sum_{k\geq n} \gamma^k R_k$ at each state, and compare it to the optimal value $V(x_n)$, the return the agent would have got if it had acted optimally with respect to the oracle model.
 

### 2020-02-04 main.tex
Update proof

@@
 However, under an additional smoothness assumption on $R$, we can bound this gap:
-\begin{theorem}
+\begin{theorem}[Approximation gap]
 \label{thm:control-error}
-If the reward function $R$ is lipschitz, then the approximation error of \autoref{alg:full} is upper-bounded by:
-\begin{equation*}
-     V^r(\bu) - \hat{V}^r(\bu) = \cO\left(\frac{1}{\sqrt{N}}\right)
+If the reward function $R$ is lipschitz, then we can bound the approximation error of \autoref{alg:full}:
+\begin{equation*}
+\hat{V}^r(\bu) \leq {V}^r(\bu) \leq V(\bu) \leq \hat{V}^r(\bu) + \cO\left(\frac{1}{\sqrt{N}}\right)
 \end{equation*}
@@
 then,
-\[\|\theta - \theta_{[N],\lambda}\|_{2} = \cO\left( \sqrt{\frac{\log N}{N}} \right) \]
+\[\|A(\theta) - A(\theta_{[N],\lambda})\|_2 = \cO\left( \sqrt{\frac{\log N}{N}} \right) \]
 \end{lemma}
@@
 \end{align*}
-
-which yields the desired bound.
+Thus,
+\[\|\theta - \theta_{[N],\lambda}\|_{2} = \cO\left( \sqrt{\frac{\log N}{N}} \right) \]
+
+And $A(\theta)$ belongs to a linear image of this ball. By writing a the $j^{th}$ column of a matrix $M$ as $M_j$, and its coefficient $i,j$ as $M_{i,j}$,
+\begin{align*}
+((A(\theta)&-A(\theta_{[N],\lambda}))^\transp (A(\theta) - A(\theta_{[N],\lambda})))_{i,j}\\
+%&= (\phi_i(\theta-\theta_{[N],\lambda}))^\transp \phi_j(\theta-\theta_{[N],\lambda}) \\
+&= (\theta-\theta_{[N],\lambda})^\transp\phi_{i}^{\transp}\phi_j(\theta-\theta_{[N],\lambda}) \\
+&\leq \lambda_{\max}(\phi_{i}^{\transp}\phi_j) \|\theta - \theta_{[N],\lambda}\|_{2} = \cO\left( \sqrt{\frac{\log N}{N}} \right) 
+\end{align*}
+
 \end{proof}
@@
 \begin{lemma}
-	\todo{Which result?}
+
+\[\|\ox(t) - \ux(t)\| \leq C_\omega(t) +\cO\left( \sqrt{\frac{\log N}{N}} \right) \]
+where $C_\omega(t)$ is the interval size $\|\ox(t) - \ux(t)\|$ obtained by running \eqref{eq:interval-predictor} with $\Delta A=0$.
+
 \end{lemma}
 \begin{proof}
-Let $\delta x = \ox - \ux$. Assuming that eventually after $n\geq n_0$ $A_0$ becomes close enough to $A(\theta)$ to always be Metlzer. Then, \eqref{eq:interval-predictor} gives the dynamics:
-\begin{align*}
-\dot{\delta x} = A_0\delta x + |\Delta A|(\ox^+ + \ux^-) + |D|(\overline{\omega} - \underline{\omega})
+Let $e = \ox - \ux$.
+Assuming that eventually after $n\geq N \geq N_0$, $A_0 = A(\theta_{[N],\lambda})$ becomes close enough to $A(\theta)$ to always be Metlzer.
+Then, \eqref{eq:interval-predictor} gives the dynamics:
+\begin{align*}
+\dot{e} = A_0e + |\Delta A|(\ox^+ + \ux^-) + |D|(\overline{\omega} - \underline{\omega})
 \end{align*}
@@
 
-Moreover, it holds that $-\ux^+ -\ox^- \leq \delta x \leq \ox^+ + \ux^-$, which implies $|\ux^+ + \ox^-| \leq 2 |\delta x|$.
-
-We define $V = \delta x^\transp P \delta x$, and compute its derivative:
+Moreover, it holds that $-\ux^+ -\ox^- \leq e \leq \ox^+ + \ux^-$, which implies $|\ux^+ + \ox^-| \leq 2 |e|$.
+
+We define $V = e^\transp P e$, which is non-negative definite provided that
+$
+P>0,
+$ and compute its derivative:
 \begin{align*}
@@
 X\\
-& - \delta x^\transp Q \delta x + \alpha |\ux^+ + \ox^-|^2 + \rho |\overline{\omega} - \underline{\omega}|^2
+& - e^\transp Q e + \alpha |\ux^+ + \ox^-|^2 + \rho |\overline{\omega} - \underline{\omega}|^2
 \end{align*}
 with $X=\begin{bmatrix}
-\delta x\\ \ux^+ + \ox^- \\ \overline{\omega} - \underline{\omega}
+e\\ \ux^+ + \ox^- \\ \overline{\omega} - \underline{\omega}
 \end{bmatrix}$. Hence, 
@@
 \dot{V} \leq {}& X^\transp
-\begin{bmatrix}
+\underbrace{\begin{bmatrix}
 A_0^\transp P + P A_0^\transp + Q + 2\alpha^2 I_p & P|\Delta A| & P|D|\\
@@
 D^\transp|P| & 0 & -\rho I_p
-\end{bmatrix}
+\end{bmatrix}}_{\Upsilon}
 X\\
-& - \delta x^\transp Q \delta x + \rho |\overline{\omega} - \underline{\omega}|^2
-\end{align*}
-
+& - e^\transp Q e + \rho |\overline{\omega} - \underline{\omega}|^2
+\end{align*}
+
+Thus, if $\Upsilon < 0$, $Q>0$, $\rho > 0$, $V$ is bounded and can only increases from $V(e(t_N)) = 0$ to a $V(e)$ such that:
+\[
+e^\transp Q e = X^\transp \Upsilon X + \rho |\overline{\omega} - \underline{\omega}|^2
+\]
 \end{proof}
@@
 \begin{proof}
- By the inclusion property \eqref{eq:inclusion-property}, for any sequence of controls $\bu$, dynamics $A(\theta)\in C_{[N],\delta}$ and perturbations $\underline{\bw} \leq \bw \leq \overline{\bw}$, we have that $\underline{x}_n \leq x_n \leq \overline{x}_n$, which implies that $R(x_n) \leq \max_{x\in[\underline{x}_n(\bu), \overline{x}_n(\bu)]}  R(x)$.
-
- Thus, assuming $R$ is $L$-lipschitz,
+
+ For any sequence of controls $\bu$, dynamics $A(\theta)\in C_{[N],\delta}$ and perturbations $\underline{\bw} \leq \bw \leq \overline{\bw}$, we clearly have 
+ \[V(\bu)^r \leq V(\bu) = \expectedvalue_{\bw}\sum_n \gamma^n R(x_n)\]
+
+ Moreover, by the inclusion property \eqref{eq:inclusion-property}, we have that $\underline{x}_n \leq x_n \leq \overline{x}_n$, which implies that $R(x_n) \leq \max_{x\in[\underline{x}_n(\bu), \overline{x}_n(\bu)]}  R(x)$.
+Assuming $R$ is $L$-lipschitz,
  \begin{align}
-     V^r(\bu) - \hat{V}^r(\bu) &\leq \sum_{n=N+1}^\infty \gamma^n \underset{{x\in[\underline{x}_n(\bu), \overline{x}_n(\bu)]}}{(\max - \min)} R(x)\\
-     &\leq \sum_{n=N+1}^\infty \gamma^n L \left\|\underline{x}_n(\bu) - \overline{x}_n(\bu)\right\|\\
-     &\leq L/(1-\gamma) \cO\left(\sqrt{\log N / N}\right)
+     V(\bu) - \hat{V}^r(\bu) &\leq \sum_{n=N+1}^\infty \gamma^n \underset{{x\in[\underline{x}_n(\bu), \overline{x}_n(\bu)]}}{(\max - \min)} R(x)\\
+     &\leq \sum_{n=N+1}^\infty \gamma^n L \left\|\underline{x}_n(\bu) - \overline{x}_n(\bu)\right\|_2\\
+     &\leq L\sum_{n>N} \gamma^n C_{\omega,n} + \cO\left(\sqrt{\log N / N}\right))
  \end{align}

### 2020-02-04 main.tex
Proof of Theorem 4

@@
 \usepackage{multirow}
+\usepackage{bm}
 \input{mathdef.tex}
@@
 For any variable $z$, we use the subscript notation to refer to these discrete times: $z_n = z(t_n)$ with $t_n = n\dd t$.
-We use bold symbols to denote sequences $\bz = (z_1,z_2,\dots)$.
+We use bold symbols to denote temporal sequences $\bz = (z_n)_{n\in\Natural}$.
 
@@
 \label{eq:robust-control}
-\sup_{\bu\in{(\Real^q)}^\Natural} \underbrace{\inf_{\substack{A(\theta) \in \cC_{[N],\delta} \\ \bw\in[\underline{\bw},\overline{\bw}]^\Natural}} \left[\sum_{n=N+1}^\infty \gamma^n R(x_n(\bu,\bw))\right]}_{V^r(\bu)}
-\end{equation}
-where $\bu = (u_{N+1},u_{N+2},\dots)$ and $\bw = (\omega_N, \omega_{N+1},\dots)$ are the sequences of future controls and perturbations, respectively.
+\sup_{\bu\in{(\Real^q)}^\Natural} \underbrace{\inf_{\substack{A(\theta) \in \cC_{[N],\delta} \\ \bom\in[\underline{\bom},\overline{\bom}]^\Natural}} \left[\sum_{n=N+1}^\infty \gamma^n R(x_n(\bu,\bom))\right]}_{V^r(\bu)}
+\end{equation}
+where $\bu = (u_{N+1},u_{N+2},\dots)$ and $\bom = (\omega_N, \omega_{N+1},\dots)$ are the sequences of future controls and perturbations, respectively.
 The rest of the paper will tackle the optimisation of this objective.
@@
 \label{eq:robust-control-disc}
-\sup_{\ba\in{\cA}^\Natural} \underbrace{\inf_{\substack{A(\theta) \in \cC_{[N],\delta} \\ \bw\in[\underline{\bw},\overline{\bw}]^\Natural}} \left[\sum_{n=N+1}^\infty \gamma^n R(x_n(\ba,\bw))\right]}_{V^r(\ba)}
-\end{equation}
-where $x_n(\ba, \bw)$ is obtained by integrating \eqref{eq:dynamics} with $u_n = \pi_{a_n}(x_n)$.
+\sup_{\ba\in{\cA}^\Natural} \underbrace{\inf_{\substack{A(\theta) \in \cC_{[N],\delta} \\ \bom\in[\underline{\bom},\overline{\bom}]^\Natural}} \left[\sum_{n=N+1}^\infty \gamma^n R(x_n(\ba,\bom))\right]}_{V^r(\ba)}
+\end{equation}
+where $x_n(\ba, \bom)$ is obtained by integrating \eqref{eq:dynamics} with $u_n = \pi_{a_n}(x_n)$.
 
@@
 However, there exists a gap between $\hat{V}^r$ and the true robust objective $V^r$, which stems from three approximations: (i) the true reachable set was approximated by an enclosing interval in \eqref{eq:inclusion-property}; (ii) the time-invariance of the dynamics uncertainty $A(\theta)\in\cC_{[N],\delta}$ was handled by the interval predictor \eqref{eq:interval-predictor} as if it were a time-varying uncertainty $\forall t, A(\theta(t))\in\cC_{[N],\delta}$ ; and (iii) the lower-bound $\sum\min\leq \min\sum$ used to define the surrogate objective \eqref{eq:surrogate_objective} is not tight.
-
-However, under an additional smoothness assumption on $R$, we can bound this gap:
-\begin{theorem}[Approximation gap]
+However, this gap can be bounded with additional assumptions:
+\begin{theorem}[Sample complexity]
 \label{thm:control-error}
-If the reward function $R$ is lipschitz, then we can bound the approximation error of \autoref{alg:full}:
-\begin{equation*}
-\hat{V}^r(\bu) \leq {V}^r(\bu) \leq V(\bu) \leq \hat{V}^r(\bu) + \cO\left(\frac{1}{\sqrt{N}}\right)
-\end{equation*}
+Under some assumptions specified in the proof, which amounts to
+\begin{enumerate}
+	\item the reward function $R$ is lipschitz;
+	\item a persistent excitation assumption;
+	\item a stability condition in the form of an LMI;
+\end{enumerate}
+ we can bound the approximation error of \autoref{alg:full}:
+\begin{equation*}
+\hat{V}^r(\bu) \leq {V}^r(\bu) \leq V(\bu) \leq \hat{V}^r(\bu) + \Delta_\omega + \cO\left({\log N / N}\right)
+\end{equation*}
+where $\Delta_\omega$ is a constant specified in the proof, which corresponds to an irreductible suboptimality suffered from being robust to the perturbations $\omega(t)$, with knowledge of $A(\theta)$.
+% $\max_a \sum_n \min_\omega$
 \end{theorem}
@@
 \begin{table}[htbp]
-	\caption{Mean and worst-case performance}
-	\label{tab:results}
+	\caption{Performances on the Obstacle task}
+	\label{tab:obstacle}
 	\centering
-	\begin{tabular}{lcccccc}
+	\begin{tabular}{lccc}
 		\toprule
-		\multicolumn{1}{l}{Task} &
-		\multicolumn{3}{c}{Obstacle}    &
-		\multicolumn{3}{c}{Driving}\\
-		\cmidrule(lr){2-4}
-		\cmidrule(lr){5-7}
-		Perf. &
-		\multicolumn{1}{c}{min} &
-		\multicolumn{1}{c}{mean} &
-		\multicolumn{1}{c}{failures} &
-		\multicolumn{1}{c}{min} &
-		\multicolumn{1}{c}{mean} & 
-		\multicolumn{1}{c}{failures}\\
+		\multirow{2}{*}{Agent} &
+		\multicolumn{2}{c}{Return} &
+		\multirow{2}{*}{Failures} \\
+		\cmidrule{2-3} & min &
+		mean $\pm$ std & \\
 		\midrule
-		Oracle & {11.6} & {14.2} & 0\% & {0} & {0} & 0\\
-		{Nominal} & {2.8} & \textbf{13.8} & 4\% & {0} & {0} & 0 \\
-		Robust & \textbf{10.4} & {13.0} & \textbf{0\%} & {0} & {0} & 0 \\
+		Oracle & {11.6} & {$14.2 \pm 1.3$} & 0\% \\
+		\midrule
+		{Nominal} & {2.8} & \textbf{$13.8 \pm 2.0$} & {4\%} \\
+		Robust & \textbf{10.4} & {$13.0 \pm 1.5$} & \textbf{0\%} \\
 		\bottomrule
@@
 Since these are unknown in practice, we adopt the multi-model perspective of \autoref{sec:multi-model} and consider one model per possible route allocation for every observed vehicle before an intersection.
+
+\begin{table}[htbp]
+	\caption{Performances on the Driving task}
+	\label{tab:driving}
+	\centering
+	\begin{tabular}{lccc}
+		\toprule
+		\multirow{2}{*}{Agent} &
+		\multicolumn{2}{c}{Return} &
+		\multirow{2}{*}{Failures} \\
+		\cmidrule{2-3} & min &
+		mean $\pm$ std & \\
+		\midrule
+		Oracle & {6.9} & {7.4} & 0\% \\
+		\midrule
+		{Nominal K} & {3.8} & \textbf{4.6} \\
+		{Nominal U} & {3.0} & {4.3} \\
+		Robust & {3.04} & {13.0} & \textbf{0\%} \\
+		\bottomrule
+	\end{tabular}
+\end{table}
 
@@
 	The predictor designed in \autoref{sec:prediction} verifies the inclusion property \eqref{eq:inclusion-property}.
-Thus, for sequence of controls $\bu$, any dynamics $A(\theta)\in C_{[N],\delta}$, and perturbations $\underline{\bw} \leq \bw \leq \overline{\bw}$, the corresponding state at time $t_n$ is bounded by $\underline{x}_n \leq x_n \leq \overline{x}_n$, which implies that $R(x_n) \geq \min_{x\in[\underline{x}_n(\bu), \overline{x}_n(\bu)]}  R(x) = \underline{R}_n(\bu)$.
-
-	Thus, by taking the min over $C_{[N],\delta}$ and $[\underline{\bw}, \overline{\bw}]$, we also have for any sequence of controls $\bu$:
-	\begin{align*}
-	    V^r(\bu) &= \min_{\substack{A(\theta)\in C_{[N],\delta}\\ \underline{\bw} \leq \bw \leq \overline{\bw}}} \sum_{n=N+1}^\infty \gamma^n R(x_n)\\
+Thus, for sequence of controls $\bu$, any dynamics $A(\theta)\in C_{[N],\delta}$, and perturbations $\underline{\bom} \leq \bom \leq \overline{\bom}$, the corresponding state at time $t_n$ is bounded by $\underline{x}_n \leq x_n \leq \overline{x}_n$, which implies that $R(x_n) \geq \min_{x\in[\underline{x}_n(\bu), \overline{x}_n(\bu)]}  R(x) = \underline{R}_n(\bu)$.
+
+	Thus, by taking the min over $C_{[N],\delta}$ and $[\underline{\bom}, \overline{\bom}]$, we also have for any sequence of controls $\bu$:
+	\begin{align*}
+	    V^r(\bu) &= \min_{\substack{A(\theta)\in C_{[N],\delta}\\ \underline{\bom} \leq \bom \leq \overline{\bom}}} \sum_{n=N+1}^\infty \gamma^n R(x_n)\\
 	    &\geq \sum_{n=N+1}^\infty \gamma^n \underline{R}_n(\bu)\\
@@
 \label{eq:excitation}
-\exists \underline{\phi},\overline{\phi}>0, n_0: \forall n\geq n_0,i,j\in[p],\nonumber\\ \underline{\phi}^2 \leq \sum_k \sum_l \phi_{n,k,i}\Sigma_{p,k,l}^{-1}\phi_{n,l,j} \leq \overline{\phi}^2,
+\exists \underline{\phi},\overline{\phi}>0, n_0: \forall n\geq n_0,\nonumber\\ \underline{\phi}^2 \leq \lambda(\Phi_{n}^\transp\Sigma_{p}^{-1}\Phi_{n}) \leq \overline{\phi}^2,
 \end{align}
@@
 \begin{proof}
-By \eqref{eq:g_n_lambda} and \eqref{eq:excitation}, we have $G_{[N],\lambda,i,j} \geq N\underline{\phi}^2 $
+By \eqref{eq:g_n_lambda} and \eqref{eq:excitation}, we have $\lambda_{\min}(G_{[N],\lambda,i,j}) \geq N\underline{\phi}^2 $
 
@@
 &= (\theta-\theta_{[N],\lambda})^\transp\phi_{i}^{\transp}\phi_j(\theta-\theta_{[N],\lambda}) \\
-&\leq \lambda_{\max}(\phi_{i}^{\transp}\phi_j) \|\theta - \theta_{[N],\lambda}\|_{2} = \cO\left( \sqrt{\frac{\log N}{N}} \right) 
+&\leq \lambda_{\max}(\phi_{i}^{\transp}\phi_j) \|\theta - \theta_{[N],\lambda}\|_{2}^2 = \cO\left( {\frac{\log N}{N}} \right) 
 \end{align*}
@@
 \begin{lemma}
-
-\[\|\ox(t) - \ux(t)\| \leq C_\omega(t) +\cO\left( \sqrt{\frac{\log N}{N}} \right) \]
-where $C_\omega(t)$ is the interval size $\|\ox(t) - \ux(t)\|$ obtained by running \eqref{eq:interval-predictor} with $\Delta A=0$.
-
+If there exist $P>0,Q_0\in\Real^{p\times p}$, $\rho>0$ such that
+\begin{align*}
+\begin{bmatrix}
+A_0^\transp P + P A_0^\transp + Q_0 & P|D| & P|\Delta A| \\
+|D|^\transp P & -\rho I_r & 0\\
+|\Delta A|^\transp P & 0 & -\lambda_{\max}(|\Delta A|) I_p
+\end{bmatrix}< 0,
+\end{align*}
+then for all $t> t_N$,
+\[\|\ox(t) - \ux(t)\| \leq \left(C_0 + \cO\left({\frac{\log N}{N}} \right)\right)C_\omega(t) \]
+where $C_\omega(t) = \sup_{\tau\in[t_N,t]} \|\overline{\omega}(\tau) - \underline{\omega}(\tau)\|_2^2$ and $C_0 = \sqrt{{\rho\lambda_{\max}(P)}/({\lambda_{\min}(P)\lambda_{\min}(Q_0)})}$.
 \end{lemma}
@@
 
-Moreover, it holds that $-\ux^+ -\ox^- \leq e \leq \ox^+ + \ux^-$, which implies $|\ux^+ + \ox^-| \leq 2 |e|$.
-
 We define $V = e^\transp P e$, which is non-negative definite provided that
@@
 \begin{bmatrix}
-A_0^\transp P + P A_0^\transp + Q & P|\Delta A| & P|D|\\
-|\Delta A|^\transp P & -\alpha I_n & 0\\
-D^\transp|P| & 0 & -\rho I_p
+A_0^\transp P + P A_0^\transp + Q & P|D| & P|\Delta A| \\
+|D|^\transp P & -\rho I_r & 0\\
+|\Delta A|^\transp P & 0 & -\alpha I_p
 \end{bmatrix}
@@
 with $X=\begin{bmatrix}
-e\\ \ux^+ + \ox^- \\ \overline{\omega} - \underline{\omega}
-\end{bmatrix}$. Hence, 
+e & \overline{\omega} - \underline{\omega} &  \ux^+ + \ox^-
+\end{bmatrix}^\transp$, for any $Q\in\Real^{p\times p}$, $\rho,\alpha\in\Real$ .
+
+Moreover, it holds that $-\ux^+ -\ox^- \leq e \leq \ox^+ + \ux^-$, which implies $|\ux^+ + \ox^-| \leq 2 |e|$. Hence,
 \begin{align*}
@@
 \underbrace{\begin{bmatrix}
-A_0^\transp P + P A_0^\transp + Q + 2\alpha^2 I_p & P|\Delta A| & P|D|\\
-|\Delta A|^\transp P & -\alpha I_n & 0\\
-D^\transp|P| & 0 & -\rho I_p
+A_0^\transp P + P A_0^\transp + Q + 4\alpha I_p & P|D| & P|\Delta A| \\
+|D|^\transp P & -\rho I_r & 0\\
+|\Delta A|^\transp P & 0 & -\alpha I_p
 \end{bmatrix}}_{\Upsilon}
 X\\
-& - e^\transp Q e + \rho |\overline{\omega} - \underline{\omega}|^2
-\end{align*}
-
-Thus, if $\Upsilon < 0$, $Q>0$, $\rho > 0$, $V$ is bounded and can only increases from $V(e(t_N)) = 0$ to a $V(e)$ such that:
+& - e^\transp Q e + \rho \|\overline{\omega} - \underline{\omega}\|_2^2
+\end{align*}
+
+Thus, if we had $\Upsilon < 0$, $Q>0$, $\rho > 0$, then we would have
 \[
-e^\transp Q e = X^\transp \Upsilon X + \rho |\overline{\omega} - \underline{\omega}|^2
+\dot{V} \leq -\mu V + \rho \|\overline{\omega} - \underline{\omega}\|_2^2
 \]
+with $\mu = \frac{\lambda_{\min}(Q)}{\lambda_{\max}(P)}$. Since $V(t_N) = 0$, this further implies that for all $t>t_N$, 
+\begin{equation}
+\label{eq:lyap-bound}
+V(t) \leq \frac{\rho}{\mu} C_\omega(t)
+\end{equation}
+
+We now examine the condition $\Upsilon < 0$.
+We resort to its Schur complement: $\Upsilon < 0$ if and only if $\alpha > 0$ and $R > S$, where $S= \alpha^{-1}\begin{bmatrix}|\Delta A|^\transp P & 0\end{bmatrix}^\transp \begin{bmatrix}|\Delta A|^\transp P & 0\end{bmatrix}$ and $R$ is the top-left block of $-\Upsilon$:
+\[R = \begin{bmatrix}
+-A_0^\transp P - P A_0^\transp - Q - 4\alpha I_p & -P|D|\\
+-|D|^\transp P & \rho I_r\\
+\end{bmatrix}\]
+
+Let $Q_0 = Q-4\alpha I_p$.
+Assume that $P$ is fixed, we have $\lambda_{\max}(S) \leq \alpha^{-1}\lambda_{\max}(P)^2\lambda_{\max}(|\Delta A|)^2$.
+Thus, by taking $\alpha_N = \lambda_{\max}(|\Delta A|)^2 = \cO(\log N / N)$, $S = \begin{bmatrix}
+S_0 & 0\\0 & 0
+\end{bmatrix}$ becomes $\cO(1)$ with respect to $N$.
+Thus, we can always find a $Q_0$ such that
+\[R-S = \begin{bmatrix}
+-A_0^\transp P - P A_0^\transp - Q_0 - S_0 & -P|D|\\
+-|D|^\transp P & \rho I_r\\
+\end{bmatrix} > 0 \]
+
+We recover \eqref{eq:lyap-bound} with $\mu = \frac{\lambda_{\min}(Q)}{\lambda_{\max}(P)} = \frac{\lambda_{\min}(Q_0) - \alpha_N}{\lambda_{\max}(P)}$.
+Finally, we obtain
+\begin{align*}
+\|e(t)\|_2^2 &\leq \lambda_{\min}(P)^{-1} V(t)\\
+& \leq \frac{\rho\lambda_{\max}(P)/\lambda_{\min}(P)}{\lambda_{\min}(Q_0) - \alpha_N} C_\omega(t)\\
+\end{align*}
+Developing at the first order in $\alpha_N$ gives
+\begin{align*}
+\|e(t)\|_2 &\leq C_0\left(1 + \frac{\alpha_N}{2\lambda_{\min}(Q_0)} + \cO(\alpha_N^2)\right)C_\omega(t)\\
+&\leq \left(C_0 + \cO(\log N/N)\right)C_\omega(t)
+\end{align*}
 \end{proof}
@@
 
- For any sequence of controls $\bu$, dynamics $A(\theta)\in C_{[N],\delta}$ and perturbations $\underline{\bw} \leq \bw \leq \overline{\bw}$, we clearly have 
- \[V(\bu)^r \leq V(\bu) = \expectedvalue_{\bw}\sum_n \gamma^n R(x_n)\]
+ For any sequence of controls $\bu$, dynamics $A(\theta)\in C_{[N],\delta}$ and perturbations $\underline{\bom} \leq \bom \leq \overline{\bom}$, we clearly have 
+ \[V(\bu)^r \leq V(\bu) = \expectedvalue_{\bom}\sum_n \gamma^n R(x_n)\]
 
@@
 Assuming $R$ is $L$-lipschitz,
- \begin{align}
+ \begin{align*}
      V(\bu) - \hat{V}^r(\bu) &\leq \sum_{n=N+1}^\infty \gamma^n \underset{{x\in[\underline{x}_n(\bu), \overline{x}_n(\bu)]}}{(\max - \min)} R(x)\\
      &\leq \sum_{n=N+1}^\infty \gamma^n L \left\|\underline{x}_n(\bu) - \overline{x}_n(\bu)\right\|_2\\
-     &\leq L\sum_{n>N} \gamma^n C_{\omega,n} + \cO\left(\sqrt{\log N / N}\right))
- \end{align}
+     &\leq L(C_0 + \cO\left({\log N / N}\right)) \sum_{n>N} \gamma^n C_{\omega}(t_n)\\
+     &= \Delta_\omega + \cO\left({\log N / N}\right)
+ \end{align*}
+ with $\Delta_\omega = L C_0\sum_{n>N} \gamma^n C_{\omega}(t_n)$.
 \end{proof}

### 2020-02-04 main.tex
Add table of results for the driving task
Update figures

@@
 
-\begin{figure}
+\begin{figure}[t]
 	\centering
-	\includegraphics[width=\linewidth]{img/epc-friction}
-	\caption{\textbf{Left}: the state prediction procedure. \textbf{Right}: the model estimation procedure.}
+	\includegraphics[width=0.6\linewidth]{img/ellipsoid}
+	\caption{The model estimation procedure. The size of the confidence region $C_{[N],\delta}$ shrinks with the number of samples $N$.}
+\end{figure}
+
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=0.8\linewidth]{img/obstacle_small}
+	\caption{The state prediction procedure. At each timestep (red to green), we bound the set of reachable states considering model uncertainty \eqref{eq:confidence}}
 	\label{fig:estimation-prediction}
@@
 		\multirow{2}{*}{Agent} &
-		\multicolumn{2}{c}{Return} &
-		\multirow{2}{*}{Failures} \\
-		\cmidrule{2-3} & min &
-		mean $\pm$ std & \\
+		\multirow{2}{*}{Failures} &
+		\multicolumn{2}{c}{Return} \\
+		\cmidrule{3-4} & & min &
+		mean $\pm$ std \\
 		\midrule
-		Oracle & {11.6} & {$14.2 \pm 1.3$} & 0\% \\
+		Oracle & 0\% & {11.6} & {$14.2 \pm 1.3$} \\
 		\midrule
-		{Nominal} & {2.8} & \textbf{$13.8 \pm 2.0$} & {4\%} \\
-		Robust & \textbf{10.4} & {$13.0 \pm 1.5$} & \textbf{0\%} \\
+		{Nominal} & {4\%} & {2.8} & \textbf{$\mathbf{13.8} \pm 2.0$} \\
+		Robust (ours) & \textbf{0\%} & \textbf{10.4} & {$13.0 \pm 1.5$} \\
 		\bottomrule
@@
 	\includegraphics[width=0.8\linewidth]{img/regret.pdf}
-	\caption{The mean regret with its $95\%$ confidence interval for the robust and nominal agents with respect to time.}
+	\caption{The mean regret with its $95\%$ confidence interval for the robust and nominal agents with respect to the number $N$ of samples.}
 	\label{fig:regret}
@@
 		\multirow{2}{*}{Agent} &
-		\multicolumn{2}{c}{Return} &
-		\multirow{2}{*}{Failures} \\
-		\cmidrule{2-3} & min &
-		mean $\pm$ std & \\
+		\multirow{2}{*}{Failures} &
+		\multicolumn{2}{c}{Return} \\
+		\cmidrule{3-4} && min &
+		mean $\pm$ std  \\
 		\midrule
-		Oracle & {6.9} & {7.4} & 0\% \\
+		Oracle & 0\% & {6.9} & $7.4 \pm 0.5$ \\
 		\midrule
-		{Nominal K} & {3.8} & \textbf{4.6} \\
-		{Nominal U} & {3.0} & {4.3} \\
-		Robust & {3.04} & {13.0} & \textbf{0\%} \\
+		{Nominal B} & 4\% & {5.2} & $\mathbf{7.3} \pm 1.5$ \\
+		{Nominal R} & 33\% & {3.5} & $6.4 \pm 0.26$ \\
+		Robust (ours) & \textbf{0\%} & \textbf{6.8} & $7.1 \pm 0.29$ \\
 		\bottomrule

### 2020-02-05 main.tex
Add highway figure
Updates from Overleaf

@@
 \begin{enumerate}
-	\item the reward function $R$ is lipschitz;
-	\item a persistent excitation assumption;
+	\item a regularity (lipschitz) assumption for the reward $R$;
+	\item a persistent excitation (PE) assumption;
 	\item a stability condition in the form of an LMI;
@@
 \end{equation*}
-where $\Delta_\omega$ is a constant specified in the proof, which corresponds to an irreductible suboptimality suffered from being robust to the perturbations $\omega(t)$, with knowledge of $A(\theta)$.
+where $\Delta_\omega$ is a constant specified in the proof, which corresponds to an irreductible suboptimality suffered from being robust to instantaneous perturbations $\omega(t)$, with knowledge of $A(\theta)$.
 % $\max_a \sum_n \min_\omega$
@@
 
+\begin{figure}
+	\centering
+	\includegraphics[width=0.8\linewidth]{img/highway-small}
+	\caption{The intersection crossing task.}
+\end{figure}
+
 \begin{table}[htbp]
@@
 \begin{lemma}
-Under sufficient excitations in the features 
+If the features $\Phi_n$ are persistently exciting:
 \begin{align}
 \label{eq:excitation}
-\exists \underline{\phi},\overline{\phi}>0, n_0: \forall n\geq n_0,\nonumber\\ \underline{\phi}^2 \leq \lambda(\Phi_{n}^\transp\Sigma_{p}^{-1}\Phi_{n}) \leq \overline{\phi}^2,
+\exists \underline{\phi},\overline{\phi}>0, n_0: \forall n\geq n_0,\nonumber\\ \underline{\phi}^2 \leq \lambda_{\min}(\Phi_{n}^\transp\Sigma_{p}^{-1}\Phi_{n}) \leq \overline{\phi}^2,
 \end{align}
@@
 \begin{proof}
-By \eqref{eq:g_n_lambda} and \eqref{eq:excitation}, we have $\lambda_{\min}(G_{[N],\lambda,i,j}) \geq N\underline{\phi}^2 $
+By \eqref{eq:g_n_lambda} and \eqref{eq:excitation}, we have $$\lambda_{\min}(G_{[N],\lambda,i,j}) \geq (N-n_0)\underline{\phi}^2 + \sum_{n<n_0}\Phi_{n}^\transp\Sigma_{p}^{-1}\Phi_{n}$$
 
@@
 \begin{align*}
-	\|\theta - \theta_{[N],\lambda}\|_{G_{[N],\lambda}} \geq \sqrt{N}\underline{\phi} \|\theta - \theta_{[N],\lambda}\|_{2} 
+	\|\theta - \theta_{[N],\lambda}\|_{G_{[N],\lambda}} \geq (\sqrt{N}\underline{\phi} + \cO(1))\|\theta - \theta_{[N],\lambda}\|_{2}
 \end{align*}
@@
 
-And $A(\theta)$ belongs to a linear image of this ball. By writing a the $j^{th}$ column of a matrix $M$ as $M_j$, and its coefficient $i,j$ as $M_{i,j}$,
+And $A(\theta)$ belongs to a linear image of this $L^2$-ball. By writing a the $j^{th}$ column of a matrix $M$ as $M_j$, and its coefficient $i,j$ as $M_{i,j}$,
 \begin{align*}

### 2020-02-05 main.tex
Update paper

@@
 
-Despite the dazzling successes of Reinforcement learning in cracking many problems considered unsolvable in the past decade [ref needed], this tool has hardly been applied in real industrial issues.
+Despite the recent successes of Reinforcement learning in cracking many hard problems, this tool has hardly been applied in real industrial issues.
 This could be attributed to two undesirable properties which limit its practical applications: the dependence on a tremendous amount of interaction data that cannot always be simulated, and the reliance on trial-and-error and random exploration.
@@
 For any variable $z$, we use the subscript notation to refer to these discrete times: $z_n = z(t_n)$ with $t_n = n\dd t$.
-We use bold symbols to denote temporal sequences $\bz = (z_n)_{n\in\Natural}$.
+We use bold symbols to denote temporal sequences $\bz = (z_n)_{n>N}$.
+We denote $z^+ = \max(z,0)$ and $z^- = z^+-z$, and $[n]$ denotes the interval $\{1,2,\dots, n\}$.
 
@@
 	\centering
-	\includegraphics[width=0.6\linewidth]{img/ellipsoid}
+	\includegraphics[trim={0 2cm 0 0}, clip, width=0.6\linewidth]{img/ellipsoid}
 	\caption{The model estimation procedure. The size of the confidence region $C_{[N],\delta}$ shrinks with the number of samples $N$.}
@@
 \end{equation}
-where $\bu = (u_{N+1},u_{N+2},\dots)$ and $\bom = (\omega_N, \omega_{N+1},\dots)$ are the sequences of future controls and perturbations, respectively.
-The rest of the paper will tackle the optimisation of this objective.
+The rest of the paper tackles the optimisation of \eqref{eq:robust-control}.
 
@@
 
-Minimax problems such as \eqref{eq:robust-control} are notoriously difficult to solve even in cases such as Linear-Quadratic systems (LQ) where the reward $R$ has a simple form.
+Minimax problems such as \eqref{eq:robust-control} are notoriously difficult to solve even in cases such as linear-quadratic systems (LQ) where the reward $R$ has a simple form.
 Here with an arbitrary function $R$, we cannot hope to derive a solution in explicit form.
@@
 
-\paragraph{Linear Quadratic systems} There is a rich body of literature dedicated to the study of LQ systems, and we focus on those providing non-asymptotic results when the system parameters $A, B$ are unknown.
+\paragraph{Linear-quadratic systems} There is a rich body of literature dedicated to the study of LQ systems, and we focus on those providing non-asymptotic results when the system parameters $A, B$ are unknown.
 In their seminal work \citet{abbasi-yadkori11a}, consider the problem of cumulative regret minimisation.
@@
 
-\begin{theorem}[Confidence ellipsoid, matrix version of \citep{Abbasi2011}]
+\begin{theorem}[Confidence ellipsoid, matrix version of \citealt{Abbasi2011}]
 \label{thm:confidence_ellipsoid}
@@
 \paragraph{Remark} The robust objective \eqref{eq:robust-control} involves bounds $\underline{\omega}(t)\leq \omega(t) \leq \overline{\omega}(t)$ over the possible perturbations we want to protect against.
-In the unbounded sub-Gaussian noise setting of \autoref{assumpt:gaussian-noise}, we can use the same formulation by deriving local high-confidence bounds that each holds with probability $\delta_t$.
-By choosing $\delta_t = \frac{\delta}{t(t+1)}$, we have that the event $\{\forall t, \underline{\omega}(t) \leq \omega(t) \leq \overline{\omega}(t)\}$ holds with probability $1-\delta$.
+In the unbounded sub-Gaussian noise setting of \autoref{assumpt:gaussian-noise}, we can use the same formulation by deriving local high-confidence bounds that each holds with probability $\delta_n$.
+By choosing $\delta_n = \frac{\delta}{n(n+1)}$, we have that the event $\{\forall n, \underline{\omega}(t_n) \leq \omega(t_n) \leq \overline{\omega}(t_n)\}$ holds with probability $1-\delta$.
 
@@
 
-In order to study the inclusion property \eqref{eq:inclusion-property}, we must start by choosing a set representation $X(t)$.
+To study the inclusion property \eqref{eq:inclusion-property}, we must start by choosing a set representation $X(t)$.
 We consider interval prediction, rather than zonotope prediction for instance, for the sake of simplicity of implementation and computational efficiency.
 Thus, we represent an interval as $X(t) = [\underline{x}(t), \overline{x}(t)]\in \Real^p\times \Real^p$, and the inclusion property becomes:
-
 \begin{equation}
@@
 
-A simple solution to \eqref{eq:inclusion-property} is proposed in \citep{efimov:hal-00701643}, where, given bounds $\underline{A}\leq A(\theta)\leq\overline{A}$ on $A(\theta)$ from $\cC_{[N],\delta}$ they use matrix interval arithmetics to derive the predictor:
-\begin{proposition}
+A simple solution to \eqref{eq:inclusion-property} is proposed in \citep{efimov:hal-00701643}, where, given bounds $\underline{A}\leq A(\theta)\leq\overline{A}$ from $\cC_{[N],\delta}$ they use matrix interval arithmetics to derive the predictor:
+\begin{proposition}[Simple predictor of \citealt{efimov:hal-00701643}]
 Assuming that \eqref{eq:confidence} is satisfied for the system \eqref{eq:dynamics}, then the interval predictor:
@@
 
-However, \citet{leurent2019interval} showed that this predictor can have unstable dynamics, even for stable systems, which can cause a rapid build-up of uncertainty.
-They propose an enhanced predictor which produces tighter and more stable predictions, and whose stability can be assessed by solving a linear matrix inequality, at the price of an additional requirement:
+However, \citet{leurent2019interval} showed that this predictor can have unstable dynamics, even for stable systems, which causes a fast build-up of uncertainty.
+They propose an enhanced predictor which exploits the polytopic structure \eqref{eq:polytope} produces tighter and more stable predictions, and whose stability can be assessed by solving an LMI, at the price of an additional requirement:
 
@@
 \label{assumpt:metzler}
-There exists an orthogonal matrix $P\in\Real^{d\times d}$ such that $P^\transp A_0 P$ is Metzler\footnote{A matrix is said to be Metlzer when all its non-diagonal coefficients are non-negative.}.
+There exists an orthogonal matrix $P\in\Real^{d\times d}$ such that $P^\transp A_0 P$ is Metzler\footnote{We say that a matrix is Metlzer when all its non-diagonal coefficients are non-negative.}.
 \end{assumption}
@@
 It is for instance the case whenever $A_0$ is diagonalisable, and a fortiori when it is stabilisable.
-The similarity transformation of \citep{Efimov_a2013} provides a method to compute such $P$ whenever there exist $C_1,C_2$ which make $A(\theta, C_1)$ and $(A_0, C_2)$ observable.
+The similarity transformation of \citep{Efimov_a2013} provides a method to compute such $P$.
+Denote $
+\Delta A_{+}=\sum_{i=1}^{2^d}\Delta A_{i}^{+},\;\Delta A_{-}=\sum_{i=1}^{2^d}\Delta A_{i}^{-}$.
+% The similarity transformation of \citep{Efimov_a2013} provides a method to compute such $P$ whenever there exist $C_1,C_2$ which make $(A(\theta), C_1)$ and $(A_0, C_2)$ observable.
 % Under this assumption, without loss of generality up to a change of basis $x\rightarrow P^{-1}x$ that we do not write for the sake of readability, this assumption is equivalent to considering that $A_0$ itself is Metzler.
 
-\begin{theorem}[Interval Predictor \citep{leurent2019interval}]
+\begin{theorem}[Enhanced Predictor of \citealt{leurent2019interval}]
 \label{thm:predictor}
@@
 	\centering
-	\includegraphics[width=\linewidth]{img/interval-predictor}
+	{\includegraphics[trim={0 0.6cm 0 0.4cm}, clip, width=\linewidth]{img/interval-predictor}}
+    \vspace{-0.5cm}
 	\caption{Comparison of \eqref{eq:predictor-naive} to \eqref{eq:interval-predictor} for a simple system $\dot{x}(t)=-\theta x(t)+d(t)$, with $\theta\in[1, 2]$.}
@@
 \label{sec:control}
-We approximate the robust objective $V^r$ in \eqref{eq:robust-control} by considering its interval prediction $[\underline{x}(t), \overline{x}(t)]$ based on the dynamics confidence region $\cC_\delta$.
+To evaluate the robust objective $V^r$ \eqref{eq:robust-control}, we approximate it thanks to the interval prediction $[\underline{x}(t), \overline{x}(t)]$ of \autoref{sec:prediction}.
 
@@
 
-This does not simply amounts to a change of reward function, since the worst case is assessed over the whole past trajectory being optimized, which means that this pessimistic reward $\underline{R_n}$ is not \emph{markovian}.
+This amounts to a change of reward function, except the worst case is assessed over the whole past trajectory being optimized, i.e. this pessimistic reward $\underline{R_n}$ is not \emph{markovian}.
 
@@
 
-The consequence of \autoref{prop:lower-bound} is that since all our approximations were conservative, if we manage to find a control sequence such that no \textit{``bad event''} (e.g.
+A direct consequence is that since all our approximations were conservative, if we manage to find a control sequence such that no \textit{``bad event''} (e.g.
 a collision) happens according to the surrogate objective $\hat{V}^r$, then we are guaranteed that they will not happen either when the controls are executed on the true system.
@@
 \paragraph{Planning}
-In order to optimise $\hat{V}^r$, we turn to sequential planning algorithms.
-We cannot use Dynamic Programming algorithms because the state space is continuous and the pessimistic rewards are non-markovian.
-Instead, we turn to tree-based planning algorithms which optimise a sequence of actions based on the corresponding sequence of rewards.
-These methods no dot require the enumeration of the states nor the markovity of the rewards.
-In particular, we consider the \emph{Optimistic Planning of Deterministic Systems} (\texttt{OPD}) algorithm \citep{Hren2008} tailored for the case where the sequence of rewards is a deterministic function of the sequence of actions.
-Indeed, the stochasticity of the perturbations and measurements is encased in $\hat{V}^r$: both the predictor dynamics \eqref{eq:interval-predictor} and the corresponding pessimistic rewards \eqref{eq:pessimistic-rewards} are deterministic.
-
-At each planning iteration $k\in[K]$, \texttt{OPD} progressively builds a tree $\cT_{k+1}$ by forming upper-bounds $B_a(k)$ over the sequence values called B-values, and expanding\footnote{The expansion of a leaf node $a$ refers to the simulation of its children transitions $aA = \{ab, b\in A\}$} the leaf $a_k$ with highest B-value:
+To optimise $\hat{V}^r$ \eqref{eq:surrogate_objective}, we cannot use Dynamic Programming algorithms since the state space is continuous and the pessimistic rewards are non-markovian.
+Instead, we turn to tree-based planning algorithms, which optimise a sequence of actions based on the corresponding sequence of rewards, without requiring markovity nor state enumeration.
+In particular, we consider the \emph{Optimistic Planning of Deterministic Systems} (\texttt{OPD}) algorithm \citep{Hren2008} tailored for the case when the relationship between actions and rewards is deterministic.
+Indeed, the stochasticity of the perturbations and measurements is encased in $\hat{V}^r$: both the predictor dynamics \eqref{eq:interval-predictor} and the pessimistic rewards \eqref{eq:pessimistic-rewards} are deterministic.
+
+At each planning iteration $k\in[K]$, \texttt{OPD} progressively builds a tree $\cT_{k+1}$ by forming upper-bounds $B_a(k)$ over the value of sequences of actions $a$, and expanding\footnote{The expansion of a leaf node $a$ refers to the simulation of its children transitions $aA = \{ab, b\in A\}$} the leaf $a_k$ with highest upper-bound:
 \begin{equation}
@@
 \end{equation}
-where $\cL_k$ is the set of leaves of $\cT_k$, $h(a)$ is the length of the sequence $a$, and $\underline{R}_n(a)$ the pessimistic reward \eqref{eq:pessimistic-rewards} obtained at time $n$ by following the sequence $a$.
+where $\cL_k$ is the set of leaves of $\cT_k$, $h(a)$ is the length of the sequence $a$, and $\underline{R}_n(a)$ the pessimistic reward \eqref{eq:pessimistic-rewards} obtained at time $n$ by following the controls $u_n = \pi_{a_n}(x_n)$.
 \begin{theorem}[Planning performance, \citep{Hren2008}]
 \label{theorem:opd-regret}
-The simple regret of the \texttt{OPD} algorithm \eqref{eq:opd} applied to the surrogate objective \eqref{eq:surrogate_objective} after $K$ iterations is:
+The simple regret of the \texttt{OPD} algorithm \eqref{eq:opd} applied to the surrogate objective \eqref{eq:surrogate_objective} after $K$ planning iterations is:
 \begin{align*}
 \text{if } \kappa>1,\quad& 
-\hat{V}^r(a^*) - \hat{V}^r({a_K}) = \cO\left(K^{-\frac{\log 1/\gamma}{\log \kappa}}\right);\\
+\hat{V}^r(a^{\star}) - \hat{V}^r({a_K}) = \cO\left(K^{-\frac{\log 1/\gamma}{\log \kappa}}\right);\\
 \text{if }\kappa=1,\quad&
-\hat{V}^r(a^*) - \hat{V}^r({a_K}) = \cO\left(\gamma^{\frac{(1-\gamma)^\beta}{c}K}\right)
+\hat{V}^r(a^{\star}) - \hat{V}^r({a_K}) = \cO\left(\gamma^{{(1-\gamma)^{\log_\gamma (\kappa/|\cA|)}}K/{c}}\right)
 \end{align*}
@@
 \[
-\kappa = \limsup_{h\rightarrow\infty} \left|\left\{a\in A^h: \hat{V}^r(a)\geq \hat{V}^r - \frac{\gamma^{h+1}}{1-\gamma}\right\}\right|^{1/h}.
+\kappa = \limsup_{h\rightarrow\infty} \left|\left\{a\in A^h: \hat{V}^r(a)\geq \hat{V}^r(a^{\star}) - \frac{\gamma^{h+1}}{1-\gamma}\right\}\right|^{1/h}.
 \]
@@
 
-Hence, by using enough computational budget $K$ for planning we can get as close as we want to the optimal surrogate value $\hat{V}^r(\bu^*)$, at a polynomial rate.
-However, there exists a gap between $\hat{V}^r$ and the true robust objective $V^r$, which stems from three approximations: (i) the true reachable set was approximated by an enclosing interval in \eqref{eq:inclusion-property}; (ii) the time-invariance of the dynamics uncertainty $A(\theta)\in\cC_{[N],\delta}$ was handled by the interval predictor \eqref{eq:interval-predictor} as if it were a time-varying uncertainty $\forall t, A(\theta(t))\in\cC_{[N],\delta}$ ; and (iii) the lower-bound $\sum\min\leq \min\sum$ used to define the surrogate objective \eqref{eq:surrogate_objective} is not tight.
+Hence, by using enough computational budget $K$ for planning we can get as close as we want to the optimal surrogate value $\hat{V}^r(a^{\star})$, at a polynomial rate.
+However, there exists a gap between $\hat{V}^r$ and the true robust objective $V^r$, which stems from three approximations: (i) the true reachable set was approximated by an enclosing interval in \eqref{eq:inclusion-property}; (ii) the time-invariance of the dynamics uncertainty $A(\theta)\in\cC_{[N],\delta}$ was handled by the interval predictor \eqref{eq:interval-predictor} as if it were a time-varying uncertainty $A(\theta(t))\in\cC_{[N],\delta},\forall t$ ; and (iii) the lower-bound $\sum\min\leq \min\sum$ used to define the surrogate objective \eqref{eq:surrogate_objective} is not tight.
 However, this gap can be bounded with additional assumptions:
@@
 \end{equation*}
-where $\Delta_\omega$ is a constant specified in the proof, which corresponds to an irreductible suboptimality suffered from being robust to instantaneous perturbations $\omega(t)$, with knowledge of $A(\theta)$.
-% $\max_a \sum_n \min_\omega$
+where $\Delta_\omega$ is a constant specified in the proof, which corresponds to an irreductible suboptimality suffered from being robust to instantaneous perturbations $\omega(t)$.
 \end{theorem}
@@
 
-The procedure we developed in sections \ref{sec:estimation}, \ref{sec:prediction} and \ref{sec:control} relies on restrictive modelling assumptions, such as the linear dynamics \eqref{eq:dynamics} or \autoref{assumpt:structure}.
+The procedure we developed in sections \ref{sec:estimation}, \ref{sec:prediction} and \ref{sec:control} relies on strong modelling assumptions, such as the linear dynamics \eqref{eq:dynamics} or \autoref{assumpt:structure}.
 But what if they are wrong?
@@
 \citet{delos2015} provide a way to test this membership in polynomial time using linear programming.
-
-Whenever this membership property is not verified, we can confidently reject the $(A,\phi)$-modelling \autoref{assumpt:structure}.
-This enables us to consider a rich set of potential features $\left((A^1, \phi^1), \dots, (A^M, \phi^M)\right)$ rather than relying on a single assumption.
+Whenever it is not verified, we can confidently reject the $(A,\phi)$-modelling \autoref{assumpt:structure}.
+This enables us to consider a rich set of potential features $\left((A^1, \phi^1), \dots, (A^M, \phi^M)\right)$ rather than relying on a single assumption, and only retain those that are consistent with the observations so far.
+Then, every remaining hypothesis must be considered during planning.
 
@@
 
-We temporarily ignore the parametric uncertainty over $\theta$ to simply consider several known candidate dynamics models, which all correspond to different modelling assumptions.
+We temporarily ignore the parametric uncertainty on $\theta$ to simply consider several candidate dynamics models, which all correspond to different modelling assumptions.
+We also restrict to deterministic dynamics, which is the case of \eqref{eq:interval-predictor}.
 
@@
 \label{assumpt:multi-model-ambiguity}
-Assume that the true dynamics $f$ lies within a finite set of candidate models $f^1, \dots, f^M$.
-\begin{equation}
+The true dynamics $f$ lies within a finite set of candidate models $f^1, \dots, f^M$.
+\begin{equation*}
 \exists m\in[M]: \dot{x}(t) = f^M(x(t), u(t)), \forall t\geq 0
-\end{equation}
+\end{equation*}
 \end{assumption}
@@
 \label{eq:robust-objective-discrete}
-V^r = \sup_{a\in\cA^\Natural}\min_{m\in[M]} \sum_{t=1}^\infty \gamma^t R_t^m
-\end{equation}
-where $R_t^m$ is the reward obtain by following the control sequence $\bu$ up to step $t$ under the dynamics $f^m$.
-This objective could be optimised in the same way as \ref{sec:control}, by computing a hull over the $M$ possible trajectories, but this would result in a coarse and lossy approximation.
-Instead, we can exploit the finite uncertainty structure of \autoref{assumpt:multi-model-ambiguity} to asymptotically recover the true $V^r$ by modifying the \texttt{OPD} planning algorithm in the following way:
-
-\begin{definition}[Robust sequence upper bounds] We define an upper-bound for the value of a sequences of action $a$:
+V^r = \sup_{a\in\cA^\Natural}\min_{m\in[M]} \sum_{n=N+1}^\infty \gamma^n R_n^m
+\end{equation}
+where $R_n^m$ is the reward obtain by following the action sequence $a$ up to step $n$ under the dynamics $f^m$.
+This objective could be optimised in the same way as in \autoref{sec:control}, but this would result in a coarse and lossy approximation.
+Instead, we can exploit the finite uncertainty structure of \autoref{assumpt:multi-model-ambiguity} to asymptotically recover the true $V^r$ by modifying the \texttt{OPD} algorithm in the following way:
+
+\begin{definition}[Robust sequence upper bounds] We replace the upper-bound \eqref{eq:opd} on sequence values in \texttt{OPD} by:
 \begin{equation}
@@
 \end{equation}
-where $R_t^m$ is the reward obtained at step $t$ by following $a$ with dynamics $f^m$.
 \end{definition}
@@
 \label{theorem:drop-regret}
-The \texttt{Robust-OPD} \eqref{eq:robust-b-values} enjoys the same regret bound as provided for \texttt{OPD} in \autoref{theorem:opd-regret}, with respect to the robust objective \eqref{eq:robust-objective-discrete}.
+The robust version of \texttt{OPD} \eqref{eq:robust-b-values} enjoys the same regret bound as provided for \texttt{OPD} in \autoref{theorem:opd-regret}, with respect to the robust objective \eqref{eq:robust-objective-discrete}.
 \end{theorem}
 
-Note that this theorem bounds the performance gap with respect to the number of node expansions, but each expansion still requires $M$ time more simulations in the multi-model setting than in the single-model setting.
+Note that this theorem bounds the performance gap with respect to the number of node expansions, but each expansion now requires $M$ times more simulations than in the single-model setting.
 The solution of the robust objective \eqref{eq:robust-objective-discrete} with discrete ambiguity $f\in\{f^m\}_{m\in[M]}$ can be recovered exactly, asymptotically when the planning budget $H$ goes to infinity.
@@
 
-The reward is non-smooth and encodes the task of reaching a goal position $x_g$ while avoiding collisions: $R(x) = \delta(x)/(1 + \|x - x_g\|_2)$  where $\delta(x)$ is $0$ whenever $x$ collides with an obstacle.
+The reward is non-smooth and encodes the task of reaching a goal state $x_g$ while avoiding collisions: $R(x) = \delta(x)/(1 + \|x - x_g\|_2)$  where $\delta(x)$ is $0$ whenever $x$ collides with an obstacle, $1$ otherwise.
 
@@
 
-In  \autoref{fig:regret} study the evolution of the agent conservativeness as they collect more data.
-Given a trajectory $x_0, R_0, x_1, R_1, \dots$, we compute the cumulative return $J_n(x_n) = \sum_{k\geq n} \gamma^k R_k$ at each state, and compare it to the optimal value $V(x_n)$, the return the agent would have got if it had acted optimally with respect to the oracle model.
+We run \autoref{alg:full} for 100 simulations, and compare in \autoref{tab:obstacle} its performances to that of a nominal agent that plans with the estimated dynamics $\theta_{[N],\lambda}$.
+We also study the evolution of the simple regret $V(x_n) - J_n(x_n)$ with respect to the number of samples $N$, where $J_n(x_n) = \sum_{i > n} \gamma^i R_i$ is the empirical return at state $x_n$ in a trajectory $x_0, R_0, x_1, R_1, \dots$, while $V(x_n)$ is the optimal value that the agent would get by acting optimally from $x_n$ with knowledge of the dynamics.
+The \autoref{fig:regret} shows that $\hat{V}^r - V$ decreases with $N$, as expected from \autoref{thm:control-error}.
 
@@
 
-We define $V = e^\transp P e$, which is non-negative definite provided that
+We define the Lyapunov function $V = e^\transp P e$, which is non-negative definite provided that
 $
@@
 	\label{eq:Rndn}
-	V^r - V_a^r &= V_{a^*}^r - V_a^r \\
-	&\leq B_{a^*}^r(t) - V_a^r \\
+	V^r - V_a^r &= V_{a^{\star}}^r - V_a^r \\
+	&\leq B_{a^{\star}}^r(t) - V_a^r \\
 	&\leq B_{a}^r(t) - U_a^r(t) \\

### 2020-02-05 main.tex
Experiments

@@
 \usepackage{bm}
+\def\sectionautorefname{Section}
 \input{mathdef.tex}
@@
 	\caption{The model estimation procedure. The size of the confidence region $C_{[N],\delta}$ shrinks with the number of samples $N$.}
+	\label{fig:estimation}
 \end{figure}
@@
 	\caption{The state prediction procedure. At each timestep (red to green), we bound the set of reachable states considering model uncertainty \eqref{eq:confidence}}
-	\label{fig:estimation-prediction}
+	\label{fig:prediction}
 \end{figure}
@@
 \begin{equation}
+\label{eq:inclusion-generic}
  x(t)\in X(t),\quad\forall t\geq t_N.
@@
 
-\begin{theorem}[Confidence ellipsoid, matrix version of \citealt{Abbasi2011}]
+\begin{theorem}[Confidence ellipsoid, a matricial version of \citealt{Abbasi2011}]
 \label{thm:confidence_ellipsoid}
@@
 
-To study the inclusion property \eqref{eq:inclusion-property}, we must start by choosing a set representation $X(t)$.
+To study the inclusion property \eqref{eq:inclusion-generic}, we must start by choosing a set representation $X(t)$.
 We consider interval prediction, rather than zonotope prediction for instance, for the sake of simplicity of implementation and computational efficiency.
@@
 
-\section{Control}
+\section{Robust Control}
 
@@
 
-This amounts to a change of reward function, except the worst case is assessed over the whole past trajectory being optimized, i.e. this pessimistic reward $\underline{R_n}$ is not \emph{markovian}.
+This amounts to a change of reward function, except the worst case is assessed over the whole past trajectory, which means that this pessimistic reward $\underline{R_n}$ is not \emph{markovian}.
 
@@
 \label{eq:robust-b-values}
-B_a^r(k)  \eqdef
-\begin{cases}
-\min_{m\in[M]} \sum_{n=0}^{h-1} \gamma^n R_n^m  + \frac{\gamma^h}{1-\gamma} &\text{if } a \text{ is a leaf;}\\
-\max_{b\in\mathcal{A}} B_{ab}^r(k) & \text{else.}
-\end{cases}
+B_a^r(k)  \eqdef \min_{m\in[M]} \sum_{n=0}^{h-1} \gamma^n R_n^m  + \frac{\gamma^h}{1-\gamma}
 \end{equation}
 \end{definition}
-An illustration of the computation of the robust b-values is presented in Figure \ref{fig:drop}. We analyse the sample complexity of the corresponding robust planning algorithm.
+An illustration of the computation of the robust b-values is presented in Figure \ref{fig:drop}.
+Note that it is not equivalent to solving each control problem independently and following the action with highest mininimal value, as we illustrate in \autoref{sec:min-max-order}.
+We analyse the sample complexity of the corresponding robust planning algorithm.
 
@@
 \paragraph{Obstacle avoidance with unknown friction}
-We first consider a simple illustrative example: the control of a 2D system with position $(p_x,p_y)$ and velocity $(v_x, v_y)$ moving by means of a force $(u_x, u_y)$ in an environment with unknown anisotropic friction.
+We first consider a simple illustrative example, shown in \autoref{fig:prediction}: the control of a 2D system with position $(p_x,p_y)$ and velocity $(v_x, v_y)$ moving by means of a force $(u_x, u_y)$ in an environment with unknown anisotropic friction.
 The dynamics are:
@@
 The reward is non-smooth and encodes the task of reaching a goal state $x_g$ while avoiding collisions: $R(x) = \delta(x)/(1 + \|x - x_g\|_2)$  where $\delta(x)$ is $0$ whenever $x$ collides with an obstacle, $1$ otherwise.
-
-\begin{table}[htbp]
-	\caption{Performances on the Obstacle task}
-	\label{tab:obstacle}
-	\centering
-	\begin{tabular}{lccc}
-		\toprule
-		\multirow{2}{*}{Agent} &
-		\multirow{2}{*}{Failures} &
-		\multicolumn{2}{c}{Return} \\
-		\cmidrule{3-4} & & min &
-		mean $\pm$ std \\
-		\midrule
-		Oracle & 0\% & {11.6} & {$14.2 \pm 1.3$} \\
-		\midrule
-		{Nominal} & {4\%} & {2.8} & \textbf{$\mathbf{13.8} \pm 2.0$} \\
-		Robust (ours) & \textbf{0\%} & \textbf{10.4} & {$13.0 \pm 1.5$} \\
-		\bottomrule
-	\end{tabular}
-\end{table}
+The actions $\cA$ are constant controls in the up, down, left and right directions.
+
+We run \autoref{alg:full} for 100 simulations, and compare in \autoref{tab:obstacle} its performances to that of the nominal agent, i.e.
+the non-robust adaptive control approach that plans with the estimated dynamics $\theta_{[N],\lambda}$.
+We observe that though the robust agent performs worse than the nominal agent on average, it manages to ensure safety and attains a better worst-case performance.
+We also study the evolution of the simple regret $V(x_n) - J_n(x_n)$ with respect to the number of samples $N$, where $J_n(x_n) = \sum_{i > n} \gamma^i R_i$ is the empirical return at state $x_n$ in a trajectory $x_0, R_0, x_1, R_1, \dots$, while $V(x_n)$ is the optimal value that the agent would get by acting optimally from $x_n$ with knowledge of the dynamics.
+The mean regret is shown in \autoref{fig:regret}, along with its 95\% confidence interval.
+We see that \autoref{alg:full} has a regret $\hat{V}^r - V$ decreasing at least polynomially with $N$, as expected from \autoref{thm:control-error}.
+\todo{The nominal gets better on average}.
 
@@
 
-We run \autoref{alg:full} for 100 simulations, and compare in \autoref{tab:obstacle} its performances to that of a nominal agent that plans with the estimated dynamics $\theta_{[N],\lambda}$.
-We also study the evolution of the simple regret $V(x_n) - J_n(x_n)$ with respect to the number of samples $N$, where $J_n(x_n) = \sum_{i > n} \gamma^i R_i$ is the empirical return at state $x_n$ in a trajectory $x_0, R_0, x_1, R_1, \dots$, while $V(x_n)$ is the optimal value that the agent would get by acting optimally from $x_n$ with knowledge of the dynamics.
-The \autoref{fig:regret} shows that $\hat{V}^r - V$ decreases with $N$, as expected from \autoref{thm:control-error}.
+\begin{table}[tbp]
+	\caption{Performances on the obstacle avoidance task}
+	\label{tab:obstacle}
+	\centering
+	\begin{tabular}{lccc}
+		\toprule
+		Agent &
+		failures &
+		min return &
+		mean return $\pm$ std  \\
+		\midrule
+		Oracle & 0\% & {11.6} & {$14.2 \pm 1.3$} \\
+		\midrule
+		{Nominal} & {4\%} & {2.8} & \textbf{$\mathbf{13.8} \pm 2.0$} \\
+		\autoref{alg:full} & \textbf{0\%} & \textbf{10.4} & {$13.0 \pm 1.5$} \\
+		\bottomrule
+	\end{tabular}
+\end{table}
 
 \paragraph{Behavioural planning for an autonomous vehicle}
-We consider the problem of safe decision-making for an autonomous vehicle.
-An autonomous vehicle with state $\chi_0\in\Real^4$ is driving on a highway populated with $V$ other vehicles with states $\chi_i\in\Real^4$, resulting in a joint traffic state $x = [\chi_0, \chi_1,\dots,\chi_V]^\top\in\Real^{4V+4}$.
-In order to plan a sequence of high-level decisions, the autonomous agent relies on both a model of its own dynamics $\chi_0 = f_0(\chi_0,u)$, but also a parametrized dynamical model for each observed agent to predict their future trajectory: \[\dot{\chi}_i=f_i(x,\theta_i),\;i\in[V],\] where $f_i$ are described below, $\chi_i\in\Real^4$ is the state of an agent, $\theta_i\in\Real^5$ is the corresponding vector of unknown parameters.
-Already, we can appreciate a first advantage of the structure imposed in \autoref{assumpt:structure}: the uncertainty space of $\theta$ is $\Real^{5V}$.
+We consider the \href{https://github.com/eleurent/highway-env}{highway-env} environment \citep{highway-env}, a  simulator for autonomous driving decision problems.
+An autonomous vehicle with state $\chi_0\in\Real^4$ is approaching an intersection among $V$ other vehicles with states $\chi_i\in\Real^4$, resulting in a joint traffic state $x = [\chi_0, \chi_1,\dots,\chi_V]^\top\in\Real^{4V+4}$.
+These other vehicles follow parametrized behaviours $\dot{\chi}_i=f_i(x,\theta_i)$ with unknown parameters $\theta_i\in\Real^5$.
+Here, we appreciate a first advantage of the structure imposed in \autoref{assumpt:structure}: the uncertainty space of $\theta$ is $\Real^{5V}$.
 In comparison, the traditional adaptive LQ setting where the whole state matrix $A$ is estimated would have resulted in a much larger parameter space $\theta\in\Real^{16V^2}$.
-%This allows to scale to larger systems: in our experiments, we used a state space of dimension $44$ ($V=10$) where \citep{Dean2018,abeille18a} only reported numerical experiments with states of dimensions 3 and 4, respectively.
-
-This system dynamics $f$ describes the couplings and interactions between vehicles, so that the autonomous agent can properly anticipate their reactions.
-It can only be expressed in the form \eqref{eq:dynamics} given the knowledge of the desired routes of each vehicle, with the features $\phi$ expressing deviations of the vehicles trajectories with respect to the lane centerline being followed.
-Since these are unknown in practice, we adopt the multi-model perspective of \autoref{sec:multi-model} and consider one model per possible route allocation for every observed vehicle before an intersection.
+%This allows to scale to larger systems: in our experiments, we used a state space of dimension $44$ ($V=10$) where e.g.
+\citep{Dean2018,abeille18a} reported numerical experiments with states of dimensions 3 and 4, respectively.
+This system dynamics $f$, which describes the couplings and interactions between vehicles, can only be expressed in the form of \autoref{assumpt:structure} given the knowledge of the desired routes of each vehicle.
+Then, the features $\phi$ express deviations of the vehicles trajectories to the centerline of the followed lane.
+Since these intentions are unknown to the agent, we adopt the multi-model perspective of \autoref{sec:multi-model} and consider one model per possible route for every observed vehicle before an intersection.
+Again, we compare \autoref{alg:full} to a nominal agent planning with the estimated parameter $\theta_{[N],\lambda}$, with two different modelling assumptions: we assume that Nominal 1 has access to the true followed route for each vehicle, while Nominal 2 does not and picks the model with minimal prediction error at the planning time.
+There performances are compared in \autoref{tab:driving}.
+Again, the robust approach is less efficient on average than planning with the nominal model, but it does better in terms of worst-case performance and manages to avoid collisions, contrary to the nominal baselines that suffer from model bias.
 
@@
 	\includegraphics[width=0.8\linewidth]{img/highway-small}
-	\caption{The intersection crossing task.}
+	\caption{The intersection crossing task. We show the trajectory intervals corresponding to behavioural uncertainty for each observed vehicle, and the multi-model assumption over the followed route.}
 \end{figure}
 
-\begin{table}[htbp]
-	\caption{Performances on the Driving task}
+\begin{table}[tbp]
+	\caption{Performances on the driving task}
 	\label{tab:driving}
@@
 		\toprule
-		\multirow{2}{*}{Agent} &
-		\multirow{2}{*}{Failures} &
-		\multicolumn{2}{c}{Return} \\
-		\cmidrule{3-4} && min &
-		mean $\pm$ std  \\
+		Agent &
+		failures &
+        min return &
+		mean return $\pm$ std  \\
 		\midrule
@@
 		\midrule
-		{Nominal B} & 4\% & {5.2} & $\mathbf{7.3} \pm 1.5$ \\
-		{Nominal R} & 33\% & {3.5} & $6.4 \pm 0.26$ \\
-		Robust (ours) & \textbf{0\%} & \textbf{6.8} & $7.1 \pm 0.29$ \\
+		{Nominal 1} & 4\% & {5.2} & $\mathbf{7.3} \pm 1.5$ \\
+		{Nominal 2} & 33\% & {3.5} & $6.4 \pm 0.26$ \\
+		\autoref{alg:full} & \textbf{0\%} & \textbf{6.8} & $7.1 \pm 0.29$ \\
 		\bottomrule
@@
 \begin{lemma}[Robust values ordering]
-	In addition to the robust B-value defined in \eqref{eq:robust-b-values}, we also define the robust value of a sequence of actions $a$
+	In addition to the robust B-value defined in \eqref{eq:robust-b-values}, that we extend to inner nodes	
+	\begin{equation}
+	\label{eq:br}
+	B_a^r(k)  \eqdef
+	\begin{cases}
+	\min_{m\in[M]} \sum_{n=0}^{h-1} \gamma^n R_n^m  + \frac{\gamma^h}{1-\gamma}&\text{if } a \text{ is a leaf;}\\
+	\max_{b\in\mathcal{A}} B_{ab}^r(k) & \text{else.}
+	\end{cases},
+	\end{equation}
+
+	we also define the robust value of a sequence of actions $a$
 	\begin{equation}
@@
 	\end{cases}
-	\end{equation}.
+	\end{equation}
 
@@
 
-	Finally, \eqref{eq:urvrbr} is extended to the rest of $\mathcal{T}_n$ by recursive application of \eqref{eq:max_vr}, \eqref{eq:ur} and \eqref{eq:robust-b-values}.
+	Finally, \eqref{eq:urvrbr} is extended to the rest of $\mathcal{T}_n$ by recursive application of \eqref{eq:max_vr}, \eqref{eq:ur} and \eqref{eq:br}.
 \end{proof}
@@
 \end{proof}
+
+\section{On the ordering of min and max}
+	\label{sec:min-max-order}
+
+	In the definition of $B_{i}^{r}(n)$ and $U_{i}^{r}(n)$ it is essential that the minimum among the models is only taken at the end of trajectories, in the same way as for the robust objective \eqref{eq:robust-objective-discrete} in which the worst-case dynamics is only determined after the action sequence has been fully specified.
+Assume that $U_{a}^{r}(n)$ is instead naively defined as:
+
+	\[
+	U_{a}^{r}(n)=\min_{m\in[1,M]}U_{a}^{m}(n),
+	\]
+
+	This would not recover the robust policy, as we show in \autoref{fig:min-max-order} with a simple counter-example.
+	\begin{figure}[htp]
+		\centering
+		\includegraphics[width=\linewidth]{img/min-max-order}
+		\caption{From left to right: two simple models and corresponding u-values with optimal sequences in blue; the naive version of the robust values returns sub-optimal paths in red; our robust U-value properly recovers the robust policy in green.}
+		\label{fig:min-max-order}
+	\end{figure}
 

### 2020-02-05 main.tex
Update intro

@@
 
-Despite the recent successes of Reinforcement learning in cracking many hard problems, this tool has hardly been applied in real industrial issues.
-This could be attributed to two undesirable properties which limit its practical applications: the dependence on a tremendous amount of interaction data that cannot always be simulated, and the reliance on trial-and-error and random exploration.
+Despite the recent successes of Reinforcement Learning in cracking many hard problems \citep[e.g.][]{mnih2015humanlevel,Silver1140}, this tool has hardly been applied in real industrial issues.
+This could be attributed to two undesirable properties which limit its practical applications.
+First, it depends on a tremendous amount of interaction data that cannot always be simulated.
+This issue is alleviated by model-based methods -- which we consider in this work -- that benefit from better sample efficiencies by exploiting a richer data stream than their model-free counterparts.
+Second, it relies on trial-and-error and random exploration.
 In this paper, we consider the problem of controlling an unknown linear system $x(t)$ so as to maximise an \emph{arbitrary} bounded reward function $R$, in a critical setting where mistakes are costly and must be avoided at all time.
-This choice of rich reward space is crucial to have sufficient flexibility to model non-convex and non-smooth functions that naturally arise in many practical problems such as combinatorial optimisation, obstacle avoidance, etc., while quadratic costs are only suited for the tracking of a reference trajectory known a priori.
+This choice of rich reward space is crucial to have sufficient flexibility to model non-convex and non-smooth functions that naturally arise in many practical problems involving combinatorial optimisation, branching decisions, etc., while quadratic costs are mostly suited for the tracking of a reference trajectory already known a priori.
 
@@
 In this work, we assume that the system dynamics are partially known, in the form of a parametrized dynamical system with unknown parameters.
-We argue that this assumption is realistic given that most industrial applications to date have been relying on physical models to describe their processes and engineered controllers to operate them, rather than machine learning.
+We argue that this assumption is realistic given that most industrial applications to date have been relying on physical models to describe their processes and well-engineered controllers to operate them, rather than machine learning.
 Our framework relaxes this modelling effort by allowing some structured uncertainty around the nominal model.
@@
 Most model-based reinforcement learning algorithms only rely on the estimated dynamics to derive the corresponding optimal controller, but these methods often suffer from \emph{model bias}: they ignore the error that exists between the learned and true dynamics, which can dramatically degrade the control performances \citep{Schneider1997}.
-In particular, the framework of maximising an objective under constraints naturally pushes systems to operate in the vicinity of constraint saturation, which makes it more prone to failure when the model is imperfect.
+This is all the more relevant when maximising an objective under constraints --or penalties-- which naturally pushes the systems to operate in the vicinity of constraint saturation and makes it prone to failures.
 
@@
 Minimax problem are hard to solve, and all the more in our setting where the reward function $R$ is generic.
-In particular, this excludes a number of tools from the robust synthesis literature, such as $\cH_\infty$ \todo{(ref needed)} control or system-level synthesis \todo{(ref needed)}.
+In particular, this excludes a number of tools from the robust synthesis literature, such as $\cH_\infty$ \citep[see, e.g.][]{Basar1996} control or system-level synthesis \citep{Dean2017,Dean2018}.
 We turn instead to more general planning algorithms.
 The continuous state space prevents us from using dynamic programming techniques, so we consider tree-based planning instead.
-Though some work address continuous actions \todo{ref needed}, we resort to a first approximation and discretise the decision space by adopting a hierarchical control architecture.
-We  formulate the problem high-level decision of selecting a low-level controller among a finite basis \todo{(ref from temporal abstraction)}.
-For instance, this could amount to choosing a short-term goal to follow, or a skill to execute such as a driving maneuver.
-The passage from continuous to discrete optimization induces a suboptimality, but it can be mitigated by diversifying the controller basis.
-However, tree-based planning algorithms are only designed for a single known generative model instead of an entire confidence region for the system dynamics.
+Though there exist work addressing continuous actions \citep{Busoniu2018,Weinstein2012}, we resort to a first approximation and discretise the decision space by adopting a hierarchical control architecture.
+At each time, the agent can select low-level controller to execute among a finite basis, e.g.
+choose a short-term goal to reach or a skill to execute such as a driving maneuver.
+The discretisation induces a suboptimality, but it can be mitigated by diversifying the controller basis.
+Tree-based planning algorithms are relevant in this context of discrete action, but are only designed for a single known generative model instead of an entire confidence region for the system dynamics.
 Hence, we adapt them to the robust framework by following a two-steps procedure: we first predict a set of states that can be reached under a planned control sequence with respect to all possible dynamics.
 This reachability set is used to provide a conservative pessimistic reward to the planning algorithm.
-The next section aims to clarify and formalize these ideas.
+The next subsection aims to clarify and formalize these ideas, and state our contributions.
 
@@
 We consider a linear system with state $x\in\Real^p$, acted on by controls $u\in\Real^q$ and perturbations $\omega\in\Real^r$, and following a dynamics in the form:
-
 \begin{equation}
@@
 
-We also have access to the observation of $x(t)$ and to a noisy measurement of $\dot{x}(t)$ in the form $\dot{x}(t) + C\nu(t)$, where $\nu(t)\in\Real^s$ is a measurement noise and $C\in\Real^{p\times s}$ is known.
+We also have access to the observation of $x(t)$ and to a noisy measurement of $\dot{x}(t)$ in the form $y(t)=\dot{x}(t) + C\nu(t)$, where $\nu(t)\in\Real^s$ is a measurement noise and $C\in\Real^{p\times s}$ is known.
 Assumptions over the disturbance $\omega$ and noise $\nu$ will be detailed further, and we denote $\eta(t) = C\nu(t) + D\omega(t)$.
@@
 \end{align}
-Our first contribution is to extend the work of \citet{Abbasi2011} that provide a confidence ellipsoid for the regularised least-square estimator to our setting of vector observations and matrix features, instead of scalar observations and vector features.
+Such regions are illustrated in \autoref{fig:estimation}.
+Our first contribution extends the work of \citet{Abbasi2011} who provide a confidence ellipsoid for the regularised least-square estimator to our setting of feature matrices, rather than feature vectors.
 
@@
 
-Minimax problems such as \eqref{eq:robust-control} are notoriously difficult to solve even in cases such as linear-quadratic systems (LQ) where the reward $R$ has a simple form.
-Here with an arbitrary function $R$, we cannot hope to derive a solution in explicit form.
+Maximin problems such as \eqref{eq:robust-control} are notoriously difficult to solve even in cases such as linear-quadratic systems (LQ) where the reward $R$ has a simple form.
+With arbitrary functions $R$, we cannot hope to derive a solution in explicit form.
 Our second contribution is to propose to solve \eqref{eq:robust-control} numerically by adopting a \emph{predict-then-optimise} scheme.
-Thus, in \autoref{sec:prediction}, we aim to derive a \emph{set predictor} $X(t)$ for the system \eqref{eq:dynamics}, which takes the information on the observed current state ${x}_N$, a confidence region $\cC_\delta$ verifying \eqref{eq:confidence}, a planned control sequence $\bu$ and some admissible bounds on the perturbation $[\underline{\omega}(t),\overline{\omega}(t)]$; and produces predictions of sets $X(t)$ that verify the inclusion property:
+In \autoref{sec:prediction}, we aim to derive a \emph{set predictor} $X(t)$ for the system \eqref{eq:dynamics}, illustrated in \autoref{fig:prediction}.
+This predictor takes the information on the observed current state ${x}_N$, a confidence region $\cC_\delta$ verifying \eqref{eq:confidence}, a planned control sequence $\bu$ and some admissible bounds on the perturbation $[\underline{\omega}(t),\overline{\omega}(t)]$; and outputs a set $X(t)$ that must verify the inclusion property:
 \begin{equation}
@@
 
-This property is illustrated in \autoref{fig:estimation-prediction}. We leverage recent results from the uncertain system simulation literature to efficiently compute such a predictor.
+We leverage recent results from the uncertain system simulation literature to efficiently compute such a predictor.
 
@@
 Since $R$ is generic, potentially non-smooth and non-convex, solving the optimal -- not to mention the robust -- control objective in the original continuous control space $(\Real^q)^\Natural$ is intractable.
-In this work, we choose to approximate the solution by turning the continuous optimisation problem \eqref{eq:robust-control} into a discrete one, by optimising over a finite set of \emph{actions} $\cA$.
+In this work, we choose to approximate the solution by turning the continuous optimisation problem \eqref{eq:robust-control} into a discrete one and optimising over a finite set of \emph{actions} $\cA$.
 Each action $a\in\cA$ corresponds to the selection of a low-level controller $\pi_a$, that we take affine:
-\[u(t) = \pi_a(x(t)) \eqdef -K_a x(t) + u_a\]
-
-The robust objective we consider becomes 
+\[u(t) = \pi_a(x(t)) \eqdef -K_a x(t) + u_a.\]
+For instance, a controller tracking a relevant subgoal $x_g$ can be encoded as $\pi_g = K(x_g - x)$.
+
+The robust objective \eqref{eq:robust-control} becomes 
 \begin{equation}
 \label{eq:robust-control-disc}
-\sup_{\ba\in{\cA}^\Natural} \underbrace{\inf_{\substack{A(\theta) \in \cC_{[N],\delta} \\ \bom\in[\underline{\bom},\overline{\bom}]^\Natural}} \left[\sum_{n=N+1}^\infty \gamma^n R(x_n(\ba,\bom))\right]}_{V^r(\ba)}
+\sup_{\ba\in{\cA}^\Natural} \underbrace{\inf_{\substack{A(\theta) \in \cC_{[N],\delta} \\ \bom\in[\underline{\bom},\overline{\bom}]^\Natural}} \left[\sum_{n=N+1}^\infty \gamma^n R(x_n(\ba,\bom))\right]}_{V^r(\ba)},
 \end{equation}
@@
 In \autoref{sec:control}, facing an optimisation problem with continuous states and discrete actions, we turn to the literature of tree-based planning.
-Our third contribution proposes to approximate the true robust objective ${V}^r$ by an easily-evaluable surrogate $\hat{V}^r$ that exploits the set predictor to define a pessimistic reward, used to evaluate sequences of actions in a tree-based planning algorithm.
+Our third contribution proposes to approximate the true robust objective ${V}^r$ by an easily-evaluable surrogate $\hat{V}^r$ that exploits the set predictor \eqref{eq:inclusion-generic} to define a pessimistic reward, used to evaluate sequences of actions in a tree-based planning algorithm.
 
@@
 
-\paragraph{Model selection} In \autoref{sec:multi-model}, we question our modelling assumption and relax them to a more flexible setting.
-
-\paragraph{Experiments} We illustrate the \autoref{alg:full} in a simple 2D example, before moving to a more realistic simulation of an autonomous driving application.
-
-% \begin{algorithm}[tb]
-%   \caption{Robust Estimation, Prediction and Control (v1)}
-%   \label{alg:full}
-% \begin{algorithmic}
-%   \STATE {\bfseries Input:} confidence level $\delta$
-%   \FOR{$N = 1,2,3,\dots$} 
-%   \STATE Compute the dynamics confidence region $\cC_{[N],\delta}$ with \textsc{Model Estimation} \eqref{eq:generic-polytope} on $\cD_{[N]}$.
-%   \FOR{planning steps $k\in[K]$}
-%   \STATE Get the tree node $\bu_k$ to expand with \textsc{Pessimistic Planning}  \eqref{eq:opd} using $\underline{R_n}$ over $[\underline{x}_{n}, \overline{x}_{n}]$. \COMMENT{Selection}
-%   \STATE For each action, simulate the child transition $[\underline{x}_{n+1}, \overline{x}_{n+1}]$ with \textsc{Interval Prediction} \eqref{eq:interval-predictor} using $\cC_{[N],\delta}$.
-\COMMENT{Expansion}
-%   \ENDFOR
-%   \STATE Execute the first recommended control $u_N$, and add the observed transition $(x_N, u_N, \dot{x}_N)$ to $\cD_{[N+1]}$.
-%   \ENDFOR
-% \end{algorithmic}
-% \end{algorithm}
+\paragraph{Model selection} In \autoref{sec:multi-model}, our forth contribution extends our framework to consider multiple modelling assumptions, while ensuring tight uncertainty estimation through data-driven model rejection, and safety via robust model-selection during planning.
+
+\paragraph{Experiments} Finally, our last contribution is to demonstrate the benefits of our proposed \autoref{alg:full} in two numerical experiments, a simple illustrative example and a more challenging simulation for an autonomous driving application.
 
@@
 	\begin{algorithmic}
-		\STATE {\bfseries Input:} confidence level $\delta$
-		\FOR{$N = 1,2,3,\dots$} 
+		\STATE {\bfseries Input:} confidence level $\delta$, structure $A,\phi$, reward $R$
+		\STATE $\cD_{[0]}\gets\emptyset,\, \ba_1\gets\emptyset$
+		\FOR{$N = 0,1,2,\dots$} 
 		\STATE $\cC_{[N],\delta} \gets$\textsc{Model Estimation}$(\cD_{[N]})$. \eqref{eq:polytope}
@@
 		\STATE $[\underline{x}_{n+1}, \overline{x}_{n+1}]\gets$ \textsc{Interval Prediction}(
-		\STATE $\qquad\qquad\qquad\qquad\cC_{[N],\delta}, a_kb$). \eqref{eq:interval-predictor}
+		\STATE $\qquad\qquad\qquad\qquad\cC_{[N],\delta}, \ba_kb$). \eqref{eq:interval-predictor}
 		\ENDFOR
-		\STATE $a_{k+1}$ $\gets$\textsc{Pessimistic Planning}$($
+		\STATE $\ba_{k+1}$ $\gets$\textsc{Pessimistic Planning}$($
 		\STATE$\qquad\qquad\underline{R_{n+1}}([\underline{x}_{n+1}, \overline{x}_{n+1}]))$.  \eqref{eq:opd}
@@
 \label{assumpt:structure}
-There exists a known feature tensor $\phi\in \Real^{d \times p \times p}$ such that for all $\theta\in\Theta$:
+There exists a known feature tensor $\phi\in \Real^{d \times p \times p}$ such that for all $\theta\in\Theta$,
 \begin{equation}
     A(\theta) = A + %\theta^\transp \phi \eqdef A + 
-    \sum_{i=1}^d \theta_i\phi_i
+    \sum_{i=1}^d \theta_i\phi_i,
 \end{equation}
@@
 
-We also assume to know an upper-bound $S$ over $\|\theta\|_\infty$.
+We also assume to know a bound $S$ such that $\theta\in[-S,S]^d$.
 \end{assumption}
 
-For readability, we denote the noisy measurement of $\dot{x}$ as:
+We abuse notations and include additional known terms in the measurement $y(t)$ as:
 \begin{equation}
 \label{eq:measurement}
-    y(t) = \dot{x}(t) + C\nu(t) - A x(t) - Bu(t)
-\end{equation}
-which is possible since the nominal dynamics $A$, the state $x(t)$ and the control $u(t)$ are known.
+    y(t) = \dot{x}(t) + C\nu(t) - A x(t) - Bu(t).
+\end{equation}
 Thus, we obtain the system
 \[
-y_n = \Phi_n\theta + \eta_n
+y_n = \Phi_n\theta + \eta_n.
 \]
@@
     \label{eq:regression_min}
-    \min_{\theta\in\Real^d} \sum_{n=1}^N \|y_n -\Phi_n\theta\|_{\Sigma_p^{-1}}^2 + \lambda\|\theta\|_{}^2
+    \min_{\theta\in\Real^d} \sum_{n=1}^N \|y_n -\Phi_n\theta\|_{\Sigma_p^{-1}}^2 + \lambda\|\theta\|_{}^2.
 \end{equation}
@@
     \label{eq:vector_rls}
-    \theta_{N,\lambda} = G_{N, \lambda}^{-1} \sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1} y_n
+    \theta_{N,\lambda} = G_{N, \lambda}^{-1} \sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1} y_n,
 \end{equation}
@@
 \begin{align}
-    \theta_{N,\lambda} - \theta = G_{N, \lambda}^{-1}\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\eta_n - \lambda G_{N, \lambda}^{-1}\theta 
+    \theta_{N,\lambda} - \theta = G_{N, \lambda}^{-1}\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\eta_n - \lambda G_{N, \lambda}^{-1}\theta.
 \end{align}
@@
 This yields directly that $a = i_0$ where $i$ is some node of maximal depth $d_n$ expanded at round $t\leq n$, which by selection rule verifies $B_a^r(t) = B_i^r(t) = \max_{x\in\mathcal{A}} B_x^r(t)$ and:
-	\begin{align}
+	\begin{align*}
 	\label{eq:Rndn}
-	V^r - V_a^r &= V_{a^{\star}}^r - V_a^r \\
-	&\leq B_{a^{\star}}^r(t) - V_a^r \\
-	&\leq B_{a}^r(t) - U_a^r(t) \\
+	V^r - V_a^r = V_{a^{\star}}^r - V_a^r  \leq B_{a^{\star}}^r(t) - V_a^r &\leq B_{a}^r(t) - U_a^r(t) \\
 	&= B_{i}^r(t) - U_i^r(t) \\
 	&= \frac{\gamma^{d_n}}{1-\gamma}.
-	\end{align}
+	\end{align*}
 
@@
 		\item If $\kappa > 1$, then $n \leq n_0 + c'\kappa^{d_0+1}\frac{\kappa^{d_n-d_0}-1}{\kappa-1}$ and thus $d_n \geq d_0 + \log_\kappa \frac{(n-n_0)(\kappa - 1)}{c'\kappa^{d_0+1}}$.
-		We conclude from \eqref{eq:Rndn} that $\mathcal{R}_n \leq \frac{\gamma^{d_n}}{1-\gamma} = \frac{1}{1-\gamma} \left( \frac{(n-n_0)(\kappa - 1)}{c'\kappa^{d_0+1}} \right)^\frac{\log \gamma}{\log \kappa} = O\left(n^{-\frac{\log 1/\gamma}{\log \kappa}}\right)$.
-
-		\item If $\kappa = 1$, then $n \leq n_0 + c'(d_n-d_0)$, hence from \eqref{eq:Rndn} we have $\mathcal{R}_n = O\left(\gamma^{nc'}\right)$.
+		We conclude that $\mathcal{R}_n \leq \frac{\gamma^{d_n}}{1-\gamma} = \frac{1}{1-\gamma} \left( \frac{(n-n_0)(\kappa - 1)}{c'\kappa^{d_0+1}} \right)^\frac{\log \gamma}{\log \kappa} = O\left(n^{-\frac{\log 1/\gamma}{\log \kappa}}\right)$.
+
+		\item If $\kappa = 1$, then $n \leq n_0 + c'(d_n-d_0)$, hence we have $\mathcal{R}_n = O\left(\gamma^{nc'}\right)$.
 	\end{itemize}

### 2020-02-05 main.tex
Remarks from Denis

@@
 
-\paragraph{Notations}
+\paragraph{Notation}
 
@@
 We use bold symbols to denote temporal sequences $\bz = (z_n)_{n>N}$.
-We denote $z^+ = \max(z,0)$ and $z^- = z^+-z$, and $[n]$ denotes the interval $\{1,2,\dots, n\}$.
+We denote $z^+ = \max(z,0)$, $z^- = z^+-z$, $|z| = z^++z^-$ and $[n]=\{1,2,\dots, n\}$.
 
@@
 \end{equation}
-The dynamics $A(\theta)\in\Real^{p\times p}$  depends on some parameter $\theta$ that belongs to a compact set $\Theta \subset \Real^d$.
+ It is assumed that the parameter vector $\theta$ in the state matrix $A(\theta)\in\Real^{p\times p}$ belongs to a compact set $\Theta \subset \Real^d$.
 The control matrix $B\in\Real^{p\times q}$ and disturbance matrix $D\in\Real^{p\times r}$ are known.
 
-We also have access to the observation of $x(t)$ and to a noisy measurement of $\dot{x}(t)$ in the form $y(t)=\dot{x}(t) + C\nu(t)$, where $\nu(t)\in\Real^s$ is a measurement noise and $C\in\Real^{p\times s}$ is known.
+We also assume having access to the observation of $x(t)$ and to a noisy measurement of $\dot{x}(t)$ in the form $y(t)=\dot{x}(t) + C\nu(t)$, where $\nu(t)\in\Real^s$ is a measurement noise and $C\in\Real^{p\times s}$ is known.
 Assumptions over the disturbance $\omega$ and noise $\nu$ will be detailed further, and we denote $\eta(t) = C\nu(t) + D\omega(t)$.
@@
 
-In \autoref{sec:estimation}, having observed history of transitions $\cD_{[N]} = \{(x_n, y_n)\}_{n\in[N]}$, and given a confidence level $\delta\in(0, 1)$, our goal is to find a confidence region $\cC_{[N],\delta}$ as tight as possible and such that it holds that:
+In \autoref{sec:estimation}, having observed history of transitions $\cD_{[N]} = \{(x_n, y_n,u_n)\}_{n\in[N]}$, and given a confidence level $\delta\in(0, 1)$, our goal is to find a confidence region $\cC_{[N],\delta} \subset \Theta$ as tight as possible and such that it holds:
 \begin{align}
@@
 \end{equation}
-The rest of the paper tackles the optimisation of \eqref{eq:robust-control}.
+where $\gamma\in(0,1)$ is a discount factor. The rest of the paper tackles the optimisation of \eqref{eq:robust-control}.
 
@@
 
-Maximin problems such as \eqref{eq:robust-control} are notoriously difficult to solve even in cases such as linear-quadratic systems (LQ) where the reward $R$ has a simple form.
+Maximin problems such as \eqref{eq:robust-control} are notoriously difficult to solve even in cases such where the reward $R$ has a simple form.
 With arbitrary functions $R$, we cannot hope to derive a solution in explicit form.
@@
 Since $R$ is generic, potentially non-smooth and non-convex, solving the optimal -- not to mention the robust -- control objective in the original continuous control space $(\Real^q)^\Natural$ is intractable.
-In this work, we choose to approximate the solution by turning the continuous optimisation problem \eqref{eq:robust-control} into a discrete one and optimising over a finite set of \emph{actions} $\cA$.
+In this work, we choose to approximate the solution of \eqref{eq:robust-control} by optimising over a finite set of \emph{actions} $\cA$.
 Each action $a\in\cA$ corresponds to the selection of a low-level controller $\pi_a$, that we take affine:
 \[u(t) = \pi_a(x(t)) \eqdef -K_a x(t) + u_a.\]
-For instance, a controller tracking a relevant subgoal $x_g$ can be encoded as $\pi_g = K(x_g - x)$.
-
-The robust objective \eqref{eq:robust-control} becomes 
+For instance, a tracking a subgoal $x_g$ can be achieved with $\pi_g = K(x_g - x)$. The robust objective \eqref{eq:robust-control} becomes 
 \begin{equation}
@@
 \end{equation}
-where $x_n(\ba, \bom)$ is obtained by integrating \eqref{eq:dynamics} with $u_n = \pi_{a_n}(x_n)$.
-
-In \autoref{sec:control}, facing an optimisation problem with continuous states and discrete actions, we turn to the literature of tree-based planning.
-Our third contribution proposes to approximate the true robust objective ${V}^r$ by an easily-evaluable surrogate $\hat{V}^r$ that exploits the set predictor \eqref{eq:inclusion-generic} to define a pessimistic reward, used to evaluate sequences of actions in a tree-based planning algorithm.
+where $x_n(\ba, \bom)$ stems from \eqref{eq:dynamics} with $u_n = \pi_{a_n}(x_n)$.
+
+In \autoref{sec:control}, facing a sequential decision problem with continuous states and discrete actions, we turn to the literature of tree-based planning algorithms.
+Our third contribution adapts them to the robust objective \eqref{eq:robust-control-disc} by approximating it with an easily-evaluable surrogate $\hat{V}^r$ that exploits the set predictor \eqref{eq:inclusion-generic} to define a pessimistic reward.
+In our main result, we show that the best surrogate performance achieved during planning is guaranteed to be attained on the true system, and we provide an upper bound for the approximation gap and simple regret of our framework.
 
@@
 
-\paragraph{Experiments} Finally, our last contribution is to demonstrate the benefits of our proposed \autoref{alg:full} in two numerical experiments, a simple illustrative example and a more challenging simulation for an autonomous driving application.
+\paragraph{Experiments} Finally, our last contribution demonstrates the benefits of our proposed \autoref{alg:full} in two numerical experiments, a simple illustrative example and a more challenging simulation for an autonomous driving application.
 
@@
 
-\paragraph{Linear-quadratic systems} There is a rich body of literature dedicated to the study of LQ systems, and we focus on those providing non-asymptotic results when the system parameters $A, B$ are unknown.
+\paragraph{Linear-quadratic problems} There is a rich body of literature dedicated to the study of LQ systems, and we focus on those providing non-asymptotic results when the system parameters $A, B$ are unknown.
 In their seminal work \citet{abbasi-yadkori11a}, consider the problem of cumulative regret minimisation.
 They follow the \emph{Optimism in the Face of Uncertainty} paradigm from the multi-armed bandit literature, that consists in selecting an optimistic system within a high-confidence region while enforcing a controllability constraint, and computing the corresponding optimal control in closed-form by solving a Riccati equation.
-They show that this procedures achieves a $\tilde{\cO}\left(T^{1/2}\right)$ cumulative regret.
+They show that this procedures achieves a $\tilde{\cO}\left(N^{1/2}\right)$ cumulative regret.
 \citet{abeille18a} provide the same result by applying Thomson Sampling rather of optimism to select a dynamical model, and rejection sampling to enforce the controllability constraint.
-These methods aim at regret minimization and explore actively to quickly reduce uncertainty, through information-seeking behaviours.
-Other work use noise injection for exploration such as \citep{Dean2017} or \citep{Dean2018}.
+These methods aim at regret minimization to quickly reduce uncertainty, through information-seeking behaviours.
+Other works use noise injection for exploration such as \citep{Dean2017} or \citep{Dean2018}.
 However, being optimistic and minimising a cumulative regret does not fit a critical setting, where ensuring safety is the first criteria requires instead to consider the pessimistic outcomes.
@@
 \paragraph{Robust planning}
-Robust optimization has also been studied in the context of finite Markov Decision Processes with uncertain parameters by \citet{Iyengar2005}, \citet{Nilim2005} and \citet{Wiesemann2013}.
+Robust optimization with generic costs has also been studied in the context of finite Markov Decision Processes with uncertain parameters by \citet{Iyengar2005}, \citet{Nilim2005} and \citet{Wiesemann2013}.
 They showed that the main results of Dynamic Programming can be extended to their robust counterparts only when the dynamics ambiguity set verifies a certain rectangularity property, that amounts to an independence assumption between the uncertainty sets of each transition and is related to time-varying uncertainty.
@@
 \end{equation}
-where $\phi_i\in\Real^{p\times p}$ for all $i\in[d]$. For all $n$, we denote $\Phi_n = [\phi_1 x_n \dots \phi_d x_n]\in\Real^{p\times d}$.
+where $A,\phi_1,\dots,\phi_d\in\Real^{p\times p}$ are known. For all $n$, we denote $\Phi_n = [\phi_1 x_n \dots \phi_d x_n]\in\Real^{p\times d}$.
 
@@
 
-We abuse notations and include additional known terms in the measurement $y(t)$ as:
+We abuse notations and include additional known terms in the measurement signal $y(t)$:
 \begin{equation}
@@
 \end{equation}
-Thus, we obtain the system
+Thus, we obtain a linear regression system
 \[
@@
 
-\paragraph{Regularised least square} We consider the weighted $L_2$-regularised regression problem with weights  $\Sigma_p\in\Real^{p\times p}$ and parameter $\lambda\in\Real^+_*$:
+\paragraph{Regularised least square} To derive an estimate on $\theta$, we consider the weighted $L_2$-regularised regression problem with weights  $\Sigma_p\in\Real^{p\times p}$ and parameter $\lambda\in\Real^+_*$:
 
@@
 
-By Hölder inequality, we obtain a confidence region $\cC_{[N],\delta}$ defined by a $L_1$-ball, i.e. a polytope with $2d$ vertices:
+This is a deterministic assumption, then by Hölder inequality a confidence region $\cC_{[N],0}$ can be derived based on a $L_1$-ball estimate of $\theta$ at time $N$, i.e.
+a polytope with $2d$ vertices:
 \begin{equation}
@@
 For instance, when the noise $\eta$ is Gaussian, then $\|\eta\|_\infty=+\infty$ which makes \eqref{eq:bounded-noise-polytope} uninformative.
-Then, a weaker assumption can be made.
+Then, another probabilistic assumption can be made.
 
@@
 \begin{equation*}
-    \forall u\in\Real^k,\, \expectedvalue \left[ \exp{\left( u^\transp \eta(t)\right)}\right] \leq \exp{\left( \frac{1}{2} u^\transp \Sigma_p u\right)}
-\end{equation*}
-For instance, this is the case when $\nu$ and $\omega$ are Gaussian noises with respective covariance matrices $\Sigma_r$ and $\Sigma_s$, with $\Sigma_p \eqdef C\Sigma_r C^\transp + D\Sigma_s D^\transp$.
-Also note that \autoref{assumpt:bounded-noise} implies that $\eta$ is $\|\eta\|_\infty I_p$-sub-Gaussian, and is therefore a stronger assumption.
+    \forall u\in\Real^p,\, \expectedvalue \left[ \exp{\left( u^\transp \eta(t)\right)}\right] \leq \exp{\left( \frac{1}{2} u^\transp \Sigma_p u\right)}
+\end{equation*}
 \end{assumption}
+For instance, it is the case when $\nu$ and $\omega$ are Gaussian noises with covariance matrices $\Sigma_r$ and $\Sigma_s$, with $\Sigma_p \eqdef C\Sigma_r C^\transp + D\Sigma_s D^\transp$.
+Note that \autoref{assumpt:bounded-noise} implies that $\eta$ is sub-Gaussian with covariance proxy $\Sigma_p=\|\eta\|_\infty I_p$.
 
@@
     \label{eq:polytope}
-     &\cC_{[N],\delta} = \left\{ A_{0}+\sum_{i=1}^{2^d}\lambda_{i}\Delta A_{i}: \lambda\in[0, 1]^{2^d},  \sum_{i=1}^{2^d}\lambda_{i}=1\right\},\\
-     &A_0 = A + \theta_{N,\lambda}^\transp\phi, \quad\Delta A_{i} = h_i \sqrt{\frac{\beta_N(\delta)}{\lambda_{\max}(G_{N,\lambda})}}
+     &\cC_{[N],\delta} = \left\{ A_{0}+\sum_{i=1}^{2^d}\alpha_{i}\Delta A_{i}: \alpha\in[0, 1]^{2^d},  \sum_{i=1}^{2^d}\alpha_{i}=1\right\},\\
+     &A_{0,N} = A + \theta_{N,\lambda}^\transp\phi, \quad\Delta A_{i} = \todo{h_i} \sqrt{\frac{\beta_N(\delta)}{\lambda_{\max}(G_{N,\lambda})}}
 \end{align}
@@
  &  &+Bu(t) + D^{+}\overline{\omega}(t)-D^{-}\underline{\omega}(t),\nonumber \\
- &  & \underline{x}(t_N)=\underline{x}_{t_N},\;\overline{x}(t_N)=\overline{x}_{t_N},\nonumber 
+ &  & \underline{x}(t_N)=\overline{x}(t_N)={x}(t_N),\nonumber 
 \end{eqnarray}
-ensures the inclusion property \eqref{eq:inclusion-property}.
+ensures the inclusion property \eqref{eq:inclusion-property} with confidence level $\delta$.
 \end{proposition}
@@
 \label{assumpt:metzler}
-There exists an orthogonal matrix $P\in\Real^{d\times d}$ such that $P^\transp A_0 P$ is Metzler\footnote{We say that a matrix is Metlzer when all its non-diagonal coefficients are non-negative.}.
+There exists an orthogonal matrix $Z\in\Real^{p\times p}$ such that $Z^\transp A_0 Z$ is Metzler\footnote{We say that a matrix is Metlzer when all its non-diagonal coefficients are non-negative.}.
 \end{assumption}
@@
 It is for instance the case whenever $A_0$ is diagonalisable, and a fortiori when it is stabilisable.
-The similarity transformation of \citep{Efimov_a2013} provides a method to compute such $P$.
+The similarity transformation of \citep{Efimov_a2013} provides a method to compute such $Z$.
+To simplify the notation, we will further assume that $Z = I_p$.
 Denote $
@@
 \end{eqnarray}
-ensures the inclusion property \eqref{eq:inclusion-property}.
+ensures the inclusion property \eqref{eq:inclusion-property} with confidence level $\delta$..
 \end{theorem}
@@
 \label{thm:control-error}
-Under some assumptions specified in the proof, which amounts to
+Under the following conditions:
 \begin{enumerate}
-	\item a regularity (lipschitz) assumption for the reward $R$;
-	\item a persistent excitation (PE) assumption;
+	\item a Lipschitz regularity assumption for the reward $R$;
+	\item a persistent excitation (PE) assumption:
+	\begin{align*}
+	\exists \underline{\phi},\overline{\phi}>0: \forall n\geq n_0,\quad \underline{\phi}^2 \leq \lambda_{\min}(\Phi_{n}^\transp\Sigma_{p}^{-1}\Phi_{n}) \leq \overline{\phi}^2;
+	\end{align*}
 	\item a stability condition in the form of an LMI;
@@
 \end{equation*}
-where $\Delta_\omega$ is a constant specified in the proof, which corresponds to an irreductible suboptimality suffered from being robust to instantaneous perturbations $\omega(t)$.
+where $\Delta_\omega$ is a constant which corresponds to an irreductible suboptimality suffered from being robust to instantaneous perturbations $\omega(t)$.
 \end{theorem}
@@
 \begin{equation*}
-\exists m\in[M]: \dot{x}(t) = f^M(x(t), u(t)), \forall t\geq 0
+\exists m\in[M]: \dot{x}(t) = f^m(x(t), u(t)), \forall t\geq 0
 \end{equation*}
@@
 We first consider a simple illustrative example, shown in \autoref{fig:prediction}: the control of a 2D system with position $(p_x,p_y)$ and velocity $(v_x, v_y)$ moving by means of a force $(u_x, u_y)$ in an environment with unknown anisotropic friction.
-The dynamics are:
 
@@
 We see that \autoref{alg:full} has a regret $\hat{V}^r - V$ decreasing at least polynomially with $N$, as expected from \autoref{thm:control-error}.
-\todo{The nominal gets better on average}.
+This shows that the agent gets more aggressive when it is more confident, as desired, while ensuring safety at all time.
+In contrast, the nominal agent has an even smaller regret but collided with obstacles in $4\%$ of simulations.
 
@@
 \begin{align*}
-\begin{bmatrix}
+\left[
+\begin{array}{cc|c}
 A_0^\transp P + P A_0^\transp + Q_0 & P|D| & P|\Delta A| \\
 |D|^\transp P & -\rho I_r & 0\\ 
+\hline
 |\Delta A|^\transp P & 0 & -\lambda_{\max}(|\Delta A|) I_p
-\end{bmatrix}< 0,
+\end{array}
+\right]< 0,
 \end{align*}
@@
 \begin{proof}
-Let $e = \ox - \ux$.
-Assuming that eventually after $n\geq N \geq N_0$, $A_0 = A(\theta_{[N],\lambda})$ becomes close enough to $A(\theta)$ to always be Metlzer.
-Then, \eqref{eq:interval-predictor} gives the dynamics:
+Let $e = \ox - \ux$. \eqref{eq:interval-predictor} gives the dynamics:
 \begin{align*}
@@
 \end{align*}
-where $|M| = M^+ + M^-$.
+where recall that $|M| = M^+ + M^-$ for any matrix $M\in\Real^{p\times p}$.
 
@@
 
-Thus, if we had $\Upsilon < 0$, $Q>0$, $\rho > 0$, then we would have
+Thus, if we had $\Upsilon \leq 0$, $Q>0$, $\rho > 0$, then we would have
 \[
@@
 We now examine the condition $\Upsilon < 0$.
-We resort to its Schur complement: $\Upsilon < 0$ if and only if $\alpha > 0$ and $R > S$, where $S= \alpha^{-1}\begin{bmatrix}|\Delta A|^\transp P & 0\end{bmatrix}^\transp \begin{bmatrix}|\Delta A|^\transp P & 0\end{bmatrix}$ and $R$ is the top-left block of $-\Upsilon$:
+We resort to its Schur complement: $\Upsilon \leq 0$ if and only if $\alpha > 0$ and $R \geq S$, where $S= \alpha^{-1}\begin{bmatrix}|\Delta A|^\transp P & 0\end{bmatrix}^\transp \begin{bmatrix}|\Delta A|^\transp P & 0\end{bmatrix}$ and $R$ is the top-left block of $-\Upsilon$:
 \[R = \begin{bmatrix}
@@
 
-Let $Q_0 = Q-4\alpha I_p$.
-Assume that $P$ is fixed, we have $\lambda_{\max}(S) \leq \alpha^{-1}\lambda_{\max}(P)^2\lambda_{\max}(|\Delta A|)^2$.
-Thus, by taking $\alpha_N = \lambda_{\max}(|\Delta A|)^2 = \cO(\log N / N)$, $S = \begin{bmatrix}
+Let $Q_0 = Q+4\alpha I_p$.
+Assume that $P$ is fixed and satisfies the conditions of the lemma. We have $\lambda_{\max}(S) \leq \alpha^{-1}\lambda_{\max}(P)^2\lambda_{\max}(|\Delta A|)^2$.
+Thus, by taking $\alpha = \lambda_{\max}(|\Delta A|)^2 = \cO(\log N / N)$, $S = \begin{bmatrix}
 S_0 & 0\\0 & 0
@@
 -|D|^\transp P & \rho I_r\\
-\end{bmatrix} > 0 \]
-
-We recover \eqref{eq:lyap-bound} with $\mu = \frac{\lambda_{\min}(Q)}{\lambda_{\max}(P)} = \frac{\lambda_{\min}(Q_0) - \alpha_N}{\lambda_{\max}(P)}$.
+\end{bmatrix} \geq 0 \]
+
+We recover \eqref{eq:lyap-bound} with $\mu = \frac{\lambda_{\min}(Q)}{\lambda_{\max}(P)} = \frac{\lambda_{\min}(Q_0) - \alpha}{\lambda_{\max}(P)}$.
 Finally, we obtain
@@
 \|e(t)\|_2^2 &\leq \lambda_{\min}(P)^{-1} V(t)\\
-& \leq \frac{\rho\lambda_{\max}(P)/\lambda_{\min}(P)}{\lambda_{\min}(Q_0) - \alpha_N} C_\omega(t)\\
+& \leq \frac{\rho\lambda_{\max}(P)/\lambda_{\min}(P)}{\lambda_{\min}(Q_0) - 4\alpha} C_\omega(t)\\
 \end{align*}
@@
 \begin{align*}
-\|e(t)\|_2 &\leq C_0\left(1 + \frac{\alpha_N}{2\lambda_{\min}(Q_0)} + \cO(\alpha_N^2)\right)C_\omega(t)\\
+\|e(t)\|_2 &\leq C_0\left(1 + \frac{2\alpha}{\lambda_{\min}(Q_0)} + \cO(\alpha_N^2)\right)C_\omega(t)\\
 &\leq \left(C_0 + \cO(\log N/N)\right)C_\omega(t)
@@
  with $\Delta_\omega = L C_0\sum_{n>N} \gamma^n C_{\omega}(t_n)$.
+
+ Note that $\Delta_\omega$ is finite, since $C_{\omega}(t_n)$ is in the order of $\underline{\omega}(t_n)$, $\overline{\omega}(t_n)$, and these are either bounded in the case of \autoref{assumpt:bounded-noise}, or in the case of \autoref{assumpt:gaussian-noise} in the order of $\sqrt{2\log n / \delta_n}$, with $\delta_n = 1/(n(n+1))$, which is dominated by $\gamma^n$.
 \end{proof}
@@
 The transformed system $Z'=S^{-1}(Z-Z_c)$ verifies \eqref{eq:confidence} with $A_0$ Metlzer as required to apply the interval predictor of Theorem~\ref{thm:predictor}.
-Finally, the obtained predictor is transformed back to the original coordinates $Z$ by using the interval arithmetic of Lemma~\ref{lem:interval}.
+Finally, the obtained predictor is transformed back to the original coordinates $Z$ by using the following lemma:
+\begin{lemma}[Interval arithmerics of \citealt{Efimov2012}]
+	 \label{lem:interval} Let $x\in\mathbb{R}^{n}$ be a vector variable, $\underline{x}\le x\le\overline{x}$ for some $\underline{x},\overline{x}\in\mathbb{R}^{n}$.
+
+	\begin{enumerate}
+		\item If $A\in\Real^{m\times n}$ is a constant matrix, then
+		\begin{equation}
+		A^{+}\underline{x}-A^{-}\overline{x}\le Ax\le A^{+}\overline{x}-A^{-}\underline{x}.\label{eq:Interval1}
+		\end{equation}
+		\item If $A\in\Real^{m\times n}$ is a matrix variable and \textup{$\underline{A}\le A\le\overline{A}$} for some $\underline{A},\overline{A}\in\Real^{m\times n}$, then
+		\begin{gather}
+		\underline{A}^{+}\underline{x}^{+}-\overline{A}^{+}\underline{x}^{-}-\underline{A}^{-}\overline{x}^{+}+\overline{A}^{-}\overline{x}^{-}\leq Ax\label{eq:Interval2}\\
+		\leq\overline{A}^{+}\overline{x}^{+}-\underline{A}^{+}\overline{x}^{-}-\overline{A}^{-}\underline{x}^{+}+\underline{A}^{-}\underline{x}^{-}.\nonumber 
+		\end{gather}
+	\end{enumerate}
+\end{lemma}
 

### 2020-02-06 main.tex
Update conclusion and proof

@@
 \usepackage{bm}
+\usepackage{enumitem}
 \def\sectionautorefname{Section}
@@
 Second, in order to handle this uncertainty we formulate a robust control objective.
-Leveraging tools from interval prediction literature, we convert the confidence regions on parameters into confidence sets on trajectories induced by the controls.
+Leveraging tools from the interval prediction literature, we convert the confidence regions on parameters into confidence sets on trajectories induced by the controls.
 These controls are then optimised resorting to tree-based planning methods.
@@
 
-\paragraph{Experiments} Finally, our last contribution demonstrates the benefits of our proposed \autoref{alg:full} in two numerical experiments, a simple illustrative example and a more challenging simulation for an autonomous driving application.
+\paragraph{Experiments} Finally, our last contribution demonstrates the applicability of our proposed \autoref{alg:full} in two numerical experiments, a simple illustrative example and a more challenging simulation for an autonomous driving application.
 
@@
 Other works use noise injection for exploration such as \citep{Dean2017} or \citep{Dean2018}.
-However, being optimistic and minimising a cumulative regret does not fit a critical setting, where ensuring safety is the first criteria requires instead to consider the pessimistic outcomes.
+However, being optimistic and minimising a cumulative regret does not fit a critical setting, where ensuring safety requires instead to consider the pessimistic outcomes.
 The work of \citet{Dean2017} is closest to our setting: after an offline estimation phase under random exploration, they estimate a simple regret between a robust controller and the oracle optimal performance.
-We also focus on where previous methods often suffer from a limited applicability and computationally intractable subroutines, with the exception of \cite{Dean2018} who provide a polynomial-time algorithm.
+We also focus on applicability where previous methods often suffer from computationally intractable subroutines, with the exception of \cite{Dean2018} who provide a polynomial-time algorithm.
 
@@
 They showed that the main results of Dynamic Programming can be extended to their robust counterparts only when the dynamics ambiguity set verifies a certain rectangularity property, that amounts to an independence assumption between the uncertainty sets of each transition and is related to time-varying uncertainty.
-Since our setting requires dealing with continuous states and time-invariant uncertainty, we rely on monte-carlo value estimates and tree-based planning rather than temporal-difference dynamic programming.
+Since our setting requires dealing with continuous states and time-invariant uncertainty, these methods do not apply.
 
@@
 We abuse notations and include additional known terms in the measurement signal $y(t)$:
-\begin{equation}
-\label{eq:measurement}
+\begin{equation*}
+%\label{eq:measurement}
     y(t) = \dot{x}(t) + C\nu(t) - A x(t) - Bu(t).
-\end{equation}
+\end{equation*}
 Thus, we obtain a linear regression system
-\[
+\begin{equation*}
 y_n = \Phi_n\theta + \eta_n.
-\]
+\end{equation*}
 
@@
 \label{assumpt:bounded-noise}
-The noise $\eta(t)$ is bounded
-\[
-\|\eta\|_\infty < \infty.
-\]
+The noise $\eta(t)$ is bounded in $\|\cdot\|_\infty$.
+\end{assumption}
+
 In particular, we denote the coefficient-wise bounds over perturbations as $\underline{\omega}(t) \leq \omega(t) \leq \overline{\omega}(t)$.
-\end{assumption}
-
 This is a deterministic assumption, then by Hölder inequality a confidence region $\cC_{[N],0}$ can be derived based on a $L_1$-ball estimate of $\theta$ at time $N$, i.e.
@@
 \label{eq:bounded-noise-polytope}
-\|\theta_{N,\lambda} - \theta\|_1 \leq {} &\|G_{N, \lambda}^{-1}\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\|_1\|\eta\|_\infty \\
-&+ \lambda\|G_{N, \lambda}^{-1}\|_1 S
+\|\theta_{N,\lambda} - \theta\|_1 \leq {} &\|G_{N, \lambda}^{-1}\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\|_1\|\eta\|_\infty + \lambda\|G_{N, \lambda}^{-1}\|_1 S
 \end{split}
@@
     \label{eq:polytope}
-     &\cC_{[N],\delta} = \left\{ A_{0}+\sum_{i=1}^{2^d}\alpha_{i}\Delta A_{i}: \alpha\in[0, 1]^{2^d},  \sum_{i=1}^{2^d}\alpha_{i}=1\right\},\\
-     &A_{0,N} = A + \theta_{N,\lambda}^\transp\phi, \quad\Delta A_{i} = \todo{h_i} \sqrt{\frac{\beta_N(\delta)}{\lambda_{\max}(G_{N,\lambda})}}
+     &\cC_{[N],\delta} = \left\{ A_{0}+\sum_{i=1}^{2^d}\alpha_{i}\Delta A_{i}: \alpha\geq 0,  \sum_{i=1}^{2^d}\alpha_{i}=1\right\}
 \end{align}
-
+where $A_{0,N} = A + \theta_{N,\lambda}^\transp\phi, \Delta A_{i} = {h_i} \sqrt{\frac{\beta_N(\delta)}{\lambda_{\max}(G_{N,\lambda})}}, h_i\in\{-1,1\}^d$.
 Another strategy presented in Appendix \ref{sec:tight-polytope} produces a much tighter polytope, at the price of an increased computational cost required by the diagonalisation of $G_{N,\lambda}$.
@@
 In the unbounded sub-Gaussian noise setting of \autoref{assumpt:gaussian-noise}, we can use the same formulation by deriving local high-confidence bounds that each holds with probability $\delta_n$.
-By choosing $\delta_n = \frac{\delta}{n(n+1)}$, we have that the event $\{\forall n, \underline{\omega}(t_n) \leq \omega(t_n) \leq \overline{\omega}(t_n)\}$ holds with probability $1-\delta$.
+By choosing $\delta_n = \frac{\delta}{n(n+1)}$, the event $\{\forall n, \underline{\omega}(t_n) \leq \omega(t_n) \leq \overline{\omega}(t_n)\}$ holds with probability $1-\delta$.
 
@@
 However, \citet{leurent2019interval} showed that this predictor can have unstable dynamics, even for stable systems, which causes a fast build-up of uncertainty.
-They propose an enhanced predictor which exploits the polytopic structure \eqref{eq:polytope} produces tighter and more stable predictions, and whose stability can be assessed by solving an LMI, at the price of an additional requirement:
+They proposed an enhanced predictor which exploits the polytopic structure \eqref{eq:polytope} to produce tighter and more stable predictions, at the price of an additional requirement:
 
@@
     \vspace{-0.5cm}
-	\caption{Comparison of \eqref{eq:predictor-naive} to \eqref{eq:interval-predictor} for a simple system $\dot{x}(t)=-\theta x(t)+d(t)$, with $\theta\in[1, 2]$.}
+	\caption{Comparison of \eqref{eq:predictor-naive} to \eqref{eq:interval-predictor} for a simple system \\$\dot{x}(t)=-\theta x(t)+\omega(t)$, with $\theta\in[1, 2]$ and $\omega(t) \in [-0.05, 0.05]$.}
 	\label{fig:predictor_example}
@@
 \label{prop:lower-bound}
-With high probability, the surrogate objective  \eqref{eq:surrogate_objective} is a lower bound of the true objective \eqref{eq:robust-control-disc}:
-\begin{equation}
+The surrogate objective  \eqref{eq:surrogate_objective} is a lower bound of the true objective  \eqref{eq:robust-control-disc} with probability at least $1-\delta$: 
+\begin{equation*}
 \hat{V}^r(\bu) \leq V^r(\bu)
-\end{equation}
+\end{equation*}
 \end{proposition}
@@
 where $\cL_k$ is the set of leaves of $\cT_k$, $h(a)$ is the length of the sequence $a$, and $\underline{R}_n(a)$ the pessimistic reward \eqref{eq:pessimistic-rewards} obtained at time $n$ by following the controls $u_n = \pi_{a_n}(x_n)$.
-\begin{theorem}[Planning performance, \citep{Hren2008}]
+\begin{theorem}[Planning performance of \citealt{Hren2008}]
 \label{theorem:opd-regret}
@@
 Hence, by using enough computational budget $K$ for planning we can get as close as we want to the optimal surrogate value $\hat{V}^r(a^{\star})$, at a polynomial rate.
-However, there exists a gap between $\hat{V}^r$ and the true robust objective $V^r$, which stems from three approximations: (i) the true reachable set was approximated by an enclosing interval in \eqref{eq:inclusion-property}; (ii) the time-invariance of the dynamics uncertainty $A(\theta)\in\cC_{[N],\delta}$ was handled by the interval predictor \eqref{eq:interval-predictor} as if it were a time-varying uncertainty $A(\theta(t))\in\cC_{[N],\delta},\forall t$ ; and (iii) the lower-bound $\sum\min\leq \min\sum$ used to define the surrogate objective \eqref{eq:surrogate_objective} is not tight.
-However, this gap can be bounded with additional assumptions:
-\begin{theorem}[Sample complexity]
+Unfortunately, there exists a gap between $\hat{V}^r$ and the true robust objective $V^r$, which stems from three approximations: (i) the true reachable set was approximated by an enclosing interval in \eqref{eq:inclusion-property}; (ii) the time-invariance of the dynamics uncertainty $A(\theta)\in\cC_{[N],\delta}$ was handled by the interval predictor \eqref{eq:interval-predictor} as if it were a time-varying uncertainty $A(\theta(t))\in\cC_{[N],\delta},\forall t$ ; and (iii) the lower-bound $\sum\min\leq \min\sum$ used to define the surrogate objective \eqref{eq:surrogate_objective} is not tight.
+However, this gap can be bounded with additional assumptions.
+\begin{theorem}[Regret bound]
 \label{thm:control-error}
-Under the following conditions:
+Under three conditions:
 \begin{enumerate}
@@
 	\end{align*}
-	\item a stability condition in the form of an LMI;
+	\item a stability condition: there exist $P>0,Q_0\in\Real^{p\times p}$, $\rho>0$ such that
+	$\begin{bmatrix}
+		A_0^\transp P + P A_0^\transp + Q_0 & P|D|  \\
+		|D|^\transp P & -\rho I_r \\
+	\end{bmatrix}< 0;$
 \end{enumerate}
@@
 \end{equation*}
-where $\Delta_\omega$ is a constant which corresponds to an irreductible suboptimality suffered from being robust to instantaneous perturbations $\omega(t)$.
+with probability at least $1-\delta$, where $\Delta_\omega$ is a constant which corresponds to an irreductible suboptimality suffered from being robust to instantaneous perturbations $\omega(t)$.
 \end{theorem}
@@
 
-\begin{theorem}[Regret bound]
+\begin{theorem}[Robust planning performance]
 \label{theorem:drop-regret}
-The robust version of \texttt{OPD} \eqref{eq:robust-b-values} enjoys the same regret bound as provided for \texttt{OPD} in \autoref{theorem:opd-regret}, with respect to the robust objective \eqref{eq:robust-objective-discrete}.
+The robust version of \texttt{OPD} \eqref{eq:robust-b-values} enjoys the same regret bound as that of \texttt{OPD} in \autoref{theorem:opd-regret}, with respect to the robust objective \eqref{eq:robust-objective-discrete}.
 \end{theorem}
 
-Note that this theorem bounds the performance gap with respect to the number of node expansions, but each expansion now requires $M$ times more simulations than in the single-model setting.
-The solution of the robust objective \eqref{eq:robust-objective-discrete} with discrete ambiguity $f\in\{f^m\}_{m\in[M]}$ can be recovered exactly, asymptotically when the planning budget $H$ goes to infinity.
+The regret depends on the number $K$ of node expansions, but each expansion now requires $M$ times more simulations than in the single-model setting.
+The solution of the robust objective \eqref{eq:robust-objective-discrete} with discrete ambiguity $f\in\{f^m\}_{m\in[M]}$ can be recovered exactly, asymptotically when the planning budget $K$ goes to infinity.
 This is in contrast to the results obtained in \autoref{sec:control} for the robust objective \eqref{eq:robust-control} with continuous ambiguity $A(\theta)\in\cC_{[N],\delta}$, for which \texttt{OPD} only recovers the surrogate approximation $\hat{V}^r$, as discussed in \autoref{thm:control-error}.
+Finally, the two approaches of Sections \ref{sec:control} and \ref{sec:multi-model} can be merged by using the pessimistic reward \eqref{eq:pessimistic-rewards} in \eqref{eq:robust-b-values}.
 
@@
 	\includegraphics[width=0.8\linewidth]{img/regret.pdf}
-	\caption{The mean regret with its $95\%$ confidence interval for the robust and nominal agents with respect to the number $N$ of samples.}
+	\caption{The mean regret along with its $95\%$ confidence interval with respect to $N$, for the robust and nominal agents.}
 	\label{fig:regret}
@@
 \paragraph{Behavioural planning for an autonomous vehicle}
-We consider the \href{https://github.com/eleurent/highway-env}{highway-env} environment \citep{highway-env}, a  simulator for autonomous driving decision problems.
-An autonomous vehicle with state $\chi_0\in\Real^4$ is approaching an intersection among $V$ other vehicles with states $\chi_i\in\Real^4$, resulting in a joint traffic state $x = [\chi_0, \chi_1,\dots,\chi_V]^\top\in\Real^{4V+4}$.
-These other vehicles follow parametrized behaviours $\dot{\chi}_i=f_i(x,\theta_i)$ with unknown parameters $\theta_i\in\Real^5$.
-Here, we appreciate a first advantage of the structure imposed in \autoref{assumpt:structure}: the uncertainty space of $\theta$ is $\Real^{5V}$.
-In comparison, the traditional adaptive LQ setting where the whole state matrix $A$ is estimated would have resulted in a much larger parameter space $\theta\in\Real^{16V^2}$.
+We consider the \href{https://github.com/eleurent/highway-env}{highway-env} environment \citep{highway-env} for simulated driving decision problems.
+An autonomous vehicle is approaching an intersection among $V$ other vehicles, resulting in a joint traffic state $x = [\chi_0, \dots,\chi_V]^\top\in\Real^{4V+4}$.
+These vehicles follow parametrized behaviours $\dot{\chi}_i=f_i(x,\theta_i)$ with unknown parameters $\theta_i\in\Real^5$.
+We appreciate a first advantage of the structure imposed in \autoref{assumpt:structure}: the uncertainty space of $\theta$ is $\Real^{5V}$.
+In comparison, the traditional LQ setting where the whole state matrix $A$ is estimated would have resulted in a much larger parameter space $\theta\in\Real^{16V^2}$.
 %This allows to scale to larger systems: in our experiments, we used a state space of dimension $44$ ($V=10$) where e.g.
 \citep{Dean2018,abeille18a} reported numerical experiments with states of dimensions 3 and 4, respectively.
-This system dynamics $f$, which describes the couplings and interactions between vehicles, can only be expressed in the form of \autoref{assumpt:structure} given the knowledge of the desired routes of each vehicle.
-Then, the features $\phi$ express deviations of the vehicles trajectories to the centerline of the followed lane.
+This system dynamics $f$ can only be expressed in the form of \autoref{assumpt:structure} given the knowledge of the desired route for each vehicle, with features $\phi$ expressing deviations to the centerline of the followed lane.
 Since these intentions are unknown to the agent, we adopt the multi-model perspective of \autoref{sec:multi-model} and consider one model per possible route for every observed vehicle before an intersection.
-Again, we compare \autoref{alg:full} to a nominal agent planning with the estimated parameter $\theta_{[N],\lambda}$, with two different modelling assumptions: we assume that Nominal 1 has access to the true followed route for each vehicle, while Nominal 2 does not and picks the model with minimal prediction error at the planning time.
+We compare \autoref{alg:full} to a nominal agent planning with the estimated parameter $\theta_{[N],\lambda}$, with two different modelling assumptions: we assume that Nominal 1 has access to the true followed route for each vehicle, while Nominal 2 does not and picks a model with minimal prediction error.
 There performances are compared in \autoref{tab:driving}.
-Again, the robust approach is less efficient on average than planning with the nominal model, but it does better in terms of worst-case performance and manages to avoid collisions, contrary to the nominal baselines that suffer from model bias.
-
-\begin{figure}
+Again, the robust approach is less efficient on average than planning with the nominal model, but it does better in terms of worst-case performance and avoids collisions, contrary to the nominal baselines that suffer from model bias.
+
+\begin{figure}[t]
 	\centering
-	\includegraphics[width=0.8\linewidth]{img/highway-small}
+	\includegraphics[width=0.7\linewidth]{img/highway-small}
 	\caption{The intersection crossing task. We show the trajectory intervals corresponding to behavioural uncertainty for each observed vehicle, and the multi-model assumption over the followed route.}
@@
 
-\begin{table}[tbp]
+\begin{table}[t]
 	\caption{Performances on the driving task}
@@
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum
+We present a framework for the robust estimation, prediction and control of a partially known linear system with generic costs.
+Leveraging tools from linear regression, interval prediction, and tree-based planning, we guarantee the predicted performance for the true system and provide a regret bound.
+The applicability of the method is further improved by a multi-model extension, and demonstrated on two simulated applications.
 
@@
 \begin{align*}
-\left[
-\begin{array}{cc|c}
-A_0^\transp P + P A_0^\transp + Q_0 & P|D| & P|\Delta A| \\
-|D|^\transp P & -\rho I_r & 0\\ 
-\hline
-|\Delta A|^\transp P & 0 & -\lambda_{\max}(|\Delta A|) I_p
-\end{array}
-\right]< 0,
+\begin{bmatrix}
+A_0^\transp P + P A_0^\transp + Q_0 & P|D|  \\
+|D|^\transp P & -\rho I_r \\
+\end{bmatrix}< 0,
 \end{align*}
@@
 \[\|\ox(t) - \ux(t)\| \leq \left(C_0 + \cO\left({\frac{\log N}{N}} \right)\right)C_\omega(t) \]
-where $C_\omega(t) = \sup_{\tau\in[t_N,t]} \|\overline{\omega}(\tau) - \underline{\omega}(\tau)\|_2^2$ and $C_0 = \sqrt{{\rho\lambda_{\max}(P)}/({\lambda_{\min}(P)\lambda_{\min}(Q_0)})}$.
+where $C_\omega(t) = \sup_{\tau\in[t_N,t]} \|\overline{\omega}(\tau) - \underline{\omega}(\tau)\|_2^2$ and $C_0 = \sqrt{{2\rho\lambda_{\max}(P)}/({\lambda_{\min}(P)\lambda_{\min}(Q_0)})}$.
 \end{lemma}
@@
 \dot{V} \leq {}& X^\transp
-\underbrace{\begin{bmatrix}
+\underbrace{
+\left[
+\begin{array}{cc|c}
 A_0^\transp P + P A_0^\transp + Q + 4\alpha I_p & P|D| & P|\Delta A| \\
 |D|^\transp P & -\rho I_r & 0\\
+\hline
 |\Delta A|^\transp P & 0 & -\alpha I_p
-\end{bmatrix}}_{\Upsilon}
+\end{array}
+\right]}_{\Upsilon}
 X\\
@@
 
-We now examine the condition $\Upsilon < 0$.
-We resort to its Schur complement: $\Upsilon \leq 0$ if and only if $\alpha > 0$ and $R \geq S$, where $S= \alpha^{-1}\begin{bmatrix}|\Delta A|^\transp P & 0\end{bmatrix}^\transp \begin{bmatrix}|\Delta A|^\transp P & 0\end{bmatrix}$ and $R$ is the top-left block of $-\Upsilon$:
+We now examine the condition $\Upsilon \leq 0$.
+We resort to its Schur complement: given $\alpha > 0$ , $\Upsilon \leq 0$ if and only if $R \geq S$, where $S= \alpha^{-1}\begin{bmatrix}|\Delta A|^\transp P & 0\end{bmatrix}^\transp \begin{bmatrix}|\Delta A|^\transp P & 0\end{bmatrix}$ and $R$ is the top-left block of $-\Upsilon$:
 \[R = \begin{bmatrix}
@@
 
-Let $Q_0 = Q+4\alpha I_p$.
-Assume that $P$ is fixed and satisfies the conditions of the lemma. We have $\lambda_{\max}(S) \leq \alpha^{-1}\lambda_{\max}(P)^2\lambda_{\max}(|\Delta A|)^2$.
-Thus, by taking $\alpha = \lambda_{\max}(|\Delta A|)^2 = \cO(\log N / N)$, $S = \begin{bmatrix}
-S_0 & 0\\0 & 0
-\end{bmatrix}$ becomes $\cO(1)$ with respect to $N$.
-Thus, we can always find a $Q_0$ such that
-\[R-S = \begin{bmatrix}
--A_0^\transp P - P A_0^\transp - Q_0 - S_0 & -P|D|\\
+Choose $Q = \frac{1}{2}Q_0-4\alpha I_p$.
+Assume that $P$ is fixed and satisfies the conditions of the lemma. We have $$\lambda_{\max}(S) \leq \alpha^{-1}\lambda_{\max}(|\Delta A|)^2\lambda_{\max}(P)^2.$$
+
+Thus, by taking $\alpha = \frac{\lambda_{\max}(|\Delta A|)^2\lambda_{\max}(P)^2}{2\lambda_{\min}(Q_0)} = \cO(\log N / N)$, we can obtain that $S \leq \begin{bmatrix}
+\frac{1}{2}Q_0 & 0\\0 & 0
+\end{bmatrix}$. Thus,
+\[R-S \geq \begin{bmatrix}
+-A_0^\transp P - P A_0^\transp - Q_0 & -P|D|\\
 -|D|^\transp P & \rho I_r\\
@@
 
-We recover \eqref{eq:lyap-bound} with $\mu = \frac{\lambda_{\min}(Q)}{\lambda_{\max}(P)} = \frac{\lambda_{\min}(Q_0) - \alpha}{\lambda_{\max}(P)}$.
+We recover \eqref{eq:lyap-bound} with $\mu = \frac{\lambda_{\min}(Q)}{\lambda_{\max}(P)} = \frac{\frac{1}{2}\lambda_{\min}(Q_0) - 4\alpha}{\lambda_{\max}(P)}$.
 Finally, we obtain
@@
 \|e(t)\|_2^2 &\leq \lambda_{\min}(P)^{-1} V(t)\\
-& \leq \frac{\rho\lambda_{\max}(P)/\lambda_{\min}(P)}{\lambda_{\min}(Q_0) - 4\alpha} C_\omega(t)\\
-\end{align*}
-Developing at the first order in $\alpha_N$ gives
-\begin{align*}
-\|e(t)\|_2 &\leq C_0\left(1 + \frac{2\alpha}{\lambda_{\min}(Q_0)} + \cO(\alpha_N^2)\right)C_\omega(t)\\
+& \leq \frac{2\rho\lambda_{\max}(P)/\lambda_{\min}(P)}{\lambda_{\min}(Q_0) - 8\alpha} C_\omega(t)\\
+\end{align*}
+Developing at the first order in $\alpha$ gives
+\begin{align*}
+\|e(t)\|_2 &\leq C_0\left(1 + \frac{4\alpha}{\lambda_{\min}(Q_0)} + \cO(\alpha_N^2)\right)C_\omega(t)\\
 &\leq \left(C_0 + \cO(\log N/N)\right)C_\omega(t)
@@
 
- Note that $\Delta_\omega$ is finite, since $C_{\omega}(t_n)$ is in the order of $\underline{\omega}(t_n)$, $\overline{\omega}(t_n)$, and these are either bounded in the case of \autoref{assumpt:bounded-noise}, or in the case of \autoref{assumpt:gaussian-noise} in the order of $\sqrt{2\log n / \delta_n}$, with $\delta_n = 1/(n(n+1))$, which is dominated by $\gamma^n$.
+ Note that $\Delta_\omega$ is finite, since $C_{\omega}(t_n)$ is in the order of $\underline{\omega}(t_n)$, $\overline{\omega}(t_n)$, and these are either bounded in the case of \autoref{assumpt:bounded-noise}, or in the case of \autoref{assumpt:gaussian-noise} in the order of $\sqrt{2\log n / \delta_n}$, with $\delta_n = \delta/(n(n+1))$, which is dominated by $\gamma^n$.
 \end{proof}

### 2020-02-06 main.tex
Remarks by Odalric

@@
 The full procedure is designed to produce reasonable and safe behaviours at deployment while recovering an asymptotic optimality.
-We illustrate it on a practical case of autonomous driving at a crossroads intersection among vehicles with uncertain behaviours.
+We illustrate it on a practical case of autonomous driving at a crossroads intersection among vehicles with uncertain behaviours.\footnote[2]{Source code and videos are available in the supplementary materials}
 \end{abstract}
@@
 In this paper, we consider the problem of controlling an unknown linear system $x(t)$ so as to maximise an \emph{arbitrary} bounded reward function $R$, in a critical setting where mistakes are costly and must be avoided at all time.
-This choice of rich reward space is crucial to have sufficient flexibility to model non-convex and non-smooth functions that naturally arise in many practical problems involving combinatorial optimisation, branching decisions, etc., while quadratic costs are mostly suited for the tracking of a reference trajectory already known a priori.
+This choice of rich reward space is crucial to have sufficient flexibility to model non-convex and non-smooth functions that naturally arise in many practical problems involving combinatorial optimisation, branching decisions, etc., while quadratic costs are mostly suited for tracking a reference trajectory already known a priori \citep[e.g.][]{Kumar2013}.
 
@@
 We argue that this assumption is realistic given that most industrial applications to date have been relying on physical models to describe their processes and well-engineered controllers to operate them, rather than machine learning.
-Our framework relaxes this modelling effort by allowing some structured uncertainty around the nominal model.
+Our framework relaxes this modelling effort by allowing some \emph{structured uncertainty} around the nominal model.
 We adopt a data-driven scheme where we wish to estimate the parameters more accurately as we interact with the true system.
-Most model-based reinforcement learning algorithms only rely on the estimated dynamics to derive the corresponding optimal controller, but these methods often suffer from \emph{model bias}: they ignore the error that exists between the learned and true dynamics, which can dramatically degrade the control performances \citep{Schneider1997}.
+Most model-based reinforcement learning algorithms rely on the estimated dynamics to derive the corresponding optimal controls \citep[e.g.][]{Lenz2015,Levine2015}, but suffer from \emph{model bias}: they ignore the error that exists between the learned and true dynamics, which can dramatically degrade the control performances \citep{Schneider1997}.
 This is all the more relevant when maximising an objective under constraints --or penalties-- which naturally pushes the systems to operate in the vicinity of constraint saturation and makes it prone to failures.
 
-To address this issue, we turn to the framework of \emph{robust} decision-making: instead of merely considering a point estimate of the dynamics, we build an entire \emph{confidence region} that contains the true dynamics with high probability, and optimise the decisions so as to maximise the worst-case outcome with respect to this uncertainty.
-Minimax problem are hard to solve, and all the more in our setting where the reward function $R$ is generic.
-In particular, this excludes a number of tools from the robust synthesis literature, such as $\cH_\infty$ \citep[see, e.g.][]{Basar1996} control or system-level synthesis \citep{Dean2017,Dean2018}.
+To address this issue, we turn to the framework of \emph{robust} decision-making \citep{Bental2009,Bertsimas2011,Gorissen2015}: instead of merely considering a point estimate of the dynamics, we build an entire \emph{confidence region} that contains the true dynamics with high probability, and optimise the decisions so as to maximise the worst-case outcome with respect to this uncertainty.
+Maximin problems are hard to solve, and all the more in our setting where the reward function $R$ is generic.
+In particular, this excludes a number of tools from the robust synthesis literature, such as $\cH_\infty$ control \citep[see, e.g.][]{Basar1996} or system-level synthesis \citep{Dean2017,Dean2018}.
 We turn instead to more general planning algorithms.
 The continuous state space prevents us from using dynamic programming techniques, so we consider tree-based planning instead.
-Though there exist work addressing continuous actions \citep{Busoniu2018,Weinstein2012}, we resort to a first approximation and discretise the decision space by adopting a hierarchical control architecture.
+Though there exist works addressing continuous actions \citep{Busoniu2018,Weinstein2012}, we resort to a first approximation and discretise the decision space by adopting a hierarchical control architecture.
 At each time, the agent can select low-level controller to execute among a finite basis, e.g.
@@
 The discretisation induces a suboptimality, but it can be mitigated by diversifying the controller basis.
-Tree-based planning algorithms are relevant in this context of discrete action, but are only designed for a single known generative model instead of an entire confidence region for the system dynamics.
+Tree-based planning algorithms are relevant in this context of discrete actions, but are only designed for a single known generative model instead of an entire confidence region for the system dynamics.
 Hence, we adapt them to the robust framework by following a two-steps procedure: we first predict a set of states that can be reached under a planned control sequence with respect to all possible dynamics.
@@
 The dynamics of the real system are described in continuous time.
-However, all the sensing and control performed on-board happen in discrete time, with time-step $\dd t$.
-For any variable $z$, we use the subscript notation to refer to these discrete times: $z_n = z(t_n)$ with $t_n = n\dd t$.
+However, all the sensing and control performed on-board happen in discrete time, with time-step $\dd t>0$.
+For any variable $z$, we use the subscript notation to refer to these discrete times: $z_n = z(t_n)$ with $t_n = n\dd t$ and $n\in\Natural$.
 We use bold symbols to denote temporal sequences $\bz = (z_n)_{n>N}$.
@@
 The control matrix $B\in\Real^{p\times q}$ and disturbance matrix $D\in\Real^{p\times r}$ are known.
-
 We also assume having access to the observation of $x(t)$ and to a noisy measurement of $\dot{x}(t)$ in the form $y(t)=\dot{x}(t) + C\nu(t)$, where $\nu(t)\in\Real^s$ is a measurement noise and $C\in\Real^{p\times s}$ is known.
 Assumptions over the disturbance $\omega$ and noise $\nu$ will be detailed further, and we denote $\eta(t) = C\nu(t) + D\omega(t)$.
+
+ Our goal is to design a robust model predictive control for \eqref{eq:dynamics}, and to this end the following steps will be performed and explained later in details.
 
@@
 	\includegraphics[trim={0 2cm 0 0}, clip, width=0.6\linewidth]{img/ellipsoid}
-	\caption{The model estimation procedure. The size of the confidence region $C_{[N],\delta}$ shrinks with the number of samples $N$.}
+	\caption{The model estimation procedure, running on the obstacle avoidance problem of \autoref{sec:experiments}.
+The size of the confidence region $C_{[N],\delta}$ shrinks with the number of samples $N$.}
 	\label{fig:estimation}
@@
 	\includegraphics[width=0.8\linewidth]{img/obstacle_small}
-	\caption{The state prediction procedure. At each timestep (red to green), we bound the set of reachable states considering model uncertainty \eqref{eq:confidence}}
+	\caption{The state prediction procedure running on the obstacle avoidance problem of \autoref{sec:experiments}.
+At each time step (red to green), we bound the set of reachable states under model uncertainty \eqref{eq:confidence}}
 	\label{fig:prediction}
@@
 In \autoref{sec:prediction}, we aim to derive a \emph{set predictor} $X(t)$ for the system \eqref{eq:dynamics}, illustrated in \autoref{fig:prediction}.
-This predictor takes the information on the observed current state ${x}_N$, a confidence region $\cC_\delta$ verifying \eqref{eq:confidence}, a planned control sequence $\bu$ and some admissible bounds on the perturbation $[\underline{\omega}(t),\overline{\omega}(t)]$; and outputs a set $X(t)$ that must verify the inclusion property:
+This predictor takes the information on the observed current state ${x}_N$, a confidence region $\cC_\delta$ verifying \eqref{eq:confidence}, a planned control sequence $\bu$ and some admissible bounds on the perturbation $[\underline{\omega}(t),\overline{\omega}(t)]$; and outputs a set $X(t)$ that must verify the \emph{inclusion property}:
 \begin{equation}
@@
 \end{equation}
-
 We leverage recent results from the uncertain system simulation literature to efficiently compute such a predictor.
@@
 Our third contribution adapts them to the robust objective \eqref{eq:robust-control-disc} by approximating it with an easily-evaluable surrogate $\hat{V}^r$ that exploits the set predictor \eqref{eq:inclusion-generic} to define a pessimistic reward.
-In our main result, we show that the best surrogate performance achieved during planning is guaranteed to be attained on the true system, and we provide an upper bound for the approximation gap and simple regret of our framework.
+In our main result, we show that the best surrogate performance achieved during planning is guaranteed to be attained on the true system, and provide an upper bound for the approximation gap and simple regret of our framework in \autoref{thm:control-error}.
 
@@
 
-\paragraph{Model selection} In \autoref{sec:multi-model}, our forth contribution extends our framework to consider multiple modelling assumptions, while ensuring tight uncertainty estimation through data-driven model rejection, and safety via robust model-selection during planning.
-
-\paragraph{Experiments} Finally, our last contribution demonstrates the applicability of our proposed \autoref{alg:full} in two numerical experiments, a simple illustrative example and a more challenging simulation for an autonomous driving application.
+\paragraph{Model selection} In \autoref{sec:multi-model}, our forth contribution extends the proposed framework to consider multiple modelling assumptions, while narrowing uncertainty through data-driven model rejection, and still ensuring safety via robust model-selection during planning.
+
+\paragraph{Experiments} Finally, in \autoref{sec:experiments} we demonstrate the applicability of our proposed \autoref{alg:full} in two numerical experiments.
+First, a simple illustrative example and then, a more challenging simulation for safe autonomous driving.
 
@@
 	\begin{algorithmic}
-		\STATE {\bfseries Input:} confidence level $\delta$, structure $A,\phi$, reward $R$
+		\STATE {\bfseries Input:} confidence level $\delta$, structure $(A,\phi)$, reward $R$
 		\STATE $\cD_{[0]}\gets\emptyset,\, \ba_1\gets\emptyset$
@@
 		\FOR{planning steps $k\in[K]$}
-		\FOR{$b\in A$}
+		\FOR{each action $b\in A$}
 		\STATE $[\underline{x}_{n+1}, \overline{x}_{n+1}]\gets$ \textsc{Interval Prediction}(
@@
 
-We abuse notations and include additional known terms in the measurement signal $y(t)$:
+We abuse notations and define a virtual measurement signal, still denoted $y(t)$, that includes additional known terms
 \begin{equation*}
 %\label{eq:measurement}
-    y(t) = \dot{x}(t) + C\nu(t) - A x(t) - Bu(t).
-\end{equation*}
-Thus, we obtain a linear regression system
-\begin{equation*}
+    y(t) = \dot{x}(t) + C\nu(t) - A x(t) - Bu(t),
+\end{equation*}
+to obtain a linear regression system
+$
 y_n = \Phi_n\theta + \eta_n.
-\end{equation*}
+$
 
 \paragraph{Regularised least square} To derive an estimate on $\theta$, we consider the weighted $L_2$-regularised regression problem with weights  $\Sigma_p\in\Real^{p\times p}$ and parameter $\lambda\in\Real^+_*$:
-
 \begin{equation}
@@
 \label{prop:regularized_solution}
-The solution to \eqref{eq:regression_min} is:
-\begin{equation}
+The solution to \eqref{eq:regression_min} is
+\begin{align}
     \label{eq:vector_rls}
-    \theta_{N,\lambda} = G_{N, \lambda}^{-1} \sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1} y_n,
-\end{equation}
-where 
-\begin{equation}
+    \theta_{N,\lambda} &= G_{N, \lambda}^{-1} \sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1} y_n,\\
 	\label{eq:g_n_lambda}
-    G_{N, \lambda} = \sum_{n=1}^N \Phi_{n}^\transp\Sigma_p^{-1}\Phi_{n}  + \lambda I_d \in \Real^{d\times d}.
-\end{equation}
+    \text{where }\quad G_{N, \lambda} &= \sum_{n=1}^N \Phi_{n}^\transp\Sigma_p^{-1}\Phi_{n}  + \lambda I_d \in \Real^{d\times d}.
+\end{align}
 \end{proposition}
 
-By simply substituting the expression of $y_n$ into \eqref{eq:vector_rls}, we obtain the regression error:
+Substituting $y_n$ into \eqref{eq:vector_rls} yields the regression error:
 \begin{align}
@@
 \begin{equation}
-\begin{split}
 \label{eq:bounded-noise-polytope}
-\|\theta_{N,\lambda} - \theta\|_1 \leq {} &\|G_{N, \lambda}^{-1}\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\|_1\|\eta\|_\infty + \lambda\|G_{N, \lambda}^{-1}\|_1 S
-\end{split}
+\|\theta_{N,\lambda}\! -\! \theta\|_1\! \leq \! \|G_{N, \lambda}^{-1}\!\sum_{n=1}^N \!\Phi_n^\transp\! \Sigma_p^{-1}\!\|_1\|\eta\|_\infty\! +\!\lambda\|G_{N, \lambda}^{-1}\!\|_1S
 \end{equation}
@@
 \begin{equation*}
-    \forall u\in\Real^p,\, \expectedvalue \left[ \exp{\left( u^\transp \eta(t)\right)}\right] \leq \exp{\left( \frac{1}{2} u^\transp \Sigma_p u\right)}
+    \forall u\in\Real^p,\, \expectedvalue \left[ \exp{\left( u^\transp \eta(t)\right)}\right] \leq \exp{\left( \frac{1}{2} u^\transp \Sigma_p u\right)}.
 \end{equation*}
@@
 We can enclose this confidence ellipsoid $\eqref{eq:confidence-ellipsoid}$ into a polytope $C_{[N],\delta}$.
-For simplicity, we present here a very simple but coarse strategy: bound the ellipsoid by its enclosing sphere, and the sphere by its enclosing hypercube:
+For simplicity, we present here a simple but coarse strategy: bound the ellipsoid by its enclosing sphere, and then the sphere by its enclosing hypercube.
+We obtain
 \begin{align}
@@
 To study the inclusion property \eqref{eq:inclusion-generic}, we must start by choosing a set representation $X(t)$.
-We consider interval prediction, rather than zonotope prediction for instance, for the sake of simplicity of implementation and computational efficiency.
-Thus, we represent an interval as $X(t) = [\underline{x}(t), \overline{x}(t)]\in \Real^p\times \Real^p$, and the inclusion property becomes:
+We consider interval prediction, rather than zonotope prediction for instance \citep[e.g.][]{le2012}, for the sake of simplicity of implementation and computational efficiency.
+We represent an interval as $X(t) = [\underline{x}(t), \overline{x}(t)]\in \Real^p\times \Real^p$, and \eqref{eq:inclusion-generic} becomes:
 \begin{equation}
@@
 
-\begin{theorem}[Enhanced Predictor of \citealt{leurent2019interval}]
+\begin{proposition}[Enhanced Predictor of \citealt{leurent2019interval}]
 \label{thm:predictor}
@@
 ensures the inclusion property \eqref{eq:inclusion-property} with confidence level $\delta$..
-\end{theorem}
+\end{proposition}
 
@@
 	{\includegraphics[trim={0 0.6cm 0 0.4cm}, clip, width=\linewidth]{img/interval-predictor}}
-    \vspace{-0.5cm}
+    \vspace{-0.7cm}
 	\caption{Comparison of \eqref{eq:predictor-naive} to \eqref{eq:interval-predictor} for a simple system \\$\dot{x}(t)=-\theta x(t)+\omega(t)$, with $\theta\in[1, 2]$ and $\omega(t) \in [-0.05, 0.05]$.}
@@
 
-The \autoref{fig:predictor_example} illustrates the differences of stability of the two predictors with a simple example.
-It suggests to always prefer \eqref{eq:interval-predictor} whenever \autoref{assumpt:metzler} is verified, and only use \eqref{eq:predictor-naive} as a last resort.
+\autoref{fig:predictor_example} illustrates the differences of stability of the two predictors with a simple example.
+It suggests to always prefer \eqref{eq:interval-predictor} whenever \autoref{assumpt:metzler} is verified, and only fallback to \eqref{eq:predictor-naive} as a last resort.
 
@@
 \label{sec:control}
-To evaluate the robust objective $V^r$ \eqref{eq:robust-control}, we approximate it thanks to the interval prediction $[\underline{x}(t), \overline{x}(t)]$ of \autoref{sec:prediction}.
+In order to evaluate the robust objective $V^r$ \eqref{eq:robust-control}, we approximate it thanks to the interval prediction $[\underline{x}(t), \overline{x}(t)]$ of \autoref{sec:prediction}.
 
@@
 
-This amounts to a change of reward function, except the worst case is assessed over the whole past trajectory, which means that this pessimistic reward $\underline{R_n}$ is not \emph{markovian}.
+This amounts to changing the reward function, except that the worst case is assessed over the whole past trajectory, which makes this pessimistic reward $\underline{R_n}$ \emph{not markovian}.
 
@@
 In particular, we consider the \emph{Optimistic Planning of Deterministic Systems} (\texttt{OPD}) algorithm \citep{Hren2008} tailored for the case when the relationship between actions and rewards is deterministic.
-Indeed, the stochasticity of the perturbations and measurements is encased in $\hat{V}^r$: both the predictor dynamics \eqref{eq:interval-predictor} and the pessimistic rewards \eqref{eq:pessimistic-rewards} are deterministic.
+Indeed, the stochasticity of the perturbations and measurements is encased in $\hat{V}^r$: given the observations up to time $N$ both the predictor dynamics \eqref{eq:interval-predictor} and the pessimistic rewards \eqref{eq:pessimistic-rewards} are deterministic.
 
@@
 
-Given $N-1$ observations, the \autoref{sec:estimation} provides a polytopic confidence region \eqref{eq:polytope} that contains $A(\theta)$ with probability at least $1-\delta$.
+Given $N-1$ observations, \autoref{sec:estimation} provides a polytopic confidence region \eqref{eq:polytope} that contains $A(\theta)$ with probability at least $1-\delta$.
 Since the dynamics are linear, we can propagate this confidence region to the next observation: $y_{N}$ must belong to the Minkowski sum of a polytope representing model uncertainty $\cP(A_{0} x_N + Bu_N, \Delta A_{1}x_N,\dots, \Delta A_{2^d}x_N)$ and a polytope $\cP(0_p, \underline{\eta}, \overline{\eta})$ bounding the perturbation and measurement noises.
@@
 This objective could be optimised in the same way as in \autoref{sec:control}, but this would result in a coarse and lossy approximation.
-Instead, we can exploit the finite uncertainty structure of \autoref{assumpt:multi-model-ambiguity} to asymptotically recover the true $V^r$ by modifying the \texttt{OPD} algorithm in the following way:
+Instead, we exploit the finite uncertainty structure of \autoref{assumpt:multi-model-ambiguity} to asymptotically recover the true $V^r$ by modifying the \texttt{OPD} algorithm in the following way:
 
@@
 The solution of the robust objective \eqref{eq:robust-objective-discrete} with discrete ambiguity $f\in\{f^m\}_{m\in[M]}$ can be recovered exactly, asymptotically when the planning budget $K$ goes to infinity.
-This is in contrast to the results obtained in \autoref{sec:control} for the robust objective \eqref{eq:robust-control} with continuous ambiguity $A(\theta)\in\cC_{[N],\delta}$, for which \texttt{OPD} only recovers the surrogate approximation $\hat{V}^r$, as discussed in \autoref{thm:control-error}.
+This contrasts the results obtained in \autoref{sec:control} for the robust objective \eqref{eq:robust-control} with continuous ambiguity $A(\theta)\in\cC_{[N],\delta}$, for which \texttt{OPD} only recovers the surrogate approximation $\hat{V}^r$, as discussed in \autoref{thm:control-error}.
 Finally, the two approaches of Sections \ref{sec:control} and \ref{sec:multi-model} can be merged by using the pessimistic reward \eqref{eq:pessimistic-rewards} in \eqref{eq:robust-b-values}.
@@
 \section{Experiments}
+\label{sec:experiments}
 
@@
 
+Note that \autoref{assumpt:metzler} is always verified.
 The reward is non-smooth and encodes the task of reaching a goal state $x_g$ while avoiding collisions: $R(x) = \delta(x)/(1 + \|x - x_g\|_2)$  where $\delta(x)$ is $0$ whenever $x$ collides with an obstacle, $1$ otherwise.
@@
 -|D|^\transp P & \rho I_r\\
-\end{bmatrix} \geq 0 \]
-
-We recover \eqref{eq:lyap-bound} with $\mu = \frac{\lambda_{\min}(Q)}{\lambda_{\max}(P)} = \frac{\frac{1}{2}\lambda_{\min}(Q_0) - 4\alpha}{\lambda_{\max}(P)}$.
+\end{bmatrix} > 0 \]
+as it is assumed in the conditions of the lemma.
+Hence, under such a choice of $\alpha$ and $Q$, we recover $\Upsilon\leq 0$.
+\eqref{eq:lyap-bound} follows with $\mu = \frac{\lambda_{\min}(Q)}{\lambda_{\max}(P)} = \frac{\frac{1}{2}\lambda_{\min}(Q_0) - 4\alpha}{\lambda_{\max}(P)}$.
 Finally, we obtain
@@
 In both cases, the obtained polytope centre $A_0$ is non-Metzler.
-We use lemma \ref{lem:metzler} to compute a similarity transformation of coordinates.
+We use the similarity transformation of coordinates of \citet{Efimov2012}.
 Precisely, we ensure that the polytope is chosen so that its centre $A_0$ is diagonalisable having real eigenvalues, and perform an eigendecomposition to compute its change of basis matrix $S$.

### 2020-02-06 main.tex
~easily-evaluable~

@@
 In \autoref{sec:control}, facing a sequential decision problem with continuous states and discrete actions, we turn to the literature of tree-based planning algorithms.
-Our third contribution adapts them to the robust objective \eqref{eq:robust-control-disc} by approximating it with an easily-evaluable surrogate $\hat{V}^r$ that exploits the set predictor \eqref{eq:inclusion-generic} to define a pessimistic reward.
+Our third contribution adapts them to the robust objective \eqref{eq:robust-control-disc} by approximating it with a tractable surrogate $\hat{V}^r$ that exploits the set predictor \eqref{eq:inclusion-generic} to define a pessimistic reward.
 In our main result, we show that the best surrogate performance achieved during planning is guaranteed to be attained on the true system, and provide an upper bound for the approximation gap and simple regret of our framework in \autoref{thm:control-error}.

### 2020-02-06 main.tex
Last minute adjustments

@@
 The full procedure is designed to produce reasonable and safe behaviours at deployment while recovering an asymptotic optimality.
-We illustrate it on a practical case of autonomous driving at a crossroads intersection among vehicles with uncertain behaviours.\footnote[2]{Source code and videos are available in the supplementary materials}
+We illustrate it on a practical case of autonomous driving at a crossroads intersection among vehicles with uncertain behaviours.\footnote[2]{Source code and videos are available in the Supplementary Material}
 \end{abstract}
@@
 Most model-based reinforcement learning algorithms rely on the estimated dynamics to derive the corresponding optimal controls \citep[e.g.][]{Lenz2015,Levine2015}, but suffer from \emph{model bias}: they ignore the error that exists between the learned and true dynamics, which can dramatically degrade the control performances \citep{Schneider1997}.
-This is all the more relevant when maximising an objective under constraints --or penalties-- which naturally pushes the systems to operate in the vicinity of constraint saturation and makes it prone to failures.
+It is particularly likely when maximising an objective under constraints, which naturally pushes the systems to operate in the vicinity of constraint saturation and makes it prone to failure.
 
 To address this issue, we turn to the framework of \emph{robust} decision-making \citep{Bental2009,Bertsimas2011,Gorissen2015}: instead of merely considering a point estimate of the dynamics, we build an entire \emph{confidence region} that contains the true dynamics with high probability, and optimise the decisions so as to maximise the worst-case outcome with respect to this uncertainty.
-Maximin problems are hard to solve, and all the more in our setting where the reward function $R$ is generic.
+Maximin problems are notoriously hard to solve, and all the more in our setting where the reward function $R$ is generic.
 In particular, this excludes a number of tools from the robust synthesis literature, such as $\cH_\infty$ control \citep[see, e.g.][]{Basar1996} or system-level synthesis \citep{Dean2017,Dean2018}.
@@
 Tree-based planning algorithms are relevant in this context of discrete actions, but are only designed for a single known generative model instead of an entire confidence region for the system dynamics.
-Hence, we adapt them to the robust framework by following a two-steps procedure: we first predict a set of states that can be reached under a planned control sequence with respect to all possible dynamics.
+We adapt them to the robust framework by following a two-steps procedure: we first predict a set of states that can be reached under a planned control sequence with respect to all possible dynamics.
 This reachability set is used to provide a conservative pessimistic reward to the planning algorithm.
-The next subsection aims to clarify and formalize these ideas, and state our contributions.
+The next section aims to clarify and formalize these ideas, and state our contributions.
 
@@
 For any variable $z$, we use the subscript notation to refer to these discrete times: $z_n = z(t_n)$ with $t_n = n\dd t$ and $n\in\Natural$.
-We use bold symbols to denote temporal sequences $\bz = (z_n)_{n>N}$.
+We use bold symbols to denote temporal sequences $\bz = (z_n)_{n\in\Natural}$.
 We denote $z^+ = \max(z,0)$, $z^- = z^+-z$, $|z| = z^++z^-$ and $[n]=\{1,2,\dots, n\}$.
@@
 \paragraph{Structured dynamics}
-We consider a linear system with state $x\in\Real^p$, acted on by controls $u\in\Real^q$ and perturbations $\omega\in\Real^r$, and following a dynamics in the form:
+We consider a linear system with state $x\in\Real^p$, acted on by controls $u\in\Real^q$ and perturbations $\omega\in\Real^r$, and following dynamics in the form:
 \begin{equation}
@@
 
-In \autoref{sec:estimation}, having observed history of transitions $\cD_{[N]} = \{(x_n, y_n,u_n)\}_{n\in[N]}$, and given a confidence level $\delta\in(0, 1)$, our goal is to find a confidence region $\cC_{[N],\delta} \subset \Theta$ as tight as possible and such that it holds:
+In \autoref{sec:estimation}, having observed history of transitions $\cD_{[N]} = \{(x_n, y_n,u_n)\}_{n\in[N]}$, and given a confidence level $\delta\in(0, 1)$, we wish to find a confidence region $\cC_{[N],\delta} \subset \Theta$ as tight as possible and such that it holds:
 \begin{align}
@@
 		\STATE $\cC_{[N],\delta} \gets$\textsc{Model Estimation}$(\cD_{[N]})$. \eqref{eq:polytope}
-		\FOR{planning steps $k\in[K]$}
-		\FOR{each action $b\in A$}
+		\FOR{each planning step $k\in[K]$}
+		\FOR{each action $b\in \cA$}
 		\STATE $[\underline{x}_{n+1}, \overline{x}_{n+1}]\gets$ \textsc{Interval Prediction}(
@@
 		\ENDFOR
-		\STATE Execute the first recommended control $u_N$, and add the observed transition $(x_N, y_N)$ to $\cD_{[N+1]}$.
+		\STATE Execute the recommended control $u_{N+1}$, and add the observed transition $(x_{N+1}, y_{N+1}, u_{N+1})$ to $\cD_{[N+1]}$.
 		\ENDFOR
@@
 
-\paragraph{Linear-quadratic problems} There is a rich body of literature dedicated to the study of LQ systems, and we focus on those providing non-asymptotic results when the system parameters $A, B$ are unknown.
+\paragraph{Linear-quadratic problems} There is a rich body of literature dedicated to the study of linear systems with quadratic costs, and we focus on those providing non-asymptotic results when the system parameters $A, B$ are unknown.
 In their seminal work \citet{abbasi-yadkori11a}, consider the problem of cumulative regret minimisation.
-They follow the \emph{Optimism in the Face of Uncertainty} paradigm from the multi-armed bandit literature, that consists in selecting an optimistic system within a high-confidence region while enforcing a controllability constraint, and computing the corresponding optimal control in closed-form by solving a Riccati equation.
+They follow the \emph{Optimism in the Face of Uncertainty} paradigm from the multi-armed bandit literature, that consists in selecting the best possible dynamics within a high-confidence region while enforcing a controllability constraint, and computing the corresponding optimal control in closed-form by solving a Riccati equation.
 They show that this procedures achieves a $\tilde{\cO}\left(N^{1/2}\right)$ cumulative regret.
-\citet{abeille18a} provide the same result by applying Thomson Sampling rather of optimism to select a dynamical model, and rejection sampling to enforce the controllability constraint.
+\citep{Ibrahimi2013,Faradonbeh2017} adapt these results to the case of sparse dynamics.
+\citet{Ouyang2017,abeille18a} provide the same result by applying Thomson Sampling rather of optimism to select a dynamical model, and rejection sampling to enforce the controllability constraint.
 These methods aim at regret minimization to quickly reduce uncertainty, through information-seeking behaviours.
-Other works use noise injection for exploration such as \citep{Dean2017} or \citep{Dean2018}.
-However, being optimistic and minimising a cumulative regret does not fit a critical setting, where ensuring safety requires instead to consider the pessimistic outcomes.
-The work of \citet{Dean2017} is closest to our setting: after an offline estimation phase under random exploration, they estimate a simple regret between a robust controller and the oracle optimal performance.
-We also focus on applicability where previous methods often suffer from computationally intractable subroutines, with the exception of \cite{Dean2018} who provide a polynomial-time algorithm.
+Other works use noise injection for exploration such as \citep{Dean2017,Dean2018}.
+However, neither optimism and cumulative regret minimization nor random exploration fit a critical setting, where ensuring safety as a top priority requires instead to consider the pessimistic outcomes.
+The work of \citet{Dean2017} is closest to our setting: after an offline estimation phase, where the controls do not aim at regret minimization, they estimate a simple regret between a robust controller and the optimal performance.
+Our work mainly differs in that it addresses generic costs and forbids random exploration.
 
@@
 where $A_{0,N} = A + \theta_{N,\lambda}^\transp\phi, \Delta A_{i} = {h_i} \sqrt{\frac{\beta_N(\delta)}{\lambda_{\max}(G_{N,\lambda})}}, h_i\in\{-1,1\}^d$.
-Another strategy presented in Appendix \ref{sec:tight-polytope} produces a much tighter polytope, at the price of an increased computational cost required by the diagonalisation of $G_{N,\lambda}$.
+Another strategy presented in the Supplementary Material produces a much tighter polytope, at the price of an increased computational cost required by the diagonalisation of $G_{N,\lambda}$.
 
 \paragraph{Remark} The robust objective \eqref{eq:robust-control} involves bounds $\underline{\omega}(t)\leq \omega(t) \leq \overline{\omega}(t)$ over the possible perturbations we want to protect against.
-In the unbounded sub-Gaussian noise setting of \autoref{assumpt:gaussian-noise}, we can use the same formulation by deriving local high-confidence bounds that each holds with probability $\delta_n$.
+In the unbounded sub-Gaussian noise setting of \autoref{assumpt:gaussian-noise}, we can use the same formulation by deriving local high-confidence bounds that each holds with confidence $\delta_n$.
 By choosing $\delta_n = \frac{\delta}{n(n+1)}$, the event $\{\forall n, \underline{\omega}(t_n) \leq \omega(t_n) \leq \overline{\omega}(t_n)\}$ holds with probability $1-\delta$.
@@
 
-A simple solution to \eqref{eq:inclusion-property} is proposed in \citep{efimov:hal-00701643}, where, given bounds $\underline{A}\leq A(\theta)\leq\overline{A}$ from $\cC_{[N],\delta}$ they use matrix interval arithmetics to derive the predictor:
-\begin{proposition}[Simple predictor of \citealt{efimov:hal-00701643}]
+A simple solution to \eqref{eq:inclusion-property} is proposed in \citep{Efimov2012}, where, given bounds $\underline{A}\leq A(\theta)\leq\overline{A}$ from $\cC_{[N],\delta}$ they use matrix interval arithmetic to derive the predictor:
+\begin{proposition}[Simple predictor of \citealt{Efimov2012}]
 Assuming that \eqref{eq:confidence} is satisfied for the system \eqref{eq:dynamics}, then the interval predictor:
@@
 In practice, this assumption is often verified.
-It is for instance the case whenever $A_0$ is diagonalisable, and a fortiori when it is stabilisable.
-The similarity transformation of \citep{Efimov_a2013} provides a method to compute such $Z$.
+It is for instance the case whenever $A_0$ is diagonalisable.
+The similarity transformation of \citep{Efimov2013} provides a method to compute such $Z$ when the system is observable.
 To simplify the notation, we will further assume that $Z = I_p$.
@@
 
-\begin{proposition}[Enhanced Predictor of \citealt{leurent2019interval}]
+\begin{proposition}[Enhanced predictor of \citealt{leurent2019interval}]
 \label{thm:predictor}
@@
     \vspace{-0.7cm}
-	\caption{Comparison of \eqref{eq:predictor-naive} to \eqref{eq:interval-predictor} for a simple system \\$\dot{x}(t)=-\theta x(t)+\omega(t)$, with $\theta\in[1, 2]$ and $\omega(t) \in [-0.05, 0.05]$.}
+	\caption{Comparison of \eqref{eq:predictor-naive} and \eqref{eq:interval-predictor} for a simple system \\$\dot{x}(t)=-\theta x(t)+\omega(t)$, with $\theta\in[1, 2]$ and $\omega(t) \in [-0.05, 0.05]$.}
 	\label{fig:predictor_example}
@@
 
-\autoref{fig:predictor_example} illustrates the differences of stability of the two predictors with a simple example.
+\autoref{fig:predictor_example} illustrates the difference of stability of the two predictors \eqref{eq:predictor-naive} and \eqref{eq:interval-predictor} with a simple example.
 It suggests to always prefer \eqref{eq:interval-predictor} whenever \autoref{assumpt:metzler} is verified, and only fallback to \eqref{eq:predictor-naive} as a last resort.
@@
 \begin{definition}[Surrogate objective]
+	Let
 \begin{align}
-\underline{R}_n(\bu) \eqdef \min_{x\in[\underline{x}_n(\bu), \overline{x}_n(\bu)]}  R(x) \label{eq:pessimistic-rewards} \\
-\hat{V}^r(\bu) \eqdef \sum_{n=N+1}^\infty \gamma^n \underline{R}_n(\bu) \label{eq:surrogate_objective}
+\label{eq:surrogate_objective} 
+\hat{V}^r(\bu) &\eqdef \sum_{n=N+1}^\infty \gamma^n \underline{R}_n(\bu)\\ 
+\text{where}\quad\underline{R}_n(\bu) &\eqdef \min_{x\in[\underline{x}_n(\bu), \overline{x}_n(\bu)]}  R(x) \label{eq:pessimistic-rewards}
 \end{align}
-where $\underline{x}_n(\bu), \overline{x}_n(\bu)$ follow the dynamics defined in \eqref{eq:interval-predictor}.
+and $\underline{x}_n(\bu), \overline{x}_n(\bu)$ follow the dynamics defined in \eqref{eq:interval-predictor}.
 \end{definition}
@@
 \label{prop:lower-bound}
-The surrogate objective  \eqref{eq:surrogate_objective} is a lower bound of the true objective  \eqref{eq:robust-control-disc} with probability at least $1-\delta$: 
+The surrogate objective  \eqref{eq:surrogate_objective} is a lower bound of the true objective  \eqref{eq:robust-control-disc}: 
 \begin{equation*}
@@
 \end{proposition}
-
-A direct consequence is that since all our approximations were conservative, if we manage to find a control sequence such that no \textit{``bad event''} (e.g.
+A direct consequence is that since all our approximations are conservative, if we manage to find a control sequence such that no \textit{``bad event''} (e.g.
 a collision) happens according to the surrogate objective $\hat{V}^r$, then we are guaranteed that they will not happen either when the controls are executed on the true system.
@@
 
-The procedure we developed in sections \ref{sec:estimation}, \ref{sec:prediction} and \ref{sec:control} relies on strong modelling assumptions, such as the linear dynamics \eqref{eq:dynamics} or \autoref{assumpt:structure}.
+The procedure we developed in sections \ref{sec:estimation}, \ref{sec:prediction} and \ref{sec:control} relies on strong modelling assumptions, such as the linear dynamics \eqref{eq:dynamics} and \autoref{assumpt:structure}.
 But what if they are wrong?
@@
 \end{definition}
-An illustration of the computation of the robust b-values is presented in Figure \ref{fig:drop}.
-Note that it is not equivalent to solving each control problem independently and following the action with highest mininimal value, as we illustrate in \autoref{sec:min-max-order}.
+An illustration of the computation of the robust upper-bounds is presented in Figure \ref{fig:drop}.
+Note that it is not equivalent to solving each control problem independently and following the action with highest worst-case value, as we show in the Supplementary Material.
 We analyse the sample complexity of the corresponding robust planning algorithm.
@@
 \label{theorem:drop-regret}
-The robust version of \texttt{OPD} \eqref{eq:robust-b-values} enjoys the same regret bound as that of \texttt{OPD} in \autoref{theorem:opd-regret}, with respect to the robust objective \eqref{eq:robust-objective-discrete}.
+The robust version of \texttt{OPD} \eqref{eq:robust-b-values} enjoys the same regret bound as \texttt{OPD} in \autoref{theorem:opd-regret}, with respect to the multi-model objective \eqref{eq:robust-objective-discrete}.
 \end{theorem}
@@
 Note that \autoref{assumpt:metzler} is always verified.
-The reward is non-smooth and encodes the task of reaching a goal state $x_g$ while avoiding collisions: $R(x) = \delta(x)/(1 + \|x - x_g\|_2)$  where $\delta(x)$ is $0$ whenever $x$ collides with an obstacle, $1$ otherwise.
+The reward is non-smooth and encodes the task of navigating to reach a goal state $x_g$ while avoiding collisions with obstacles: $R(x) = \delta(x)/(1 + \|x - x_g\|_2)$  where $\delta(x)$ is $0$ whenever $x$ collides with an obstacle, $1$ otherwise.
 The actions $\cA$ are constant controls in the up, down, left and right directions.
@@
 the non-robust adaptive control approach that plans with the estimated dynamics $\theta_{[N],\lambda}$.
-We observe that though the robust agent performs worse than the nominal agent on average, it manages to ensure safety and attains a better worst-case performance.
+We observe that though the robust agent performs worse than the nominal agent on average, it manages to ensure safety and attains a better worst-case performance, as intended.
 We also study the evolution of the simple regret $V(x_n) - J_n(x_n)$ with respect to the number of samples $N$, where $J_n(x_n) = \sum_{i > n} \gamma^i R_i$ is the empirical return at state $x_n$ in a trajectory $x_0, R_0, x_1, R_1, \dots$, while $V(x_n)$ is the optimal value that the agent would get by acting optimally from $x_n$ with knowledge of the dynamics.
@@
 We consider the \href{https://github.com/eleurent/highway-env}{highway-env} environment \citep{highway-env} for simulated driving decision problems.
-An autonomous vehicle is approaching an intersection among $V$ other vehicles, resulting in a joint traffic state $x = [\chi_0, \dots,\chi_V]^\top\in\Real^{4V+4}$.
+An autonomous vehicle with state $\chi_0\in\Real^4$ is approaching an intersection among $V$ other vehicles with states $\chi_i\in\Real^4$, resulting in a joint traffic state $x = [\chi_0, \dots,\chi_V]^\top\in\Real^{4V+4}$.
 These vehicles follow parametrized behaviours $\dot{\chi}_i=f_i(x,\theta_i)$ with unknown parameters $\theta_i\in\Real^5$.
@@
 \citep{Dean2018,abeille18a} reported numerical experiments with states of dimensions 3 and 4, respectively.
-This system dynamics $f$ can only be expressed in the form of \autoref{assumpt:structure} given the knowledge of the desired route for each vehicle, with features $\phi$ expressing deviations to the centerline of the followed lane.
+The system dynamics $f$, which describes the couplings and interactions between vehicles, can only be expressed in the form of \autoref{assumpt:structure} given the knowledge of the desired route for each vehicle, with features $\phi$ expressing deviations to the centerline of the followed lane.
 Since these intentions are unknown to the agent, we adopt the multi-model perspective of \autoref{sec:multi-model} and consider one model per possible route for every observed vehicle before an intersection.
@@
 There performances are compared in \autoref{tab:driving}.
-Again, the robust approach is less efficient on average than planning with the nominal model, but it does better in terms of worst-case performance and avoids collisions, contrary to the nominal baselines that suffer from model bias.
+Again, the robust approach is less efficient on average than planning with a nominal model, but it does better in terms of worst-case performance and manages to avoid collisions, contrary to the nominal baselines that suffer from model bias.
+We provide more details about the system and videos of the experiments in the Supplementary Material.
 
@@
 
+\clearpage
 \bibliography{references}
@@
 
-In the following, we describe the structure of the model representing the dynamics of of several vehicles driving and interacting with one another.
+In the following, we describe the structure of the model representing the dynamics of several vehicles driving and interacting with one another.
 
@@
 
-The kinematics of any vehicle $i\in\overline{1,V}$ are represented by the Kinematic Bicycle Model:
+The kinematics of any vehicle $i\in[V]$ are represented by the Kinematic Bicycle Model:
 \begin{align}
@@
 \subsection{Longitudinal control}
-Longitudinal behaviour is modelled by a linear controller using three features inspired from the intelligent driver model (IDM) \cite{Treiber2000}: a desired velocity, a braking term to drive slower than the front vehicle, and a braking term to respect a safe distance to the front vehicle.
+Longitudinal behaviour is modelled by a linear controller using three features: a desired velocity, a braking term to drive slower than the front vehicle, and a braking term to respect a safe distance to the front vehicle.
 
@@
 In both cases, the obtained polytope centre $A_0$ is non-Metzler.
-We use the similarity transformation of coordinates of \citet{Efimov2012}.
-Precisely, we ensure that the polytope is chosen so that its centre $A_0$ is diagonalisable having real eigenvalues, and perform an eigendecomposition to compute its change of basis matrix $S$.
+We use the similarity transformation of coordinates of \citet{Efimov2013}.
+Precisely, we choose $\Theta$ such that for any $\theta\in\Theta$, $A(\theta)$ is always diagonalisable with real eigenvalues, and perform an eigendecomposition to compute its change of basis matrix $S$.
 The transformed system $Z'=S^{-1}(Z-Z_c)$ verifies \eqref{eq:confidence} with $A_0$ Metlzer as required to apply the interval predictor of Theorem~\ref{thm:predictor}.

### 2020-02-07 main.tex
Submission version
Update supplementary

@@
 \usepackage{enumitem}
+\usepackage{comment}
 \def\sectionautorefname{Section}
 \input{mathdef.tex}
-\newcommand{\todo}[1]{\textcolor{red}{#1}}
 
@@
 \begin{proposition}[Enhanced predictor of \citealt{leurent2019interval}]
-\label{thm:predictor}
+\label{prop:predictor}
 Assuming that \eqref{eq:polytope} and \autoref{assumpt:metzler} are satisfied for the system \eqref{eq:dynamics}, then the interval predictor:
@@
 \clearpage
+\onecolumn
 \appendix
 
+\begin{center}
+	\LARGE Supplementary Material
+\end{center}
+
+\paragraph{Outline}
+In \autoref{sec:proof}, we provide a proof for every novel result introduced in this paper.
+\autoref{sec:tight-polytope} describes a better method of conversion from ellipsoid to polytope than that of \eqref{eq:polytope}.
+\autoref{sec:min-max-order} highlights the fact that robustness cannot be recovered by aggregating independent solutions to many optimal control problem.
+Finally, \autoref{sec:experimental-setting} gives additional details on the setting of our experiments.
+
 \section{Proofs}
+\label{sec:proof}
 
@@
 
-\begin{proposition}[Theorem 1 of \citep{Abbasi2011}, Matrix version]
+\begin{proposition}[Matrix version of Theorem 1 of \citealt{Abbasi2011}]
 \label{prop:concentration}
@@
 	\label{eq:max_vr}
-	V_a^r \eqdef \max_{\bu \in a\mathcal{A^\infty}} \min_{m\in[1, M]} \sum_{n=h(a)+1}^\infty \gamma^n R^m_n
+	V_a^r \eqdef \max_{\bu \in a\mathcal{A^\infty}} \min_{m\in[M]} \sum_{n=h(a)+1}^\infty \gamma^n R^m_n
 	\end{equation}
@@
 	\label{eq:ur}
-	U_a^r(T)  \eqdef
+	U_a^r(K)  \eqdef
 	\begin{cases}
@@
 
-	Then, the robust values, U-values and B-values exhibit similar properties as the optimal values, U-values and B-values, that is: for all $0 < t < T$ and $a\in\mathcal{T}_T$,
-	\begin{equation}
-	U^r_a(t) \leq U^r_a(T) \leq V^r_a \leq B^r_a(T) \leq B^r_a(t)
+	Then, the robust values, U-values and B-values exhibit similar properties as the optimal values, U-values and B-values, that is: for all $0 < k < K$ and $a\in\mathcal{T}_T$,
+	\begin{equation}
+	U^r_a(k) \leq U^r_a(K) \leq V^r_a \leq B^r_a(K) \leq B^r_a(k)
 	\end{equation}
@@
 \begin{proof}
-	By definition, when starting with sequence $i$, the value $U_i^m(n)$ represents the minimum admissible reward, while $B_i^m(n)$ corresponds to the best admissible reward achievable with respect to the the possible continuations of $i$.
-Thus, for all $i\in\mathcal{A}^*$, $U_i^m(n)$ and $U_i^r(n)$ are non-decreasing functions of $n$ and $b_i^m(n)$ and $B_i^r(n)$ are a non-increasing functions of $n$, while $V_i^m$ and $V_i^r$ do not depend on $n$.
-
-	Moreover, since the reward function $R$ is assumed to have values in $[0, 1]$, the sum of discounted rewards from a node of depth $d$ is at most $\gamma^d + \gamma^{d+1}+\dots = \frac{\gamma^d}{1-\gamma}$.
-As a consequence, for all $n \geq 0$ , $i\in\mathcal{L}_n$ of depth $d$, and any sequence of rewards $(R_t)_{t\in\mathbb{N}}$ obtained from following a path in $i\mathcal{A}^\infty$ with any dynamics $m \in [1, M]$:
-
-	\begin{equation*}
-	\sum_{t=0}^{d-1} \gamma^t R_t \leq \sum_{t=0}^{d-1} \gamma^t R_t + \sum_{t=d}^\infty \gamma^t R_t \leq \sum_{t=0}^{d-1} \gamma^t R_t + \frac{\gamma^d}{1-\gamma}
-	\end{equation*}
-	That is equivalent to:
-	\begin{equation*}
-	U^m_i(n) \leq \sum_{t=0}^\infty \gamma^t R_t \leq B^m_i(n) 
+	By definition, when starting with sequence $a$, the value $U_a^m(k)$ represents the minimum admissible reward, while $B_a^m(k)$ corresponds to the best admissible reward achievable with respect to the the possible continuations of $a$.
+Thus, for all $a\in\mathcal{A}^*$, $U_a^m(k)$ and $U_a^r(k)$ are non-decreasing functions of $k$ and $B_a^m(k)$ and $B_a^r(k)$ are a non-increasing functions of $k$, while $V_a^m$ and $V_a^r$ do not depend on $k$.
+
+	Moreover, since the reward function $R$ is assumed be bounded in $[0, 1]$, the sum of discounted rewards from a node of depth $d$ is at most $\gamma^d + \gamma^{d+1}+\dots = \frac{\gamma^d}{1-\gamma}$.
+As a consequence, for all $k \geq 0$ , $a\in\mathcal{L}_k$ of depth $d$, and any sequence of rewards $(R_n)_{n\in\mathbb{N}}$ obtained from following a path in $a\mathcal{A}^\infty$ with any dynamics $m \in [M]$:
+
+	\begin{equation*}
+	U^m_a(k) = \sum_{n=0}^{d-1} \gamma^n R_n^m \leq \sum_{n=0}^\infty \gamma^n R_n^m \leq \sum_{n=0}^{d-1} \gamma^n R_n^m + \frac{\gamma^d}{1-\gamma} = B^m_a(k) 
 	\end{equation*}
@@
 	\label{eq:min_m_values}
-	\min_{m \in [1, M]} U^m_i(n) \leq \min_{m \in [1, M]} \sum_{t=0}^\infty \gamma^t R_t \leq \min_{m \in [1, M]} B^m_i(n)
-	\end{equation}
-	And as the left-hand and right-hand sides of \eqref{eq:min_m_values} are independent of the particular path that was followed in $i\mathcal{A}^\infty$, it also holds for the robust path:
-
-	\begin{equation*}
-	\min_{m \in [1, M]} U^m_i(n) \leq \max_{\pi\in i\mathcal{A}^\infty} \min_{m \in [1, M]} \sum_{t=0}^\infty \gamma^t R_t \leq \min_{m \in [1, M]} B^m_i(n)
+	\min_{m \in [M]} U^m_a(k) \leq \min_{m \in [M]} \sum_{n=0}^\infty \gamma^n R_n \leq \min_{m \in [M]} B^m_a(k)
+	\end{equation}
+	And as the left-hand and right-hand sides of \eqref{eq:min_m_values} are independent of the particular path that was followed in $a\mathcal{A}^\infty$, it also holds for the robust path:
+
+	\begin{equation*}
+	\min_{m \in [M]} U^m_i(k) \leq \max_{a'\in a\mathcal{A}^\infty} \min_{m \in [M]} \sum_{t=0}^\infty \gamma^n R_n^m \leq \min_{m \in [M]} B^m_i(k)
 	\end{equation*}
@@
 	\label{eq:urvrbr}
-	U^r_i(n) \leq V^r_i  \leq B^r_i(n)
-	\end{equation}
-
-	Finally, \eqref{eq:urvrbr} is extended to the rest of $\mathcal{T}_n$ by recursive application of \eqref{eq:max_vr}, \eqref{eq:ur} and \eqref{eq:br}.
+	U^r_a(k) \leq V^r_a  \leq B^r_a(k)
+	\end{equation}
+
+	Finally, \eqref{eq:urvrbr} is extended to the rest of $\mathcal{T}_k$ by recursive application of \eqref{eq:max_vr}, \eqref{eq:ur} and \eqref{eq:br}.
 \end{proof}
@@
 \begin{proof}
-	\citet{Hren2008} first show in Theorem 2 that the simple regret of their optimistic planner is bounded by $\frac{\gamma^{d_n}}{1 - \gamma}$ where $d_n$ is the depth of $\mathcal{T}_n$.
+	\citet{Hren2008} first show in Theorem 2 that the simple regret $r_K$ of their optimistic planner is bounded by $\frac{\gamma^{d_K}}{1 - \gamma}$ where $d_K$ is the depth of $\mathcal{T}_K$.
 This properties relies on the fact that the returned action belongs to the deepest explored branch, which we can show likewise by contradiction using Lemma \ref{lemma:uvb}.
-This yields directly that $a = i_0$ where $i$ is some node of maximal depth $d_n$ expanded at round $t\leq n$, which by selection rule verifies $B_a^r(t) = B_i^r(t) = \max_{x\in\mathcal{A}} B_x^r(t)$ and:
+This yields directly that the returned action $a = i_0$ where $i$ is some node of maximal depth $d_K$ expanded at round $k\leq K$, which by selection rule verifies $B_a^r(k) = B_i^r(k) = \max_{x\in\mathcal{A}} B_x^r(k)$ and:
 	\begin{align*}
 	\label{eq:Rndn}
-	V^r - V_a^r = V_{a^{\star}}^r - V_a^r  \leq B_{a^{\star}}^r(t) - V_a^r &\leq B_{a}^r(t) - U_a^r(t) \\
-	&= B_{i}^r(t) - U_i^r(t) \\
-	&= \frac{\gamma^{d_n}}{1-\gamma}.
-	\end{align*}
-
-	Secondly, they bound the depth $d_n$ of $\mathcal{T}_n$ with respect to $n$.
+	V^r - V_a^r = V_{a^{\star}}^r - V_a^r  \leq B_{a^{\star}}^r(k) - V_a^r &\leq B_{a}^r(k) - U_a^r(k) \\
+	&= B_{i}^r(k) - U_i^r(k) \\
+	&= \frac{\gamma^{d_K}}{1-\gamma}.
+	\end{align*}
+
+	Secondly, they bound the depth $d_K$ of $\mathcal{T}_K$ with respect to $K$.
 To that end, they show that the expanded nodes always belong to the sub-tree $\mathcal{T}_\infty$ of all the nodes of depth $d$ that are $\frac{\gamma^d}{1-\gamma}$-optimal.
-Indeed, if a node $i$ of depth $d$ is expanded at round $n$, then $B_i^r(n) \geq B_j^r(n)$ for all $j\in \mathcal{L}_n$ by selection rule, thus the max-backups of \eqref{eq:robust-b-values} up to the root yield $B^r_i(n) = B_\emptyset^r(n)$.
-Moreover, by Lemma \ref{lemma:uvb} we have that $B_\emptyset^r(n) \geq V_\emptyset^r = V^r$ and so $V_i^r \geq U_i^r(n) = B_i^r(n) - \frac{\gamma^d}{1-\gamma} \geq V^r - \frac{\gamma^d}{1-\gamma}$, thus $i \in \mathcal{T}_\infty$.
+Indeed, if a node $i$ of depth $d$ is expanded at round $k$, then $B_i^r(k) \geq B_j^r(k)$ for all $j\in \mathcal{L}_k$ by selection rule, thus the max-backups of \eqref{eq:robust-b-values} up to the root yield $B^r_i(k) = B_\emptyset^r(k)$.
+Moreover, by Lemma \ref{lemma:uvb} we have that $B_\emptyset^r(k) \geq V_\emptyset^r = V^r$ and so $V_i^r \geq U_i^r(k) = B_i^r(k) - \frac{\gamma^d}{1-\gamma} \geq V^r - \frac{\gamma^d}{1-\gamma}$, thus $i \in \mathcal{T}_\infty$.
 
@@
 	\begin{eqnarray*}
-		n &= \sum_{d=0}^{d_n} n_d = n_0 + \sum_{d=d_0+1}^{d_n} n_d \\
-		&\leq n_0 + c\sum_{d={d_0+1}}^{d_n} \kappa^d
+		K &= \sum_{d=0}^{d_K} n_d = n_0 + \sum_{d=d_0+1}^{d_K} n_d \leq n_0 + c\sum_{d={d_0+1}}^{d_K} \kappa^d.
 	\end{eqnarray*}
-	where $c'=\frac{c}{(1-\gamma)^\beta}$.
 
 	\begin{itemize}
-		\item If $\kappa > 1$, then $n \leq n_0 + c'\kappa^{d_0+1}\frac{\kappa^{d_n-d_0}-1}{\kappa-1}$ and thus $d_n \geq d_0 + \log_\kappa \frac{(n-n_0)(\kappa - 1)}{c'\kappa^{d_0+1}}$.
-		We conclude that $\mathcal{R}_n \leq \frac{\gamma^{d_n}}{1-\gamma} = \frac{1}{1-\gamma} \left( \frac{(n-n_0)(\kappa - 1)}{c'\kappa^{d_0+1}} \right)^\frac{\log \gamma}{\log \kappa} = O\left(n^{-\frac{\log 1/\gamma}{\log \kappa}}\right)$.
-
-		\item If $\kappa = 1$, then $n \leq n_0 + c'(d_n-d_0)$, hence we have $\mathcal{R}_n = O\left(\gamma^{nc'}\right)$.
+		\item If $\kappa > 1$, then $K \leq n_0 + c\kappa^{d_0+1}\frac{\kappa^{d_K-d_0}-1}{\kappa-1}$ and thus $d_K \geq d_0 + \log_\kappa \frac{(K-n_0)(\kappa - 1)}{c\kappa^{d_0+1}}$.
+
+		We conclude that $r_K \leq \frac{\gamma^{d_K}}{1-\gamma} = \frac{1}{1-\gamma} \left( \frac{(K-n_0)(\kappa - 1)}{c\kappa^{d_0+1}} \right)^\frac{\log \gamma}{\log \kappa} = \cO\left(K^{-\frac{\log 1/\gamma}{\log \kappa}}\right)$.
+
+		\item If $\kappa = 1$, then $K \leq n_0 + c(d_K-d_0)$, hence we have $r_K = O\left(\gamma^{Kc}\right)$.
 	\end{itemize}
@@
 
+\section{A tighter conversion from ellipsoid to polytope}
+\label{sec:tight-polytope}
+\begin{lemma}[Confidence polytope]
+	\label{lem:tight_polytope}
+	We can enclose the confidence ellipsoid obtained in $\eqref{eq:confidence-ellipsoid}$ within a polytope $C_\delta$:
+	\begin{equation}
+	\cC_\delta = \left\{ A_{1}+\sum_{i=1}^{2^d}\lambda_{i}\Delta A_{i}: \lambda\in[0, 1]^{2^d},  \sum_{i=1}^{2^d}\lambda_{i}=1\right\}.
+	\end{equation}
+	with 
+	\begin{align*}
+	&h_k \text{ is the }k^\text{th}\text{ element of }\{-1,1\}^d\text{ for } k\in[2^d],\\
+	&G_{N,\lambda} = PDP^{-1}, \quad \Delta\theta_k = \beta_{N}(\delta)^{1/2} P^{-1}D^{-1/2} h_k, \\
+	&A_0 = A + \theta_{N,\lambda}^\transp\Phi, \quad \Delta A_k = \Delta\theta_k^\transp\Phi.
+	\end{align*}
+	This conversion is illustrated in \autoref{fig:ellipsoid_to_polytope}.
+\end{lemma}
+
+\begin{proof}
+	The ellipsoid in \eqref{eq:confidence-ellipsoid} is described by:
+	\begin{align*}
+	\theta\in\cC_\delta &\implies
+	(\theta-\theta_{N,\lambda})^\transp G_{N,\lambda}(\theta-\theta_{N,\lambda}) \leq \beta_{N}(\delta)\\
+	&\implies (\theta'-\theta'_{N,\lambda})^\transp D (\theta'-\theta'_{N,\lambda}) \leq \beta_{N}(\delta)\\
+	&\implies \sum_{i=1}^d D_{i,i}(\theta'_i-\theta'_{N,\lambda,i})^2\leq \beta_{N}(\delta)\\
+	&\implies\forall i, |\theta'_i-\theta'_{N,\lambda,i}|\leq \beta_{N}(\delta)^{1/2}D_{i,i}^{-1/2}
+	\end{align*}
+	This describes a $\Real^d$ box containing $\theta' = P\theta$, whose $k^\text{th}$ vertex is represented by $\theta_{N,\lambda}' + \beta_{N}(\delta)^{1/2}D^{-1/2} h_k$.
+We obtain the corresponding box on $\theta$ by transforming each vertex of the box with $P^{-1}$.
+\end{proof}
+
+\begin{figure}
+	\centering
+	\includegraphics[trim={3.8cm, 2cm, 5cm, 3.8cm}, clip, width=0.7\linewidth]{img/ellipsoid_to_polytope}
+	\caption{From the confidence ellipsoid $\cC_\delta$ to its enclosing polytope $\cP_\delta$}
+	\label{fig:ellipsoid_to_polytope}
+\end{figure}
+
 \section{On the ordering of min and max}
@@
 
-	In the definition of $B_{i}^{r}(n)$ and $U_{i}^{r}(n)$ it is essential that the minimum among the models is only taken at the end of trajectories, in the same way as for the robust objective \eqref{eq:robust-objective-discrete} in which the worst-case dynamics is only determined after the action sequence has been fully specified.
-Assume that $U_{a}^{r}(n)$ is instead naively defined as:
+	In the definition of $B_{a}^{r}(k)$ \eqref{eq:br} and $U_{a}^{r}(k)$ \eqref{eq:ur} it is essential that the minimum over the models is only taken at the end of trajectories, in the same way as for the robust objective \eqref{eq:robust-objective-discrete} in which the worst-case dynamics is only determined after the action sequence has been fully specified.
+Assume that $U_{a}^{r}(k)$ is instead naively defined as:
 
 	\[
-	U_{a}^{r}(n)=\min_{m\in[1,M]}U_{a}^{m}(n),
+	U_{a}^{r}(k)=\min_{m\in[1,M]}U_{a}^{m}(k),
 	\]
@@
 
-\section{The use case of autonomous driving}
-
-In the following, we describe the structure of the model representing the dynamics of several vehicles driving and interacting with one another.
-
-\subsection{Kinematics}
+\section{Experimental setting}
+\label{sec:experimental-setting}
+
+In both experiments, we used $\gamma=0.9$ and $\delta=0.9$.
+The perturbations were sampled uniformly in $[-0.1, 0.1]^r$ while the measurements are gaussian with covariance $\Sigma_r = 0.1 I_s$.
+
+\subsection{Autonomous Driving}
+
+In the following, we describe the structure of the dynamical system $f$ representing the couplings and interactions between several vehicles.
+
+\paragraph{Kinematics}
 
@@
 
-\subsection{Longitudinal control}
+\paragraph{Longitudinal control}
 Longitudinal behaviour is modelled by a linear controller using three features: a desired velocity, a braking term to drive slower than the front vehicle, and a braking term to respect a safe distance to the front vehicle.
@@
 
-\subsection{Lateral control}
+\paragraph{Lateral control}
 
@@
 
-\subsection{LPV formulation}
+\paragraph{LPV formulation}
 
@@
 
-It can be rewritten in the form $$\dot{Z} = A(\theta)(Z-Z_c) + d.$$ For example, in the case of two vehicles only:
-\begin{equation*}
-    Z = \begin{bmatrix}
+It can be rewritten in the form $$\dot{X} = A(\theta)(X-X_c) + \omega.$$ For example, in the case of two vehicles only:
+\begin{equation*}
+    X = \begin{bmatrix}
 x_i \\
@@
 ,\quad
-Z_c = \begin{bmatrix}
+X_c = \begin{bmatrix}
 -d_0-v_0 T \\
@@
 ,\quad
-d = \begin{bmatrix}
+\omega = \begin{bmatrix}
 v_0 \\
@@
 
-\subsection{Tighter conversion form ellipsoid to polytope}
-\label{sec:tight-polytope}
-\begin{lemma}[Confidence polytope]
-\label{lem:tight_polytope}
-We can enclose the confidence ellipsoid obtained in $\eqref{eq:confidence-ellipsoid}$ within a polytope $C_\delta$:
-\begin{equation}
-     \cC_\delta = \left\{ A_{1}+\sum_{i=1}^{2^d}\lambda_{i}\Delta A_{i}: \lambda\in[0, 1]^{2^d},  \sum_{i=1}^{2^d}\lambda_{i}=1\right\}.
-\end{equation}
-with 
-\begin{align*}
-    &h_k \text{ is the }k^\text{th}\text{ element of }\{-1,1\}^d\text{ for } k\in[2^d],\\
-    &G_{N,\lambda} = PDP^{-1}, \quad \Delta\theta_k = \beta_{N}(\delta)^{1/2} P^{-1}D^{-1/2} h_k, \\
-    &A_0 = A + \theta_{N,\lambda}^\transp\Phi, \quad \Delta A_k = \Delta\theta_k^\transp\Phi.
-\end{align*}
-This conversion is illustrated in \autoref{fig:ellipsoid_to_polytope}.
-\end{lemma}
-
-\begin{proof}
-The ellipsoid in \eqref{eq:confidence-ellipsoid} is described by:
-\begin{align*}
-    \theta\in\cC_\delta &\implies
-    (\theta-\theta_{N,\lambda})^\transp G_{N,\lambda}(\theta-\theta_{N,\lambda}) \leq \beta_{N}(\delta)\\
-    &\implies (\theta'-\theta'_{N,\lambda})^\transp D (\theta'-\theta'_{N,\lambda}) \leq \beta_{N}(\delta)\\
-    &\implies \sum_{i=1}^d D_{i,i}(\theta'_i-\theta'_{N,\lambda,i})^2\leq \beta_{N}(\delta)\\
-    &\implies\forall i, |\theta'_i-\theta'_{N,\lambda,i}|\leq \beta_{N}(\delta)^{1/2}D_{i,i}^{-1/2}
-\end{align*}
-This describes a $\Real^d$ box containing $\theta' = P\theta$, whose $k^\text{th}$ vertex is represented by $\theta_{N,\lambda}' + \beta_{N}(\delta)^{1/2}D^{-1/2} h_k$.
-We obtain the corresponding box on $\theta$ by transforming each vertex of the box with $P^{-1}$.
-\end{proof}
-
-\begin{figure}
-    \centering
-    \includegraphics[trim={3.8cm, 2cm, 5cm, 3.8cm}, clip, width=0.4\textwidth]{img/ellipsoid_to_polytope}
-    \caption{From the confidence ellipsoid $\cC_\delta$ to its enclosing polytope $\cP_\delta$}
-    \label{fig:ellipsoid_to_polytope}
-\end{figure}
-
-\subsection{Change of coordinates}
+\paragraph{Change of coordinates}
 In both cases, the obtained polytope centre $A_0$ is non-Metzler.
 We use the similarity transformation of coordinates of \citet{Efimov2013}.
-Precisely, we choose $\Theta$ such that for any $\theta\in\Theta$, $A(\theta)$ is always diagonalisable with real eigenvalues, and perform an eigendecomposition to compute its change of basis matrix $S$.
-The transformed system $Z'=S^{-1}(Z-Z_c)$ verifies \eqref{eq:confidence} with $A_0$ Metlzer as required to apply the interval predictor of Theorem~\ref{thm:predictor}.
+Precisely, we choose $\Theta$ such that for any $\theta\in\Theta$, $A(\theta)$ is always diagonalisable with real eigenvalues, and perform an eigendecomposition to compute its change of basis matrix $Z$.
+The transformed system $X'=Z^{-1}(X-X_c)$ verifies \eqref{eq:confidence} with $A_0$ Metlzer as required to apply the interval predictor of \autoref{prop:predictor}.
 Finally, the obtained predictor is transformed back to the original coordinates $Z$ by using the following lemma:
-\begin{lemma}[Interval arithmerics of \citealt{Efimov2012}]
+\begin{lemma}[Interval arithmetic of \citealt{Efimov2012}]
 	 \label{lem:interval} Let $x\in\mathbb{R}^{n}$ be a vector variable, $\underline{x}\le x\le\overline{x}$ for some $\underline{x},\overline{x}\in\mathbb{R}^{n}$.
@@
 
+\paragraph{Actions}
+
+The action space $\cA$ is constituted of five actions: faster, slower, lane change to the right, lane change to the left, and no-op.
+They are implemented by a lateral linear controller that track a reference lateral position $y_L$, affected by the lane change actions, and a lateral longitudinal linear controller that tracks the desired velocity $v_0$, affected by the faster and slower actions.
+
+\paragraph{Reward}
+
+The reward function $R$ is the following:
+\[
+R(x) = 
+\begin{cases}
+1 & \text{if the ego-vehicle is at full velocity;}\\
+0 & \text{if the ego-vehicle has collided with another vehicle;}\\
+0.5 & \text{else.}
+\end{cases}\]
+
 \end{document}

### 2020-02-10 main.tex
Updates from Overleaf

@@
 	\includegraphics[trim={0 2cm 0 0}, clip, width=0.6\linewidth]{img/ellipsoid}
-	\caption{The model estimation procedure, running on the obstacle avoidance problem of \autoref{sec:experiments}.
-The size of the confidence region $C_{[N],\delta}$ shrinks with the number of samples $N$.}
+	\caption{The model estimation procedure, running on the obstacle avoidance problem of \autoref{sec:experiments}. The confidence region $C_{[N],\delta}$ shrinks with the number of samples $N$.}
 	\label{fig:estimation}
@@
 
-In both experiments, we used $\gamma=0.9$ and $\delta=0.9$.
+In both experiments, we used $\gamma=0.9$,  $\delta=0.9$ and a planning budget $K=100$.
 The perturbations were sampled uniformly in $[-0.1, 0.1]^r$ while the measurements are gaussian with covariance $\Sigma_r = 0.1 I_s$.

### 2020-02-13 main.tex
Updates from Overleaf

@@
 The full procedure is designed to produce reasonable and safe behaviours at deployment while recovering an asymptotic optimality.
-We illustrate it on a practical case of autonomous driving at a crossroads intersection among vehicles with uncertain behaviours.\footnote[2]{Source code and videos are available in the Supplementary Material}
+We illustrate it on a practical case of autonomous driving at a crossroads intersection among vehicles with uncertain behaviours.\footnote[2]{Source code and videos are available in the Supplementary Material.}
 \end{abstract}
@@
 
-To derive a confidence region for the dynamical parameters $\theta$, the functional relationship $A(\theta)$ must be specified.
+To derive a confidence region \eqref{eq:confidence} for the dynamical parameters $\theta$, the functional relationship $A(\theta)$ must be specified.
 \begin{assumption}[Structure]
@@
 \centering
-\includegraphics[width=0.4\linewidth]{img/robust-control-tree}
+\includegraphics[width=0.45\linewidth]{img/robust-control-tree}
 \caption{The computation of robust B-values in \eqref{eq:robust-b-values}.
@@
 We present a framework for the robust estimation, prediction and control of a partially known linear system with generic costs.
-Leveraging tools from linear regression, interval prediction, and tree-based planning, we guarantee the predicted performance for the true system and provide a regret bound.
-The applicability of the method is further improved by a multi-model extension, and demonstrated on two simulated applications.
+Leveraging tools from linear regression, interval prediction, and tree-based planning, we guarantee the predicted performance and provide a regret bound.
+The applicability of the method is further improved by a multi-model extension and demonstrated on two simulated applications.
 

### 2020-02-14 supplementary/code/highway_env/envs/__init__.py
Update supplementary

@@ -1,0 +1,1 @@
+from highway_env.envs.intersection_env import *

### 2020-02-14 supplementary/code/highway_env/envs/common/abstract.py

@@ -1,0 +1,380 @@
+from __future__ import division, print_function, absolute_import
+import copy
+import gym
+from gym import spaces
+from gym.utils import seeding
+
+from highway_env import utils
+from highway_env.envs.common.observation import observation_factory
+from highway_env.envs.common.finite_mdp import finite_mdp
+from highway_env.envs.common.graphics import EnvViewer
+from highway_env.vehicle.behavior import IDMVehicle, LinearVehicle
+from highway_env.vehicle.control import MDPVehicle
+from highway_env.vehicle.dynamics import Obstacle
+
+
+class AbstractEnv(gym.Env):
+    """
+        A generic environment for various tasks involving a vehicle driving on a road.
+
+        The environment contains a road populated with vehicles, and a controlled ego-vehicle that can change lane and
+        velocity. The action space is fixed, but the observation space and reward function must be defined in the
+        environment implementations.
+    """
+    metadata = {'render.modes': ['human', 'rgb_array']}
+
+    ACTIONS = {0: 'LANE_LEFT',
+               1: 'IDLE',
+               2: 'LANE_RIGHT',
+               3: 'FASTER',
+               4: 'SLOWER'}
+    """
+        A mapping of action indexes to action labels
+    """
+    ACTIONS_INDEXES = {v: k for k, v in ACTIONS.items()}
+    """
+        A mapping of action labels to action indexes
+    """
+
+    SIMULATION_FREQUENCY = 15
+    """
+        The frequency at which the system dynamics are simulated [Hz]
+    """
+
+    PERCEPTION_DISTANCE = 6.0 * MDPVehicle.SPEED_MAX
+    """
+        The maximum distance of any vehicle present in the observation [m]
+    """
+
+    def __init__(self, config=None):
+        # Configuration
+        self.config = self.default_config()
+        if config:
+            self.config.update(config)
+
+        # Seeding
+        self.np_random = None
+        self.seed()
+
+        # Scene
+        self.road = None
+        self.vehicle = None
+
+        # Spaces
+        self.observation = None
+        self.action_space = None
+        self.observation_space = None
+        self.define_spaces()
+
+        # Running
+        self.time = 0  # Simulation time
+        self.steps = 0  # Actions performed
+        self.done = False
+
+        # Rendering
+        self.viewer = None
+        self.automatic_rendering_callback = None
+        self.should_update_rendering = True
+        self.rendering_mode = 'human'
[…]

### 2020-02-14 supplementary/code/highway_env/envs/common/graphics.py

@@ -1,0 +1,145 @@
+from __future__ import division, print_function, absolute_import
+
+import os
+
+import numpy as np
+import pygame
+from gym.spaces import Discrete
+
+from highway_env.road.graphics import WorldSurface, RoadGraphics
+from highway_env.vehicle.graphics import VehicleGraphics
+
+
+class EnvViewer(object):
+    """
+        A viewer to render a highway driving environment.
+    """
+    SAVE_IMAGES = False
+
+    def __init__(self, env, offscreen=False):
+        self.env = env
+        self.offscreen = offscreen
+
+        pygame.init()
+        pygame.display.set_caption("Highway-env")
+        panel_size = (self.env.config["screen_width"], self.env.config["screen_height"])
+
+        # A display is not mandatory to draw things. Ignoring the display.set_mode()
+        # instruction allows the drawing to be done on surfaces without
+        # handling a screen display, useful for e.g. cloud computing
+        if not self.offscreen:
+            self.screen = pygame.display.set_mode([self.env.config["screen_width"], self.env.config["screen_height"]])
+        self.sim_surface = WorldSurface(panel_size, 0, pygame.Surface(panel_size))
+        self.sim_surface.scaling = env.config.get("scaling", self.sim_surface.INITIAL_SCALING)
+        self.sim_surface.centering_position = env.config.get("centering_position", self.sim_surface.INITIAL_CENTERING)
+        self.clock = pygame.time.Clock()
+
+        self.enabled = True
+        if "SDL_VIDEODRIVER" in os.environ and os.environ["SDL_VIDEODRIVER"] == "dummy":
+            self.enabled = False
+
+        self.agent_display = None
+        self.agent_surface = None
+        self.vehicle_trajectory = None
+        self.frame = 0
+        self.directory = None
+
+    def set_agent_display(self, agent_display):
+        """
+            Set a display callback provided by an agent, so that they can render their behaviour on a dedicated
+            agent surface, or even on the simulation surface.
+        :param agent_display: a callback provided by the agent to display on surfaces
+        """
+        if self.agent_display is None:
+            if self.env.config["screen_width"] > self.env.config["screen_height"]:
+                self.screen = pygame.display.set_mode((self.env.config["screen_width"],
+                                                       2 * self.env.config["screen_height"]))
+            else:
+                self.screen = pygame.display.set_mode((2 * self.env.config["screen_width"],
+                                                       self.env.config["screen_height"]))
[…]

### 2020-02-14 supplementary/code/highway_env/envs/common/observation.py

@@ -1,0 +1,298 @@
+from __future__ import division, print_function, absolute_import
+import pandas
+from gym import spaces
+import numpy as np
+
+from highway_env import utils
+from highway_env.envs.common.finite_mdp import compute_ttc_grid
+from highway_env.road.lane import AbstractLane
+from highway_env.vehicle.control import MDPVehicle
+from highway_env.road.graphics import WorldSurface
+
+
+class ObservationType(object):
+    def space(self):
+        raise NotImplementedError()
+
+    def observe(self):
+        raise NotImplementedError()
+
+
+class GrayscaleObservation(ObservationType):
+    """
+        An observation class that collects directly what the simulator renders
+        as the input, and stacks the collected frames just as in the nature DQN
+        . Specific keys are expected in the configuration dictionnary passed.
+
+        Example of observation dictionnary in the environment config:
+            observation": {
+                "type": "GrayscaleObservation",
+                "weights": [0.2989, 0.5870, 0.1140],  #weights for RGB conversion,
+                "stack_size": 4,
+                "observation_shape": (84, 84)
+            }
+
+        Also, the screen_height and screen_width of the environment should match the
+        expected observation_shape. 
+    """
+    def __init__(self, env, **config):
+        self.env = env
+        self.config = config
+        self.observation_shape = config["observation_shape"]
+        self.shape = self.observation_shape + (config["stack_size"], )
+        self.state = np.zeros(self.shape)
+
+    def space(self):
+        try:
+            return spaces.Box(shape=self.shape,
+                              low=0, high=1,
+                              dtype=np.float32)
+        except AttributeError:
+            return None
+
+    def observe(self):
+        new_obs = self._record_to_grayscale()
+        new_obs = np.reshape(new_obs, self.observation_shape)
+        self.state = np.roll(self.state, -1, axis=-1)
+        self.state[:, :, -1] = new_obs
+        return self.state
+
+    def _record_to_grayscale(self):
+        raw_rgb = self.env.render('rgb_array')
+        return np.dot(raw_rgb[..., :3],
+                      self.config['weights'])
+
+
+class TimeToCollisionObservation(ObservationType):
+    def __init__(self, env, horizon=10, **kwargs):
+        self.env = env
+        self.horizon = horizon
+
+    def space(self):
+        try:
[…]

### 2020-02-14 supplementary/code/highway_env/envs/intersection_env.py

@@ -1,0 +1,226 @@
+from __future__ import division, print_function, absolute_import
+from gym.envs.registration import register
+import numpy as np
+
+from highway_env import utils
+from highway_env.envs.common.abstract import AbstractEnv
+from highway_env.road.lane import LineType, StraightLane, CircularLane, SineLane, AbstractLane
+from highway_env.road.regulation import RegulatedRoad
+from highway_env.road.road import RoadNetwork
+from highway_env.vehicle.control import MDPVehicle
+
+
+class IntersectionEnv(AbstractEnv):
+    COLLISION_REWARD = -5
+    HIGH_VELOCITY_REWARD = 1
+    ARRIVED_REWARD = 1
+
+    ACTIONS = {
+        0: 'SLOWER',
+        1: 'IDLE',
+        2: 'FASTER'
+    }
+    ACTIONS_INDEXES = {v: k for k, v in ACTIONS.items()}
+
+    @classmethod
+    def default_config(cls):
+        config = super().default_config()
+        config.update({
+            "observation": {
+                "type": "Kinematics",
+                "vehicles_count": 15,
+                "features": ["presence", "x", "y", "vx", "vy", "cos_h", "sin_h"],
+                "features_range": {
+                    "x": [-100, 100],
+                    "y": [-100, 100],
+                    "vx": [-20, 20],
+                    "vy": [-20, 20],
+                },
+                "absolute": True,
+                "flatten": False,
+                "observe_intentions": False
+            },
+            "duration": 13,  # [s]
+            "destination": "o1",
+            "initial_vehicle_count": 10,
+            "spawn_probability": 0.6,
+            "screen_width": 600,
+            "screen_height": 600,
+            "centering_position": [0.5, 0.6],
+            "scaling": 5.5 * 1.3,
+            "collision_reward": IntersectionEnv.COLLISION_REWARD,
+            "normalize_reward": False
+        })
+        return config
+
+    def _reward(self, action):
+        reward = self.config["collision_reward"] * self.vehicle.crashed \
+                 + self.HIGH_VELOCITY_REWARD * (self.vehicle.velocity_index == self.vehicle.SPEED_COUNT - 1)
+        reward = self.ARRIVED_REWARD if self.has_arrived else reward
+        if self.config["normalize_reward"]:
+            reward = utils.remap(reward, [self.config["collision_reward"], self.ARRIVED_REWARD], [0, 1])
+        return reward
+
+    def _is_terminal(self):
+        """
[…]

### 2020-02-14 supplementary/code/highway_env/road/road.py

@@ -1,0 +1,328 @@
+from __future__ import division, print_function
+import numpy as np
+import pandas as pd
+import logging
+
+from highway_env.logger import Loggable
+from highway_env.road.lane import LineType, StraightLane
+from highway_env.vehicle.dynamics import Obstacle
+
+logger = logging.getLogger(__name__)
+
+
+class RoadNetwork(object):
+    def __init__(self):
+        self.graph = {}
+
+    def add_node(self, node):
+        """
+            A node represents an symbolic intersection in the road network.
+        :param node: the node label.
+        """
+        if node not in self.graph:
+            self.graph[node] = []
+
+    def add_lane(self, _from, _to, lane):
+        """
+            A lane is encoded as an edge in the road network.
+        :param _from: the node at which the lane starts.
+        :param _to: the node at which the lane ends.
+        :param AbstractLane lane: the lane geometry.
+        """
+        if _from not in self.graph:
+            self.graph[_from] = {}
+        if _to not in self.graph[_from]:
+            self.graph[_from][_to] = []
+        self.graph[_from][_to].append(lane)
+
+    def get_lane(self, index):
+        """
+            Get the lane geometry corresponding to a given index in the road network.
+        :param index: a tuple (origin node, destination node, lane id on the road).
+        :return: the corresponding lane geometry.
+        """
+        _from, _to, _id = index
+        if _id is None and len(self.graph[_from][_to]) == 1:
+            _id = 0
+        return self.graph[_from][_to][_id]
+
+    def get_closest_lane_index(self, position):
+        """
+            Get the index of the lane closest to a world position.
+
+        :param position: a world position [m].
+        :return: the index of the closest lane.
+        """
+        indexes, distances = [], []
+        for _from, to_dict in self.graph.items():
+            for _to, lanes in to_dict.items():
+                for _id, l in enumerate(lanes):
+                    distances.append(l.distance(position))
+                    indexes.append((_from, _to, _id))
+        return indexes[int(np.argmin(distances))]
+
+    def next_lane(self, current_index, route=None, position=None, np_random=np.random):
+        """
+            Get the index of the next lane that should be followed after finishing the current lane.
+
+            If a plan is available and matches with current lane, follow it.
+            Else, pick next road randomly.
+            If it has the same number of lanes as current road, stay in the same lane.
+            Else, pick next road's closest lane.
[…]

### 2020-02-14 supplementary/code/highway_env/utils.py

@@ -1,0 +1,190 @@
+from __future__ import division, print_function
+
+import copy
+import importlib
+import itertools
+
+import numpy as np
+
+
+def do_every(duration, timer):
+    return duration < timer
+
+
+def remap(v, x, y):
+    return y[0] + (v-x[0])*(y[1]-y[0])/(x[1]-x[0])
+
+
+def class_from_path(path):
+    module_name, class_name = path.rsplit(".", 1)
+    class_object = getattr(importlib.import_module(module_name), class_name)
+    return class_object
+
+
+def constrain(x, a, b):
+    return np.minimum(np.maximum(x, a), b)
+
+
+def not_zero(x, eps=1e-2):
+    if abs(x) > eps:
+        return x
+    elif x > 0:
+        return eps
+    else:
+        return -eps
+
+
+def wrap_to_pi(x):
+    return ((x+np.pi) % (2*np.pi)) - np.pi
+
+
+def point_in_rectangle(point, rect_min, rect_max):
+    """
+        Check if a point is inside a rectangle
+    :param point: a point (x, y)
+    :param rect_min: x_min, y_min
+    :param rect_max: x_max, y_max
+    """
+    return rect_min[0] <= point[0] <= rect_max[0] and rect_min[1] <= point[1] <= rect_max[1]
+
+
+def point_in_rotated_rectangle(point, center, length, width, angle):
+    """
+        Check if a point is inside a rotated rectangle
+    :param point: a point
+    :param center: rectangle center
+    :param length: rectangle length
+    :param width: rectangle width
+    :param angle: rectangle angle [rad]
+    """
+    c, s = np.cos(angle), np.sin(angle)
+    r = np.array([[c, -s], [s, c]])
+    ru = r.dot(point - center)
+    return point_in_rectangle(ru, [-length/2, -width/2], [length/2, width/2])
+
+
+def point_in_ellipse(point, center, angle, length, width):
+    """
+        Check if a point is inside an ellipse
+    :param point: a point
+    :param center: ellipse center
+    :param angle: ellipse main axis angle
+    :param length: ellipse big axis
+    :param width: ellipse small axis
+    """
+    c, s = np.cos(angle), np.sin(angle)
+    r = np.matrix([[c, -s], [s, c]])
+    ru = r.dot(point - center)
+    return np.sum(np.square(ru / np.array([length, width]))) < 1
+
+
[…]

### 2020-02-14 supplementary/code/highway_env/vehicle/behavior.py

@@ -1,0 +1,474 @@
+from __future__ import division, print_function
+import numpy as np
+from highway_env.vehicle.control import ControlledVehicle
+from highway_env import utils
+
+
+class IDMVehicle(ControlledVehicle):
+    """
+        A vehicle using both a longitudinal and a lateral decision policies.
+
+        - Longitudinal: the IDM model computes an acceleration given the preceding vehicle's distance and velocity.
+        - Lateral: the MOBIL model decides when to change lane by maximizing the acceleration of nearby vehicles.
+        """
+
+    # Longitudinal policy parameters
+    ACC_MAX = 6.0  # [m/s2]
+    COMFORT_ACC_MAX = 3.0  # [m/s2]
+    COMFORT_ACC_MIN = -5.0  # [m/s2]
+    DISTANCE_WANTED = 5.0 + ControlledVehicle.LENGTH  # [m]
+    TIME_WANTED = 1.5  # [s]
+    DELTA = 4.0  # []
+
+    # Lateral policy parameters
+    POLITENESS = 0.  # in [0, 1]
+    LANE_CHANGE_MIN_ACC_GAIN = 0.2  # [m/s2]
+    LANE_CHANGE_MAX_BRAKING_IMPOSED = 2.0  # [m/s2]
+    LANE_CHANGE_DELAY = 1.0  # [s]
+
+    def __init__(self, road, position,
+                 heading=0,
+                 velocity=0,
+                 target_lane_index=None,
+                 target_velocity=None,
+                 route=None,
+                 enable_lane_change=True,
+                 timer=None):
+        super(IDMVehicle, self).__init__(road, position, heading, velocity, target_lane_index, target_velocity, route)
+        self.enable_lane_change = enable_lane_change
+        self.timer = timer or (np.sum(self.position)*np.pi) % self.LANE_CHANGE_DELAY
+
+    def randomize_behavior(self):
+        pass
+
+    @classmethod
+    def create_from(cls, vehicle):
+        """
+            Create a new vehicle from an existing one.
+            The vehicle dynamics and target dynamics are copied, other properties are default.
+
+        :param vehicle: a vehicle
+        :return: a new vehicle at the same dynamical state
+        """
+        v = cls(vehicle.road, vehicle.position, heading=vehicle.heading, velocity=vehicle.velocity,
+                target_lane_index=vehicle.target_lane_index, target_velocity=vehicle.target_velocity,
+                route=vehicle.route, timer=getattr(vehicle, 'timer', None))
+        return v
+
[…]

### 2020-02-14 supplementary/code/highway_env/vehicle/control.py

@@ -1,0 +1,281 @@
+from __future__ import division, print_function
+import numpy as np
+import copy
+from highway_env import utils
+from highway_env.vehicle.dynamics import Vehicle
+
+
+class ControlledVehicle(Vehicle):
+    """
+        A vehicle piloted by two low-level controller, allowing high-level actions
+        such as cruise control and lane changes.
+
+        - The longitudinal controller is a velocity controller;
+        - The lateral controller is a heading controller cascaded with a lateral position controller.
+    """
+
+    TAU_A = 0.6  # [s]
+    TAU_DS = 0.14  # [s]
+    PURSUIT_TAU = 1.5*TAU_DS  # [s]
+    KP_A = 1 / TAU_A
+    KP_HEADING = 1 / TAU_DS
+    KP_LATERAL = KP_HEADING / 7  # [1/s]
+    MAX_STEERING_ANGLE = np.pi / 3  # [rad]
+
+    DELTA_VELOCITY = 5  # [m/s]
+
+    def __init__(self,
+                 road,
+                 position,
+                 heading=0,
+                 velocity=0,
+                 target_lane_index=None,
+                 target_velocity=None,
+                 route=None):
+        super(ControlledVehicle, self).__init__(road, position, heading, velocity)
+        self.target_lane_index = target_lane_index or self.lane_index
+        self.target_velocity = target_velocity or self.velocity
+        self.route = route
+
+    @classmethod
+    def create_from(cls, vehicle):
+        """
+            Create a new vehicle from an existing one.
+            The vehicle dynamics and target dynamics are copied, other properties are default.
+
+        :param vehicle: a vehicle
+        :return: a new vehicle at the same dynamical state
+        """
+        v = cls(vehicle.road, vehicle.position, heading=vehicle.heading, velocity=vehicle.velocity,
+                target_lane_index=vehicle.target_lane_index, target_velocity=vehicle.target_velocity,
+                route=vehicle.route)
+        return v
+
+    def plan_route_to(self, destination):
+        """
+            Plan a route to a destination in the road network
+
+        :param destination: a node in the road network
+        """
+        path = self.road.network.shortest_path(self.lane_index[1], destination)
+        if path:
+            self.route = [self.lane_index] + [(path[i], path[i + 1], None) for i in range(len(path) - 1)]
+        else:
+            self.route = [self.lane_index]
+        return self
+
+    def act(self, action=None):
+        """
+            Perform a high-level action to change the desired lane or velocity.
+
+            - If a high-level action is provided, update the target velocity and lane;
[…]

### 2020-02-14 supplementary/code/highway_env/vehicle/dynamics.py

@@ -1,0 +1,276 @@
+from __future__ import division, print_function
+
+import copy
+
+import numpy as np
+import pandas as pd
+from collections import deque
+
+from highway_env import utils
+from highway_env.logger import Loggable
+
+
+class Vehicle(Loggable):
+    """
+        A moving vehicle on a road, and its dynamics.
+
+        The vehicle is represented by a dynamical system: a modified bicycle model.
+        It's state is propagated depending on its steering and acceleration actions.
+    """
+    COLLISIONS_ENABLED = True
+    """ Enable collision detection between vehicles """
+
+    LENGTH = 5.0
+    """ Vehicle length [m] """
+    WIDTH = 2.0
+    """ Vehicle width [m] """
+    DEFAULT_VELOCITIES = [23, 25]
+    """ Range for random initial velocities [m/s] """
+    MAX_VELOCITY = 40
+    """ Maximum reachable velocity [m/s] """
+
+    def __init__(self, road, position, heading=0, velocity=0):
+        self.road = road
+        self.position = np.array(position).astype('float')
+        self.heading = heading
+        self.velocity = velocity
+        self.lane_index = self.road.network.get_closest_lane_index(self.position) if self.road else np.nan
+        self.lane = self.road.network.get_lane(self.lane_index) if self.road else None
+        self.action = {'steering': 0, 'acceleration': 0}
+        self.crashed = False
+        self.log = []
+        self.history = deque(maxlen=30)
+
+    @classmethod
+    def make_on_lane(cls, road, lane_index, longitudinal, velocity=0):
+        """
+            Create a vehicle on a given lane at a longitudinal position.
+
+        :param road: the road where the vehicle is driving
+        :param lane_index: index of the lane where the vehicle is located
+        :param longitudinal: longitudinal position along the lane
+        :param velocity: initial velocity in [m/s]
+        :return: A vehicle with at the specified position
+        """
+        lane = road.network.get_lane(lane_index)
+        if velocity is None:
+            velocity = lane.speed_limit
+        return cls(road, lane.position(longitudinal, 0), lane.heading_at(longitudinal), velocity)
+
+    @classmethod
+    def create_random(cls, road, velocity=None, spacing=1):
+        """
+            Create a random vehicle on the road.
+
+            The lane and /or velocity are chosen randomly, while longitudinal position is chosen behind the last
+            vehicle in the road with density based on the number of lanes.
+
+        :param road: the road where the vehicle is driving
[…]

### 2020-02-14 supplementary/code/highway_env/vehicle/graphics.py

@@ -1,0 +1,183 @@
+from __future__ import division, print_function
+
+import itertools
+
+import numpy as np
+import pygame
+
+from highway_env.vehicle.dynamics import Vehicle, Obstacle
+from highway_env.vehicle.control import ControlledVehicle, MDPVehicle
+from highway_env.vehicle.behavior import IDMVehicle, LinearVehicle
+
+
+class VehicleGraphics(object):
+    RED = (255, 100, 100)
+    GREEN = (50, 200, 0)
+    BLUE = (100, 200, 255)
+    YELLOW = (200, 200, 0)
+    BLACK = (60, 60, 60)
+    PURPLE = (200, 0, 150)
+    DEFAULT_COLOR = YELLOW
+    EGO_COLOR = GREEN
+
+    @classmethod
+    def display(cls, vehicle, surface, transparent=False, offscreen=False):
+        """
+            Display a vehicle on a pygame surface.
+
+            The vehicle is represented as a colored rotated rectangle.
+
+        :param vehicle: the vehicle to be drawn
+        :param surface: the surface to draw the vehicle on
+        :param transparent: whether the vehicle should be drawn slightly transparent
+        :param offscreen: whether the rendering should be done offscreen or not
+        """
+        v = vehicle
+        s = pygame.Surface((surface.pix(v.LENGTH), surface.pix(v.LENGTH)), pygame.SRCALPHA)  # per-pixel alpha
+        rect = (0, surface.pix(v.LENGTH) / 2 - surface.pix(v.WIDTH) / 2, surface.pix(v.LENGTH), surface.pix(v.WIDTH))
+        pygame.draw.rect(s, cls.get_color(v, transparent), rect, 0)
+        pygame.draw.rect(s, cls.BLACK, rect, 1)
+        if not offscreen:  # convert_alpha throws errors in offscreen mode TODO() Explain why
+            s = pygame.Surface.convert_alpha(s)
+        h = v.heading if abs(v.heading) > 2 * np.pi / 180 else 0
+        # Centered rotation
+        position = (surface.pos2pix(v.position[0], v.position[1]))
+        cls.blitRotate(surface, s, position, np.rad2deg(-h))
+
+    @staticmethod
+    def blitRotate(surf, image, pos, angle, origin_pos=None, show_rect=False):
+        """Many thanks to https://stackoverflow.com/a/54714144 """
+        # calculate the axis aligned bounding box of the rotated image
[…]

### 2020-02-14 supplementary/code/highway_env/vehicle/uncertainty/prediction.py

@@ -1,0 +1,236 @@
+import copy
+
+import numpy as np
+
+from highway_env import utils
+from highway_env.interval import polytope, LPV, interval_absolute_to_local, \
+    interval_local_to_absolute
+from highway_env.vehicle.behavior import LinearVehicle
+from highway_env.vehicle.control import MDPVehicle
+
+
+class IntervalVehicle(LinearVehicle):
+    """
+        Estimator for the interval-membership of a LinearVehicle under parameter uncertainty.
+
+        The model trajectory is stored in a model_vehicle, and the lower and upper bounds of the states are stored
+        in a min_vehicle and max_vehicle. Note that these vehicles do not follow a proper Vehicle dynamics, and
+        are only used for storage of the bounds.
+    """
+    def __init__(self,
+                 road,
+                 position,
+                 heading=0,
+                 velocity=0,
+                 target_lane_index=None,
+                 target_velocity=None,
+                 route=None,
+                 enable_lane_change=True,
+                 timer=None,
+                 theta_a_i=None,
+                 theta_b_i=None,
+                 data=None):
+        """
+        :param theta_a_i: The interval of possible acceleration parameters
+        :param theta_b_i: The interval of possible steering parameters
+        """
+        super().__init__(road,
+                         position,
+                         heading,
+                         velocity,
+                         target_lane_index,
+                         target_velocity,
+                         route,
+                         enable_lane_change,
+                         timer)
+        self.theta_a_i = theta_a_i if theta_a_i is not None else LinearVehicle.ACCELERATION_RANGE
+        self.theta_b_i = theta_b_i if theta_b_i is not None else LinearVehicle.STEERING_RANGE
+        self.data = data
+        self.interval = VehicleInterval(self)
+        self.trajectory = []
+        self.interval_trajectory = []
+        self.longitudinal_lpv, self.lateral_lpv = None, None
+        self.previous_target_lane_index = self.target_lane_index
+
+    @classmethod
+    def create_from(cls, vehicle):
+        v = cls(vehicle.road,
+                vehicle.position,
+                heading=vehicle.heading,
+                velocity=vehicle.velocity,
+                target_lane_index=getattr(vehicle, 'target_lane_index', None),
+                target_velocity=getattr(vehicle, 'target_velocity', None),
+                route=getattr(vehicle, 'route', None),
[…]

### 2020-02-14 supplementary/code/obstacle_env/__init__.py

@@ -1,0 +1,7 @@
+from gym.envs.registration import register
+
+register(
+    id='obstacle-v0',
+    entry_point='obstacle_env.envs:ObstacleEnv',
+    max_episode_steps=20,
+)

### 2020-02-14 supplementary/code/obstacle_env/dynamics.py

@@ -1,0 +1,221 @@
+from __future__ import print_function, division
+import numpy as np
+from scipy import signal
+
+
+class Dynamics1D(object):
+    """
+        A fourth-order one-dimensional dynamical system.
+    """
+    DEFAULT_PARAMS = {'Cx': 1.0,
+                      'w0': 50.0,
+                      'zeta': 1.0,
+                      'dt': 1/30,
+                      'acceleration': 5,
+                      'perturbation': 0.1}
+
+    def __init__(self, state=None, params=None):
+        self.A = self.B = self.C = self.D = None
+        self.discrete = self.continuous = None
+        if params is None:
+            params = self.DEFAULT_PARAMS
+        self.params = params
+        self.derivative = None
+
+        self.continuous_dynamics()
+        self.discrete_dynamics()
+
+        if state is None:
+            state = np.zeros((np.shape(self.A)[0], 1))
+        self.state = state
+        self.control = np.zeros((1, 1))
+        self.desired_action = 0
+
+        self.crashed = False
+
+    def continuous_dynamics(self):
+        """
+            Continuous state-space model
+        """
+        self.A = np.array(
+            [[0, 1, 0, 0],
+             [0, -self.params['Cx'], 1, 0],
+             [0, 0, 0, 1],
+             [0, 0, -self.params['w0']**2, -2*self.params['zeta']*self.params['w0']]])
+        self.B = np.array([[0], [0], [0], [self.params['w0']**2]])
+        self.C = np.identity(np.shape(self.A)[0])
+        self.D = np.zeros(np.shape(self.B))
+
+        self.continuous = (self.A, self.B, self.C, self.D)
+
+    def discrete_dynamics(self):
+        """
+            Discrete state-space model
+        """
+
+        self.discrete = signal.cont2discrete(self.continuous, self.params['dt'], method='zoh')
+
+    def act(self, action):
+        if action == 'RIGHT':
+            self.control = np.array([1])
+        elif action == 'LEFT':
+            self.control = np.array([-1])
+        else:
+            self.control = np.array([0])
+
+    def step(self):
+        """
+            Step the dynamics
+        """
+        # self.state = np.dot(self.discrete[0], self.state)+np.dot(self.discrete[1], self.control)
+        self.derivative = np.dot(self.continuous[0], self.state)+np.dot(self.continuous[1], self.control)
[…]

### 2020-02-14 supplementary/code/obstacle_env/envs/__init__.py

@@ -1,0 +1,1 @@
+from obstacle_env.envs.obstacle import ObstacleEnv

### 2020-02-14 supplementary/code/obstacle_env/envs/obstacle.py

@@ -1,0 +1,309 @@
+from __future__ import print_function, division
+import copy
+import numpy as np
+import gym
+from gym import spaces
+from gym.utils import seeding
+
+from obstacle_env.dynamics import Dynamics2D2
+from obstacle_env.graphics import EnvViewer
+from obstacle_env.scene import Scene2D, PolarGrid
+
+
+class ObstacleEnv(gym.Env):
+    metadata = {'render.modes': ['human', 'rgb_array']}
+
+    config = {
+        "simulation_frequency": 10,
+        "policy_frequency": 2,
+        "grid_cells": 16,
+        "collision_reward": -0.5,
+        "observation_type": "grid",
+        "observation_noise": 0.1,
+    }
+
+    def __init__(self):
+        # Seeding
+        self.np_random = None
+        self.seed()
+
+        # Dynamics
+        params = Dynamics2D2.DEFAULT_PARAMS.update({'dt': 1 / self.config["simulation_frequency"]})
+        self.dynamics = Dynamics2D2(params=params)
+        self.dynamics.desired_action = self.np_random.randint(1, len(self.dynamics.ACTIONS))
+
+        # Scene
+        self.scene = Scene2D()
+        self.scene.create_random_scene(np_random=self.np_random)
+        self.grid = PolarGrid(self.scene, cells=self.config["grid_cells"])
+
+        # Spaces
+        self.action_space = spaces.Discrete(len(self.dynamics.ACTIONS))
+        low_obs = np.hstack((-self.dynamics.terminal_velocity * np.ones((2,)),
+                             -self.dynamics.params['acceleration'] * np.ones((2,)),
+                             0 * np.ones((self.grid.cells,)),))
+        high_obs = np.hstack((self.dynamics.terminal_velocity * np.ones((2,)),
+                              self.dynamics.params['acceleration'] * np.ones((2,)),
+                              self.grid.MAXIMUM_RANGE * np.ones((self.grid.cells,)),))
+        self.observation_space = spaces.Box(low=low_obs, high=high_obs, dtype=np.float32)
+
+        # Viewer
+        self.viewer = None
+        self.automatic_rendering_callback = None
+        self.should_update_rendering = True
+        self.rendering_mode = 'human'
+        self.enable_auto_render = False
+
+        self.lpv = None
+
+        self.steps = 0
+        self.time = 0
+        self.done = False
+        self.trajectory = []
+        self.interval_trajectory = []
+        self.automatic_record_callback = None
+
[…]

### 2020-02-14 supplementary/code/obstacle_env/graphics.py

@@ -1,0 +1,241 @@
+from __future__ import print_function, division
+
+import datetime
+import shutil
+
+import numpy as np
+import pygame
+import os
+
+from obstacle_env.scene import PolarGrid
+
+
+class EnvViewer(object):
+    """
+        A viewer to render an environment.
+    """
+    SCREEN_WIDTH = 800
+    SCREEN_HEIGHT = 800
+    SAVE_IMAGES = True
+
+    def __init__(self, env, record_video=True):
+        self.env = env
+        self.record_video = record_video
+
+        pygame.init()
+        pygame.display.set_caption("Obstacle-env")
+        panel_size = (self.SCREEN_WIDTH, self.SCREEN_HEIGHT)
+        self.screen = pygame.display.set_mode([self.SCREEN_WIDTH, self.SCREEN_HEIGHT])
+        self.sim_surface = SimulationSurface(panel_size, 0, pygame.Surface(panel_size))
+        self.clock = pygame.time.Clock()
+
+        self.agent_display = None
+        self.agent_surface = None
+        self.frame = 0
+
+    def set_agent_display(self, agent_display):
+        if self.agent_display is None:
+            self.agent_display = agent_display
+            self.screen = pygame.display.set_mode((self.SCREEN_WIDTH * 2, self.SCREEN_HEIGHT))
+            self.agent_surface = pygame.Surface((self.SCREEN_WIDTH, self.SCREEN_HEIGHT))
+
+    def handle_events(self):
+        """
+            Handle pygame events by forwarding them to the display and environment vehicle.
+        """
+        for event in pygame.event.get():
+            if event.type == pygame.QUIT:
+                self.env.close()
+            self.sim_surface.handle_event(event)
+            if self.env.dynamics:
+                DynamicsGraphics.handle_event(self.env.dynamics, event)
+
+    def display(self, show_grid=False):
+        """
+            Display the scene on a pygame window.
+        """
+        self.sim_surface.move_display_window_to(self.window_position())
+        Scene2dGraphics.display(self.env.scene, self.sim_surface)
+        DynamicsGraphics.display(self.env.dynamics, self.sim_surface)
+        if show_grid:
+            self.env.grid.trace(self.env.dynamics.position)
+            DynamicsGraphics.display_grid(self.env.grid, self.sim_surface)
+
+        if self.agent_display:
+            self.agent_display(self.agent_surface, self.sim_surface)
[…]

### 2020-02-14 supplementary/code/obstacle_env/scene.py

@@ -1,0 +1,126 @@
+from __future__ import print_function, division
+import numpy as np
+import math
+
+
+class Scene1D(object):
+    BOUNDS = 10
+
+    def __init__(self):
+        self.obstacles = [{'position': np.array([-self.BOUNDS]), 'radius': 1},
+                          {'position': np.array([+self.BOUNDS]), 'radius': 1}]
+
+
+class Scene2D(object):
+    BOUNDS_X = 50
+    BOUNDS_Y = 50
+
+    def __init__(self):
+        self.obstacles = []
+        self.goal = None
+        self.create_random_scene()
+
+    def create_random_scene(self, np_random=np.random):
+        self.obstacles = []
+        for _ in range(400):
+            o = np.zeros((2, 1))
+            while np.linalg.norm(o) < 2:
+                o = np.array([[self.BOUNDS_X * (np_random.rand() * 2 - 1)],
+                              [self.BOUNDS_Y * (np_random.rand() * 2 - 1)]])
+            self.obstacles.append({'position': o, 'radius': 1})
+        self.goal = {'position': np.array([[self.BOUNDS_X * (np_random.rand() * 2 - 1)],
+                                           [self.BOUNDS_Y * (np_random.rand() * 2 - 1)]]),
+                     'radius': 1}
+
+    def create_corridor_scene(self):
+        for y in np.linspace(-self.BOUNDS_Y, self.BOUNDS_Y, int(self.BOUNDS_Y)+1):
+            self.obstacles.append({'position': np.array([[-self.BOUNDS_X], [y]]), 'radius': 1})
+        for x in np.linspace(-self.BOUNDS_X, 5*self.BOUNDS_X, int(3*self.BOUNDS_Y)+1):
+            self.obstacles.append({'position': np.array([[x], [-self.BOUNDS_Y]]), 'radius': 1})
+            self.obstacles.append({'position': np.array([[x], [self.BOUNDS_Y]]), 'radius': 1})
+        self.obstacles.extend([
+            {'position': np.array([[10], [0]]), 'radius': 1},
+            {'position': np.array([[20], [2]]), 'radius': 1},
+            {'position': np.array([[20], [-2]]), 'radius': 1},
+        ])
+
+
+class PolarGrid:
+    MAXIMUM_RANGE = 12
+
+    def __init__(self, scene, cells=8):
+        self.scene = scene
+        self.cells = cells
+        self.angle = 2 * math.pi / self.cells
[…]

### 2020-02-14 supplementary/code/rl_agents/agents/common/factory.py

@@ -1,0 +1,121 @@
+import copy
+import importlib
+import json
+import logging
+import gym
+
+logger = logging.getLogger(__name__)
+
+
+def agent_factory(environment, config):
+    """
+        Handles creation of agents.
+
+    :param environment: the environment
+    :param config: configuration of the agent, must contain a '__class__' key
+    :return: a new agent
+    """
+    if "__class__" in config:
+        path = config['__class__'].split("'")[1]
+        module_name, class_name = path.rsplit(".", 1)
+        agent_class = getattr(importlib.import_module(module_name), class_name)
+        agent = agent_class(environment, config)
+        return agent
+    else:
+        raise ValueError("The configuration should specify the agent __class__")
+
+
+def load_agent(agent_path, env):
+    """
+        Load an agent from a configuration file.
+
+    :param agent_path: the path to the agent configuration file
+    :param env: the environment with which the agent interacts
+    :return: the agent
+    """
+    # Load agent from file
+    if not isinstance(agent_path, dict):
+        with open(agent_path) as f:
+            agent_config = json.loads(f.read())
+    else:
+        agent_config = agent_path
+
+    return agent_factory(env, agent_config)
+
+
+def load_environment(env_config):
+    """
+        Load an environment from a configuration file.
+
+    :param env_config: the configuration, or path to the environment configuration file
+    :return: the environment
+    """
+    # Load the environment config from file
+    if not isinstance(env_config, dict):
+        with open(env_config) as f:
+            env_config = json.loads(f.read())
+
+    # Make the environment
+    if env_config.get("import_module", None):
+        __import__(env_config["import_module"])
+    try:
+        env = gym.make(env_config['id'])
+        # Save env module in order to be able to import it again
+        env.import_module = env_config.get("import_module", None)
+    except KeyError:
+        raise ValueError("The gym register id of the environment must be provided")
+    except gym.error.UnregisteredEnv:
+        # The environment is unregistered.
+        print("import_module", env_config["import_module"])
+        raise gym.error.UnregisteredEnv('Environment {} not registered. The environment module should be specified by '
+                                        'the "import_module" key of the environment configuration'.format(
+                                            env_config['id']))
+
+    # Configure the environment, if supported
+    try:
+        env.unwrapped.configure(env_config)
+        # Reset the environment to ensure configuration is applied
+        env.reset()
+    except AttributeError as e:
[…]

### 2020-02-14 supplementary/code/rl_agents/agents/common/graphics.py

@@ -1,0 +1,32 @@
+from __future__ import division, print_function
+
+from rl_agents.agents.tree_search.abstract import AbstractTreeSearchAgent
+from rl_agents.agents.tree_search.graphics.graphics import TreeGraphics
+from rl_agents.agents.tree_search.graphics.robust_epc import RobustEPCGraphics
+from rl_agents.agents.tree_search.graphics.robust import DiscreteRobustPlannerGraphics, IntervalRobustPlannerGraphics
+from rl_agents.agents.tree_search.robust import DiscreteRobustPlannerAgent, IntervalRobustPlannerAgent
+from rl_agents.agents.tree_search.robust_epc import RobustEPCAgent
+
+
+class AgentGraphics(object):
+    """
+        Graphical visualization of any Agent implementing AbstractAgent.
+    """
+    @classmethod
+    def display(cls, agent, agent_surface, sim_surface=None):
+        """
+            Display an agent visualization on a pygame surface.
+
+        :param agent: the agent to be displayed
+        :param agent_surface: the pygame surface on which the agent is displayed
+        :param sim_surface: the pygame surface on which the environment is displayed
+        """
+
+        if isinstance(agent, IntervalRobustPlannerAgent):
+            IntervalRobustPlannerGraphics.display(agent, agent_surface, sim_surface)
+        elif isinstance(agent, DiscreteRobustPlannerAgent):
+            DiscreteRobustPlannerGraphics.display(agent, agent_surface, sim_surface)
+        elif isinstance(agent, RobustEPCAgent):
+            RobustEPCGraphics.display(agent, agent_surface, sim_surface)
+        elif isinstance(agent, AbstractTreeSearchAgent):
+            TreeGraphics.display(agent, agent_surface)

### 2020-02-14 supplementary/code/rl_agents/agents/common/interval.py

@@ -1,0 +1,229 @@
+import itertools
+
+import numpy as np
+
+
+def intervals_product(a, b):
+    """
+        Compute the product of two intervals
+    :param a: interval [a_min, a_max]
+    :param b: interval [b_min, b_max]
+    :return: the interval of their product ab
+    """
+    p = lambda x: np.maximum(x, 0)
+    n = lambda x: np.maximum(-x, 0)
+    return np.array(
+        [np.dot(p(a[0]), p(b[0])) - np.dot(p(a[1]), n(b[0])) - np.dot(n(a[0]), p(b[1])) + np.dot(n(a[1]), n(b[1])),
+         np.dot(p(a[1]), p(b[1])) - np.dot(p(a[0]), n(b[1])) - np.dot(n(a[1]), p(b[0])) + np.dot(n(a[0]), n(b[0]))])
+
+
+def intervals_scaling(a, b):
+    """
+        Scale an intervals
+    :param a: matrix a
+    :param b: interval [b_min, b_max]
+    :return: the interval of their product ab
+    """
+    p = lambda x: np.maximum(x, 0)
+    n = lambda x: np.maximum(-x, 0)
+    return np.array(
+        [np.dot(p(a), b[0]) - np.dot(n(a), b[1]),
+         np.dot(p(a), b[1]) - np.dot(n(a), b[0])])
+
+
+def vector_interval_section(v_i, direction):
+    corners = [[v_i[0, 0], v_i[0, 1]],
+               [v_i[0, 0], v_i[1, 1]],
+               [v_i[1, 0], v_i[0, 1]],
+               [v_i[1, 0], v_i[1, 1]]]
+    corners_dist = [np.dot(corner, direction) for corner in corners]
+    return np.array([min(corners_dist), max(corners_dist)])
+
+
+def interval_absolute_to_local(position_i, lane):
+    """
+        Converts an interval in absolute x,y coordinates to an interval in local (longiturinal, lateral) coordinates
+    :param position_i: the position interval [x_min, x_max]
+    :param lane: the lane giving the local frame
+    :return: the corresponding local interval
+    """
+    position_corners = [[position_i[0, 0], position_i[0, 1]],
+                        [position_i[0, 0], position_i[1, 1]],
+                        [position_i[1, 0], position_i[0, 1]],
+                        [position_i[1, 0], position_i[1, 1]]]
+    corners_local = np.array([lane.local_coordinates(c) for c in position_corners])
[…]

### 2020-02-14 supplementary/code/rl_agents/agents/common/utils.py

@@ -1,0 +1,99 @@
+import logging
+import os
+import re
+import numpy as np
+from subprocess import PIPE, run, check_output
+import torch
+
+
+logger = logging.getLogger(__name__)
+
+
+def sample_simplex(coeff, bias, min_x, max_x, np_random=np.random):
+    """
+    Sample from a simplex.
+
+    The simplex is defined by:
+        w.x + b <= 0
+        x_min <= x <= x_max
+
+    Warning: this is not uniform sampling.
+
+    :param coeff: coefficient w
+    :param bias: bias b
+    :param min_x: lower bound on x
+    :param max_x: upper bound on x
+    :param np_random: source of randomness
+    :return: a sample from the simplex
+    """
+    x = np.zeros(len(coeff))
+    indexes = np.asarray(range(0, len(coeff)))
+    np_random.shuffle(indexes)
+    remain_indexes = np.copy(indexes)
+    for i_index, index in enumerate(indexes):
+        remain_indexes = remain_indexes[1:]
+        current_coeff = np.take(coeff, remain_indexes)
+        full_min = np.full(len(remain_indexes), min_x)
+        full_max = np.full(len(remain_indexes), max_x)
+        dot_max = np.dot(current_coeff, full_max)
+        dot_min = np.dot(current_coeff, full_min)
+        min_xi = (bias - dot_max) / coeff[index]
+        max_xi = (bias - dot_min) / coeff[index]
+        min_xi = np.max([min_xi, min_x])
+        max_xi = np.min([max_xi, max_x])
+        xi = min_xi + np_random.random_sample() * (max_xi - min_xi)
+        bias = bias - xi * coeff[index]
+        x[index] = xi
+        if len(remain_indexes) == 1:
+            break
+    last_index = remain_indexes[0]
+    x[last_index] = bias / coeff[last_index]
+    return x
+
+
+def load_pytorch():
+    torch.backends.cudnn.benchmark = False
+    torch.backends.cudnn.enabled = False
+    logger.info("Using torch.multiprocessing.set_start_method('spawn')")
+    import torch.multiprocessing as multiprocessing
+    try:
+        multiprocessing.set_start_method('spawn')
+    except RuntimeError as e:
+        logger.warning(str(e))
+
+
+def get_gpu_memory_map():
+    result = check_output(['nvidia-smi', '--query-gpu=memory.used', '--format=csv,nounits,noheader'])
+    return [int(x) for x in result.split()]
+
+
+def least_used_device():
[…]

### 2020-02-14 supplementary/code/rl_agents/agents/tree_search/abstract.py

@@ -1,0 +1,325 @@
+import logging
+import numpy as np
+from gym.utils import seeding
+
+from rl_agents.agents.common.abstract import AbstractAgent
+from rl_agents.agents.common.factory import preprocess_env, safe_deepcopy_env
+from rl_agents.configuration import Configurable
+from rl_agents.agents.tree_search.graphics.graphics import TreePlot
+
+logger = logging.getLogger(__name__)
+
+
+class AbstractTreeSearchAgent(AbstractAgent):
+    def __init__(self,
+                 env,
+                 config=None):
+        """
+            A new Tree Search agent.
+        :param env: The environment
+        :param config: The agent configuration. Use default if None.
+        """
+        super(AbstractTreeSearchAgent, self).__init__(config)
+        self.env = env
+        self.planner = self.make_planner()
+        self.previous_actions = []
+        self.remaining_horizon = 0
+        self.steps = 0
+
+    @classmethod
+    def default_config(cls):
+        return {
+            "env_preprocessors": [],
+            "display_tree": False
+        }
+
+    def make_planner(self):
+        raise NotImplementedError()
+
+    def plan(self, observation):
+        """
+            Plan an optimal sequence of actions.
+
+            Start by updating the previously found tree with the last action performed.
+
+        :param observation: the current state
+        :return: the list of actions
+        """
+        self.steps += 1
+        replanning_required = self.step(self.previous_actions)
+        if replanning_required:
+            env = preprocess_env(self.env, self.config["env_preprocessors"])
+            actions = self.planner.plan(state=env, observation=observation)
+        else:
+            actions = self.previous_actions[1:]
+        self.write_tree()
+
+        self.previous_actions = actions
+        return actions
+
+    def step(self, actions):
+        """
+            Handle receding horizon mechanism
+        :return: whether a replanning is required
+        """
+        replanning_required = self.remaining_horizon == 0 or len(actions) <= 1
+        if replanning_required:
+            self.remaining_horizon = self.config["receding_horizon"] - 1
+        else:
+            self.remaining_horizon -= 1
+
+        self.planner.step(actions)
+        return replanning_required
+
+    def reset(self):
+        self.planner.step_by_reset()
+        self.steps = 0
+
+    def seed(self, seed=None):
+        return self.planner.seed(seed)
+
+    def record(self, state, action, reward, next_state, done, info):
+        pass
+
+    def act(self, state):
+        return self.plan(state)[0]
+
+    def save(self, filename):
[…]

### 2020-02-14 supplementary/code/rl_agents/agents/tree_search/deterministic.py

@@ -1,0 +1,121 @@
+import numpy as np
+import logging
+from rl_agents.agents.common.factory import safe_deepcopy_env
+from rl_agents.agents.tree_search.abstract import Node, AbstractTreeSearchAgent, AbstractPlanner
+
+logger = logging.getLogger(__name__)
+
+
+class DeterministicPlannerAgent(AbstractTreeSearchAgent):
+    """
+        An agent that performs optimistic planning in deterministic MDPs.
+    """
+    def make_planner(self):
+        return OptimisticDeterministicPlanner(self.env, self.config)
+
+
+class OptimisticDeterministicPlanner(AbstractPlanner):
+    """
+       An implementation of Optimistic Planning for Deterministic systems.
+    """
+    def __init__(self, env, config=None):
+        super().__init__(config)
+        self.env = env
+        self.leaves = None
+
+    def make_root(self):
+        root = DeterministicNode(None, planner=self)
+        self.leaves = [root]
+        return root
+
+    def run(self):
+        """
+            Run an OptimisticDeterministicPlanner episode
+        """
+        leaf_to_expand = max(self.leaves, key=lambda n: n.get_value_upper_bound())
+        if leaf_to_expand.done:
+            return
+        leaf_to_expand.expand()
+        leaf_to_expand.backup_to_root()
+
+    def plan(self, state, observation):
+        self.root.state = state
+        for epoch in np.arange(self.config["budget"] // state.action_space.n):
+            logger.debug("Expansion {}/{}".format(epoch + 1, self.config["budget"] // state.action_space.n))
+            self.run()
+
+        return self.get_plan()
+
+    def step_by_subtree(self, action):
+        super(OptimisticDeterministicPlanner, self).step_by_subtree(action)
+        if not self.root.children:
+            self.leaves = [self.root]
+        #  v0 = r0 + g r1 + g^2 r2 +... and v1 = r1 + g r2 + ... = (v0-r0)/g
+        for leaf in self.leaves:
+            leaf.value = (leaf.value - self.root.reward) / self.config["gamma"]
+            leaf.value_upper_bound = (leaf.value_upper_bound - self.root.reward) / self.config["gamma"]
+        self.root.backup_values()
+
+
+class DeterministicNode(Node):
+    def __init__(self, parent, planner, state=None, depth=0):
+        super(DeterministicNode, self).__init__(parent, planner)
+        self.state = state
+        self.depth = depth
+        self.reward = 0
+        self.value_upper_bound = 0
[…]

### 2020-02-14 supplementary/code/rl_agents/agents/tree_search/graphics/robust.py

@@ -1,0 +1,127 @@
+import matplotlib as mpl
+import numpy as np
+from matplotlib import cm as cm
+
+from rl_agents.agents.common.factory import preprocess_env
+from rl_agents.agents.tree_search.graphics.graphics import TreeGraphics
+
+
+class DiscreteRobustPlannerGraphics(TreeGraphics):
+    @classmethod
+    def display(cls, agent, agent_surface, sim_surface):
+        plan = agent.planner.get_plan()
+        for env in [preprocess_env(agent.true_env, preprocessors) for preprocessors in agent.config["models"]]:
+            IntervalRobustPlannerGraphics.display_uncertainty(env, plan, sim_surface, trajectory=False)
+            # for vehicle in env.road.vehicles:
+            #     if hasattr(vehicle, ):
+            #         IntervalRobustPlannerGraphics.display(vehicle)
+            # for vehicle in env.road.vehicles:
+            #     vehicle.trajectory = []
+            # for action in plan[:horizon] + (horizon - len(plan)) * [1]:
+            #     env.step(action)
+            # for vehicle in env.road.vehicles:
+            #     if vehicle is env.vehicle:
+            #         continue
+            #     uncertainty_surface = pygame.Surface(sim_surface.get_size(), pygame.SRCALPHA, 32)
+            #     IntervalRobustPlannerGraphics.display_trajectory(vehicle.trajectory, uncertainty_surface, sim_surface,
+            #                                                      IntervalRobustPlannerGraphics.MODEL_TRAJ_COLOR)
+            #     sim_surface.blit(uncertainty_surface, (0, 0))
+        TreeGraphics.display(agent, agent_surface)
+
+    @classmethod
+    def draw_node(cls, node, surface, origin, size, config):
+        import pygame
+        cmap = cm.jet_r
+        norm = mpl.colors.Normalize(vmin=0, vmax=config["gamma"] / (1 - config["gamma"]))
+        n = np.size(node.value)
+        for i in range(n):
+            v = node.value[i] if n > 1 else node.value
+            color = cmap(norm(v), bytes=True)
+            pygame.draw.rect(surface, color, (origin[0] + i / n * size[0], origin[1], size[0] / n, size[1]), 0)
+
+
+class IntervalRobustPlannerGraphics(object):
+    """
+        Graphical visualization of the IntervalRobustPlannerAgent interval observer.
+    """
+    UNCERTAINTY_TIME_COLORMAP = cm.RdYlGn
+    MODEL_TRAJ_COLOR = (0, 0, 255)
[…]

### 2020-02-14 supplementary/code/rl_agents/agents/tree_search/graphics/robust_epc.py

@@ -1,0 +1,108 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib.patches import Ellipse
+import matplotlib.transforms as transforms
+import matplotlib
+matplotlib.rc('text', usetex=True)
+import seaborn as sns
+import os
+
+from rl_agents.agents.tree_search.graphics.robust import IntervalRobustPlannerGraphics
+
+
+class RobustEPCGraphics(IntervalRobustPlannerGraphics):
+    SAVE_IMAGES = None
+
+    @classmethod
+    def display(cls, agent, agent_surface, sim_surface):
+        import pygame
+        robust_env = agent.robustify_env()
+        cls.display_uncertainty(robust_env=robust_env, plan=agent.get_plan(), surface=sim_surface)
+        if agent_surface and hasattr(agent, "sub_agent"):
+            true_theta = agent.env.unwrapped.dynamics.theta
+            surf_size = agent_surface.get_size()
+            figsize = (surf_size[0]/100, surf_size[1]/100)
+            save_to = None
+            if cls.SAVE_IMAGES:
+                save_to = agent.evaluation.run_directory / "ellipsoid.{}.{}.pdf".format(agent.evaluation.episode, len(agent.ellipsoids))
+            image_str, size = cls.plot_ellipsoid(agent.ellipsoids, true_theta, figsize=figsize, save_to=save_to)
+            surf = pygame.image.fromstring(image_str, size, "RGB")
+            agent_surface.blit(surf, (0, 0))
+
+    @classmethod
+    def display_uncertainty(cls, robust_env, plan, surface, trajectory=True):
+        import pygame
+        horizon = 3
+        if plan:
+            plan = plan[1:]  # First action has already been performed
+        plan = plan[:horizon]
+        for action in plan:
+            robust_env.step(action)
+        min_traj = [o[0] for o in robust_env.unwrapped.interval_trajectory]
+        max_traj = [o[1] for o in robust_env.unwrapped.interval_trajectory]
+        uncertainty_surface = pygame.Surface(surface.get_size(), pygame.SRCALPHA, 32)
+        cls.display_traj_uncertainty(min_traj, max_traj, uncertainty_surface, surface, cls.UNCERTAINTY_TIME_COLORMAP)
+        surface.blit(uncertainty_surface, (0, 0))
+
+    @classmethod
[…]

### 2020-02-14 supplementary/code/rl_agents/agents/tree_search/robust.py

@@ -1,0 +1,107 @@
+import numpy as np
+
+from rl_agents.agents.common.abstract import AbstractAgent
+from rl_agents.agents.common.factory import load_agent, preprocess_env
+from rl_agents.agents.tree_search.deterministic import DeterministicPlannerAgent, OptimisticDeterministicPlanner, \
+    DeterministicNode
+
+
+class DiscreteRobustPlannerAgent(DeterministicPlannerAgent):
+    def __init__(self,
+                 env,
+                 config=None):
+        self.true_env = env
+        super(DiscreteRobustPlannerAgent, self).__init__(env, config)
+
+    def make_planner(self):
+        return DiscreteRobustPlanner(self.env, self.config)
+
+    @classmethod
+    def default_config(cls):
+        config = super(DiscreteRobustPlannerAgent, cls).default_config()
+        config.update(dict(models=[]))
+        return config
+
+    def plan(self, observation):
+        envs = [preprocess_env(self.true_env, preprocessors) for preprocessors in self.config["models"]]
+        self.env = JointEnv(envs)
+        return super(DiscreteRobustPlannerAgent, self).plan(observation)
+
+
+class JointEnv(object):
+    def __init__(self, envs):
+        self.joint_state = envs
+
+    def step(self, action):
+        transitions = [state.step(action) for state in self.joint_state]
+        observations, rewards, terminals, info = zip(*transitions)
+        return observations, np.array(rewards), np.array(terminals), info
+
+    @property
+    def action_space(self):
+        return self.joint_state[0].action_space
+
+    def get_available_actions(self):
+        return list(set().union(*[s.get_available_actions() if hasattr(s, "get_available_actions")
+                                  else range(s.action_space.n)
+                                  for s in self.joint_state]))
+
+
+class DiscreteRobustPlanner(OptimisticDeterministicPlanner):
+    def make_root(self):
+        root = RobustNode(parent=None, planner=self)
+        self.leaves = [root]
+        return root
+
+    def run(self):
+        """
+            Run an OptimisticDeterministicPlanner episode
+        """
+        leaf_to_expand = max(self.leaves, key=lambda n: n.get_value_upper_bound())
+        leaf_to_expand.expand()
+        leaf_to_expand.backup_to_root()
+
+
+class RobustNode(DeterministicNode):
+    def get_value(self):
+        return np.min(self.value)
+
+    def get_value_upper_bound(self):
+        return np.min(self.value_upper_bound)
+
[…]

### 2020-02-14 supplementary/code/rl_agents/agents/tree_search/robust_epc.py

@@ -1,0 +1,178 @@
+import itertools
+import numpy as np
+
+from interval import LPV
+from rl_agents.agents.common.abstract import AbstractAgent
+from rl_agents.agents.common.factory import load_agent, safe_deepcopy_env
+
+
+class RobustEPCAgent(AbstractAgent):
+    """
+        Robust Estimation, Prediction and Control.
+    """
+
+    def __init__(self, env, config):
+        super().__init__(config)
+        self.A = np.array(self.config["A"])
+        self.B = np.array(self.config["B"])
+        self.phi = np.array(self.config["phi"])
+        self.env = env
+        self.env.unwrapped.automatic_record_callback = self.record_transition
+        self.data = []
+        self.robust_env = None
+        self.sub_agent = load_agent(self.config['sub_agent_path'], env)
+        self.ellipsoids = [self.ellipsoid()]
+
+    @classmethod
+    def default_config(cls):
+        return {
+            "gamma": 0.9,
+            "delta": 0.9,
+            "lambda": 1e-6,
+            "sigma": [[1]],
+            "A": [[1]],
+            "B": [[1]],
+            "D": [[1]],
+            "omega": [[0], [0]],
+            "phi": [[[1]]],
+            "simulation_frequency": 10,
+            "policy_frequency": 2,
+            "parameter_bound": 1
+        }
+
+    def record(self, state, action, reward, next_state, done, info):
+        """
+            Add a transition to the dataset D_[N].
+
+            The environment must be able to convert a discrete action to a continuous control.
+        :param state: state x_t at time t
+        :param action: action a_t performed
+        :param reward: reward r_t obtained
+        :param next_state: next state x_{t+dt} at time t+dt
+        :param done: is the state terminal
+        :param info: information about the transition
+        """
+        if hasattr(self.env.unwrapped, "automatic_record_callback"):
+            return
+        control = self.env.unwrapped.dynamics.action_to_control(action)
+        try:
+            derivative = self.env.unwrapped.dynamics.derivative
+        except AttributeError:
+            derivative = (next_state - state) * self.config["policy_frequency"]
+        self.record_transition((state, control, derivative))
+
+    def record_transition(self, state, derivative, control):
+        """
+            A callback that can be called by the environment in place of RobustEPCAgent.record(),
[…]

### 2020-02-14 supplementary/code/rl_agents/trainer/evaluation.py

@@ -1,0 +1,266 @@
+import datetime
+import json
+import logging
+import os
+from pathlib import Path
+import numpy as np
+from tensorboardX import SummaryWriter
+
+import rl_agents.trainer.logger
+from rl_agents.agents.common.graphics import AgentGraphics
+from rl_agents.configuration import serialize
+from rl_agents.trainer.graphics import RewardViewer
+from rl_agents.trainer.monitor import MonitorV2
+
+logger = logging.getLogger(__name__)
+
+
+class Evaluation(object):
+    """
+        The evaluation of an agent interacting with an environment to maximize its expected reward.
+    """
+
+    OUTPUT_FOLDER = 'out'
+    SAVED_MODELS_FOLDER = 'saved_models'
+    RUN_FOLDER = 'run_{}_{}'
+    METADATA_FILE = 'metadata.{}.json'
+    LOGGING_FILE = 'logging.{}.log'
+
+    def __init__(self,
+                 env,
+                 agent,
+                 directory=None,
+                 run_directory=None,
+                 num_episodes=1000,
+                 training=True,
+                 sim_seed=None,
+                 recover=None,
+                 display_env=True,
+                 display_agent=True,
+                 display_rewards=True,
+                 close_env=True):
+        """
+
+        :param env: The environment to be solved, possibly wrapping an AbstractEnv environment
+        :param AbstractAgent agent: The agent solving the environment
+        :param Path directory: Workspace directory path
+        :param Path run_directory: Run directory path
+        :param int num_episodes: Number of episodes run
+        !param training: Whether the agent is being trained or tested
+        :param sim_seed: The seed used for the environment/agent randomness source
+        :param recover: Recover the agent parameters from a file.
+                        - If True, it the default latest save will be used.
+                        - If a string, it will be used as a path.
+        :param display_env: Render the environment, and have a monitor recording its videos
+        :param display_agent: Add the agent graphics to the environment viewer, if supported
+        :param display_rewards: Display the performances of the agent through the episodes
+        :param close_env: Should the environment be closed when the evaluation is closed
+
+        """
+        self.env = env
+        self.agent = agent
+        self.num_episodes = num_episodes
+        self.training = training
+        self.sim_seed = sim_seed
+        self.close_env = close_env
+        self.display_env = display_env
+
+        self.directory = Path(directory or self.default_directory)
+        self.run_directory = self.directory / (run_directory or self.default_run_directory)
[…]

### 2020-02-14 supplementary/code/rl_agents/trainer/monitor.py

@@ -1,0 +1,188 @@
+import json
+import logging
+import os
+
+from gym.wrappers import Monitor
+from gym.wrappers.monitor import detect_training_manifests, collapse_env_infos, merge_stats_files
+from gym.wrappers.monitoring import video_recorder
+from gym.wrappers.monitoring.stats_recorder import StatsRecorder
+from gym.utils import atomic_write
+from gym.utils.json_utils import json_encode_np
+
+logger = logging.getLogger(__name__)
+
+
+class MonitorV2(Monitor):
+    """
+        A modified Environment Monitor that includes the following features:
+
+        - The stats recorder is a StatsRecorderV2, that implements additional features, including the environment seed
+        at each episode so that they can be reproduced
+        - The wrapped environment is closed with the monitor
+        - Video recording of all frames during an ongoing environment step
+        - Automatic saving of all fields of the stats recorder
+    """
+
+    def __init__(self, env, directory, video_callable=None, force=False, resume=True,
+                 write_upon_reset=False, uid=None, mode=None):
+        super(MonitorV2, self).__init__(env, directory, video_callable, force, resume, write_upon_reset, uid, mode)
+
+    def _start(self, directory, video_callable=None, force=False, resume=False, write_upon_reset=False, uid=None,
+               mode=None):
+        super(MonitorV2, self)._start(directory, video_callable, force, resume, write_upon_reset, uid, mode)
+        self.stats_recorder = StatsRecorderV2(directory,
+                                              '{}.episode_batch.{}'.format(self.file_prefix, self.file_infix)
+                                              , autoreset=self.env_semantics_autoreset, env_id=self.env.spec.id)
+
+    def seed(self, seed=None):
+        seeds = super(MonitorV2, self).seed(seed)
+        self.stats_recorder.seed = seeds[0]  # Not sure why gym envs typically return *a list* of one seed
+        return seeds
+
+    def reset_video_recorder(self):
+        # Close any existing video recorder
+        if self.video_recorder:
+            self._close_video_recorder()
+
+        # Start recording the next video.
+        self.video_recorder = video_recorder.VideoRecorder(
+            env=self.env,
+            base_path=os.path.join(self.directory,
+                                   '{}.video.{}.video{:06}'.format(self.file_prefix, self.file_infix, self.episode_id)),
+            metadata={'episode_id': self.episode_id},
+            enabled=self._video_enabled(),
+        )
+
+        # Instead of capturing just one frame, allow the environment to send all render frames when a step is ongoing
[…]

### 2020-02-14 supplementary/code/scripts/experiments.py

@@ -1,0 +1,68 @@
+"""
+Usage:
+  experiments evaluate <environment> <agent> [options]
+  experiments -h | --help
+
+Options:
+  -h --help              Show this screen.
+  --episodes <count>     Number of episodes [default: 1].
+  --no-display           Disable environment, agent, and rewards rendering.
+  --name-from-config     Name the output folder from the corresponding config files
+  --seed <str>           Seed the environments and agents.
+  --verbose              Set log level to debug instead of info.
+  --repeat <times>       Repeat several times [default: 1].
+"""
+import datetime
+import os
+from pathlib import Path
+from docopt import docopt
+
+from rl_agents.agents.common.factory import load_environment, load_agent
+from rl_agents.trainer import logger
+from rl_agents.trainer.evaluation import Evaluation
+
+BENCHMARK_FILE = 'benchmark_summary'
+LOGGING_CONFIG = 'configs/logging.json'
+VERBOSE_CONFIG = 'configs/verbose.json'
+
+
+def main():
+    opts = docopt(__doc__)
+    for _ in range(int(opts['--repeat'])):
+        evaluate(opts['<environment>'], opts['<agent>'], opts)
+
+
+def evaluate(environment_config, agent_config, options):
+    """
+        Evaluate an agent interacting with an environment.
+
+    :param environment_config: the path of the environment configuration file
+    :param agent_config: the path of the agent configuration file
+    :param options: the evaluation options
+    """
+    logger.configure(LOGGING_CONFIG)
+    if options['--verbose']:
+        logger.configure(VERBOSE_CONFIG)
+    env = load_environment(environment_config)
+    agent = load_agent(agent_config, env)
+    run_directory = None
+    if options['--name-from-config']:
+        run_directory = "{}_{}_{}".format(Path(agent_config).with_suffix('').name,
+                                  datetime.datetime.now().strftime('%Y%m%d-%H%M%S'),
+                                  os.getpid())
+    options['--seed'] = int(options['--seed']) if options['--seed'] is not None else None
+    evaluation = Evaluation(env,
+                            agent,
+                            run_directory=run_directory,
+                            num_episodes=int(options['--episodes']),
+                            sim_seed=options['--seed'],
+                            recover=False,
+                            display_env=not options['--no-display'],
+                            display_agent=not options['--no-display'],
+                            display_rewards=not options['--no-display'])
+    evaluation.test()
+    return os.path.relpath(evaluation.monitor.directory)
+
+
+if __name__ == "__main__":
+    main()

### 2020-02-14 main.tex
Add supplmentary description

@@
 \usepackage{comment}
+\usepackage{listings}
 \def\sectionautorefname{Section}
@@
 In \autoref{sec:proof}, we provide a proof for every novel result introduced in this paper.
-\autoref{sec:tight-polytope} describes a better method of conversion from ellipsoid to polytope than that of \eqref{eq:polytope}.
+\autoref{sec:attachments} describes the attached video files and source code.
+\autoref{sec:tight-polytope} gives a better method of conversion from ellipsoid to polytope than that of \eqref{eq:polytope}.
 \autoref{sec:min-max-order} highlights the fact that robustness cannot be recovered by aggregating independent solutions to many optimal control problem.
-Finally, \autoref{sec:experimental-setting} gives additional details on the setting of our experiments.
+Finally, \autoref{sec:experimental-setting} provides additional details on the setting of our experiments.
 
@@
 \end{proof}
+
+\section{Description of attached files}
+\label{sec:attachments}
+
+\paragraph{Videos}
+The \texttt{video} folder contains videos comparing trajectories of the oracle planner and \autoref{alg:full}.
+The oracle planner has access to the true dynamics and follows aggressive trajectories that nearly saturate the collision constraints.
+In contrast, the \autoref{alg:full} produces more conservative trajectories.
+In the obstacle experiment, we show the confidence ellipsoid over $\theta = (\theta_x,\theta_y)$ in the right panel.
+In the driving experiment, we show the multi-model rejection and robust selection procedure through the display of several trajectory hulls for all possible destinations of the observed vehicles.
+
+\paragraph{Source code}
+We describe where the main contributions of this work are implemented in the attached code.
+\begin{enumerate}
+	\item The confidence ellipsoid \eqref{eq:confidence-ellipsoid} is implemented in the \texttt{ellipsoid()} method in \url{code/rl_agents/agents/tree_search/robust_epc.py}
+	\item The corresponding polytope \eqref{eq:polytope} is implemented in the \texttt{polytope()} method of \url{code/rl_agents/agents/tree_search/robust_epc.py}
+	\item The simple predictor of \eqref{eq:predictor-naive} is implemented in the \texttt{step\_simple\_predictor()} method of \url{code/rl_agents/agents/common/interval.py}
+	\item The enhanced predictor of \eqref{eq:interval-predictor} is implemented in the \texttt{step\_interval\_predictor()} method of \url{code/rl_agents/agents/common/interval.py}
+	\item The pessimistic reward of \eqref{eq:pessimistic-rewards} is implemented in the \texttt{pessimistic\_reward()} method of \url{code/obstacle_env/envs/obstacle.py} and the \texttt{check\_collision()} method of \url{code/highway_env/vehicle/uncertainty/prediction.py}
+	\item The robust upper-bound of \eqref{eq:robust-b-values} is implemented in the \texttt{RobustNode} class of \url{code/rl_agents/agents/tree_search/robust.py}
+\end{enumerate}
+The experiments can be reproduced by running:
+\lstset{language=bash}
+\begin{lstlisting}
+cd scripts
+python experiments.py configs/<env>/env.json configs/<env>/agents/<agent>.json
+\end{lstlisting}
 

### 2020-02-20 main.tex
Soothe my bleeding eyes
Minor change

@@
 We compare \autoref{alg:full} to a nominal agent planning with the estimated parameter $\theta_{[N],\lambda}$, with two different modelling assumptions: we assume that Nominal 1 has access to the true followed route for each vehicle, while Nominal 2 does not and picks a model with minimal prediction error.
-There performances are compared in \autoref{tab:driving}.
+Their performances are compared in \autoref{tab:driving}.
 Again, the robust approach is less efficient on average than planning with a nominal model, but it does better in terms of worst-case performance and manages to avoid collisions, contrary to the nominal baselines that suffer from model bias.
@@
 \paragraph{Source code}
-We describe where the main contributions of this work are implemented in the attached code.
+The attached \texttt{code} directory contains an implementation of \autoref{alg:full}. We relate the algorithmic steps of this paper to their location in the source code.
 \begin{enumerate}

### 2020-02-21 main.tex
Preprint version
Updates from Overleaf

@@
 % Use the following line for the initial blind version submitted for review:
-\usepackage{icml2020}
+%\usepackage{icml2020}
 
 % If accepted, instead use the following line for the camera-ready submission:
-%\usepackage[accepted]{icml2020}
+\usepackage[accepted,preprint]{icml2020}
 
@@
 		\icmlauthor{Denis Efimov}{val}
-		\icmlauthor{Odalric Ambrym-Maillard}{seq}
+		\icmlauthor{Odalric-Ambrym Maillard}{seq}
 	\end{icmlauthorlist}
 
-	\icmlaffiliation{seq}{Inria Lille Nord-Europe, Sequel Project, Lille, France}
+	\icmlaffiliation{seq}{Inria Lille Nord-Europe, SequeL Project, Lille, France}
 	\icmlaffiliation{val}{Inria Lille Nord-Europe, Valse Project, Lille, France}
@@
 This reachability set is used to provide a conservative pessimistic reward to the planning algorithm.
-The next section aims to clarify and formalize these ideas, and state our contributions.
+The next section aims to clarify and formalise these ideas, and state our contributions.
 
@@
 \citet{Ouyang2017,abeille18a} provide the same result by applying Thomson Sampling rather of optimism to select a dynamical model, and rejection sampling to enforce the controllability constraint.
-These methods aim at regret minimization to quickly reduce uncertainty, through information-seeking behaviours.
+These methods aim at regret minimisation to quickly reduce uncertainty, through information-seeking behaviours.
 Other works use noise injection for exploration such as \citep{Dean2017,Dean2018}.
-However, neither optimism and cumulative regret minimization nor random exploration fit a critical setting, where ensuring safety as a top priority requires instead to consider the pessimistic outcomes.
-The work of \citet{Dean2017} is closest to our setting: after an offline estimation phase, where the controls do not aim at regret minimization, they estimate a simple regret between a robust controller and the optimal performance.
+However, neither optimism and cumulative regret minimisation nor random exploration fit a critical setting, where ensuring safety as a top priority requires instead to consider the pessimistic outcomes.
+The work of \citet{Dean2017} is closest to our setting: after an offline estimation phase, where the controls do not aim at regret minimisation, they estimate a simple regret between a robust controller and the optimal performance.
 Our work mainly differs in that it addresses generic costs and forbids random exploration.
@@
 \paragraph{Robust planning}
-Robust optimization with generic costs has also been studied in the context of finite Markov Decision Processes with uncertain parameters by \citet{Iyengar2005}, \citet{Nilim2005} and \citet{Wiesemann2013}.
+Robust optimisation with generic costs has also been studied in the context of finite Markov Decision Processes with uncertain parameters by \citet{Iyengar2005}, \citet{Nilim2005} and \citet{Wiesemann2013}.
 They showed that the main results of Dynamic Programming can be extended to their robust counterparts only when the dynamics ambiguity set verifies a certain rectangularity property, that amounts to an independence assumption between the uncertainty sets of each transition and is related to time-varying uncertainty.
@@
 \end{equation*}
-with probability at least $1-\delta$, where $\Delta_\omega$ is a constant which corresponds to an irreductible suboptimality suffered from being robust to instantaneous perturbations $\omega(t)$.
+with probability at least $1-\delta$, where $\Delta_\omega$ is a constant which corresponds to an irreducible suboptimality suffered from being robust to instantaneous perturbations $\omega(t)$.
 \end{theorem}
@@
 In both experiments, we used $\gamma=0.9$,  $\delta=0.9$ and a planning budget $K=100$.
-The perturbations were sampled uniformly in $[-0.1, 0.1]^r$ while the measurements are gaussian with covariance $\Sigma_r = 0.1 I_s$.
+The perturbations were sampled uniformly in $[-0.1, 0.1]^r$ while the measurements are Gaussian with covariance $\Sigma_r = 0.1 I_s$.
 

### 2020-03-12 main.tex
Updates from Overleaf
Fix typo in Prop 2

@@
 These controls are then optimised resorting to tree-based planning methods.
-We eventually relax our modeling assumptions with a multi-model extension based on a data-driven robust model selection mechanism.
+We eventually relax our modelling assumptions with a multi-model extension based on a data-driven robust model selection mechanism.
 The full procedure is designed to produce reasonable and safe behaviours at deployment while recovering an asymptotic optimality.
@@
 \begin{align*}
-\| S_n \|_{\overline{G}_n^{-1}} \geq \sqrt{2\ln \left(\frac{\det\left(\overline{G}_n\right)^{1/2}}{\delta\det(G)^{1/2}}\right)}.
+\| S_n \|_{\overline{G}_n^{-1}} \leq \sqrt{2\ln \left(\frac{\det\left(\overline{G}_n\right)^{1/2}}{\delta\det(G)^{1/2}}\right)}.
 \end{align*}
@@
 	&h_k \text{ is the }k^\text{th}\text{ element of }\{-1,1\}^d\text{ for } k\in[2^d],\\
-	&G_{N,\lambda} = PDP^{-1}, \quad \Delta\theta_k = \beta_{N}(\delta)^{1/2} P^{-1}D^{-1/2} h_k, \\
+	&G_{N,\lambda} = PDP^{-1}, \quad \Delta\theta_k = \beta_{N}(\delta)P^{-1}D^{-1/2} h_k, \\
 	&A_0 = A + \theta_{N,\lambda}^\transp\Phi, \quad \Delta A_k = \Delta\theta_k^\transp\Phi.
@@
 	\theta\in\cC_\delta &\implies
-	(\theta-\theta_{N,\lambda})^\transp G_{N,\lambda}(\theta-\theta_{N,\lambda}) \leq \beta_{N}(\delta)\\
-	&\implies (\theta'-\theta'_{N,\lambda})^\transp D (\theta'-\theta'_{N,\lambda}) \leq \beta_{N}(\delta)\\
-	&\implies \sum_{i=1}^d D_{i,i}(\theta'_i-\theta'_{N,\lambda,i})^2\leq \beta_{N}(\delta)\\
-	&\implies\forall i, |\theta'_i-\theta'_{N,\lambda,i}|\leq \beta_{N}(\delta)^{1/2}D_{i,i}^{-1/2}
-	\end{align*}
-	This describes a $\Real^d$ box containing $\theta' = P\theta$, whose $k^\text{th}$ vertex is represented by $\theta_{N,\lambda}' + \beta_{N}(\delta)^{1/2}D^{-1/2} h_k$.
+	(\theta-\theta_{N,\lambda})^\transp G_{N,\lambda}(\theta-\theta_{N,\lambda}) \leq \beta_{N}(\delta)^2\\
+	&\implies (\theta'-\theta'_{N,\lambda})^\transp D (\theta'-\theta'_{N,\lambda}) \leq \beta_{N}(\delta)^2\\
+	&\implies \sum_{i=1}^d D_{i,i}(\theta'_i-\theta'_{N,\lambda,i})^2\leq \beta_{N}(\delta)^2\\
+	&\implies\forall i, |\theta'_i-\theta'_{N,\lambda,i}|\leq D_{i,i}^{-1/2}\beta_{N}(\delta)
+	\end{align*}
+	This describes a $\Real^d$ box containing $\theta' = P\theta$, whose $k^\text{th}$ vertex is represented by $\theta_{N,\lambda}' + \beta_{N}(\delta)D^{-1/2} h_k$.
 We obtain the corresponding box on $\theta$ by transforming each vertex of the box with $P^{-1}$.

### 2020-05-04 main.tex
Use neurips template and try to compress

@@
-%%%%%%%% ICML 2020 EXAMPLE LATEX SUBMISSION FILE %%%%%%%%%%%%%%%%%
-
 \documentclass{article}
 
+% if you need to pass options to natbib, use, e.g.:
+%     \PassOptionsToPackage{numbers, compress}{natbib}
+% before loading neurips_2020
+
+% ready for submission
+ \usepackage{neurips_2020}
+
+% to compile a preprint version, e.g., for submission to arXiv, add add the
+% [preprint] option:
+%     \usepackage[preprint]{neurips_2020}
+
+% to compile a camera-ready version, add the [final] option, e.g.:
+%     \usepackage[final]{neurips_2020}
+
+% to avoid loading the natbib package, add option nonatbib:
+%\usepackage[nonatbib]{neurips_2020}
+
+\usepackage[utf8]{inputenc} % allow utf-8 input
+\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
+\usepackage{hyperref}       % hyperlinks
+\usepackage{url}            % simple URL typesetting
+\usepackage{booktabs}       % professional-quality tables
+\usepackage{amsfonts}       % blackboard math symbols
+\usepackage{nicefrac}       % compact symbols for 1/2, etc.
+\usepackage{microtype}      % microtypography
+
 % Custom packages
+\usepackage{graphicx}
+\usepackage{subfigure}
 \usepackage{amsthm}
@@
 \usepackage{listings}
+\usepackage{algorithm}
+\usepackage{algorithmic}
+
 \def\sectionautorefname{Section}
@@
 
-% Recommended, but optional, packages for figures and better typesetting:
-\usepackage{microtype}
-\usepackage{graphicx}
-\usepackage{subfigure}
-\usepackage{booktabs} % for professional tables
-
-% hyperref makes hyperlinks in the resulting PDF.
-% If your build breaks (sometimes temporarily if a hyperlink spans a page)
-% please comment out the following usepackage line and replace
-% \usepackage{icml2020} with \usepackage[nohyperref]{icml2020} above.
-\usepackage{hyperref}
-
-% Attempt to make hyperref and algorithmic work together better:
-\newcommand{\theHalgorithm}{\arabic{algorithm}}
-
-% Use the following line for the initial blind version submitted for review:
-%\usepackage{icml2020}
-
-% If accepted, instead use the following line for the camera-ready submission:
-\usepackage[accepted,preprint]{icml2020}
-
-% The \icmltitle you define below is probably too long as a header.
-% Therefore, a short form for the running title is supplied here:
-\icmltitlerunning{Robust Estimation, Prediction and Control}
+\title{Robust Estimation, Prediction and Control with \\ Linear Dynamics and Generic Costs}
+
+% The \author macro works with any number of authors. There are two commands
+% used to separate the names and addresses of multiple authors: \And and \AND.
+%
+% Using \And between authors leaves it to LaTeX to determine where to break the
+% lines. Using \AND forces a line break at that point. So, if LaTeX puts 3 of 4
+% authors names on the first line, and the last on the second line, try using
+% \AND instead of \And before the third author name.
+
+\author{%
+	David S.~Hippocampus\thanks{Use footnote for providing further information
+		about author (webpage, alternative address)---\emph{not} for acknowledging
+		funding agencies.} \\
+	Department of Computer Science\\
+	Cranberry-Lemon University\\
+	Pittsburgh, PA 15213 \\
+	\texttt{hippo@cs.cranberry-lemon.edu} \\
+	% examples of more authors
+	% \And
+	% Coauthor \\
+	% Affiliation \\
+	% Address \\
+	% \texttt{email} \\
+	% \AND
+	% Coauthor \\
+	% Affiliation \\
+	% Address \\
+	% \texttt{email} \\
+	% \And
+	% Coauthor \\
+	% Affiliation \\
+	% Address \\
+	% \texttt{email} \\
+	% \And
+	% Coauthor \\
+	% Affiliation \\
+	% Address \\
+	% \texttt{email} \\
+}
 
 \begin{document}
-
-	\twocolumn[
-	\icmltitle{Robust Estimation, Prediction and Control with \\ Linear Dynamics and Generic Costs}
-
-	% It is OKAY to include author information, even for blind
-	% submissions: the style file will automatically remove it for you
-	% unless you've provided the [accepted] option to the icml2020
-	% package.
-
-	% List of affiliations: The first argument should be a (short)
-	% identifier you will use later to specify author affiliations
-	% Academic affiliations should list Department, University, City, Region, Country
-	% Industry affiliations should list Company, City, Region, Country
-
-	% You can specify symbols, otherwise they are numbered in order.
-	% Ideally, you should not use this facility. Affiliations will be numbered
-	% in order of appearance and this is the preferred way.
-	\icmlsetsymbol{equal}{*}
-
-	\begin{icmlauthorlist}
-		\icmlauthor{Edouard Leurent}{seq,val,ren}
-		\icmlauthor{Denis Efimov}{val}
-		\icmlauthor{Odalric-Ambrym Maillard}{seq}
-	\end{icmlauthorlist}
-
-	\icmlaffiliation{seq}{Inria Lille Nord-Europe, SequeL Project, Lille, France}
-	\icmlaffiliation{val}{Inria Lille Nord-Europe, Valse Project, Lille, France}
-	\icmlaffiliation{ren}{Renault Group, Guyancourt, France}
-
-	\icmlcorrespondingauthor{Edouard Leurent}{edouard.leurent@inria.fr}
-
-	% You may provide any keywords that you
-	% find helpful for describing your paper; these are used to populate
-	% the "keywords" metadata in the PDF but will not be shown in the document
-	\icmlkeywords{Machine Learning, ICML}
-
-	\vskip 0.3in
-	]
-
-	% this must go after the closing bracket ] following \twocolumn[ ...
-
-	% This command actually creates the footnote in the first column
-	% listing the affiliations and the copyright notice.
-	% The command takes one argument, which is text to display at the start of the footnote.
-	% The \icmlEqualContribution command is standard text for equal contribution.
-	% Remove it (just {}) if you do not need this facility.
-
-	\printAffiliationsAndNotice{}  % leave blank if no need to mention equal contribution
-%	\printAffiliationsAndNotice{\icmlEqualContribution} % otherwise use the standard text.
 
@@
 	\centering
-	\includegraphics[trim={0 2cm 0 0}, clip, width=0.6\linewidth]{img/ellipsoid}
+	\includegraphics[trim={0 2cm 0 0}, clip, width=0.3\linewidth]{img/ellipsoid}
 	\caption{The model estimation procedure, running on the obstacle avoidance problem of \autoref{sec:experiments}. The confidence region $C_{[N],\delta}$ shrinks with the number of samples $N$.}
@@
 	\centering
-	\includegraphics[width=0.8\linewidth]{img/obstacle_small}
+	\includegraphics[trim={4cm 0 0 0}, clip, width=0.3\linewidth]{img/obstacle_small}
 	\caption{The state prediction procedure running on the obstacle avoidance problem of \autoref{sec:experiments}.
@@
 	\begin{algorithmic}
-		\STATE {\bfseries Input:} confidence level $\delta$, structure $(A,\phi)$, reward $R$
-		\STATE $\cD_{[0]}\gets\emptyset,\, \ba_1\gets\emptyset$
+		\STATE {\bfseries Input:} confidence level $\delta$, structure $(A,\phi)$, reward $R$, $\cD_{[0]}\gets\emptyset,\, \ba_1\gets\emptyset$
 		\FOR{$N = 0,1,2,\dots$} 
@@
 		\FOR{each planning step $k\in[K]$}
-		\FOR{each action $b\in \cA$}
-		\STATE $[\underline{x}_{n+1}, \overline{x}_{n+1}]\gets$ \textsc{Interval Prediction}(
-		\STATE $\qquad\qquad\qquad\qquad\cC_{[N],\delta}, \ba_kb$). \eqref{eq:interval-predictor}
+		\STATE $[\underline{x}_{n+1}, \overline{x}_{n+1}]\gets$ \textsc{Interval Prediction}($\cC_{[N],\delta}, \ba_kb$) for each action $b\in \cA$. \eqref{eq:interval-predictor}
+
+		\STATE $\ba_{k+1}$ $\gets$\textsc{Pessimistic Planning}$(\underline{R_{n+1}}([\underline{x}_{n+1}, \overline{x}_{n+1}]))$.  \eqref{eq:opd}
 		\ENDFOR
-		\STATE $\ba_{k+1}$ $\gets$\textsc{Pessimistic Planning}$($
-		\STATE$\qquad\qquad\underline{R_{n+1}}([\underline{x}_{n+1}, \overline{x}_{n+1}]))$.  \eqref{eq:opd}
-		\ENDFOR
-		\STATE Execute the recommended control $u_{N+1}$, and add the observed transition $(x_{N+1}, y_{N+1}, u_{N+1})$ to $\cD_{[N+1]}$.
+		\STATE Execute the control $u_{N+1}$, and add the observed transition $(x_{N+1}, y_{N+1}, u_{N+1})$ to $\cD_{[N+1]}$.
 		\ENDFOR
@@
     \label{eq:vector_rls}
-    \theta_{N,\lambda} &= G_{N, \lambda}^{-1} \sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1} y_n,\\
-	\label{eq:g_n_lambda}
-    \text{where }\quad G_{N, \lambda} &= \sum_{n=1}^N \Phi_{n}^\transp\Sigma_p^{-1}\Phi_{n}  + \lambda I_d \in \Real^{d\times d}.
+    \theta_{N,\lambda} = G_{N, \lambda}^{-1} \sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1} y_n,\qquad
+%    \label{eq:g_n_lambda}
+    \text{where }\quad G_{N, \lambda} = \sum_{n=1}^N \Phi_{n}^\transp\Sigma_p^{-1}\Phi_{n}  + \lambda I_d \in \Real^{d\times d}.
 \end{align}
@@
 Substituting $y_n$ into \eqref{eq:vector_rls} yields the regression error:
-\begin{align}
+$
     \theta_{N,\lambda} - \theta = G_{N, \lambda}^{-1}\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\eta_n - \lambda G_{N, \lambda}^{-1}\theta.
-\end{align}
-
-Depending on the assumption we have over the noise $\eta_n$, we can bound this error in different ways.
-
-\subsection{Bounded noise}
-
-\begin{assumption}[Bounded noise]
-\label{assumpt:bounded-noise}
-The noise $\eta(t)$ is bounded in $\|\cdot\|_\infty$.
-\end{assumption}
-
-In particular, we denote the coefficient-wise bounds over perturbations as $\underline{\omega}(t) \leq \omega(t) \leq \overline{\omega}(t)$.
+$
+
+To bound this error, we need the noise $\eta_n$ to concentrate.
+%Depending on the assumption we have over the noise $\eta_n$, we can bound this error in different ways.
+%
+%\subsection{Bounded noise}
+%
+%\begin{assumption}[Bounded noise]
+%\label{assumpt:bounded-noise}
+%The noise $\eta(t)$ is bounded in $\|\cdot\|_\infty$.
+%\end{assumption}
+%
+%In particular, we denote the coefficient-wise bounds over perturbations as $\underline{\omega}(t) \leq \omega(t) \leq \overline{\omega}(t)$.
 This is a deterministic assumption, then by Hölder inequality a confidence region $\cC_{[N],0}$ can be derived based on a $L_1$-ball estimate of $\theta$ at time $N$, i.e.
 a polytope with $2d$ vertices:
-\begin{equation}
-\label{eq:bounded-noise-polytope}
-\|\theta_{N,\lambda}\! -\! \theta\|_1\! \leq \! \|G_{N, \lambda}^{-1}\!\sum_{n=1}^N \!\Phi_n^\transp\! \Sigma_p^{-1}\!\|_1\|\eta\|_\infty\! +\!\lambda\|G_{N, \lambda}^{-1}\!\|_1S
-\end{equation}
-
-There may be cases where \autoref{assumpt:bounded-noise} does not hold.
+%\begin{equation}
+%\label{eq:bounded-noise-polytope}
+%\|\theta_{N,\lambda}\! -\! \theta\|_1\! \leq \! \|G_{N, \lambda}^{-1}\!\sum_{n=1}^N \!\Phi_n^\transp\! \Sigma_p^{-1}\!\|_1\|\eta\|_\infty\! +\!\lambda\|G_{N, \lambda}^{-1}\!\|_1S
+%\end{equation}
+%
+%There may be cases where \autoref{assumpt:bounded-noise} does not hold.
 For instance, when the noise $\eta$ is Gaussian, then $\|\eta\|_\infty=+\infty$ which makes \eqref{eq:bounded-noise-polytope} uninformative.
 Then, another probabilistic assumption can be made.
-
-\subsection{Sub-Gaussian noise}
+%
+%\subsection{Sub-Gaussian noise}
 
@@
 For instance, it is the case when $\nu$ and $\omega$ are Gaussian noises with covariance matrices $\Sigma_r$ and $\Sigma_s$, with $\Sigma_p \eqdef C\Sigma_r C^\transp + D\Sigma_s D^\transp$. 
-Note that \autoref{assumpt:bounded-noise} implies that $\eta$ is sub-Gaussian with covariance proxy $\Sigma_p=\|\eta\|_\infty I_p$.
+%Note that \autoref{assumpt:bounded-noise} implies that $\eta$ is sub-Gaussian with covariance proxy $\Sigma_p=\|\eta\|_\infty I_p$.
 
@@
     \label{eq:confidence-ellipsoid}
-    \| \theta_{N,\lambda}  - \theta\|_{G_{N,\lambda}} \leq \beta_N(\delta),
-\end{align}
-with
-\begin{equation}
-	\label{eq:beta_n}
+    \| \theta_{N,\lambda}  - \theta\|_{G_{N,\lambda}} \leq \beta_N(\delta), \quad \text{with}\quad
+%	\label{eq:beta_n}
     \beta_N(\delta)\eqdef \sqrt{2\ln \left(\frac{\det(G_{N,\lambda})^{1/2}}{\delta\det(\lambda I_d)^{1/2}}\right)}
      + (\lambda d)^{1/2}S.
-\end{equation}
+\end{align}
 \end{theorem}
@@
     \label{eq:polytope}
-     &\cC_{[N],\delta} = \left\{ A_{0}+\sum_{i=1}^{2^d}\alpha_{i}\Delta A_{i}: \alpha\geq 0,  \sum_{i=1}^{2^d}\alpha_{i}=1\right\}
+     \cC_{[N],\delta} = \left\{ A + \theta_{N,\lambda}^\transp\phi +\sum_{i=1}^{2^d}\alpha_{i}\Delta A_{i}: \alpha\geq 0,  \sum_{i=1}^{2^d}\alpha_{i}=1\right\} \text{ where }\Delta A_{i} = {h_i} \sqrt{\frac{\beta_N(\delta)}{\lambda_{\max}(G_{N,\lambda})}}, h_i\in\{-1,1\}^d.
 \end{align}
-where $A_{0,N} = A + \theta_{N,\lambda}^\transp\phi, \Delta A_{i} = {h_i} \sqrt{\frac{\beta_N(\delta)}{\lambda_{\max}(G_{N,\lambda})}}, h_i\in\{-1,1\}^d$.
 Another strategy presented in the Supplementary Material produces a much tighter polytope, at the price of an increased computational cost required by the diagonalisation of $G_{N,\lambda}$.
@@
 \paragraph{Remark} The robust objective \eqref{eq:robust-control} involves bounds $\underline{\omega}(t)\leq \omega(t) \leq \overline{\omega}(t)$ over the possible perturbations we want to protect against.
-In the unbounded sub-Gaussian noise setting of \autoref{assumpt:gaussian-noise}, we can use the same formulation by deriving local high-confidence bounds that each holds with confidence $\delta_n$.
-By choosing $\delta_n = \frac{\delta}{n(n+1)}$, the event $\{\forall n, \underline{\omega}(t_n) \leq \omega(t_n) \leq \overline{\omega}(t_n)\}$ holds with probability $1-\delta$.
+We use local bounds that each holds with confidence $\delta_n = \frac{\delta}{n(n+1)}$, so that the event $\{\forall n, \underline{\omega}(t_n) \leq \omega(t_n) \leq \overline{\omega}(t_n)\}$ holds with probability $1-\delta$.
 
@@
 We represent an interval as $X(t) = [\underline{x}(t), \overline{x}(t)]\in \Real^p\times \Real^p$, and \eqref{eq:inclusion-generic} becomes:
-\begin{equation}
-\label{eq:inclusion-property}
-\underline{x}(t)\leq x(t)\leq\overline{x}(t),\quad\forall t\geq t_N.
-\end{equation}
-
-A simple solution to \eqref{eq:inclusion-property} is proposed in \citep{Efimov2012}, where, given bounds $\underline{A}\leq A(\theta)\leq\overline{A}$ from $\cC_{[N],\delta}$ they use matrix interval arithmetic to derive the predictor:
+$
+%\label{eq:inclusion-property}
+\underline{x}(t)\leq x(t)\leq\overline{x}(t), \forall t\geq t_N.
+$
+A simple solution to \eqref{eq:inclusion-generic} is proposed in \citep{Efimov2012}, where, given bounds $\underline{A}\leq A(\theta)\leq\overline{A}$ from $\cC_{[N],\delta}$ they use matrix interval arithmetic to derive the predictor:
 \begin{proposition}[Simple predictor of \citealt{Efimov2012}]
-Assuming that \eqref{eq:confidence} is satisfied for the system \eqref{eq:dynamics}, then the interval predictor:
+Assuming that \eqref{eq:confidence} is satisfied for the system \eqref{eq:dynamics}, then the interval predictor following $\underline{x}(t_N)=\overline{x}(t_N)={x}(t_N)$ and:
 \begin{eqnarray}
-\dot{\underline{x}}(t) & = & \underline{A}^{+}\underline{x}^{+}(t)-\overline{A}^{+}\underline{x}^{-}(t)-\underline{A}^{-}\overline{x}^{+}(t) +\overline{A}^{-}\overline{x}^{-}(t)\nonumber \\
- &  &+Bu(t) + D^{+}\underline{\omega}(t)-D^{-}\overline{\omega}(t),\label{eq:predictor-naive}\\
-\dot{\overline{x}}(t) & = & \overline{A}^{+}\overline{x}^{+}(t)-\underline{A}^{+}\overline{x}^{-}(t)-\overline{A}^{-}\underline{x}^{+}(t)+\underline{A}^{-}\underline{x}^{-}(t)\nonumber \\
- &  &+Bu(t) + D^{+}\overline{\omega}(t)-D^{-}\underline{\omega}(t),\nonumber \\
- &  & \underline{x}(t_N)=\overline{x}(t_N)={x}(t_N),\nonumber 
+\dot{\underline{x}}(t) = \underline{A}^{+}\underline{x}^{+}(t)-\overline{A}^{+}\underline{x}^{-}(t)-\underline{A}^{-}\overline{x}^{+}(t) +\overline{A}^{-}\overline{x}^{-}(t) +Bu(t) + D^{+}\underline{\omega}(t)-D^{-}\overline{\omega}(t),\label{eq:predictor-naive}\\
+\dot{\overline{x}}(t) = \overline{A}^{+}\overline{x}^{+}(t)-\underline{A}^{+}\overline{x}^{-}(t)-\overline{A}^{-}\underline{x}^{+}(t)+\underline{A}^{-}\underline{x}^{-}(t)\nonumber+Bu(t) + D^{+}\overline{\omega}(t)-D^{-}\underline{\omega}(t),\nonumber
 \end{eqnarray}
@@
 \label{prop:predictor}
-Assuming that \eqref{eq:polytope} and \autoref{assumpt:metzler} are satisfied for the system \eqref{eq:dynamics}, then the interval predictor:
+Assuming that \eqref{eq:polytope} and \autoref{assumpt:metzler} are satisfied for the system \eqref{eq:dynamics}, then the interval predictor following $ \underline{x}(t_N)=\overline{x}(t_N)={x}(t_N)$ and:
 \begin{eqnarray}
-\dot{\underline{x}}(t) & = & A_{0}\underline{x}(t)-\Delta A_{+}\underline{x}^{-}(t)-\Delta A_{-}\overline{x}^{+}(t)\nonumber \\
- &  & +Bu(t)+D^{+}\underline{\omega}(t)-D^{-}\overline{\omega}(t),\nonumber\\
-\dot{\overline{x}}(t) & = & A_{0}\overline{x}(t)+\Delta A_{+}\overline{x}^{+}(t)+\Delta A_{-}\underline{x}^{-}(t) \label{eq:interval-predictor} \\
- &  & +Bu(t)+D^{+}\overline{\omega}(t)-D^{-}\underline{\omega}(t),\nonumber \\
- &  & \underline{x}(t_N)=\overline{x}(t_N)={x}(t_N)\nonumber 
+\dot{\underline{x}}(t) & = & A_{0}\underline{x}(t)-\Delta A_{+}\underline{x}^{-}(t)-\Delta A_{-}\overline{x}^{+}(t)  +Bu(t)+D^{+}\underline{\omega}(t)-D^{-}\overline{\omega}(t),\label{eq:interval-predictor}\\
+\dot{\overline{x}}(t) & = & A_{0}\overline{x}(t)+\Delta A_{+}\overline{x}^{+}(t)+\Delta A_{-}\underline{x}^{-}(t)  +Bu(t)+D^{+}\overline{\omega}(t)-D^{-}\underline{\omega}(t),\nonumber
 \end{eqnarray}
@@
 	\centering
-	{\includegraphics[trim={0 0.6cm 0 0.4cm}, clip, width=\linewidth]{img/interval-predictor}}
-    \vspace{-0.7cm}
-	\caption{Comparison of \eqref{eq:predictor-naive} and \eqref{eq:interval-predictor} for a simple system \\$\dot{x}(t)=-\theta x(t)+\omega(t)$, with $\theta\in[1, 2]$ and $\omega(t) \in [-0.05, 0.05]$.}
+	{\includegraphics[trim={0 0.6cm 0 0.4cm}, clip, width=0.6\linewidth]{img/interval-predictor}}
+	\caption{Comparison of \eqref{eq:predictor-naive} and \eqref{eq:interval-predictor} for a simple system $\dot{x}(t)=-\theta x(t)+\omega(t)$, with $\theta\in[1, 2]$ and $\omega(t) \in [-0.05, 0.05]$.}
 	\label{fig:predictor_example}
@@
 \begin{definition}[Surrogate objective]
-	Let
+	Let $\underline{x}_n(\bu), \overline{x}_n(\bu)$ following the dynamics defined in \eqref{eq:interval-predictor} and
 \begin{align}
 \label{eq:surrogate_objective} 
-\hat{V}^r(\bu) &\eqdef \sum_{n=N+1}^\infty \gamma^n \underline{R}_n(\bu)\\ 
-\text{where}\quad\underline{R}_n(\bu) &\eqdef \min_{x\in[\underline{x}_n(\bu), \overline{x}_n(\bu)]}  R(x) \label{eq:pessimistic-rewards}
+\hat{V}^r(\bu) \eqdef \sum_{n=N+1}^\infty \gamma^n \underline{R}_n(\bu)\quad\text{where}\quad\underline{R}_n(\bu) \eqdef \min_{x\in[\underline{x}_n(\bu), \overline{x}_n(\bu)]}  R(x).
+%\label{eq:pessimistic-rewards}
 \end{align}
-and $\underline{x}_n(\bu), \overline{x}_n(\bu)$ follow the dynamics defined in \eqref{eq:interval-predictor}.
+
 \end{definition}
@@
 \label{prop:lower-bound}
-The surrogate objective  \eqref{eq:surrogate_objective} is a lower bound of the true objective  \eqref{eq:robust-control-disc}: 
-\begin{equation*}
-\hat{V}^r(\bu) \leq V^r(\bu)
-\end{equation*}
+The surrogate objective  \eqref{eq:surrogate_objective} is a lower bound of the objective  \eqref{eq:robust-control-disc}.
+%\begin{equation*}
+%\hat{V}^r(\bu) \leq V^r(\bu)
+%\end{equation*}
 \end{proposition}
@@
 \centering
-\includegraphics[width=0.45\linewidth]{img/robust-control-tree}
+\includegraphics[width=0.3\linewidth]{img/robust-control-tree}
 \caption{The computation of robust B-values in \eqref{eq:robust-b-values}.
@@
 	\centering
-	\includegraphics[width=0.8\linewidth]{img/regret.pdf}
+	\includegraphics[width=0.5\linewidth]{img/regret.pdf}
 	\caption{The mean regret along with its $95\%$ confidence interval with respect to $N$, for the robust and nominal agents.}
@@
 	\centering
-	\includegraphics[width=0.7\linewidth]{img/highway-small}
+	\includegraphics[width=0.4\linewidth]{img/highway-small}
 	\caption{The intersection crossing task. We show the trajectory intervals corresponding to behavioural uncertainty for each observed vehicle, and the multi-model assumption over the followed route.}

### 2020-05-18 main.tex
Compress NeurIPS version

@@
 \begin{abstract}
-We develop a framework for the adaptive model predictive control of a linear system with unknown parameters and arbitrary bounded costs, in a critical setting where failures are costly and should be prevented at all time.
-Our approach builds on two ideas: first, we incorporate prior knowledge of the dynamics in the form of a known structure that shapes uncertainty, which can be tightened as we collect interaction data by building high-confidence regions through least-square regression.
-Second, in order to handle this uncertainty we formulate a robust control objective.
-Leveraging tools from the interval prediction literature, we convert the confidence regions on parameters into confidence sets on trajectories induced by the controls.
+We develop a framework for the adaptive model predictive control (MPC) of a linear system with unknown parameters, in a critical setting where failures are costly and should be prevented at all time.
+We provide the first regret bound for the minimax problem with arbitrary bounded costs, in contrast to the literature which focuses on quadratic costs only.
+Our approach builds on two ideas: first, the dynamics uncertainty is shaped by the prior knowledge of a structure, and refined by a data-driven regression scheme.
+Second, this uncertainty is used to inform decision-making through a minimax control objective.
+Leveraging tools from the interval prediction literature, we convert the confidence regions on dynamics into confidence sets on trajectories induced by the controls.
 These controls are then optimised resorting to tree-based planning methods.
@@
 The full procedure is designed to produce reasonable and safe behaviours at deployment while recovering an asymptotic optimality.
-We illustrate it on a practical case of autonomous driving at a crossroads intersection among vehicles with uncertain behaviours.\footnote[2]{Source code and videos are available in the Supplementary Material.}
+We illustrate it on a simulated application of autonomous driving at a crossroads intersection among vehicles with uncertain behaviours.\footnote{Source code and videos are available in the Supplementary Material.}
 \end{abstract}
@@
 We turn instead to more general planning algorithms.
-The continuous state space prevents us from using dynamic programming techniques, so we consider tree-based planning instead.
+The continuous state space prevents us from using Dynamic Programming (DP) techniques, so we consider tree-based planning instead.
 Though there exist works addressing continuous actions \citep{Busoniu2018,Weinstein2012}, we resort to a first approximation and discretise the decision space by adopting a hierarchical control architecture.
@@
 
-The dynamics of the real system are described in continuous time.
-However, all the sensing and control performed on-board happen in discrete time, with time-step $\dd t>0$.
-For any variable $z$, we use the subscript notation to refer to these discrete times: $z_n = z(t_n)$ with $t_n = n\dd t$ and $n\in\Natural$.
+The system dynamics are described in continuous time, but sensing and control happen in discrete time with time-step $\dd t>0$.
+For any variable $z$, we use subscript to refer to these discrete times: $z_n = z(t_n)$ with $t_n = n\dd t$ and $n\in\Natural$.
 We use bold symbols to denote temporal sequences $\bz = (z_n)_{n\in\Natural}$.
-We denote $z^+ = \max(z,0)$, $z^- = z^+-z$, $|z| = z^++z^-$ and $[n]=\{1,2,\dots, n\}$.
+We denote $z^+ = \max(z,0)$, $z^- = z^+-z$, $|z| = z^++z^-$ and $[n]=\{1,\dots, n\}$.
 
@@
 Assumptions over the disturbance $\omega$ and noise $\nu$ will be detailed further, and we denote $\eta(t) = C\nu(t) + D\omega(t)$.
-
- Our goal is to design a robust model predictive control for \eqref{eq:dynamics}, and to this end the following steps will be performed and explained later in details.
+ Our goal is to design a robust MPC for \eqref{eq:dynamics}, the steps presented next will be detailed in the sequel.
 
@@
 
-\begin{figure}[t]
+%\begin{figure}[t]
+%	\centering
+%	\includegraphics[trim={0 2cm 0 0}, clip, width=0.3\linewidth]{img/ellipsoid}
+%	\caption{The model estimation procedure, running on the obstacle avoidance problem of \autoref{sec:experiments}. The confidence region $C_{[N],\delta}$ shrinks with the number of samples $N$.}
+%	\label{fig:estimation}
+%\end{figure}
+%
+%\begin{figure}[t]
+%	\centering
+%	\includegraphics[trim={4cm 0 0 0}, clip, width=0.3\linewidth]{img/obstacle_small}
+%	\caption{The state prediction procedure running on the obstacle avoidance problem of \autoref{sec:experiments}.
+At each time step (red to green), we bound the set of reachable states under model uncertainty \eqref{eq:confidence}}
+%	\label{fig:prediction}
+%\end{figure}
+
+%\begin{figure}
+%	\centering
+%	\begin{minipage}{.5\textwidth}
+%		\centering
+%		\includegraphics[trim={0 2cm 0 0}, clip, width=0.3\linewidth]{img/ellipsoid}
+%		\captionof{figure}{The model estimation procedure, running on the obstacle avoidance problem of \autoref{sec:experiments}.
+The confidence region $C_{[N],\delta}$ shrinks with the number of samples $N$.}
+%		\label{fig:estimation}
+%	\end{minipage}%
+%	\begin{minipage}{.5\textwidth}
+%		\centering
+%		\includegraphics[trim={4cm 0 0 0}, clip, width=0.3\linewidth]{img/obstacle_small}
+%		\captionof{figure}{The state prediction procedure running on the obstacle avoidance problem of \autoref{sec:experiments}.
+At each time step (red to green), we bound the set of reachable states under model uncertainty \eqref{eq:confidence}}
+%		\label{fig:prediction}
+%	\end{minipage}
+%\end{figure}
+
+% Side by side figures 
+\begin{figure}
+	\begin{minipage}[b]{0.49\linewidth}
 		\centering
-	\includegraphics[trim={0 2cm 0 0}, clip, width=0.3\linewidth]{img/ellipsoid}
+		\includegraphics[trim={4cm 0 0 0}, clip, width=0.5\linewidth]{img/ellipsoid}
 		\caption{The model estimation procedure, running on the obstacle avoidance problem of \autoref{sec:experiments}. The confidence region $C_{[N],\delta}$ shrinks with the number of samples $N$.}
 		\label{fig:estimation}
-\end{figure}
-
-\begin{figure}[t]
+	\end{minipage}
+	\hfill
+	\begin{minipage}[b]{0.49\linewidth}
 		\centering
-	\includegraphics[trim={4cm 0 0 0}, clip, width=0.3\linewidth]{img/obstacle_small}
+		\includegraphics[trim={4cm 0 0 0}, clip, width=0.8\linewidth]{img/obstacle_small}
 		\caption{The state prediction procedure running on the obstacle avoidance problem of \autoref{sec:experiments}.
@@
 		\label{fig:prediction}
+	\end{minipage}%
 \end{figure}
@@
 With arbitrary functions $R$, we cannot hope to derive a solution in explicit form.
-Our second contribution is to propose to solve \eqref{eq:robust-control} numerically by adopting a \emph{predict-then-optimise} scheme.
-In \autoref{sec:prediction}, we aim to derive a \emph{set predictor} $X(t)$ for the system \eqref{eq:dynamics}, illustrated in \autoref{fig:prediction}.
-This predictor takes the information on the observed current state ${x}_N$, a confidence region $\cC_\delta$ verifying \eqref{eq:confidence}, a planned control sequence $\bu$ and some admissible bounds on the perturbation $[\underline{\omega}(t),\overline{\omega}(t)]$; and outputs a set $X(t)$ that must verify the \emph{inclusion property}:
+Our second contribution is to propose to solve \eqref{eq:robust-control} numerically by adopting an MPC scheme.
+In \autoref{sec:prediction}, we aim to derive an \emph{interval predictor} $[\underline{\omega}(t),\overline{\omega}(t)]$ for the system \eqref{eq:dynamics}, illustrated in \autoref{fig:prediction}.
+This predictor takes the information on the observed current state ${x}_N$, a confidence region $\cC_\delta$ verifying \eqref{eq:confidence}, a planned control sequence $\bu$ and some admissible bounds on the perturbation $[\underline{\omega}(t),\overline{\omega}(t)]$; and must verify the \emph{inclusion property}:
 \begin{equation}
-\label{eq:inclusion-generic}
- x(t)\in X(t),\quad\forall t\geq t_N.
+\label{eq:inclusion-property}
+ \underline{x}(t)\leq x(t)\leq\overline{x}(t), \forall t\geq t_N.
 \end{equation}
@@
 Each action $a\in\cA$ corresponds to the selection of a low-level controller $\pi_a$, that we take affine:
-\[u(t) = \pi_a(x(t)) \eqdef -K_a x(t) + u_a.\]
+$
+u(t) = \pi_a(x(t)) \eqdef -K_a x(t) + u_a.
+$
 For instance, a tracking a subgoal $x_g$ can be achieved with $\pi_g = K(x_g - x)$. The robust objective \eqref{eq:robust-control} becomes 
-\begin{equation}
-\label{eq:robust-control-disc}
-\sup_{\ba\in{\cA}^\Natural} \underbrace{\inf_{\substack{A(\theta) \in \cC_{[N],\delta} \\ \bom\in[\underline{\bom},\overline{\bom}]^\Natural}} \left[\sum_{n=N+1}^\infty \gamma^n R(x_n(\ba,\bom))\right]}_{V^r(\ba)},
-\end{equation}
+$
+%\label{eq:robust-control-disc}
+\sup_{\ba\in{\cA}^\Natural} V^r(\ba)
+%\refstepcounter{equation}\hfill(\theequation)\label{eq:robust-control-disc}
+$
 where $x_n(\ba, \bom)$ stems from \eqref{eq:dynamics} with $u_n = \pi_{a_n}(x_n)$.
@@
 In \autoref{sec:control}, facing a sequential decision problem with continuous states and discrete actions, we turn to the literature of tree-based planning algorithms.
-Our third contribution adapts them to the robust objective \eqref{eq:robust-control-disc} by approximating it with a tractable surrogate $\hat{V}^r$ that exploits the set predictor \eqref{eq:inclusion-generic} to define a pessimistic reward.
+Our third contribution adapts them to the robust objective \eqref{eq:robust-control} by approximating it with a tractable surrogate $\hat{V}^r$ that exploits the interval predictor \eqref{eq:inclusion-property} to define a pessimistic reward.
 In our main result, we show that the best surrogate performance achieved during planning is guaranteed to be attained on the true system, and provide an upper bound for the approximation gap and simple regret of our framework in \autoref{thm:control-error}.
@@
 However, neither optimism and cumulative regret minimisation nor random exploration fit a critical setting, where ensuring safety as a top priority requires instead to consider the pessimistic outcomes.
-The work of \citet{Dean2017} is closest to our setting: after an offline estimation phase, where the controls do not aim at regret minimisation, they estimate a simple regret between a robust controller and the optimal performance.
+The work of \citet{Dean2017} is closest to our setting: after an offline estimation phase, they estimate a simple regret between a robust controller and the optimal performance.
 Our work mainly differs in that it addresses generic costs and forbids random exploration.
@@
 Robust optimisation with generic costs has also been studied in the context of finite Markov Decision Processes with uncertain parameters by \citet{Iyengar2005}, \citet{Nilim2005} and \citet{Wiesemann2013}.
-They showed that the main results of Dynamic Programming can be extended to their robust counterparts only when the dynamics ambiguity set verifies a certain rectangularity property, that amounts to an independence assumption between the uncertainty sets of each transition and is related to time-varying uncertainty.
+They showed that the main results of DP can be extended to their robust counterparts only when the dynamics ambiguity set verifies a certain rectangularity property, that amounts to an independence assumption between the uncertainty sets of each transition and is related to time-varying uncertainty.
 Since our setting requires dealing with continuous states and time-invariant uncertainty, these methods do not apply.
@@
 where $A,\phi_1,\dots,\phi_d\in\Real^{p\times p}$ are known. For all $n$, we denote $\Phi_n = [\phi_1 x_n \dots \phi_d x_n]\in\Real^{p\times d}$.
-
 We also assume to know a bound $S$ such that $\theta\in[-S,S]^d$.
@@
 
-We abuse notations and define a virtual measurement signal, still denoted $y(t)$, that includes additional known terms
-\begin{equation*}
+We abuse notations and define and include additional known terms in the measurement signal
+$
+%\begin{equation*}
 %\label{eq:measurement}
     y(t) = \dot{x}(t) + C\nu(t) - A x(t) - Bu(t),
-\end{equation*}
+%\end{equation*}
+$ 
 to obtain a linear regression system
@@
 
-\paragraph{Regularised least square} To derive an estimate on $\theta$, we consider the weighted $L_2$-regularised regression problem with weights  $\Sigma_p\in\Real^{p\times p}$ and parameter $\lambda\in\Real^+_*$:
-\begin{equation}
-    \label{eq:regression_min}
+\paragraph{Regularised least square} To derive an estimate on $\theta$, we consider the $L_2$-regularised regression problem with weights $\Sigma_p\in\Real^{p\times p}$ and $\lambda\in\Real^+_*$:\hfill
+$
+%    \label{eq:regression_min}
     \min_{\theta\in\Real^d} \sum_{n=1}^N \|y_n -\Phi_n\theta\|_{\Sigma_p^{-1}}^2 + \lambda\|\theta\|_{}^2.
-\end{equation}
-
-The solution can be obtained as:
+    \refstepcounter{equation}~(\theequation)\label{eq:regression_min}
+$
+
+%The solution can be obtained as:
 
@@
 $
-
 To bound this error, we need the noise $\eta_n$ to concentrate.
@@
 At each time $t\geq0$ the noise $\eta(t)$ is an independent sub-Gaussian noise with covariance proxy $\Sigma_p \in \Real^{p\times p}$:
-\begin{equation*}
+$
     \forall u\in\Real^p,\, \expectedvalue \left[ \exp{\left( u^\transp \eta(t)\right)}\right] \leq \exp{\left( \frac{1}{2} u^\transp \Sigma_p u\right)}.
-\end{equation*}
+$
 \end{assumption}
-For instance, it is the case when $\nu$ and $\omega$ are Gaussian noises with covariance matrices $\Sigma_r$ and $\Sigma_s$, with $\Sigma_p \eqdef C\Sigma_r C^\transp + D\Sigma_s D^\transp$. 
+For instance, it is the case when $\nu$ and $\omega$ are bounded or Gaussian noises.
 %Note that \autoref{assumpt:bounded-noise} implies that $\eta$ is sub-Gaussian with covariance proxy $\Sigma_p=\|\eta\|_\infty I_p$.
@@
 We can enclose this confidence ellipsoid $\eqref{eq:confidence-ellipsoid}$ into a polytope $C_{[N],\delta}$.
-For simplicity, we present here a simple but coarse strategy: bound the ellipsoid by its enclosing sphere, and then the sphere by its enclosing hypercube.
+For simplicity, we present here a simple but coarse strategy: bound the ellipsoid by its enclosing axis-aligned hypercube.
 We obtain
@@
     \label{eq:polytope}
-     \cC_{[N],\delta} = \left\{ A + \theta_{N,\lambda}^\transp\phi +\sum_{i=1}^{2^d}\alpha_{i}\Delta A_{i}: \alpha\geq 0,  \sum_{i=1}^{2^d}\alpha_{i}=1\right\} \text{ where }\Delta A_{i} = {h_i} \sqrt{\frac{\beta_N(\delta)}{\lambda_{\max}(G_{N,\lambda})}}, h_i\in\{-1,1\}^d.
+     \cC_{[N],\delta} = \left\{ A + \theta_{N,\lambda}^\transp\phi +\sum_{i=1}^{2^d}\alpha_{i}\Delta A_{i}: \alpha\geq 0,  \sum_{i=1}^{2^d}\alpha_{i}=1\right\} \text{ where } h_i\in\{-1,1\}^d,
 \end{align}
-Another strategy presented in the Supplementary Material produces a much tighter polytope, at the price of an increased computational cost required by the diagonalisation of $G_{N,\lambda}$.
+$\Delta A_{i} = {h_i} \sqrt{\frac{\beta_N(\delta)}{\lambda_{\max}(G_{N,\lambda})}}$.
+A tighter polytope derivation is presented in the Supplementary Material.
+% at the price of an increased computational cost required by the diagonalisation of $G_{N,\lambda}$.
 
@@
 
-To study the inclusion property \eqref{eq:inclusion-generic}, we must start by choosing a set representation $X(t)$.
+%To study the inclusion property \eqref{eq:inclusion-generic}, we must start by choosing a set representation $X(t)$.
 We consider interval prediction, rather than zonotope prediction for instance \citep[e.g.][]{le2012}, for the sake of simplicity of implementation and computational efficiency.
 We represent an interval as $X(t) = [\underline{x}(t), \overline{x}(t)]\in \Real^p\times \Real^p$, and \eqref{eq:inclusion-generic} becomes:
-$
-%\label{eq:inclusion-property}
-\underline{x}(t)\leq x(t)\leq\overline{x}(t), \forall t\geq t_N.
-$
-A simple solution to \eqref{eq:inclusion-generic} is proposed in \citep{Efimov2012}, where, given bounds $\underline{A}\leq A(\theta)\leq\overline{A}$ from $\cC_{[N],\delta}$ they use matrix interval arithmetic to derive the predictor:
+%$
+%%\label{eq:inclusion-property}
+%\underline{x}(t)\leq x(t)\leq\overline{x}(t), \forall t\geq t_N.
+%$
+A simple solution to \eqref{eq:inclusion-property} is proposed in \citep{Efimov2012}, where, given bounds $\underline{A}\leq A(\theta)\leq\overline{A}$ from $\cC_{[N],\delta}$ they use matrix interval arithmetic to derive the predictor:
 \begin{proposition}[Simple predictor of \citealt{Efimov2012}]
@@
 \label{assumpt:metzler}
-There exists an orthogonal matrix $Z\in\Real^{p\times p}$ such that $Z^\transp A_0 Z$ is Metzler\footnote{We say that a matrix is Metlzer when all its non-diagonal coefficients are non-negative.}.
+There exists an orthogonal matrix $Z\in\Real^{p\times p}$ such that $Z^\transp A_0 Z$ is Metzler\footnote{We say that a matrix is Metzler when all its non-diagonal coefficients are non-negative.}.
 \end{assumption}
@@
 \end{align}
-
 \end{definition}
-
-This amounts to changing the reward function, except that the worst case is assessed over the whole past trajectory, which makes this pessimistic reward $\underline{R_n}$ \emph{not markovian}.
+This amounts to changing the reward function, except that the worst case is assessed over the whole past trajectory, which makes this pessimistic reward $\underline{R_n}$ \emph{not Markovian}.
 
@@
 \end{proposition}
-A direct consequence is that since all our approximations are conservative, if we manage to find a control sequence such that no \textit{``bad event''} (e.g.
-a collision) happens according to the surrogate objective $\hat{V}^r$, then we are guaranteed that they will not happen either when the controls are executed on the true system.
-
-\paragraph{Planning}
-To optimise $\hat{V}^r$ \eqref{eq:surrogate_objective}, we cannot use Dynamic Programming algorithms since the state space is continuous and the pessimistic rewards are non-markovian.
+Consequently, since all our approximations are conservative, if we manage to find a control sequence such that no \textit{``bad event''} (e.g.
+a collision) happens according to the surrogate objective $\hat{V}^r$, they are guaranteed not to happen either when the controls are executed on the true system.
+
+To optimise $\hat{V}^r$ in \eqref{eq:surrogate_objective}, we cannot use DP algorithms since the state space is continuous and the pessimistic rewards are non-Markovian.
 Instead, we turn to tree-based planning algorithms, which optimise a sequence of actions based on the corresponding sequence of rewards, without requiring markovity nor state enumeration.
 In particular, we consider the \emph{Optimistic Planning of Deterministic Systems} (\texttt{OPD}) algorithm \citep{Hren2008} tailored for the case when the relationship between actions and rewards is deterministic.
-Indeed, the stochasticity of the perturbations and measurements is encased in $\hat{V}^r$: given the observations up to time $N$ both the predictor dynamics \eqref{eq:interval-predictor} and the pessimistic rewards \eqref{eq:pessimistic-rewards} are deterministic.
-
+Indeed, the stochasticity of the perturbations and measurements is encased in $\hat{V}^r$: given the observations up to time $N$ both the predictor dynamics \eqref{eq:interval-predictor} and the pessimistic rewards in \eqref{eq:surrogate_objective} are deterministic.
 At each planning iteration $k\in[K]$, \texttt{OPD} progressively builds a tree $\cT_{k+1}$ by forming upper-bounds $B_a(k)$ over the value of sequences of actions $a$, and expanding\footnote{The expansion of a leaf node $a$ refers to the simulation of its children transitions $aA = \{ab, b\in A\}$} the leaf $a_k$ with highest upper-bound:
@@
 The simple regret of the \texttt{OPD} algorithm \eqref{eq:opd} applied to the surrogate objective \eqref{eq:surrogate_objective} after $K$ planning iterations is:
-\begin{align*}
-\text{if } \kappa>1,\quad& 
-\hat{V}^r(a^{\star}) - \hat{V}^r({a_K}) = \cO\left(K^{-\frac{\log 1/\gamma}{\log \kappa}}\right);\\
-\text{if }\kappa=1,\quad&
-\hat{V}^r(a^{\star}) - \hat{V}^r({a_K}) = \cO\left(\gamma^{{(1-\gamma)^{\log_\gamma (\kappa/|\cA|)}}K/{c}}\right)
-\end{align*}
-where $\kappa$ is a problem-dependent measure of the proportion of near-optimal paths:
-\[
-\kappa = \limsup_{h\rightarrow\infty} \left|\left\{a\in A^h: \hat{V}^r(a)\geq \hat{V}^r(a^{\star}) - \frac{\gamma^{h+1}}{1-\gamma}\right\}\right|^{1/h}.
-\]
+$
+\hat{V}^r(a^{\star}) - \hat{V}^r({a_K}) = \cO\left(K^{-\frac{\log 1/\gamma}{\log \kappa}}\right);
+$
+where $\kappa \eqdef \limsup_{h\rightarrow\infty} \left|\left\{a\in A^h: \hat{V}^r(a)\geq \hat{V}^r(a^{\star}) - \frac{\gamma^{h+1}}{1-\gamma}\right\}\right|^{1/h}$ is a problem-dependent measure of the proportion of near-optimal paths.
 \end{theorem}
@@
 One of the major benefits of using the family of linear models, compared to richer model classes, is that they provide strict conditions allowing to quantify the adequacy of the modelling assumptions to the observations.
-
 Given $N-1$ observations, \autoref{sec:estimation} provides a polytopic confidence region \eqref{eq:polytope} that contains $A(\theta)$ with probability at least $1-\delta$.
@@
 \label{assumpt:multi-model-ambiguity}
-The true dynamics $f$ lies within a finite set of candidate models $f^1, \dots, f^M$.
-\begin{equation*}
+The true dynamics $f$ lies within a finite set of candidate models $f^1, \dots, f^M$:
+$
 \exists m\in[M]: \dot{x}(t) = f^m(x(t), u(t)), \forall t\geq 0
-\end{equation*}
+$
 \end{assumption}
-We want to adapt our planning algorithm in order to balance these concurrent hypotheses in a robust fashion, i.e. maximise a robust objective with discrete ambiguity:
-\begin{equation}
-\label{eq:robust-objective-discrete}
-V^r = \sup_{a\in\cA^\Natural}\min_{m\in[M]} \sum_{n=N+1}^\infty \gamma^n R_n^m
-\end{equation}
+We adapt our planning algorithm to balance these concurrent hypotheses in a robust fashion, i.e. maximise a robust objective with discrete ambiguity:
+$
+%\label{eq:robust-objective-discrete}
+V^r = \sup_{a\in\cA^\Natural}\min_{m\in[M]} \sum_{n=N+1}^\infty \gamma^n R_n^m, \refstepcounter{equation}\hfill(\theequation)\label{eq:robust-objective-discrete}
+$
 where $R_n^m$ is the reward obtain by following the action sequence $a$ up to step $n$ under the dynamics $f^m$.
@@
 \begin{definition}[Robust sequence upper bounds] We replace the upper-bound \eqref{eq:opd} on sequence values in \texttt{OPD} by: 
-\begin{equation}
-\label{eq:robust-b-values}
-B_a^r(k)  \eqdef \min_{m\in[M]} \sum_{n=0}^{h-1} \gamma^n R_n^m  + \frac{\gamma^h}{1-\gamma}
-\end{equation}
+$
+%\label{eq:robust-b-values}
+B_a^r(k)  \eqdef \min_{m\in[M]} \sum_{n=0}^{h-1} \gamma^n R_n^m  + \frac{\gamma^h}{1-\gamma}. \refstepcounter{equation}\hfill(\theequation)\label{eq:robust-b-values}
+$
 \end{definition}
-An illustration of the computation of the robust upper-bounds is presented in Figure \ref{fig:drop}.
 Note that it is not equivalent to solving each control problem independently and following the action with highest worst-case value, as we show in the Supplementary Material.
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=0.3\linewidth]{img/robust-control-tree}
-\caption{The computation of robust B-values in \eqref{eq:robust-b-values}.
+%\begin{figure}
+%\centering
+%\includegraphics[width=0.3\linewidth]{img/robust-control-tree}
+%\caption{The computation of robust B-values in \eqref{eq:robust-b-values}.
 The simulation of trajectories for every dynamics model $f^m$ is represented as stacked versions of the expanded tree $\mathcal{T}_k$.}
-\label{fig:drop}
-\end{figure}
+%\label{fig:drop}
+%\end{figure}
 
@@
 
+This result is of independent interest for robust planning with discrete ambiguity: the exact solution is recovered asymptotically, which Robust DP algorithms do not allow.
 The regret depends on the number $K$ of node expansions, but each expansion now requires $M$ times more simulations than in the single-model setting.
@@
 \paragraph{Obstacle avoidance with unknown friction}
-We first consider a simple illustrative example, shown in \autoref{fig:prediction}: the control of a 2D system with position $(p_x,p_y)$ and velocity $(v_x, v_y)$ moving by means of a force $(u_x, u_y)$ in an environment with unknown anisotropic friction.
-
-\begin{equation*}
-\begin{bmatrix}
-\dot{p_x}\\
-\dot{p_y}\\
-\dot{v_x}\\
-\dot{v_y}\\
-\end{bmatrix} = 
-\begin{bmatrix}
-0 & 0 & 1 & 0 \\
-0 & 0 & 0 & 1 \\
-0 & 0 & -\theta_x & 0 \\
-0 & 0 & 0 & -\theta_y
-\end{bmatrix}
-\begin{bmatrix}
-{p_x}\\
-{p_y}\\
-{v_x}\\
-{v_y}\\
-\end{bmatrix}
-+
-\begin{bmatrix}
-0\\
-0\\
-{u_x}\\
-{u_y}\\
-\end{bmatrix}
-\end{equation*}
-
+We first consider a simple illustrative example, shown in \autoref{fig:prediction}: the control of a 2D system with position $(p_x,p_y)$ and velocity $(v_x, v_y)$ moving by means of a force $(u_x, u_y)$ in an environment with unknown anisotropic linear friction with coefficients $(\theta_x, \theta_y)$.
+%$
+%\begin{bmatrix}
+%\dot{p_x}\\
+%\dot{p_y}\\
+%\dot{v_x}\\
+%\dot{v_y}\\
+%\end{bmatrix} = 
+%\begin{bmatrix}
+%0 & 0 & 1 & 0 \\
+%0 & 0 & 0 & 1 \\
+%0 & 0 & -\theta_x & 0 \\
+%0 & 0 & 0 & -\theta_y
+%\end{bmatrix}
+%\begin{bmatrix}
+%{p_x}\\
+%{p_y}\\
+%{v_x}\\
+%{v_y}\\
+%\end{bmatrix}
+%+
+%\begin{bmatrix}
+%0\\
+%0\\
+%{u_x}\\
+%{u_y}\\
+%\end{bmatrix}.
+%$
 Note that \autoref{assumpt:metzler} is always verified.
@@
 The actions $\cA$ are constant controls in the up, down, left and right directions.
-
 We run \autoref{alg:full} for 100 simulations, and compare in \autoref{tab:obstacle} its performances to that of the nominal agent, i.e.
@@
 
-\begin{figure}[tp]
+%\begin{figure}[tp]
+%	\centering
+%	\includegraphics[width=0.3\linewidth]{img/regret.pdf}
+%	\caption{The mean regret along with its $95\%$ confidence interval with respect to $N$, for the robust and nominal agents.}
+%	\label{fig:regret}
+%\end{figure}
+%\begin{figure}[t]
+%	\centering
+%	\includegraphics[width=0.4\linewidth]{img/highway-small}
+%	\caption{The intersection crossing task. We show the trajectory intervals corresponding to behavioural uncertainty for each observed vehicle, and the multi-model assumption over the followed route.}
+%\end{figure}
+\begin{figure}[!tbp]
 	\centering
-	\includegraphics[width=0.5\linewidth]{img/regret.pdf}
+	\begin{minipage}[t]{0.43\textwidth}
+		\centering
+		\includegraphics[trim={0 0.2cm 0 0.2cm}, clip, width=0.9\linewidth]{img/regret.pdf}
 		\caption{The mean regret along with its $95\%$ confidence interval with respect to $N$, for the robust and nominal agents.}
 		\label{fig:regret}
+	\end{minipage}
+	\hfill
+	\begin{minipage}[t]{0.55\textwidth}
+		\centering
+		\includegraphics[width=0.65\linewidth]{img/highway-small}
+		\caption{The intersection crossing task. Trajectory intervals show behavioural uncertainty for each vehicle, with a multi-model assumption over their route.}
+	\end{minipage}
 \end{figure}
@@
 \begin{table}[tbp]
-	\caption{Performances on the obstacle avoidance task}
+%	\caption{Performances on the obstacle avoidance task}
+%	\label{tab:obstacle}
+%	\centering
+%	\begin{tabular}{lccc}
+%		\toprule
+%		Agent &
+%		failures &
+%		min return &
+%		mean return $\pm$ std  \\
+%		\midrule
+%		Oracle & 0\% & {11.6} & {$14.2 \pm 1.3$} \\
+%		\midrule
+%		{Nominal} & {4\%} & {2.8} & \textbf{$\mathbf{13.8} \pm 2.0$} \\
+%		\autoref{alg:full} & \textbf{0\%} & \textbf{10.4} & {$13.0 \pm 1.5$} \\
+%		\bottomrule
+%	\end{tabular}
+
+\parbox{.49\linewidth}{
+	\centering
+	\caption{Performances on the obstacle task}
 	\label{tab:obstacle}
-	\centering
+	\small
 	\begin{tabular}{lccc}
@@
 		failures &
-		min return &
-		mean return $\pm$ std  \\
+		min $J$ &
+		mean $J$ $\pm$ std  \\
 		\midrule
@@
 	\end{tabular}
+}
+\hfill
+\parbox{.49\linewidth}{
+	\small
+	\caption{Performances on the driving task}
+	\label{tab:driving}
+	\centering
+	\begin{tabular}{lccc}
+		\toprule
+		Agent &
+		failures &
+		min $J$ &
+		mean $J$ $\pm$ std  \\
+		\midrule
+		Oracle & 0\% & {6.9} & $7.4 \pm 0.5$ \\
+		\midrule
+		{Nominal 1} & 4\% & {5.2} & $\mathbf{7.3} \pm 1.5$ \\
+		{Nominal 2} & 33\% & {3.5} & $6.4 \pm 0.26$ \\
+		\autoref{alg:full} & \textbf{0\%} & \textbf{6.8} & $7.1 \pm 0.29$ \\
+		\bottomrule
+	\end{tabular}
+}
 \end{table}
@@
 
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=0.4\linewidth]{img/highway-small}
-	\caption{The intersection crossing task. We show the trajectory intervals corresponding to behavioural uncertainty for each observed vehicle, and the multi-model assumption over the followed route.}
-\end{figure}
-
-\begin{table}[t]
-	\caption{Performances on the driving task}
-	\label{tab:driving}
-	\centering
-	\begin{tabular}{lccc}
-		\toprule
-		Agent &
-		failures &
-        min return &
-		mean return $\pm$ std  \\
-		\midrule
-		Oracle & 0\% & {6.9} & $7.4 \pm 0.5$ \\
-		\midrule
-		{Nominal 1} & 4\% & {5.2} & $\mathbf{7.3} \pm 1.5$ \\
-		{Nominal 2} & 33\% & {3.5} & $6.4 \pm 0.26$ \\
-		\autoref{alg:full} & \textbf{0\%} & \textbf{6.8} & $7.1 \pm 0.29$ \\
-		\bottomrule
-	\end{tabular}
-\end{table}
+%
+%\begin{table}[t]
+%	\caption{Performances on the driving task}
+%	\label{tab:driving}
+%	\centering
+%	\begin{tabular}{lccc}
+%		\toprule
+%		Agent &
+%		failures &
+%        min return &
+%		mean return $\pm$ std  \\
+%		\midrule
+%		Oracle & 0\% & {6.9} & $7.4 \pm 0.5$ \\
+%		\midrule
+%		{Nominal 1} & 4\% & {5.2} & $\mathbf{7.3} \pm 1.5$ \\
+%		{Nominal 2} & 33\% & {3.5} & $6.4 \pm 0.26$ \\
+%		\autoref{alg:full} & \textbf{0\%} & \textbf{6.8} & $7.1 \pm 0.29$ \\
+%		\bottomrule
+%	\end{tabular}
+%\end{table}
 
@@
 Leveraging tools from linear regression, interval prediction, and tree-based planning, we guarantee the predicted performance and provide a regret bound.
-The applicability of the method is further improved by a multi-model extension and demonstrated on two simulated applications.
+The method applicability is further improved by a multi-model extension and demonstrated on two simulations.
 

### 2020-05-18 main.tex
Merge Introduction with Problem statement -> 8 pages

@@
 \usepackage{algorithmic}
-
-\def\sectionautorefname{Section}
+\usepackage{cleveref}
+
+\def\sectionCrefname{Section}
 \input{mathdef.tex}
@@
 In this work, we assume that the system dynamics are partially known, in the form of a parametrized dynamical system with unknown parameters.
-We argue that this assumption is realistic given that most industrial applications to date have been relying on physical models to describe their processes and well-engineered controllers to operate them, rather than machine learning.
-Our framework relaxes this modelling effort by allowing some \emph{structured uncertainty} around the nominal model.
-We adopt a data-driven scheme where we wish to estimate the parameters more accurately as we interact with the true system.
-Most model-based reinforcement learning algorithms rely on the estimated dynamics to derive the corresponding optimal controls \citep[e.g.][]{Lenz2015,Levine2015}, but suffer from \emph{model bias}: they ignore the error that exists between the learned and true dynamics, which can dramatically degrade the control performances \citep{Schneider1997}.
-It is particularly likely when maximising an objective under constraints, which naturally pushes the systems to operate in the vicinity of constraint saturation and makes it prone to failure.
-
-To address this issue, we turn to the framework of \emph{robust} decision-making \citep{Bental2009,Bertsimas2011,Gorissen2015}: instead of merely considering a point estimate of the dynamics, we build an entire \emph{confidence region} that contains the true dynamics with high probability, and optimise the decisions so as to maximise the worst-case outcome with respect to this uncertainty.
-Maximin problems are notoriously hard to solve, and all the more in our setting where the reward function $R$ is generic.
-In particular, this excludes a number of tools from the robust synthesis literature, such as $\cH_\infty$ control \citep[see, e.g.][]{Basar1996} or system-level synthesis \citep{Dean2017,Dean2018}.
-We turn instead to more general planning algorithms.
-The continuous state space prevents us from using Dynamic Programming (DP) techniques, so we consider tree-based planning instead.
-Though there exist works addressing continuous actions \citep{Busoniu2018,Weinstein2012}, we resort to a first approximation and discretise the decision space by adopting a hierarchical control architecture.
-At each time, the agent can select low-level controller to execute among a finite basis, e.g.
-choose a short-term goal to reach or a skill to execute such as a driving maneuver.
-The discretisation induces a suboptimality, but it can be mitigated by diversifying the controller basis.
-Tree-based planning algorithms are relevant in this context of discrete actions, but are only designed for a single known generative model instead of an entire confidence region for the system dynamics.
-We adapt them to the robust framework by following a two-steps procedure: we first predict a set of states that can be reached under a planned control sequence with respect to all possible dynamics.
-This reachability set is used to provide a conservative pessimistic reward to the planning algorithm.
-The next section aims to clarify and formalise these ideas, and state our contributions.
-
-\subsection{Problem Statement and Our Contributions}
-
-\paragraph{Notation}
-
-The system dynamics are described in continuous time, but sensing and control happen in discrete time with time-step $\dd t>0$.
-For any variable $z$, we use subscript to refer to these discrete times: $z_n = z(t_n)$ with $t_n = n\dd t$ and $n\in\Natural$.
-We use bold symbols to denote temporal sequences $\bz = (z_n)_{n\in\Natural}$.
-We denote $z^+ = \max(z,0)$, $z^- = z^+-z$, $|z| = z^++z^-$ and $[n]=\{1,\dots, n\}$.
-
-\paragraph{Structured dynamics}
-We consider a linear system with state $x\in\Real^p$, acted on by controls $u\in\Real^q$ and perturbations $\omega\in\Real^r$, and following dynamics in the form:
+More precisely, we consider a linear system with state $x\in\Real^p$, acted on by controls $u\in\Real^q$ and perturbations $\omega\in\Real^r$, and following dynamics in the form:
 \begin{equation}
@@
 Assumptions over the disturbance $\omega$ and noise $\nu$ will be detailed further, and we denote $\eta(t) = C\nu(t) + D\omega(t)$.
- Our goal is to design a robust MPC for \eqref{eq:dynamics}, the steps presented next will be detailed in the sequel.
-
-\paragraph{Model estimation}
-
-%\begin{figure}[t]
-%	\centering
-%	\includegraphics[trim={0 2cm 0 0}, clip, width=0.3\linewidth]{img/ellipsoid}
-%	\caption{The model estimation procedure, running on the obstacle avoidance problem of \autoref{sec:experiments}. The confidence region $C_{[N],\delta}$ shrinks with the number of samples $N$.}
-%	\label{fig:estimation}
-%\end{figure}
-%
-%\begin{figure}[t]
-%	\centering
-%	\includegraphics[trim={4cm 0 0 0}, clip, width=0.3\linewidth]{img/obstacle_small}
-%	\caption{The state prediction procedure running on the obstacle avoidance problem of \autoref{sec:experiments}.
-At each time step (red to green), we bound the set of reachable states under model uncertainty \eqref{eq:confidence}}
-%	\label{fig:prediction}
-%\end{figure}
-
-%\begin{figure}
-%	\centering
-%	\begin{minipage}{.5\textwidth}
-%		\centering
-%		\includegraphics[trim={0 2cm 0 0}, clip, width=0.3\linewidth]{img/ellipsoid}
-%		\captionof{figure}{The model estimation procedure, running on the obstacle avoidance problem of \autoref{sec:experiments}.
-The confidence region $C_{[N],\delta}$ shrinks with the number of samples $N$.}
-%		\label{fig:estimation}
-%	\end{minipage}%
-%	\begin{minipage}{.5\textwidth}
-%		\centering
-%		\includegraphics[trim={4cm 0 0 0}, clip, width=0.3\linewidth]{img/obstacle_small}
-%		\captionof{figure}{The state prediction procedure running on the obstacle avoidance problem of \autoref{sec:experiments}.
-At each time step (red to green), we bound the set of reachable states under model uncertainty \eqref{eq:confidence}}
-%		\label{fig:prediction}
-%	\end{minipage}
-%\end{figure}
-
-% Side by side figures 
+We argue that this assumption is realistic given that most industrial applications to date have been relying on physical models to describe their processes and well-engineered controllers to operate them, rather than machine learning.
+Our framework relaxes this modelling effort by allowing some \emph{structured uncertainty} around the nominal model.
+We adopt a data-driven scheme to estimate the parameters more accurately as we interact with the true system.
+Most model-based reinforcement learning algorithms rely on the estimated dynamics to derive the corresponding optimal controls \citep[e.g.][]{Lenz2015,Levine2015}, but suffer from \emph{model bias}: they ignore the error between the learned and true dynamics, which can dramatically degrade control performances \citep{Schneider1997}.
+%It is particularly likely when maximising an objective under constraints, which naturally pushes the systems to operate in the vicinity of constraint saturation and makes it prone to failure.
+
+To address this issue, we turn to the framework of \emph{robust} decision-making: instead of merely considering a point estimate of the dynamics, we build an entire \emph{confidence region} $\cC_{[N],\delta} \subset \Theta$, illustrated in \Cref{fig:estimation}, that contains the true dynamics with high probability:
+\begin{align}
+\probability{A(\theta)\in \cC_{[N],\delta}} \geq 1-\delta,
+\label{eq:confidence}
+\end{align}
+where $\delta\in(0,1)$.
+In \Cref{sec:estimation}, having observed a history $\cD_{[N]} = \{(x_n, y_n,u_n)\}_{n\in[N]}$ of transitions, our first contribution extends the work of \citet{Abbasi2011} who provide a confidence ellipsoid for the least-square estimator to our setting of feature matrices, rather than feature vectors.
+
+This confidence region $\cC_{[N],\delta}$ allows to formulate the \emph{robust control objective} $V^r$ \citep{Bental2009,Bertsimas2011,Gorissen2015} which maximises the worst-case outcome with respect to this uncertainty:
+\begin{equation}
+\label{eq:robust-control}
+\sup_{\bu\in{(\Real^q)}^\Natural} \underbrace{\inf_{\substack{A(\theta) \in \cC_{[N],\delta} \\ \bom\in[\underline{\bom},\overline{\bom}]^\Natural}} \left[\sum_{n=N+1}^\infty \gamma^n R(x_n(\bu,\bom))\right]}_{V^r(\bu)}
+\end{equation}
+where $\gamma\in(0,1)$ is a discount factor.
+Maximin problems such as $\eqref{eq:robust-control}$ even in cases such where the reward $R$ has a simple form.
+With arbitrary functions $R$, we cannot hope to derive a solution in explicit form.
+In particular, this excludes a number of tools from the robust synthesis literature which is focused on stabilization problems, such as $\cH_\infty$ control \citep[see, e.g.][]{Basar1996}, sliding-mode control, tube-MPC or system-level synthesis \citep{Dean2017,Dean2018}.
+In our second contribution, we propose a robust MPC algorithm for solving \eqref{eq:robust-control} numerically.
+In \Cref{sec:prediction}, we leverage recent results from the uncertain system simulation literature to derive an \emph{interval predictor} $[\underline{x}(t),\overline{x}(t)]$ for the system \eqref{eq:dynamics}, illustrated in \Cref{fig:prediction}.
+This predictor takes the information on the observed current state ${x}_N$, the confidence region $\cC_\delta$, planned control sequence $\bu$ and some admissible bounds on the perturbation $[\underline{\omega}(t),\overline{\omega}(t)]$; and must verify the \emph{inclusion property}:
+\begin{equation}
+\label{eq:inclusion-property}
+\underline{x}(t)\leq x(t)\leq\overline{x}(t), \forall t\geq t_N.
+\end{equation}
+
+Since $R$ is generic, potentially non-smooth and non-convex, solving the optimal -- not to mention the robust -- control objective is intractable.
+In \Cref{sec:control}, facing a sequential decision problem with continuous states, we turn to the literature of tree-based planning algorithms.
+Though there exist works addressing continuous actions \citep{Busoniu2018,Weinstein2012}, we resort to a first approximation and discretise the continuous decision $(\Real^q)^\Natural$ space by adopting a hierarchical control architecture: at each time, the agent can select a high-level \emph{action} $a$ from a finite action space $\cA$.
+Each action $a\in\cA$ corresponds to the selection of a low-level controller $\pi_a$, that we take affine: $u(t) = \pi_a(x(t)) \eqdef -K_a x(t) + u_a.$ For instance, a tracking a subgoal $x_g$ can be achieved with $\pi_g = K(x_g - x)$.
+The discretisation induces a suboptimality, but it can be mitigated by diversifying the controller basis.
+The robust objective \eqref{eq:robust-control} becomes $\sup_{\ba\in{\cA}^\Natural} V^r(\ba)$, where $x_n(\ba, \bom)$ stems from \eqref{eq:dynamics} with $u_n = \pi_{a_n}(x_n)$.
+However, tree-based planning algorithms are designed for a single known generative model rather than a confidence region for the system dynamics.
+Our third contribution adapts them to the robust objective \eqref{eq:robust-control} by approximating it with a tractable surrogate $\hat{V}^r$ that exploits the interval predictor \eqref{eq:inclusion-property} to define a pessimistic reward.
+In our main result, we show that the best surrogate performance achieved during planning is guaranteed to be attained on the true system, and provide an upper bound for the approximation gap and simple regret of our framework in \Cref{thm:control-error}.
+This is the first result of this kind for maximin control with generic costs to the best of our knowledge.
+\Cref{alg:full} shows the full integration of the three procedures of estimation, prediction and control.
+
+In \Cref{sec:multi-model}, our forth contribution extends the proposed framework to consider multiple modelling assumptions, while narrowing uncertainty through data-driven model rejection, and still ensuring safety via robust model-selection during planning.
+
+Finally, in \Cref{sec:experiments} we demonstrate the applicability of our proposed \Cref{alg:full} in two numerical experiments.
+First, a simple illustrative example and then, a more challenging simulation for safe autonomous driving.
+
+\paragraph{Notation}
+
+The system dynamics are described in continuous time, but sensing and control happen in discrete time with time-step $\dd t>0$.
+For any variable $z$, we use subscript to refer to these discrete times: $z_n = z(t_n)$ with $t_n = n\dd t$ and $n\in\Natural$.
+We use bold symbols to denote temporal sequences $\bz = (z_n)_{n\in\Natural}$.
+We denote $z^+ = \max(z,0)$, $z^- = z^+-z$, $|z| = z^++z^-$ and $[n]=\{1,\dots, n\}$.
+
 \begin{figure}
@@
 		\includegraphics[trim={4cm 0 0 0}, clip, width=0.5\linewidth]{img/ellipsoid}
-		\caption{The model estimation procedure, running on the obstacle avoidance problem of \autoref{sec:experiments}. The confidence region $C_{[N],\delta}$ shrinks with the number of samples $N$.}
+		\caption{The model estimation procedure, running on the obstacle avoidance problem of \Cref{sec:experiments}. The confidence region $C_{[N],\delta}$ shrinks with the number of samples $N$.}
 		\label{fig:estimation}
@@
 		\includegraphics[trim={4cm 0 0 0}, clip, width=0.8\linewidth]{img/obstacle_small}
-		\caption{The state prediction procedure running on the obstacle avoidance problem of \autoref{sec:experiments}.
+		\caption{The state prediction procedure running on the obstacle avoidance problem of \Cref{sec:experiments}.
 At each time step (red to green), we bound the set of reachable states under model uncertainty \eqref{eq:confidence}}
@@
 \end{figure}
-
-In \autoref{sec:estimation}, having observed history of transitions $\cD_{[N]} = \{(x_n, y_n,u_n)\}_{n\in[N]}$, and given a confidence level $\delta\in(0, 1)$, we wish to find a confidence region $\cC_{[N],\delta} \subset \Theta$ as tight as possible and such that it holds:
-\begin{align}
-\probability{A(\theta)\in \cC_{[N],\delta}} \geq 1-\delta
-\label{eq:confidence}
-\end{align}
-Such regions are illustrated in \autoref{fig:estimation}.
-Our first contribution extends the work of \citet{Abbasi2011} who provide a confidence ellipsoid for the regularised least-square estimator to our setting of feature matrices, rather than feature vectors.
-
-\paragraph{Robust objective}
-
-At the time step $n=N$, considering the confidence region $\cC_{[N],\delta}$ obtained in the model estimation phase, we formulate our robust control objective:
-\begin{equation}
-\label{eq:robust-control}
-\sup_{\bu\in{(\Real^q)}^\Natural} \underbrace{\inf_{\substack{A(\theta) \in \cC_{[N],\delta} \\ \bom\in[\underline{\bom},\overline{\bom}]^\Natural}} \left[\sum_{n=N+1}^\infty \gamma^n R(x_n(\bu,\bom))\right]}_{V^r(\bu)}
-\end{equation}
-where $\gamma\in(0,1)$ is a discount factor. The rest of the paper tackles the optimisation of \eqref{eq:robust-control}.
-
-\paragraph{State prediction}
-
-Maximin problems such as \eqref{eq:robust-control} are notoriously difficult to solve even in cases such where the reward $R$ has a simple form.
-With arbitrary functions $R$, we cannot hope to derive a solution in explicit form.
-Our second contribution is to propose to solve \eqref{eq:robust-control} numerically by adopting an MPC scheme.
-In \autoref{sec:prediction}, we aim to derive an \emph{interval predictor} $[\underline{\omega}(t),\overline{\omega}(t)]$ for the system \eqref{eq:dynamics}, illustrated in \autoref{fig:prediction}.
-This predictor takes the information on the observed current state ${x}_N$, a confidence region $\cC_\delta$ verifying \eqref{eq:confidence}, a planned control sequence $\bu$ and some admissible bounds on the perturbation $[\underline{\omega}(t),\overline{\omega}(t)]$; and must verify the \emph{inclusion property}:
-\begin{equation}
-\label{eq:inclusion-property}
- \underline{x}(t)\leq x(t)\leq\overline{x}(t), \forall t\geq t_N.
-\end{equation}
-We leverage recent results from the uncertain system simulation literature to efficiently compute such a predictor.
-
-\paragraph{Robust planning}
-
-Since $R$ is generic, potentially non-smooth and non-convex, solving the optimal -- not to mention the robust -- control objective in the original continuous control space $(\Real^q)^\Natural$ is intractable.
-In this work, we choose to approximate the solution of \eqref{eq:robust-control} by optimising over a finite set of \emph{actions} $\cA$.
-Each action $a\in\cA$ corresponds to the selection of a low-level controller $\pi_a$, that we take affine:
-$
-u(t) = \pi_a(x(t)) \eqdef -K_a x(t) + u_a.
-$
-For instance, a tracking a subgoal $x_g$ can be achieved with $\pi_g = K(x_g - x)$. The robust objective \eqref{eq:robust-control} becomes 
-$
-%\label{eq:robust-control-disc}
-\sup_{\ba\in{\cA}^\Natural} V^r(\ba)
-%\refstepcounter{equation}\hfill(\theequation)\label{eq:robust-control-disc}
-$
-where $x_n(\ba, \bom)$ stems from \eqref{eq:dynamics} with $u_n = \pi_{a_n}(x_n)$.
-
-In \autoref{sec:control}, facing a sequential decision problem with continuous states and discrete actions, we turn to the literature of tree-based planning algorithms.
-Our third contribution adapts them to the robust objective \eqref{eq:robust-control} by approximating it with a tractable surrogate $\hat{V}^r$ that exploits the interval predictor \eqref{eq:inclusion-property} to define a pessimistic reward.
-In our main result, we show that the best surrogate performance achieved during planning is guaranteed to be attained on the true system, and provide an upper bound for the approximation gap and simple regret of our framework in \autoref{thm:control-error}.
-
-The \autoref{alg:full} shows the full integration of the three procedures of estimation, prediction and control.
-
-\paragraph{Model selection} In \autoref{sec:multi-model}, our forth contribution extends the proposed framework to consider multiple modelling assumptions, while narrowing uncertainty through data-driven model rejection, and still ensuring safety via robust model-selection during planning.
-
-\paragraph{Experiments} Finally, in \autoref{sec:experiments} we demonstrate the applicability of our proposed \autoref{alg:full} in two numerical experiments.
-First, a simple illustrative example and then, a more challenging simulation for safe autonomous driving.
 
@@
 
-\paragraph{Linear-quadratic problems} There is a rich body of literature dedicated to the study of linear systems with quadratic costs, and we focus on those providing non-asymptotic results when the system parameters $A, B$ are unknown.
+\paragraph{Linear dynamics} There is a rich body of literature dedicated to the study of linear systems with quadratic costs, and we focus on those providing non-asymptotic results when the system parameters $A, B$ are unknown.
 In their seminal work \citet{abbasi-yadkori11a}, consider the problem of cumulative regret minimisation.
@@
 
-\paragraph{Robust planning}
+\paragraph{Generic costs}
 Robust optimisation with generic costs has also been studied in the context of finite Markov Decision Processes with uncertain parameters by \citet{Iyengar2005}, \citet{Nilim2005} and \citet{Wiesemann2013}.
@@
 %
-%There may be cases where \autoref{assumpt:bounded-noise} does not hold.
+%There may be cases where \Cref{assumpt:bounded-noise} does not hold.
 For instance, when the noise $\eta$ is Gaussian, then $\|\eta\|_\infty=+\infty$ which makes \eqref{eq:bounded-noise-polytope} uninformative.
@@
 For instance, it is the case when $\nu$ and $\omega$ are bounded or Gaussian noises.
-%Note that \autoref{assumpt:bounded-noise} implies that $\eta$ is sub-Gaussian with covariance proxy $\Sigma_p=\|\eta\|_\infty I_p$.
+%Note that \Cref{assumpt:bounded-noise} implies that $\eta$ is sub-Gaussian with covariance proxy $\Sigma_p=\|\eta\|_\infty I_p$.
 
@@
 \label{thm:confidence_ellipsoid}
-Under \autoref{assumpt:gaussian-noise}, it holds with probability at least $1-\delta$ that
+Under \Cref{assumpt:gaussian-noise}, it holds with probability at least $1-\delta$ that
 \begin{align}
@@
 \label{prop:predictor}
-Assuming that \eqref{eq:polytope} and \autoref{assumpt:metzler} are satisfied for the system \eqref{eq:dynamics}, then the interval predictor following $ \underline{x}(t_N)=\overline{x}(t_N)={x}(t_N)$ and:
+Assuming that \eqref{eq:polytope} and \Cref{assumpt:metzler} are satisfied for the system \eqref{eq:dynamics}, then the interval predictor following $ \underline{x}(t_N)=\overline{x}(t_N)={x}(t_N)$ and:
 \begin{eqnarray}
@@
 
-\autoref{fig:predictor_example} illustrates the difference of stability of the two predictors \eqref{eq:predictor-naive} and \eqref{eq:interval-predictor} with a simple example.
-It suggests to always prefer \eqref{eq:interval-predictor} whenever \autoref{assumpt:metzler} is verified, and only fallback to \eqref{eq:predictor-naive} as a last resort.
+\Cref{fig:predictor_example} illustrates the difference of stability of the two predictors \eqref{eq:predictor-naive} and \eqref{eq:interval-predictor} with a simple example.
+It suggests to always prefer \eqref{eq:interval-predictor} whenever \Cref{assumpt:metzler} is verified, and only fallback to \eqref{eq:predictor-naive} as a last resort.
 
@@
 \label{sec:control}
-In order to evaluate the robust objective $V^r$ \eqref{eq:robust-control}, we approximate it thanks to the interval prediction $[\underline{x}(t), \overline{x}(t)]$ of \autoref{sec:prediction}.
+In order to evaluate the robust objective $V^r$ \eqref{eq:robust-control}, we approximate it thanks to the interval prediction $[\underline{x}(t), \overline{x}(t)]$ of \Cref{sec:prediction}.
 
@@
 \begin{align}
-\label{eq:surrogate_objective} 
+\label{eq:surrogate-objective} 
 \hat{V}^r(\bu) \eqdef \sum_{n=N+1}^\infty \gamma^n \underline{R}_n(\bu)\quad\text{where}\quad\underline{R}_n(\bu) \eqdef \min_{x\in[\underline{x}_n(\bu), \overline{x}_n(\bu)]}  R(x).
@@
 \label{prop:lower-bound}
-The surrogate objective  \eqref{eq:surrogate_objective} is a lower bound of the objective  \eqref{eq:robust-control-disc}.
+The surrogate objective  \eqref{eq:surrogate-objective} is a lower bound of the objective  \eqref{eq:robust-control-disc}.
 %\begin{equation*}
@@
 
-To optimise $\hat{V}^r$ in \eqref{eq:surrogate_objective}, we cannot use DP algorithms since the state space is continuous and the pessimistic rewards are non-Markovian.
+To optimise $\hat{V}^r$ in \eqref{eq:surrogate-objective}, we cannot use DP algorithms since the state space is continuous and the pessimistic rewards are non-Markovian.
 Instead, we turn to tree-based planning algorithms, which optimise a sequence of actions based on the corresponding sequence of rewards, without requiring markovity nor state enumeration.
 In particular, we consider the \emph{Optimistic Planning of Deterministic Systems} (\texttt{OPD}) algorithm \citep{Hren2008} tailored for the case when the relationship between actions and rewards is deterministic.
-Indeed, the stochasticity of the perturbations and measurements is encased in $\hat{V}^r$: given the observations up to time $N$ both the predictor dynamics \eqref{eq:interval-predictor} and the pessimistic rewards in \eqref{eq:surrogate_objective} are deterministic.
+Indeed, the stochasticity of the perturbations and measurements is encased in $\hat{V}^r$: given the observations up to time $N$ both the predictor dynamics \eqref{eq:interval-predictor} and the pessimistic rewards in \eqref{eq:surrogate-objective} are deterministic.
 At each planning iteration $k\in[K]$, \texttt{OPD} progressively builds a tree $\cT_{k+1}$ by forming upper-bounds $B_a(k)$ over the value of sequences of actions $a$, and expanding\footnote{The expansion of a leaf node $a$ refers to the simulation of its children transitions $aA = \{ab, b\in A\}$} the leaf $a_k$ with highest upper-bound:
@@
 \end{equation}
-where $\cL_k$ is the set of leaves of $\cT_k$, $h(a)$ is the length of the sequence $a$, and $\underline{R}_n(a)$ the pessimistic reward \eqref{eq:pessimistic-rewards} obtained at time $n$ by following the controls $u_n = \pi_{a_n}(x_n)$.
+where $\cL_k$ is the set of leaves of $\cT_k$, $h(a)$ is the length of the sequence $a$, and $\underline{R}_n(a)$ the pessimistic reward \eqref{eq:surrogate-objective} obtained at time $n$ by following the controls $u_n = \pi_{a_n}(x_n)$.
 \begin{theorem}[Planning performance of \citealt{Hren2008}]
 \label{theorem:opd-regret}
-The simple regret of the \texttt{OPD} algorithm \eqref{eq:opd} applied to the surrogate objective \eqref{eq:surrogate_objective} after $K$ planning iterations is:
+The simple regret of the \texttt{OPD} algorithm \eqref{eq:opd} applied to the surrogate objective \eqref{eq:surrogate-objective} after $K$ planning iterations is:
 $
@@
 Hence, by using enough computational budget $K$ for planning we can get as close as we want to the optimal surrogate value $\hat{V}^r(a^{\star})$, at a polynomial rate.
-Unfortunately, there exists a gap between $\hat{V}^r$ and the true robust objective $V^r$, which stems from three approximations: (i) the true reachable set was approximated by an enclosing interval in \eqref{eq:inclusion-property}; (ii) the time-invariance of the dynamics uncertainty $A(\theta)\in\cC_{[N],\delta}$ was handled by the interval predictor \eqref{eq:interval-predictor} as if it were a time-varying uncertainty $A(\theta(t))\in\cC_{[N],\delta},\forall t$ ; and (iii) the lower-bound $\sum\min\leq \min\sum$ used to define the surrogate objective \eqref{eq:surrogate_objective} is not tight.
+Unfortunately, there exists a gap between $\hat{V}^r$ and the true robust objective $V^r$, which stems from three approximations: (i) the true reachable set was approximated by an enclosing interval in \eqref{eq:inclusion-property}; (ii) the time-invariance of the dynamics uncertainty $A(\theta)\in\cC_{[N],\delta}$ was handled by the interval predictor \eqref{eq:interval-predictor} as if it were a time-varying uncertainty $A(\theta(t))\in\cC_{[N],\delta},\forall t$ ; and (iii) the lower-bound $\sum\min\leq \min\sum$ used to define the surrogate objective \eqref{eq:surrogate-objective} is not tight.
 However, this gap can be bounded with additional assumptions.
@@
 \end{enumerate}
- we can bound the approximation error of \autoref{alg:full}:
+ we can bound the approximation error of \Cref{alg:full}:
 \begin{equation*}
@@
 
-The procedure we developed in sections \ref{sec:estimation}, \ref{sec:prediction} and \ref{sec:control} relies on strong modelling assumptions, such as the linear dynamics \eqref{eq:dynamics} and \autoref{assumpt:structure}.
+The procedure we developed in sections \ref{sec:estimation}, \ref{sec:prediction} and \ref{sec:control} relies on strong modelling assumptions, such as the linear dynamics \eqref{eq:dynamics} and \Cref{assumpt:structure}.
 But what if they are wrong?
@@
 One of the major benefits of using the family of linear models, compared to richer model classes, is that they provide strict conditions allowing to quantify the adequacy of the modelling assumptions to the observations.
-Given $N-1$ observations, \autoref{sec:estimation} provides a polytopic confidence region \eqref{eq:polytope} that contains $A(\theta)$ with probability at least $1-\delta$.
+Given $N-1$ observations, \Cref{sec:estimation} provides a polytopic confidence region \eqref{eq:polytope} that contains $A(\theta)$ with probability at least $1-\delta$.
 Since the dynamics are linear, we can propagate this confidence region to the next observation: $y_{N}$ must belong to the Minkowski sum of a polytope representing model uncertainty $\cP(A_{0} x_N + Bu_N, \Delta A_{1}x_N,\dots, \Delta A_{2^d}x_N)$ and a polytope $\cP(0_p, \underline{\eta}, \overline{\eta})$ bounding the perturbation and measurement noises.
 \citet{delos2015} provide a way to test this membership in polynomial time using linear programming.
-Whenever it is not verified, we can confidently reject the $(A,\phi)$-modelling \autoref{assumpt:structure}.
+Whenever it is not verified, we can confidently reject the $(A,\phi)$-modelling \Cref{assumpt:structure}.
 This enables us to consider a rich set of potential features $\left((A^1, \phi^1), \dots, (A^M, \phi^M)\right)$ rather than relying on a single assumption, and only retain those that are consistent with the observations so far.
@@
 where $R_n^m$ is the reward obtain by following the action sequence $a$ up to step $n$ under the dynamics $f^m$.
-This objective could be optimised in the same way as in \autoref{sec:control}, but this would result in a coarse and lossy approximation.
-Instead, we exploit the finite uncertainty structure of \autoref{assumpt:multi-model-ambiguity} to asymptotically recover the true $V^r$ by modifying the \texttt{OPD} algorithm in the following way:
+This objective could be optimised in the same way as in \Cref{sec:control}, but this would result in a coarse and lossy approximation.
+Instead, we exploit the finite uncertainty structure of \Cref{assumpt:multi-model-ambiguity} to asymptotically recover the true $V^r$ by modifying the \texttt{OPD} algorithm in the following way:
 
@@
 \label{theorem:drop-regret}
-The robust version of \texttt{OPD} \eqref{eq:robust-b-values} enjoys the same regret bound as \texttt{OPD} in \autoref{theorem:opd-regret}, with respect to the multi-model objective \eqref{eq:robust-objective-discrete}.
+The robust version of \texttt{OPD} \eqref{eq:robust-b-values} enjoys the same regret bound as \texttt{OPD} in \Cref{theorem:opd-regret}, with respect to the multi-model objective \eqref{eq:robust-objective-discrete}.
 \end{theorem}
@@
 The solution of the robust objective \eqref{eq:robust-objective-discrete} with discrete ambiguity $f\in\{f^m\}_{m\in[M]}$ can be recovered exactly, asymptotically when the planning budget $K$ goes to infinity.
-This contrasts the results obtained in \autoref{sec:control} for the robust objective \eqref{eq:robust-control} with continuous ambiguity $A(\theta)\in\cC_{[N],\delta}$, for which \texttt{OPD} only recovers the surrogate approximation $\hat{V}^r$, as discussed in \autoref{thm:control-error}.
-Finally, the two approaches of Sections \ref{sec:control} and \ref{sec:multi-model} can be merged by using the pessimistic reward \eqref{eq:pessimistic-rewards} in \eqref{eq:robust-b-values}.
+This contrasts the results obtained in \Cref{sec:control} for the robust objective \eqref{eq:robust-control} with continuous ambiguity $A(\theta)\in\cC_{[N],\delta}$, for which \texttt{OPD} only recovers the surrogate approximation $\hat{V}^r$, as discussed in \Cref{thm:control-error}.
+Finally, the two approaches of Sections \ref{sec:control} and \ref{sec:multi-model} can be merged by using the pessimistic reward \eqref{eq:surrogate-objective} in \eqref{eq:robust-b-values}.
 
@@
 \paragraph{Obstacle avoidance with unknown friction}
-We first consider a simple illustrative example, shown in \autoref{fig:prediction}: the control of a 2D system with position $(p_x,p_y)$ and velocity $(v_x, v_y)$ moving by means of a force $(u_x, u_y)$ in an environment with unknown anisotropic linear friction with coefficients $(\theta_x, \theta_y)$.
+We first consider a simple illustrative example, shown in \Cref{fig:prediction}: the control of a 2D system with position $(p_x,p_y)$ and velocity $(v_x, v_y)$ moving by means of a force $(u_x, u_y)$ in an environment with unknown anisotropic linear friction with coefficients $(\theta_x, \theta_y)$.
 %$
@@
 %$
-Note that \autoref{assumpt:metzler} is always verified.
+Note that \Cref{assumpt:metzler} is always verified.
 The reward is non-smooth and encodes the task of navigating to reach a goal state $x_g$ while avoiding collisions with obstacles: $R(x) = \delta(x)/(1 + \|x - x_g\|_2)$  where $\delta(x)$ is $0$ whenever $x$ collides with an obstacle, $1$ otherwise.
 The actions $\cA$ are constant controls in the up, down, left and right directions.
-We run \autoref{alg:full} for 100 simulations, and compare in \autoref{tab:obstacle} its performances to that of the nominal agent, i.e.
+We run \Cref{alg:full} for 100 simulations, and compare in \Cref{tab:obstacle} its performances to that of the nominal agent, i.e.
 the non-robust adaptive control approach that plans with the estimated dynamics $\theta_{[N],\lambda}$.
@@
 We also study the evolution of the simple regret $V(x_n) - J_n(x_n)$ with respect to the number of samples $N$, where $J_n(x_n) = \sum_{i > n} \gamma^i R_i$ is the empirical return at state $x_n$ in a trajectory $x_0, R_0, x_1, R_1, \dots$, while $V(x_n)$ is the optimal value that the agent would get by acting optimally from $x_n$ with knowledge of the dynamics.
-The mean regret is shown in \autoref{fig:regret}, along with its 95\% confidence interval.
-We see that \autoref{alg:full} has a regret $\hat{V}^r - V$ decreasing at least polynomially with $N$, as expected from \autoref{thm:control-error}.
+The mean regret is shown in \Cref{fig:regret}, along with its 95\% confidence interval.
+We see that \Cref{alg:full} has a regret $\hat{V}^r - V$ decreasing at least polynomially with $N$, as expected from \Cref{thm:control-error}.
 This shows that the agent gets more aggressive when it is more confident, as desired, while ensuring safety at all time.
@@
 %		{Nominal} & {4\%} & {2.8} & \textbf{$\mathbf{13.8} \pm 2.0$} \\
-%		\autoref{alg:full} & \textbf{0\%} & \textbf{10.4} & {$13.0 \pm 1.5$} \\
+%		\Cref{alg:full} & \textbf{0\%} & \textbf{10.4} & {$13.0 \pm 1.5$} \\
 %		\bottomrule
@@
 		{Nominal} & {4\%} & {2.8} & \textbf{$\mathbf{13.8} \pm 2.0$} \\
-		\autoref{alg:full} & \textbf{0\%} & \textbf{10.4} & {$13.0 \pm 1.5$} \\
+		\Cref{alg:full} & \textbf{0\%} & \textbf{10.4} & {$13.0 \pm 1.5$} \\
 		\bottomrule
@@
 		{Nominal 2} & 33\% & {3.5} & $6.4 \pm 0.26$ \\
-		\autoref{alg:full} & \textbf{0\%} & \textbf{6.8} & $7.1 \pm 0.29$ \\
+		\Cref{alg:full} & \textbf{0\%} & \textbf{6.8} & $7.1 \pm 0.29$ \\
 		\bottomrule
@@
 These vehicles follow parametrized behaviours $\dot{\chi}_i=f_i(x,\theta_i)$ with unknown parameters $\theta_i\in\Real^5$.
-We appreciate a first advantage of the structure imposed in \autoref{assumpt:structure}: the uncertainty space of $\theta$ is $\Real^{5V}$.
+We appreciate a first advantage of the structure imposed in \Cref{assumpt:structure}: the uncertainty space of $\theta$ is $\Real^{5V}$.
 In comparison, the traditional LQ setting where the whole state matrix $A$ is estimated would have resulted in a much larger parameter space $\theta\in\Real^{16V^2}$.
@@
 \citep{Dean2018,abeille18a} reported numerical experiments with states of dimensions 3 and 4, respectively.
-The system dynamics $f$, which describes the couplings and interactions between vehicles, can only be expressed in the form of \autoref{assumpt:structure} given the knowledge of the desired route for each vehicle, with features $\phi$ expressing deviations to the centerline of the followed lane.
-Since these intentions are unknown to the agent, we adopt the multi-model perspective of \autoref{sec:multi-model} and consider one model per possible route for every observed vehicle before an intersection.
-We compare \autoref{alg:full} to a nominal agent planning with the estimated parameter $\theta_{[N],\lambda}$, with two different modelling assumptions: we assume that Nominal 1 has access to the true followed route for each vehicle, while Nominal 2 does not and picks a model with minimal prediction error.
-Their performances are compared in \autoref{tab:driving}.
+The system dynamics $f$, which describes the couplings and interactions between vehicles, can only be expressed in the form of \Cref{assumpt:structure} given the knowledge of the desired route for each vehicle, with features $\phi$ expressing deviations to the centerline of the followed lane.
+Since these intentions are unknown to the agent, we adopt the multi-model perspective of \Cref{sec:multi-model} and consider one model per possible route for every observed vehicle before an intersection.
+We compare \Cref{alg:full} to a nominal agent planning with the estimated parameter $\theta_{[N],\lambda}$, with two different modelling assumptions: we assume that Nominal 1 has access to the true followed route for each vehicle, while Nominal 2 does not and picks a model with minimal prediction error.
+Their performances are compared in \Cref{tab:driving}.
 Again, the robust approach is less efficient on average than planning with a nominal model, but it does better in terms of worst-case performance and manages to avoid collisions, contrary to the nominal baselines that suffer from model bias.
@@
 %		{Nominal 2} & 33\% & {3.5} & $6.4 \pm 0.26$ \\
-%		\autoref{alg:full} & \textbf{0\%} & \textbf{6.8} & $7.1 \pm 0.29$ \\
+%		\Cref{alg:full} & \textbf{0\%} & \textbf{6.8} & $7.1 \pm 0.29$ \\
 %		\bottomrule
@@
 \paragraph{Outline}
-In \autoref{sec:proof}, we provide a proof for every novel result introduced in this paper.
-\autoref{sec:attachments} describes the attached video files and source code.
-\autoref{sec:tight-polytope} gives a better method of conversion from ellipsoid to polytope than that of \eqref{eq:polytope}.
-\autoref{sec:min-max-order} highlights the fact that robustness cannot be recovered by aggregating independent solutions to many optimal control problem.
-Finally, \autoref{sec:experimental-setting} provides additional details on the setting of our experiments.
+In \Cref{sec:proof}, we provide a proof for every novel result introduced in this paper.
+\Cref{sec:attachments} describes the attached video files and source code.
+\Cref{sec:tight-polytope} gives a better method of conversion from ellipsoid to polytope than that of \eqref{eq:polytope}.
+\Cref{sec:min-max-order} highlights the fact that robustness cannot be recovered by aggregating independent solutions to many optimal control problem.
+Finally, \Cref{sec:experimental-setting} provides additional details on the setting of our experiments.
 
@@
 
-\subsection{Proof of \autoref{prop:regularized_solution}}
+\subsection{Proof of \Cref{prop:regularized_solution}}
 
@@
 
-\subsection{Proof of \autoref{thm:confidence_ellipsoid}}
+\subsection{Proof of \Cref{thm:confidence_ellipsoid}}
 
@@
 
-Having shown this preliminary result, we move on to the proof of \autoref{thm:confidence_ellipsoid}.
+Having shown this preliminary result, we move on to the proof of \Cref{thm:confidence_ellipsoid}.
 
@@
 
-By applying \autoref{prop:concentration} with $G=\lambda I_d$, we obtain that with probability at least $1-\delta$,
+By applying \Cref{prop:concentration} with $G=\lambda I_d$, we obtain that with probability at least $1-\delta$,
 \begin{align*}
@@
 
-\subsection{Proof of \autoref{prop:lower-bound}}
+\subsection{Proof of \Cref{prop:lower-bound}}
 
 \begin{proof}
-	The predictor designed in \autoref{sec:prediction} verifies the inclusion property \eqref{eq:inclusion-property}.
+	The predictor designed in \Cref{sec:prediction} verifies the inclusion property \eqref{eq:inclusion-property}.
 Thus, for sequence of controls $\bu$, any dynamics $A(\theta)\in C_{[N],\delta}$, and perturbations $\underline{\bom} \leq \bom \leq \overline{\bom}$, the corresponding state at time $t_n$ is bounded by $\underline{x}_n \leq x_n \leq \overline{x}_n$, which implies that $R(x_n) \geq \min_{x\in[\underline{x}_n(\bu), \overline{x}_n(\bu)]}  R(x) = \underline{R}_n(\bu)$.
@@
 
-\subsection{Proof of \autoref{thm:control-error}}
+\subsection{Proof of \Cref{thm:control-error}}
 
@@
 
- Note that $\Delta_\omega$ is finite, since $C_{\omega}(t_n)$ is in the order of $\underline{\omega}(t_n)$, $\overline{\omega}(t_n)$, and these are either bounded in the case of \autoref{assumpt:bounded-noise}, or in the case of \autoref{assumpt:gaussian-noise} in the order of $\sqrt{2\log n / \delta_n}$, with $\delta_n = \delta/(n(n+1))$, which is dominated by $\gamma^n$.
+ Note that $\Delta_\omega$ is finite, since $C_{\omega}(t_n)$ is in the order of $\underline{\omega}(t_n)$, $\overline{\omega}(t_n)$, and these are either bounded in the case of \Cref{assumpt:bounded-noise}, or in the case of \Cref{assumpt:gaussian-noise} in the order of $\sqrt{2\log n / \delta_n}$, with $\delta_n = \delta/(n(n+1))$, which is dominated by $\gamma^n$.
 \end{proof}
 
-\subsection{Proof of \autoref{theorem:drop-regret}}
+\subsection{Proof of \Cref{theorem:drop-regret}}
 
@@
 \paragraph{Videos}
-The \texttt{video} folder contains videos comparing trajectories of the oracle planner and \autoref{alg:full}.
+The \texttt{video} folder contains videos comparing trajectories of the oracle planner and \Cref{alg:full}.
 The oracle planner has access to the true dynamics and follows aggressive trajectories that nearly saturate the collision constraints.
-In contrast, the \autoref{alg:full} produces more conservative trajectories.
+In contrast, the \Cref{alg:full} produces more conservative trajectories.
 In the obstacle experiment, we show the confidence ellipsoid over $\theta = (\theta_x,\theta_y)$ in the right panel.
@@
 \paragraph{Source code}
-The attached \texttt{code} directory contains an implementation of \autoref{alg:full}. We relate the algorithmic steps of this paper to their location in the source code.
+The attached \texttt{code} directory contains an implementation of \Cref{alg:full}. We relate the algorithmic steps of this paper to their location in the source code.
 \begin{enumerate}
@@
 	\end{align*}
-	This conversion is illustrated in \autoref{fig:ellipsoid_to_polytope}.
+	This conversion is illustrated in \Cref{fig:ellipsoid_to_polytope}.
 \end{lemma}
@@
 
-	This would not recover the robust policy, as we show in \autoref{fig:min-max-order} with a simple counter-example.
+	This would not recover the robust policy, as we show in \Cref{fig:min-max-order} with a simple counter-example.
 	\begin{figure}[htp]
@@
 Precisely, we choose $\Theta$ such that for any $\theta\in\Theta$, $A(\theta)$ is always diagonalisable with real eigenvalues, and perform an eigendecomposition to compute its change of basis matrix $Z$.
-The transformed system $X'=Z^{-1}(X-X_c)$ verifies \eqref{eq:confidence} with $A_0$ Metlzer as required to apply the interval predictor of \autoref{prop:predictor}.
+The transformed system $X'=Z^{-1}(X-X_c)$ verifies \eqref{eq:confidence} with $A_0$ Metlzer as required to apply the interval predictor of \Cref{prop:predictor}.
 Finally, the obtained predictor is transformed back to the original coordinates $Z$ by using the following lemma:

### 2020-05-20 main.tex
Add title, update abstract, related work and experiments

@@
 
-\title{Robust Estimation, Prediction and Control with \\ Linear Dynamics and Generic Costs}
+\title{Interval-based Robust Control of Linear Systems with Generic Costs}
 
@@
 
+\maketitle
+
 \begin{abstract}
 We develop a framework for the adaptive model predictive control (MPC) of a linear system with unknown parameters, in a critical setting where failures are costly and should be prevented at all time.
-We provide the first regret bound for the minimax problem with arbitrary bounded costs, in contrast to the literature which focuses on quadratic costs only.
-Our approach builds on two ideas: first, the dynamics uncertainty is shaped by the prior knowledge of a structure, and refined by a data-driven regression scheme.
-Second, this uncertainty is used to inform decision-making through a minimax control objective.
-Leveraging tools from the interval prediction literature, we convert the confidence regions on dynamics into confidence sets on trajectories induced by the controls.
-These controls are then optimised resorting to tree-based planning methods.
-We eventually relax our modelling assumptions with a multi-model extension based on a data-driven robust model selection mechanism.
-The full procedure is designed to produce reasonable and safe behaviours at deployment while recovering an asymptotic optimality.
-We illustrate it on a simulated application of autonomous driving at a crossroads intersection among vehicles with uncertain behaviours.\footnote{Source code and videos are available in the Supplementary Material.}
+Through the careful selection and non-trivial adaptation of tools from different communities --namely linear regression, interval prediction and tree-based planning--, we provide an integrated solution to the problem of maximin control with arbitrary bounded costs.
+We ensured that theoretical guarantees at each layer could be combined to provide what we believe is the first end-to-end analysis in this general setting.
+The full procedure is designed to produce reasonable and safe behaviours at deployment while progressively recovering an asymptotic optimality.
+Finally, we relax our modelling assumptions in a multi-model extension based on a data-driven robust model selection mechanism.
+In addition to our theoretical results we strived to preserve tractable computations for practical applicability, as we illustrate on a simulated application of autonomous driving at a crossroads intersection.\footnote{Source code and videos are available in the Supplementary Material.}
 \end{abstract}
@@
 First, it depends on a tremendous amount of interaction data that cannot always be simulated.
-This issue is alleviated by model-based methods -- which we consider in this work -- that benefit from better sample efficiencies by exploiting a richer data stream than their model-free counterparts.
+This issue is alleviated by model-based methods -- which we consider in this work -- that often benefit from better sample efficiencies than their model-free counterparts.
 Second, it relies on trial-and-error and random exploration.
 In this paper, we consider the problem of controlling an unknown linear system $x(t)$ so as to maximise an \emph{arbitrary} bounded reward function $R$, in a critical setting where mistakes are costly and must be avoided at all time.
-This choice of rich reward space is crucial to have sufficient flexibility to model non-convex and non-smooth functions that naturally arise in many practical problems involving combinatorial optimisation, branching decisions, etc., while quadratic costs are mostly suited for tracking a reference trajectory already known a priori \citep[e.g.][]{Kumar2013}.
+This choice of rich reward space is crucial to have sufficient flexibility to model non-convex and non-smooth functions that naturally arise in many practical problems involving combinatorial optimisation, branching decisions, etc., while quadratic costs are mostly suited for tracking a fixed reference trajectory \citep[e.g.][]{Kumar2013}.
 
@@
 With arbitrary functions $R$, we cannot hope to derive a solution in explicit form.
-In particular, this excludes a number of tools from the robust synthesis literature which is focused on stabilization problems, such as $\cH_\infty$ control \citep[see, e.g.][]{Basar1996}, sliding-mode control, tube-MPC or system-level synthesis \citep{Dean2017,Dean2018}.
 In our second contribution, we propose a robust MPC algorithm for solving \eqref{eq:robust-control} numerically.
@@
 
-Finally, in \Cref{sec:experiments} we demonstrate the applicability of our proposed \Cref{alg:full} in two numerical experiments.
-First, a simple illustrative example and then, a more challenging simulation for safe autonomous driving.
+Finally, in \Cref{sec:experiments} we demonstrate the applicability of \Cref{alg:full} in two numerical experiments: a simple illustrative example and a more challenging simulation for safe autonomous driving.
 
@@
 
-\paragraph{Linear dynamics} There is a rich body of literature dedicated to the study of linear systems with quadratic costs, and we focus on those providing non-asymptotic results when the system parameters $A, B$ are unknown.
-In their seminal work \citet{abbasi-yadkori11a}, consider the problem of cumulative regret minimisation.
-They follow the \emph{Optimism in the Face of Uncertainty} paradigm from the multi-armed bandit literature, that consists in selecting the best possible dynamics within a high-confidence region while enforcing a controllability constraint, and computing the corresponding optimal control in closed-form by solving a Riccati equation.
-They show that this procedures achieves a $\tilde{\cO}\left(N^{1/2}\right)$ cumulative regret.
-\citep{Ibrahimi2013,Faradonbeh2017} adapt these results to the case of sparse dynamics.
-\citet{Ouyang2017,abeille18a} provide the same result by applying Thomson Sampling rather of optimism to select a dynamical model, and rejection sampling to enforce the controllability constraint.
-These methods aim at regret minimisation to quickly reduce uncertainty, through information-seeking behaviours.
+While there exists a vast body of literature on the control of uncertain systems, its majority is only concerned with the problem of stabilisation at an equilibrium, including $\cH_\infty$ control \citep[see, e.g.][]{Basar1996}, sliding-mode control \citep{}, tube-MPC \citep{} or system-level synthesis \citep{Dean2017,Dean2018}.
+Yet, we made the case that many tasks cannot be framed as stabilisation problems (e.g.
+obstacle avoidance) and are better addressed in our harder setting of maximising an arbitrary utility function, where no prior result exists to our knowledge.
+Therefore, we limit references to focus only on two lines of work closest to ours.
+
+\paragraph{Linear systems with quadratic costs} Several approaches have been proposed for the problem of cumulative regret minimisation of a LQ problem.
+In the \emph{Optimism in the Face of Uncertainty} paradigm, the best possible dynamics within a high-confidence region is selected under a controllability constraint, to compute the corresponding optimal control in closed-form by solving a Riccati equation.
+\citep{abbasi-yadkori11a,Ibrahimi2013,Faradonbeh2017} show that this procedures achieves a $\tilde{\cO}\left(N^{1/2}\right)$ regret.
+Posterior sampling algorithms \citep{Ouyang2017,abeille18a} select candidate dynamics randomly instead, and obtain the same result.
 Other works use noise injection for exploration such as \citep{Dean2017,Dean2018}.
-However, neither optimism and cumulative regret minimisation nor random exploration fit a critical setting, where ensuring safety as a top priority requires instead to consider the pessimistic outcomes.
+However, neither optimism nor random exploration fit a critical setting, where ensuring safety requires instead to consider pessimistic outcomes.
 The work of \citet{Dean2017} is closest to our setting: after an offline estimation phase, they estimate a simple regret between a robust controller and the optimal performance.
-Our work mainly differs in that it addresses generic costs and forbids random exploration.
-
-\paragraph{Generic costs}
+Our work mainly differs in that it addresses generic costs.
+
+\paragraph{Robust Dynamic Programming with generic costs}
 Robust optimisation with generic costs has also been studied in the context of finite Markov Decision Processes with uncertain parameters by \citet{Iyengar2005}, \citet{Nilim2005} and \citet{Wiesemann2013}.
@@
 
-To derive a confidence region \eqref{eq:confidence} for the dynamical parameters $\theta$, the functional relationship $A(\theta)$ must be specified.
+To derive a confidence region \eqref{eq:confidence} for $\theta$, the functional relationship $A(\theta)$ must be specified.
 \begin{assumption}[Structure]
@@
 However, \citet{leurent2019interval} showed that this predictor can have unstable dynamics, even for stable systems, which causes a fast build-up of uncertainty.
-They proposed an enhanced predictor which exploits the polytopic structure \eqref{eq:polytope} to produce tighter and more stable predictions, at the price of an additional requirement:
+They proposed an enhanced predictor which exploits the polytopic structure \eqref{eq:polytope} to produce more stable predictions, at the price of a requirement:
 
@@
 \end{assumption}
-In practice, this assumption is often verified.
-It is for instance the case whenever $A_0$ is diagonalisable.
+In practice, this assumption is often verified: it is for instance the case whenever $A_0$ is diagonalisable.
 The similarity transformation of \citep{Efimov2013} provides a method to compute such $Z$ when the system is observable.
@@
 
-\Cref{fig:predictor_example} illustrates the difference of stability of the two predictors \eqref{eq:predictor-naive} and \eqref{eq:interval-predictor} with a simple example.
+\Cref{fig:predictor_example} compares the stability of the predictors \eqref{eq:predictor-naive} and \eqref{eq:interval-predictor} in a simple example.
 It suggests to always prefer \eqref{eq:interval-predictor} whenever \Cref{assumpt:metzler} is verified, and only fallback to \eqref{eq:predictor-naive} as a last resort.
@@
 \label{sec:control}
-In order to evaluate the robust objective $V^r$ \eqref{eq:robust-control}, we approximate it thanks to the interval prediction $[\underline{x}(t), \overline{x}(t)]$ of \Cref{sec:prediction}.
+To evaluate the robust objective $V^r$ \eqref{eq:robust-control}, we approximate it thanks to the interval prediction $[\underline{x}(t), \overline{x}(t)]$.
 
@@
 \label{prop:lower-bound}
-The surrogate objective  \eqref{eq:surrogate-objective} is a lower bound of the objective  \eqref{eq:robust-control-disc}.
+The surrogate objective  \eqref{eq:surrogate-objective} is a lower bound of the objective  \eqref{eq:robust-control}.
 %\begin{equation*}
@@
 To optimise $\hat{V}^r$ in \eqref{eq:surrogate-objective}, we cannot use DP algorithms since the state space is continuous and the pessimistic rewards are non-Markovian.
-Instead, we turn to tree-based planning algorithms, which optimise a sequence of actions based on the corresponding sequence of rewards, without requiring markovity nor state enumeration.
+Instead, we turn to tree-based planning algorithms, which optimise a sequence of actions based on the corresponding sequence of rewards, without requiring Markovity nor state enumeration.
 In particular, we consider the \emph{Optimistic Planning of Deterministic Systems} (\texttt{OPD}) algorithm \citep{Hren2008} tailored for the case when the relationship between actions and rewards is deterministic.
@@
 Unfortunately, there exists a gap between $\hat{V}^r$ and the true robust objective $V^r$, which stems from three approximations: (i) the true reachable set was approximated by an enclosing interval in \eqref{eq:inclusion-property}; (ii) the time-invariance of the dynamics uncertainty $A(\theta)\in\cC_{[N],\delta}$ was handled by the interval predictor \eqref{eq:interval-predictor} as if it were a time-varying uncertainty $A(\theta(t))\in\cC_{[N],\delta},\forall t$ ; and (iii) the lower-bound $\sum\min\leq \min\sum$ used to define the surrogate objective \eqref{eq:surrogate-objective} is not tight.
-However, this gap can be bounded with additional assumptions.
+However, this gap can be bounded under additional assumptions.
 \begin{theorem}[Regret bound]
@@
 	\item a Lipschitz regularity assumption for the reward $R$;
-	\item a persistent excitation (PE) assumption:
-	\begin{align*}
+	\item a persistent excitation assumption:
+	$
 	\exists \underline{\phi},\overline{\phi}>0: \forall n\geq n_0,\quad \underline{\phi}^2 \leq \lambda_{\min}(\Phi_{n}^\transp\Sigma_{p}^{-1}\Phi_{n}) \leq \overline{\phi}^2;
-	\end{align*}
+	$
 	\item a stability condition: there exist $P>0,Q_0\in\Real^{p\times p}$, $\rho>0$ such that
@@
 $
-\exists m\in[M]: \dot{x}(t) = f^m(x(t), u(t)), \forall t\geq 0
+\qquad\qquad
+\exists m\in[M]: \dot{x}(t) = f^m(x(t), u(t)), \forall t\geq 0.
 $
@@
 
-\begin{definition}[Robust sequence upper bounds] We replace the upper-bound \eqref{eq:opd} on sequence values in \texttt{OPD} by: 
+\begin{definition}[Robust sequence upper bounds] We replace the upper-bound \eqref{eq:opd} on sequence values in \texttt{OPD} by: \hfill
 $
@@
 
-This result is of independent interest for robust planning with discrete ambiguity: the exact solution is recovered asymptotically, which Robust DP algorithms do not allow.
-The regret depends on the number $K$ of node expansions, but each expansion now requires $M$ times more simulations than in the single-model setting.
-The solution of the robust objective \eqref{eq:robust-objective-discrete} with discrete ambiguity $f\in\{f^m\}_{m\in[M]}$ can be recovered exactly, asymptotically when the planning budget $K$ goes to infinity.
-This contrasts the results obtained in \Cref{sec:control} for the robust objective \eqref{eq:robust-control} with continuous ambiguity $A(\theta)\in\cC_{[N],\delta}$, for which \texttt{OPD} only recovers the surrogate approximation $\hat{V}^r$, as discussed in \Cref{thm:control-error}.
+This result is of independent interest: the solution of a robust objective \eqref{eq:robust-objective-discrete} with discrete ambiguity $f\in\{f^m\}_{m\in[M]}$ can be recovered exactly, asymptotically when the planning budget $K$ goes to infinity, which Robust DP algorithms do not allow.
+This also contrasts with the results obtained in \Cref{sec:control} for the robust objective \eqref{eq:robust-control} with continuous ambiguity $A(\theta)\in\cC_{[N],\delta}$, for which \texttt{OPD} only recovers the surrogate approximation $\hat{V}^r$, as discussed in \Cref{thm:control-error}.
+Note that here the regret depends on the number $K$ of node expansions, but each expansion now requires $M$ times more simulations than in the single-model setting.
 Finally, the two approaches of Sections \ref{sec:control} and \ref{sec:multi-model} can be merged by using the pessimistic reward \eqref{eq:surrogate-objective} in \eqref{eq:robust-b-values}.
@@
 \paragraph{Obstacle avoidance with unknown friction}
-We first consider a simple illustrative example, shown in \Cref{fig:prediction}: the control of a 2D system with position $(p_x,p_y)$ and velocity $(v_x, v_y)$ moving by means of a force $(u_x, u_y)$ in an environment with unknown anisotropic linear friction with coefficients $(\theta_x, \theta_y)$.
+We first consider a simple illustrative example, shown in \Cref{fig:prediction}: the control of a 2D system %with position $(p_x,p_y)$ and velocity $(v_x, v_y)$ 
+moving by means of a force $(u_x, u_y)$ in an environment with unknown anisotropic linear friction with coefficients $(\theta_x, \theta_y)$.
 %$
@@
 %$
-Note that \Cref{assumpt:metzler} is always verified.
 The reward is non-smooth and encodes the task of navigating to reach a goal state $x_g$ while avoiding collisions with obstacles: $R(x) = \delta(x)/(1 + \|x - x_g\|_2)$  where $\delta(x)$ is $0$ whenever $x$ collides with an obstacle, $1$ otherwise.
 The actions $\cA$ are constant controls in the up, down, left and right directions.
-We run \Cref{alg:full} for 100 simulations, and compare in \Cref{tab:obstacle} its performances to that of the nominal agent, i.e.
-the non-robust adaptive control approach that plans with the estimated dynamics $\theta_{[N],\lambda}$.
-We observe that though the robust agent performs worse than the nominal agent on average, it manages to ensure safety and attains a better worst-case performance, as intended.
-We also study the evolution of the simple regret $V(x_n) - J_n(x_n)$ with respect to the number of samples $N$, where $J_n(x_n) = \sum_{i > n} \gamma^i R_i$ is the empirical return at state $x_n$ in a trajectory $x_0, R_0, x_1, R_1, \dots$, while $V(x_n)$ is the optimal value that the agent would get by acting optimally from $x_n$ with knowledge of the dynamics.
+For the reasons mentioned above, no robust baseline applies to our setting.
+Rather than comparing \Cref{alg:full} to RL baselines which inevitably commit many failures, we consider the nominal agent i.e.
+the non-robust adaptive control approach that plans with the estimated dynamics $\theta_{[N],\lambda}$, and thus enjoys the same prior knowledge of dynamics structure and reward.
+This highlights the benefits of the robust formulation solely rather than stemming from algorithm design.
+The results of 100 simulations are shown in \Cref{tab:obstacle}: though the robust agent performs worse than the nominal agent on average, it manages to ensure safety and attains a better worst-case performance.
+We also study the evolution of the simple regret $V(x_n) - J_n(x_n)$ with respect to the number of samples $N$, where $J_n(x_n) = \sum_{i > n} \gamma^i R_i$ is the empirical return at state $x_n$ in a trajectory, while $V(x_n)$ is the optimal value that the agent would get by acting optimally from $x_n$ with knowledge of the dynamics.
 The mean regret is shown in \Cref{fig:regret}, along with its 95\% confidence interval.
 We see that \Cref{alg:full} has a regret $\hat{V}^r - V$ decreasing at least polynomially with $N$, as expected from \Cref{thm:control-error}.
-This shows that the agent gets more aggressive when it is more confident, as desired, while ensuring safety at all time.
+Thus, the agent gets more aggressive when more confident, as desired, while ensuring safety at all time.
 In contrast, the nominal agent has an even smaller regret but collided with obstacles in $4\%$ of simulations.
@@
 	\label{tab:obstacle}
-	\small
+
 	\begin{tabular}{lccc}
 		\toprule
-		Agent &
+		Performance &
 		failures &
-		min $J$ &
-		mean $J$ $\pm$ std  \\
+		min &
+		avg $\pm$ std  \\
 		\midrule
@@
 \parbox{.49\linewidth}{
-	\small
+
 	\caption{Performances on the driving task}
@@
 		\toprule
-		Agent &
+		Performance &
 		failures &
-		min $J$ &
-		mean $J$ $\pm$ std  \\
+		min &
+		avg $\pm$ std  \\
 		\midrule
@@
 \clearpage
+
+\section*{Broader Impact}
+
+Authors are required to include a statement of the broader impact of their work, including its ethical aspects and future societal consequences. 
+Authors should discuss both positive and negative outcomes, if any. For instance, authors should discuss a) 
+who may benefit from this research, b) who may be put at disadvantage from this research, c) what are the consequences of failure of the system, and d) whether the task/method leverages
+biases in the data. If authors believe this is not applicable to them, authors can simply state this.
+
+Use unnumbered first level headings for this section, which should go at the end of the paper. {\bf Note that this section does not count towards the eight pages of content that are allowed.}
+
 \bibliography{references}
@@
 	\item The enhanced predictor of \eqref{eq:interval-predictor} is implemented in the \texttt{step\_interval\_predictor()} method of \url{code/rl_agents/agents/common/interval.py}
-	\item The pessimistic reward of \eqref{eq:pessimistic-rewards} is implemented in the \texttt{pessimistic\_reward()} method of \url{code/obstacle_env/envs/obstacle.py} and the \texttt{check\_collision()} method of \url{code/highway_env/vehicle/uncertainty/prediction.py}
+	\item The pessimistic reward of \eqref{eq:surrogate-objective} is implemented in the \texttt{pessimistic\_reward()} method of \url{code/obstacle_env/envs/obstacle.py} and the \texttt{check\_collision()} method of \url{code/highway_env/vehicle/uncertainty/prediction.py}
 	\item The robust upper-bound of \eqref{eq:robust-b-values} is implemented in the \texttt{RobustNode} class of \url{code/rl_agents/agents/tree_search/robust.py}
@@
 
-\section{Experimental setting}
+\section{Experimental details}
 \label{sec:experimental-setting}
@@
 
+\subsection{Obstacle Avoidance}
+
+Note that \Cref{assumpt:metzler} is always verified.
+
 \subsection{Autonomous Driving}
@@
 
-\paragraph{Kinematics}
+\paragraph{States}
+
+In addition to the ego-vehicle, the scene contains $V$ other vehicles.
+Any vehicle $i\in[0,V]$ is represented by its position $(x_i, y_i)$, its forward velocity $v_i$ its heading $\psi_i$.
+The resulting joint state is the traffic description: $x = (x_i, y_i, v_i, psi_i)_{i\in[0,V]}\in\Real^{4V+4}$.
+
+\paragraph{Actions}
+
+The ego-vehicle is following a fixed path, and the tasks consists in adapting its velocity by means of three actions $\cA = \{$faster, constant velocity, slower$\}$.
+They are achieved by a longitudinal linear controller that tracks the desired velocity $v_0$, as described below in the system dynamics.
+
+\paragraph{Reward}
+
+The reward function $R$ is the following:
+\[
+R(x) = 
+\begin{cases}
+1 & \text{if the ego-vehicle is at full velocity;}\\
+0 & \text{if the ego-vehicle has collided with another vehicle;}\\
+0.5 & \text{else.}
+\end{cases}\]
+
+\paragraph{Dynamics}
 
@@
 	\dot{v}_i &= a_i, \nonumber\\
-	\dot{\psi}_i &= \frac{v_i}{l}tan(\beta_i), \nonumber
+	\dot{\psi}_i &= \frac{v_i}{l}\sin(\beta_i), \nonumber
 \end{align}
@@
 
-\paragraph{Longitudinal control}
+\paragraph{Longitudinal dynamics}
 Longitudinal behaviour is modelled by a linear controller using three features: a desired velocity, a braking term to drive slower than the front vehicle, and a braking term to respect a safe distance to the front vehicle.
@@
 
-\paragraph{Lateral control}
+\paragraph{Lateral dynamics}
 
@@
 \end{align}
-We assume that the drivers choose their steering command $\beta_i$ such that \eqref{eq:heading-command} is always achieved: $\beta_i = \tan^{-1}(\frac{l}{v_i}\dot{\psi}_i)$.
+We assume that the drivers choose their steering command $\beta_i$ such that \eqref{eq:heading-command} is always achieved: $\beta_i = \sin^{-1}(\frac{l}{v_i}\dot{\psi}_i)$.
 
@@
 
-\paragraph{Actions}
-
-The action space $\cA$ is constituted of five actions: faster, slower, lane change to the right, lane change to the left, and no-op.
-They are implemented by a lateral linear controller that track a reference lateral position $y_L$, affected by the lane change actions, and a lateral longitudinal linear controller that tracks the desired velocity $v_0$, affected by the faster and slower actions.
-
-\paragraph{Reward}
-
-The reward function $R$ is the following:
-\[
-R(x) = 
-\begin{cases}
-1 & \text{if the ego-vehicle is at full velocity;}\\
-0 & \text{if the ego-vehicle has collided with another vehicle;}\\
-0.5 & \text{else.}
-\end{cases}\]
-
 \end{document}

### 2020-05-23 main.tex
Various changes and broader impact

@@
 Assumptions over the disturbance $\omega$ and noise $\nu$ will be detailed further, and we denote $\eta(t) = C\nu(t) + D\omega(t)$.
-We argue that this assumption is realistic given that most industrial applications to date have been relying on physical models to describe their processes and well-engineered controllers to operate them, rather than machine learning.
+We argue that this structure assumption is realistic given that most industrial applications to date have been relying on physical models to describe their processes and well-engineered controllers to operate them, rather than machine learning.
 Our framework relaxes this modelling effort by allowing some \emph{structured uncertainty} around the nominal model.
@@
 
-This confidence region $\cC_{[N],\delta}$ allows to formulate the \emph{robust control objective} $V^r$ \citep{Bental2009,Bertsimas2011,Gorissen2015} which maximises the worst-case outcome with respect to this uncertainty:
+The \emph{robust control objective} $V^r$ \citep{Bental2009,Bertsimas2011,Gorissen2015} aims to maximise the worst-case outcome with respect to this confidence region $\cC_{[N],\delta}$:
 \begin{equation}
 \label{eq:robust-control}
-\sup_{\bu\in{(\Real^q)}^\Natural} \underbrace{\inf_{\substack{A(\theta) \in \cC_{[N],\delta} \\ \bom\in[\underline{\bom},\overline{\bom}]^\Natural}} \left[\sum_{n=N+1}^\infty \gamma^n R(x_n(\bu,\bom))\right]}_{V^r(\bu)}
-\end{equation}
-where $\gamma\in(0,1)$ is a discount factor.
-Maximin problems such as $\eqref{eq:robust-control}$ even in cases such where the reward $R$ has a simple form.
-With arbitrary functions $R$, we cannot hope to derive a solution in explicit form.
+\sup_{\bu\in{(\Real^q)}^\Natural} {V^r(\bu)}, \qquad \text{ where }\qquad {V^r(\bu)} \eqdef \inf_{\substack{A(\theta) \in \cC_{[N],\delta} \\ \bom\in[\underline{\bom},\overline{\bom}]^\Natural}} \left[\sum_{n=N+1}^\infty \gamma^n R(x_n(\bu,\bom))\right],
+\end{equation}
+$\gamma\in(0,1)$ is a discount factor, and $x_n(\bu,\bom)$ is the state reached at step $n$ under controls $\bu$ and perturbations $\bom$.
+Maximin problems such as $\eqref{eq:robust-control}$ are notoriously hard in cases such where the reward $R$ has a simple form.
+With arbitrary functions $R$, we cannot hope to derive an explicit solution.
 In our second contribution, we propose a robust MPC algorithm for solving \eqref{eq:robust-control} numerically.
@@
 In \Cref{sec:control}, facing a sequential decision problem with continuous states, we turn to the literature of tree-based planning algorithms.
-Though there exist works addressing continuous actions \citep{Busoniu2018,Weinstein2012}, we resort to a first approximation and discretise the continuous decision $(\Real^q)^\Natural$ space by adopting a hierarchical control architecture: at each time, the agent can select a high-level \emph{action} $a$ from a finite action space $\cA$.
+Though there exist works addressing continuous actions \citep{Busoniu2018,Weinstein2012}, we resort to a first approximation and discretise the continuous decision $(\Real^q)^\Natural$ space by adopting a hierarchical control architecture: at each time, the agent can select a high-level \emph{action} $a$ from a finite space $\cA$.
 Each action $a\in\cA$ corresponds to the selection of a low-level controller $\pi_a$, that we take affine: $u(t) = \pi_a(x(t)) \eqdef -K_a x(t) + u_a.$ For instance, a tracking a subgoal $x_g$ can be achieved with $\pi_g = K(x_g - x)$.
-The discretisation induces a suboptimality, but it can be mitigated by diversifying the controller basis.
+This discretisation induces a suboptimality, but it can be mitigated by diversifying the controller basis.
 The robust objective \eqref{eq:robust-control} becomes $\sup_{\ba\in{\cA}^\Natural} V^r(\ba)$, where $x_n(\ba, \bom)$ stems from \eqref{eq:dynamics} with $u_n = \pi_{a_n}(x_n)$.
@@
 
-While there exists a vast body of literature on the control of uncertain systems, its majority is only concerned with the problem of stabilisation at an equilibrium, including $\cH_\infty$ control \citep[see, e.g.][]{Basar1996}, sliding-mode control \citep{}, tube-MPC \citep{} or system-level synthesis \citep{Dean2017,Dean2018}.
-Yet, we made the case that many tasks cannot be framed as stabilisation problems (e.g.
-obstacle avoidance) and are better addressed in our harder setting of maximising an arbitrary utility function, where no prior result exists to our knowledge.
+While there exists a vast body of literature on the control of uncertain systems, its majority is only concerned with the problem of stabilisation at an equilibrium, including $\cH_\infty$ control \citep[see, e.g.][]{Basar1996}, sliding-mode control \citep{Lu1997}, tube-MPC \citep{Limon2010} or system-level synthesis \citep{Dean2017,Dean2018}.
+Yet, we argue that many tasks cannot be framed as stabilisation problems (e.g.
+obstacle avoidance) and are better addressed in our setting of maximising an arbitrary utility function, where no prior result exists to our knowledge.
+Other safety frameworks exist such as constraining the state $x$ in a safe region $\mathbb{X}$ often chosen convex \citep[e.g.][]{Turchetta2016}, which again is not suitable for many tasks (e.g.
+these of \Cref{sec:experiments}).
 Therefore, we limit references to focus only on two lines of work closest to ours.
 
-\paragraph{Linear systems with quadratic costs} Several approaches have been proposed for the problem of cumulative regret minimisation of a LQ problem.
+\paragraph{Linear systems with quadratic costs} Several approaches have been proposed for cumulative regret minimisation in the LQ problem.
 In the \emph{Optimism in the Face of Uncertainty} paradigm, the best possible dynamics within a high-confidence region is selected under a controllability constraint, to compute the corresponding optimal control in closed-form by solving a Riccati equation.
 \citep{abbasi-yadkori11a,Ibrahimi2013,Faradonbeh2017} show that this procedures achieves a $\tilde{\cO}\left(N^{1/2}\right)$ regret.
-Posterior sampling algorithms \citep{Ouyang2017,abeille18a} select candidate dynamics randomly instead, and obtain the same result.
+Posterior sampling algorithms \citep{Ouyang2017,abeille18a} sample candidate dynamics randomly instead, and obtain the same result.
 Other works use noise injection for exploration such as \citep{Dean2017,Dean2018}.
@@
 \paragraph{Robust Dynamic Programming with generic costs}
-Robust optimisation with generic costs has also been studied in the context of finite Markov Decision Processes with uncertain parameters by \citet{Iyengar2005}, \citet{Nilim2005} and \citet{Wiesemann2013}.
-They showed that the main results of DP can be extended to their robust counterparts only when the dynamics ambiguity set verifies a certain rectangularity property, that amounts to an independence assumption between the uncertainty sets of each transition and is related to time-varying uncertainty.
-Since our setting requires dealing with continuous states and time-invariant uncertainty, these methods do not apply.
+Robust optimisation with generic costs has been studied in the context of finite Markov Decision Processes with uncertain parameters by \citet{Iyengar2005}, \citet{Nilim2005} and \citet{Wiesemann2013}.
+They showed that the main results of Dynamic Programming can be extended to their robust counterparts only when the dynamics ambiguity set verifies a certain rectangularity property, related to time-varying uncertainty.
+Since our setting considers continuous states and time-invariant uncertainty, these methods do not apply.
 
@@
 	Let $\underline{x}_n(\bu), \overline{x}_n(\bu)$ following the dynamics defined in \eqref{eq:interval-predictor} and
-\begin{align}
+\begin{equation}
 \label{eq:surrogate-objective} 
@@
 %\label{eq:pessimistic-rewards}
-\end{align}
+\end{equation}
 \end{definition}
@@
 $
-where $R_n^m$ is the reward obtain by following the action sequence $a$ up to step $n$ under the dynamics $f^m$.
+where $R_n^m$ is the reward obtained by following the action sequence $a$ up to step $n$ under the dynamics $f^m$.
 This objective could be optimised in the same way as in \Cref{sec:control}, but this would result in a coarse and lossy approximation.
@@
 We first consider a simple illustrative example, shown in \Cref{fig:prediction}: the control of a 2D system %with position $(p_x,p_y)$ and velocity $(v_x, v_y)$ 
-moving by means of a force $(u_x, u_y)$ in an environment with unknown anisotropic linear friction with coefficients $(\theta_x, \theta_y)$.
+moving by means of a force $(u_x, u_y)$ in an medium with anisotropic linear friction with unknown coefficients $(\theta_x, \theta_y)$.
 %$
@@
 This highlights the benefits of the robust formulation solely rather than stemming from algorithm design.
-The results of 100 simulations are shown in \Cref{tab:obstacle}: though the robust agent performs worse than the nominal agent on average, it manages to ensure safety and attains a better worst-case performance.
-We also study the evolution of the simple regret $V(x_n) - J_n(x_n)$ with respect to the number of samples $N$, where $J_n(x_n) = \sum_{i > n} \gamma^i R_i$ is the empirical return at state $x_n$ in a trajectory, while $V(x_n)$ is the optimal value that the agent would get by acting optimally from $x_n$ with knowledge of the dynamics.
-The mean regret is shown in \Cref{fig:regret}, along with its 95\% confidence interval.
-We see that \Cref{alg:full} has a regret $\hat{V}^r - V$ decreasing at least polynomially with $N$, as expected from \Cref{thm:control-error}.
-Thus, the agent gets more aggressive when more confident, as desired, while ensuring safety at all time.
+The results of 100 simulations are shown in \Cref{tab:obstacle}: the robust agent performs worse than the nominal agent on average, but manages to ensure safety and attains a better worst-case performance.
+We also study the evolution of the simple regret $V(x_n) - J_n(x_n)$ with respect to the number of samples $N$, where $J_n(x_n) = \sum_{i > n} \gamma^i R_i$ is the empirical return from state $x_n$, while $V(x_n)$ is the optimal value that the agent would get by acting optimally from $x_n$ with knowledge of the dynamics.
+The mean regret $\hat{V}^r - V$, shown in \Cref{fig:regret} with its 95\% confidence interval, decreases polynomially with $N$ as expected from \Cref{thm:control-error}.
+Thus, \Cref{alg:full} gets more aggressive as it is more confident, while ensuring safety at all time.
 In contrast, the nominal agent has an even smaller regret but collided with obstacles in $4\%$ of simulations.
@@
 Since these intentions are unknown to the agent, we adopt the multi-model perspective of \Cref{sec:multi-model} and consider one model per possible route for every observed vehicle before an intersection.
-We compare \Cref{alg:full} to a nominal agent planning with the estimated parameter $\theta_{[N],\lambda}$, with two different modelling assumptions: we assume that Nominal 1 has access to the true followed route for each vehicle, while Nominal 2 does not and picks a model with minimal prediction error.
+We compare \Cref{alg:full} to a nominal agent planning with the estimated parameter $\theta_{[N],\lambda}$, with two different modelling assumptions: we assume that Nominal 1 has access to the true followed route for each vehicle, while Nominal 2 does not and picks the model with minimal prediction error.
 Their performances are compared in \Cref{tab:driving}.
@@
 
-Authors are required to include a statement of the broader impact of their work, including its ethical aspects and future societal consequences. 
-Authors should discuss both positive and negative outcomes, if any. For instance, authors should discuss a) 
-who may benefit from this research, b) who may be put at disadvantage from this research, c) what are the consequences of failure of the system, and d) whether the task/method leverages
-biases in the data. If authors believe this is not applicable to them, authors can simply state this.
-
-Use unnumbered first level headings for this section, which should go at the end of the paper. {\bf Note that this section does not count towards the eight pages of content that are allowed.}
+The motivation behind this work is to enable the development of Reinforcement Learning solutions for industrial applications, when it has hitherto been mainly limited to simulated games.
+In particular, many industries already rely on non-adaptive control systems and could benefit from an increased efficiency, including Oil and Gas, robotics for industrial automation, Data Center cooling, etc.
+But more often than not, safety-critical constraints bar the use of exploration, and industrials are reluctant to turn to learning-based methods that lack accountability.
+This work addresses these concerns by focusing on risk-averse decisions and by providing worst-case guarantees.
+Note however that these guarantees are only as good as the validity of the underlying hypotheses, and \Cref{assumpt:structure} in particular should be submitted to a comprehensive validation procedure; otherwise, decisions formed on a wrong basis could easily lead to dramatic consequences in such critical settings.
+Beyond industrial perspectives, this work could be of general interest for risk-averse decision-making.
+For instance, parametrized epidemiological models have been used to represent the propagation of Covid\nobreakdash-19 and study the impact of several lockdown policies.
+These model parameters are estimated from observational data and corresponding confidence intervals are often available, but rarely used in the decision-making loop.
+In contrast, our approach would enable evaluating and optimising the worst-case outcome of such public policies.
 
@@
 \Cref{sec:min-max-order} highlights the fact that robustness cannot be recovered by aggregating independent solutions to many optimal control problem.
-Finally, \Cref{sec:experimental-setting} provides additional details on the setting of our experiments.
+Finally, \Cref{sec:experimental-setting} provides additional details on our experiments.
 
@@
 \begin{proof}
-By \eqref{eq:g_n_lambda} and \eqref{eq:excitation}, we have $$\lambda_{\min}(G_{[N],\lambda,i,j}) \geq (N-n_0)\underline{\phi}^2 + \sum_{n<n_0}\Phi_{n}^\transp\Sigma_{p}^{-1}\Phi_{n}$$
+By \eqref{eq:vector_rls} and \eqref{eq:excitation}, we have $$\lambda_{\min}(G_{[N],\lambda,i,j}) \geq (N-n_0)\underline{\phi}^2 + \sum_{n<n_0}\Phi_{n}^\transp\Sigma_{p}^{-1}\Phi_{n}$$
 
@@
 \end{align*}
-and \eqref{eq:beta_n} gives
+and \eqref{eq:confidence-ellipsoid} gives
 
@@
 
- Note that $\Delta_\omega$ is finite, since $C_{\omega}(t_n)$ is in the order of $\underline{\omega}(t_n)$, $\overline{\omega}(t_n)$, and these are either bounded in the case of \Cref{assumpt:bounded-noise}, or in the case of \Cref{assumpt:gaussian-noise} in the order of $\sqrt{2\log n / \delta_n}$, with $\delta_n = \delta/(n(n+1))$, which is dominated by $\gamma^n$.
+ Note that $\Delta_\omega$ is finite, since $C_{\omega}(t_n)$ is in the order of $\underline{\omega}(t_n)$, $\overline{\omega}(t_n)$, and these are in the order of $\sqrt{2\log n / \delta_n}$, with $\delta_n = \delta/(n(n+1))$, which is dominated by $\gamma^n$.
 \end{proof}
@@
 \subsection{Obstacle Avoidance}
+
+\paragraph{States}
+\paragraph{Actions}
+\paragraph{Reward}
+\paragraph{Dynamics}
 

### 2020-05-25 main.tex
Remarks from Denis, bis
Conflict merge with overleaf basically wiped my changes... why?

@@
 We develop a framework for the adaptive model predictive control (MPC) of a linear system with unknown parameters, in a critical setting where failures are costly and should be prevented at all time.
-Through the careful selection and non-trivial adaptation of tools from different communities --namely linear regression, interval prediction and tree-based planning--, we provide an integrated solution to the problem of maximin control with arbitrary bounded costs.
-We ensured that theoretical guarantees at each layer could be combined to provide what we believe is the first end-to-end analysis in this general setting.
-The full procedure is designed to produce reasonable and safe behaviours at deployment while progressively recovering an asymptotic optimality.
+Through the careful selection and non-trivial combination of tools from different communities --namely linear regression, interval prediction and tree-based planning--, we provide an integrated solution to the problem of maximin control with arbitrary bounded costs.
+We ensure that theoretical guarantees at each layer could be combined to provide what we believe is the first end-to-end analysis in this general setting.
+The full procedure is designed to produce reasonable and safe behaviours, which progressively recover an asymptotic optimality.
 Finally, we relax our modelling assumptions in a multi-model extension based on a data-driven robust model selection mechanism.
@@
 Since experiencing failures is out of question, the only way to prevent them from the outset, when the system is first deployed, is to rely on some sort of prior knowledge.
-In this work, we assume that the system dynamics are partially known, in the form of a parametrized dynamical system with unknown parameters.
+In this work, we assume that the system dynamics are partially known, in the form of a linear differential equation with unknown parameters and inputs.
 More precisely, we consider a linear system with state $x\in\Real^p$, acted on by controls $u\in\Real^q$ and perturbations $\omega\in\Real^r$, and following dynamics in the form:
@@
 \label{eq:dynamics}
-\dot{x}(t)=A(\theta)x(t) + B u(t) + D \omega(t),\;t\geq0.
-\end{equation}
-It is assumed that the parameter vector $\theta$ in the state matrix $A(\theta)\in\Real^{p\times p}$ belongs to a compact set $\Theta \subset \Real^d$.
+\dot{x}(t)=A(\theta)x(t) + B u(t) + D \omega(t),\;t\geq0,
+\end{equation}
+where the parameter vector $\theta$ in the state matrix $A(\theta)\in\Real^{p\times p}$ belongs to a compact set $\Theta \subset \Real^d$.
 The control matrix $B\in\Real^{p\times q}$ and disturbance matrix $D\in\Real^{p\times r}$ are known.
@@
 \end{equation}
-$\gamma\in(0,1)$ is a discount factor, and $x_n(\bu,\bom)$ is the state reached at step $n$ under controls $\bu$ and perturbations $\bom$.
-Maximin problems such as $\eqref{eq:robust-control}$ are notoriously hard in cases such where the reward $R$ has a simple form.
+$\gamma\in(0,1)$ is a discount factor, and $x_n(\bu,\bom)$ is the state reached at step $n$ under controls $\bu$ and perturbations $\bom$ within the given admissible bounds $[\underline\omega(t),\overline\omega(t)]$.
+Maximin problems such as $\eqref{eq:robust-control}$ are notoriously hard if the reward $R$ has a simple form.
 With arbitrary functions $R$, we cannot hope to derive an explicit solution.
@@
 In \Cref{sec:prediction}, we leverage recent results from the uncertain system simulation literature to derive an \emph{interval predictor} $[\underline{x}(t),\overline{x}(t)]$ for the system \eqref{eq:dynamics}, illustrated in \Cref{fig:prediction}.
-This predictor takes the information on the observed current state ${x}_N$, the confidence region $\cC_\delta$, planned control sequence $\bu$ and some admissible bounds on the perturbation $[\underline{\omega}(t),\overline{\omega}(t)]$; and must verify the \emph{inclusion property}:
+This predictor takes the information on the observed current state ${x}_N$, the confidence region $\cC_\delta$, planned control sequence $\bu$ and admissible perturbation bounds $[\underline{\omega}(t),\overline{\omega}(t)]$; and must verify the \emph{inclusion property}:
 \begin{equation}
@@
 In the \emph{Optimism in the Face of Uncertainty} paradigm, the best possible dynamics within a high-confidence region is selected under a controllability constraint, to compute the corresponding optimal control in closed-form by solving a Riccati equation.
-\citep{abbasi-yadkori11a,Ibrahimi2013,Faradonbeh2017} show that this procedures achieves a $\tilde{\cO}\left(N^{1/2}\right)$ regret.
-Posterior sampling algorithms \citep{Ouyang2017,abeille18a} sample candidate dynamics randomly instead, and obtain the same result.
+\citep{abbasi-yadkori11a,Ibrahimi2013,Faradonbeh2017} show that this procedure achieves a $\tilde{\cO}\left(N^{1/2}\right)$ regret.
+Posterior sampling algorithms \citep{Ouyang2017,abeille18a} select candidate dynamics randomly instead, and obtain the same result.
 Other works use noise injection for exploration such as \citep{Dean2017,Dean2018}.
@@
     \label{eq:polytope}
-     \cC_{[N],\delta} = \left\{ A + \theta_{N,\lambda}^\transp\phi +\sum_{i=1}^{2^d}\alpha_{i}\Delta A_{i}: \alpha\geq 0,  \sum_{i=1}^{2^d}\alpha_{i}=1\right\} \text{ where } h_i\in\{-1,1\}^d,
+     \cC_{[N],\delta} = \left\{ A_0 +\sum_{i=1}^{2^d}\alpha_{i}\Delta A_{i}: \alpha\geq 0,  \sum_{i=1}^{2^d}\alpha_{i}=1\right\} \text{ where } A_0 = A + \theta_{N,\lambda}^\transp\phi,\; h_i\in\{-1,1\}^d,
 \end{align}
@@
 \end{eqnarray}
-ensures the inclusion property \eqref{eq:inclusion-property} with confidence level $\delta$..
+ensures the inclusion property \eqref{eq:inclusion-property} with confidence level $\delta$.
 \end{proposition}
@@
 
-\Cref{fig:predictor_example} compares the stability of the predictors \eqref{eq:predictor-naive} and \eqref{eq:interval-predictor} in a simple example.
+\Cref{fig:predictor_example} compares the performance of the predictors \eqref{eq:predictor-naive} and \eqref{eq:interval-predictor} in a simple example.
 It suggests to always prefer \eqref{eq:interval-predictor} whenever \Cref{assumpt:metzler} is verified, and only fallback to \eqref{eq:predictor-naive} as a last resort.
@@
 \end{definition}
-This amounts to changing the reward function, except that the worst case is assessed over the whole past trajectory, which makes this pessimistic reward $\underline{R_n}$ \emph{not Markovian}.
+Such a substitution makes this pessimistic reward $\underline{R_n}$ \emph{not Markovian}, since the worst case is assessed over the whole past trajectory.
 
@@
 We adapt our planning algorithm to balance these concurrent hypotheses in a robust fashion, i.e. maximise a robust objective with discrete ambiguity:
-$
-%\label{eq:robust-objective-discrete}
-V^r = \sup_{a\in\cA^\Natural}\min_{m\in[M]} \sum_{n=N+1}^\infty \gamma^n R_n^m, \refstepcounter{equation}\hfill(\theequation)\label{eq:robust-objective-discrete}
-$
+\begin{equation}
+\label{eq:robust-objective-discrete}
+V^r = \sup_{a\in\cA^\Natural}\min_{m\in[M]} \sum_{n=N+1}^\infty \gamma^n R_n^m, 
+%\refstepcounter{equation}\hfill(\theequation)\label{eq:robust-objective-discrete}
+\end{equation}
 where $R_n^m$ is the reward obtained by following the action sequence $a$ up to step $n$ under the dynamics $f^m$.
@@
 
-The motivation behind this work is to enable the development of Reinforcement Learning solutions for industrial applications, when it has hitherto been mainly limited to simulated games.
+The motivation behind this work is to enable the development of Reinforcement Learning solutions for industrial applications, when it has been mainly limited to simulated games so far.
 In particular, many industries already rely on non-adaptive control systems and could benefit from an increased efficiency, including Oil and Gas, robotics for industrial automation, Data Center cooling, etc.

### 2020-05-25 main.tex
More compression -> 8  pages

@@
 In \Cref{sec:prediction}, we leverage recent results from the uncertain system simulation literature to derive an \emph{interval predictor} $[\underline{x}(t),\overline{x}(t)]$ for the system \eqref{eq:dynamics}, illustrated in \Cref{fig:prediction}.
-This predictor takes the information on the observed current state ${x}_N$, the confidence region $\cC_\delta$, planned control sequence $\bu$ and admissible perturbation bounds $[\underline{\omega}(t),\overline{\omega}(t)]$; and must verify the \emph{inclusion property}:
+This predictor takes the information on the current state ${x}_N$, the confidence region $\cC_\delta$, planned control sequence $\bu$ and admissible perturbation bounds $[\underline{\omega}(t),\overline{\omega}(t)]$; and must verify the \emph{inclusion property}:
 \begin{equation}
@@
 Under three conditions:
-\begin{enumerate}
+\begin{enumerate}[nosep]
 	\item a Lipschitz regularity assumption for the reward $R$;
@@
 
-\paragraph{Model adequacy}
-
+\textbf{Model adequacy}~~~
 One of the major benefits of using the family of linear models, compared to richer model classes, is that they provide strict conditions allowing to quantify the adequacy of the modelling assumptions to the observations.
@@
 
-\paragraph{Robust selection}
-
+\textbf{Robust selection}~~~
 We temporarily ignore the parametric uncertainty on $\theta$ to simply consider several candidate dynamics models, which all correspond to different modelling assumptions.
@@
 
-\paragraph{Obstacle avoidance with unknown friction}
+\textbf{Obstacle avoidance with unknown friction}~~~
 We first consider a simple illustrative example, shown in \Cref{fig:prediction}: the control of a 2D system %with position $(p_x,p_y)$ and velocity $(v_x, v_y)$ 
@@
 
-%\begin{figure}[tp]
-%	\centering
-%	\includegraphics[width=0.3\linewidth]{img/regret.pdf}
-%	\caption{The mean regret along with its $95\%$ confidence interval with respect to $N$, for the robust and nominal agents.}
-%	\label{fig:regret}
-%\end{figure}
-%\begin{figure}[t]
-%	\centering
-%	\includegraphics[width=0.4\linewidth]{img/highway-small}
-%	\caption{The intersection crossing task. We show the trajectory intervals corresponding to behavioural uncertainty for each observed vehicle, and the multi-model assumption over the followed route.}
-%\end{figure}
 \begin{figure}[!tbp]
@@
 \begin{table}[tbp]
-%	\caption{Performances on the obstacle avoidance task}
-%	\label{tab:obstacle}
-%	\centering
-%	\begin{tabular}{lccc}
-%		\toprule
-%		Agent &
-%		failures &
-%		min return &
-%		mean return $\pm$ std  \\
-%		\midrule
-%		Oracle & 0\% & {11.6} & {$14.2 \pm 1.3$} \\
-%		\midrule
-%		{Nominal} & {4\%} & {2.8} & \textbf{$\mathbf{13.8} \pm 2.0$} \\
-%		\Cref{alg:full} & \textbf{0\%} & \textbf{10.4} & {$13.0 \pm 1.5$} \\
-%		\bottomrule
-%	\end{tabular}
 
@@
 
-\paragraph{Behavioural planning for an autonomous vehicle}
+\textbf{Behavioural planning for an autonomous vehicle}~~~
 We consider the \href{https://github.com/eleurent/highway-env}{highway-env} environment \citep{highway-env} for simulated driving decision problems.
@@
 \citep{Dean2018,abeille18a} reported numerical experiments with states of dimensions 3 and 4, respectively.
-The system dynamics $f$, which describes the couplings and interactions between vehicles, can only be expressed in the form of \Cref{assumpt:structure} given the knowledge of the desired route for each vehicle, with features $\phi$ expressing deviations to the centerline of the followed lane.
+The system dynamics $f$, which describes the interactions between vehicles, can only be expressed in the form of \Cref{assumpt:structure} given the knowledge of the desired route for each vehicle, with features $\phi$ expressing deviations to the centerline of the followed lane.
 Since these intentions are unknown to the agent, we adopt the multi-model perspective of \Cref{sec:multi-model} and consider one model per possible route for every observed vehicle before an intersection.
-We compare \Cref{alg:full} to a nominal agent planning with the estimated parameter $\theta_{[N],\lambda}$, with two different modelling assumptions: we assume that Nominal 1 has access to the true followed route for each vehicle, while Nominal 2 does not and picks the model with minimal prediction error.
-Their performances are compared in \Cref{tab:driving}.
+In \Cref{tab:driving}, we compare \Cref{alg:full} to a nominal agent planning with the estimated parameter $\theta_{[N],\lambda}$, with two different modelling assumptions: we assume that Nominal 1 has access to the true followed route for each vehicle, while Nominal 2 does not and picks the model with minimal prediction error.
 Again, the robust approach is less efficient on average than planning with a nominal model, but it does better in terms of worst-case performance and manages to avoid collisions, contrary to the nominal baselines that suffer from model bias.

### 2020-05-25 main.tex
Last remark from Denis

@@
 In particular, many industries already rely on non-adaptive control systems and could benefit from an increased efficiency, including Oil and Gas, robotics for industrial automation, Data Center cooling, etc.
-But more often than not, safety-critical constraints bar the use of exploration, and industrials are reluctant to turn to learning-based methods that lack accountability.
+But more often than not, safety-critical constraints proscribe the use of exploration, and industrials are reluctant to turn to learning-based methods that lack accountability.
 This work addresses these concerns by focusing on risk-averse decisions and by providing worst-case guarantees.

### 2020-05-25 main.tex
Minor wording

@@
 obstacle avoidance) and are better addressed in our setting of maximising an arbitrary utility function, where no prior result exists to our knowledge.
-Other safety frameworks exist such as constraining the state $x$ in a safe region $\mathbb{X}$ often chosen convex \citep[e.g.][]{Turchetta2016}, which again is not suitable for many tasks (e.g.
+Other safety frameworks exist, such as constraining the state $x$ in a given region $\mathbb{X}$ often chosen convex \citep[e.g.][]{Turchetta2016}, which again is not suitable for many tasks (e.g.
 these of \Cref{sec:experiments}).

### 2020-05-27 main.tex
Few words about assumptions in experiments

@@
 Through the careful selection and non-trivial combination of tools from different communities --namely linear regression, interval prediction and tree-based planning--, we provide an integrated solution to the problem of maximin control with arbitrary bounded costs.
-We ensure that theoretical guarantees at each layer could be combined to provide what we believe is the first end-to-end analysis in this general setting.
+We ensure that theoretical guarantees at each layer can be combined to provide what we believe is the first end-to-end analysis in this general setting.
 The full procedure is designed to produce reasonable and safe behaviours, which progressively recover an asymptotic optimality.
@@
 %$
-The reward is non-smooth and encodes the task of navigating to reach a goal state $x_g$ while avoiding collisions with obstacles: $R(x) = \delta(x)/(1 + \|x - x_g\|_2)$  where $\delta(x)$ is $0$ whenever $x$ collides with an obstacle, $1$ otherwise.
+The reward encodes the task of navigating to reach a goal state $x_g$ while avoiding collisions with obstacles: $R(x) = \delta(x)/(1 + \|x - x_g\|_2)$  where $\delta(x)$ is $0$ whenever $x$ collides with an obstacle, $1$ otherwise.
 The actions $\cA$ are constant controls in the up, down, left and right directions.
@@
 The results of 100 simulations are shown in \Cref{tab:obstacle}: the robust agent performs worse than the nominal agent on average, but manages to ensure safety and attains a better worst-case performance.
-We also study the evolution of the simple regret $V(x_n) - J_n(x_n)$ with respect to the number of samples $N$, where $J_n(x_n) = \sum_{i > n} \gamma^i R_i$ is the empirical return from state $x_n$, while $V(x_n)$ is the optimal value that the agent would get by acting optimally from $x_n$ with knowledge of the dynamics.
-The mean regret $\hat{V}^r - V$, shown in \Cref{fig:regret} with its 95\% confidence interval, decreases polynomially with $N$ as expected from \Cref{thm:control-error}.
-Thus, \Cref{alg:full} gets more aggressive as it is more confident, while ensuring safety at all time.
-In contrast, the nominal agent has an even smaller regret but collided with obstacles in $4\%$ of simulations.
+We also study the evolution of the simple regret $V(x_N) - \hat{V}^r(x_N)$ with respect to the number of samples $N$, by comparing the empirical returns from a state $x_N$ to the value $V(x_N)$ that the agent would get by acting optimally from $x_N$ with knowledge of the dynamics.
+Although the assumptions of \Cref{thm:control-error} are not satisfied (e.g.
+non-smooth reward), the mean regret of the robust agent, shown in \Cref{fig:regret}, still decreases polynomially with $N$: \Cref{alg:full} gets more efficient as it is more confident while ensuring safety at all time.
+In contrast, the nominal agent has a smaller average regret but collides with obstacles in $4\%$ of simulations.
 
@@
 
-\textbf{Behavioural planning for an autonomous vehicle}~~~
+\textbf{Motion planning for an autonomous vehicle}~~~
 We consider the \href{https://github.com/eleurent/highway-env}{highway-env} environment \citep{highway-env} for simulated driving decision problems.

### 2020-05-27 main.tex
Update code readme

@@
 \Cref{sec:attachments} describes the attached video files and source code.
+\Cref{sec:experimental-setting} provides additional details on our experiments.
 \Cref{sec:tight-polytope} gives a better method of conversion from ellipsoid to polytope than that of \eqref{eq:polytope}.
-\Cref{sec:min-max-order} highlights the fact that robustness cannot be recovered by aggregating independent solutions to many optimal control problem.
-Finally, \Cref{sec:experimental-setting} provides additional details on our experiments.
+Finally, \Cref{sec:min-max-order} highlights the fact that robustness cannot be recovered by aggregating independent solutions to many optimal control problem.
 
@@
 \paragraph{Source code}
-The attached \texttt{code} directory contains an implementation of \Cref{alg:full}. We relate the algorithmic steps of this paper to their location in the source code.
-\begin{enumerate}
-	\item The confidence ellipsoid \eqref{eq:confidence-ellipsoid} is implemented in the \texttt{ellipsoid()} method in \url{code/rl_agents/agents/tree_search/robust_epc.py}
-	\item The corresponding polytope \eqref{eq:polytope} is implemented in the \texttt{polytope()} method of \url{code/rl_agents/agents/tree_search/robust_epc.py}
-	\item The simple predictor of \eqref{eq:predictor-naive} is implemented in the \texttt{step\_simple\_predictor()} method of \url{code/rl_agents/agents/common/interval.py}
-	\item The enhanced predictor of \eqref{eq:interval-predictor} is implemented in the \texttt{step\_interval\_predictor()} method of \url{code/rl_agents/agents/common/interval.py}
-	\item The pessimistic reward of \eqref{eq:surrogate-objective} is implemented in the \texttt{pessimistic\_reward()} method of \url{code/obstacle_env/envs/obstacle.py} and the \texttt{check\_collision()} method of \url{code/highway_env/vehicle/uncertainty/prediction.py}
-	\item The robust upper-bound of \eqref{eq:robust-b-values} is implemented in the \texttt{RobustNode} class of \url{code/rl_agents/agents/tree_search/robust.py}
-\end{enumerate}
-The experiments can be reproduced by running:
-\lstset{language=bash}
-\begin{lstlisting}
-cd scripts
-python experiments.py configs/<env>/env.json configs/<env>/agents/<agent>.json
-\end{lstlisting}
-
-\section{A tighter conversion from ellipsoid to polytope}
-\label{sec:tight-polytope}
-\begin{lemma}[Confidence polytope]
-	\label{lem:tight_polytope}
-	We can enclose the confidence ellipsoid obtained in $\eqref{eq:confidence-ellipsoid}$ within a polytope $C_\delta$:
-	\begin{equation}
-	\cC_\delta = \left\{ A_{1}+\sum_{i=1}^{2^d}\lambda_{i}\Delta A_{i}: \lambda\in[0, 1]^{2^d},  \sum_{i=1}^{2^d}\lambda_{i}=1\right\}.
-	\end{equation}
-	with 
-	\begin{align*}
-	&h_k \text{ is the }k^\text{th}\text{ element of }\{-1,1\}^d\text{ for } k\in[2^d],\\
-	&G_{N,\lambda} = PDP^{-1}, \quad \Delta\theta_k = \beta_{N}(\delta)P^{-1}D^{-1/2} h_k, \\
-	&A_0 = A + \theta_{N,\lambda}^\transp\Phi, \quad \Delta A_k = \Delta\theta_k^\transp\Phi.
-	\end{align*}
-	This conversion is illustrated in \Cref{fig:ellipsoid_to_polytope}.
-\end{lemma}
-
-\begin{proof}
-	The ellipsoid in \eqref{eq:confidence-ellipsoid} is described by:
-	\begin{align*}
-	\theta\in\cC_\delta &\implies
-	(\theta-\theta_{N,\lambda})^\transp G_{N,\lambda}(\theta-\theta_{N,\lambda}) \leq \beta_{N}(\delta)^2\\
-	&\implies (\theta'-\theta'_{N,\lambda})^\transp D (\theta'-\theta'_{N,\lambda}) \leq \beta_{N}(\delta)^2\\
-	&\implies \sum_{i=1}^d D_{i,i}(\theta'_i-\theta'_{N,\lambda,i})^2\leq \beta_{N}(\delta)^2\\
-	&\implies\forall i, |\theta'_i-\theta'_{N,\lambda,i}|\leq D_{i,i}^{-1/2}\beta_{N}(\delta)
-	\end{align*}
-	This describes a $\Real^d$ box containing $\theta' = P\theta$, whose $k^\text{th}$ vertex is represented by $\theta_{N,\lambda}' + \beta_{N}(\delta)D^{-1/2} h_k$.
-We obtain the corresponding box on $\theta$ by transforming each vertex of the box with $P^{-1}$.
-\end{proof}
-
-\begin{figure}
-	\centering
-	\includegraphics[trim={3.8cm, 2cm, 5cm, 3.8cm}, clip, width=0.7\linewidth]{img/ellipsoid_to_polytope}
-	\caption{From the confidence ellipsoid $\cC_\delta$ to its enclosing polytope $\cP_\delta$}
-	\label{fig:ellipsoid_to_polytope}
-\end{figure}
-
-\section{On the ordering of min and max}
-	\label{sec:min-max-order}
-
-	In the definition of $B_{a}^{r}(k)$ \eqref{eq:br} and $U_{a}^{r}(k)$ \eqref{eq:ur} it is essential that the minimum over the models is only taken at the end of trajectories, in the same way as for the robust objective \eqref{eq:robust-objective-discrete} in which the worst-case dynamics is only determined after the action sequence has been fully specified.
-Assume that $U_{a}^{r}(k)$ is instead naively defined as:
-
-	\[
-	U_{a}^{r}(k)=\min_{m\in[1,M]}U_{a}^{m}(k),
-	\]
-
-	This would not recover the robust policy, as we show in \Cref{fig:min-max-order} with a simple counter-example.
-	\begin{figure}[htp]
-		\centering
-		\includegraphics[width=\linewidth]{img/min-max-order}
-		\caption{From left to right: two simple models and corresponding u-values with optimal sequences in blue; the naive version of the robust values returns sub-optimal paths in red; our robust U-value properly recovers the robust policy in green.}
-		\label{fig:min-max-order}
-	\end{figure}
+The attached \texttt{code} directory contains an implementation of \Cref{alg:full}.
+The \texttt{README.md} file relates the algorithmic steps of this paper to their location in the source code, and contains instructions to reproduce our experimental results.
 
@@
 \paragraph{States}
+
 \paragraph{Actions}
@@
 \paragraph{Dynamics}
+
+$
+\begin{bmatrix}
+\dot{p_x}\\
+\dot{p_y}\\
+\dot{v_x}\\
+\dot{v_y}\\
+\end{bmatrix} = 
+\begin{bmatrix}
+0 & 0 & 1 & 0 \\
+0 & 0 & 0 & 1 \\
+0 & 0 & -\theta_x & 0 \\
+0 & 0 & 0 & -\theta_y
+\end{bmatrix}
+\begin{bmatrix}
+{p_x}\\
+{p_y}\\
+{v_x}\\
+{v_y}\\
+\end{bmatrix}
++
+\begin{bmatrix}
+0\\
+0\\
+{u_x}\\
+{u_y}\\
+\end{bmatrix}.
+$
 
@@
 
+\section{A tighter conversion from ellipsoid to polytope}
+\label{sec:tight-polytope}
+\begin{lemma}[Confidence polytope]
+	\label{lem:tight_polytope}
+	We can enclose the confidence ellipsoid obtained in $\eqref{eq:confidence-ellipsoid}$ within a polytope $C_\delta$:
+	\begin{equation}
+	\cC_\delta = \left\{ A_{1}+\sum_{i=1}^{2^d}\lambda_{i}\Delta A_{i}: \lambda\in[0, 1]^{2^d},  \sum_{i=1}^{2^d}\lambda_{i}=1\right\}.
+	\end{equation}
+	with 
+	\begin{align*}
+	&h_k \text{ is the }k^\text{th}\text{ element of }\{-1,1\}^d\text{ for } k\in[2^d],\\
+	&G_{N,\lambda} = PDP^{-1}, \quad \Delta\theta_k = \beta_{N}(\delta)P^{-1}D^{-1/2} h_k, \\
+	&A_0 = A + \theta_{N,\lambda}^\transp\Phi, \quad \Delta A_k = \Delta\theta_k^\transp\Phi.
+	\end{align*}
+	This conversion is illustrated in \Cref{fig:ellipsoid_to_polytope}.
+\end{lemma}
+
+\begin{proof}
+	The ellipsoid in \eqref{eq:confidence-ellipsoid} is described by:
+	\begin{align*}
+	\theta\in\cC_\delta &\implies
+	(\theta-\theta_{N,\lambda})^\transp G_{N,\lambda}(\theta-\theta_{N,\lambda}) \leq \beta_{N}(\delta)^2\\
+	&\implies (\theta'-\theta'_{N,\lambda})^\transp D (\theta'-\theta'_{N,\lambda}) \leq \beta_{N}(\delta)^2\\
+	&\implies \sum_{i=1}^d D_{i,i}(\theta'_i-\theta'_{N,\lambda,i})^2\leq \beta_{N}(\delta)^2\\
+	&\implies\forall i, |\theta'_i-\theta'_{N,\lambda,i}|\leq D_{i,i}^{-1/2}\beta_{N}(\delta)
+	\end{align*}
+	This describes a $\Real^d$ box containing $\theta' = P\theta$, whose $k^\text{th}$ vertex is represented by $\theta_{N,\lambda}' + \beta_{N}(\delta)D^{-1/2} h_k$.
+We obtain the corresponding box on $\theta$ by transforming each vertex of the box with $P^{-1}$.
+\end{proof}
+
+\begin{figure}
+	\centering
+	\includegraphics[trim={3.8cm, 2cm, 5cm, 3.8cm}, clip, width=0.7\linewidth]{img/ellipsoid_to_polytope}
+	\caption{From the confidence ellipsoid $\cC_\delta$ to its enclosing polytope $\cP_\delta$}
+	\label{fig:ellipsoid_to_polytope}
+\end{figure}
+
+\section{On the ordering of min and max}
+	\label{sec:min-max-order}
+
+	In the definition of $B_{a}^{r}(k)$ \eqref{eq:br} and $U_{a}^{r}(k)$ \eqref{eq:ur} it is essential that the minimum over the models is only taken at the end of trajectories, in the same way as for the robust objective \eqref{eq:robust-objective-discrete} in which the worst-case dynamics is only determined after the action sequence has been fully specified.
+Assume that $U_{a}^{r}(k)$ is instead naively defined as:
+
+	\[
+	U_{a}^{r}(k)=\min_{m\in[1,M]}U_{a}^{m}(k),
+	\]
+
+	This would not recover the robust policy, as we show in \Cref{fig:min-max-order} with a simple counter-example.
+	\begin{figure}[htp]
+		\centering
+		\includegraphics[width=\linewidth]{img/min-max-order}
+		\caption{From left to right: two simple models and corresponding u-values with optimal sequences in blue; the naive version of the robust values returns sub-optimal paths in red; our robust U-value properly recovers the robust policy in green.}
+		\label{fig:min-max-order}
+	\end{figure}
+
 \end{document}

### 2020-05-27 main.tex
Edit abstract
Updates from Overleaf

@@
 
-\title{Interval-based Robust Control of Linear Systems with Generic Costs}
+\title{Interval-based Robust-Adaptive Control of Linear Systems with Generic Costs}
 
@@
 \begin{abstract}
-We develop a framework for the adaptive model predictive control (MPC) of a linear system with unknown parameters, in a critical setting where failures are costly and should be prevented at all time.
-Through the careful selection and non-trivial combination of tools from different communities --namely linear regression, interval prediction and tree-based planning--, we provide an integrated solution to the problem of maximin control with arbitrary bounded costs.
-We ensure that theoretical guarantees at each layer can be combined to provide what we believe is the first end-to-end analysis in this general setting.
-The full procedure is designed to produce reasonable and safe behaviours, which progressively recover an asymptotic optimality.
+We develop a framework for the robust adaptive model predictive control (MPC) of a linear system with unknown parameters, in a critical setting where failures are costly and should be prevented at all time.
+So far, this problem has been studied in the case of quadratic costs --known as the LQ problem--, which limits applications to stabilisation tasks.
+In this paper, we extend this setting to consider arbitrary bounded costs, including non-convex and potentially non-smooth costs that arise in many practical problems.
+To this end, we carefully select and bring together several tools from different communities, namely linear regression, recent results in interval prediction, and tree-based planning.
+Thanks to the non-trivial combination of theoretical guarantees at each layer, we provide the first end-to-end regret analysis in this setting.
+The full procedure is designed to produce safe behaviours which progressively recover an asymptotic optimality.
 Finally, we relax our modelling assumptions in a multi-model extension based on a data-driven robust model selection mechanism.

### 2020-05-27 main.tex
Update abstract

@@
 \begin{abstract}
-We develop a framework for the robust adaptive model predictive control (MPC) of a linear system with unknown parameters, in a critical setting where failures are costly and should be prevented at all time.
-So far, this problem has been studied in the case of quadratic costs --known as the LQ problem--, which limits applications to stabilisation tasks.
-In this paper, we extend this setting to consider arbitrary bounded costs, including non-convex and potentially non-smooth costs that arise in many practical problems.
+We develop a framework for the robust adaptive model predictive control (MPC) of a linear system with unknown parameters, in a critical setting where failures are costly.
+So far, this problem has been studied in the case of quadratic costs --the LQ problem--, which limits applications to stabilisation tasks.
+In this paper, we extend this setting to consider arbitrary bounded costs, including non-convex, that arise in many practical problems.
 To this end, we carefully select and bring together several tools from different communities, namely linear regression, recent results in interval prediction, and tree-based planning.
 Thanks to the non-trivial combination of theoretical guarantees at each layer, we provide the first end-to-end regret analysis in this setting.
-The full procedure is designed to produce safe behaviours which progressively recover an asymptotic optimality.
 Finally, we relax our modelling assumptions in a multi-model extension based on a data-driven robust model selection mechanism.
-In addition to our theoretical results we strived to preserve tractable computations for practical applicability, as we illustrate on a simulated application of autonomous driving at a crossroads intersection.\footnote{Source code and videos are available in the Supplementary Material.}
+In addition to our theoretical results we strived to preserve tractable computations for practical applicability, as we illustrate on a two simulated applications.\footnote{Source code and videos are available in the Supplementary Material.}
 \end{abstract}

### 2020-05-27 main.tex
Update title and abstract

@@
 
-\title{Interval-based Robust-Adaptive Control of Linear Systems with Generic Costs}
+\title{Robust-Adaptive Control of Linear Systems: beyond Quadratic Costs}
 
@@
 \begin{abstract}
-We develop a framework for the robust adaptive model predictive control (MPC) of a linear system with unknown parameters, in a critical setting where failures are costly.
+%We develop a framework for the robust adaptive model predictive control (MPC) of a linear system with unknown parameters, in a critical setting where failures are costly.
 So far, this problem has been studied in the case of quadratic costs --the LQ problem--, which limits applications to stabilisation tasks.
@@
 Finally, we relax our modelling assumptions in a multi-model extension based on a data-driven robust model selection mechanism.
-In addition to our theoretical results we strived to preserve tractable computations for practical applicability, as we illustrate on a two simulated applications.\footnote{Source code and videos are available in the Supplementary Material.}
+In addition to our theoretical results we strived to preserve tractable computations for practical applicability, as we illustrate on a two simulated applications.
+We consider the problem of robust and adaptive model predictive control (MPC) of a linear system, with unknown parameters that are learned on the way (adaptive), in a critical setting where failures are costly (robust).
+This problem has been studied from different perspectives by different communities.
+However, only the case of quadratic costs --the LQ problem-- has been considered, which limits applications to stabilisation tasks.
+In order to handle more general (bounded, non-convex) costs that naturally arise in many practical problems,
+we carefully select and bring together several tools from different communities, namely non-asymptotic linear regression, recent results in interval prediction, and tree-based planning. 
+Combining and adapting the theoretical guarantees at each layer is non trivial, and we provide the first end-to-end regret analysis for this setting.  
+Interestingly, our analysis naturally adapts to handle many models and combines with a data-driven robust model selection strategy, which enables to relax the modelling assumptions.
+Last, we strive to preserve tractability at any stage of the method, that we illustrate on two challenging simulated environments.\footnote{Source code and videos are available in the Supplementary Material.}
 \end{abstract}

### 2020-05-27 main.tex
Updates from Overleaf

@@
 
-\title{Robust-Adaptive Control of Linear Systems: beyond Quadratic Costs}
+\title{Robust-Adaptive Control of Linear Systems:\\ beyond Quadratic Costs}
 
@@
 \begin{abstract}
-%We develop a framework for the robust adaptive model predictive control (MPC) of a linear system with unknown parameters, in a critical setting where failures are costly.
-So far, this problem has been studied in the case of quadratic costs --the LQ problem--, which limits applications to stabilisation tasks.
-In this paper, we extend this setting to consider arbitrary bounded costs, including non-convex, that arise in many practical problems.
-To this end, we carefully select and bring together several tools from different communities, namely linear regression, recent results in interval prediction, and tree-based planning.
-Thanks to the non-trivial combination of theoretical guarantees at each layer, we provide the first end-to-end regret analysis in this setting.
-Finally, we relax our modelling assumptions in a multi-model extension based on a data-driven robust model selection mechanism.
-In addition to our theoretical results we strived to preserve tractable computations for practical applicability, as we illustrate on a two simulated applications.
 We consider the problem of robust and adaptive model predictive control (MPC) of a linear system, with unknown parameters that are learned on the way (adaptive), in a critical setting where failures are costly (robust).
 This problem has been studied from different perspectives by different communities.
-However, only the case of quadratic costs --the LQ problem-- has been considered, which limits applications to stabilisation tasks.
+However, only the case of quadratic costs --the LQ problem-- has been considered, which limits applications to stabilisation tasks only.
 In order to handle more general (bounded, non-convex) costs that naturally arise in many practical problems,

### 2020-05-27 main.tex
Updates from Overleaf

@@
 \begin{abstract}
-We consider the problem of robust and adaptive model predictive control (MPC) of a linear system, with unknown parameters that are learned on the way (adaptive), in a critical setting where failures are costly (robust).
+We consider the problem of robust and adaptive model predictive control (MPC) of a linear system, with unknown parameters that are learned along the way (adaptive), in a critical setting where failures must be prevented (robust).
 This problem has been studied from different perspectives by different communities.
 However, only the case of quadratic costs --the LQ problem-- has been considered, which limits applications to stabilisation tasks only.
-In order to handle more general (bounded, non-convex) costs that naturally arise in many practical problems,
-we carefully select and bring together several tools from different communities, namely non-asymptotic linear regression, recent results in interval prediction, and tree-based planning. 
+In order to handle more general (bounded, non-convex) costs that naturally arise in many practical problems, we carefully select and bring together several tools from different communities, namely non-asymptotic linear regression, recent results in interval prediction, and tree-based planning.
 Combining and adapting the theoretical guarantees at each layer is non trivial, and we provide the first end-to-end regret analysis for this setting.

### 2020-05-27 main.tex
Update intro -> 8 pages

@@
 
-Despite the recent successes of Reinforcement Learning in cracking many hard problems \citep[e.g.][]{mnih2015humanlevel,Silver1140}, this tool has hardly been applied in real industrial issues.
+Despite the recent successes of Reinforcement Learning \citep[e.g.][]{mnih2015humanlevel,Silver1140}, it has hardly been applied in real industrial issues.
 This could be attributed to two undesirable properties which limit its practical applications.
@@
 This choice of rich reward space is crucial to have sufficient flexibility to model non-convex and non-smooth functions that naturally arise in many practical problems involving combinatorial optimisation, branching decisions, etc., while quadratic costs are mostly suited for tracking a fixed reference trajectory \citep[e.g.][]{Kumar2013}.
-
-Since experiencing failures is out of question, the only way to prevent them from the outset, when the system is first deployed, is to rely on some sort of prior knowledge.
+Since experiencing failures is out of question, the only way to prevent them from the outset is to rely on some sort of prior knowledge.
 In this work, we assume that the system dynamics are partially known, in the form of a linear differential equation with unknown parameters and inputs.

### 2020-05-28 main.tex
Use wording of trajectory tracking rather than stabilisation

@@
 This problem has been studied from different perspectives by different communities.
-However, only the case of quadratic costs --the LQ problem-- has been considered, which limits applications to stabilisation tasks only.
+However, only the case of quadratic costs --the LQ problem-- has been considered, which limits applications to tracking a fixed reference trajectory only.
 In order to handle more general (bounded, non-convex) costs that naturally arise in many practical problems, we carefully select and bring together several tools from different communities, namely non-asymptotic linear regression, recent results in interval prediction, and tree-based planning.
@@
 
-While there exists a vast body of literature on the control of uncertain systems, its majority is only concerned with the problem of stabilisation at an equilibrium, including $\cH_\infty$ control \citep[see, e.g.][]{Basar1996}, sliding-mode control \citep{Lu1997}, tube-MPC \citep{Limon2010} or system-level synthesis \citep{Dean2017,Dean2018}.
+While there exists a vast body of literature on the control of uncertain systems, its majority is only concerned with the problem of stabilisation around a fixed reference state or trajectory, including $\cH_\infty$ control \citep[see, e.g.][]{Basar1996}, sliding-mode control \citep{Lu1997}, tube-MPC \citep{Limon2010} or system-level synthesis \citep{Dean2017,Dean2018}.
 Yet, we argue that many tasks cannot be framed as stabilisation problems (e.g.

### 2020-05-28 main.tex
Experimental details

@@
 In both experiments, we used $\gamma=0.9$,  $\delta=0.9$ and a planning budget $K=100$.
-The perturbations were sampled uniformly in $[-0.1, 0.1]^r$ while the measurements are Gaussian with covariance $\Sigma_r = 0.1 I_s$.
+The perturbations were sampled uniformly in $[-0.1, 0.1]^r$ while the measurements are Gaussian with covariance $\Sigma_s = 0.1 I_s$.
 
@@
 
+The system is described by its position $(p_x,p_y)$ and velocity $(v_x, v_y)$:
+\begin{equation*}
+x = \begin{bmatrix}
+p_x & p_y & v_x & v_y
+\end{bmatrix}^\transp
+\end{equation*}
+
 \paragraph{Actions}
+
+It is acted upon by means horizontal and vertical forces $u=(u_x, u_y)\in [-1,1]^2$.
+We discretise the action space into four constant controls, for each direction:
+\begin{equation*}
+\cA = \{(-1, -1), (-1, 1), (1, -1), (1, 1)\}
+\end{equation*}
+
 \paragraph{Reward}
+
+The reward encodes the task of navigating to reach a goal state $x_g$ while avoiding collisions with obstacles: $$R(x) = \delta(x)/(1 + \|x - x_g\|_2),$$  where $\delta(x)$ is $0$ whenever $x$ collides with an obstacle, $1$ otherwise.
+
 \paragraph{Dynamics}
-
-$
+The system dynamics consist in a double integrator, with friction parameters $(\theta_x, \theta_y)$:
+$$
 \begin{bmatrix}
@@
 \end{bmatrix}.
-$
+$$
 

### 2020-05-29 main.tex
Minor abstract change

@@
 This problem has been studied from different perspectives by different communities.
-However, only the case of quadratic costs --the LQ problem-- has been considered, which limits applications to tracking a fixed reference trajectory only.
+However, only the case of quadratic costs --the LQ problem-- has been considered, which limits applications to stabilisation and tracking tasks only.
 In order to handle more general (bounded, non-convex) costs that naturally arise in many practical problems, we carefully select and bring together several tools from different communities, namely non-asymptotic linear regression, recent results in interval prediction, and tree-based planning.

### 2020-05-29 main.tex
Minor change of broader impact

@@
 Beyond industrial perspectives, this work could be of general interest for risk-averse decision-making.
-For instance, parametrized epidemiological models have been used to represent the propagation of Covid\nobreakdash-19 and study the impact of several lockdown policies.
+For instance, parametrized epidemiological models have been used to represent the propagation of Covid\nobreakdash-19 and study the impact of lockdown policies.
 These model parameters are estimated from observational data and corresponding confidence intervals are often available, but rarely used in the decision-making loop.

### 2020-06-01 main.tex
Fix typo
Draft new version of related work

@@
 % before loading neurips_2020
-
+\PassOptionsToPackage{numbers, compress}{natbib}
 % ready for submission
@@
 
-While there exists a vast body of literature on the control of uncertain systems, its majority is only concerned with the problem of stabilisation around a fixed reference state or trajectory, including $\cH_\infty$ control \citep[see, e.g.][]{Basar1996}, sliding-mode control \citep{Lu1997}, tube-MPC \citep{Limon2010} or system-level synthesis \citep{Dean2017,Dean2018}.
+The control of uncertain systems is a long-standing problem, to which a vast body of literature is dedicated.
+Existing work is mostly concerned with the problem of \emph{stabilisation} around a fixed reference state or trajectory, including approaches such as $\cH_\infty$ control \citep[see, e.g.][]{Basar1996}, sliding-mode control \citep{Lu1997} or system-level synthesis \citep{Dean2017,Dean2018}.
+This paper fits in the popular MPC framework, for which adaptive data-driven schemes have been developed to deal with model uncertainty \citep{Sastry1990,Tanaskovic2014}.
+Need for guarantees.
+a common safety objective is the \emph{robust constraint satisfaction}, where the state $x$ is constrained into a region $\mathbb{X}$, often chosen convex \citep[e.g.][]{Turchetta2016,Lorenzen2017,Kohler2019,Lu2019} a line of work commonly referred to as Tube-MPC algorithms.
+
+To go beyond stabilization, we consider is the minimax objective. 
+Yet, we argue that many tasks cannot be framed as stabilisation problems (e.g. obstacle avoidance) and are better addressed in our setting of maximising an utility function. 
+It has been mostly studied in two particular cases: (1) linear systems with quadratic costs, and (2) finite state space. 
+Another kind of guarantee, is the minimax
+
+Finite states
+Robust optimisation with generic costs has been studied in the context of finite Markov Decision Processes with uncertain parameters by \citet{Iyengar2005}, \citet{Nilim2005} and \citet{Wiesemann2013}.
+They showed that the main results of Dynamic Programming can be extended to their robust counterparts only when the dynamics ambiguity set verifies a certain rectangularity property.
+Since we consider continuous states, these methods do not apply.
+
+Linear dynamics + Quadratic costs
+This has been vastly studied for quadratic costs, where several approaches have been proposed for cumulative regret minimisation in the LQ problem.
+In the \emph{Optimism in the Face of Uncertainty} paradigm, the best possible dynamics within a high-confidence region is selected under a controllability constraint, to compute the corresponding optimal control in closed-form by solving a Riccati equation.
+\citep{abbasi-yadkori11a,Ibrahimi2013,Faradonbeh2017} show that this procedure achieves a $\tilde{\cO}\left(N^{1/2}\right)$ regret.
+Posterior sampling algorithms \citep{Ouyang2017,abeille18a} select candidate dynamics randomly instead, and obtain the same result.
+Other works use noise injection for exploration such as \citep{Dean2017,Dean2018}.
+However, neither optimism nor random exploration fit a critical setting, where ensuring safety requires instead to consider pessimistic outcomes.
+The work of \citet{Dean2017} is closest to our setting: after an offline estimation phase, they estimate a simple regret between a robust controller and the optimal performance.
+Our work differs in that it addresses arbitrary bounded costs, rather than quadratic costs only.
+
+%While there exists a vast body of literature on the control of uncertain systems, its majority is only concerned with the problem of stabilisation around a fixed reference state or trajectory, including $\cH_\infty$ control \citep[see, e.g.][]{Basar1996}, sliding-mode control \citep{Lu1997}, tube-MPC \citep{Limon2010} or system-level synthesis \citep{Dean2017,Dean2018}.
 Yet, we argue that many tasks cannot be framed as stabilisation problems (e.g.
@@
 Therefore, we limit references to focus only on two lines of work closest to ours.
-
-\paragraph{Linear systems with quadratic costs} Several approaches have been proposed for cumulative regret minimisation in the LQ problem.
+%
+%\paragraph{Linear systems with quadratic costs} Several approaches have been proposed for cumulative regret minimisation in the LQ problem.
 In the \emph{Optimism in the Face of Uncertainty} paradigm, the best possible dynamics within a high-confidence region is selected under a controllability constraint, to compute the corresponding optimal control in closed-form by solving a Riccati equation.
@@
 Our work mainly differs in that it addresses generic costs.
-
-\paragraph{Robust Dynamic Programming with generic costs}
-Robust optimisation with generic costs has been studied in the context of finite Markov Decision Processes with uncertain parameters by \citet{Iyengar2005}, \citet{Nilim2005} and \citet{Wiesemann2013}.
+%
+%\paragraph{Robust Dynamic Programming with generic costs}
+%Robust optimisation with generic costs has been studied in the context of finite Markov Decision Processes with uncertain parameters by \citet{Iyengar2005}, \citet{Nilim2005} and \citet{Wiesemann2013}.
 They showed that the main results of Dynamic Programming can be extended to their robust counterparts only when the dynamics ambiguity set verifies a certain rectangularity property, related to time-varying uncertainty.
@@
 
-We abuse notations and define and include additional known terms in the measurement signal
+We slightly abuse notations and include additional known terms in the measurement signal
 $

### 2020-06-01 main.tex
Edit related work

@@
 This paper fits in the popular MPC framework, for which adaptive data-driven schemes have been developed to deal with model uncertainty \citep{Sastry1990,Tanaskovic2014}.
-Need for guarantees.
-a common safety objective is the \emph{robust constraint satisfaction}, where the state $x$ is constrained into a region $\mathbb{X}$, often chosen convex \citep[e.g.][]{Turchetta2016,Lorenzen2017,Kohler2019,Lu2019} a line of work commonly referred to as Tube-MPC algorithms.
-
-To go beyond stabilization, we consider is the minimax objective. 
-Yet, we argue that many tasks cannot be framed as stabilisation problems (e.g. obstacle avoidance) and are better addressed in our setting of maximising an utility function. 
-It has been mostly studied in two particular cases: (1) linear systems with quadratic costs, and (2) finite state space. 
-Another kind of guarantee, is the minimax
-
-Finite states
-Robust optimisation with generic costs has been studied in the context of finite Markov Decision Processes with uncertain parameters by \citet{Iyengar2005}, \citet{Nilim2005} and \citet{Wiesemann2013}.
-They showed that the main results of Dynamic Programming can be extended to their robust counterparts only when the dynamics ambiguity set verifies a certain rectangularity property.
+The family of tube-MPC algorithms seeks to derive theoretical guarantees of \emph{robust constraint satisfaction}: state $x$ is constrained in a safe region $\mathbb{X}$ around the origin, often chosen convex \citep[e.g.][]{Turchetta2016,Lorenzen2017,Kohler2019,Lu2019}.
+Yet, we argue that many tasks cannot be framed as (robust) stabilisation problems (e.g.
+obstacle avoidance) and are better addressed with the minimax control objective, which can allow more flexible goal formulations.
+Minimax control has mostly been studied in two particular instances.
+
+\textbf{Finite states} ~~ Minimax control of finite Markov Decision Processes with uncertain parameters was studied in \citep{Iyengar2005,Nilim2005,Wiesemann2013}, who showed that the main results of Dynamic Programming can be extended to their robust counterparts only when the dynamics ambiguity set verifies a certain rectangularity property.
 Since we consider continuous states, these methods do not apply.
 
-Linear dynamics + Quadratic costs
-This has been vastly studied for quadratic costs, where several approaches have been proposed for cumulative regret minimisation in the LQ problem.
+\textbf{Linear dynamics and quadratic costs} ~~ Several approaches have been proposed for cumulative regret minimisation in the LQ problem.
 In the \emph{Optimism in the Face of Uncertainty} paradigm, the best possible dynamics within a high-confidence region is selected under a controllability constraint, to compute the corresponding optimal control in closed-form by solving a Riccati equation.
@@
 However, neither optimism nor random exploration fit a critical setting, where ensuring safety requires instead to consider pessimistic outcomes.
-The work of \citet{Dean2017} is closest to our setting: after an offline estimation phase, they estimate a simple regret between a robust controller and the optimal performance.
+The work of \citet{Dean2017} is closest to our setting: after an offline estimation phase, they estimate a simple regret between a minimax controller and the optimal performance.
 Our work differs in that it addresses arbitrary bounded costs, rather than quadratic costs only.

### 2020-06-02 main.tex
More related work, and remarks from Denis

@@
 This problem has been studied from different perspectives by different communities.
-However, only the case of quadratic costs --the LQ problem-- has been considered, which limits applications to stabilisation and tracking tasks only.
-In order to handle more general (bounded, non-convex) costs that naturally arise in many practical problems, we carefully select and bring together several tools from different communities, namely non-asymptotic linear regression, recent results in interval prediction, and tree-based planning.
+However, the existing theory deals only with the case of quadratic costs (the LQ problem), which limits applications to stabilisation and tracking tasks only.
+In order to handle more general (non-convex) costs that naturally arise in many practical problems, we carefully select and bring together several tools from different communities, namely non-asymptotic linear regression, recent results in interval prediction, and tree-based planning.
 Combining and adapting the theoretical guarantees at each layer is non trivial, and we provide the first end-to-end regret analysis for this setting.
@@
 First, it depends on a tremendous amount of interaction data that cannot always be simulated.
-This issue is alleviated by model-based methods -- which we consider in this work -- that often benefit from better sample efficiencies than their model-free counterparts.
+This issue can be alleviated by model-based methods -- which we consider in this work -- that often benefit from better sample efficiencies than their model-free counterparts.
 Second, it relies on trial-and-error and random exploration.
-In this paper, we consider the problem of controlling an unknown linear system $x(t)$ so as to maximise an \emph{arbitrary} bounded reward function $R$, in a critical setting where mistakes are costly and must be avoided at all time.
+In order to overcome these shortages, and motivated by the path planning problem for a self-driving car, in this paper we consider the problem of controlling an unknown linear system $x(t)$ so as to maximise an \emph{arbitrary} bounded reward function $R$, in a critical setting where mistakes are costly and must be avoided at all time.
 This choice of rich reward space is crucial to have sufficient flexibility to model non-convex and non-smooth functions that naturally arise in many practical problems involving combinatorial optimisation, branching decisions, etc., while quadratic costs are mostly suited for tracking a fixed reference trajectory \citep[e.g.][]{Kumar2013}.
@@
 
-To address this issue, we turn to the framework of \emph{robust} decision-making: instead of merely considering a point estimate of the dynamics, we build an entire \emph{confidence region} $\cC_{[N],\delta} \subset \Theta$, illustrated in \Cref{fig:estimation}, that contains the true dynamics with high probability:
+To address this issue, we turn to the framework of \emph{robust} decision-making: instead of merely considering a point estimate of the dynamics, for any $N\in\Natural$, we build an entire \emph{confidence region} $\cC_{[N],\delta}$, illustrated in \Cref{fig:estimation}, that contains the true dynamics with high probability:
 \begin{align}
@@
 Maximin problems such as $\eqref{eq:robust-control}$ are notoriously hard if the reward $R$ has a simple form.
-With arbitrary functions $R$, we cannot hope to derive an explicit solution.
+However, without a restriction on the shape of functions $R$, we cannot hope to derive an explicit solution.
 In our second contribution, we propose a robust MPC algorithm for solving \eqref{eq:robust-control} numerically.
 In \Cref{sec:prediction}, we leverage recent results from the uncertain system simulation literature to derive an \emph{interval predictor} $[\underline{x}(t),\overline{x}(t)]$ for the system \eqref{eq:dynamics}, illustrated in \Cref{fig:prediction}.
-This predictor takes the information on the current state ${x}_N$, the confidence region $\cC_\delta$, planned control sequence $\bu$ and admissible perturbation bounds $[\underline{\omega}(t),\overline{\omega}(t)]$; and must verify the \emph{inclusion property}:
+For any $N\in\Natural$, his predictor takes the information on the current state ${x}_N$, the confidence region $\cC_{[N],\delta}$, planned control sequence $\bu$ and admissible perturbation bounds $[\underline{\omega}(t),\overline{\omega}(t)]$; and must verify the \emph{inclusion property}:
 \begin{equation}
@@
 However, tree-based planning algorithms are designed for a single known generative model rather than a confidence region for the system dynamics.
-Our third contribution adapts them to the robust objective \eqref{eq:robust-control} by approximating it with a tractable surrogate $\hat{V}^r$ that exploits the interval predictor \eqref{eq:inclusion-property} to define a pessimistic reward.
+Our third contribution adapts them to the robust objective \eqref{eq:robust-control} by approximating it with a tractable surrogate $\hat{V}^r$ that exploits the interval predictions \eqref{eq:inclusion-property} to define a pessimistic reward.
 In our main result, we show that the best surrogate performance achieved during planning is guaranteed to be attained on the true system, and provide an upper bound for the approximation gap and simple regret of our framework in \Cref{thm:control-error}.
@@
 		\STATE $\cC_{[N],\delta} \gets$\textsc{Model Estimation}$(\cD_{[N]})$. \eqref{eq:polytope}
-		\FOR{each planning step $k\in[K]$}
-		\STATE $[\underline{x}_{n+1}, \overline{x}_{n+1}]\gets$ \textsc{Interval Prediction}($\cC_{[N],\delta}, \ba_kb$) for each action $b\in \cA$. \eqref{eq:interval-predictor}
-
-		\STATE $\ba_{k+1}$ $\gets$\textsc{Pessimistic Planning}$(\underline{R_{n+1}}([\underline{x}_{n+1}, \overline{x}_{n+1}]))$.  \eqref{eq:opd}
+		\FOR{each planning step $k\in\{N,\dots,N+K\}=N+[K]$}
+		\STATE $[\underline{x}_{k+1}, \overline{x}_{k+1}]\gets$ \textsc{Interval Prediction}($\cC_{[N],\delta}, \ba_kb$) for each action $b\in \cA$. \eqref{eq:interval-predictor}
+
+		\STATE $\ba_{k+1}$ $\gets$\textsc{Pessimistic Planning}$(\underline{R_{k+1}}([\underline{x}_{k+1}, \overline{x}_{k+1}]))$.  \eqref{eq:opd}
 		\ENDFOR
-		\STATE Execute the control $u_{N+1}$, and add the observed transition $(x_{N+1}, y_{N+1}, u_{N+1})$ to $\cD_{[N+1]}$.
+		\STATE Execute the recommended control $u_{N+1}$, and add the transition $(x_{N+1}, y_{N+1}, u_{N+1})$ to $\cD_{[N+1]}$.
 		\ENDFOR
@@
 The control of uncertain systems is a long-standing problem, to which a vast body of literature is dedicated.
-Existing work is mostly concerned with the problem of \emph{stabilisation} around a fixed reference state or trajectory, including approaches such as $\cH_\infty$ control \citep[see, e.g.][]{Basar1996}, sliding-mode control \citep{Lu1997} or system-level synthesis \citep{Dean2017,Dean2018}.
-This paper fits in the popular MPC framework, for which adaptive data-driven schemes have been developed to deal with model uncertainty \citep{Sastry1990,Tanaskovic2014}.
-The family of tube-MPC algorithms seeks to derive theoretical guarantees of \emph{robust constraint satisfaction}: state $x$ is constrained in a safe region $\mathbb{X}$ around the origin, often chosen convex \citep[e.g.][]{Turchetta2016,Lorenzen2017,Kohler2019,Lu2019}.
-Yet, we argue that many tasks cannot be framed as (robust) stabilisation problems (e.g.
+Existing work is mostly concerned with the problem of \emph{stabilisation} around a fixed reference state or trajectory, including approaches such as $\cH_\infty$ control \citep[][]{Basar1996}, sliding-mode control \citep{Lu1997} or system-level synthesis \citep{Dean2017,Dean2018}.
+This paper fits in the popular MPC framework, for which adaptive data-driven schemes have been developed to deal with model uncertainty \citep{Sastry1990,Tanaskovic2014,Amos2018}, but lack guarantees.
+The family of tube-MPC algorithms seeks to derive theoretical guarantees of \emph{robust constraint satisfaction}: the state $x$ is constrained in a safe region $\mathbb{X}$ around the origin, often chosen convex \citep{Fukushima2007,Adetola2009,Aswani2013,Turchetta2016,Lorenzen2017,Kohler2019,Lu2019}.
+%, their adaptive versions take also into account the possible parametric model uncertainty
+Yet, many tasks cannot be framed as stabilisation problems (e.g.
 obstacle avoidance) and are better addressed with the minimax control objective, which can allow more flexible goal formulations.
@@
 In the \emph{Optimism in the Face of Uncertainty} paradigm, the best possible dynamics within a high-confidence region is selected under a controllability constraint, to compute the corresponding optimal control in closed-form by solving a Riccati equation.
-\citep{abbasi-yadkori11a,Ibrahimi2013,Faradonbeh2017} show that this procedure achieves a $\tilde{\cO}\left(N^{1/2}\right)$ regret.
+The results of 	\citep{abbasi-yadkori11a,Ibrahimi2013,Faradonbeh2017} show that this procedure achieves a $\tilde{\cO}\left(N^{1/2}\right)$ regret.
 Posterior sampling algorithms \citep{Ouyang2017,abeille18a} select candidate dynamics randomly instead, and obtain the same result.
@@
 However, neither optimism nor random exploration fit a critical setting, where ensuring safety requires instead to consider pessimistic outcomes.
-The work of \citet{Dean2017} is closest to our setting: after an offline estimation phase, they estimate a simple regret between a minimax controller and the optimal performance.
-Our work differs in that it addresses arbitrary bounded costs, rather than quadratic costs only.
+The work of \citet{Dean2017} is close to our setting: after an offline estimation phase, they estimate a simple regret between a minimax controller and the optimal performance.
+Our work differs in that it addresses a generic shape cost.
+Another work of interest is \citep{Rosolia2019} where worst-case generic costs are considered.
+However, they assume the knowledge of the dynamics, and their rollout-based solution only produces inner-approximations and do not yield any guarantee.
+In this paper, interval prediction is used to produce oversets, while a near-optimal control is found using a tree-based planning procedure.
 
@@
 For instance, it is the case when $\nu$ and $\omega$ are bounded or Gaussian noises.
+
+\textbf{Remark} ~ In the objective \eqref{eq:robust-control}, we use local bounds  $\underline{\omega}(t)\leq \omega(t) \leq \overline{\omega}(t)$ that hold with confidence $\delta_n = \frac{\delta}{n(n+1)}$, so that the event $\{\forall n, \underline{\omega}(t_n) \leq \omega(t_n) \leq \overline{\omega}(t_n)\}$ holds with probability $1-\delta$.
 %Note that \Cref{assumpt:bounded-noise} implies that $\eta$ is sub-Gaussian with covariance proxy $\Sigma_p=\|\eta\|_\infty I_p$.
@@
 % at the price of an increased computational cost required by the diagonalisation of $G_{N,\lambda}$.
-
-\paragraph{Remark} The robust objective \eqref{eq:robust-control} involves bounds $\underline{\omega}(t)\leq \omega(t) \leq \overline{\omega}(t)$ over the possible perturbations we want to protect against.
-We use local bounds that each holds with confidence $\delta_n = \frac{\delta}{n(n+1)}$, so that the event $\{\forall n, \underline{\omega}(t_n) \leq \omega(t_n) \leq \overline{\omega}(t_n)\}$ holds with probability $1-\delta$.
 

### 2020-06-03 main.tex
C_N,delta is a confidence region on theta, not A(theta)

@@
 
-To address this issue, we turn to the framework of \emph{robust} decision-making: instead of merely considering a point estimate of the dynamics, for any $N\in\Natural$, we build an entire \emph{confidence region} $\cC_{[N],\delta}$, illustrated in \Cref{fig:estimation}, that contains the true dynamics with high probability:
+To address this issue, we turn to the framework of \emph{robust} decision-making: instead of merely considering a point estimate of the dynamics, for any $N\in\Natural$, we build an entire \emph{confidence region} $\cC_{[N],\delta}\subset\Theta$, illustrated in \Cref{fig:estimation}, that contains the true dynamics parameter with high probability:
 \begin{align}
-\probability{A(\theta)\in \cC_{[N],\delta}} \geq 1-\delta,
+\probability{\theta\in \cC_{[N],\delta}} \geq 1-\delta,
 \label{eq:confidence}
@@
 \label{eq:robust-control}
-\sup_{\bu\in{(\Real^q)}^\Natural} {V^r(\bu)}, \qquad \text{ where }\qquad {V^r(\bu)} \eqdef \inf_{\substack{A(\theta) \in \cC_{[N],\delta} \\ \bom\in[\underline{\bom},\overline{\bom}]^\Natural}} \left[\sum_{n=N+1}^\infty \gamma^n R(x_n(\bu,\bom))\right],
+\sup_{\bu\in{(\Real^q)}^\Natural} {V^r(\bu)}, \qquad \text{ where }\qquad {V^r(\bu)} \eqdef \inf_{\substack{\theta \in \cC_{[N],\delta} \\ \bom\in[\underline{\bom},\overline{\bom}]^\Natural}} \left[\sum_{n=N+1}^\infty \gamma^n R(x_n(\bu,\bom))\right],
 \end{equation}
@@
 In \Cref{sec:prediction}, we leverage recent results from the uncertain system simulation literature to derive an \emph{interval predictor} $[\underline{x}(t),\overline{x}(t)]$ for the system \eqref{eq:dynamics}, illustrated in \Cref{fig:prediction}.
-For any $N\in\Natural$, his predictor takes the information on the current state ${x}_N$, the confidence region $\cC_{[N],\delta}$, planned control sequence $\bu$ and admissible perturbation bounds $[\underline{\omega}(t),\overline{\omega}(t)]$; and must verify the \emph{inclusion property}:
+For any $N\in\Natural$, this predictor takes the information on the current state ${x}_N$, the confidence region $\cC_{[N],\delta}$, planned control sequence $\bu$ and admissible perturbation bounds $[\underline{\omega}(t),\overline{\omega}(t)]$; and must verify the \emph{inclusion property}:
 \begin{equation}
@@
 		\centering
-		\includegraphics[trim={4cm 0 0 0}, clip, width=0.5\linewidth]{img/ellipsoid}
+		\includegraphics[trim={1cm 0 0 0}, clip, width=0.6\linewidth]{img/ellipsoid}
 		\caption{The model estimation procedure, running on the obstacle avoidance problem of \Cref{sec:experiments}. The confidence region $C_{[N],\delta}$ shrinks with the number of samples $N$.}
@@
 Another work of interest is \citep{Rosolia2019} where worst-case generic costs are considered.
-However, they assume the knowledge of the dynamics, and their rollout-based solution only produces inner-approximations and do not yield any guarantee.
+However, they assume the knowledge of the dynamics, and their rollout-based solution only produces inner-approximations and does not yield any guarantee.
 In this paper, interval prediction is used to produce oversets, while a near-optimal control is found using a tree-based planning procedure.
@@
 
-We can enclose this confidence ellipsoid $\eqref{eq:confidence-ellipsoid}$ into a polytope $C_{[N],\delta}$.
-For simplicity, we present here a simple but coarse strategy: bound the ellipsoid by its enclosing axis-aligned hypercube.
-We obtain
+We convert this confidence ellipsoid $\cC_{[N],\delta}$ from \eqref{eq:confidence-ellipsoid} into a polytope for $A(\theta)$.
+For simplicity, we present here a simple but coarse strategy: bound the ellipsoid by its enclosing axis-aligned hypercube:
 \begin{align}
     \label{eq:polytope}
-     \cC_{[N],\delta} = \left\{ A_0 +\sum_{i=1}^{2^d}\alpha_{i}\Delta A_{i}: \alpha\geq 0,  \sum_{i=1}^{2^d}\alpha_{i}=1\right\} \text{ where } A_0 = A + \theta_{N,\lambda}^\transp\phi,\; h_i\in\{-1,1\}^d,
+     A(\theta)\in \left\{ A_0 +\sum_{i=1}^{2^d}\alpha_{i}\Delta A_{i}: \alpha\geq 0,  \sum_{i=1}^{2^d}\alpha_{i}=1\right\} \text{ where } A_0 = A + \theta_{N,\lambda}^\transp\phi,\; h_i\in\{-1,1\}^d,
 \end{align}

### 2020-08-08 neurips_2020.tex
Add author response

\documentclass{article}

% if you need to pass options to natbib, use, e.g.:
%     \PassOptionsToPackage{numbers, compress}{natbib}
% before loading neurips_2020

% ready for submission
% \usepackage{neurips_2020}

% to compile a preprint version, e.g., for submission to arXiv, add add the
% [preprint] option:
     \usepackage[preprint]{neurips_2020}

% to compile a camera-ready version, add the [final] option, e.g.:
%     \usepackage[final]{neurips_2020}

% to avoid loading the natbib package, add option nonatbib:
%     \usepackage[nonatbib]{neurips_2020}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

\title{Formatting Instructions For NeurIPS 2020}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to break the
% lines. Using \AND forces a line break at that point. So, if LaTeX puts 3 of 4
% authors names on the first line, and the last on the second line, try using
% \AND instead of \And before the third author name.

\author{%
  David S.~Hippocampus\thanks{Use footnote for providing further information
    about author (webpage, alternative address)---\emph{not} for acknowledging
    funding agencies.} \\
  Department of Computer Science\\
  Cranberry-Lemon University\\
  Pittsburgh, PA 15213 \\
  \texttt{hippo@cs.cranberry-lemon.edu} \\
  % examples of more authors
   \And
   Coauthor \\
   Affiliation \\
   Address \\
   \texttt{email} \\
   \AND
   Coauthor \\
   Affiliation \\
   Address \\
   \texttt{email} \\
   \And
   Coauthor \\
   Affiliation \\
   Address \\
   \texttt{email} \\
   \AND
   Coauthor \\
   Affiliation \\
   Address \\
   \texttt{email} \\
}

\begin{document}

\maketitle

\begin{abstract}
  The abstract paragraph should be indented \nicefrac{1}{2}~inch (3~picas) on
  both the left- and right-hand margins. Use 10~point type, with a vertical
  spacing (leading) of 11~points.  The word \textbf{Abstract} must be centered,
  bold, and in point size 12. Two line spaces precede the abstract. The abstract
  must be limited to one paragraph.
\end{abstract}

\section{Submission of papers to NeurIPS 2020}

NeurIPS requires electronic submissions.  The electronic submission site is
\begin{center}
  \url{https://cmt3.research.microsoft.com/NeurIPS2020/}
\end{center}

Please read the instructions below carefully and follow them faithfully.

\subsection{Style}

Papers to be submitted to NeurIPS 2020 must be prepared according to the
instructions presented here. Papers may only be up to eight pages long,
including figures. Additional pages \emph{containing only a section on the broader impact, acknowledgments and/or cited references} are allowed. Papers that exceed eight pages of content will not be reviewed, or in any other way considered for
presentation at the conference.

The margins in 2020 are the same as those in 2007, which allow for $\sim$$15\%$
more words in the paper compared to earlier years.

Authors are required to use the NeurIPS \LaTeX{} style files obtainable at the
NeurIPS website as indicated below. Please make sure you use the current files
and not previous versions. Tweaking the style files may be grounds for
rejection.

\subsection{Retrieval of style files}

The style files for NeurIPS and other conference information are available on
the World Wide Web at
\begin{center}
  \url{http://www.neurips.cc/}
\end{center}
The file \verb+neurips_2020.pdf+ contains these instructions and illustrates the
various formatting requirements your NeurIPS paper must satisfy.

The only supported style file for NeurIPS 2020 is \verb+neurips_2020.sty+,
rewritten for \LaTeXe{}.  \textbf{Previous style files for \LaTeX{} 2.09,
  Microsoft Word, and RTF are no longer supported!}

The \LaTeX{} style file contains three optional arguments: \verb+final+, which
creates a camera-ready copy, \verb+preprint+, which creates a preprint for
submission to, e.g., arXiv, and \verb+nonatbib+, which will not load the
\verb+natbib+ package for you in case of package clash.

\paragraph{Preprint option}
If you wish to post a preprint of your work online, e.g., on arXiv, using the
NeurIPS style, please use the \verb+preprint+ option. This will create a
nonanonymized version of your work with the text ``Preprint. Work in progress.''
in the footer. This version may be distributed as you see fit. Please \textbf{do
  not} use the \verb+final+ option, which should \textbf{only} be used for
papers accepted to NeurIPS.

At submission time, please omit the \verb+final+ and \verb+preprint+
options. This will anonymize your submission and add line numbers to aid
review. Please do \emph{not} refer to these line numbers in your paper as they
will be removed during generation of camera-ready copies.

The file \verb+neurips_2020.tex+ may be used as a ``shell'' for writing your
paper. All you have to do is replace the author, title, abstract, and text of
the paper with your own.

The formatting instructions contained in these style files are summarized in
Sections \ref{gen_inst}, \ref{headings}, and \ref{others} below.

\section{General formatting instructions}
\label{gen_inst}

The text must be confined within a rectangle 5.5~inches (33~picas) wide and
9~inches (54~picas) long. The left margin is 1.5~inch (9~picas).  Use 10~point
type with a vertical spacing (leading) of 11~points.  Times New Roman is the
preferred typeface throughout, and will be selected for you by default.
Paragraphs are separated by \nicefrac{1}{2}~line space (5.5 points), with no
indentation.

The paper title should be 17~point, initial caps/lower case, bold, centered
between two horizontal rules. The top rule should be 4~points thick and the
bottom rule should be 1~point thick. Allow \nicefrac{1}{4}~inch space above and
below the title to rules. All pages should start at 1~inch (6~picas) from the
top of the page.

For the final version, authors' names are set in boldface, and each name is
centered above the corresponding address. The lead author's name is to be listed
first (left-most), and the co-authors' names (if different address) are set to
follow. If there is only one co-author, list both author and co-author side by
side.

Please pay special attention to the instructions in Section \ref{others}
regarding figures, tables, acknowledgments, and references.

\section{Headings: first level}
\label{headings}

All headings should be lower case (except for first word and proper nouns),
flush left, and bold.

First-level headings should be in 12-point type.

\subsection{Headings: second level}

Second-level headings should be in 10-point type.

\subsubsection{Headings: third level}

Third-level headings should be in 10-point type.

\paragraph{Paragraphs}

There is also a \verb+\paragraph+ command available, which sets the heading in
bold, flush left, and inline with the text, with the heading followed by 1\,em
of space.

\section{Citations, figures, tables, references}
\label{others}

These instructions apply to everyone.

\subsection{Citations within the text}

The \verb+natbib+ package will be loaded for you by default.  Citations may be
author/year or numeric, as long as you maintain internal consistency.  As to the
format of the references themselves, any style is acceptable as long as it is
used consistently.

The documentation for \verb+natbib+ may be found at
\begin{center}
  \url{http://mirrors.ctan.org/macros/latex/contrib/natbib/natnotes.pdf}
\end{center}
Of note is the command \verb+\citet+, which produces citations appropriate for
use in inline text.  For example,
\begin{verbatim}
   \citet{hasselmo} investigated\dots
\end{verbatim}
produces
\begin{quote}
  Hasselmo, et al.\ (1995) investigated\dots
\end{quote}

If you wish to load the \verb+natbib+ package with options, you may add the
following before loading the \verb+neurips_2020+ package:
\begin{verbatim}
   \PassOptionsToPackage{options}{natbib}
\end{verbatim}

If \verb+natbib+ clashes with another package you load, you can add the optional
argument \verb+nonatbib+ when loading the style file:
\begin{verbatim}
   \usepackage[nonatbib]{neurips_2020}
\end{verbatim}

As submission is double blind, refer to your own published work in the third
person. That is, use ``In the previous work of Jones et al.\ [4],'' not ``In our
previous work [4].'' If you cite your other papers that are not widely available
(e.g., a journal paper under review), use anonymous author names in the
citation, e.g., an author of the form ``A.\ Anonymous.''

\subsection{Footnotes}

Footnotes should be used sparingly.  If you do require a footnote, indicate
footnotes with a number\footnote{Sample of the first footnote.} in the
text. Place the footnotes at the bottom of the page on which they appear.
Precede the footnote with a horizontal rule of 2~inches (12~picas).

Note that footnotes are properly typeset \emph{after} punctuation
marks.\footnote{As in this example.}

\subsection{Figures}

\begin{figure}
  \centering
  \fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
  \caption{Sample figure caption.}
\end{figure}

All artwork must be neat, clean, and legible. Lines should be dark enough for
purposes of reproduction. The figure number and caption always appear after the
figure. Place one line space before the figure caption and one line space after
the figure. The figure caption should be lower case (except for first word and
proper nouns); figures are numbered consecutively.

You may use color figures.  However, it is best for the figure captions and the
paper body to be legible if the paper is printed in either black/white or in
color.

\subsection{Tables}

All tables must be centered, neat, clean and legible.  The table number and
title always appear before the table.  See Table~\ref{sample-table}.

Place one line space before the table title, one line space after the
table title, and one line space after the table. The table title must
be lower case (except for first word and proper nouns); tables are
numbered consecutively.

Note that publication-quality tables \emph{do not contain vertical rules.} We
strongly suggest the use of the \verb+booktabs+ package, which allows for
typesetting high-quality, professional tables:
\begin{center}
  \url{https://www.ctan.org/pkg/booktabs}
\end{center}
This package was used to typeset Table~\ref{sample-table}.

\begin{table}
  \caption{Sample table title}
  \label{sample-table}
  \centering
  \begin{tabular}{lll}
    \toprule
    \multicolumn{2}{c}{Part}                   \\
    \cmidrule(r){1-2}
    Name     & Description     & Size ($\mu$m) \\
    \midrule
    Dendrite & Input terminal  & $\sim$100     \\
    Axon     & Output terminal & $\sim$10      \\
    Soma     & Cell body       & up to $10^6$  \\
    \bottomrule
  \end{tabular}
\end{table}

\section{Final instructions}

Do not change any aspects of the formatting parameters in the style files.  In
particular, do not modify the width or length of the rectangle the text should
fit into, and do not change font sizes (except perhaps in the
\textbf{References} section; see below). Please note that pages should be
numbered.

\section{Preparing PDF files}

Please prepare submission files with paper size ``US Letter,'' and not, for
example, ``A4.''

Fonts were the main cause of problems in the past years. Your PDF file must only
contain Type 1 or Embedded TrueType fonts. Here are a few instructions to
achieve this.

\begin{itemize}

\item You should directly generate PDF files using \verb+pdflatex+.

\item You can check which fonts a PDF files uses.  In Acrobat Reader, select the
  menu Files$>$Document Properties$>$Fonts and select Show All Fonts. You can
  also use the program \verb+pdffonts+ which comes with \verb+xpdf+ and is
  available out-of-the-box on most Linux machines.

\item The IEEE has recommendations for generating PDF files whose fonts are also
  acceptable for NeurIPS. Please see
  \url{http://www.emfield.org/icuwb2010/downloads/IEEE-PDF-SpecV32.pdf}

\item \verb+xfig+ "patterned" shapes are implemented with bitmap fonts.  Use
  "solid" shapes instead.

\item The \verb+\bbold+ package almost always uses bitmap fonts.  You should use
  the equivalent AMS Fonts:
\begin{verbatim}
   \usepackage{amsfonts}
\end{verbatim}
followed by, e.g., \verb+\mathbb{R}+, \verb+\mathbb{N}+, or \verb+\mathbb{C}+
for $\mathbb{R}$, $\mathbb{N}$ or $\mathbb{C}$.  You can also use the following
workaround for reals, natural and complex:
\begin{verbatim}
   \newcommand{\RR}{I\!\!R} %real numbers
   \newcommand{\Nat}{I\!\!N} %natural numbers
   \newcommand{\CC}{I\!\!\!\!C} %complex numbers
\end{verbatim}
Note that \verb+amsfonts+ is automatically loaded by the \verb+amssymb+ package.

\end{itemize}

If your file contains type 3 fonts or non embedded TrueType fonts, we will ask
you to fix it.

\subsection{Margins in \LaTeX{}}

Most of the margin problems come from figures positioned by hand using
\verb+\special+ or other commands. We suggest using the command
\verb+\includegraphics+ from the \verb+graphicx+ package. Always specify the
figure width as a multiple of the line width as in the example below:
\begin{verbatim}
   \usepackage[pdftex]{graphicx} ...
   \includegraphics[width=0.8\linewidth]{myfile.pdf}
\end{verbatim}
See Section 4.4 in the graphics bundle documentation
(\url{http://mirrors.ctan.org/macros/latex/required/graphics/grfguide.pdf})

A number of width problems arise when \LaTeX{} cannot properly hyphenate a
line. Please give LaTeX hyphenation hints using the \verb+\-+ command when
necessary.

\section*{Broader Impact}

Authors are required to include a statement of the broader impact of their work, including its ethical aspects and future societal consequences. 
Authors should discuss both positive and negative outcomes, if any. For instance, authors should discuss a) 
who may benefit from this research, b) who may be put at disadvantage from this research, c) what are the consequences of failure of the system, and d) whether the task/method leverages
biases in the data. If authors believe this is not applicable to them, authors can simply state this.

Use unnumbered first level headings for this section, which should go at the end of the paper. {\bf Note that this section does not count towards the eight pages of content that are allowed.}

\begin{ack}
Use unnumbered first level headings for the acknowledgments. All acknowledgments
go at the end of the paper before the list of references. Moreover, you are required to declare 
funding (financial activities supporting the submitted work) and competing interests (related financial activities outside the submitted work). 
More information about this disclosure can be found at: \url{https://neurips.cc/Conferences/2020/PaperInformation/FundingDisclosure}.

Do {\bf not} include this section in the anonymized submission, only in the final paper. You can use the \texttt{ack} environment provided in the style file to autmoatically hide this section in the anonymized submission.
\end{ack}

\section*{References}

References follow the acknowledgments. Use unnumbered first-level heading for
the references. Any choice of citation style is acceptable as long as you are
consistent. It is permissible to reduce the font size to \verb+small+ (9 point)
when listing the references.
{\bf Note that the Reference section does not count towards the eight pages of content that are allowed.}
\medskip

\small

[1] Alexander, J.A.\ \& Mozer, M.C.\ (1995) Template-based algorithms for
connectionist rule extraction. In G.\ Tesauro, D.S.\ Touretzky and T.K.\ Leen
(eds.), {\it Advances in Neural Information Processing Systems 7},
pp.\ 609--616. Cambridge, MA: MIT Press.

[2] Bower, J.M.\ \& Beeman, D.\ (1995) {\it The Book of GENESIS: Exploring
  Realistic Neural Models with the GEneral NEural SImulation System.}  New York:
TELOS/Springer--Verlag.

[3] Hasselmo, M.E., Schnell, E.\ \& Barkai, E.\ (1995) Dynamics of learning and
recall at excitatory recurrent synapses and cholinergic modulation in rat
hippocampal region CA3. {\it Journal of Neuroscience} {\bf 15}(7):5249-5262.

\end{document}

### 2020-08-08 neurips_2020_author_response.tex
Add author response

\documentclass{article}

\usepackage{neurips_2020_author_response}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

\usepackage{lipsum}

\usepackage[dvipsnames]{xcolor}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{blkarray}
\usepackage{mathtools}
\usepackage{multirow}
\usepackage{bm}
\usepackage{enumitem}
\usepackage{comment}
\usepackage{listings}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{cleveref}

\input{mathdef.tex}

\begin{document}

We thank all reviewers for their careful reading, their insightful and constructive comments, and for recognizing the importance of this research area (\hlr{R1},\hlg{R2},\hlb{R3},\hlm{R4}), the effort we put in bringing together tools from different areas (\hlr{R1},\hlg{R2},\hlb{R3},\hlm{R4}), and the soundness of theoretical results (\hlr{R1},\hlm{R4}). We answer the main concerns below, but will incorporate all feedback (typos, presentation, additional references) in the final version.

\paragraph{(\hlg{R2}) Unclear connections between the finite planning and the infinite horizon performance $V$.} We decided to study separately the errors stemming from the approximation of $V^r$ by $\hat{V}^r$ for any controls $\mathbf{u}$ (in Thm. 3); and those caused by the optimization of $\hat{V}^r$ with a finite budget $K$ (in Thm. 2). Following your suggestion, we propose to reformulate Thm. 3 to also account for the effect of finite planning, through the planned action $a_K$ (see next point).

\paragraph{(\hlg{R2}) Reliance of the main result on the PE assumption.} We resorted to this assumption to get asymptotic near-optimal performance when $N\to\infty$. It is quite common in the control literature, as recognized by \hlm{R4}. % and was used in similar context (LQ control) by [11,2]. 
However, as you pointed out, our non-asymptotic analysis actually yields a stronger input-dependent result. Accordingly, we propose to remove the PE assumption from Thm. 3, which reverts the $\log N / N$ term in the bound back to the input-dependent term $\beta_N(\delta)^2/\lambda_{\min}(G_{N,\lambda})$. Thus, our main result becomes:
\begin{equation*}
\hat{V}^r(a_K) \leq {V}^r(a^\star) \leq V(a^\star) \leq \hat{V}^r(a_K) + \hlr{\underbrace{\Delta_\omega}_{\substack{\text{robustness to}\\ \text{perturbations}}}} + \hlb{\underbrace{\cO\left(\frac{\beta_N(\delta)^2}{\lambda_{\min}(G_{N,\lambda})}\right)}_{\text{estimation error}}} + \hlg{\underbrace{\cO\left(K^{-\frac{\log 1/\gamma}{\log \kappa}}\right)}_{\text{planning error}}}
\end{equation*}
 Then, we will mention in a corollary that under the (restrictive) PE assumption, this estimation error term reduces to the more explicit form $\hlb{{\cO\left(\frac{\log(N^{d/2}/\delta)}{N}\right)}}$ which ensures asymptotic near-optimality when $N\to\infty$ (and $K\to\infty$).

\paragraph{(\hlg{R2}) Unclear connection between the discrete measurement noise and the continuous time noise process.}  Indeed, the reasoning of the remark on line 135 is insufficient, since it only bounds $\omega(t)$ at discrete time steps $(t_n)_{n\in\Natural}$ while the interval prediction requires bounds $\underline{\omega}(t)\leq\omega(t)\leq\overline{\omega}(t)$ that hold at all times $t\geq 0$. We overlooked it, and are very grateful to \hlg{R2} for pointing it out. Thankfully, this gap can easily be fixed. The most straightforward way is to directly assume bounded perturbations, such a hypothesis is both realistic and ubiquitous in the robust MPC literature [17, 4, 6, 28, 22, 29]. Another solution, in the spirit of our remark, is to further specify the continuous-time noise process $\omega(t)$: in place of Assumpt. 2, the disturbance $\omega(t)$ can be modeled as a Wiener process $W_t$. This has two effects: first, the increments $W_{t+\dd t} - W_t$ are independently and normally distributed, which allows keeping the estimation procedure of Thm. 1 by simply replacing $y_n$ and $\Phi_n$ by the differences $\tilde{y}_n = y_n-y_{n-1}$ and $\tilde{\Phi}_n = \Phi_n-\Phi_{n-1}$ in the expressions of $\theta_{N,\lambda}$ and $G_{N,\lambda}$. Second, the running maximum $\max_{0\leq s\leq t} W_s$ of a Wiener process is Half-normally distributed, which allows to define bounds $\overline{\omega}_n$ on $W_t$ that hold with probability $\delta_n$ \emph{for all $0\leq t\leq t_n$}. Then, a union bound over all $[0,t_{n}]$ intervals can be applied to effectively bound $\omega(t)$ for all $t\geq 0$. That being said, we would rather include the first solution (bounded perturbations assumption) in the final version for simplicity.

\paragraph{(\hlg{R2}) Suboptimality result defined as regret.} The term \textit{simple} (as opposed to cumulative) \textit{regret} has been used in the planning literature [e.g. 19] as a synonym for \textit{suboptimality} . We agree to use the latter, less ambiguous, instead.

\paragraph{(\hlg{R2},\hlb{R3}) Relevance of the multi-model extension.}
We added this section to mitigate the assumption of linear dynamics and uncertainty, which \hlb{R3} finds quite restrictive. Allowing multiple models enables to make multi-modal predictions, which we consider a substantial improvement: it was \textit{e.g.} necessary for our simulated driving experiment.

\paragraph{(\hlb{R3}) The discretization of controls might result in some loss of performance.}
Indeed. However, as suggested in line 67, this issue could be circumvented by resorting to more complex planning algorithms for continuous actions, such as \texttt{SOPC} [10] which also comes with a regret bound. We settled for discrete actions for ease of presentation.

\paragraph{(\hlm{R4}) Comparison against other methods.}
We have wondered about what methods to compare against. In our related work, we made the case that three major families of robust control (robust stabilization, robust constraint satisfaction, and minimax LQ) cannot be applied to our environments, which are not stabilization tasks, involve non-convex constraints and cannot be solved with quadratic costs. Turning to non-robust RL methods, we argued in lines 249-252 that a model-based approach with the same dynamics priors and planning algorithm (our \textit{nominal} baseline) would make the fairest comparison. We have since run an additional comparison to DQN, which converged in 30k samples --causing 2k collisions-- to a policy that still suffers a 6\% collision rate. This discussion will be included in the final version. 
% We may add a comparison to [Constrained Policy Optimization, Achiam et al, 2017], in a different setting.

\paragraph{(\hlr{R1}) More varied environments.} We share your enthusiasm about trying more applications. Note however that the driving experiment with a state space of dimension $44$ is already quite ambitious compared to usual experimental settings in similar works, often limited to systems of dimension 2, 3 or 4 [3,4,11,12,17,28,29,34,38].

\end{document}

### 2020-09-03 main.tex
Add author response
Incorporate reviewer comments

@@
 \usepackage{cleveref}
+\usepackage[dvipsnames]{xcolor}
+\usepackage{subfigure}
 
@@
 \input{mathdef.tex}
+\input{style.tex}
 
@@
 In this work, we assume that the system dynamics are partially known, in the form of a linear differential equation with unknown parameters and inputs.
-More precisely, we consider a linear system with state $x\in\Real^p$, acted on by controls $u\in\Real^q$ and perturbations $\omega\in\Real^r$, and following dynamics in the form:
+More precisely, we consider a linear system with state $x\in\Real^p$, acted on by controls $u\in\Real^q$ and disturbances $\omega\in\Real^r$, and following dynamics in the form:
 \begin{equation}
@@
 We adopt a data-driven scheme to estimate the parameters more accurately as we interact with the true system.
-Most model-based reinforcement learning algorithms rely on the estimated dynamics to derive the corresponding optimal controls \citep[e.g.][]{Lenz2015,Levine2015}, but suffer from \emph{model bias}: they ignore the error between the learned and true dynamics, which can dramatically degrade control performances \citep{Schneider1997}.
+Many model-based reinforcement learning algorithms rely on the estimated dynamics to derive the corresponding optimal controls \citep[e.g.][]{Lenz2015,Levine2015}, but suffer from \emph{model bias}: they ignore the error between the learned and true dynamics, which can dramatically degrade control performances \citep{Schneider1997}.
 %It is particularly likely when maximising an objective under constraints, which naturally pushes the systems to operate in the vicinity of constraint saturation and makes it prone to failure.
 
-To address this issue, we turn to the framework of \emph{robust} decision-making: instead of merely considering a point estimate of the dynamics, for any $N\in\Natural$, we build an entire \emph{confidence region} $\cC_{[N],\delta}\subset\Theta$, illustrated in \Cref{fig:estimation}, that contains the true dynamics parameter with high probability:
+To address this issue, we turn to the framework of \emph{robust} decision-making: instead of merely considering a point estimate of the dynamics, for any $N\in\Natural$, we build an entire \emph{confidence region} $\cC_{N,\delta}\subset\Theta$, illustrated in \Cref{fig:estimation}, that contains the true dynamics parameter with high probability:
 \begin{align}
-\probability{\theta\in \cC_{[N],\delta}} \geq 1-\delta,
+\probability{\theta\in \cC_{N,\delta}} \geq 1-\delta,
 \label{eq:confidence}
@@
 where $\delta\in(0,1)$.
-In \Cref{sec:estimation}, having observed a history $\cD_{[N]} = \{(x_n, y_n,u_n)\}_{n\in[N]}$ of transitions, our first contribution extends the work of \citet{Abbasi2011} who provide a confidence ellipsoid for the least-square estimator to our setting of feature matrices, rather than feature vectors.
-
-The \emph{robust control objective} $V^r$ \citep{Bental2009,Bertsimas2011,Gorissen2015} aims to maximise the worst-case outcome with respect to this confidence region $\cC_{[N],\delta}$:
+In \Cref{sec:estimation}, having observed a history $\cD_{N} = \{(x_n, y_n,u_n)\}_{n\in\left[N\right]}$ of transitions, our first contribution extends the work of \citet{Abbasi2011} who provide a confidence ellipsoid for the least-square estimator to our setting of feature matrices, rather than feature vectors.
+
+The \emph{robust control objective} $V^r$ \citep{Bental2009,Bertsimas2011,Gorissen2015} aims to maximise the worst-case outcome with respect to this confidence region $\cC_{N,\delta}$:
 \begin{equation}
 \label{eq:robust-control}
-\sup_{\bu\in{(\Real^q)}^\Natural} {V^r(\bu)}, \qquad \text{ where }\qquad {V^r(\bu)} \eqdef \inf_{\substack{\theta \in \cC_{[N],\delta} \\ \bom\in[\underline{\bom},\overline{\bom}]^\Natural}} \left[\sum_{n=N+1}^\infty \gamma^n R(x_n(\bu,\bom))\right],
-\end{equation}
-$\gamma\in(0,1)$ is a discount factor, and $x_n(\bu,\bom)$ is the state reached at step $n$ under controls $\bu$ and perturbations $\bom$ within the given admissible bounds $[\underline\omega(t),\overline\omega(t)]$.
+\sup_{\bu\in{(\Real^q)}^\Natural} {V^r(\bu)}, \qquad \text{ where }\qquad {V^r(\bu)} \eqdef \inf_{\substack{\theta \in \cC_{N,\delta} \\ \omega\in[\underline{\omega},\overline{\omega}]^\Real}} \left[\sum_{n=N+1}^\infty \gamma^n R(x_n(\bu,\omega))\right],
+\end{equation}
+$\gamma\in(0,1)$ is a discount factor, and $x_n(\bu,\bom)$ is the state reached at step $n$ under controls $\bu$ and disturbances $\omega(t)$ within the given admissible bounds $[\underline\omega(t),\overline\omega(t)]$.
 Maximin problems such as $\eqref{eq:robust-control}$ are notoriously hard if the reward $R$ has a simple form.
@@
 In \Cref{sec:prediction}, we leverage recent results from the uncertain system simulation literature to derive an \emph{interval predictor} $[\underline{x}(t),\overline{x}(t)]$ for the system \eqref{eq:dynamics}, illustrated in \Cref{fig:prediction}.
-For any $N\in\Natural$, this predictor takes the information on the current state ${x}_N$, the confidence region $\cC_{[N],\delta}$, planned control sequence $\bu$ and admissible perturbation bounds $[\underline{\omega}(t),\overline{\omega}(t)]$; and must verify the \emph{inclusion property}:
+For any $N\in\Natural$, this predictor takes the information on the current state ${x}_N$, the confidence region $\cC_{N,\delta}$, planned control sequence $\bu$ and admissible disturbance bounds $[\underline{\omega}(t),\overline{\omega}(t)]$; and must verify the \emph{inclusion property}:
 \begin{equation}
@@
 This discretisation induces a suboptimality, but it can be mitigated by diversifying the controller basis.
-The robust objective \eqref{eq:robust-control} becomes $\sup_{\ba\in{\cA}^\Natural} V^r(\ba)$, where $x_n(\ba, \bom)$ stems from \eqref{eq:dynamics} with $u_n = \pi_{a_n}(x_n)$.
+The robust objective \eqref{eq:robust-control} becomes $\sup_{\ba\in{\cA}^\Natural} V^r(\ba)$, where $x_n(\ba, \omega)$ stems from \eqref{eq:dynamics} with $u_n = \pi_{a_n}(x_n)$.
 However, tree-based planning algorithms are designed for a single known generative model rather than a confidence region for the system dynamics.
 Our third contribution adapts them to the robust objective \eqref{eq:robust-control} by approximating it with a tractable surrogate $\hat{V}^r$ that exploits the interval predictions \eqref{eq:inclusion-property} to define a pessimistic reward.
-In our main result, we show that the best surrogate performance achieved during planning is guaranteed to be attained on the true system, and provide an upper bound for the approximation gap and simple regret of our framework in \Cref{thm:control-error}.
+In our main result, we show that the best surrogate performance achieved during planning is guaranteed to be attained on the true system, and provide an upper bound for the approximation gap and simple regret of our framework in \Cref{thm:minimax-regret-bound}.
 This is the first result of this kind for maximin control with generic costs to the best of our knowledge.
@@
 		\includegraphics[trim={1cm 0 0 0}, clip, width=0.6\linewidth]{img/ellipsoid}
-		\caption{The model estimation procedure, running on the obstacle avoidance problem of \Cref{sec:experiments}. The confidence region $C_{[N],\delta}$ shrinks with the number of samples $N$.}
+		\caption{The model estimation procedure, running on the obstacle avoidance problem of \Cref{sec:experiments}. The confidence region $C_{N,\delta}$ shrinks with the number of samples $N$.}
 		\label{fig:estimation}
@@
 		\FOR{$N = 0,1,2,\dots$} 
-		\STATE $\cC_{[N],\delta} \gets$\textsc{Model Estimation}$(\cD_{[N]})$. \eqref{eq:polytope}
+		\STATE $\cC_{N,\delta} \gets$\textsc{Model Estimation}$(\cD_{N})$. \eqref{eq:polytope}
 		\FOR{each planning step $k\in\{N,\dots,N+K\}=N+[K]$}
-		\STATE $[\underline{x}_{k+1}, \overline{x}_{k+1}]\gets$ \textsc{Interval Prediction}($\cC_{[N],\delta}, \ba_kb$) for each action $b\in \cA$. \eqref{eq:interval-predictor}
+		\STATE $[\underline{x}_{k+1}, \overline{x}_{k+1}]\gets$ \textsc{Interval Prediction}($\cC_{N,\delta}, \ba_kb$) for each action $b\in \cA$. \eqref{eq:interval-predictor}
 
@@
 
-\textbf{Finite states} ~~ Minimax control of finite Markov Decision Processes with uncertain parameters was studied in \citep{Iyengar2005,Nilim2005,Wiesemann2013}, who showed that the main results of Dynamic Programming can be extended to their robust counterparts only when the dynamics ambiguity set verifies a certain rectangularity property.
+\paragraph{Finite states} Minimax control of finite Markov Decision Processes with uncertain parameters was studied in \citep{Iyengar2005,Nilim2005,Wiesemann2013}, who showed that the main results of Dynamic Programming can be extended to their robust counterparts only when the dynamics ambiguity set verifies a certain rectangularity property.
 Since we consider continuous states, these methods do not apply.
 
-\textbf{Linear dynamics and quadratic costs} ~~ Several approaches have been proposed for cumulative regret minimisation in the LQ problem.
+\paragraph{Linear dynamics and quadratic costs} Several approaches have been proposed for cumulative regret minimisation in the LQ problem.
 In the \emph{Optimism in the Face of Uncertainty} paradigm, the best possible dynamics within a high-confidence region is selected under a controllability constraint, to compute the corresponding optimal control in closed-form by solving a Riccati equation.
@@
 \paragraph{Regularised least square} To derive an estimate on $\theta$, we consider the $L_2$-regularised regression problem with weights $\Sigma_p\in\Real^{p\times p}$ and $\lambda\in\Real^+_*$:\hfill
-$
+$$
 %    \label{eq:regression_min}
@@
     \refstepcounter{equation}~(\theequation)\label{eq:regression_min}
-$
+$$
 
@@
 %
-%In particular, we denote the coefficient-wise bounds over perturbations as $\underline{\omega}(t) \leq \omega(t) \leq \overline{\omega}(t)$.
-This is a deterministic assumption, then by Hölder inequality a confidence region $\cC_{[N],0}$ can be derived based on a $L_1$-ball estimate of $\theta$ at time $N$, i.e.
+%In particular, we denote the coefficient-wise bounds over disturbances as $\underline{\omega}(t) \leq \omega(t) \leq \overline{\omega}(t)$.
+This is a deterministic assumption, then by Hölder inequality a confidence region $\cC_{N,0}$ can be derived based on a $L_1$-ball estimate of $\theta$ at time $N$, i.e.
 a polytope with $2d$ vertices:
@@
 
-\begin{assumption}[Sub-Gaussian Noise]
+\begin{assumption}[Noise Model]
 \label{assumpt:gaussian-noise}
-At each time $t\geq0$ the noise $\eta(t)$ is an independent sub-Gaussian noise with covariance proxy $\Sigma_p \in \Real^{p\times p}$:
-$
-    \forall u\in\Real^p,\, \expectedvalue \left[ \exp{\left( u^\transp \eta(t)\right)}\right] \leq \exp{\left( \frac{1}{2} u^\transp \Sigma_p u\right)}.
-$
+We assume that
+\begin{enumerate}
+	\item at each time $t\geq0$, the combined noise $\eta(t)$ is an independent sub-Gaussian noise with covariance proxy $\Sigma_p \in \Real^{p\times p}$:
+	$$
+	\forall u\in\Real^p,\; \expectedvalue \left[ \exp{\left( u^\transp \eta(t)\right)}\right] \leq \exp{\left( \frac{1}{2} u^\transp \Sigma_p u\right)};
+	$$
+	\item at each time $t\geq0$, the disturbance $\omega(t)$ is enclosed by \emph{known} bounds $\underline{\omega}(t) \leq \omega(t) \leq \overline{\omega}(t)$, whose amplitude verifies $\sum_{n=0}^\infty \gamma^n C_\omega(t_n) < \infty$, where $$C_\omega(t) \eqdef \sup_{\tau\in[0,t]} \|\overline{\omega}(\tau) - \underline{\omega}(\tau)\|_2.$$
+\end{enumerate}
+
 \end{assumption}
-For instance, it is the case when $\nu$ and $\omega$ are bounded or Gaussian noises.
-
-\textbf{Remark} ~ In the objective \eqref{eq:robust-control}, we use local bounds  $\underline{\omega}(t)\leq \omega(t) \leq \overline{\omega}(t)$ that hold with confidence $\delta_n = \frac{\delta}{n(n+1)}$, so that the event $\{\forall n, \underline{\omega}(t_n) \leq \omega(t_n) \leq \overline{\omega}(t_n)\}$ holds with probability $1-\delta$.
-%Note that \Cref{assumpt:bounded-noise} implies that $\eta$ is sub-Gaussian with covariance proxy $\Sigma_p=\|\eta\|_\infty I_p$.
 
@@
 
-We convert this confidence ellipsoid $\cC_{[N],\delta}$ from \eqref{eq:confidence-ellipsoid} into a polytope for $A(\theta)$.
+We convert this confidence ellipsoid $\cC_{N,\delta}$ from \eqref{eq:confidence-ellipsoid} into a polytope for $A(\theta)$.
 For simplicity, we present here a simple but coarse strategy: bound the ellipsoid by its enclosing axis-aligned hypercube:
@@
     \label{eq:polytope}
-     A(\theta)\in \left\{ A_0 +\sum_{i=1}^{2^d}\alpha_{i}\Delta A_{i}: \alpha\geq 0,  \sum_{i=1}^{2^d}\alpha_{i}=1\right\} \text{ where } A_0 = A + \theta_{N,\lambda}^\transp\phi,\; h_i\in\{-1,1\}^d,
+     A(\theta)\in \left\{ A_N +\sum_{i=1}^{2^d}\alpha_{i}\Delta A_{N,i}: \alpha\geq 0,  \sum_{i=1}^{2^d}\alpha_{i}=1\right\}
 \end{align}
-$\Delta A_{i} = {h_i} \sqrt{\frac{\beta_N(\delta)}{\lambda_{\max}(G_{N,\lambda})}}$.
+where $A_N = A(\theta_{N,\lambda}),\; h_i\in\{-1,1\}^d,\; \Delta A_{N,i} = {h_i} \sqrt{\frac{\beta_N(\delta)}{\lambda_{\max}(G_{N,\lambda})}}$.
 A tighter polytope derivation is presented in the Supplementary Material.
@@
 %$
-A simple solution to \eqref{eq:inclusion-property} is proposed in \citep{Efimov2012}, where, given bounds $\underline{A}\leq A(\theta)\leq\overline{A}$ from $\cC_{[N],\delta}$ they use matrix interval arithmetic to derive the predictor:
+A simple solution to \eqref{eq:inclusion-property} is proposed in \citep{Efimov2012}, where, given bounds $\underline{A}\leq A(\theta)\leq\overline{A}$ from $\cC_{N,\delta}$ they use matrix interval arithmetic to derive the predictor:
 \begin{proposition}[Simple predictor of \citealt{Efimov2012}]
@@
 \label{assumpt:metzler}
-There exists an orthogonal matrix $Z\in\Real^{p\times p}$ such that $Z^\transp A_0 Z$ is Metzler\footnote{We say that a matrix is Metzler when all its non-diagonal coefficients are non-negative.}.
+There exists an orthogonal matrix $Z\in\Real^{p\times p}$ such that $Z^\transp A_N Z$ is Metzler\footnote{We say that a matrix is Metzler when all its non-diagonal coefficients are non-negative.}.
 \end{assumption}
-In practice, this assumption is often verified: it is for instance the case whenever $A_0$ is diagonalisable.
+In practice, this assumption is often verified: it is for instance the case whenever $A_N$ is diagonalisable.
 The similarity transformation of \citep{Efimov2013} provides a method to compute such $Z$ when the system is observable.
@@
 Denote $
-\Delta A_{+}=\sum_{i=1}^{2^d}\Delta A_{i}^{+},\;\Delta A_{-}=\sum_{i=1}^{2^d}\Delta A_{i}^{-}$.
-% The similarity transformation of \citep{Efimov_a2013} provides a method to compute such $P$ whenever there exist $C_1,C_2$ which make $(A(\theta), C_1)$ and $(A_0, C_2)$ observable.
-% Under this assumption, without loss of generality up to a change of basis $x\rightarrow P^{-1}x$ that we do not write for the sake of readability, this assumption is equivalent to considering that $A_0$ itself is Metzler.
+\Delta A_{+}=\sum_{i=1}^{2^d}\Delta A_{N,i}^{+},\;\Delta A_{-}=\sum_{i=1}^{2^d}\Delta A_{N,i}^{-}$.
+% The similarity transformation of \citep{Efimov_a2013} provides a method to compute such $P$ whenever there exist $C_1,C_2$ which make $(A(\theta), C_1)$ and $(A_N, C_2)$ observable.
+% Under this assumption, without loss of generality up to a change of basis $x\rightarrow P^{-1}x$ that we do not write for the sake of readability, this assumption is equivalent to considering that $A_N$ itself is Metzler.
 
@@
 \begin{eqnarray}
-\dot{\underline{x}}(t) & = & A_{0}\underline{x}(t)-\Delta A_{+}\underline{x}^{-}(t)-\Delta A_{-}\overline{x}^{+}(t)  +Bu(t)+D^{+}\underline{\omega}(t)-D^{-}\overline{\omega}(t),\label{eq:interval-predictor}\\
-\dot{\overline{x}}(t) & = & A_{0}\overline{x}(t)+\Delta A_{+}\overline{x}^{+}(t)+\Delta A_{-}\underline{x}^{-}(t)  +Bu(t)+D^{+}\overline{\omega}(t)-D^{-}\underline{\omega}(t),\nonumber
+\dot{\underline{x}}(t) & = & A_{N}\underline{x}(t)-\Delta A_{+}\underline{x}^{-}(t)-\Delta A_{-}\overline{x}^{+}(t)  +Bu(t)+D^{+}\underline{\omega}(t)-D^{-}\overline{\omega}(t),\label{eq:interval-predictor}\\
+\dot{\overline{x}}(t) & = & A_{N}\overline{x}(t)+\Delta A_{+}\overline{x}^{+}(t)+\Delta A_{-}\underline{x}^{-}(t)  +Bu(t)+D^{+}\overline{\omega}(t)-D^{-}\underline{\omega}(t),\nonumber
 \end{eqnarray}
@@
 
-\begin{proposition}[Lower bound]
+\begin{theorem}[Lower bound]
 \label{prop:lower-bound}
 The surrogate objective  \eqref{eq:surrogate-objective} is a lower bound of the objective  \eqref{eq:robust-control}.
-%\begin{equation*}
-%\hat{V}^r(\bu) \leq V^r(\bu)
-%\end{equation*}
-\end{proposition}
+\begin{equation*}
+\hat{V}^r(\bu) \leq V^r(\bu)
+\end{equation*}
+\end{theorem}
 Consequently, since all our approximations are conservative, if we manage to find a control sequence such that no \textit{``bad event''} (e.g.
-a collision) happens according to the surrogate objective $\hat{V}^r$, they are guaranteed not to happen either when the controls are executed on the true system.
-
-To optimise $\hat{V}^r$ in \eqref{eq:surrogate-objective}, we cannot use DP algorithms since the state space is continuous and the pessimistic rewards are non-Markovian.
-Instead, we turn to tree-based planning algorithms, which optimise a sequence of actions based on the corresponding sequence of rewards, without requiring Markovity nor state enumeration.
+a collision) happens according to the surrogate objective $\hat{V}^r$, they are \emph{guaranteed} not to happen either when the controls are executed on the true system.
+
+To maximise $\hat{V}^r$, we cannot use DP algorithms since the state space is continuous and the pessimistic rewards are non-Markovian.
+Rather, we turn to tree-based planning algorithms, which optimise a sequence of actions based on the corresponding sequence of rewards, without requiring Markovity nor state enumeration.
 In particular, we consider the \emph{Optimistic Planning of Deterministic Systems} (\texttt{OPD}) algorithm \citep{Hren2008} tailored for the case when the relationship between actions and rewards is deterministic.
-Indeed, the stochasticity of the perturbations and measurements is encased in $\hat{V}^r$: given the observations up to time $N$ both the predictor dynamics \eqref{eq:interval-predictor} and the pessimistic rewards in \eqref{eq:surrogate-objective} are deterministic.
+Indeed, the stochasticity of the disturbances and measurements is encased in $\hat{V}^r$: given the observations up to time $N$ both the predictor dynamics \eqref{eq:interval-predictor} and the pessimistic rewards in \eqref{eq:surrogate-objective} are deterministic.
 At each planning iteration $k\in[K]$, \texttt{OPD} progressively builds a tree $\cT_{k+1}$ by forming upper-bounds $B_a(k)$ over the value of sequences of actions $a$, and expanding\footnote{The expansion of a leaf node $a$ refers to the simulation of its children transitions $aA = \{ab, b\in A\}$} the leaf $a_k$ with highest upper-bound:
@@
 where $\cL_k$ is the set of leaves of $\cT_k$, $h(a)$ is the length of the sequence $a$, and $\underline{R}_n(a)$ the pessimistic reward \eqref{eq:surrogate-objective} obtained at time $n$ by following the controls $u_n = \pi_{a_n}(x_n)$.
-\begin{theorem}[Planning performance of \citealt{Hren2008}]
+\begin{lemma}[Planning performance of \citealt{Hren2008}]
 \label{theorem:opd-regret}
-The simple regret of the \texttt{OPD} algorithm \eqref{eq:opd} applied to the surrogate objective \eqref{eq:surrogate-objective} after $K$ planning iterations is:
-$
-\hat{V}^r(a^{\star}) - \hat{V}^r({a_K}) = \cO\left(K^{-\frac{\log 1/\gamma}{\log \kappa}}\right);
-$
+The suboptimality of the \texttt{OPD} algorithm \eqref{eq:opd} applied to the surrogate objective \eqref{eq:surrogate-objective} after $K$ planning iterations is:
+$$
+\hat{V}^r(a_{\star}) - \hat{V}^r({a_K}) = \cO\left(K^{-\frac{\log 1/\gamma}{\log \kappa}}\right);
+$$
 where $\kappa \eqdef \limsup_{h\rightarrow\infty} \left|\left\{a\in A^h: \hat{V}^r(a)\geq \hat{V}^r(a^{\star}) - \frac{\gamma^{h+1}}{1-\gamma}\right\}\right|^{1/h}$ is a problem-dependent measure of the proportion of near-optimal paths.
+\end{lemma}
+
+Hence, by using enough computational budget $K$ for planning we can get as close as we want to the optimal surrogate value $\hat{V}^r(a^{\star})$, at a polynomial rate.
+Unfortunately, there exists a gap between $\hat{V}^r$ and the true robust objective $V^r$, which stems from three approximations: (i) the true reachable set was approximated by an enclosing interval in \eqref{eq:inclusion-property}; (ii) the time-invariance of the dynamics uncertainty $A(\theta)\in\cC_{N,\delta}$ was handled by the interval predictor \eqref{eq:interval-predictor} as if it were a time-varying uncertainty $A(\theta(t))\in\cC_{N,\delta},\forall t$ ; and (iii) the lower-bound $\sum\min\leq \min\sum$ used to define the surrogate objective \eqref{eq:surrogate-objective} is not tight.
+However, this gap can be bounded under additional assumptions.
+
+\begin{theorem}[Suboptimality bound]
+	\label{thm:minimax-regret-bound}
+		Under two conditions:
+		\begin{enumerate}
+			\item a Lipschitz regularity assumption for the reward function $R$:
+			\item a stability condition: there exist $P>0,Q_0\in\Real^{p\times p}$, $\rho>0$, and $N_0\in\Natural$ such that
+			$$\forall N>N_0,\quad \begin{bmatrix}
+			A_N^\transp P + P A_N^\transp + Q_0 & P|D|  \\
+			|D|^\transp P & -\rho I_r \\
+			\end{bmatrix}< 0;$$
+		\end{enumerate}
+		we can bound the suboptimality of \Cref{alg:full} with planning budget $K$ as:
+		\begin{equation*}
+		V(a_\star) - \hat{V}^r(a_K) \leq  \hlr{\underbrace{\Delta_\omega}_{\substack{\text{robustness to}\\ \text{disturbances}}}} + \hlb{\underbrace{\cO\left(\frac{\beta_N(\delta)^2}{\lambda_{\min}(G_{N,\lambda})}\right)}_{\text{estimation error}}} + \hlg{\underbrace{\cO\left(K^{-\frac{\log 1/\gamma}{\log \kappa}}\right)}_{\text{planning error}}}
+		\end{equation*}
+		with probability at least $1-\delta$, where $V(a)$ is the optimal expected return after executing an action $a\in\cA$, $a_\star$ is an optimal action, and $\hlr{\Delta_\omega}$ is a constant which corresponds to an irreducible suboptimality suffered from being robust to instantaneous disturbances $\omega(t)$.
 \end{theorem}
 
-Hence, by using enough computational budget $K$ for planning we can get as close as we want to the optimal surrogate value $\hat{V}^r(a^{\star})$, at a polynomial rate.
-Unfortunately, there exists a gap between $\hat{V}^r$ and the true robust objective $V^r$, which stems from three approximations: (i) the true reachable set was approximated by an enclosing interval in \eqref{eq:inclusion-property}; (ii) the time-invariance of the dynamics uncertainty $A(\theta)\in\cC_{[N],\delta}$ was handled by the interval predictor \eqref{eq:interval-predictor} as if it were a time-varying uncertainty $A(\theta(t))\in\cC_{[N],\delta},\forall t$ ; and (iii) the lower-bound $\sum\min\leq \min\sum$ used to define the surrogate objective \eqref{eq:surrogate-objective} is not tight.
-However, this gap can be bounded under additional assumptions.
-\begin{theorem}[Regret bound]
-\label{thm:control-error}
-Under three conditions:
-\begin{enumerate}[nosep]
-	\item a Lipschitz regularity assumption for the reward $R$;
-	\item a persistent excitation assumption:
-	$
-	\exists \underline{\phi},\overline{\phi}>0: \forall n\geq n_0,\quad \underline{\phi}^2 \leq \lambda_{\min}(\Phi_{n}^\transp\Sigma_{p}^{-1}\Phi_{n}) \leq \overline{\phi}^2;
-	$
-	\item a stability condition: there exist $P>0,Q_0\in\Real^{p\times p}$, $\rho>0$ such that
-	$\begin{bmatrix}
-		A_0^\transp P + P A_0^\transp + Q_0 & P|D|  \\
+This bound contains an input-dependent \hlb{estimation error} term, which can be further bounded under an additional assumption that the features are sufficiently excited.
+
+\begin{corollary}[Asymptotic near-optimality]
+	\label{cor:pe}
+		Under an additional persistent excitation (PE) assumption
+		\begin{align}
+		\label{eq:pe}
+		\exists \underline{\phi},\overline{\phi}>0: \forall n\geq n_0,\quad \underline{\phi}^2 \leq \lambda_{\min}(\Phi_{n}^\transp\Sigma_{p}^{-1}\Phi_{n}) \leq \overline{\phi}^2,
+		\end{align} the stability condition 2. of \Cref{thm:minimax-regret-bound} can be relaxed to its limit: there exist $P,Q_0,\rho$ such that
+		$$\begin{bmatrix}
+		A(\theta)^\transp P + P A(\theta)^\transp + Q_0 & P|D|  \\
 		|D|^\transp P & -\rho I_r \\
-	\end{bmatrix}< 0;$
-\end{enumerate}
- we can bound the approximation error of \Cref{alg:full}:
+		\end{bmatrix}< 0;$$
+		and the suboptimality bound takes the more explicit form
 		\begin{equation*}
-\hat{V}^r(\bu) \leq {V}^r(\bu) \leq V(\bu) \leq \hat{V}^r(\bu) + \Delta_\omega + \cO\left({\log N / N}\right)
+		V(a_\star) - \hat{V}^r(a_K) \leq  \hlr{{\Delta_\omega}} + \hlb{{\cO\left(\frac{\log\left(N^{d/2}/\delta\right)}{N}\right)}} + \hlg{{\cO\left(K^{-\frac{\log 1/\gamma}{\log \kappa}}\right)}} 
 		\end{equation*}
-with probability at least $1-\delta$, where $\Delta_\omega$ is a constant which corresponds to an irreducible suboptimality suffered from being robust to instantaneous perturbations $\omega(t)$.
-\end{theorem}
+		which ensures asymptotic near-optimality when $N\to\infty$ and $K\to\infty$.
+\end{corollary}
 
@@
 
-\textbf{Model adequacy}~~~
+\paragraph{Model adequacy}
 One of the major benefits of using the family of linear models, compared to richer model classes, is that they provide strict conditions allowing to quantify the adequacy of the modelling assumptions to the observations.
 Given $N-1$ observations, \Cref{sec:estimation} provides a polytopic confidence region \eqref{eq:polytope} that contains $A(\theta)$ with probability at least $1-\delta$.
-Since the dynamics are linear, we can propagate this confidence region to the next observation: $y_{N}$ must belong to the Minkowski sum of a polytope representing model uncertainty $\cP(A_{0} x_N + Bu_N, \Delta A_{1}x_N,\dots, \Delta A_{2^d}x_N)$ and a polytope $\cP(0_p, \underline{\eta}, \overline{\eta})$ bounding the perturbation and measurement noises.
+Since the dynamics are linear, we can propagate this confidence region to the next observation: $y_{N}$ must belong to the Minkowski sum of a polytope representing model uncertainty $\cP(A_{0} x_N + Bu_N, \Delta A_{1}x_N,\dots, \Delta A_{2^d}x_N)$ and a polytope $\cP(0_p, \underline{\eta}, \overline{\eta})$ bounding the disturbance and measurement noises.
 \citet{delos2015} provide a way to test this membership in polynomial time using linear programming.
@@
 
-\textbf{Robust selection}~~~
+\paragraph{Robust selection}
 We temporarily ignore the parametric uncertainty on $\theta$ to simply consider several candidate dynamics models, which all correspond to different modelling assumptions.
@@
 The true dynamics $f$ lies within a finite set of candidate models $f^1, \dots, f^M$:
-$
-\qquad\qquad
+$$
 \exists m\in[M]: \dot{x}(t) = f^m(x(t), u(t)), \forall t\geq 0.
-$
+$$
 \end{assumption}
@@
 
-\begin{definition}[Robust sequence upper bounds] We replace the upper-bound \eqref{eq:opd} on sequence values in \texttt{OPD} by: \hfill
-$
+\begin{definition}[Robust sequence upper bounds] We replace the upper-bound \eqref{eq:opd} on sequence values in \texttt{OPD} by:
+$$
 %\label{eq:robust-b-values}
 B_a^r(k)  \eqdef \min_{m\in[M]} \sum_{n=0}^{h-1} \gamma^n R_n^m  + \frac{\gamma^h}{1-\gamma}. \refstepcounter{equation}\hfill(\theequation)\label{eq:robust-b-values}
-$
+$$
 \end{definition}
@@
 
-\begin{theorem}[Robust planning performance]
+\begin{proposition}[Robust planning performance]
 \label{theorem:drop-regret}
 The robust version of \texttt{OPD} \eqref{eq:robust-b-values} enjoys the same regret bound as \texttt{OPD} in \Cref{theorem:opd-regret}, with respect to the multi-model objective \eqref{eq:robust-objective-discrete}.
-\end{theorem}
+\end{proposition}
 
 This result is of independent interest: the solution of a robust objective \eqref{eq:robust-objective-discrete} with discrete ambiguity $f\in\{f^m\}_{m\in[M]}$ can be recovered exactly, asymptotically when the planning budget $K$ goes to infinity, which Robust DP algorithms do not allow.
-This also contrasts with the results obtained in \Cref{sec:control} for the robust objective \eqref{eq:robust-control} with continuous ambiguity $A(\theta)\in\cC_{[N],\delta}$, for which \texttt{OPD} only recovers the surrogate approximation $\hat{V}^r$, as discussed in \Cref{thm:control-error}.
+This also contrasts with the results obtained in \Cref{sec:control} for the robust objective \eqref{eq:robust-control} with continuous ambiguity $A(\theta)\in\cC_{N,\delta}$, for which \texttt{OPD} only recovers the surrogate approximation $\hat{V}^r$, as discussed in \Cref{thm:minimax-regret-bound}.
 Note that here the regret depends on the number $K$ of node expansions, but each expansion now requires $M$ times more simulations than in the single-model setting.
@@
 
-\textbf{Obstacle avoidance with unknown friction}~~~
+\paragraph{Obstacle avoidance with unknown friction}
 We first consider a simple illustrative example, shown in \Cref{fig:prediction}: the control of a 2D system %with position $(p_x,p_y)$ and velocity $(v_x, v_y)$ 
@@
 For the reasons mentioned above, no robust baseline applies to our setting.
-Rather than comparing \Cref{alg:full} to RL baselines which inevitably commit many failures, we consider the nominal agent i.e.
-the non-robust adaptive control approach that plans with the estimated dynamics $\theta_{[N],\lambda}$, and thus enjoys the same prior knowledge of dynamics structure and reward.
+We compare \Cref{alg:full} to the non-robust adaptive control approach that plans with the estimated dynamics $\theta_{N,\lambda}$, and thus enjoys the same prior knowledge of dynamics structure and reward.
 This highlights the benefits of the robust formulation solely rather than stemming from algorithm design.
-The results of 100 simulations are shown in \Cref{tab:obstacle}: the robust agent performs worse than the nominal agent on average, but manages to ensure safety and attains a better worst-case performance.
+We show in \Cref{tab:obstacle} the results of 100 simulations of a single episode: the robust agent performs worse than the nominal agent on average, but manages to ensure safety and attains a better worst-case performance.
+We also compare to a standard model-free approach, DQN, which does not benefit from the prior knowledge on the system dynamics, and is instead trained over multiple episodes.
+The reported performance is that of the final policy obtained after training for 3000 episodes, during which $897\pm64$ collisions occurred ($29.9\pm2.1$\%).
 We also study the evolution of the simple regret $V(x_N) - \hat{V}^r(x_N)$ with respect to the number of samples $N$, by comparing the empirical returns from a state $x_N$ to the value $V(x_N)$ that the agent would get by acting optimally from $x_N$ with knowledge of the dynamics.
-Although the assumptions of \Cref{thm:control-error} are not satisfied (e.g.
-non-smooth reward), the mean regret of the robust agent, shown in \Cref{fig:regret}, still decreases polynomially with $N$: \Cref{alg:full} gets more efficient as it is more confident while ensuring safety at all time.
+Although the assumptions of \Cref{thm:minimax-regret-bound} are not satisfied (e.g.
+non-smooth reward), the mean regret of the robust agent, shown in \Cref{fig:regret}, still decreases polynomially with $N$: \Cref{alg:full} gets \emph{more efficient} as it is \emph{more confident} while \emph{ensuring safety} at all time.
 In contrast, the nominal agent has a smaller average regret but collides with obstacles in $4\%$ of simulations.
@@
 \begin{table}[tbp]
-
-\parbox{.49\linewidth}{
+\caption{Frequency of collision, minimum and average return achieved on a single episode, repeated with 100 random seeds.
+In both tasks, the robust agent performs worse than the nominal agent on average, but manages to ensure safety and attains a better worst-case performance.}
+\subfigure[Performances on the obstacle task]{
 	\centering
-	\caption{Performances on the obstacle task}
 	\label{tab:obstacle}
-
 	\begin{tabular}{lccc}
@@
 		\Cref{alg:full} & \textbf{0\%} & \textbf{10.4} & {$13.0 \pm 1.5$} \\
+		\midrule
+		DQN (trained) & 6\% & 1.7 & $12.3\pm2.5$ \\
 		\bottomrule
@@
 }
-\hfill
-\parbox{.49\linewidth}{
-
-	\caption{Performances on the driving task}
+\subfigure[Performances on the driving task]{
 	\label{tab:driving}
@@
 		{Nominal 1} & 4\% & {5.2} & $\mathbf{7.3} \pm 1.5$ \\
-		{Nominal 2} & 33\% & {3.5} & $6.4 \pm 0.26$ \\
-		\Cref{alg:full} & \textbf{0\%} & \textbf{6.8} & $7.1 \pm 0.29$ \\
+		{Nominal 2} & 33\% & {3.5} & $6.4 \pm 0.3$ \\
+		\Cref{alg:full} & \textbf{0\%} & \textbf{6.8} & $7.1 \pm 0.3$ \\
+		\midrule
+		DQN (trained) & 3\% & 5.4 & $6.3\pm0.6$ \\
 		\bottomrule
@@
 }
+
 \end{table}
 
-\textbf{Motion planning for an autonomous vehicle}~~~
+\paragraph{Motion planning for an autonomous vehicle}
 We consider the \href{https://github.com/eleurent/highway-env}{highway-env} environment \citep{highway-env} for simulated driving decision problems.
@@
 Since these intentions are unknown to the agent, we adopt the multi-model perspective of \Cref{sec:multi-model} and consider one model per possible route for every observed vehicle before an intersection.
-In \Cref{tab:driving}, we compare \Cref{alg:full} to a nominal agent planning with the estimated parameter $\theta_{[N],\lambda}$, with two different modelling assumptions: we assume that Nominal 1 has access to the true followed route for each vehicle, while Nominal 2 does not and picks the model with minimal prediction error.
-Again, the robust approach is less efficient on average than planning with a nominal model, but it does better in terms of worst-case performance and manages to avoid collisions, contrary to the nominal baselines that suffer from model bias.
+In \Cref{tab:driving}, we compare \Cref{alg:full} to a nominal agent planning with the estimated parameter $\theta_{N,\lambda}$, with two different modelling assumptions: we assume that Nominal 1 has access to the true followed route for each vehicle, while Nominal 2 does not and picks the model with minimal prediction error.
+As before, the robust approach is less efficient on average than planning with a nominal model, but it does better in terms of worst-case performance and manages to avoid collisions, contrary to the nominal baselines that suffer from model bias.
+Again, we also compare to the final policy of a DQN baseline trained over 3000 episodes, causing $1058\pm113$ collisions while training ($35\pm4\%$).
 We provide more details about the system and videos of the experiments in the Supplementary Material.
-
-%
-%\begin{table}[t]
-%	\caption{Performances on the driving task}
-%	\label{tab:driving}
-%	\centering
-%	\begin{tabular}{lccc}
-%		\toprule
-%		Agent &
-%		failures &
-%        min return &
-%		mean return $\pm$ std  \\
-%		\midrule
-%		Oracle & 0\% & {6.9} & $7.4 \pm 0.5$ \\
-%		\midrule
-%		{Nominal 1} & 4\% & {5.2} & $\mathbf{7.3} \pm 1.5$ \\
-%		{Nominal 2} & 33\% & {3.5} & $6.4 \pm 0.26$ \\
-%		\Cref{alg:full} & \textbf{0\%} & \textbf{6.8} & $7.1 \pm 0.29$ \\
-%		\bottomrule
-%	\end{tabular}
-%\end{table}
 
@@
 
+%\begin{comment}
 \clearpage
@@
 	The predictor designed in \Cref{sec:prediction} verifies the inclusion property \eqref{eq:inclusion-property}.
-Thus, for sequence of controls $\bu$, any dynamics $A(\theta)\in C_{[N],\delta}$, and perturbations $\underline{\bom} \leq \bom \leq \overline{\bom}$, the corresponding state at time $t_n$ is bounded by $\underline{x}_n \leq x_n \leq \overline{x}_n$, which implies that $R(x_n) \geq \min_{x\in[\underline{x}_n(\bu), \overline{x}_n(\bu)]}  R(x) = \underline{R}_n(\bu)$.
-
-	Thus, by taking the min over $C_{[N],\delta}$ and $[\underline{\bom}, \overline{\bom}]$, we also have for any sequence of controls $\bu$:
-	\begin{align*}
-	    V^r(\bu) &= \min_{\substack{A(\theta)\in C_{[N],\delta}\\ \underline{\bom} \leq \bom \leq \overline{\bom}}} \sum_{n=N+1}^\infty \gamma^n R(x_n)\\
+Thus, for sequence of controls $\bu$, any dynamics $A(\theta)\in C_{N,\delta}$, and disturbances $\underline{\bom} \leq \bom \leq \overline{\bom}$, the corresponding state at time $t_n$ is bounded by $\underline{x}_n \leq x_n \leq \overline{x}_n$, which implies that $R(x_n) \geq \min_{x\in[\underline{x}_n(\bu), \overline{x}_n(\bu)]}  R(x) = \underline{R}_n(\bu)$.
+
+	Thus, by taking the min over $C_{N,\delta}$ and $[\underline{\bom}, \overline{\bom}]$, we also have for any sequence of controls $\bu$:
+	\begin{align*}
+	    V^r(\bu) &= \min_{\substack{A(\theta)\in C_{N,\delta}\\ \underline{\bom} \leq \bom \leq \overline{\bom}}} \sum_{n=N+1}^\infty \gamma^n R(x_n)\\
 	    &\geq \sum_{n=N+1}^\infty \gamma^n \underline{R}_n(\bu)\\
@@
 
-\subsection{Proof of \Cref{thm:control-error}}
-
+\subsection{Proof of \Cref{thm:minimax-regret-bound}}
+\label{sec:proof-minimax-regret-bound}
 We first bound the model estimation error.
 \begin{lemma}
-If the features $\Phi_n$ are persistently exciting:
-\begin{align}
-\label{eq:excitation}
-\exists \underline{\phi},\overline{\phi}>0, n_0: \forall n\geq n_0,\nonumber\\ \underline{\phi}^2 \leq \lambda_{\min}(\Phi_{n}^\transp\Sigma_{p}^{-1}\Phi_{n}) \leq \overline{\phi}^2,
-\end{align}
-then,
-\[\|A(\theta) - A(\theta_{[N],\lambda})\|_2 = \cO\left( \sqrt{\frac{\log N}{N}} \right) \]
+	\label{lem:dynamics-est-bound}
+		\[\|A(\theta) - A(\theta_{N,\lambda})\|_F = \cO\left(\sqrt{ {\frac{\beta_N(\delta)^2}{\lambda_{\min}(G_{N,\lambda})}}}\right) \]
 \end{lemma}
 \begin{proof}
-By \eqref{eq:vector_rls} and \eqref{eq:excitation}, we have $$\lambda_{\min}(G_{[N],\lambda,i,j}) \geq (N-n_0)\underline{\phi}^2 + \sum_{n<n_0}\Phi_{n}^\transp\Sigma_{p}^{-1}\Phi_{n}$$
-
-Hence, by \eqref{eq:confidence-ellipsoid} we have 
-\begin{align*}
-	\|\theta - \theta_{[N],\lambda}\|_{G_{[N],\lambda}} \geq (\sqrt{N}\underline{\phi} + \cO(1))\|\theta - \theta_{[N],\lambda}\|_{2}
-\end{align*}
-and \eqref{eq:confidence-ellipsoid} gives
-
-\begin{align*}
-\beta_N(\delta) &= \sqrt{2\ln \left(\frac{\det(G_{N,\lambda})^{1/2}}{\delta\det(\lambda I_d)^{1/2}}\right)}
-+ (\lambda d)^{1/2}S\\
-&\leq \sqrt{d\log (N\overline{\phi}^2) / \lambda^{d/2}} + \cO(1)
-\end{align*}
-Thus,
-\[\|\theta - \theta_{[N],\lambda}\|_{2} = \cO\left( \sqrt{\frac{\log N}{N}} \right) \]
-
-And $A(\theta)$ belongs to a linear image of this $L^2$-ball. By writing a the $j^{th}$ column of a matrix $M$ as $M_j$, and its coefficient $i,j$ as $M_{i,j}$,
-\begin{align*}
-((A(\theta)&-A(\theta_{[N],\lambda}))^\transp (A(\theta) - A(\theta_{[N],\lambda})))_{i,j}\\
-%&= (\phi_i(\theta-\theta_{[N],\lambda}))^\transp \phi_j(\theta-\theta_{[N],\lambda}) \\
-&= (\theta-\theta_{[N],\lambda})^\transp\phi_{i}^{\transp}\phi_j(\theta-\theta_{[N],\lambda}) \\
-&\leq \lambda_{\max}(\phi_{i}^{\transp}\phi_j) \|\theta - \theta_{[N],\lambda}\|_{2}^2 = \cO\left( {\frac{\log N}{N}} \right) 
-\end{align*}
+	We have 
+	\begin{align*}
+	\|\theta - \theta_{N,\lambda}\|_{G_{N,\lambda}}^2 \geq \lambda_{\min}(G_{N,\lambda})\|\theta - \theta_{N,\lambda}\|_{2}^2
+	\end{align*}
+	And \eqref{eq:confidence-ellipsoid} gives
+	\[\|\theta - \theta_{N,\lambda}\|_{G_{N,\lambda}}^2 = \cO(\beta_N(\delta)^2) \]
+
+	Moreover, $A(\theta)$ belongs to a linear image of this $L^2$-ball. By writing a the $j^{th}$ column of a matrix $M$ as $M_j$, and its coefficient $i,j$ as $M_{i,j}$,
+	\begin{align*}
+	((A(\theta)-A(\theta_{N,\lambda}))^\transp (A(\theta) - A(\theta_{N,\lambda})))_{i,j}
+	&= (\theta-\theta_{N,\lambda})^\transp\phi_{i}^{\transp}\phi_j(\theta-\theta_{N,\lambda}) \\
+	&\leq \lambda_{\max}(\phi_{i}^{\transp}\phi_j) \|\theta - \theta_{N,\lambda}\|_{2}^2
+	\end{align*}
+
+	Thus, $\|A(\theta) - A(\theta_{N,\lambda})\|_F^2 = \Tr{\left[(A(\theta)-A(\theta_{N,\lambda}))^\transp (A(\theta) - A(\theta_{N,\lambda}))\right]} = \cO\left( {\frac{\beta_N(\delta)^2}{\lambda_{\min}(G_{N,\lambda})}}\right) $
 
@@
 		\begin{bmatrix}
-A_0^\transp P + P A_0^\transp + Q_0 & P|D|  \\
+		A_N^\transp P + P A_N^\transp + Q_0 & P|D|  \\
 		|D|^\transp P & -\rho I_r \\
@@
 		then for all $t> t_N$,
-\[\|\ox(t) - \ux(t)\| \leq \left(C_0 + \cO\left({\frac{\log N}{N}} \right)\right)C_\omega(t) \]
-where $C_\omega(t) = \sup_{\tau\in[t_N,t]} \|\overline{\omega}(\tau) - \underline{\omega}(\tau)\|_2^2$ and $C_0 = \sqrt{{2\rho\lambda_{\max}(P)}/({\lambda_{\min}(P)\lambda_{\min}(Q_0)})}$.
+		\[\|\ox(t) - \ux(t)\| \leq \left(C_0 + \cO\left({\frac{\beta_N(\delta)}{\sqrt{\lambda_{\min}(G_{N,\lambda})}}} \right)\right)C_\omega(t), \]
+		where $$C_0 = \sqrt{\frac{2\rho\lambda_{\max}(P)}{\lambda_{\min}(P)\lambda_{\min}(Q_0)}},$$ and $$C_\omega(t) = \sup_{\tau\in[0,t]} \|\overline{\omega}(\tau) - \underline{\omega}(\tau)\|_2.$$
 \end{lemma}
 \begin{proof}
-Let $e = \ox - \ux$. \eqref{eq:interval-predictor} gives the dynamics:
-\begin{align*}
-\dot{e} = A_0e + |\Delta A|(\ox^+ + \ux^-) + |D|(\overline{\omega} - \underline{\omega})
+	Let $e = \ox - \ux$. \eqref{eq:interval-predictor} gives the dynamics
+	\begin{align*}
+	\dot{e} = A_Ne + |\Delta A|(\ox^+ + \ux^-) + |D|(\overline{\omega} - \underline{\omega})
 	\end{align*}
@@
 	P>0,
-$ and compute its derivative:
+	$ and compute its derivative
 	\begin{align*}
@@
 	\begin{bmatrix}
-A_0^\transp P + P A_0^\transp + Q & P|D| & P|\Delta A| \\
+	A_N^\transp P + P A_N^\transp + Q & P|D| & P|\Delta A| \\
 	|D|^\transp P & -\rho I_r & 0\\
@@
 		\begin{array}{cc|c}
-A_0^\transp P + P A_0^\transp + Q + 4\alpha I_p & P|D| & P|\Delta A| \\
+		A_N^\transp P + P A_N^\transp + Q + 4\alpha I_p & P|D| & P|\Delta A| \\
 		|D|^\transp P & -\rho I_r & 0\\
@@
 	\label{eq:lyap-bound}
-V(t) \leq \frac{\rho}{\mu} C_\omega(t)
+	V(t) \leq \frac{\rho}{\mu} C_\omega^2(t)
 	\end{equation}
@@
 	We now examine the condition $\Upsilon \leq 0$.
-We resort to its Schur complement: given $\alpha > 0$ , $\Upsilon \leq 0$ if and only if $R \geq S$, where $S= \alpha^{-1}\begin{bmatrix}|\Delta A|^\transp P & 0\end{bmatrix}^\transp \begin{bmatrix}|\Delta A|^\transp P & 0\end{bmatrix}$ and $R$ is the top-left block of $-\Upsilon$:
+	We resort to its Schur complement: given $\alpha > 0$, $\Upsilon \leq 0$ if and only if $R \geq S$, where $S= \alpha^{-1}\begin{bmatrix}|\Delta A|^\transp P & 0\end{bmatrix}^\transp \begin{bmatrix}|\Delta A|^\transp P & 0\end{bmatrix}$ and $R$ is the top-left block of $-\Upsilon$:
 	\[R = \begin{bmatrix}
--A_0^\transp P - P A_0^\transp - Q - 4\alpha I_p & -P|D|\\
+	-A_N^\transp P - P A_N^\transp - Q - 4\alpha I_p & -P|D|\\
 	-|D|^\transp P & \rho I_r\\
@@
 	Choose $Q = \frac{1}{2}Q_0-4\alpha I_p$.
-Assume that $P$ is fixed and satisfies the conditions of the lemma. We have $$\lambda_{\max}(S) \leq \alpha^{-1}\lambda_{\max}(|\Delta A|)^2\lambda_{\max}(P)^2.$$
-
-Thus, by taking $\alpha = \frac{\lambda_{\max}(|\Delta A|)^2\lambda_{\max}(P)^2}{2\lambda_{\min}(Q_0)} = \cO(\log N / N)$, we can obtain that $S \leq \begin{bmatrix}
+	Assume that $P$ is fixed and satisfies the conditions of the lemma. We have 
+	\begin{align*}
+	\lambda_{\max}(S) &\leq \alpha^{-1}\lambda_{\max}(P)^2\lambda_{\max}(|\Delta A|^\top |\Delta A|)\\
+	&\leq\alpha^{-1}\lambda_{\max}(P)^2\|\Delta A\|_F^2
+	\end{align*}
+
+	Thus, by taking $\alpha = \frac{2\lambda_{\max}(P)^2\|\Delta A\|_F^2}{\lambda_{\min}(Q_0)} = \cO({\frac{\beta_N(\delta)^2}{\lambda_{\min}(G_{N,\lambda})}})$, we can obtain that $S \leq \begin{bmatrix}
 	\frac{1}{2}Q_0 & 0\\0 & 0
@@
 	\[R-S \geq \begin{bmatrix}
--A_0^\transp P - P A_0^\transp - Q_0 & -P|D|\\
+	-A_N^\transp P - P A_N^\transp - Q_0 & -P|D|\\
 	-|D|^\transp P & \rho I_r\\
@@
 	\|e(t)\|_2^2 &\leq \lambda_{\min}(P)^{-1} V(t)\\
-& \leq \frac{2\rho\lambda_{\max}(P)/\lambda_{\min}(P)}{\lambda_{\min}(Q_0) - 8\alpha} C_\omega(t)\\
+	& \leq \frac{2\rho\lambda_{\max}(P)/\lambda_{\min}(P)}{\lambda_{\min}(Q_0) - 8\alpha} C_\omega^2(t)\\
 	\end{align*}
@@
 	\begin{align*}
-\|e(t)\|_2 &\leq C_0\left(1 + \frac{4\alpha}{\lambda_{\min}(Q_0)} + \cO(\alpha_N^2)\right)C_\omega(t)\\
-&\leq \left(C_0 + \cO(\log N/N)\right)C_\omega(t)
+	\|e(t)\|_2 &\leq C_0\left(1 + \frac{4\alpha}{\lambda_{\min}(Q_0)} + \cO(\alpha^2)\right)C_\omega(t)\\
+	&\leq \left(C_0 + \cO\left({\frac{\beta_N(\delta)^2}{\lambda_{\min}(G_{N,\lambda})}}\right)\right)C_\omega(t)
 	\end{align*}
@@
 \begin{proof}
-
- For any sequence of controls $\bu$, dynamics $A(\theta)\in C_{[N],\delta}$ and perturbations $\underline{\bom} \leq \bom \leq \overline{\bom}$, we clearly have 
+	For any sequence of controls $\bu$, dynamical parameters $\theta\in C_{N,\delta}$ and disturbances $\underline{\bom} \leq \bom \leq \overline{\bom}$, we clearly have 
 	\[V(\bu)^r \leq V(\bu) = \expectedvalue_{\bom}\sum_n \gamma^n R(x_n)\]
@@
 	&\leq \sum_{n=N+1}^\infty \gamma^n L \left\|\underline{x}_n(\bu) - \overline{x}_n(\bu)\right\|_2\\
-     &\leq L(C_0 + \cO\left({\log N / N}\right)) \sum_{n>N} \gamma^n C_{\omega}(t_n)\\
-     &= \Delta_\omega + \cO\left({\log N / N}\right)
- \end{align*}
- with $\Delta_\omega = L C_0\sum_{n>N} \gamma^n C_{\omega}(t_n)$.
-
- Note that $\Delta_\omega$ is finite, since $C_{\omega}(t_n)$ is in the order of $\underline{\omega}(t_n)$, $\overline{\omega}(t_n)$, and these are in the order of $\sqrt{2\log n / \delta_n}$, with $\delta_n = \delta/(n(n+1))$, which is dominated by $\gamma^n$.
+	&\leq L\left(C_0 + \cO\left({\frac{\beta_N(\delta)^2}{\lambda_{\min}(G_{N,\lambda})}}\right)\right) \sum_{n>N} \gamma^n C_{\omega}(t_n)\\
+	&= \Delta_\omega + \cO\left({\frac{\beta_N(\delta)^2}{\lambda_{\min}(G_{N,\lambda})}}\right)
+	\end{align*}
+	with $\Delta_\omega = L C_0\sum_{n>N} \gamma^n C_{\omega}(t_n)$, which is finite by \Cref{assumpt:gaussian-noise}.
+
+	Finally, we use the result of \Cref{theorem:opd-regret} to account for planning with a finite budget, and relate $\hat{V}^r(a^\star)$ to $\hat{V}^r(a_K)$.
+\end{proof}
+
+\subsection{Proof of \Cref{cor:pe}}
+\label{sec:proof-pe}
+
+\begin{proof}
+	By \eqref{eq:vector_rls} and \eqref{eq:pe}, we have $$\lambda_{\min}(G_{N,\lambda}) \geq (N-n_0)\underline{\phi}^2 + \sum_{n<n_0}\Phi_{n}^\transp\Sigma_{p}^{-1}\Phi_{n}$$
+
+	and by \eqref{eq:confidence-ellipsoid},
+	\begin{align*}
+	\beta_N(\delta) &= \sqrt{2\log \left(\frac{\det(G_{N,\lambda})^{1/2}}{\delta\det(\lambda I_d)^{1/2}}\right)}
+	+ (\lambda d)^{1/2}S\\
+	&\leq \sqrt{\log \left(N^{d/2}\overline{\phi}^d / (\delta\lambda^{d/2})\right)} + \cO(1)
+	\end{align*}
+	Thus,
+	\[
+	\frac{\beta_N(\delta)^2}{\lambda_{\min}(G_{N,\lambda})} = \cO\left(\frac{\log (N^{d/2}/\delta)}{N} \right)
+	\]
+
+\paragraph{Stability condition 2.}
+
+By \Cref{lem:dynamics-est-bound} and the above, the sequence $(A_N)_{N}$ converges to $A(\theta)$ in Frobenius norm. Thus, 
+$$M_n \eqdef \begin{bmatrix}
+A_N^\transp P + P A_N^\transp + Q_0 & P|D|  \\
+|D|^\transp P & -\rho I_r \\
+\end{bmatrix}\text{ also converges to } M\eqdef\begin{bmatrix}
+A(\theta)^\transp P + P A(\theta)^\transp + Q_0 & P|D|  \\
+|D|^\transp P & -\rho I_r \\
+\end{bmatrix},$$ which is assumed to be negative definite.
+
+Moreover, the two functions that map a matrix to its characteristic polynomial and a polynomial to its roots, are both continuous.
+Thus, by continuity, the largest eigenvalue of $M_n$ converges to that of $M$, which is strictly negative.
+Hence, there exists some $N_0\in\Natural$ such that for all $N>N_0$, $M_N$ is negative definite, as required in the condition 2.
+of \Cref{thm:minimax-regret-bound}.
 \end{proof}
@@
 In both experiments, we used $\gamma=0.9$,  $\delta=0.9$ and a planning budget $K=100$.
-The perturbations were sampled uniformly in $[-0.1, 0.1]^r$ while the measurements are Gaussian with covariance $\Sigma_s = 0.1 I_s$.
+The disturbances were sampled uniformly in $[-0.1, 0.1]^r$ while the measurements are Gaussian with covariance $\Sigma_s = 0.1^2 I_s$.
 
@@
 
+\paragraph{DQN baseline}
+
+In addition to the state, knowledge of the obstacles is encoded in the observation as an angular grid of laser-like distance measurements, as well as the goal location relative to the system position.
+As a model for the $Q$-function, we used a Multi-Layer Perceptron with two hidden layers of size $100$. An $\epsilon$-greedy strategy was used for exploration.
+
 \subsection{Autonomous Driving}
@@
 Any vehicle $i\in[0,V]$ is represented by its position $(x_i, y_i)$, its forward velocity $v_i$ its heading $\psi_i$.
-The resulting joint state is the traffic description: $x = (x_i, y_i, v_i, psi_i)_{i\in[0,V]}\in\Real^{4V+4}$.
+The resulting joint state is the traffic description: $x = (x_i, y_i, v_i, \psi_i)_{i\in[0,V]}\in\Real^{4V+4}$.
 
@@
 \paragraph{Change of coordinates}
-In both cases, the obtained polytope centre $A_0$ is non-Metzler.
+In both cases, the obtained polytope centre $A_N$ is non-Metzler.
 We use the similarity transformation of coordinates of \citet{Efimov2013}.
 Precisely, we choose $\Theta$ such that for any $\theta\in\Theta$, $A(\theta)$ is always diagonalisable with real eigenvalues, and perform an eigendecomposition to compute its change of basis matrix $Z$.
-The transformed system $X'=Z^{-1}(X-X_c)$ verifies \eqref{eq:confidence} with $A_0$ Metlzer as required to apply the interval predictor of \Cref{prop:predictor}.
+The transformed system $X'=Z^{-1}(X-X_c)$ verifies \eqref{eq:confidence} with $A_N$ Metlzer as required to apply the interval predictor of \Cref{prop:predictor}.
 Finally, the obtained predictor is transformed back to the original coordinates $Z$ by using the following lemma:
@@
 
+\paragraph{DQN baseline}
+
+In order to avoid discontinuities in the vehicles headings, the state is encoded as $x = (x_i, y_i, v^x_i, v^y_i, \cos\psi_i, \sin\psi_i)_{i\in[0,V]}\in\Real^{6V+6}$, with the ego-vehicle always in the first position.
+As a model for the $Q$-function, we used the Social Attention architecture from \citep{leurent2019social}, that allows to support an arbitrary number of vehicles as input and enforce an invariance to their order.
+
 \section{A tighter conversion from ellipsoid to polytope}
@@
 	&G_{N,\lambda} = PDP^{-1}, \quad \Delta\theta_k = \beta_{N}(\delta)P^{-1}D^{-1/2} h_k, \\
-	&A_0 = A + \theta_{N,\lambda}^\transp\Phi, \quad \Delta A_k = \Delta\theta_k^\transp\Phi.
-	\end{align*}
-	This conversion is illustrated in \Cref{fig:ellipsoid_to_polytope}.
+	&A_N = A(\theta_{N,\lambda}), \quad \Delta A_k = \Delta\theta_k^\transp\Phi.
+	\end{align*}
 \end{lemma}
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[trim={3.8cm, 2cm, 5cm, 3.8cm}, clip, width=0.7\linewidth]{img/ellipsoid_to_polytope}
-	\caption{From the confidence ellipsoid $\cC_\delta$ to its enclosing polytope $\cP_\delta$}
-	\label{fig:ellipsoid_to_polytope}
-\end{figure}
+%\begin{figure}
+%	\centering
+%	\includegraphics[trim={3.8cm, 2cm, 5cm, 3.8cm}, clip, width=0.7\linewidth]{img/ellipsoid_to_polytope}
+%	\caption{From the confidence ellipsoid $\cC_\delta$ to its enclosing polytope $\cP_\delta$}
+%	\label{fig:ellipsoid_to_polytope}
+%\end{figure}
 
@@
 	\end{figure}
-
+%\end{comment}
 \end{document}

### 2020-10-06 main.tex
Remove wrong transpose in LMI

@@
 			$$\forall N>N_0,\quad \begin{bmatrix}
-			A_N^\transp P + P A_N^\transp + Q_0 & P|D|  \\
+			A_N^\transp P + P A_N + Q_0 & P|D|  \\
 			|D|^\transp P & -\rho I_r \\
@@
 		$$\begin{bmatrix}
-		A(\theta)^\transp P + P A(\theta)^\transp + Q_0 & P|D|  \\
+		A(\theta)^\transp P + P A(\theta) + Q_0 & P|D|  \\
 		|D|^\transp P & -\rho I_r \\
@@
 		\begin{bmatrix}
-		A_N^\transp P + P A_N^\transp + Q_0 & P|D|  \\
+		A_N^\transp P + P A_N + Q_0 & P|D|  \\
 		|D|^\transp P & -\rho I_r \\
@@
 	\begin{bmatrix}
-	A_N^\transp P + P A_N^\transp + Q & P|D| & P|\Delta A| \\
+	A_N^\transp P + P A_N + Q & P|D| & P|\Delta A| \\
 	|D|^\transp P & -\rho I_r & 0\\
@@
 		\begin{array}{cc|c}
-		A_N^\transp P + P A_N^\transp + Q + 4\alpha I_p & P|D| & P|\Delta A| \\
+		A_N^\transp P + P A_N + Q + 4\alpha I_p & P|D| & P|\Delta A| \\
 		|D|^\transp P & -\rho I_r & 0\\
@@
 	\[R = \begin{bmatrix}
-	-A_N^\transp P - P A_N^\transp - Q - 4\alpha I_p & -P|D|\\
+	-A_N^\transp P - P A_N - Q - 4\alpha I_p & -P|D|\\
 	-|D|^\transp P & \rho I_r\\
@@
 	\[R-S \geq \begin{bmatrix}
-	-A_N^\transp P - P A_N^\transp - Q_0 & -P|D|\\
+	-A_N^\transp P - P A_N - Q_0 & -P|D|\\
 	-|D|^\transp P & \rho I_r\\

### 2020-10-12 main.tex
Add paragraph and acks, final option

@@
 % ready for submission
- \usepackage{neurips_2020}
+% \usepackage{neurips_2020}
 
@@
 % to compile a camera-ready version, add the [final] option, e.g.:
-%     \usepackage[final]{neurips_2020}
+     \usepackage[final]{neurips_2020}
 
@@
 \author{%
-	David S.~Hippocampus\thanks{Use footnote for providing further information
-		about author (webpage, alternative address)---\emph{not} for acknowledging
-		funding agencies.} \\
-	Department of Computer Science\\
-	Cranberry-Lemon University\\
-	Pittsburgh, PA 15213 \\
-	\texttt{hippo@cs.cranberry-lemon.edu} \\
+	Edouard~Leurent \\
+	Inria Lille Nord-Europe \& Renault\\
+	Paris, France\\
+	\texttt{edouard.leurent@inria.fr} \\
 	% examples of more authors
-	% \And
-	% Coauthor \\
-	% Affiliation \\
-	% Address \\
-	% \texttt{email} \\
-	% \AND
-	% Coauthor \\
-	% Affiliation \\
-	% Address \\
-	% \texttt{email} \\
-	% \And
-	% Coauthor \\
-	% Affiliation \\
-	% Address \\
-	% \texttt{email} \\
-	% \And
-	% Coauthor \\
-	% Affiliation \\
-	% Address \\
-	% \texttt{email} \\
+	 \And
+	 Denis~Efimov \\
+	 Inria Lille Nord-Europe, Valse team\\
+	 Lille, France\\
+	 \texttt{denis.efimov@inria.fr} \\
+	 \And
+	 Odalric-Ambrym~Maillard \\
+	 Inria Lille Nord-Europe, SequeL team\\
+	 Lille, France\\
+	 \texttt{odalric.maillard@inria.fr} \\
 }
@@
 This paper fits in the popular MPC framework, for which adaptive data-driven schemes have been developed to deal with model uncertainty \citep{Sastry1990,Tanaskovic2014,Amos2018}, but lack guarantees.
-The family of tube-MPC algorithms seeks to derive theoretical guarantees of \emph{robust constraint satisfaction}: the state $x$ is constrained in a safe region $\mathbb{X}$ around the origin, often chosen convex \citep{Fukushima2007,Adetola2009,Aswani2013,Turchetta2016,Lorenzen2017,Kohler2019,Lu2019}.
-%, their adaptive versions take also into account the possible parametric model uncertainty
+The family of tube-MPC algorithms seeks to derive theoretical guarantees of \emph{robust constraint satisfaction}: the state $x$ is constrained in a safe region $\mathbb{X}$ around the origin, often chosen convex \citep{Fukushima2007,Adetola2009,Aswani2013,Turchetta2016,Lorenzen2017,Kohler2019,Lu2019,Leurent2020robust}.
 Yet, many tasks cannot be framed as stabilisation problems (e.g.
@@
 
-This bound contains an input-dependent \hlb{estimation error} term, which can be further bounded under an additional assumption that the features are sufficiently excited.
+It is difficult to check the validity of the stability condition 2.
+since it applies to matrices $A_N$ produced by the algorithm rather than to the system parameters.
+A stronger but easier to check condition is that the polytope \eqref{eq:polytope} at some point becomes included in a set where this property is uniformly satisfied.
+For instance, if the features are sufficiently excited, the estimation converges to a neighbourhood of the true dynamics $A(\theta)$.
+This also allows to further bound the input-dependent \hlb{estimation error} term.
 
@@
 
-The procedure we developed in sections \ref{sec:estimation}, \ref{sec:prediction} and \ref{sec:control} relies on strong modelling assumptions, such as the linear dynamics \eqref{eq:dynamics} and \Cref{assumpt:structure}.
+The procedure we developed in \Cref{sec:estimation,sec:prediction,sec:control} relies on strong modelling assumptions, such as the linear dynamics \eqref{eq:dynamics} and \Cref{assumpt:structure}.
 But what if they are wrong?
@@
 \citet{delos2015} provide a way to test this membership in polynomial time using linear programming.
-Whenever it is not verified, we can confidently reject the $(A,\phi)$-modelling \Cref{assumpt:structure}.
+Whenever it is not verified, we can confidently reject the $(A,\phi)$-modelling \cref{assumpt:structure}.
 This enables us to consider a rich set of potential features $\left((A^1, \phi^1), \dots, (A^M, \phi^M)\right)$ rather than relying on a single assumption, and only retain those that are consistent with the observations so far.
@@
 \label{assumpt:multi-model-ambiguity}
-The true dynamics $f$ lies within a finite set of candidate models $f^1, \dots, f^M$:
-$$
-\exists m\in[M]: \dot{x}(t) = f^m(x(t), u(t)), \forall t\geq 0.
-$$
+The dynamics $f$ lie in a finite set of candidates $(f^m)_{m\in[M]}$.
+%$
+%\exists m\in[M]: \dot{x}(t) = f^m(x(t), u(t)), \forall t\geq 0.
+%$
 \end{assumption}
@@
 
-\begin{definition}[Robust sequence upper bounds] We replace the upper-bound \eqref{eq:opd} on sequence values in \texttt{OPD} by:
-$$
-%\label{eq:robust-b-values}
-B_a^r(k)  \eqdef \min_{m\in[M]} \sum_{n=0}^{h-1} \gamma^n R_n^m  + \frac{\gamma^h}{1-\gamma}. \refstepcounter{equation}\hfill(\theequation)\label{eq:robust-b-values}
-$$
+\begin{definition}[Robust UCB] We replace the upper-bound \eqref{eq:opd} on sequence values in \texttt{OPD} by:
+\begin{equation}
+\label{eq:robust-b-values}
+B_a^r(k)  \eqdef \min_{m\in[M]} \sum_{n=0}^{h-1} \gamma^n R_n^m  + \frac{\gamma^h}{1-\gamma}. 
+\end{equation}
 \end{definition}
@@
 
-\paragraph{Motion planning for an autonomous vehicle}
+\textbf{Motion planning for an autonomous vehicle}~~
 We consider the \href{https://github.com/eleurent/highway-env}{highway-env} environment \citep{highway-env} for simulated driving decision problems.
@@
 Since these intentions are unknown to the agent, we adopt the multi-model perspective of \Cref{sec:multi-model} and consider one model per possible route for every observed vehicle before an intersection.
-In \Cref{tab:driving}, we compare \Cref{alg:full} to a nominal agent planning with the estimated parameter $\theta_{N,\lambda}$, with two different modelling assumptions: we assume that Nominal 1 has access to the true followed route for each vehicle, while Nominal 2 does not and picks the model with minimal prediction error.
-As before, the robust approach is less efficient on average than planning with a nominal model, but it does better in terms of worst-case performance and manages to avoid collisions, contrary to the nominal baselines that suffer from model bias.
-Again, we also compare to the final policy of a DQN baseline trained over 3000 episodes, causing $1058\pm113$ collisions while training ($35\pm4\%$).
+In \Cref{tab:driving}, we compare \Cref{alg:full} to a nominal agent planning with two different modelling assumptions: Nominal 1 has access to the true followed route for each vehicle, while Nominal 2 does not and picks the model with minimal prediction error.
+Again we also compare to a DQN baseline trained over 3000 episodes, causing $1058\pm113$ collisions while training ($35\pm4\%$).
+We observe similar results as before: the robust agents has a higher worst-case performance and avoids collisions at all time, at the price of a decreased average performance.
 We provide more details about the system and videos of the experiments in the Supplementary Material.
@@
 In contrast, our approach would enable evaluating and optimising the worst-case outcome of such public policies.
+
+\begin{ack}
+	This work was supported by the French Ministry of Higher Education and Research, and CPER Nord-Pas de Calais/FEDER DATA Advanced data science and technologies 2015-2020.
+\end{ack}
 

### 2020-10-13 paper/main.tex
Move paper to a subdir

--- 2020-10-12 main.tex
@@
 Interestingly, our analysis naturally adapts to handle many models and combines with a data-driven robust model selection strategy, which enables to relax the modelling assumptions.
-Last, we strive to preserve tractability at any stage of the method, that we illustrate on two challenging simulated environments.\footnote{Source code and videos are available in the Supplementary Material.}
+Last, we strive to preserve tractability at any stage of the method, that we illustrate on two challenging simulated environments.\footnote{Code and videos available at  \url{https://eleurent.github.io/robust-beyond-quadratic/}.}
 \end{abstract}
@@
 Yet, many tasks cannot be framed as stabilisation problems (e.g.
-obstacle avoidance) and are better addressed with the minimax control objective, which can allow more flexible goal formulations.
+obstacle avoidance) and are better addressed with the minimax control objective, which allows more flexible goal formulations.
 Minimax control has mostly been studied in two particular instances.
@@
 In this paper, interval prediction is used to produce oversets, while a near-optimal control is found using a tree-based planning procedure.
-
-%While there exists a vast body of literature on the control of uncertain systems, its majority is only concerned with the problem of stabilisation around a fixed reference state or trajectory, including $\cH_\infty$ control \citep[see, e.g.][]{Basar1996}, sliding-mode control \citep{Lu1997}, tube-MPC \citep{Limon2010} or system-level synthesis \citep{Dean2017,Dean2018}.
-Yet, we argue that many tasks cannot be framed as stabilisation problems (e.g.
-obstacle avoidance) and are better addressed in our setting of maximising an arbitrary utility function, where no prior result exists to our knowledge.
-Other safety frameworks exist, such as constraining the state $x$ in a given region $\mathbb{X}$ often chosen convex \citep[e.g.][]{Turchetta2016}, which again is not suitable for many tasks (e.g.
-these of \Cref{sec:experiments}).
-Therefore, we limit references to focus only on two lines of work closest to ours.
-%
-%\paragraph{Linear systems with quadratic costs} Several approaches have been proposed for cumulative regret minimisation in the LQ problem.
-In the \emph{Optimism in the Face of Uncertainty} paradigm, the best possible dynamics within a high-confidence region is selected under a controllability constraint, to compute the corresponding optimal control in closed-form by solving a Riccati equation.
-\citep{abbasi-yadkori11a,Ibrahimi2013,Faradonbeh2017} show that this procedure achieves a $\tilde{\cO}\left(N^{1/2}\right)$ regret.
-Posterior sampling algorithms \citep{Ouyang2017,abeille18a} select candidate dynamics randomly instead, and obtain the same result.
-Other works use noise injection for exploration such as \citep{Dean2017,Dean2018}.
-However, neither optimism nor random exploration fit a critical setting, where ensuring safety requires instead to consider pessimistic outcomes.
-The work of \citet{Dean2017} is closest to our setting: after an offline estimation phase, they estimate a simple regret between a robust controller and the optimal performance.
-Our work mainly differs in that it addresses generic costs.
-%
-%\paragraph{Robust Dynamic Programming with generic costs}
-%Robust optimisation with generic costs has been studied in the context of finite Markov Decision Processes with uncertain parameters by \citet{Iyengar2005}, \citet{Nilim2005} and \citet{Wiesemann2013}.
-They showed that the main results of Dynamic Programming can be extended to their robust counterparts only when the dynamics ambiguity set verifies a certain rectangularity property, related to time-varying uncertainty.
-Since our setting considers continuous states and time-invariant uncertainty, these methods do not apply.
 
@@
 
-% Limitations: set-based method assumes time-varying uncertainty where we have time-invariant uncertainty: $A(\theta)$ is fixed vs $A(\theta)$ can vary in $\cC_\delta$ at each step.
-Consequence: conservative overset.
-
 \section{Robust Control}
@@
 V^r = \sup_{a\in\cA^\Natural}\min_{m\in[M]} \sum_{n=N+1}^\infty \gamma^n R_n^m, 
-%\refstepcounter{equation}\hfill(\theequation)\label{eq:robust-objective-discrete}
 \end{equation}
@@
 \label{sec:experiments}
+
+Videos and code are available at \url{https://eleurent.github.io/robust-beyond-quadratic/}.
 
@@
 }
-
+\vspace*{-0.5cm}
 \end{table}
@@
 Again we also compare to a DQN baseline trained over 3000 episodes, causing $1058\pm113$ collisions while training ($35\pm4\%$).
-We observe similar results as before: the robust agents has a higher worst-case performance and avoids collisions at all time, at the price of a decreased average performance.
-We provide more details about the system and videos of the experiments in the Supplementary Material.
+As before, the robust agent has a higher worst-case performance and avoids collisions at all time, at the price of a decreased average performance..
 
@@
 \bibliography{references}
-\bibliographystyle{icml2020}
+\bibliographystyle{biblio}
 

### 2020-10-13 supplementary/code/highway_env/envs/__init__.py

@@ -1,1 +1,0 @@
-from highway_env.envs.intersection_env import *

### 2020-10-13 supplementary/code/highway_env/envs/common/abstract.py

@@ -1,380 +1,0 @@
-from __future__ import division, print_function, absolute_import
-import copy
-import gym
-from gym import spaces
-from gym.utils import seeding
-
-from highway_env import utils
-from highway_env.envs.common.observation import observation_factory
-from highway_env.envs.common.finite_mdp import finite_mdp
-from highway_env.envs.common.graphics import EnvViewer
-from highway_env.vehicle.behavior import IDMVehicle, LinearVehicle
-from highway_env.vehicle.control import MDPVehicle
-from highway_env.vehicle.dynamics import Obstacle
-
-
-class AbstractEnv(gym.Env):
-    """
-        A generic environment for various tasks involving a vehicle driving on a road.
-
-        The environment contains a road populated with vehicles, and a controlled ego-vehicle that can change lane and
-        velocity. The action space is fixed, but the observation space and reward function must be defined in the
-        environment implementations.
-    """
-    metadata = {'render.modes': ['human', 'rgb_array']}
-
-    ACTIONS = {0: 'LANE_LEFT',
-               1: 'IDLE',
-               2: 'LANE_RIGHT',
-               3: 'FASTER',
-               4: 'SLOWER'}
-    """
-        A mapping of action indexes to action labels
-    """
-    ACTIONS_INDEXES = {v: k for k, v in ACTIONS.items()}
-    """
-        A mapping of action labels to action indexes
-    """
-
-    SIMULATION_FREQUENCY = 15
-    """
-        The frequency at which the system dynamics are simulated [Hz]
-    """
-
-    PERCEPTION_DISTANCE = 6.0 * MDPVehicle.SPEED_MAX
-    """
-        The maximum distance of any vehicle present in the observation [m]
-    """
-
-    def __init__(self, config=None):
-        # Configuration
-        self.config = self.default_config()
-        if config:
-            self.config.update(config)
-
-        # Seeding
-        self.np_random = None
-        self.seed()
-
-        # Scene
-        self.road = None
-        self.vehicle = None
-
-        # Spaces
-        self.observation = None
-        self.action_space = None
-        self.observation_space = None
-        self.define_spaces()
-
-        # Running
-        self.time = 0  # Simulation time
-        self.steps = 0  # Actions performed
-        self.done = False
-
-        # Rendering
-        self.viewer = None
-        self.automatic_rendering_callback = None
-        self.should_update_rendering = True
-        self.rendering_mode = 'human'
[…]

### 2020-10-13 supplementary/code/highway_env/envs/common/graphics.py

@@ -1,145 +1,0 @@
-from __future__ import division, print_function, absolute_import
-
-import os
-
-import numpy as np
-import pygame
-from gym.spaces import Discrete
-
-from highway_env.road.graphics import WorldSurface, RoadGraphics
-from highway_env.vehicle.graphics import VehicleGraphics
-
-
-class EnvViewer(object):
-    """
-        A viewer to render a highway driving environment.
-    """
-    SAVE_IMAGES = False
-
-    def __init__(self, env, offscreen=False):
-        self.env = env
-        self.offscreen = offscreen
-
-        pygame.init()
-        pygame.display.set_caption("Highway-env")
-        panel_size = (self.env.config["screen_width"], self.env.config["screen_height"])
-
-        # A display is not mandatory to draw things. Ignoring the display.set_mode()
-        # instruction allows the drawing to be done on surfaces without
-        # handling a screen display, useful for e.g. cloud computing
-        if not self.offscreen:
-            self.screen = pygame.display.set_mode([self.env.config["screen_width"], self.env.config["screen_height"]])
-        self.sim_surface = WorldSurface(panel_size, 0, pygame.Surface(panel_size))
-        self.sim_surface.scaling = env.config.get("scaling", self.sim_surface.INITIAL_SCALING)
-        self.sim_surface.centering_position = env.config.get("centering_position", self.sim_surface.INITIAL_CENTERING)
-        self.clock = pygame.time.Clock()
-
-        self.enabled = True
-        if "SDL_VIDEODRIVER" in os.environ and os.environ["SDL_VIDEODRIVER"] == "dummy":
-            self.enabled = False
-
-        self.agent_display = None
-        self.agent_surface = None
-        self.vehicle_trajectory = None
-        self.frame = 0
-        self.directory = None
-
-    def set_agent_display(self, agent_display):
-        """
-            Set a display callback provided by an agent, so that they can render their behaviour on a dedicated
-            agent surface, or even on the simulation surface.
-        :param agent_display: a callback provided by the agent to display on surfaces
-        """
-        if self.agent_display is None:
-            if self.env.config["screen_width"] > self.env.config["screen_height"]:
-                self.screen = pygame.display.set_mode((self.env.config["screen_width"],
-                                                       2 * self.env.config["screen_height"]))
-            else:
-                self.screen = pygame.display.set_mode((2 * self.env.config["screen_width"],
-                                                       self.env.config["screen_height"]))
[…]

### 2020-10-13 supplementary/code/highway_env/envs/common/observation.py

@@ -1,298 +1,0 @@
-from __future__ import division, print_function, absolute_import
-import pandas
-from gym import spaces
-import numpy as np
-
-from highway_env import utils
-from highway_env.envs.common.finite_mdp import compute_ttc_grid
-from highway_env.road.lane import AbstractLane
-from highway_env.vehicle.control import MDPVehicle
-from highway_env.road.graphics import WorldSurface
-
-
-class ObservationType(object):
-    def space(self):
-        raise NotImplementedError()
-
-    def observe(self):
-        raise NotImplementedError()
-
-
-class GrayscaleObservation(ObservationType):
-    """
-        An observation class that collects directly what the simulator renders
-        as the input, and stacks the collected frames just as in the nature DQN
-        . Specific keys are expected in the configuration dictionnary passed.
-
-        Example of observation dictionnary in the environment config:
-            observation": {
-                "type": "GrayscaleObservation",
-                "weights": [0.2989, 0.5870, 0.1140],  #weights for RGB conversion,
-                "stack_size": 4,
-                "observation_shape": (84, 84)
-            }
-
-        Also, the screen_height and screen_width of the environment should match the
-        expected observation_shape. 
-    """
-    def __init__(self, env, **config):
-        self.env = env
-        self.config = config
-        self.observation_shape = config["observation_shape"]
-        self.shape = self.observation_shape + (config["stack_size"], )
-        self.state = np.zeros(self.shape)
-
-    def space(self):
-        try:
-            return spaces.Box(shape=self.shape,
-                              low=0, high=1,
-                              dtype=np.float32)
-        except AttributeError:
-            return None
-
-    def observe(self):
-        new_obs = self._record_to_grayscale()
-        new_obs = np.reshape(new_obs, self.observation_shape)
-        self.state = np.roll(self.state, -1, axis=-1)
-        self.state[:, :, -1] = new_obs
-        return self.state
-
-    def _record_to_grayscale(self):
-        raw_rgb = self.env.render('rgb_array')
-        return np.dot(raw_rgb[..., :3],
-                      self.config['weights'])
-
-
-class TimeToCollisionObservation(ObservationType):
-    def __init__(self, env, horizon=10, **kwargs):
-        self.env = env
-        self.horizon = horizon
-
-    def space(self):
-        try:
[…]

### 2020-10-13 supplementary/code/highway_env/envs/intersection_env.py

@@ -1,226 +1,0 @@
-from __future__ import division, print_function, absolute_import
-from gym.envs.registration import register
-import numpy as np
-
-from highway_env import utils
-from highway_env.envs.common.abstract import AbstractEnv
-from highway_env.road.lane import LineType, StraightLane, CircularLane, SineLane, AbstractLane
-from highway_env.road.regulation import RegulatedRoad
-from highway_env.road.road import RoadNetwork
-from highway_env.vehicle.control import MDPVehicle
-
-
-class IntersectionEnv(AbstractEnv):
-    COLLISION_REWARD = -5
-    HIGH_VELOCITY_REWARD = 1
-    ARRIVED_REWARD = 1
-
-    ACTIONS = {
-        0: 'SLOWER',
-        1: 'IDLE',
-        2: 'FASTER'
-    }
-    ACTIONS_INDEXES = {v: k for k, v in ACTIONS.items()}
-
-    @classmethod
-    def default_config(cls):
-        config = super().default_config()
-        config.update({
-            "observation": {
-                "type": "Kinematics",
-                "vehicles_count": 15,
-                "features": ["presence", "x", "y", "vx", "vy", "cos_h", "sin_h"],
-                "features_range": {
-                    "x": [-100, 100],
-                    "y": [-100, 100],
-                    "vx": [-20, 20],
-                    "vy": [-20, 20],
-                },
-                "absolute": True,
-                "flatten": False,
-                "observe_intentions": False
-            },
-            "duration": 13,  # [s]
-            "destination": "o1",
-            "initial_vehicle_count": 10,
-            "spawn_probability": 0.6,
-            "screen_width": 600,
-            "screen_height": 600,
-            "centering_position": [0.5, 0.6],
-            "scaling": 5.5 * 1.3,
-            "collision_reward": IntersectionEnv.COLLISION_REWARD,
-            "normalize_reward": False
-        })
-        return config
-
-    def _reward(self, action):
-        reward = self.config["collision_reward"] * self.vehicle.crashed \
-                 + self.HIGH_VELOCITY_REWARD * (self.vehicle.velocity_index == self.vehicle.SPEED_COUNT - 1)
-        reward = self.ARRIVED_REWARD if self.has_arrived else reward
-        if self.config["normalize_reward"]:
-            reward = utils.remap(reward, [self.config["collision_reward"], self.ARRIVED_REWARD], [0, 1])
-        return reward
-
-    def _is_terminal(self):
-        """
[…]

### 2020-10-13 supplementary/code/highway_env/interval.py

@@ -1,229 +1,0 @@
-import itertools
-
-import numpy as np
-
-
-def intervals_product(a, b):
-    """
-        Compute the product of two intervals
-    :param a: interval [a_min, a_max]
-    :param b: interval [b_min, b_max]
-    :return: the interval of their product ab
-    """
-    p = lambda x: np.maximum(x, 0)
-    n = lambda x: np.maximum(-x, 0)
-    return np.array(
-        [np.dot(p(a[0]), p(b[0])) - np.dot(p(a[1]), n(b[0])) - np.dot(n(a[0]), p(b[1])) + np.dot(n(a[1]), n(b[1])),
-         np.dot(p(a[1]), p(b[1])) - np.dot(p(a[0]), n(b[1])) - np.dot(n(a[1]), p(b[0])) + np.dot(n(a[0]), n(b[0]))])
-
-
-def intervals_scaling(a, b):
-    """
-        Scale an intervals
-    :param a: matrix a
-    :param b: interval [b_min, b_max]
-    :return: the interval of their product ab
-    """
-    p = lambda x: np.maximum(x, 0)
-    n = lambda x: np.maximum(-x, 0)
-    return np.array(
-        [np.dot(p(a), b[0]) - np.dot(n(a), b[1]),
-         np.dot(p(a), b[1]) - np.dot(n(a), b[0])])
-
-
-def vector_interval_section(v_i, direction):
-    corners = [[v_i[0, 0], v_i[0, 1]],
-               [v_i[0, 0], v_i[1, 1]],
-               [v_i[1, 0], v_i[0, 1]],
-               [v_i[1, 0], v_i[1, 1]]]
-    corners_dist = [np.dot(corner, direction) for corner in corners]
-    return np.array([min(corners_dist), max(corners_dist)])
-
-
-def interval_absolute_to_local(position_i, lane):
-    """
-        Converts an interval in absolute x,y coordinates to an interval in local (longiturinal, lateral) coordinates
-    :param position_i: the position interval [x_min, x_max]
-    :param lane: the lane giving the local frame
-    :return: the corresponding local interval
-    """
-    position_corners = [[position_i[0, 0], position_i[0, 1]],
-                        [position_i[0, 0], position_i[1, 1]],
-                        [position_i[1, 0], position_i[0, 1]],
-                        [position_i[1, 0], position_i[1, 1]]]
-    corners_local = np.array([lane.local_coordinates(c) for c in position_corners])
[…]

### 2020-10-13 supplementary/code/highway_env/road/graphics.py

@@ -1,214 +1,0 @@
-from __future__ import division, print_function
-import numpy as np
-import pygame
-
-from highway_env.road.lane import LineType
-from highway_env.vehicle.graphics import VehicleGraphics
-
-
-class LaneGraphics(object):
-    """
-        A visualization of a lane.
-    """
-    STRIPE_SPACING = 5
-    """ Offset between stripes [m]"""
-
-    STRIPE_LENGTH = 3
-    """ Length of a stripe [m]"""
-
-    STRIPE_WIDTH = 0.3
-    """ Width of a stripe [m]"""
-
-    @classmethod
-    def display(cls, lane, surface):
-        """
-            Display a lane on a surface.
-
-        :param lane: the lane to be displayed
-        :param surface: the pygame surface
-        """
-        stripes_count = int(2 * (surface.get_height() + surface.get_width()) / (cls.STRIPE_SPACING * surface.scaling))
-        s_origin, _ = lane.local_coordinates(surface.origin)
-        s0 = (int(s_origin) // cls.STRIPE_SPACING - stripes_count // 2) * cls.STRIPE_SPACING
-        for side in range(2):
-            if lane.line_types[side] == LineType.STRIPED:
-                cls.striped_line(lane, surface, stripes_count, s0, side)
-            elif lane.line_types[side] == LineType.CONTINUOUS:
-                cls.continuous_curve(lane, surface, stripes_count, s0, side)
-            elif lane.line_types[side] == LineType.CONTINUOUS_LINE:
-                cls.continuous_line(lane, surface, stripes_count, s0, side)
-
-    @classmethod
-    def striped_line(cls, lane, surface, stripes_count, s0, side):
-        """
-            Draw a striped line on one side of a lane, on a surface.
-
-        :param lane: the lane
-        :param surface: the pygame surface
-        :param stripes_count: the number of stripes to draw
-        :param s0: the longitudinal position of the first stripe [m]
-        :param side: which side of the road to draw [0:left, 1:right]
-        """
-        starts = s0 + np.arange(stripes_count) * cls.STRIPE_SPACING
-        ends = s0 + np.arange(stripes_count) * cls.STRIPE_SPACING + cls.STRIPE_LENGTH
-        lats = [(side - 0.5) * lane.width_at(s) for s in starts]
-        cls.draw_stripes(lane, surface, starts, ends, lats)
-
-    @classmethod
-    def continuous_curve(cls, lane, surface, stripes_count, s0, side):
-        """
[…]

### 2020-10-13 supplementary/code/highway_env/road/road.py

@@ -1,328 +1,0 @@
-from __future__ import division, print_function
-import numpy as np
-import pandas as pd
-import logging
-
-from highway_env.logger import Loggable
-from highway_env.road.lane import LineType, StraightLane
-from highway_env.vehicle.dynamics import Obstacle
-
-logger = logging.getLogger(__name__)
-
-
-class RoadNetwork(object):
-    def __init__(self):
-        self.graph = {}
-
-    def add_node(self, node):
-        """
-            A node represents an symbolic intersection in the road network.
-        :param node: the node label.
-        """
-        if node not in self.graph:
-            self.graph[node] = []
-
-    def add_lane(self, _from, _to, lane):
-        """
-            A lane is encoded as an edge in the road network.
-        :param _from: the node at which the lane starts.
-        :param _to: the node at which the lane ends.
-        :param AbstractLane lane: the lane geometry.
-        """
-        if _from not in self.graph:
-            self.graph[_from] = {}
-        if _to not in self.graph[_from]:
-            self.graph[_from][_to] = []
-        self.graph[_from][_to].append(lane)
-
-    def get_lane(self, index):
-        """
-            Get the lane geometry corresponding to a given index in the road network.
-        :param index: a tuple (origin node, destination node, lane id on the road).
-        :return: the corresponding lane geometry.
-        """
-        _from, _to, _id = index
-        if _id is None and len(self.graph[_from][_to]) == 1:
-            _id = 0
-        return self.graph[_from][_to][_id]
-
-    def get_closest_lane_index(self, position):
-        """
-            Get the index of the lane closest to a world position.
-
-        :param position: a world position [m].
-        :return: the index of the closest lane.
-        """
-        indexes, distances = [], []
-        for _from, to_dict in self.graph.items():
-            for _to, lanes in to_dict.items():
-                for _id, l in enumerate(lanes):
-                    distances.append(l.distance(position))
-                    indexes.append((_from, _to, _id))
-        return indexes[int(np.argmin(distances))]
-
-    def next_lane(self, current_index, route=None, position=None, np_random=np.random):
-        """
-            Get the index of the next lane that should be followed after finishing the current lane.
-
-            If a plan is available and matches with current lane, follow it.
-            Else, pick next road randomly.
-            If it has the same number of lanes as current road, stay in the same lane.
-            Else, pick next road's closest lane.
[…]

### 2020-10-13 supplementary/code/highway_env/utils.py

@@ -1,190 +1,0 @@
-from __future__ import division, print_function
-
-import copy
-import importlib
-import itertools
-
-import numpy as np
-
-
-def do_every(duration, timer):
-    return duration < timer
-
-
-def remap(v, x, y):
-    return y[0] + (v-x[0])*(y[1]-y[0])/(x[1]-x[0])
-
-
-def class_from_path(path):
-    module_name, class_name = path.rsplit(".", 1)
-    class_object = getattr(importlib.import_module(module_name), class_name)
-    return class_object
-
-
-def constrain(x, a, b):
-    return np.minimum(np.maximum(x, a), b)
-
-
-def not_zero(x, eps=1e-2):
-    if abs(x) > eps:
-        return x
-    elif x > 0:
-        return eps
-    else:
-        return -eps
-
-
-def wrap_to_pi(x):
-    return ((x+np.pi) % (2*np.pi)) - np.pi
-
-
-def point_in_rectangle(point, rect_min, rect_max):
-    """
-        Check if a point is inside a rectangle
-    :param point: a point (x, y)
-    :param rect_min: x_min, y_min
-    :param rect_max: x_max, y_max
-    """
-    return rect_min[0] <= point[0] <= rect_max[0] and rect_min[1] <= point[1] <= rect_max[1]
-
-
-def point_in_rotated_rectangle(point, center, length, width, angle):
-    """
-        Check if a point is inside a rotated rectangle
-    :param point: a point
-    :param center: rectangle center
-    :param length: rectangle length
-    :param width: rectangle width
-    :param angle: rectangle angle [rad]
-    """
-    c, s = np.cos(angle), np.sin(angle)
-    r = np.array([[c, -s], [s, c]])
-    ru = r.dot(point - center)
-    return point_in_rectangle(ru, [-length/2, -width/2], [length/2, width/2])
-
-
-def point_in_ellipse(point, center, angle, length, width):
-    """
-        Check if a point is inside an ellipse
-    :param point: a point
-    :param center: ellipse center
-    :param angle: ellipse main axis angle
-    :param length: ellipse big axis
-    :param width: ellipse small axis
-    """
-    c, s = np.cos(angle), np.sin(angle)
-    r = np.matrix([[c, -s], [s, c]])
-    ru = r.dot(point - center)
-    return np.sum(np.square(ru / np.array([length, width]))) < 1
-
-
[…]

### 2020-10-13 supplementary/code/highway_env/vehicle/behavior.py

@@ -1,474 +1,0 @@
-from __future__ import division, print_function
-import numpy as np
-from highway_env.vehicle.control import ControlledVehicle
-from highway_env import utils
-
-
-class IDMVehicle(ControlledVehicle):
-    """
-        A vehicle using both a longitudinal and a lateral decision policies.
-
-        - Longitudinal: the IDM model computes an acceleration given the preceding vehicle's distance and velocity.
-        - Lateral: the MOBIL model decides when to change lane by maximizing the acceleration of nearby vehicles.
-        """
-
-    # Longitudinal policy parameters
-    ACC_MAX = 6.0  # [m/s2]
-    COMFORT_ACC_MAX = 3.0  # [m/s2]
-    COMFORT_ACC_MIN = -5.0  # [m/s2]
-    DISTANCE_WANTED = 5.0 + ControlledVehicle.LENGTH  # [m]
-    TIME_WANTED = 1.5  # [s]
-    DELTA = 4.0  # []
-
-    # Lateral policy parameters
-    POLITENESS = 0.  # in [0, 1]
-    LANE_CHANGE_MIN_ACC_GAIN = 0.2  # [m/s2]
-    LANE_CHANGE_MAX_BRAKING_IMPOSED = 2.0  # [m/s2]
-    LANE_CHANGE_DELAY = 1.0  # [s]
-
-    def __init__(self, road, position,
-                 heading=0,
-                 velocity=0,
-                 target_lane_index=None,
-                 target_velocity=None,
-                 route=None,
-                 enable_lane_change=True,
-                 timer=None):
-        super(IDMVehicle, self).__init__(road, position, heading, velocity, target_lane_index, target_velocity, route)
-        self.enable_lane_change = enable_lane_change
-        self.timer = timer or (np.sum(self.position)*np.pi) % self.LANE_CHANGE_DELAY
-
-    def randomize_behavior(self):
-        pass
-
-    @classmethod
-    def create_from(cls, vehicle):
-        """
-            Create a new vehicle from an existing one.
-            The vehicle dynamics and target dynamics are copied, other properties are default.
-
-        :param vehicle: a vehicle
-        :return: a new vehicle at the same dynamical state
-        """
-        v = cls(vehicle.road, vehicle.position, heading=vehicle.heading, velocity=vehicle.velocity,
-                target_lane_index=vehicle.target_lane_index, target_velocity=vehicle.target_velocity,
-                route=vehicle.route, timer=getattr(vehicle, 'timer', None))
-        return v
-
[…]

### 2020-10-13 supplementary/code/highway_env/vehicle/control.py

@@ -1,281 +1,0 @@
-from __future__ import division, print_function
-import numpy as np
-import copy
-from highway_env import utils
-from highway_env.vehicle.dynamics import Vehicle
-
-
-class ControlledVehicle(Vehicle):
-    """
-        A vehicle piloted by two low-level controller, allowing high-level actions
-        such as cruise control and lane changes.
-
-        - The longitudinal controller is a velocity controller;
-        - The lateral controller is a heading controller cascaded with a lateral position controller.
-    """
-
-    TAU_A = 0.6  # [s]
-    TAU_DS = 0.14  # [s]
-    PURSUIT_TAU = 1.5*TAU_DS  # [s]
-    KP_A = 1 / TAU_A
-    KP_HEADING = 1 / TAU_DS
-    KP_LATERAL = KP_HEADING / 7  # [1/s]
-    MAX_STEERING_ANGLE = np.pi / 3  # [rad]
-
-    DELTA_VELOCITY = 5  # [m/s]
-
-    def __init__(self,
-                 road,
-                 position,
-                 heading=0,
-                 velocity=0,
-                 target_lane_index=None,
-                 target_velocity=None,
-                 route=None):
-        super(ControlledVehicle, self).__init__(road, position, heading, velocity)
-        self.target_lane_index = target_lane_index or self.lane_index
-        self.target_velocity = target_velocity or self.velocity
-        self.route = route
-
-    @classmethod
-    def create_from(cls, vehicle):
-        """
-            Create a new vehicle from an existing one.
-            The vehicle dynamics and target dynamics are copied, other properties are default.
-
-        :param vehicle: a vehicle
-        :return: a new vehicle at the same dynamical state
-        """
-        v = cls(vehicle.road, vehicle.position, heading=vehicle.heading, velocity=vehicle.velocity,
-                target_lane_index=vehicle.target_lane_index, target_velocity=vehicle.target_velocity,
-                route=vehicle.route)
-        return v
-
-    def plan_route_to(self, destination):
-        """
-            Plan a route to a destination in the road network
-
-        :param destination: a node in the road network
-        """
-        path = self.road.network.shortest_path(self.lane_index[1], destination)
-        if path:
-            self.route = [self.lane_index] + [(path[i], path[i + 1], None) for i in range(len(path) - 1)]
-        else:
-            self.route = [self.lane_index]
-        return self
-
-    def act(self, action=None):
-        """
-            Perform a high-level action to change the desired lane or velocity.
-
-            - If a high-level action is provided, update the target velocity and lane;
[…]

### 2020-10-13 supplementary/code/highway_env/vehicle/dynamics.py

@@ -1,276 +1,0 @@
-from __future__ import division, print_function
-
-import copy
-
-import numpy as np
-import pandas as pd
-from collections import deque
-
-from highway_env import utils
-from highway_env.logger import Loggable
-
-
-class Vehicle(Loggable):
-    """
-        A moving vehicle on a road, and its dynamics.
-
-        The vehicle is represented by a dynamical system: a modified bicycle model.
-        It's state is propagated depending on its steering and acceleration actions.
-    """
-    COLLISIONS_ENABLED = True
-    """ Enable collision detection between vehicles """
-
-    LENGTH = 5.0
-    """ Vehicle length [m] """
-    WIDTH = 2.0
-    """ Vehicle width [m] """
-    DEFAULT_VELOCITIES = [23, 25]
-    """ Range for random initial velocities [m/s] """
-    MAX_VELOCITY = 40
-    """ Maximum reachable velocity [m/s] """
-
-    def __init__(self, road, position, heading=0, velocity=0):
-        self.road = road
-        self.position = np.array(position).astype('float')
-        self.heading = heading
-        self.velocity = velocity
-        self.lane_index = self.road.network.get_closest_lane_index(self.position) if self.road else np.nan
-        self.lane = self.road.network.get_lane(self.lane_index) if self.road else None
-        self.action = {'steering': 0, 'acceleration': 0}
-        self.crashed = False
-        self.log = []
-        self.history = deque(maxlen=30)
-
-    @classmethod
-    def make_on_lane(cls, road, lane_index, longitudinal, velocity=0):
-        """
-            Create a vehicle on a given lane at a longitudinal position.
-
-        :param road: the road where the vehicle is driving
-        :param lane_index: index of the lane where the vehicle is located
-        :param longitudinal: longitudinal position along the lane
-        :param velocity: initial velocity in [m/s]
-        :return: A vehicle with at the specified position
-        """
-        lane = road.network.get_lane(lane_index)
-        if velocity is None:
-            velocity = lane.speed_limit
-        return cls(road, lane.position(longitudinal, 0), lane.heading_at(longitudinal), velocity)
-
-    @classmethod
-    def create_random(cls, road, velocity=None, spacing=1):
-        """
-            Create a random vehicle on the road.
-
-            The lane and /or velocity are chosen randomly, while longitudinal position is chosen behind the last
-            vehicle in the road with density based on the number of lanes.
-
-        :param road: the road where the vehicle is driving
[…]

### 2020-10-13 supplementary/code/highway_env/vehicle/graphics.py

@@ -1,183 +1,0 @@
-from __future__ import division, print_function
-
-import itertools
-
-import numpy as np
-import pygame
-
-from highway_env.vehicle.dynamics import Vehicle, Obstacle
-from highway_env.vehicle.control import ControlledVehicle, MDPVehicle
-from highway_env.vehicle.behavior import IDMVehicle, LinearVehicle
-
-
-class VehicleGraphics(object):
-    RED = (255, 100, 100)
-    GREEN = (50, 200, 0)
-    BLUE = (100, 200, 255)
-    YELLOW = (200, 200, 0)
-    BLACK = (60, 60, 60)
-    PURPLE = (200, 0, 150)
-    DEFAULT_COLOR = YELLOW
-    EGO_COLOR = GREEN
-
-    @classmethod
-    def display(cls, vehicle, surface, transparent=False, offscreen=False):
-        """
-            Display a vehicle on a pygame surface.
-
-            The vehicle is represented as a colored rotated rectangle.
-
-        :param vehicle: the vehicle to be drawn
-        :param surface: the surface to draw the vehicle on
-        :param transparent: whether the vehicle should be drawn slightly transparent
-        :param offscreen: whether the rendering should be done offscreen or not
-        """
-        v = vehicle
-        s = pygame.Surface((surface.pix(v.LENGTH), surface.pix(v.LENGTH)), pygame.SRCALPHA)  # per-pixel alpha
-        rect = (0, surface.pix(v.LENGTH) / 2 - surface.pix(v.WIDTH) / 2, surface.pix(v.LENGTH), surface.pix(v.WIDTH))
-        pygame.draw.rect(s, cls.get_color(v, transparent), rect, 0)
-        pygame.draw.rect(s, cls.BLACK, rect, 1)
-        if not offscreen:  # convert_alpha throws errors in offscreen mode TODO() Explain why
-            s = pygame.Surface.convert_alpha(s)
-        h = v.heading if abs(v.heading) > 2 * np.pi / 180 else 0
-        # Centered rotation
-        position = (surface.pos2pix(v.position[0], v.position[1]))
-        cls.blitRotate(surface, s, position, np.rad2deg(-h))
-
-    @staticmethod
-    def blitRotate(surf, image, pos, angle, origin_pos=None, show_rect=False):
-        """Many thanks to https://stackoverflow.com/a/54714144 """
-        # calculate the axis aligned bounding box of the rotated image
[…]

### 2020-10-13 supplementary/code/highway_env/vehicle/uncertainty/prediction.py

@@ -1,236 +1,0 @@
-import copy
-
-import numpy as np
-
-from highway_env import utils
-from highway_env.interval import polytope, LPV, interval_absolute_to_local, \
-    interval_local_to_absolute
-from highway_env.vehicle.behavior import LinearVehicle
-from highway_env.vehicle.control import MDPVehicle
-
-
-class IntervalVehicle(LinearVehicle):
-    """
-        Estimator for the interval-membership of a LinearVehicle under parameter uncertainty.
-
-        The model trajectory is stored in a model_vehicle, and the lower and upper bounds of the states are stored
-        in a min_vehicle and max_vehicle. Note that these vehicles do not follow a proper Vehicle dynamics, and
-        are only used for storage of the bounds.
-    """
-    def __init__(self,
-                 road,
-                 position,
-                 heading=0,
-                 velocity=0,
-                 target_lane_index=None,
-                 target_velocity=None,
-                 route=None,
-                 enable_lane_change=True,
-                 timer=None,
-                 theta_a_i=None,
-                 theta_b_i=None,
-                 data=None):
-        """
-        :param theta_a_i: The interval of possible acceleration parameters
-        :param theta_b_i: The interval of possible steering parameters
-        """
-        super().__init__(road,
-                         position,
-                         heading,
-                         velocity,
-                         target_lane_index,
-                         target_velocity,
-                         route,
-                         enable_lane_change,
-                         timer)
-        self.theta_a_i = theta_a_i if theta_a_i is not None else LinearVehicle.ACCELERATION_RANGE
-        self.theta_b_i = theta_b_i if theta_b_i is not None else LinearVehicle.STEERING_RANGE
-        self.data = data
-        self.interval = VehicleInterval(self)
-        self.trajectory = []
-        self.interval_trajectory = []
-        self.longitudinal_lpv, self.lateral_lpv = None, None
-        self.previous_target_lane_index = self.target_lane_index
-
-    @classmethod
-    def create_from(cls, vehicle):
-        v = cls(vehicle.road,
-                vehicle.position,
-                heading=vehicle.heading,
-                velocity=vehicle.velocity,
-                target_lane_index=getattr(vehicle, 'target_lane_index', None),
-                target_velocity=getattr(vehicle, 'target_velocity', None),
-                route=getattr(vehicle, 'route', None),
[…]

### 2020-10-13 supplementary/code/obstacle_env/__init__.py

@@ -1,7 +1,0 @@
-from gym.envs.registration import register
-
-register(
-    id='obstacle-v0',
-    entry_point='obstacle_env.envs:ObstacleEnv',
-    max_episode_steps=20,
-)

### 2020-10-13 supplementary/code/obstacle_env/dynamics.py

@@ -1,221 +1,0 @@
-from __future__ import print_function, division
-import numpy as np
-from scipy import signal
-
-
-class Dynamics1D(object):
-    """
-        A fourth-order one-dimensional dynamical system.
-    """
-    DEFAULT_PARAMS = {'Cx': 1.0,
-                      'w0': 50.0,
-                      'zeta': 1.0,
-                      'dt': 1/30,
-                      'acceleration': 5,
-                      'perturbation': 0.1}
-
-    def __init__(self, state=None, params=None):
-        self.A = self.B = self.C = self.D = None
-        self.discrete = self.continuous = None
-        if params is None:
-            params = self.DEFAULT_PARAMS
-        self.params = params
-        self.derivative = None
-
-        self.continuous_dynamics()
-        self.discrete_dynamics()
-
-        if state is None:
-            state = np.zeros((np.shape(self.A)[0], 1))
-        self.state = state
-        self.control = np.zeros((1, 1))
-        self.desired_action = 0
-
-        self.crashed = False
-
-    def continuous_dynamics(self):
-        """
-            Continuous state-space model
-        """
-        self.A = np.array(
-            [[0, 1, 0, 0],
-             [0, -self.params['Cx'], 1, 0],
-             [0, 0, 0, 1],
-             [0, 0, -self.params['w0']**2, -2*self.params['zeta']*self.params['w0']]])
-        self.B = np.array([[0], [0], [0], [self.params['w0']**2]])
-        self.C = np.identity(np.shape(self.A)[0])
-        self.D = np.zeros(np.shape(self.B))
-
-        self.continuous = (self.A, self.B, self.C, self.D)
-
-    def discrete_dynamics(self):
-        """
-            Discrete state-space model
-        """
-
-        self.discrete = signal.cont2discrete(self.continuous, self.params['dt'], method='zoh')
-
-    def act(self, action):
-        if action == 'RIGHT':
-            self.control = np.array([1])
-        elif action == 'LEFT':
-            self.control = np.array([-1])
-        else:
-            self.control = np.array([0])
-
-    def step(self):
-        """
-            Step the dynamics
-        """
-        # self.state = np.dot(self.discrete[0], self.state)+np.dot(self.discrete[1], self.control)
-        self.derivative = np.dot(self.continuous[0], self.state)+np.dot(self.continuous[1], self.control)
[…]

### 2020-10-13 supplementary/code/obstacle_env/envs/__init__.py

@@ -1,1 +1,0 @@
-from obstacle_env.envs.obstacle import ObstacleEnv

### 2020-10-13 supplementary/code/obstacle_env/envs/obstacle.py

@@ -1,309 +1,0 @@
-from __future__ import print_function, division
-import copy
-import numpy as np
-import gym
-from gym import spaces
-from gym.utils import seeding
-
-from obstacle_env.dynamics import Dynamics2D2
-from obstacle_env.graphics import EnvViewer
-from obstacle_env.scene import Scene2D, PolarGrid
-
-
-class ObstacleEnv(gym.Env):
-    metadata = {'render.modes': ['human', 'rgb_array']}
-
-    config = {
-        "simulation_frequency": 10,
-        "policy_frequency": 2,
-        "grid_cells": 16,
-        "collision_reward": -0.5,
-        "observation_type": "grid",
-        "observation_noise": 0.1,
-    }
-
-    def __init__(self):
-        # Seeding
-        self.np_random = None
-        self.seed()
-
-        # Dynamics
-        params = Dynamics2D2.DEFAULT_PARAMS.update({'dt': 1 / self.config["simulation_frequency"]})
-        self.dynamics = Dynamics2D2(params=params)
-        self.dynamics.desired_action = self.np_random.randint(1, len(self.dynamics.ACTIONS))
-
-        # Scene
-        self.scene = Scene2D()
-        self.scene.create_random_scene(np_random=self.np_random)
-        self.grid = PolarGrid(self.scene, cells=self.config["grid_cells"])
-
-        # Spaces
-        self.action_space = spaces.Discrete(len(self.dynamics.ACTIONS))
-        low_obs = np.hstack((-self.dynamics.terminal_velocity * np.ones((2,)),
-                             -self.dynamics.params['acceleration'] * np.ones((2,)),
-                             0 * np.ones((self.grid.cells,)),))
-        high_obs = np.hstack((self.dynamics.terminal_velocity * np.ones((2,)),
-                              self.dynamics.params['acceleration'] * np.ones((2,)),
-                              self.grid.MAXIMUM_RANGE * np.ones((self.grid.cells,)),))
-        self.observation_space = spaces.Box(low=low_obs, high=high_obs, dtype=np.float32)
-
-        # Viewer
-        self.viewer = None
-        self.automatic_rendering_callback = None
-        self.should_update_rendering = True
-        self.rendering_mode = 'human'
-        self.enable_auto_render = False
-
-        self.lpv = None
-
-        self.steps = 0
-        self.time = 0
-        self.done = False
-        self.trajectory = []
-        self.interval_trajectory = []
-        self.automatic_record_callback = None
-
[…]

### 2020-10-13 supplementary/code/obstacle_env/graphics.py

@@ -1,241 +1,0 @@
-from __future__ import print_function, division
-
-import datetime
-import shutil
-
-import numpy as np
-import pygame
-import os
-
-from obstacle_env.scene import PolarGrid
-
-
-class EnvViewer(object):
-    """
-        A viewer to render an environment.
-    """
-    SCREEN_WIDTH = 800
-    SCREEN_HEIGHT = 800
-    SAVE_IMAGES = True
-
-    def __init__(self, env, record_video=True):
-        self.env = env
-        self.record_video = record_video
-
-        pygame.init()
-        pygame.display.set_caption("Obstacle-env")
-        panel_size = (self.SCREEN_WIDTH, self.SCREEN_HEIGHT)
-        self.screen = pygame.display.set_mode([self.SCREEN_WIDTH, self.SCREEN_HEIGHT])
-        self.sim_surface = SimulationSurface(panel_size, 0, pygame.Surface(panel_size))
-        self.clock = pygame.time.Clock()
-
-        self.agent_display = None
-        self.agent_surface = None
-        self.frame = 0
-
-    def set_agent_display(self, agent_display):
-        if self.agent_display is None:
-            self.agent_display = agent_display
-            self.screen = pygame.display.set_mode((self.SCREEN_WIDTH * 2, self.SCREEN_HEIGHT))
-            self.agent_surface = pygame.Surface((self.SCREEN_WIDTH, self.SCREEN_HEIGHT))
-
-    def handle_events(self):
-        """
-            Handle pygame events by forwarding them to the display and environment vehicle.
-        """
-        for event in pygame.event.get():
-            if event.type == pygame.QUIT:
-                self.env.close()
-            self.sim_surface.handle_event(event)
-            if self.env.dynamics:
-                DynamicsGraphics.handle_event(self.env.dynamics, event)
-
-    def display(self, show_grid=False):
-        """
-            Display the scene on a pygame window.
-        """
-        self.sim_surface.move_display_window_to(self.window_position())
-        Scene2dGraphics.display(self.env.scene, self.sim_surface)
-        DynamicsGraphics.display(self.env.dynamics, self.sim_surface)
-        if show_grid:
-            self.env.grid.trace(self.env.dynamics.position)
-            DynamicsGraphics.display_grid(self.env.grid, self.sim_surface)
-
-        if self.agent_display:
-            self.agent_display(self.agent_surface, self.sim_surface)
[…]

### 2020-10-13 supplementary/code/obstacle_env/scene.py

@@ -1,126 +1,0 @@
-from __future__ import print_function, division
-import numpy as np
-import math
-
-
-class Scene1D(object):
-    BOUNDS = 10
-
-    def __init__(self):
-        self.obstacles = [{'position': np.array([-self.BOUNDS]), 'radius': 1},
-                          {'position': np.array([+self.BOUNDS]), 'radius': 1}]
-
-
-class Scene2D(object):
-    BOUNDS_X = 50
-    BOUNDS_Y = 50
-
-    def __init__(self):
-        self.obstacles = []
-        self.goal = None
-        self.create_random_scene()
-
-    def create_random_scene(self, np_random=np.random):
-        self.obstacles = []
-        for _ in range(400):
-            o = np.zeros((2, 1))
-            while np.linalg.norm(o) < 2:
-                o = np.array([[self.BOUNDS_X * (np_random.rand() * 2 - 1)],
-                              [self.BOUNDS_Y * (np_random.rand() * 2 - 1)]])
-            self.obstacles.append({'position': o, 'radius': 1})
-        self.goal = {'position': np.array([[self.BOUNDS_X * (np_random.rand() * 2 - 1)],
-                                           [self.BOUNDS_Y * (np_random.rand() * 2 - 1)]]),
-                     'radius': 1}
-
-    def create_corridor_scene(self):
-        for y in np.linspace(-self.BOUNDS_Y, self.BOUNDS_Y, int(self.BOUNDS_Y)+1):
-            self.obstacles.append({'position': np.array([[-self.BOUNDS_X], [y]]), 'radius': 1})
-        for x in np.linspace(-self.BOUNDS_X, 5*self.BOUNDS_X, int(3*self.BOUNDS_Y)+1):
-            self.obstacles.append({'position': np.array([[x], [-self.BOUNDS_Y]]), 'radius': 1})
-            self.obstacles.append({'position': np.array([[x], [self.BOUNDS_Y]]), 'radius': 1})
-        self.obstacles.extend([
-            {'position': np.array([[10], [0]]), 'radius': 1},
-            {'position': np.array([[20], [2]]), 'radius': 1},
-            {'position': np.array([[20], [-2]]), 'radius': 1},
-        ])
-
-
-class PolarGrid:
-    MAXIMUM_RANGE = 12
-
-    def __init__(self, scene, cells=8):
-        self.scene = scene
-        self.cells = cells
-        self.angle = 2 * math.pi / self.cells
[…]

### 2020-10-13 supplementary/code/rl_agents/agents/common/abstract.py

@@ -1,111 +1,0 @@
-from abc import ABC, abstractmethod
-
-from rl_agents.configuration import Configurable
-
-
-class AbstractAgent(Configurable, ABC):
-
-    def __init__(self, config=None):
-        super(AbstractAgent, self).__init__(config)
-        self.writer = None  # Tensorboard writer
-        self.directoy = None  # Run directory
-
-    """
-        An abstract class specifying the interface of a generic agent.
-    """
-    @abstractmethod
-    def record(self, state, action, reward, next_state, done, info):
-        """
-            Record a transition of the environment to update the agent
-        :param state: s, the current state of the agent
-        :param action: a, the action performed
-        :param reward: r(s, a), the reward collected
-        :param next_state: s', the new state of the agent after the action was performed
-        :param done: whether the next state is terminal
-        :return:
-        """
-        raise NotImplementedError()
-
-    @abstractmethod
-    def act(self, state):
-        """
-            Pick an action
-
-        :param state: s, the current state of the agent
-        :return: a, the action to perform
-        """
-        raise NotImplementedError()
-
-    def plan(self, state):
-        """
-            Plan an optimal trajectory from an initial state.
-
-        :param state: s, the initial state of the agent
-        :return: [a0, a1, a2...], a sequence of actions to perform
-        """
-        return [self.act(state)]
-
-    @abstractmethod
-    def reset(self):
-        """
-            Reset the agent to its initial internal state
-        """
-        raise NotImplementedError()
-
-    @abstractmethod
-    def seed(self, seed=None):
-        """
-            Seed the agent's random number generator
-        :param seed: the seed to be used to generate random numbers
-        :return: the used seed
-        """
-        raise NotImplementedError()
-
-    @abstractmethod
-    def save(self, filename):
-        """
-            Save the model parameters to a file
-        :param str filename: the path of the file to save the model parameters in
-        """
-        raise NotImplementedError()
-
-    @abstractmethod
-    def load(self, filename):
-        """
-            Load the model parameters from a file
-        :param str filename: the path of the file to load the model parameters from
-        """
-        raise NotImplementedError()
-
-    def eval(self):
-        """
-            Set to testing mode. Disable any unnecessary exploration.
-        """
-        pass
-
-    def set_writer(self, writer):
-        """
-            Set a tensorboard writer to log the agent internal variables.
-        :param SummaryWriter writer: a summary writer
-        """
-        self.writer = writer
-
[…]

### 2020-10-13 supplementary/code/rl_agents/agents/common/factory.py

@@ -1,121 +1,0 @@
-import copy
-import importlib
-import json
-import logging
-import gym
-
-logger = logging.getLogger(__name__)
-
-
-def agent_factory(environment, config):
-    """
-        Handles creation of agents.
-
-    :param environment: the environment
-    :param config: configuration of the agent, must contain a '__class__' key
-    :return: a new agent
-    """
-    if "__class__" in config:
-        path = config['__class__'].split("'")[1]
-        module_name, class_name = path.rsplit(".", 1)
-        agent_class = getattr(importlib.import_module(module_name), class_name)
-        agent = agent_class(environment, config)
-        return agent
-    else:
-        raise ValueError("The configuration should specify the agent __class__")
-
-
-def load_agent(agent_path, env):
-    """
-        Load an agent from a configuration file.
-
-    :param agent_path: the path to the agent configuration file
-    :param env: the environment with which the agent interacts
-    :return: the agent
-    """
-    # Load agent from file
-    if not isinstance(agent_path, dict):
-        with open(agent_path) as f:
-            agent_config = json.loads(f.read())
-    else:
-        agent_config = agent_path
-
-    return agent_factory(env, agent_config)
-
-
-def load_environment(env_config):
-    """
-        Load an environment from a configuration file.
-
-    :param env_config: the configuration, or path to the environment configuration file
-    :return: the environment
-    """
-    # Load the environment config from file
-    if not isinstance(env_config, dict):
-        with open(env_config) as f:
-            env_config = json.loads(f.read())
-
-    # Make the environment
-    if env_config.get("import_module", None):
-        __import__(env_config["import_module"])
-    try:
-        env = gym.make(env_config['id'])
-        # Save env module in order to be able to import it again
-        env.import_module = env_config.get("import_module", None)
-    except KeyError:
-        raise ValueError("The gym register id of the environment must be provided")
-    except gym.error.UnregisteredEnv:
-        # The environment is unregistered.
-        print("import_module", env_config["import_module"])
-        raise gym.error.UnregisteredEnv('Environment {} not registered. The environment module should be specified by '
-                                        'the "import_module" key of the environment configuration'.format(
-                                            env_config['id']))
-
-    # Configure the environment, if supported
-    try:
-        env.unwrapped.configure(env_config)
-        # Reset the environment to ensure configuration is applied
-        env.reset()
-    except AttributeError as e:
[…]

### 2020-10-13 supplementary/code/rl_agents/agents/common/graphics.py

@@ -1,32 +1,0 @@
-from __future__ import division, print_function
-
-from rl_agents.agents.tree_search.abstract import AbstractTreeSearchAgent
-from rl_agents.agents.tree_search.graphics.graphics import TreeGraphics
-from rl_agents.agents.tree_search.graphics.robust_epc import RobustEPCGraphics
-from rl_agents.agents.tree_search.graphics.robust import DiscreteRobustPlannerGraphics, IntervalRobustPlannerGraphics
-from rl_agents.agents.tree_search.robust import DiscreteRobustPlannerAgent, IntervalRobustPlannerAgent
-from rl_agents.agents.tree_search.robust_epc import RobustEPCAgent
-
-
-class AgentGraphics(object):
-    """
-        Graphical visualization of any Agent implementing AbstractAgent.
-    """
-    @classmethod
-    def display(cls, agent, agent_surface, sim_surface=None):
-        """
-            Display an agent visualization on a pygame surface.
-
-        :param agent: the agent to be displayed
-        :param agent_surface: the pygame surface on which the agent is displayed
-        :param sim_surface: the pygame surface on which the environment is displayed
-        """
-
-        if isinstance(agent, IntervalRobustPlannerAgent):
-            IntervalRobustPlannerGraphics.display(agent, agent_surface, sim_surface)
-        elif isinstance(agent, DiscreteRobustPlannerAgent):
-            DiscreteRobustPlannerGraphics.display(agent, agent_surface, sim_surface)
-        elif isinstance(agent, RobustEPCAgent):
-            RobustEPCGraphics.display(agent, agent_surface, sim_surface)
-        elif isinstance(agent, AbstractTreeSearchAgent):
-            TreeGraphics.display(agent, agent_surface)

### 2020-10-13 supplementary/code/rl_agents/agents/common/utils.py

@@ -1,99 +1,0 @@
-import logging
-import os
-import re
-import numpy as np
-from subprocess import PIPE, run, check_output
-import torch
-
-
-logger = logging.getLogger(__name__)
-
-
-def sample_simplex(coeff, bias, min_x, max_x, np_random=np.random):
-    """
-    Sample from a simplex.
-
-    The simplex is defined by:
-        w.x + b <= 0
-        x_min <= x <= x_max
-
-    Warning: this is not uniform sampling.
-
-    :param coeff: coefficient w
-    :param bias: bias b
-    :param min_x: lower bound on x
-    :param max_x: upper bound on x
-    :param np_random: source of randomness
-    :return: a sample from the simplex
-    """
-    x = np.zeros(len(coeff))
-    indexes = np.asarray(range(0, len(coeff)))
-    np_random.shuffle(indexes)
-    remain_indexes = np.copy(indexes)
-    for i_index, index in enumerate(indexes):
-        remain_indexes = remain_indexes[1:]
-        current_coeff = np.take(coeff, remain_indexes)
-        full_min = np.full(len(remain_indexes), min_x)
-        full_max = np.full(len(remain_indexes), max_x)
-        dot_max = np.dot(current_coeff, full_max)
-        dot_min = np.dot(current_coeff, full_min)
-        min_xi = (bias - dot_max) / coeff[index]
-        max_xi = (bias - dot_min) / coeff[index]
-        min_xi = np.max([min_xi, min_x])
-        max_xi = np.min([max_xi, max_x])
-        xi = min_xi + np_random.random_sample() * (max_xi - min_xi)
-        bias = bias - xi * coeff[index]
-        x[index] = xi
-        if len(remain_indexes) == 1:
-            break
-    last_index = remain_indexes[0]
-    x[last_index] = bias / coeff[last_index]
-    return x
-
-
-def load_pytorch():
-    torch.backends.cudnn.benchmark = False
-    torch.backends.cudnn.enabled = False
-    logger.info("Using torch.multiprocessing.set_start_method('spawn')")
-    import torch.multiprocessing as multiprocessing
-    try:
-        multiprocessing.set_start_method('spawn')
-    except RuntimeError as e:
-        logger.warning(str(e))
-
-
-def get_gpu_memory_map():
-    result = check_output(['nvidia-smi', '--query-gpu=memory.used', '--format=csv,nounits,noheader'])
-    return [int(x) for x in result.split()]
-
-
-def least_used_device():
[…]

### 2020-10-13 supplementary/code/rl_agents/agents/tree_search/abstract.py

@@ -1,325 +1,0 @@
-import logging
-import numpy as np
-from gym.utils import seeding
-
-from rl_agents.agents.common.abstract import AbstractAgent
-from rl_agents.agents.common.factory import preprocess_env, safe_deepcopy_env
-from rl_agents.configuration import Configurable
-from rl_agents.agents.tree_search.graphics.graphics import TreePlot
-
-logger = logging.getLogger(__name__)
-
-
-class AbstractTreeSearchAgent(AbstractAgent):
-    def __init__(self,
-                 env,
-                 config=None):
-        """
-            A new Tree Search agent.
-        :param env: The environment
-        :param config: The agent configuration. Use default if None.
-        """
-        super(AbstractTreeSearchAgent, self).__init__(config)
-        self.env = env
-        self.planner = self.make_planner()
-        self.previous_actions = []
-        self.remaining_horizon = 0
-        self.steps = 0
-
-    @classmethod
-    def default_config(cls):
-        return {
-            "env_preprocessors": [],
-            "display_tree": False
-        }
-
-    def make_planner(self):
-        raise NotImplementedError()
-
-    def plan(self, observation):
-        """
-            Plan an optimal sequence of actions.
-
-            Start by updating the previously found tree with the last action performed.
-
-        :param observation: the current state
-        :return: the list of actions
-        """
-        self.steps += 1
-        replanning_required = self.step(self.previous_actions)
-        if replanning_required:
-            env = preprocess_env(self.env, self.config["env_preprocessors"])
-            actions = self.planner.plan(state=env, observation=observation)
-        else:
-            actions = self.previous_actions[1:]
-        self.write_tree()
-
-        self.previous_actions = actions
-        return actions
-
-    def step(self, actions):
-        """
-            Handle receding horizon mechanism
-        :return: whether a replanning is required
-        """
-        replanning_required = self.remaining_horizon == 0 or len(actions) <= 1
-        if replanning_required:
-            self.remaining_horizon = self.config["receding_horizon"] - 1
-        else:
-            self.remaining_horizon -= 1
-
-        self.planner.step(actions)
-        return replanning_required
-
-    def reset(self):
-        self.planner.step_by_reset()
-        self.steps = 0
-
-    def seed(self, seed=None):
-        return self.planner.seed(seed)
-
-    def record(self, state, action, reward, next_state, done, info):
-        pass
-
-    def act(self, state):
-        return self.plan(state)[0]
-
-    def save(self, filename):
[…]

### 2020-10-13 supplementary/code/rl_agents/agents/tree_search/deterministic.py

@@ -1,121 +1,0 @@
-import numpy as np
-import logging
-from rl_agents.agents.common.factory import safe_deepcopy_env
-from rl_agents.agents.tree_search.abstract import Node, AbstractTreeSearchAgent, AbstractPlanner
-
-logger = logging.getLogger(__name__)
-
-
-class DeterministicPlannerAgent(AbstractTreeSearchAgent):
-    """
-        An agent that performs optimistic planning in deterministic MDPs.
-    """
-    def make_planner(self):
-        return OptimisticDeterministicPlanner(self.env, self.config)
-
-
-class OptimisticDeterministicPlanner(AbstractPlanner):
-    """
-       An implementation of Optimistic Planning for Deterministic systems.
-    """
-    def __init__(self, env, config=None):
-        super().__init__(config)
-        self.env = env
-        self.leaves = None
-
-    def make_root(self):
-        root = DeterministicNode(None, planner=self)
-        self.leaves = [root]
-        return root
-
-    def run(self):
-        """
-            Run an OptimisticDeterministicPlanner episode
-        """
-        leaf_to_expand = max(self.leaves, key=lambda n: n.get_value_upper_bound())
-        if leaf_to_expand.done:
-            return
-        leaf_to_expand.expand()
-        leaf_to_expand.backup_to_root()
-
-    def plan(self, state, observation):
-        self.root.state = state
-        for epoch in np.arange(self.config["budget"] // state.action_space.n):
-            logger.debug("Expansion {}/{}".format(epoch + 1, self.config["budget"] // state.action_space.n))
-            self.run()
-
-        return self.get_plan()
-
-    def step_by_subtree(self, action):
-        super(OptimisticDeterministicPlanner, self).step_by_subtree(action)
-        if not self.root.children:
-            self.leaves = [self.root]
-        #  v0 = r0 + g r1 + g^2 r2 +... and v1 = r1 + g r2 + ... = (v0-r0)/g
-        for leaf in self.leaves:
-            leaf.value = (leaf.value - self.root.reward) / self.config["gamma"]
-            leaf.value_upper_bound = (leaf.value_upper_bound - self.root.reward) / self.config["gamma"]
-        self.root.backup_values()
-
-
-class DeterministicNode(Node):
-    def __init__(self, parent, planner, state=None, depth=0):
-        super(DeterministicNode, self).__init__(parent, planner)
-        self.state = state
-        self.depth = depth
-        self.reward = 0
-        self.value_upper_bound = 0
[…]

### 2020-10-13 supplementary/code/rl_agents/agents/tree_search/graphics/graphics.py

@@ -1,162 +1,0 @@
-from pathlib import Path
-
-import matplotlib as mpl
-import matplotlib.cm as cm
-import numpy as np
-import matplotlib.pyplot as plt
-
-from rl_agents.utils import remap, constrain
-
-
-class TreeGraphics(object):
-    """
-        Graphical visualization of a tree-search based agent.
-    """
-    RED = (255, 0, 0)
-    BLACK = (0, 0, 0)
-
-    @classmethod
-    def display(cls, agent, surface):
-        """
-            Display the whole tree.
-
-        :param agent: the agent to be displayed
-        :param surface: the pygame surface on which the agent is displayed
-        """
-        if not surface:
-            return
-        import pygame
-        cell_size = (surface.get_width() // (agent.planner.config['max_depth'] + 1), surface.get_height())
-        pygame.draw.rect(surface, cls.BLACK, (0, 0, surface.get_width(), surface.get_height()), 0)
-        cls.display_node(agent.planner.root, agent.env.action_space, surface, (0, 0), cell_size,
-                         config=agent.planner.config, depth=0, selected=True)
-
-        actions = agent.planner.get_plan()
-        font = pygame.font.Font(None, 13)
-        text = font.render('-'.join(map(str, actions)), 1, (10, 10, 10), (255, 255, 255))
-        surface.blit(text, (1, surface.get_height()-10))
-
-    @classmethod
-    def display_node(cls, node, action_space, surface, origin, size,
-                     config=0,
-                     depth=0,
-                     selected=False):
-        """
-            Display an MCTS node at a given position on a surface.
-
-        :param node: the MCTS node to be displayed
-        :param action_space: the environment action space
-        :param surface: the pygame surface on which the node is displayed
-        :param origin: the location of the node on the surface [px]
-        :param size: the size of the node on the surface [px]
-        :param config: the agent configuration
-        :param depth: the depth of the node in the tree
-        :param selected: whether the node is within a selected branch of the tree
-        """
-        import pygame
-        # Display node value
-        cls.draw_node(node, surface, origin, size, config)
-
-        # Add selection display
-        if selected:
-            pygame.draw.rect(surface, cls.RED, (origin[0], origin[1], size[0], size[1]), 1)
-
-        if depth < 3:
-            cls.display_text(node, surface, origin, config)
-
[…]

### 2020-10-13 supplementary/code/rl_agents/agents/tree_search/graphics/robust.py

@@ -1,127 +1,0 @@
-import matplotlib as mpl
-import numpy as np
-from matplotlib import cm as cm
-
-from rl_agents.agents.common.factory import preprocess_env
-from rl_agents.agents.tree_search.graphics.graphics import TreeGraphics
-
-
-class DiscreteRobustPlannerGraphics(TreeGraphics):
-    @classmethod
-    def display(cls, agent, agent_surface, sim_surface):
-        plan = agent.planner.get_plan()
-        for env in [preprocess_env(agent.true_env, preprocessors) for preprocessors in agent.config["models"]]:
-            IntervalRobustPlannerGraphics.display_uncertainty(env, plan, sim_surface, trajectory=False)
-            # for vehicle in env.road.vehicles:
-            #     if hasattr(vehicle, ):
-            #         IntervalRobustPlannerGraphics.display(vehicle)
-            # for vehicle in env.road.vehicles:
-            #     vehicle.trajectory = []
-            # for action in plan[:horizon] + (horizon - len(plan)) * [1]:
-            #     env.step(action)
-            # for vehicle in env.road.vehicles:
-            #     if vehicle is env.vehicle:
-            #         continue
-            #     uncertainty_surface = pygame.Surface(sim_surface.get_size(), pygame.SRCALPHA, 32)
-            #     IntervalRobustPlannerGraphics.display_trajectory(vehicle.trajectory, uncertainty_surface, sim_surface,
-            #                                                      IntervalRobustPlannerGraphics.MODEL_TRAJ_COLOR)
-            #     sim_surface.blit(uncertainty_surface, (0, 0))
-        TreeGraphics.display(agent, agent_surface)
-
-    @classmethod
-    def draw_node(cls, node, surface, origin, size, config):
-        import pygame
-        cmap = cm.jet_r
-        norm = mpl.colors.Normalize(vmin=0, vmax=config["gamma"] / (1 - config["gamma"]))
-        n = np.size(node.value)
-        for i in range(n):
-            v = node.value[i] if n > 1 else node.value
-            color = cmap(norm(v), bytes=True)
-            pygame.draw.rect(surface, color, (origin[0] + i / n * size[0], origin[1], size[0] / n, size[1]), 0)
-
-
-class IntervalRobustPlannerGraphics(object):
-    """
-        Graphical visualization of the IntervalRobustPlannerAgent interval observer.
-    """
-    UNCERTAINTY_TIME_COLORMAP = cm.RdYlGn
-    MODEL_TRAJ_COLOR = (0, 0, 255)
[…]

### 2020-10-13 supplementary/code/rl_agents/agents/tree_search/graphics/robust_epc.py

@@ -1,108 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-from matplotlib.patches import Ellipse
-import matplotlib.transforms as transforms
-import matplotlib
-matplotlib.rc('text', usetex=True)
-import seaborn as sns
-import os
-
-from rl_agents.agents.tree_search.graphics.robust import IntervalRobustPlannerGraphics
-
-
-class RobustEPCGraphics(IntervalRobustPlannerGraphics):
-    SAVE_IMAGES = None
-
-    @classmethod
-    def display(cls, agent, agent_surface, sim_surface):
-        import pygame
-        robust_env = agent.robustify_env()
-        cls.display_uncertainty(robust_env=robust_env, plan=agent.get_plan(), surface=sim_surface)
-        if agent_surface and hasattr(agent, "sub_agent"):
-            true_theta = agent.env.unwrapped.dynamics.theta
-            surf_size = agent_surface.get_size()
-            figsize = (surf_size[0]/100, surf_size[1]/100)
-            save_to = None
-            if cls.SAVE_IMAGES:
-                save_to = agent.evaluation.run_directory / "ellipsoid.{}.{}.pdf".format(agent.evaluation.episode, len(agent.ellipsoids))
-            image_str, size = cls.plot_ellipsoid(agent.ellipsoids, true_theta, figsize=figsize, save_to=save_to)
-            surf = pygame.image.fromstring(image_str, size, "RGB")
-            agent_surface.blit(surf, (0, 0))
-
-    @classmethod
-    def display_uncertainty(cls, robust_env, plan, surface, trajectory=True):
-        import pygame
-        horizon = 3
-        if plan:
-            plan = plan[1:]  # First action has already been performed
-        plan = plan[:horizon]
-        for action in plan:
-            robust_env.step(action)
-        min_traj = [o[0] for o in robust_env.unwrapped.interval_trajectory]
-        max_traj = [o[1] for o in robust_env.unwrapped.interval_trajectory]
-        uncertainty_surface = pygame.Surface(surface.get_size(), pygame.SRCALPHA, 32)
-        cls.display_traj_uncertainty(min_traj, max_traj, uncertainty_surface, surface, cls.UNCERTAINTY_TIME_COLORMAP)
-        surface.blit(uncertainty_surface, (0, 0))
-
-    @classmethod
[…]

### 2020-10-13 supplementary/code/rl_agents/agents/tree_search/robust.py

@@ -1,107 +1,0 @@
-import numpy as np
-
-from rl_agents.agents.common.abstract import AbstractAgent
-from rl_agents.agents.common.factory import load_agent, preprocess_env
-from rl_agents.agents.tree_search.deterministic import DeterministicPlannerAgent, OptimisticDeterministicPlanner, \
-    DeterministicNode
-
-
-class DiscreteRobustPlannerAgent(DeterministicPlannerAgent):
-    def __init__(self,
-                 env,
-                 config=None):
-        self.true_env = env
-        super(DiscreteRobustPlannerAgent, self).__init__(env, config)
-
-    def make_planner(self):
-        return DiscreteRobustPlanner(self.env, self.config)
-
-    @classmethod
-    def default_config(cls):
-        config = super(DiscreteRobustPlannerAgent, cls).default_config()
-        config.update(dict(models=[]))
-        return config
-
-    def plan(self, observation):
-        envs = [preprocess_env(self.true_env, preprocessors) for preprocessors in self.config["models"]]
-        self.env = JointEnv(envs)
-        return super(DiscreteRobustPlannerAgent, self).plan(observation)
-
-
-class JointEnv(object):
-    def __init__(self, envs):
-        self.joint_state = envs
-
-    def step(self, action):
-        transitions = [state.step(action) for state in self.joint_state]
-        observations, rewards, terminals, info = zip(*transitions)
-        return observations, np.array(rewards), np.array(terminals), info
-
-    @property
-    def action_space(self):
-        return self.joint_state[0].action_space
-
-    def get_available_actions(self):
-        return list(set().union(*[s.get_available_actions() if hasattr(s, "get_available_actions")
-                                  else range(s.action_space.n)
-                                  for s in self.joint_state]))
-
-
-class DiscreteRobustPlanner(OptimisticDeterministicPlanner):
-    def make_root(self):
-        root = RobustNode(parent=None, planner=self)
-        self.leaves = [root]
-        return root
-
-    def run(self):
-        """
-            Run an OptimisticDeterministicPlanner episode
-        """
-        leaf_to_expand = max(self.leaves, key=lambda n: n.get_value_upper_bound())
-        leaf_to_expand.expand()
-        leaf_to_expand.backup_to_root()
-
-
-class RobustNode(DeterministicNode):
-    def get_value(self):
-        return np.min(self.value)
-
-    def get_value_upper_bound(self):
-        return np.min(self.value_upper_bound)
-
[…]

### 2020-10-13 supplementary/code/rl_agents/agents/tree_search/robust_epc.py

@@ -1,178 +1,0 @@
-import itertools
-import numpy as np
-
-from interval import LPV
-from rl_agents.agents.common.abstract import AbstractAgent
-from rl_agents.agents.common.factory import load_agent, safe_deepcopy_env
-
-
-class RobustEPCAgent(AbstractAgent):
-    """
-        Robust Estimation, Prediction and Control.
-    """
-
-    def __init__(self, env, config):
-        super().__init__(config)
-        self.A = np.array(self.config["A"])
-        self.B = np.array(self.config["B"])
-        self.phi = np.array(self.config["phi"])
-        self.env = env
-        self.env.unwrapped.automatic_record_callback = self.record_transition
-        self.data = []
-        self.robust_env = None
-        self.sub_agent = load_agent(self.config['sub_agent_path'], env)
-        self.ellipsoids = [self.ellipsoid()]
-
-    @classmethod
-    def default_config(cls):
-        return {
-            "gamma": 0.9,
-            "delta": 0.9,
-            "lambda": 1e-6,
-            "sigma": [[1]],
-            "A": [[1]],
-            "B": [[1]],
-            "D": [[1]],
-            "omega": [[0], [0]],
-            "phi": [[[1]]],
-            "simulation_frequency": 10,
-            "policy_frequency": 2,
-            "parameter_bound": 1
-        }
-
-    def record(self, state, action, reward, next_state, done, info):
-        """
-            Add a transition to the dataset D_[N].
-
-            The environment must be able to convert a discrete action to a continuous control.
-        :param state: state x_t at time t
-        :param action: action a_t performed
-        :param reward: reward r_t obtained
-        :param next_state: next state x_{t+dt} at time t+dt
-        :param done: is the state terminal
-        :param info: information about the transition
-        """
-        if hasattr(self.env.unwrapped, "automatic_record_callback"):
-            return
-        control = self.env.unwrapped.dynamics.action_to_control(action)
-        try:
-            derivative = self.env.unwrapped.dynamics.derivative
-        except AttributeError:
-            derivative = (next_state - state) * self.config["policy_frequency"]
-        self.record_transition((state, control, derivative))
-
-    def record_transition(self, state, derivative, control):
-        """
-            A callback that can be called by the environment in place of RobustEPCAgent.record(),
[…]

### 2020-10-13 supplementary/code/rl_agents/trainer/evaluation.py

@@ -1,266 +1,0 @@
-import datetime
-import json
-import logging
-import os
-from pathlib import Path
-import numpy as np
-from tensorboardX import SummaryWriter
-
-import rl_agents.trainer.logger
-from rl_agents.agents.common.graphics import AgentGraphics
-from rl_agents.configuration import serialize
-from rl_agents.trainer.graphics import RewardViewer
-from rl_agents.trainer.monitor import MonitorV2
-
-logger = logging.getLogger(__name__)
-
-
-class Evaluation(object):
-    """
-        The evaluation of an agent interacting with an environment to maximize its expected reward.
-    """
-
-    OUTPUT_FOLDER = 'out'
-    SAVED_MODELS_FOLDER = 'saved_models'
-    RUN_FOLDER = 'run_{}_{}'
-    METADATA_FILE = 'metadata.{}.json'
-    LOGGING_FILE = 'logging.{}.log'
-
-    def __init__(self,
-                 env,
-                 agent,
-                 directory=None,
-                 run_directory=None,
-                 num_episodes=1000,
-                 training=True,
-                 sim_seed=None,
-                 recover=None,
-                 display_env=True,
-                 display_agent=True,
-                 display_rewards=True,
-                 close_env=True):
-        """
-
-        :param env: The environment to be solved, possibly wrapping an AbstractEnv environment
-        :param AbstractAgent agent: The agent solving the environment
-        :param Path directory: Workspace directory path
-        :param Path run_directory: Run directory path
-        :param int num_episodes: Number of episodes run
-        !param training: Whether the agent is being trained or tested
-        :param sim_seed: The seed used for the environment/agent randomness source
-        :param recover: Recover the agent parameters from a file.
-                        - If True, it the default latest save will be used.
-                        - If a string, it will be used as a path.
-        :param display_env: Render the environment, and have a monitor recording its videos
-        :param display_agent: Add the agent graphics to the environment viewer, if supported
-        :param display_rewards: Display the performances of the agent through the episodes
-        :param close_env: Should the environment be closed when the evaluation is closed
-
-        """
-        self.env = env
-        self.agent = agent
-        self.num_episodes = num_episodes
-        self.training = training
-        self.sim_seed = sim_seed
-        self.close_env = close_env
-        self.display_env = display_env
-
-        self.directory = Path(directory or self.default_directory)
-        self.run_directory = self.directory / (run_directory or self.default_run_directory)
[…]

### 2020-10-13 supplementary/code/rl_agents/trainer/monitor.py

@@ -1,188 +1,0 @@
-import json
-import logging
-import os
-
-from gym.wrappers import Monitor
-from gym.wrappers.monitor import detect_training_manifests, collapse_env_infos, merge_stats_files
-from gym.wrappers.monitoring import video_recorder
-from gym.wrappers.monitoring.stats_recorder import StatsRecorder
-from gym.utils import atomic_write
-from gym.utils.json_utils import json_encode_np
-
-logger = logging.getLogger(__name__)
-
-
-class MonitorV2(Monitor):
-    """
-        A modified Environment Monitor that includes the following features:
-
-        - The stats recorder is a StatsRecorderV2, that implements additional features, including the environment seed
-        at each episode so that they can be reproduced
-        - The wrapped environment is closed with the monitor
-        - Video recording of all frames during an ongoing environment step
-        - Automatic saving of all fields of the stats recorder
-    """
-
-    def __init__(self, env, directory, video_callable=None, force=False, resume=True,
-                 write_upon_reset=False, uid=None, mode=None):
-        super(MonitorV2, self).__init__(env, directory, video_callable, force, resume, write_upon_reset, uid, mode)
-
-    def _start(self, directory, video_callable=None, force=False, resume=False, write_upon_reset=False, uid=None,
-               mode=None):
-        super(MonitorV2, self)._start(directory, video_callable, force, resume, write_upon_reset, uid, mode)
-        self.stats_recorder = StatsRecorderV2(directory,
-                                              '{}.episode_batch.{}'.format(self.file_prefix, self.file_infix)
-                                              , autoreset=self.env_semantics_autoreset, env_id=self.env.spec.id)
-
-    def seed(self, seed=None):
-        seeds = super(MonitorV2, self).seed(seed)
-        self.stats_recorder.seed = seeds[0]  # Not sure why gym envs typically return *a list* of one seed
-        return seeds
-
-    def reset_video_recorder(self):
-        # Close any existing video recorder
-        if self.video_recorder:
-            self._close_video_recorder()
-
-        # Start recording the next video.
-        self.video_recorder = video_recorder.VideoRecorder(
-            env=self.env,
-            base_path=os.path.join(self.directory,
-                                   '{}.video.{}.video{:06}'.format(self.file_prefix, self.file_infix, self.episode_id)),
-            metadata={'episode_id': self.episode_id},
-            enabled=self._video_enabled(),
-        )
-
-        # Instead of capturing just one frame, allow the environment to send all render frames when a step is ongoing
[…]

### 2020-10-13 supplementary/code/scripts/experiments.py

@@ -1,68 +1,0 @@
-"""
-Usage:
-  experiments evaluate <environment> <agent> [options]
-  experiments -h | --help
-
-Options:
-  -h --help              Show this screen.
-  --episodes <count>     Number of episodes [default: 1].
-  --no-display           Disable environment, agent, and rewards rendering.
-  --name-from-config     Name the output folder from the corresponding config files
-  --seed <str>           Seed the environments and agents.
-  --verbose              Set log level to debug instead of info.
-  --repeat <times>       Repeat several times [default: 1].
-"""
-import datetime
-import os
-from pathlib import Path
-from docopt import docopt
-
-from rl_agents.agents.common.factory import load_environment, load_agent
-from rl_agents.trainer import logger
-from rl_agents.trainer.evaluation import Evaluation
-
-BENCHMARK_FILE = 'benchmark_summary'
-LOGGING_CONFIG = 'configs/logging.json'
-VERBOSE_CONFIG = 'configs/verbose.json'
-
-
-def main():
-    opts = docopt(__doc__)
-    for _ in range(int(opts['--repeat'])):
-        evaluate(opts['<environment>'], opts['<agent>'], opts)
-
-
-def evaluate(environment_config, agent_config, options):
-    """
-        Evaluate an agent interacting with an environment.
-
-    :param environment_config: the path of the environment configuration file
-    :param agent_config: the path of the agent configuration file
-    :param options: the evaluation options
-    """
-    logger.configure(LOGGING_CONFIG)
-    if options['--verbose']:
-        logger.configure(VERBOSE_CONFIG)
-    env = load_environment(environment_config)
-    agent = load_agent(agent_config, env)
-    run_directory = None
-    if options['--name-from-config']:
-        run_directory = "{}_{}_{}".format(Path(agent_config).with_suffix('').name,
-                                  datetime.datetime.now().strftime('%Y%m%d-%H%M%S'),
-                                  os.getpid())
-    options['--seed'] = int(options['--seed']) if options['--seed'] is not None else None
-    evaluation = Evaluation(env,
-                            agent,
-                            run_directory=run_directory,
-                            num_episodes=int(options['--episodes']),
-                            sim_seed=options['--seed'],
-                            recover=False,
-                            display_env=not options['--no-display'],
-                            display_agent=not options['--no-display'],
-                            display_rewards=not options['--no-display'])
-    evaluation.test()
-    return os.path.relpath(evaluation.monitor.directory)
-
-
-if __name__ == "__main__":
-    main()

### 2020-10-13 paper/main.tex
Fix typos

@@
 In \Cref{sec:proof}, we provide a proof for every novel result introduced in this paper.
-\Cref{sec:attachments} describes the attached video files and source code.
 \Cref{sec:experimental-setting} provides additional details on our experiments.
@@
 $$M_n \eqdef \begin{bmatrix}
-A_N^\transp P + P A_N^\transp + Q_0 & P|D|  \\
+A_N^\transp P + P A_N + Q_0 & P|D|  \\
 |D|^\transp P & -\rho I_r \\
 \end{bmatrix}\text{ also converges to } M\eqdef\begin{bmatrix}
-A(\theta)^\transp P + P A(\theta)^\transp + Q_0 & P|D|  \\
+A(\theta)^\transp P + P A(\theta) + Q_0 & P|D|  \\
 |D|^\transp P & -\rho I_r \\
@@
 \end{proof}
-
-\section{Description of attached files}
-\label{sec:attachments}
-
-\paragraph{Videos}
-The \texttt{video} folder contains videos comparing trajectories of the oracle planner and \Cref{alg:full}.
-The oracle planner has access to the true dynamics and follows aggressive trajectories that nearly saturate the collision constraints.
-In contrast, the \Cref{alg:full} produces more conservative trajectories.
-In the obstacle experiment, we show the confidence ellipsoid over $\theta = (\theta_x,\theta_y)$ in the right panel.
-In the driving experiment, we show the multi-model rejection and robust selection procedure through the display of several trajectory hulls for all possible destinations of the observed vehicles.
-
-\paragraph{Source code}
-The attached \texttt{code} directory contains an implementation of \Cref{alg:full}.
-The \texttt{README.md} file relates the algorithmic steps of this paper to their location in the source code, and contains instructions to reproduce our experimental results.
 

### 2020-10-13 paper/main.tex
Minor changes

@@
 	Edouard~Leurent \\
-	Inria Lille Nord-Europe \& Renault\\
-	Paris, France\\
+	Univ. Lille, Inria, CNRS, Centrale Lille, UMR 9189 – CRIStAL, Renault\\
+	F-59000 Lille, France\\
 	\texttt{edouard.leurent@inria.fr} \\
-	% examples of more authors
 	 \And
 	 Denis~Efimov \\
-	 Inria Lille Nord-Europe, Valse team\\
-	 Lille, France\\
+	 Univ. Lille, Inria, CNRS, Centrale Lille, UMR 9189 – CRIStAL\\
+	 F-59000 Lille, France\\
 	 \texttt{denis.efimov@inria.fr} \\
@@
 	 Odalric-Ambrym~Maillard \\
-	 Inria Lille Nord-Europe, SequeL team\\
-	 Lille, France\\
+	 Univ. Lille, Inria, CNRS, Centrale Lille, UMR 9189 – CRIStAL\\
+	 F-59000 Lille, France\\
 	 \texttt{odalric.maillard@inria.fr} \\
@@
 since it applies to matrices $A_N$ produced by the algorithm rather than to the system parameters.
-A stronger but easier to check condition is that the polytope \eqref{eq:polytope} at some point becomes included in a set where this property is uniformly satisfied.
+A stronger but easier to check condition is that the polytope \eqref{eq:polytope} at some iteration becomes included in a set where this property is uniformly satisfied.
 For instance, if the features are sufficiently excited, the estimation converges to a neighbourhood of the true dynamics $A(\theta)$.

### 2020-10-15 paper/talk/talk.tex
Add beamer talk (no videos...)

\documentclass[slideopt,A4,showboxes,svgnames]{beamer}

%% list of packages here
\usepackage[absolute,showboxes,overlay]{textpos}
\usepackage{booktabs}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{pifont}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{array, makecell}
\usepackage{blkarray}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage[backend=biber, style=authoryear]{biblatex}
\renewcommand*{\nameyeardelim}{\addcomma\addspace}
\addbibresource{../references.bib}

\usepackage{theme/beamerthemeinria}
\input{mathdef}
\input{theme/style}

\title[Robust-Adaptive Control]{Robust-Adaptive Control\\of Linear Systems:\\beyond Quadratic Costs}
\subtitle{Sous-titre}
\date[date]{date}
\author[Edouard Leurent]{\textbf{Edouard Leurent}\inst{1,2},\\
	Odalric-Ambrym Maillard\inst{1},\\
	Denis Efimov\inst{1}}
\institute{
	\inst{1} Univ. Lille, Inria, CNRS, \\ ~Centrale Lille, UMR 9189 – CRIStAL,\\
	\inst{2} Renault Group}

\begin{document}

\begin{frame}
    \titlepage
\end{frame}

\begin{frame}{Motivation}
Most RL algorithms rely on trial and {\red error}
\begin{itemize}
	\item {\blue random} exploration
	\item {\green optimism} in the face of uncertainty
\end{itemize}
\leavevmode\newline
Our work: ensure safety at all time
\begin{itemize}
	\item {\red pessimism} in the face of uncertainty
	\item {\green learn} from observations
\end{itemize}
\end{frame}

\begin{frame}{Setting}
\begin{alertblock}{Dynamical priors with structured uncertainty}
	State $x$, control $u$, bounded disturbance $\omega$
	\begin{align*}
	\dot{x}(t) &= {\orange A(\theta)}x(t) + B u(t) + \omega(t),\\
	{\orange A(\theta)} &= A + \sum_{i=1}^d {\orange \theta_i}\phi_i,
	\end{align*}
	where $A,B,\phi_1,\dots,\phi_d$ are \alert{known}.
\end{alertblock}

\begin{alertblock}{Performance measure}
	\begin{itemize}
		\item Discounted return $\sum_n\gamma^n R(x(t_n))$.
		\item Reward $R$ only assumed to be \alert{bounded}.
	\end{itemize}
\end{alertblock}
\end{frame}

\begin{frame}{Robust control framework}
Given $N$ observations,
\begin{enumerate}
	\item Build a {\red confidence region} for the dynamics
	$$\probability{{\orange \theta}\in {\red \cC_{N,\delta}}} \geq 1-\delta,$$
	\item Maximize the {\red worst-case} performance ${\red V^r}$
	$${\green\sup_{\bu\in{(\Real^q)}^\Natural}} \underbrace{{\red\inf_{\substack{\theta \in \cC_{N,\delta} \\ \omega\in[\underline{\omega},\overline{\omega}]^\Real}}} \left[\sum_{n=N+1}^\infty \gamma^n R(x(t_n))\middle| {\green \bu},{\red \theta},{\red\omega}\right]}_{{\red V^r(\bu)}},$$
\end{enumerate}

Related work
\begin{itemize}
	\item Robust Dynamic Programming (finite states only)
	\item Linear-Quadratic setting (quadratic costs only)
\end{itemize}
\end{frame}

\begin{frame}{Algorithm 1/3}
\begin{block}{Model Estimation}
	Confidence ellipsoid from non-asymptotic linear regression.
	\[\| \theta_{N,\lambda}  - \theta\|_{G_{N,\lambda}} \leq \beta_N(\delta) \]
\end{block}

\begin{center}
	\includegraphics[width=0.4\linewidth]{../img/ellipsoid}
\end{center}

\end{frame}

\begin{frame}{Algorithm 2/3}
To optimise $V^r$ $\rightarrow$ approximate it by a tractable surrogate $\hat{V}^r$
\begin{block}{Interval Prediction} Propagate uncertainty ${\red \cC_{N,\delta}}$ through time and bound the state
	$${\blue \underline{x}(t)}\leq x(t)\leq{\blue \overline{x}(t)},\quad\forall t\geq t_N$$
\end{block}

\begin{center}
%	\includegraphics[width=0.6\linewidth]{../img/obstacle_small}
	\includegraphics[width=0.4\linewidth]{./img/interval-hull}
\end{center}

\end{frame}

\begin{frame}{Algorithm 3/3}

\begin{block}{Pessimistic Planning}
	Surrogate pessimistic return, maximized by tree based-planning
	\[{\orange \hat{V}^r(\bu)} \eqdef \sum_{n=N+1}^\infty \gamma^n \min_{x\in{\blue [\underline{x}(t_n), \overline{x}(t_n)]}}  R(x).\]
\end{block}
\begin{center}
	\includegraphics[trim={0 1.2cm 0 0}, clip, width=0.75\linewidth]{./img/planning}
\end{center}
\end{frame}

\begin{frame}{Results}
\begin{theorem}[Lower bound]
	\begin{equation*}
	{\orange \hat{V}^r(\bu)} \leq {\red V^r(\bu)} \leq V(u)
	\end{equation*}
\end{theorem}

\begin{theorem}[Suboptimality bound]
	Under two conditions:
	\begin{enumerate}
		\item Lipschitz rewards $R$:
		\item a stability condition over ${\red A(\theta_N)}$, for $N>N_0$
	\end{enumerate}
	we can bound the suboptimality with probability $1-\delta$ as:
	\begin{equation*}
	\underbrace{V(u_\star) - V(u_K)}_{\text{suboptimality}} \leq  {\red \underbrace{\Delta_\omega}_{\substack{\text{robustness to}\\ \text{disturbances}}}} + {\blue \underbrace{\cO\left(\frac{\beta_N(\delta)^2}{\lambda_{\min}(G_{N,\lambda})}\right)}_{\text{estimation error}}} + {\green \underbrace{\cO\left(K^{-\frac{\log 1/\gamma}{\log \kappa}}\right)}_{\text{planning error}}} 
	\end{equation*}
\end{theorem}
\end{frame}

\begin{frame}
\begin{corollary}[Asymptotic Near-Optimality]
	If the features $\phi_i x_n$ are \alert{persistently excited}, 
	\begin{itemize}
		\item the stability condition can be \alert{relaxed} to ${\orange A(\theta)}$ only
		\item the suboptimality bound takes the more explicit form
	\end{itemize}
	\begin{equation*}
	{V(u_\star) - V(u_K)}\leq  {\red \Delta_\omega} + {\blue {\cO\left(\frac{\log(N^{d/2}/\delta)}{N}\right)}} + {\green {\cO\left(K^{-\frac{\log 1/\gamma}{\log \kappa}}\right)}}
	\end{equation*}
	which ensures near-optimality as ${\blue N\to\infty}$ and ${\green K\to\infty}$.
\end{corollary}
\end{frame}

\begin{frame}{Experiments}

\end{frame}

\begin{frame}
\centering \LARGE Thank You!\\[1cm]
\large \emph{I am looking for a postdoctoral position.}
\end{frame}

\end{document}

### 2020-10-15 paper/main.tex
Update oral

@@
 Second, it relies on trial-and-error and random exploration.
-In order to overcome these shortages, and motivated by the path planning problem for a self-driving car, in this paper we consider the problem of controlling an unknown linear system $x(t)$ so as to maximise an \emph{arbitrary} bounded reward function $R$, in a critical setting where mistakes are costly and must be avoided at all time.
+In order to overcome these shortages, and motivated by the path planning problem for a self-driving car, in this paper we consider the problem of controlling an unknown linear system $x(t)$ so as to maximise an \emph{arbitrary} bounded reward function $R$, in a critical setting where mistakes are costly and must be avoided at all times.
 This choice of rich reward space is crucial to have sufficient flexibility to model non-convex and non-smooth functions that naturally arise in many practical problems involving combinatorial optimisation, branching decisions, etc., while quadratic costs are mostly suited for tracking a fixed reference trajectory \citep[e.g.][]{Kumar2013}.
@@
 Although the assumptions of \Cref{thm:minimax-regret-bound} are not satisfied (e.g.
-non-smooth reward), the mean regret of the robust agent, shown in \Cref{fig:regret}, still decreases polynomially with $N$: \Cref{alg:full} gets \emph{more efficient} as it is \emph{more confident} while \emph{ensuring safety} at all time.
+non-smooth reward), the mean regret of the robust agent, shown in \Cref{fig:regret}, still decreases polynomially with $N$: \Cref{alg:full} gets \emph{more efficient} as it is \emph{more confident} while \emph{ensuring safety} at all times.
 In contrast, the nominal agent has a smaller average regret but collides with obstacles in $4\%$ of simulations.
@@
 Again we also compare to a DQN baseline trained over 3000 episodes, causing $1058\pm113$ collisions while training ($35\pm4\%$).
-As before, the robust agent has a higher worst-case performance and avoids collisions at all time, at the price of a decreased average performance..
+As before, the robust agent has a higher worst-case performance and avoids collisions at all times, at the price of a decreased average performance..
 

### 2020-10-19 paper/main.tex
Update presentations
Minor updates
- rephrasing
- regret -> suboptimality
- add max suboptimality to the graph

@@
 In order to handle more general (non-convex) costs that naturally arise in many practical problems, we carefully select and bring together several tools from different communities, namely non-asymptotic linear regression, recent results in interval prediction, and tree-based planning.
-Combining and adapting the theoretical guarantees at each layer is non trivial, and we provide the first end-to-end regret analysis for this setting.
+Combining and adapting the theoretical guarantees at each layer is non trivial, and we provide the first end-to-end suboptimality analysis for this setting.
 Interestingly, our analysis naturally adapts to handle many models and combines with a data-driven robust model selection strategy, which enables to relax the modelling assumptions.
@@
 In \Cref{sec:control}, facing a sequential decision problem with continuous states, we turn to the literature of tree-based planning algorithms.
-Though there exist works addressing continuous actions \citep{Busoniu2018,Weinstein2012}, we resort to a first approximation and discretise the continuous decision $(\Real^q)^\Natural$ space by adopting a hierarchical control architecture: at each time, the agent can select a high-level \emph{action} $a$ from a finite space $\cA$.
+Although there exist works addressing continuous actions \citep{Busoniu2018,Weinstein2012}, we resort to a first approximation and discretise the continuous decision $(\Real^q)^\Natural$ space by adopting a hierarchical control architecture: at each time, the agent can select a high-level \emph{action} $a$ from a finite space $\cA$.
 Each action $a\in\cA$ corresponds to the selection of a low-level controller $\pi_a$, that we take affine: $u(t) = \pi_a(x(t)) \eqdef -K_a x(t) + u_a.$ For instance, a tracking a subgoal $x_g$ can be achieved with $\pi_g = K(x_g - x)$.
@@
 Our third contribution adapts them to the robust objective \eqref{eq:robust-control} by approximating it with a tractable surrogate $\hat{V}^r$ that exploits the interval predictions \eqref{eq:inclusion-property} to define a pessimistic reward.
-In our main result, we show that the best surrogate performance achieved during planning is guaranteed to be attained on the true system, and provide an upper bound for the approximation gap and simple regret of our framework in \Cref{thm:minimax-regret-bound}.
+In our main result, we show that the best surrogate performance achieved during planning is guaranteed to be attained on the true system, and provide an upper bound for the approximation gap and suboptimality of our framework in \Cref{thm:minimax-regret-bound}.
 This is the first result of this kind for maximin control with generic costs to the best of our knowledge.
@@
 However, neither optimism nor random exploration fit a critical setting, where ensuring safety requires instead to consider pessimistic outcomes.
-The work of \citet{Dean2017} is close to our setting: after an offline estimation phase, they estimate a simple regret between a minimax controller and the optimal performance.
+The work of \citet{Dean2017} is close to our setting: after an offline estimation phase, they estimate a suboptimality between a minimax controller and the optimal performance.
 Our work differs in that it addresses a generic shape cost.
@@
 \begin{equation*}
-\hat{V}^r(\bu) \leq V^r(\bu)
+\hat{V}^r(\bu) \leq V^r(\bu) \leq V(\bu)
 \end{equation*}
@@
 		\end{equation*}
-		with probability at least $1-\delta$, where $V(a)$ is the optimal expected return after executing an action $a\in\cA$, $a_\star$ is an optimal action, and $\hlr{\Delta_\omega}$ is a constant which corresponds to an irreducible suboptimality suffered from being robust to instantaneous disturbances $\omega(t)$.
+		with probability at least $1-\delta$, where $V(a)$ is the optimal expected return when executing an action $a\in\cA$, $a_\star$ is an optimal action, and $\hlr{\Delta_\omega}$ is a constant which corresponds to an irreducible suboptimality suffered from being robust to instantaneous disturbances $\omega(t)$.
 \end{theorem}
@@
 		\exists \underline{\phi},\overline{\phi}>0: \forall n\geq n_0,\quad \underline{\phi}^2 \leq \lambda_{\min}(\Phi_{n}^\transp\Sigma_{p}^{-1}\Phi_{n}) \leq \overline{\phi}^2,
-		\end{align} the stability condition 2. of \Cref{thm:minimax-regret-bound} can be relaxed to its limit: there exist $P,Q_0,\rho$ such that
+		\end{align} the stability condition 2. of \Cref{thm:minimax-regret-bound} can be relaxed to apply to the true system: there exist $P,Q_0,\rho$ such that
 		$$\begin{bmatrix}
@@
 This highlights the benefits of the robust formulation solely rather than stemming from algorithm design.
-We show in \Cref{tab:obstacle} the results of 100 simulations of a single episode: the robust agent performs worse than the nominal agent on average, but manages to ensure safety and attains a better worst-case performance.
+We show in \Cref{tab:obstacle} the results of 100 simulations of a single episode: the robust agent performs worse than the nominal agent on average, but manages to ensure safety while the nominal agent collides with obstacles in $4\%$ of simulations.
 We also compare to a standard model-free approach, DQN, which does not benefit from the prior knowledge on the system dynamics, and is instead trained over multiple episodes.
 The reported performance is that of the final policy obtained after training for 3000 episodes, during which $897\pm64$ collisions occurred ($29.9\pm2.1$\%).
-We also study the evolution of the simple regret $V(x_N) - \hat{V}^r(x_N)$ with respect to the number of samples $N$, by comparing the empirical returns from a state $x_N$ to the value $V(x_N)$ that the agent would get by acting optimally from $x_N$ with knowledge of the dynamics.
+We study the evolution of the suboptimality $V(x_N) - \sum_{n>N}\gamma^{n-N}R(x_n)$ with respect to the number of samples $N$, by comparing the empirical returns from a state $x_N$ to the value $V(x_N)$ that the agent would get by acting optimally from $x_N$ with knowledge of the dynamics.
 Although the assumptions of \Cref{thm:minimax-regret-bound} are not satisfied (e.g.
-non-smooth reward), the mean regret of the robust agent, shown in \Cref{fig:regret}, still decreases polynomially with $N$: \Cref{alg:full} gets \emph{more efficient} as it is \emph{more confident} while \emph{ensuring safety} at all times.
-In contrast, the nominal agent has a smaller average regret but collides with obstacles in $4\%$ of simulations.
+non-smooth reward), the mean suboptimality of the robust agent, shown in \Cref{fig:regret}, still decreases polynomially with $N$: \Cref{alg:full} gets \emph{more efficient} as it is \emph{more confident} while \emph{ensuring safety} at all times.
+In comparison, the nominal agent enjoys a smaller suboptimality on average, but higher in the worst-case.
 
@@
 		\includegraphics[trim={0 0.2cm 0 0.2cm}, clip, width=0.9\linewidth]{img/regret.pdf}
-		\caption{The mean regret along with its $95\%$ confidence interval with respect to $N$, for the robust and nominal agents.}
+		\caption{The mean (solid), $95\%$ CI (shaded) and maximum (dashed) suboptimality with respect to $N$.}
 		\label{fig:regret}
@@
 We present a framework for the robust estimation, prediction and control of a partially known linear system with generic costs.
-Leveraging tools from linear regression, interval prediction, and tree-based planning, we guarantee the predicted performance and provide a regret bound.
+Leveraging tools from linear regression, interval prediction, and tree-based planning, we guarantee the predicted performance and provide a suboptimality bound.
 The method applicability is further improved by a multi-model extension and demonstrated on two simulations.
@@
 	The predictor designed in \Cref{sec:prediction} verifies the inclusion property \eqref{eq:inclusion-property}.
-Thus, for sequence of controls $\bu$, any dynamics $A(\theta)\in C_{N,\delta}$, and disturbances $\underline{\bom} \leq \bom \leq \overline{\bom}$, the corresponding state at time $t_n$ is bounded by $\underline{x}_n \leq x_n \leq \overline{x}_n$, which implies that $R(x_n) \geq \min_{x\in[\underline{x}_n(\bu), \overline{x}_n(\bu)]}  R(x) = \underline{R}_n(\bu)$.
-
-	Thus, by taking the min over $C_{N,\delta}$ and $[\underline{\bom}, \overline{\bom}]$, we also have for any sequence of controls $\bu$:
-	\begin{align*}
-	    V^r(\bu) &= \min_{\substack{A(\theta)\in C_{N,\delta}\\ \underline{\bom} \leq \bom \leq \overline{\bom}}} \sum_{n=N+1}^\infty \gamma^n R(x_n)\\
+Thus, for sequence of controls $\bu$, any dynamics $A(\theta)\in C_{N,\delta}$, and disturbances $\underline{\omega} \leq \omega \leq \overline{\omega}$, the corresponding state at time $t_n$ is bounded by $\underline{x}_n \leq x_n \leq \overline{x}_n$, which implies that $R(x_n) \geq \min_{x\in[\underline{x}_n(\bu), \overline{x}_n(\bu)]}  R(x) = \underline{R}_n(\bu)$.
+
+	Thus, by taking the min over $C_{N,\delta}$ and $[\underline{\omega}, \overline{\omega}]$, we also have for any sequence of controls $\bu$:
+	\begin{align*}
+	    V^r(\bu) &= \min_{\substack{A(\theta)\in C_{N,\delta}\\ \underline{\omega} \leq \omega \leq \overline{\omega}}} \sum_{n=N+1}^\infty \gamma^n R(x_n)\\
 	    &\geq \sum_{n=N+1}^\infty \gamma^n \underline{R}_n(\bu)\\
@@
 	\end{align*}
+
+	And  $V^r(\bu) \leq V(\bu) = \expectedvalue_\omega \left[\sum_{n=N+1}^\infty \gamma^n R(x_n)\right]$ by definition.
 \end{proof}
